### 2020-12-04 r_notebooks/exploring_gp_data.Rmd
Adding files from local work

---
title: "GP data"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(lubridate)
library(janitor)

#### Functions ####

read_interim <- function(path){ # Read processed files in
  if (str_detect(path, ".rds")) {
    read_rds(paste0("../OneDrive/2_interimdata/", path))
  } else
    if  (str_detect(path, ".csv")) {
      read_csv(paste0("../OneDrive/2_interimdata/", path))
    } else
      stop("File is not .rds or .csv")
}

interim_explore <- function(x){ # Summary of data
  glimpse(x)
  DataExplorer::plot_missing(x)
  DataExplorer::plot_bar(x)
  DataExplorer::plot_histogram(x)
  janitor::get_dupes(x)
}

```

## Reading data in

```{r}
gp_analysis <- read_interim("2_gpanalysis/gpanalysis1.rds")
wimd <- read_interim("3_wimd/lsoa_wimd_2019.csv")
agesex <- read_interim("5_agesexdata/gp_agesexdata_combined.rds")
qof <- read_interim("6_qof/gp_qof_dregs_combined.rds")
phwo <- read_interim("7_phwodata/gp_phwo_summary_2015.csv")

```

## agesex

```{r}
glimpse(agesex)
DataExplorer::plot_missing(agesex)
```
* npat could be used to replace missing data in `gp_analysis`
* Age by sex data is stored as the number of patients in an age range

## gp_analysis

```{r}
interim_explore(gp_analysis)
```
* Missing some northing and eastings but not postcodes - fixable either with additional data or manual search
* Missing number of GPs - fixable using manual search?
* Missing `nprespats` - Replace using agesex data?

```{r}
df <- left_join(filter(gp_analysis, year == 2020), agesex, by = "PracticeID")
cor.test((df$nprespats + df$ndisppats), df$npat)
plot((df$nprespats + df$ndisppats), df$npat)
plot(lm((df$nprespats + df$ndisppats) ~ df$npat))
```
* Why is the correlation not higher? There appear to be some major discrepancies in the two numbers.
  * Which year is the `agesex` data from?
  * Is r = `r round(cor((df$nprespats + df$ndisppats), df$npat, use = "complete.obs"), 2)` high enough to replace missing data?
  * Which data is more reliable?
  * r is higher by ~ .04 when `nprespats + ndisppats)` which is probs high enough
  * Would the `agedata` data be better to use as it relates to the distribution of pts by age and sex? Or once that is made into percentages would the rounding errors be greater than the difference in data quality?

```{r}
agesex %>% 
  mutate(female_sum = if_else(npat_fem == nf_0_4 + nf_5_14 + nf_15_44 + nf_45_64 + nf_65_74 + nf_75_84 + nf_85, TRUE, FALSE),
         male_sum = if_else(npat_male == nm_0_4 + nm_5_14 + nm_15_44 + nm_45_64 + nm_65_74 + nm_75_84 + nm_85, TRUE, FALSE)) %>% 
  filter(female_sum == FALSE | male_sum == FALSE)

agesex %>% 
  filter(PracticeID == "W00100")
```

* What is `hlthau`?
* Why are there `r nrow(gp_analysis)` cases when there are far fewer in the other data files?
  * There are multiple years of data (2013-2020)
  * `r nrow(filter(gp_analysis, year == 2020))` Practices in 2020

## phwo

```{r}
interim_explore(phwo)
```

## qof

```{r}
glimpse(qof)
DataExplorer::plot_histogram(qof)
DataExplorer::plot_correlation(qof)
```

## wimd

```{r}
interim_explore(wimd)
```
## Linked data

```{r}
gp_linked <- 
  gp_analysis %>% 
  filter(year == 2020) %>% 
  full_join(agesex, by = "PracticeID") %>% 
  full_join(phwo, by = "PracticeID") %>% 
  full_join(qof, by = "PracticeID") #%>% 
  #left_join(wimd, by = "lsoacode") already included in the data

Amelia::missmap(gp_linked)

```

### GPCluster

* `GPClyster` is in three datasets:
  * `agesex`
  * `phwo`
  * `qof`

```{r}
clus_disagree <- gp_linked %>% 
  select(PracticeID, starts_with("GPC")) %>% 
  mutate(miss = is.na(GPCluster.x) + is.na(GPCluster.y) + is.na(GPCluster),
         agree = if_else((GPCluster.x == GPCluster.y & 
                             GPCluster.x == GPCluster &
                             GPCluster.y == GPCluster), TRUE, FALSE)) %>% 
  filter(agree != TRUE)

clus_miss <- gp_linked %>% 
  select(PracticeID, starts_with("GPC")) %>% 
  mutate(miss = is.na(GPCluster.x) + is.na(GPCluster.y) + is.na(GPCluster),
         agree = if_else((GPCluster.x == GPCluster.y & 
                             GPCluster.x == GPCluster &
                             GPCluster.y == GPCluster), TRUE, FALSE)) %>% 
  filter(miss == 3)

str_detect(gp_linked$GPCluster, "Mold, Buckley & Caergwle") %>% sum(na.rm = T)
str_detect(gp_linked$GPCluster, "South Flintshire") %>% sum(na.rm = T)
str_detect(gp_linked$GPCluster.y, "Mold, Buckley & Caergwle") %>% sum(na.rm = T)
str_detect(gp_linked$GPCluster.y, "South Flintshire") %>% sum(na.rm = T)

gp_linked %>% 
  filter(GPCluster.y == "Mold, Buckley & Caergwle") %>% 
  select(starts_with("GPC"))
```

* `r nrow(clus_disagree)` Practices have different cluster names across the data files
  * Some of these look like different names for the same thing
    * "North & West Wrexham" & "West & North Wrexham"
    * "South Flintshire" & "Mold, Buckley & Caergwle"
* `r nrow(clus_miss)` Practices have no cluster name

## Write rds

```{r}
gp_linked %>% 
  na.omit() %>% 
  write_rds("../data/gp_linked_na_omit.rds")
```

### 2020-12-04 r_notebooks/exploring_hydroxychloroquine_sulphate.Rmd
Adding files from local work

---
title: "Exploring Hydroxychloroquine Sulfate"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(lubridate)
library(rstan) # needed to load prophet
library(prophet)
```

BNF code: 1001030C0

```{r prep-data}
con <- DBI::dbConnect(RSQLite::SQLite(), "../OneDrive/1_data/gpextract/db-gpextract.sqlite")
db.gpextract <- tbl(con, "gpextract")

chlor <- db.gpextract %>% 
  filter(bnfchem %in% "1001030C0") %>% 
  collect() %>% 
  mutate(datename = dmy(paste0("01-", datename))) # Add day component to date and convert to date-time object

chlor_monthly_count <- chlor %>% 
  group_by(datename) %>% 
  count()

chlor_monthly_count$datename %>% unique()

chlor_monthly_count_pre_cv19 <- chlor %>% 
  filter(datename < dmy("01-03-2020")) %>% 
  group_by(datename) %>% 
  count()
```

```{r chlor-monthly-ts-plot}
chlor_monthly_count %>% 
  ggplot(aes(x = datename, y = n)) +
  geom_line() +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

```{r chlor-monthly-models}
# RW model
chlor_rw_model <-
  arima(as.ts(chlor_monthly_count_pre_cv19$n), order = c(0, 1, 0))
# 1st order MA model
chlor_ma1_model <-
  arima(as.ts(chlor_monthly_count_pre_cv19$n), order = c(0, 0, 1))

print(chlor_rw_model)

# Prophet model
chlor_prophet_model <- 
  prophet(df = chlor_monthly_count_pre_cv19 %>% 
            transmute(ds = datename, y = n)) # data in prophet format
future <- make_future_dataframe(chlor_prophet_model, periods = 5)
prophet_forecast <- predict(chlor_prophet_model, future)
```

```{r chlor-monthly-models-plots}
chlor_monthly_count %>% 
  ggplot(aes(x = datename, y = n)) +
  geom_line() +
  geom_ribbon(aes(ymin = c(rep(NA,50), 
                           (predict(chlor_rw_model, n.ahead = 5)$pred) - 
                             1.96*predict(chlor_rw_model, n.ahead = 5)$se),
                  ymax = c(rep(NA,50), 
                           (predict(chlor_rw_model, n.ahead = 5)$pred) + 
                             1.96*predict(chlor_rw_model, n.ahead = 5)$se)),
              alpha = .1, fill = "blue") +
  geom_ribbon(aes(ymin = c(rep(NA,50), prophet_forecast[51:55,]$yhat_lower),
                  ymax = c(rep(NA,50), prophet_forecast[51:55,]$yhat_upper)),
              alpha = .1, fill = "green") +
  geom_line(aes(y = c(chlor_monthly_count[1:50,]$n - chlor_rw_model$residuals, rep(NA, 5))),
            col = "blue", lty = 2) +
  geom_line(aes(y = c(chlor_monthly_count[1:50,]$n - chlor_ma1_model$residuals, rep(NA, 5))),
            col = "cyan", lty = 2) +
  geom_line(aes(y = c(prophet_forecast[1:50,]$yhat, rep(NA, 5))),
            col = "green", lty = 2) +
  geom_line(aes(y = c(rep(NA,50), predict(chlor_rw_model, n.ahead = 5)$pred)),
            col = "blue", lty = 3) +
  geom_line(aes(y = c(rep(NA,50), predict(chlor_ma1_model, n.ahead = 5)$pred)),
            col = "cyan", lty = 3) +
  geom_line(aes(y = c(rep(NA,50), prophet_forecast[51:55,]$yhat)),
            col = "green", lty = 3) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

Look at `fable` package and prohpet version too for forecasting

### 2020-12-04 r_notebooks/exploring_oral_anticoagulants.Rmd
Adding files from local work

---
title: "Oral contraceptives"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

## Functions
countRegional <- function(data, region, datename = datename, unit = Quantity){
 # Function to create tsibble object for a count of `unit` per `datename`
  # e.g. countRegional(oac, Locality, datename, Quantity) is the `Quantity`
  # per `datename` grouped by `Locality` from `oac`. `Quantity` is corrected for
  # the number of days in each month.
  region <- enquo(region)
  datename <- enquo(datename)
  unit <- enquo(unit)

  data %>% 
  mutate(regional_unit = as_factor(set_names(!!region))) %>% 
  group_by(regional_unit, !!datename) %>% 
  summarise(n = sum(!!unit),
            npat = sum(npat)) %>% 
  mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
                       str_detect(!!datename, pattern = "-02-") ~ n/28.25,
                       str_detect(!!datename, pattern = "-03-") ~ n/31,
                       str_detect(!!datename, pattern = "-04-") ~ n/30,
                       str_detect(!!datename, pattern = "-05-") ~ n/31,
                       str_detect(!!datename, pattern = "-06-") ~ n/30,
                       str_detect(!!datename, pattern = "-07-") ~ n/31,
                       str_detect(!!datename, pattern = "-08-") ~ n/31,
                       str_detect(!!datename, pattern = "-09-") ~ n/30,
                       str_detect(!!datename, pattern = "-10-") ~ n/31,
                       str_detect(!!datename, pattern = "-11-") ~ n/30,
                       str_detect(!!datename, pattern = "-12-") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = !!datename, key = regional_unit)
}

regionalPlot <- function(region, data){

  ## Prophet forecast - can this be taken outside of the function?
      ## no, when it is taken outside of the model, the forecast is becomes 
      ## much worse 2020-11-14
  df <- data %>%
    filter(regional_unit == region & datename < ymd("2020-03-23")) %>%
    transmute(ds = datename, y = n)

  m <- prophet::prophet(df, holidays = holidays,
                        seasonality.mode = "additive",# mcmc.samples = 1000,
                        weekly.seasonality = FALSE, daily.seasonality = FALSE)
  future <- make_future_dataframe(m, periods = 5, freq = 'month')
  fcst <- predict(m, future)

  ## Plotting
  plot <- fcsts %>% 
    filter(regional_unit == region) %>% 
    fabletools::autoplot(data, level = 80) + # fable forecasts over observed data
    geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)), # prophet prediction
              col = "blue", lty = 3) +
    geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower), # prophet confidence
                    ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
                alpha = .3, fill = "blue") +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") + # add line to mark the start of lockdown
    labs(title = region)

  ## Results
  result <- list("plots" = plot)#, "prophet" = fcst)
  return(result)
}
```

## Preparing data

```{r prep-data}
## Drugs of interest
oral_anticoagulants <- 
  c("0208020H0", "0208020Z0", "0208020X0", "0208020AA", "0208020W0", 
    "020802000", "0208020I0", "0208020N0", "0208020S0", "0208020Y0", 
    "0208020V0")

# ## Read from database
# con <- DBI::dbConnect(RSQLite::SQLite(), 
#                       "../OneDrive/1_data/gpextract/db-gpextract.sqlite")
# db.gpextract <- tbl(con, "gpextract")
# oac <- db.gpextract %>%
#   filter(bnfchem %in% oral_anticoagulants) %>%
#   collect() %>%
#   mutate(datename = dmy(paste0("28-", datename)))  # Add day component to date and convert to date-time object
# DBI::dbDisconnect(con)
# 
# ## Write to local file
# oac %>%
#   write_rds("../data/oral_anticoagulants.rds")

## Read from local file
gp <- read_rds("../data/gp_linked_na_omit.rds")
oac <- read_rds("../data/oral_anticoagulants.rds")

## Sort into monthly count data
oac_monthly_count <- oac %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31
                             )) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

oac_monthly_quantity_locality <- 
  right_join(oac, select(gp, c(PracticeID, npat, GPCluster)), 
             by = c("PracticeID" = "PracticeID")) %>%
  countRegional(., Locality, datename, Quantity)

oac_monthly_quantity_cluster <- 
  right_join(oac, select(gp, c(PracticeID, npat, GPCluster)), 
             by = c("PracticeID" = "PracticeID")) %>%
  countRegional(., GPCluster, datename, Quantity) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_monthly_quantity_gp <- 
    right_join(oac, select(gp, c(PracticeID, npat, GPCluster)), 
             by = c("PracticeID" = "PracticeID")) %>% 
  countRegional(., PracticeID, datename, Quantity)%>% 
  mutate(n = 1000*n/npat)

## Sort into monthly count data pre-lockdown (2020-03-23)
oac_monthly_count_pre_cv19 <- 
  oac_monthly_count %>% 
  filter(datename < dmy("01-03-2020"))

oac_monthly_quantity_locality_pre_cv19 <- 
  oac_monthly_quantity_locality %>% 
    filter(datename < dmy("01-03-2020"))

oac_monthly_quantity_cluster_pre_cv19 <- 
  oac_monthly_quantity_cluster %>% 
    filter(datename < dmy("01-03-2020"))

oac_monthly_quantity_gp_pre_cv19 <- 
  oac_monthly_quantity_gp %>% 
    filter(datename < dmy("01-03-2020"))

```

## Overview

### 2016-2020 plot of all oac prescriptions

```{r oac-monthly-ts-plot, fig.cap="Total quantity of combined hormonal and progestogen only oral contraceptives prescribed per month."}
oac %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  tsibble() %>% 
  autoplot(n) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

* General negative trend
* Seasonality unclear
  * Holiday effect? Drop in prescribing in Dec 2016-2019 followed by peak in Jan for 2017-2020.

### Seasonality

```{r oac-monthly-seasonality-plot}
df <- oac_monthly_count_pre_cv19 %>% 
  mutate(month = as.factor(month(datename, label = TRUE, abbr = TRUE)),
         year = as.factor(year(datename)))

df2 <- df %>% 
  as_tibble() %>% 
  filter(year(datename) != 2020) %>% 
  group_by(month) %>% 
  summarise(n = mean(n))

df %>% 
  ggplot(aes(x = month, y = n, colour = year, group = year)) +
  geom_line() +
  geom_line(data = df2, aes(x = month, y = n, group = "Avg"), 
            colour = "red", lty = 2) +
  labs(caption = "Red dashed line is mean for 2016-2019")

```
*

```{r}
oac_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  gg_subseries(y = n, period = "year")
```

*

### By `Quantity`

*

### By `Items`

*

### Lag plots

```{r}
oac_monthly_count_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>% 
  gg_lag(y = n, geom = "point", lags = 1:12)
```

* Here the colours indicate the month of the variable on the y-axis. The relationship is strongest at lag 3, 6, 9, and 12 suggesting seasonal data

### Autocorrelation

```{r}
tseries::adf.test(oac_monthly_count$n)
urca::ur.df(oac_monthly_count$n)
```

```{r}
oac_monthly_count_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>% 
  ACF(n, lag_max = 24) %>% autoplot()
```

* Autocorrelation greatest at 2 and 12

```{r}
oac_monthly_count_pre_cv19$n %>%
  pacf(lag.max = 24)
```

## Time series components

```{r}
dcmp <- 
  oac_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(STL(n))

oac_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  autoplot(n, color = "grey") + 
  autolayer(components(dcmp), trend, color = "red")

components(dcmp) %>% 
  autoplot()
```

```{r}
oac_monthly_count %>% 
  mutate(datename = yearmonth(datename)) %>% 
  autoplot(n, color = "grey") + 
  autolayer(components(dcmp), season_adjust, colour = "blue") +
  labs(title = "Seasonally adjusted")
```

## Moving average

```{r}
df <- oac_monthly_count %>% 
  mutate(datename = yearmonth(datename),
         `5-MA` = slider::slide_dbl(n, mean, .before = 2, .after = 2, 
                                    .complete = TRUE),
         `12-MA` = slider::slide_dbl(n, mean, .before = 5, .after = 6, 
                                    .complete = TRUE),
         `2x12-MA` = slider::slide_dbl(`12-MA`, mean, .before = 2, .after = 2, 
                                    .complete = TRUE),
         )
df %>% 
  autoplot(n) + 
  autolayer(df, `5-MA`, colour = "red") +
  autolayer(df, `2x12-MA`, colour = "blue") +
  labs(caption = "Daily prescriptions (black) along with the 5-MA estimate of the trend-cycle (red) and 2x12-MA (blue).")
```

## Predictions by `Locality`

```{r}
regions <- unique(as.character(oac_monthly_quantity_locality$regional_unit))
holidays <- 
  bind_rows(tibble(holiday = "christmas",
                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
                                  "2019-12-25", "2020-12-25", "2021-12-25")),
                   lower_window = -1, 
                   upper_window = 1),

            tibble(holiday = "easter",
                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
                                  "2019-04-21", "2020-04-12", "2021-04-04")),
                   lower_window = -1, 
                   upper_window = 1))

fit <- oac_monthly_quantity_locality_pre_cv19 %>% 
  # filter(year(datename) > 2016) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
        trend_model2 = TSLM(n ~ trend() + season()),
        #ets1 = ETS(n ~ trend()),
        ets2 = ETS(n ~ trend() + season()),
        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),
        #comb1 = combination_model(TSLM(n ~ trend()), ETS(n ~ trend())),
        comb2 = combination_model(TSLM(n ~ trend() + season()), 
                                  ETS(n ~ trend() + season())),
        # stl_dcmp1 = decomposition_model(STL(n ~ trend(),
        #                                    iterations = 1000, robust = FALSE),
        #                                NAIVE(season_adjust)),
        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
                                            iterations = 1000, robust = FALSE),
        SNAIVE(season_adjust)),
        s_naive = SNAIVE(n)
  )

fcsts <-  fit %>% 
  forecast(h = "6 months", bootstrap = FALSE) # can use `times = x` to control the number of samples

# single thread
regional_plots <- 
  map(.x = regions, 
      .f = ~regionalPlot(.x, oac_monthly_quantity_locality))

regional_plots

left_join(accuracy(fit),
          fit %>% 
            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
            report(), 
by = c("regional_unit", ".model"))

fit %>% 
  accuracy() %>% 
  group_by(.model) %>% 
  summarise(across(is.numeric, .fns = ~mean(., na.rm = TRUE)))

```

* https://fabletools.tidyverts.org/reference/combination_model.html

### Residual diagnostics

```{r}
augment(fit) %>% 
  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
```

## Predictions by `GPCluster`

```{r}
regions <- unique(as.character(gp$GPCluster))
holidays <- 
  bind_rows(tibble(holiday = "christmas",
                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
                                  "2019-12-25", "2020-12-25", "2021-12-25")),
                   lower_window = -1, 
                   upper_window = 1),

            tibble(holiday = "easter",
                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
                                  "2019-04-21", "2020-04-12", "2021-04-04")),
                   lower_window = -1, 
                   upper_window = 1))

fit <- oac_monthly_quantity_cluster_pre_cv19 %>% 
    filter(regional_unit %in% gp$GPCluster) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
        trend_model2 = TSLM(n ~ trend() + season()),
        ets2 = ETS(n ~ trend() + season()),
        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),

        comb2 = combination_model(TSLM(n ~ trend() + season()), 
                                  ETS(n ~ trend() + season())),
        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
                                            iterations = 1000, robust = FALSE),
        SNAIVE(season_adjust)),
        # s_naive = SNAIVE(n)
  )

fcsts <-  fit %>% 
  forecast(h = "5 months", bootstrap = FALSE) # can use `times = x` to control the number of samples

# single thread
regional_plots <- 
  map(.x = regions, 
      .f = ~regionalPlot(.x, filter(oac_monthly_quantity_cluster, 
                                    regional_unit %in% oac_monthly_quantity_cluster$regional_unit)))

regional_plots

left_join(accuracy(fit),
          fit %>% 
            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
            report(), 
by = c("regional_unit", ".model"))

fit %>% 
  accuracy() %>% 
  group_by(.model) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

```

### Residual diagnostics

```{r}
augment(fit) %>% 
  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
```

## Predictions by `PracticeID`

```{r}
regions <- unique(as.character(gp$PracticeID))
holidays <- 
  bind_rows(tibble(holiday = "christmas",
                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
                                  "2019-12-25", "2020-12-25", "2021-12-25")),
                   lower_window = -1, 
                   upper_window = 1),

            tibble(holiday = "easter",
                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
                                  "2019-04-21", "2020-04-12", "2021-04-04")),
                   lower_window = -1, 
                   upper_window = 1))

fit <- oac_monthly_quantity_gp_pre_cv19 %>% 
    filter(regional_unit %in% gp$PracticeID) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
        trend_model2 = TSLM(n ~ trend() + season()),
        ets2 = ETS(n ~ trend() + season()),
        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),

        comb2 = combination_model(TSLM(n ~ trend() + season()), 
                                  ETS(n ~ trend() + season())),
        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
                                            iterations = 1000, robust = FALSE),
        SNAIVE(season_adjust)),
        # s_naive = SNAIVE(n)
  )

fcsts <-  fit %>% 
  forecast(h = "5 months", bootstrap = FALSE) # can use `times = x` to control the number of samples

# single thread
regional_plots <- 
  map(.x = regions, 
      .f = ~regionalPlot(.x, filter(oac_monthly_quantity_gp, 
                                    regional_unit %in% gp$PracticeID)))

regional_plots

left_join(accuracy(fit),
          fit %>% 
            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
            report(), 
by = c("regional_unit", ".model"))

fit %>% 
  accuracy() %>% 
  group_by(.model) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

```

### Residual diagnostics

```{r}
augment(fit) %>% 
  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
```

## Overview of each drug

```{r}
oac %>% 
  group_by(datename, chemname) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
                       str_detect(datename, pattern = "-02-") ~ n/28.25,
                       str_detect(datename, pattern = "-03-") ~ n/31,
                       str_detect(datename, pattern = "-04-") ~ n/30,
                       str_detect(datename, pattern = "-05-") ~ n/31,
                       str_detect(datename, pattern = "-06-") ~ n/30,
                       str_detect(datename, pattern = "-07-") ~ n/31,
                       str_detect(datename, pattern = "-08-") ~ n/31,
                       str_detect(datename, pattern = "-09-") ~ n/30,
                       str_detect(datename, pattern = "-10-") ~ n/31,
                       str_detect(datename, pattern = "-11-") ~ n/30,
                       str_detect(datename, pattern = "-12-") ~ n/31
                             )) %>% 
  as_tsibble(index = datename, key = chemname) %>% 
  autoplot(n) +
  # theme(legend.position = "none") +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

## Modelling

### Prophet

```{r}
# Prophet model
oac_prophet_model <- 
  fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
                           season("year", type = "additive") + holiday(holidays))

fit <- oac_monthly_quantity_locality_pre_cv19 %>% 
  as_tsibble(index = datename) %>% 
  model(oac_prophet_model)

fc <- 
  fit %>% 
  forecast(h = "5 months")

accuracy(fit)

df <- oac_monthly_count_pre_cv19 %>% 
  transmute(ds = datename, y = n)
m <- prophet::prophet(df, seasonality.mode = "additive")
future <- make_future_dataframe(m, periods = 6, freq = 'month')
fcst <- predict(m, future)
prophet_plot_components(m, fcst)

oac_monthly_count %>% 
  ggplot(aes(x = datename, y = n)) +
  geom_line() +
  geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower),
                  ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
              alpha = .1, fill = "blue") +
  geom_line(aes(y = c(fcst[1:50,]$yhat, rep(NA, 5))),
            col = "blue", lty = 2) +
  geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)),
            col = "blue", lty = 3) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown

perf <- cross_validation(model = m, initial = 3*52, horizon = 52, units = "weeks")
performance_metrics(perf)
plot_cross_validation_metric(perf, metric = "rmse")
```

## Split by practice

```{r}
oac %>% 
  tibble %>% 
  group_by(datename, PracticeID) %>% 
  count %>% 
  group_by(PracticeID) %>% 
  summarise(n_min = min(n), 
            n_mean = mean(n)) %>% arrange((n_min)) %>% 
  filter(n_min >1)

oac %>% filter(PracticeID == "W91626") %>% 
  group_by(datename) %>% 
  count() %>% 
  as_tsibble(index = datename) %>% 
  autoplot()

```

### 2020-12-04 r_notebooks/exploring_oral_contraceptives.Rmd
Adding files from local work

---
title: "Oral contraceptives"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)
options(future.rng.onMisue = "ignore")

## Seed
set.seed(32)

## Functions
source("../r_scripts/functions.r")

## Drugs of interest
combined_hormonal <- 
  c("0703010E0", "0703010F0", "0703010G0", "0703010H0", "0703010M0",
    "0703010S0", "0703010R0","0703010A0", "0703010P0")
progestogen_only <- 
  c("0703021Q0", "0703022P0", "0703021C0", "0703021L0", "0703023L0",
    "0703022M0", "0703021N0", "0703022N0", "0703021P0")

oral_contraceptives <- c(combined_hormonal, progestogen_only)

## Read from database
# con <- DBI::dbConnect(RSQLite::SQLite(), "../OneDrive/1_data/gpextract/db-gpextract.sqlite")
# db.gpextract <- tbl(con, "gpextract")
# 
# oc <- db.gpextract %>%
#   filter(bnfchem %in% oral_contraceptives) %>%
#   collect() %>%
#   mutate(datename = dmy(paste0("28-", datename)))  # Add day component to date and convert to date-time object

## Write to local file
# oc %>%
#   write_rds("../data/oral_contraceptives.rds")

## Read from local file
gp <- read_rds("../data/gp_linked_na_omit.rds")
oc <- read_rds("../data/oral_contraceptives.rds")

## Sort into monthly count data
# oc_monthly_count <- oc %>% 
#   group_by(datename) %>% 
#   summarise(n = sum(Quantity)) %>% 
#   mutate(datename = yearmonth(datename),
#          n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
#                        str_detect(datename, pattern = "-02-") ~ n/28.25,
#                        str_detect(datename, pattern = "-03-") ~ n/31,
#                        str_detect(datename, pattern = "-04-") ~ n/30,
#                        str_detect(datename, pattern = "-05-") ~ n/31,
#                        str_detect(datename, pattern = "-06-") ~ n/30,
#                        str_detect(datename, pattern = "-07-") ~ n/31,
#                        str_detect(datename, pattern = "-08-") ~ n/31,
#                        str_detect(datename, pattern = "-09-") ~ n/30,
#                        str_detect(datename, pattern = "-10-") ~ n/31,
#                        str_detect(datename, pattern = "-11-") ~ n/30,
#                        str_detect(datename, pattern = "-12-") ~ n/31
#                              )) %>% 
#   ungroup() %>% 
#   as_tsibble(index = datename)
# 
# oc_monthly_quantity_locality <- 
#   right_join(oc, select(gp, c(PracticeID, npat, GPCluster)), 
#              by = c("PracticeID" = "PracticeID")) %>%
#   countRegional(., Locality, datename, Quantity)
# 
# oc_monthly_quantity_cluster <- 
#   right_join(oc, select(gp, c(PracticeID, npat, GPCluster)), 
#              by = c("PracticeID" = "PracticeID")) %>%
#   countRegional(., GPCluster, datename, Quantity) %>% 
#   mutate(n = 1000*n/npat) # quantity per 1000 pts
# 
# oc_monthly_quantity_gp <- 
#   countRegional(oc, PracticeID, datename, Quantity) %>% 
#   right_join(gp, by = c("regional_unit" = "PracticeID")) %>% # want to have GPs which have recorded data for the duration, not just part of it as that would add noise
#   mutate(n = 1000*n/npat) # quantity per 1000 pts
# 
# ## Sort into monthly count data pre-lockdown (2020-03-23)
# oc_monthly_count_pre_cv19 <- 
#   oc_monthly_count %>% 
#   filter(datename < dmy("01-03-2020"))
# 
# oc_monthly_quantity_locality_pre_cv19 <- 
#   oc_monthly_quantity_locality %>% 
#     filter(datename < dmy("01-03-2020"))
# 
# oc_monthly_quantity_cluster_pre_cv19 <- 
#   oc_monthly_quantity_cluster %>% 
#     filter(datename < dmy("01-03-2020"))
# 
# oc_monthly_quantity_gp_pre_cv19 <- 
#   oc_monthly_quantity_gp %>% 
#     filter(datename < dmy("01-03-2020"))

###
## Sort into monthly count data
oc_monthly_count <- oc %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31
                             )) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

oc_monthly_quantity_locality <- 
  right_join(oc, select(gp, c(PracticeID, npat, GPCluster)), 
             by = c("PracticeID" = "PracticeID")) %>%
  countRegional(., Locality, datename, Quantity)

oc_monthly_quantity_cluster <- 
  right_join(oc, select(gp, c(PracticeID, GPCluster)), 
             by = c("PracticeID" = "PracticeID")) %>%
  countRegional(., GPCluster, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(PracticeID, npat, GPCluster)) %>% 
  group_by(GPCluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "GPCluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oc_monthly_quantity_gp <- 
  oc %>% 
  countRegional(., PracticeID, datename, Quantity) %>% 
  left_join(select(gp, c(PracticeID, npat)), 
            by = c("regional_unit" = "PracticeID")) %>% 
  mutate(n = 1000*n/npat)

## Sort into monthly count data pre-lockdown (2020-03-23)
oc_monthly_count_pre_cv19 <- 
  oc_monthly_count %>% 
  filter(datename < dmy("01-03-2020"))

oc_monthly_quantity_locality_pre_cv19 <- 
  oc_monthly_quantity_locality %>% 
    filter(datename < dmy("01-03-2020"))

oc_monthly_quantity_cluster_pre_cv19 <- 
  oc_monthly_quantity_cluster %>% 
    filter(datename < dmy("01-03-2020"))

oc_monthly_quantity_gp_pre_cv19 <- 
  oc_monthly_quantity_gp %>% 
    filter(datename < dmy("01-03-2020"))

```

## Overview

### 2016-2020 plot of all oc prescriptions

```{r oc-monthly-ts-plot, fig.cap="Total quantity of combined hormonal and progestogen only oral contraceptives prescribed per month."}
oc %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  tsibble() %>% 
  autoplot(n) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

* General negative trend
* Seasonality unclear
  * Holiday effect? Drop in prescribing in Dec 2016-2019 followed by peak in Jan for 2017-2020.

### Seasonality

```{r oc-monthly-seasonality-plot}
df <- oc_monthly_count_pre_cv19 %>% 
  mutate(month = as.factor(month(datename, label = TRUE, abbr = TRUE)),
         year = as.factor(year(datename)))

df2 <- df %>% 
  as_tibble() %>% 
  filter(year(datename) != 2020) %>% 
  group_by(month) %>% 
  summarise(n = mean(n))

df %>% 
  ggplot(aes(x = month, y = n, colour = year, group = year)) +
  geom_line() +
  geom_line(data = df2, aes(x = month, y = n, group = "Avg"), 
            colour = "red", lty = 2) +
  labs(caption = "Red dashed line is mean for 2016-2019")

```
* 2016 is very different. Is that grounds to remove it?
* Dec/Jan holiday effect
  * How, if at all, does the population of Wales change with students?
* Easter effect? Mar/Apr has a pattern with 2017 as exception (does the opposite)
  * What would be expected? If people are travelling for Easter, then they may get their prescriptions before and after, but not in the weeks around?
  * Range (2000-2020): March 23rd (2008) to April 21st (2019)
  * Dates:
    * 2016-03-27
    * 2017-04-16
    * 2018-04-01
    * 2019-04-21

    * 2020-04-12

```{r}
oc_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  gg_subseries(y = n, period = "year")
```

*

### By `Quantity`
* Jan high and Dec low

### By `Items`
* Feb is lower, but has fewer days in it
* Dec is lower, holiday effect?
* Jan is higher, people who haven't had prescriptions due to holidays/have been entered late onto the system due to holidays

### Lag plots

```{r}
oc_monthly_count_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>% 
  gg_lag(y = n, geom = "point", lags = 1:12)
```

```{r}
oc_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  gg_lag(y = n, geom = "point", lags = 13:24)
```
* Here the colours indicate the month of the variable on the y-axis. The relationship is strongest at lag 12 and 24 suggesting seasonal data

### Autocorrelation

```{r}
tseries::adf.test(oc_monthly_count$n)
urca::ur.df(oc_monthly_count$n)
```

```{r}
oc_monthly_count_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>% 
  ACF(n, lag_max = 60) %>% autoplot()
```

* Autocorrelation greatest at 2 and 12

```{r}
oc_monthly_count_pre_cv19$n %>%
  pacf(lag.max = 60)
```

## Time series components

```{r}
dcmp <- 
  oc_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(STL(n))

oc_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  autoplot(n, color = "grey") + 
  autolayer(components(dcmp), trend, color = "red")

components(dcmp) %>% 
  autoplot()
```

```{r}
oc_monthly_count %>% 
  mutate(datename = yearmonth(datename)) %>% 
  autoplot(n, color = "grey") + 
  autolayer(components(dcmp), season_adjust, colour = "blue") +
  labs(title = "Seasonally adjusted")
```

## Moving average

```{r}
df <- oc_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename),
         `5-MA` = slider::slide_dbl(n, mean, .before = 2, .after = 2, 
                                    .complete = TRUE),
         `12-MA` = slider::slide_dbl(n, mean, .before = 5, .after = 6, 
                                    .complete = TRUE),
         `2x12-MA` = slider::slide_dbl(`12-MA`, mean, .before = 2, .after = 2, 
                                    .complete = TRUE),
         )
df %>% 
  autoplot(n) + 
  autolayer(df, `5-MA`, colour = "red") +
  autolayer(df, `2x12-MA`, colour = "blue") +
  labs(caption = "Daily prescriptions (black) along with the 5-MA estimate of the trend-cycle (red) and 2x12-MA (blue).")
```

## Predictions by `Locality`

```{r}
regions <- unique(as.character(oc_monthly_quantity_locality$regional_unit))
holidays <- 
  bind_rows(tibble(holiday = "christmas",
                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
                                  "2019-12-25", "2020-12-25", "2021-12-25")),
                   lower_window = -1, 
                   upper_window = 1),

            tibble(holiday = "easter",
                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
                                  "2019-04-21", "2020-04-12", "2021-04-04")),
                   lower_window = -1, 
                   upper_window = 1))

fit <- oc_monthly_quantity_locality_pre_cv19 %>% 
  # filter(year(datename) > 2016) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
        trend_model2 = TSLM(n ~ trend() + season()),
        #ets1 = ETS(n ~ trend()),
        ets2 = ETS(n ~ trend() + season()),
        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),
        #comb1 = combination_model(TSLM(n ~ trend()), ETS(n ~ trend())),
        comb2 = combination_model(TSLM(n ~ trend() + season()), 
                                  ETS(n ~ trend() + season())),
        # stl_dcmp1 = decomposition_model(STL(n ~ trend(),
        #                                    iterations = 1000, robust = FALSE),
        #                                NAIVE(season_adjust)),
        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
                                            iterations = 1000, robust = FALSE),
        SNAIVE(season_adjust)),
        s_naive = SNAIVE(n)
  )

fcsts <-  fit %>% 
  forecast(h = "6 months", bootstrap = FALSE) # can use `times = x` to control the number of samples

# single thread
regional_plots <- 
  map(.x = regions, 
      .f = ~regionalPlot(.x, oc_monthly_quantity_locality))

regional_plots

left_join(accuracy(fit),
          fit %>% 
            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
            report(), 
by = c("regional_unit", ".model"))

fit %>% 
  accuracy() %>% 
  group_by(.model) %>% 
  summarise(across(is.numeric, .fns = ~mean(., na.rm = TRUE)))

```

* https://fabletools.tidyverts.org/reference/combination_model.html

### Residual diagnostics

```{r}
augment(fit) %>% 
  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
```

## Predictions by `GPCluster`

```{r}
# system.time(cluster_fit <- regionalJointFits(oc_monthly_quantity_cluster_pre_cv19))

```

### Residual diagnostics

```{r}
augment(fit) %>% 
  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
```

## Predictions by `PracticeID`

```{r}
regions <- unique(as.character(gp$PracticeID))
holidays <- 
  bind_rows(tibble(holiday = "christmas",
                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
                                  "2019-12-25", "2020-12-25", "2021-12-25")),
                   lower_window = -1, 
                   upper_window = 1),

            tibble(holiday = "easter",
                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
                                  "2019-04-21", "2020-04-12", "2021-04-04")),
                   lower_window = -1, 
                   upper_window = 1))

fit <- oc_monthly_quantity_gp_pre_cv19 %>% 
    filter(regional_unit %in% gp$PracticeID) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
        trend_model2 = TSLM(n ~ trend() + season()),
        ets2 = ETS(n ~ trend() + season()),
        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),

        comb2 = combination_model(TSLM(n ~ trend() + season()), 
                                  ETS(n ~ trend() + season())),
        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
                                            iterations = 1000, robust = FALSE),
        SNAIVE(season_adjust)),
        # s_naive = SNAIVE(n)
  )

fcsts <-  fit %>% 
  forecast(h = "5 months", bootstrap = FALSE) # can use `times = x` to control the number of samples

# single thread
regional_plots <- 
  map(.x = regions, 
      .f = ~regionalPlot(.x, filter(oc_monthly_quantity_gp, 
                                    regional_unit %in% gp$PracticeID)))

regional_plots

left_join(accuracy(fit),
          fit %>% 
            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
            report(), 
by = c("regional_unit", ".model"))

fit %>% 
  accuracy() %>% 
  group_by(.model) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

```

### Residual diagnostics

```{r}
augment(fit) %>% 
  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
```

## Overview of each drug

```{r}
oc %>% 
  group_by(datename, chemname) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
                       str_detect(datename, pattern = "-02-") ~ n/28.25,
                       str_detect(datename, pattern = "-03-") ~ n/31,
                       str_detect(datename, pattern = "-04-") ~ n/30,
                       str_detect(datename, pattern = "-05-") ~ n/31,
                       str_detect(datename, pattern = "-06-") ~ n/30,
                       str_detect(datename, pattern = "-07-") ~ n/31,
                       str_detect(datename, pattern = "-08-") ~ n/31,
                       str_detect(datename, pattern = "-09-") ~ n/30,
                       str_detect(datename, pattern = "-10-") ~ n/31,
                       str_detect(datename, pattern = "-11-") ~ n/30,
                       str_detect(datename, pattern = "-12-") ~ n/31
                             )) %>% 
  as_tsibble(index = datename, key = chemname) %>% 
  autoplot(n) +
  theme(legend.position = "none") +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

## Modelling

### By GP Cluster

```{r}
# system.time(oc_gp_cluster_cv_models <-
#   regionalCV(data = oc_monthly_quantity_cluster_pre_cv19))
# 
# oc_gp_cluster_cv_models %>%
#   write_rds("../data/oc_gp_cluster_cv_models.rds")

oc_gp_cluster_cv_models <- 
  read_rds("../data/oc_gp_cluster_cv_models.rds")

oc_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

oc_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

oc_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

```

```{r}
system.time(oc_gp_cluster_fcts <- regionalJointFcsts(oc_monthly_quantity_cluster_pre_cv19))

oc_gp_cluster_fcts
```

## Discrepancies

```{r}
best_model <- 
  oc_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none") #+
#  coord_cartesian(ylim = c(-1,1)) +
  facet_wrap(~.model)
```

```{r}
library(tidyLPA)
best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  estimate_profiles(5) %>% plot_profiles()
    estimate_profiles(1:5,
                      variances = c("equal", "varying"),
                      covariances = c("zero", "varying")
                      ) %>% 
    compare_solutions(statistics = c("AIC", "BIC"))
```

### Plotting

```{r}
best_model <- 
  oc_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = .mean, colour = as.factor(regional_unit))) +
  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, fill = as.factor(regional_unit),
              alpha = .05), outline.type = "both") +
  geom_line(aes(y = n, group = regional_unit, colour = as.factor(regional_unit)), lty = 3) +
  coord_cartesian(ylim = c(0,50))+
  theme(legend.position = "none") +
  facet_wrap(~.model) + 
  labs(caption = "Dotted line = observed data, solid line and ribbon is predicted data with 80% CIs")

```

```{r}
bestModelPlot <- function(models, forecasts, data, region){
  best_model <- 
    models %>% 
    group_by(regional_unit) %>% 
    arrange(RMSE, MAE) %>% 
    slice(1, .preserve = TRUE)

  full_data <- filter(data, 
                      datename > ymd("2020-02-28") &
                        regional_unit == region) %>% 
    mutate(datename = yearmonth(datename))

best_model %>% 
    select(.model, regional_unit) %>% 
    filter(regional_unit == region) %>% 
    inner_join(forecasts, by = c(".model", "regional_unit")) %>%
    left_join(full_data, by = c("datename", "regional_unit")) %>% 
    ggplot(aes(x = datename, colour = as.factor(regional_unit))) +
    geom_line(aes(y = .mean)) +
    geom_ribbon(aes(ymin = lb_80, ymax = ub_80, fill = as.factor(regional_unit),
                   alpha = .1)) +
    geom_line(aes(y = n),
              colour = "black") +
    theme(legend.position = "none") +
    facet_wrap(~.model)
}

bestModelPlot(models = oc_gp_cluster_cv_models, 
              forecasts = oc_gp_cluster_fcts$forecasts,
              data = oc_monthly_quantity_cluster,
              region = "CityHealth")

```

## Other
### Prophet

```{r}
# Prophet model
oc_prophet_model <- 
  fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
                           season("year", type = "additive") + holiday(holidays))

fit <- oc_monthly_quantity_locality_pre_cv19 %>% 
  as_tsibble(index = datename) %>% 
  model(oc_prophet_model)

fc <- 
  fit %>% 
  forecast(h = "5 months")

accuracy(fit)

df <- oc_monthly_count_pre_cv19 %>% 
  transmute(ds = datename, y = n)
m <- prophet::prophet(df, seasonality.mode = "additive")
future <- make_future_dataframe(m, periods = 6, freq = 'month')
fcst <- predict(m, future)
prophet_plot_components(m, fcst)

oc_monthly_count %>% 
  ggplot(aes(x = datename, y = n)) +
  geom_line() +
  geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower),
                  ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
              alpha = .1, fill = "blue") +
  geom_line(aes(y = c(fcst[1:50,]$yhat, rep(NA, 5))),
            col = "blue", lty = 2) +
  geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)),
            col = "blue", lty = 3) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown

perf <- cross_validation(model = m, initial = 3*52, horizon = 52, units = "weeks")
performance_metrics(perf)
plot_cross_validation_metric(perf, metric = "rmse")
```

## Split by practice

```{r}
oc %>% 
  tibble %>% 
  group_by(datename, PracticeID) %>% 
  count %>% 
  group_by(PracticeID) %>% 
  summarise(n_min = min(n), 
            n_mean = mean(n)) %>% arrange((n_min)) %>% 
  filter(n_min >1)

oc %>% filter(PracticeID == "W91626") %>% 
  group_by(datename) %>% 
  count() %>% 
  as_tsibble(index = datename) %>% 
  autoplot()

```

### 2020-12-04 r_notebooks/htai_descriptives.Rmd
Adding files from local work

---
title: "R Notebook"
output: html_notebook
---

```{r, include=FALSE}
# Packages ####
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(knitr)

# Data ####
oc <- read_rds("../data/oral_contraceptives.rds")
oac <- read_rds("../data/oral_anticoagulants.rds")
```

## 2019 vs 2020

### Oral anticoagulants
```{r}
an_ch_oc_mar <- 
  oc %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  filter(str_detect(datename, "-03-") & year(datename) %in% c(2019:2020))

print("march")
100*an_ch_oc_mar$n[2] / an_ch_oc_mar$n[1]

an_ch_oc_apr <- 
  oc %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  filter(str_detect(datename, "-04-") & year(datename) %in% c(2019:2020))

print("april")
100*an_ch_oc_apr$n[2] / an_ch_oc_apr$n[1]

```

### Oral anticoagulants
```{r}
an_ch_oac_mar <- 
  oac %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  filter(str_detect(datename, "-03-") & year(datename) %in% c(2019:2020))

print("march")
100*an_ch_oac_mar$n[2] / an_ch_oac_mar$n[1]

an_ch_oac_apr <- 
  oac %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  filter(str_detect(datename, "-04-") & year(datename) %in% c(2019:2020))

print("april")
100*an_ch_oac_apr$n[2] / an_ch_oac_apr$n[1]

```

### 2020-12-04 r_notebooks/parallel_forecasting-copy.Rmd
Adding files from local work

---
title: "Parallel forecasting"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, setup}
# Packages ####
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(knitr)

# Options ####
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

# Seed ####
set.seed(32)

# Functions ####

holidays <- 
  bind_rows(tibble(holiday = "christmas",
                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
                                  "2019-12-25", "2020-12-25", "2021-12-25")),
                   lower_window = -1, 
                   upper_window = 1),

            tibble(holiday = "easter", # Sunday
                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
                                  "2019-04-21", "2020-04-12", "2021-04-04")),
                   lower_window = -2, 
                   upper_window = 1))

countRegional <- function(data, region, datename = datename, unit = Quantity){
 # Function to create tsibble object for a count of `unit` per `datename`
  # e.g. countRegional(oc, Locality, datename, Quantity) is the `Quantity`
  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
  # the number of days in each month.
  region <- enquo(region)
  datename <- enquo(datename)
  unit <- enquo(unit)

  data %>% 
  mutate(regional_unit = as_factor(set_names(!!region))) %>% 
  group_by(regional_unit, !!datename) %>% 
  summarise(n = sum(!!unit)) %>% 
  mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
                       str_detect(!!datename, pattern = "-02-") ~ n/28.25,
                       str_detect(!!datename, pattern = "-03-") ~ n/31,
                       str_detect(!!datename, pattern = "-04-") ~ n/30,
                       str_detect(!!datename, pattern = "-05-") ~ n/31,
                       str_detect(!!datename, pattern = "-06-") ~ n/30,
                       str_detect(!!datename, pattern = "-07-") ~ n/31,
                       str_detect(!!datename, pattern = "-08-") ~ n/31,
                       str_detect(!!datename, pattern = "-09-") ~ n/30,
                       str_detect(!!datename, pattern = "-10-") ~ n/31,
                       str_detect(!!datename, pattern = "-11-") ~ n/30,
                       str_detect(!!datename, pattern = "-12-") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = !!datename, key = regional_unit)
}

regionalPlot <- function(region, data){

  ## Prophet forecast - can this be taken outside of the function?
      ## no, when it is taken outside of the model, the forecast is becomes 
      ## much worse 2020-11-14
  df <- data %>%
    filter(regional_unit == region & datename < ymd("2020-03-23")) %>%
    transmute(ds = datename, y = n)

  m <- prophet::prophet(df, holidays = holidays,
                        seasonality.mode = "additive",# mcmc.samples = 1000,
                        weekly.seasonality = FALSE, daily.seasonality = FALSE)
  future <- make_future_dataframe(m, periods = 5, freq = 'month')
  fcst <- predict(m, future)

  ## Plotting
  plot <- fcsts %>% 
    filter(regional_unit == region) %>% 
    fabletools::autoplot(data, level = 80) + # fable forecasts over observed data
    geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)), # prophet prediction
              col = "blue", lty = 3) +
    geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower), # prophet confidence
                    ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
                alpha = .3, fill = "blue") +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") + # add line to mark the start of lockdown
    labs(title = region)

  ## Results
  result <- list("plots" = plot)#, "prophet" = fcst)
  return(result)
}

fableModels <- function(data){
  data %>% 
    model(trend_model1 = TSLM(n ~ trend()),#time series linear model
          trend_model2 = TSLM(n ~ trend() + season("year")),
          ets1 = ETS(n ~ trend()),
          ets2 = ETS(n ~ trend() + season("A")),
          ets3 = ETS(n ~ trend() + season("M")),
          arima = ARIMA(n, stepwise = FALSE, approximation = FALSE),
          comb1 = combination_model(TSLM(n ~ trend()), 
                                    ETS(n ~ trend())),
          comb2 = combination_model(TSLM(n ~ trend() + season("year")), 
                                    ETS(n ~ trend() + season("A"))),
          stl_dcmp1 = decomposition_model(STL(n ~ trend(),
                                              iterations = 1000, 
                                              robust = FALSE),
                                          SNAIVE(season_adjust)),
          stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
                                              iterations = 1000, 
                                              robust = FALSE),
                                          SNAIVE(season_adjust)),
          s_naive = SNAIVE(n))
}

regionalFits <- function(data, region){
  # Return various model objects for each region
  region <- enquo(region)

  data %>% 
    filter(regional_unit == !!region) %>% 
    mutate(datename = yearmonth(datename)) %>% 
    fableModels()
}

prophetModels <- function(data, region){
  # Return various model objects for each region
  region <- enquo(region)

  oc_prophet_model1 <- 
    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
                             season("year", type = "additive") + holiday(holidays))
  oc_prophet_model2 <- 
    fable.prophet::prophet(n ~ season("year", type = "multiplicative") + holiday(holidays))
  oc_prophet_model3 <- 
    fable.prophet::prophet(n ~ growth("linear",) +
                             season("year", type = "additive") + holiday(holidays))
  oc_prophet_model4 <- 
    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
                             season("year", type = "multiplicative") + holiday(holidays))
  oc_prophet_model5 <- 
    fable.prophet::prophet(n ~ growth("linear",) +
                             season("year", type = "additive") + holiday(holidays))
  oc_prophet_model6 <- 
    fable.prophet::prophet(n ~ season("year", type = "multiplicative") + holiday(holidays))
  oc_prophet_model7 <- 
    fable.prophet::prophet(n ~ holiday(holidays))
  oc_prophet_model8 <- 
    fable.prophet::prophet(n)

  data %>% 
    as_tsibble(index = datename) %>% 
    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3, 
          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6, 
          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
}

regionalFitsProphet <- function(data, region){
  # Return various model objects for each region
  region <- enquo(region)

  oc_prophet_model1 <- 
    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
                             season("year", type = "additive") + holiday(holidays))
  oc_prophet_model2 <- 
    fable.prophet::prophet(n ~ season("year", type = "multiplicative") + holiday(holidays))
  oc_prophet_model3 <- 
    fable.prophet::prophet(n ~ growth("linear",) +
                             season("year", type = "additive") + holiday(holidays))
  oc_prophet_model3 <- 
    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
                             season("year", type = "multiplicative") + holiday(holidays))
  oc_prophet_model5 <- 
    fable.prophet::prophet(n ~ growth("linear",) +
                             season("year", type = "additive") + holiday(holidays))
  oc_prophet_model6 <- 
    fable.prophet::prophet(n ~ season("year", type = "multiplicative") + holiday(holidays))
  oc_prophet_model7 <- 
    fable.prophet::prophet(n ~ holiday(holidays))
  oc_prophet_model8 <- 
    fable.prophet::prophet(n)

  data %>% 
    filter(regional_unit == !!region) %>% 
    as_tsibble(index = datename) %>% 
    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3, 
          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6, 
          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
}

# Data ####

## Read from local file
gp <- read_rds("../data/gp_linked_na_omit.rds")
oc <- read_rds("../data/oral_contraceptives.rds")

## Sort into monthly count data

oc_monthly_quantity_gp <- 
  countRegional(oc, PracticeID, datename, Quantity) %>% 
  right_join(gp, by = c("regional_unit" = "PracticeID")) %>% # want to have GPs which have recorded data for the duration, not just part of it as that would add noise
  mutate(n = 1000*n/npat) # quantity per 1000 pts

## Sort into monthly count data pre-lockdown (2020-03-23)

oc_monthly_quantity_gp_pre_cv19 <- 
  oc_monthly_quantity_gp %>% 
    filter(datename < dmy("01-03-2020"))

## Smaller GP data set to develop process
regions <- unique(as.character(gp$PracticeID))
dev_data <- 
  oc_monthly_quantity_gp_pre_cv19 %>% 
  filter(regional_unit %in% sample(regions, 50))

rm(oc)
rm(gp)
```

## Fable fits

* Fits can be estimated across several different fable models
* This can be done on the original data frame, or on each practice individually
* Need to ensure that models are the same using each method

### As single dataframe

```{r}
# As one df
system.time(fit <- dev_data %>% 
  filter(regional_unit %in% gp$PracticeID) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  fableModels())

fits1 <- accuracy(fit) %>% 
  group_by(regional_unit) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

fits1 %>% 
  kable(digits = 2)
```

### map()

#### Single core

* `model()` takes advantage of `plan(multisession)` to automatically compute in parallel, but does not include the proper options (i.e., `furrr_options(seed = TRUE)`) and generates a warning. Does not appear to influence estimates.

```{r, eval=FALSE}
system.time(fit2 <- map_dfr(.x = unique(dev_data$regional_unit), 
             .f = ~regionalFits(dev_data, .x)))

fits2 <- accuracy(fit2) %>% 
  group_by(regional_unit) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

fits2 %>% 
  kable(digits = 2)
```

#### Multi core

```{r}
plan(multisession)

system.time(
fit3 <- future_map_dfr(.x = unique(dev_data$regional_unit), 
             .f = ~regionalFits(dev_data, .x), 
             .options = furrr_options(seed = TRUE)))

fits3 <- accuracy(fit3) %>% 
  group_by(regional_unit) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

fits3 %>% 
  kable(digits = 2)

plan(sequential)
```

### Are the results the same?

```{r}
fits1 == fits3

head(fits1); head(fits3)
```

* Yes

### Function to provide model

## Prophet fits

* Prophet is fastest as a single data frame, but are its predictions unique

### As single dataframe

```{r}
oc_prophet_model1 <- 
  fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
                           season("year", type = "additive") + holiday(holidays))
oc_prophet_model2 <- 
  fable.prophet::prophet(n ~ growth("linear",) +
                           season("year", type = "additive") + holiday(holidays))
oc_prophet_model3 <- 
  fable.prophet::prophet(n ~ season("year", type = "additive") + holiday(holidays))
oc_prophet_model4 <- 
  fable.prophet::prophet(n ~ holiday(holidays))
oc_prophet_model5 <- 
  fable.prophet::prophet(n)

system.time(proph_fit <- dev_data %>% 
              mutate(datename = yearmonth(datename)) %>% 
              as_tsibble(index = datename) %>% 
              model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3, 
                    oc_prophet_model4, oc_prophet_model5))

proph_fits <- accuracy(proph_fit) %>% 
  group_by(regional_unit) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

proph_fits %>% 
  kable(digits = 2)

```

### map()

#### Single core
##### Sequential

```{r}
system.time(proph_fit2 <- map_dfr(.x = unique(dev_data$regional_unit), 
             .f = ~regionalFitsProphet(dev_data, .x)))

proph_fits2 <- accuracy(proph_fit2) %>% 
  group_by(.model) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

proph_fits2 %>% 
  kable(digits = 2)
```

##### multisession
```{r, eval=FALSE}
plan(multisession)

system.time(proph_fit2 <- map_dfr(.x = unique(dev_data$regional_unit), 
             .f = ~regionalFitsProphet(dev_data, .x)))

proph_fits2 <- accuracy(proph_fit2) %>% 
  group_by(regional_unit) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

proph_fits2 %>% 
  kable(digits = 2)
plan(sequential)

```

#### Multi core

```{r, eval=FALSE}
plan(multisession)
system.time(
  proph_fit3 <- future_map_dfr(.x = unique(dev_data$regional_unit), 
                               .f = ~regionalFitsProphet(dev_data, .x), 
                               .options = furrr_options(seed = TRUE)))

proph_fits3 <- accuracy(proph_fit3) %>% 
  group_by(regional_unit) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))

proph_fits3 %>% 
  kable(digits = 2)

plan(sequential)
```

## Model comparions

```{r}
bind_rows(accuracy(fit3), accuracy(proph_fit), .id = "a") %>% 
  group_by(.model, a) %>% 
  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE))) %>% 
  arrange(RMSE) %>% 
  kable(digits = 2)
```
### Plots

## Joint fable and prophet fits

```{r}
regionalFitsJoint <- function(data){
  regions <- unique(data$regional_unit)

  plan(multisession)
  fable_fit <- 
    future_map_dfr(.x = regions, 
                   .f = ~regionalFits(data, .x), 
                   .options = furrr_options(seed = TRUE)) 
  message("fable fits")

  plan(sequential)

  prophet_fit <- 
    map_dfr(.x = regions, 
            .f = ~regionalFitsProphet(data, .x))
  message("prophet fits")

  message("prophet forecasts")

  joint_fit <- 
    left_join(fable_fit, prophet_fit, by = "regional_unit")

  return(joint_fit)
}
```

## LOO CV

### Example

From https://otexts.com/fpp3/tscv.html

```{r}
## example 
google_2015 <- 
  tsibbledata::gafa_stock %>% 
  filter(Symbol == "GOOG") %>% 
  fill_gaps()

# Time series cross-validation accuracy
google_2015_tr <- google_2015 %>%
  slice(1:(n()-1)) %>%
  stretch_tsibble(.init = 3, .step = 1)
fc <- google_2015_tr %>%
  model(RW(Close ~ drift())) %>%
  forecast(h = 1)

fc %>% accuracy(google_2015)

# Residual accuracy
google_2015 %>%
  model(RW(Close ~ drift())) %>%
  accuracy()
```

#### Plotting RMSE for different forecast windows

```{r}
google_2015_tr <- google_2015 %>%
  slice(1:(n()-8)) %>%
  stretch_tsibble(.init = 3, .step = 1)

fc <- google_2015_tr %>%
  model(RW(Close ~ drift())) %>%
  forecast(h = 8) %>%
  group_by(.id) %>%
  mutate(h = row_number()) %>%
  ungroup()

fc %>%
  accuracy(google_2015, by = c("h", ".model")) %>%
  ggplot(aes(x = h, y = RMSE)) +
  geom_point()
```

### dev_data single region

```{r}
tictoc::tic()
dev_data_tr <- dev_data %>% 
  filter(regional_unit == "W92003") %>%
  mutate(datename = yearmonth(datename)) %>% 
  select(datename, n) %>%
  fill_gaps() %>% 
  slice(1:(n()-6)) %>% 
  stretch_tsibble(.init = 36, .step = 1)

plan(multisession)
fit <- dev_data_tr %>%
  fableModels()

fc <- fit %>%
  forecast(h = 6)
plan(sequential)
tictoc::toc()

fc %>%
    accuracy(mutate(filter(dev_data, regional_unit == "W92003"),
                    datename = yearmonth(datename)))

plan(multisession)
bind_rows(
  fc %>%
    accuracy(mutate(filter(dev_data, regional_unit == "W92003"),
                    datename = yearmonth(datename))),
  filter(dev_data, regional_unit == "W92003") %>% 
    mutate(datename = yearmonth(datename)) %>%
    fableModels() %>%
    accuracy())
plan(sequential)

fc %>%
  group_by(.id, .model) %>%
  mutate(h = row_number()) %>%
  ungroup() %>%
  accuracy(mutate(filter(dev_data, regional_unit == "W92003"),
                    datename = yearmonth(datename))) %>%
  ggplot(aes(x = .model, y = RMSE, fill = as.factor(.id))) +
  geom_point() +
  facet_grid(~"regional_unit")

dev_data_tr %>% 
  filter(.id == 1) %>% 
  .$datename %>% 
  unique()

fc %>%
  group_by(.id, .model) %>%
  ungroup() %>% 
    accuracy(mutate(filter(dev_data, regional_unit == "W92003"),
                    datename = yearmonth(datename)))
ggplot(aes(x = datename, y = ))

```

* 1 practice, 6 months, 15 windows = 55 secs
* With 1 practice, init = 36, step = 1 you end up with 360 obs of 3 variables (datename, n, .id) in the training data set
* with 1 practice, init = 35, step = 1 you end up with 395 obs of 3 variables (same as above) in the training data set

### multiple regions, single window

```{r}
tictoc::tic()
dev_data_tr <- dev_data %>% 
  mutate(datename = yearmonth(datename)) %>% 
  select(datename, n, regional_unit) %>%
  group_by(regional_unit) %>% 
  fill_gaps() %>% 
  slice(1:(n()-6), .preserve = TRUE) %>% # group_by(regional_unit) and .preserve must be true to maintain structure
  stretch_tsibble(.init = 35, .step = 1)

regions <- unique(dev_data_tr$regional_unit)
.ids <- unique(dev_data_tr$.id)

plan(multisession)
fable_fit <-
  future_map_dfr(.x = regions,
                  .f = ~regionalFits(filter(dev_data_tr, .id == 1), .x),
                  .options = furrr_options(seed = TRUE))

message("fable fits complete")

fc <- forecast(fable_fit, h = 6)

message("fabel forecasts complete")

plan(sequential)
tictoc::toc()

fc %>% 
    accuracy(mutate(dev_data,
                    datename = yearmonth(datename)), by = c("regional_unit", ".model"))

bind_rows(
  fc %>%
    accuracy(mutate(dev_data, datename = yearmonth(datename))),
  dev_data %>%
    mutate(datename = yearmonth(datename)) %>%
    fableModels() %>%
    accuracy())

```

* With 2 practices, you end up with 1005 obs of 4 variables (datename, n, regional_unit, .id)
* 100 practices, 6 months, 1 window = 285 seconds

```{r}
dev_data_tr_36 <- dev_data %>% 
  mutate(datename = yearmonth(datename)) %>% 
  select(datename, n, regional_unit) %>%
  group_by(regional_unit) %>% 
  fill_gaps() %>% 
  slice(1:(n()-6), .preserve = TRUE) %>% # group_by(regional_unit) and .preserve must be true to maintain structure
  stretch_tsibble(.init = 36, .step = 1)

dev_data_tr_36 %>% 
  as_tibble() %>% 
  group_by(.id, regional_unit) %>% 
  count

dev_data_tr_35 <- dev_data %>% 
  mutate(datename = yearmonth(datename)) %>% 
  select(datename, n, regional_unit) %>%
  group_by(regional_unit) %>% 
  fill_gaps() %>% 
  slice(1:(n()-6), .preserve = TRUE) %>% # group_by(regional_unit) and .preserve must be true to maintain structure
  stretch_tsibble(.init = 35, .step = 1)

dev_data_tr_35 %>% 
  as_tibble() %>% 
  group_by(.id, regional_unit) %>% 
  count
```

### dev_data

```{r, loo-cv}
#  .init = nrow(df)-cv_dist and slice 1:n()-cv_dist when .step = 1 allows 
  # parallelFableFits() for .ids[1:length(ids)-cv_dist]

parallelFableRegionalFits <- function(data, regions, window){

  print(paste("fable regional fit", window))
  future_map_dfr(.x = regions,
                 .f = ~regionalFits(filter(data, .id == window), .x),
                 .options = furrr_options(seed = TRUE))
}

trainingFableRegionalFits <- function(data, cv_dist = 6, init = 36, step = 1){
  # This function will make use of parallel processing if set up using plan()
  # Set variables
  cv_dist <- cv_dist

  # Create training data
  data_tr <- data %>% 
    # group_by(regional_unit) and slice(..., .preserve = TRUE) to maintain structure
    mutate(datename = yearmonth(datename)) %>% 
    select(datename, n, regional_unit) %>%
    group_by(regional_unit) %>% 
    fill_gaps() %>% 
    slice(1:(n()-cv_dist), .preserve = TRUE) %>% 
    stretch_tsibble(.init = init, .step = step)

  # Set helper variables
  regions_ids <- unique(data_tr$regional_unit)
  ids <- unique(data_tr$.id)

  # Call functions
  ## Fits
  fable_fit <- 
    map(.x = ids,#(length(ids)-cv_dist)],
            .f = ~parallelFableRegionalFits(dev_data_tr, 
                                            regions = regions_ids, window = .x),
            .id = "window")
  message("fable fits complete")

  ## Forecasts
  fc <- forecast(fable_fit, h = cv_dist)
  message("fable forecasts complete")

  # Return
  res <- list(fits = fable_fit, forecasts = fc)
  return(res)
}

# # As script
# tictoc::tic()
# cv_dist <- 6
# dev_data_tr <- dev_data %>% # Training data for CV
#   mutate(datename = yearmonth(datename)) %>% 
#   select(datename, n) %>%
#   fill_gaps() %>% 
#   slice(1:(n()-cv_dist)) %>% 
#   stretch_tsibble(.init = 36, .step = 1)
# 
# regions_ids <- unique(dev_data_tr$regional_unit)
# ids <- unique(dev_data_tr$.id)
# 
# plan(multisession)
# 
# 
# fable_fit <- 
#   map_dfr(.x = ids[1:(length(ids)-cv_dist)],
#           .f = ~parallelFableRegionalFits(dev_data_tr, 
#                                           regions = regions_ids, window = .x),
#           .id = "window")
# 
# message("fable fits complete")
# 
# fc <- forecast(fable_fit, h = cv_dist)
# 
# message("fabel forecasts complete")
# 
# plan(sequential)
# tictoc::toc()

# As function with default values
plan(multisession)
system.time(fable_cv <- trainingFableRegionalFits(data = dev_data))
plan(sequential)

# As function with different init value
plan(multisession)
system.time(fable_cv_2 <- trainingFableRegionalFits(data = dev_data, init = 37)) 
system.time(fable_cv_2 <- trainingFableRegionalFits(data = dev_data, init = 35))
# Fails with init < 36
plan(sequential)

fable_cv_2$forecasts %>% 
  accuracy(mutate(dev_data,
                    datename = yearmonth(datename)), by = c("regional_unit", ".model"))

fc %>% 
    accuracy(mutate(dev_data,
                    datename = yearmonth(datename)), by = c("regional_unit", ".model"))

bind_rows(
fc %>% 
    accuracy(mutate(dev_data,
                    datename = yearmonth(datename)), by = c("regional_unit", ".model")),
          dev_data %>%
            mutate(datename = yearmonth(datename)) %>%
            fableModels() %>%
            accuracy()) %>% 
  group_by(.model, .type) %>% 
  summarise(across(where(is.numeric), mean))

```

* ~108 seconds to CV 2 practices for 6 months across 9 windows
* ~270 seconds to CV 10 practices for 6 months across 9 windows
  * If this extrapolates in a  linear fashion, 400 practices would take `r 40*270/60/60` hours to calculate
  * Based on the 2 practice timing, this seems unlikely and the final time should be less than that
* Why is id 9 the maximum that will work?

### fitting and cv in the same function

```{r}
tictoc::tic()
regions <- unique(dev_data$regional_unit)
cv_dist <- 6
init <- 36
step <- 1
data <- 
  dev_data %>% 
  filter(regional_unit == regions[1]) %>% 
  select(regional_unit, datename, n) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  fill_gaps() %>% 
  slice(1:(n()-cv_dist), .preserve = TRUE) %>% 
  stretch_tsibble(.init = init, .step = step)

fits <- fableModels(data)

fc <- fits %>% forecast(h = cv_dist)

acc <- fc %>% 
  accuracy(mutate(filter(dev_data, regional_unit == regions[[1]]),
                    datename = yearmonth(datename))) %>% 
  arrange(RMSE) %>% 
  slice(1)
acc

tictoc::toc()
```

* `r mean(c(87.7, 76.6, 77.3, 82.517))`

```{r}
tictoc::tic()
regions <- unique(dev_data$regional_unit)
cv_dist <- 6
init <- 36
step <- 1
data_test <- mutate(filter(dev_data, regional_unit == regions[[1]]),
                  datename = yearmonth(datename))
data_tr <- dev_data %>% 
  filter(regional_unit == regions[1]) %>% 
  select(regional_unit, datename, n) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  fill_gaps() %>% 
  slice(1:(n()-cv_dist), .preserve = TRUE) %>% 
  stretch_tsibble(.init = init, .step = step)

bind_rows(data_tr %>% 
  fableModels() %>% 
  forecast(h = cv_dist) %>% 
  accuracy(data_test),
data_tr %>% 
  prophetModels() %>% 
  forecast(h = cv_dist) %>% 
  accuracy(data_test)) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1)

tictoc::toc()

regionalCV <- function(data, region, cv_dist = 6, init = 36, step = 1){
  # Data must be filtered outside of the function
  data <-
    filter(data, regional_unit == region)
  data_test <- 
    data %>% 
    mutate(datename = yearmonth(datename))

  data_tr <- data %>% 
    select(regional_unit, datename, n) %>% 
    mutate(datename = yearmonth(datename)) %>% 
    fill_gaps() %>% 
    slice(1:(n()-cv_dist), .preserve = TRUE) %>% 
    stretch_tsibble(.init = init, .step = step)

  plan(multisession)
  fable_fits <- 
    data_tr %>% 
    fableModels() %>% 
    forecast(h = cv_dist) %>% 
    accuracy(data_test)
  plan(sequential)

  prophet_fits <- 
    data_tr %>% 
    prophetModels() %>% 
    forecast(h = cv_dist) %>% 
    accuracy(data_test)

  bind_rows(fable_fits, prophet_fits) %>% 
    arrange(RMSE, MAE) %>% 
    slice(1)
}

regions <- unique(dev_data$regional_unit)
# plan(multisession)
system.time(best_models <- map_dfr(.x = unique(dev_data$regional_unit),
        .f = ~regionalCV(data = dev_data, region = .x),
        .id = "a"))
# plan(sequential)

best_models %>% 
  group_by(.model) %>% 
  count %>% 
  arrange(desc(n))

best_models %>% 
  ggplot(aes(x = MASE)) +
  geom_histogram()
```

* 1 regional_unit
  * Mean time `r mean(c(78.5, 77.7))` s w/o prophet
  * Mean time `r mean(c(142.466, 147.631))` s w prophet
* 2 regional units
  * min = 671.0648, lq = 691.4213, mean = 699.9314, median = 700.2545, uq = 710.868, max = 726.0485,

## Model selection

```{r}
## accuracy of each model on each regional_unit
accuracies <- joint_fits$fits %>% 
  accuracy()

bestModelFit <- function(data, measure){
  measure = enquo(measure)

  data <- janitor::clean_names(data)

  data %>% 
    group_by(regional_unit) %>% 
    summarise("{{ measure }}" := min(!!measure), .groups = "drop") %>% 
    select(regional_unit, !!measure) %>% 
    left_join(data, by = c("regional_unit", as_name(measure))) %>% # doesn't provide the single match if models are tied 
    select(regional_unit, model, everything(), -type)

}

bestModelFit(accuracies, rmse)

```

## Joint Fable and Prophet fits & forecast

* Take a tsibble and fit both the fable and prophet models to return a single dataframe of models that can be used for forecasting

```{r}
library(progressr)
handlers("progress")

regionalFitsJoint <- function(data){
  regions <- unique(data$regional_unit)

  plan(multisession)
  fable_fit <- 
    future_map_dfr(.x = regions, 
                   .f = ~regionalFits(data, .x), 
                   .options = furrr_options(seed = TRUE)) 
  message("fable fits")

  fable_fcst <- forecast(fable_fit, h = "5 months") %>% 
    as_tibble()

  message("fabel forecasts")

  plan(sequential)

  prophet_fit <- 
    map_dfr(.x = regions, 
            .f = ~regionalFitsProphet(data, .x))
  message("prophet fits")

  prophet_fcst <- forecast(prophet_fit, h = "5 months") %>% 
    as_tibble()
  message("prophet forecasts")

  joint_fit <- 
    left_join(fable_fit, prophet_fit, by = "regional_unit")
  joint_fcst <- 
    bind_rows(fable_fcst, prophet_fcst) %>% 
    mutate(lb_95 = quantile(n, .025),
           lb_80 = quantile(n, .1),
           med = median(n),
           ub_80 = quantile(n, .9),
           ub_95 = quantile(n, .975),
           n = NULL)

  return(list(fits = joint_fit, forecasts = joint_fcst))
}

joint_fits <- regionalFitsJoint(data = dev_data)

joint_fits
```

## Close multisession workers
```{r}
plan(sequential)
```

## Other

```{r, eval=FALSE}
x <- dev_data %>% 
  mutate(datename = yearmonth(datename)) %>% 
  as_tsibble(index = datename) %>% 
  model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3, 
        oc_prophet_model4, oc_prophet_model5)

x2 <- forecast(x, h = "5 months")

mean(quantile(x = x2$n, p = c(.1)))
mean(quantile(x = x2$n, p = c(.5)))
mean(quantile(x = x2$n, p = c(.9)))

x3 <- 
  x2 %>% 
  mutate(LB = quantile(n, p = .05),
         .median = quantile(n, p = .5),
         UB = quantile(n, p = .95))

x3 %>% 
  mutate(model = as.factor(.model)) %>% 
  filter(regional_unit == "W91027") %>% 
  ggplot(aes(x = datename, y = .median, colour = as.factor(model))) + 
  geom_line(aes(colour = as.factor(model)), lty = 2) +
  geom_ribbon(aes(ymin = LB, ymax = UB, fill = as.factor(model)), alpha = .3) +
  geom_line(aes(y = n, x = datename), data = filter(oc_monthly_quantity_gp %>% mutate(datename = yearmonth(datename)), regional_unit == "W91027"))

###

proph_fcst1 <-
  proph_fit %>% 
  forecast(h = "5 months")
autoplot(filter(proph_fcst1, regional_unit == "W91027"))

proph_fcst1 %>% 
  ggplot(aes(x = datename, y = .mean, colour = as.factor(regional_unit))) +
  geom_line() +
  facet_wrap(~as.factor(regional_unit))

filter(proph_fcst1, regional_unit == "W92003") %>% 
  autoplot(filter(oc_monthly_quantity_gp, regional_unit == "W92003"))

###

df <- oc_monthly_quantity_gp_pre_cv19 %>% 
  transmute(ds = yearmonth(datename), y = n)
m <- prophet::prophet(df, seasonality.mode = "additive")
future <- make_future_dataframe(m, periods = 6, freq = 'month')
fcst <- predict(m, future)
prophet_plot_components(m, fcst)

oc_monthly_quantity_gp %>% 
  ggplot(aes(x = datename, y = n)) +
  geom_line() +
  geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower),
                  ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
              alpha = .1, fill = "blue") +
  geom_line(aes(y = c(fcst[1:50,]$yhat, rep(NA, 5))),
            col = "blue", lty = 2) +
  geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)),
            col = "blue", lty = 3) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

### 2020-12-04 r_notebooks/parallel_forecasting.Rmd
Adding files from local work

--- 2020-12-04 r_notebooks/parallel_forecasting-copy.Rmd
@@
 library(feasts)
+library(fasster)
 library(furrr)
@@
 rstan_options(auto_write = TRUE)
+options(future.rng.onMisue = "ignore")
 
@@
 
-holidays <- 
-  bind_rows(tibble(holiday = "christmas",
-                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
-                                  "2019-12-25", "2020-12-25", "2021-12-25")),
-                   lower_window = -1, 
-                   upper_window = 1),
-
-            tibble(holiday = "easter", # Sunday
-                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
-                                  "2019-04-21", "2020-04-12", "2021-04-04")),
-                   lower_window = -2, 
-                   upper_window = 1))
-
-countRegional <- function(data, region, datename = datename, unit = Quantity){
- # Function to create tsibble object for a count of `unit` per `datename`
-  # e.g. countRegional(oc, Locality, datename, Quantity) is the `Quantity`
-  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
-  # the number of days in each month.
-  region <- enquo(region)
-  datename <- enquo(datename)
-  unit <- enquo(unit)
-
-  data %>% 
-  mutate(regional_unit = as_factor(set_names(!!region))) %>% 
-  group_by(regional_unit, !!datename) %>% 
-  summarise(n = sum(!!unit)) %>% 
-  mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
-                       str_detect(!!datename, pattern = "-02-") ~ n/28.25,
-                       str_detect(!!datename, pattern = "-03-") ~ n/31,
-                       str_detect(!!datename, pattern = "-04-") ~ n/30,
-                       str_detect(!!datename, pattern = "-05-") ~ n/31,
-                       str_detect(!!datename, pattern = "-06-") ~ n/30,
-                       str_detect(!!datename, pattern = "-07-") ~ n/31,
-                       str_detect(!!datename, pattern = "-08-") ~ n/31,
-                       str_detect(!!datename, pattern = "-09-") ~ n/30,
-                       str_detect(!!datename, pattern = "-10-") ~ n/31,
-                       str_detect(!!datename, pattern = "-11-") ~ n/30,
-                       str_detect(!!datename, pattern = "-12-") ~ n/31)) %>% 
-  ungroup() %>% 
-  as_tsibble(index = !!datename, key = regional_unit)
-}
-
-regionalPlot <- function(region, data){
-
-  ## Prophet forecast - can this be taken outside of the function?
-      ## no, when it is taken outside of the model, the forecast is becomes 
-      ## much worse 2020-11-14
-  df <- data %>%
-    filter(regional_unit == region & datename < ymd("2020-03-23")) %>%
-    transmute(ds = datename, y = n)
-
-  m <- prophet::prophet(df, holidays = holidays,
-                        seasonality.mode = "additive",# mcmc.samples = 1000,
-                        weekly.seasonality = FALSE, daily.seasonality = FALSE)
-  future <- make_future_dataframe(m, periods = 5, freq = 'month')
-  fcst <- predict(m, future)
-
-  ## Plotting
-  plot <- fcsts %>% 
-    filter(regional_unit == region) %>% 
-    fabletools::autoplot(data, level = 80) + # fable forecasts over observed data
-    geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)), # prophet prediction
-              col = "blue", lty = 3) +
-    geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower), # prophet confidence
-                    ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
-                alpha = .3, fill = "blue") +
-  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") + # add line to mark the start of lockdown
-    labs(title = region)
-
-  ## Results
-  result <- list("plots" = plot)#, "prophet" = fcst)
-  return(result)
-}
-
-fableModels <- function(data){
-  data %>% 
-    model(trend_model1 = TSLM(n ~ trend()),#time series linear model
-          trend_model2 = TSLM(n ~ trend() + season("year")),
-          ets1 = ETS(n ~ trend()),
-          ets2 = ETS(n ~ trend() + season("A")),
-          ets3 = ETS(n ~ trend() + season("M")),
-          arima = ARIMA(n, stepwise = FALSE, approximation = FALSE),
-          comb1 = combination_model(TSLM(n ~ trend()), 
-                                    ETS(n ~ trend())),
-          comb2 = combination_model(TSLM(n ~ trend() + season("year")), 
-                                    ETS(n ~ trend() + season("A"))),
-          stl_dcmp1 = decomposition_model(STL(n ~ trend(),
-                                              iterations = 1000, 
-                                              robust = FALSE),
-                                          SNAIVE(season_adjust)),
-          stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
-                                              iterations = 1000, 
-                                              robust = FALSE),
-                                          SNAIVE(season_adjust)),
-          s_naive = SNAIVE(n))
-}
-
-regionalFits <- function(data, region){
-  # Return various model objects for each region
-  region <- enquo(region)
-
-  data %>% 
-    filter(regional_unit == !!region) %>% 
-    mutate(datename = yearmonth(datename)) %>% 
-    fableModels()
-}
-
-prophetModels <- function(data, region){
-  # Return various model objects for each region
-  region <- enquo(region)
-
-  oc_prophet_model1 <- 
-    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "additive") + holiday(holidays))
-  oc_prophet_model2 <- 
-    fable.prophet::prophet(n ~ season("year", type = "multiplicative") + holiday(holidays))
-  oc_prophet_model3 <- 
-    fable.prophet::prophet(n ~ growth("linear",) +
-                             season("year", type = "additive") + holiday(holidays))
-  oc_prophet_model4 <- 
-    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "multiplicative") + holiday(holidays))
-  oc_prophet_model5 <- 
-    fable.prophet::prophet(n ~ growth("linear",) +
-                             season("year", type = "additive") + holiday(holidays))
-  oc_prophet_model6 <- 
-    fable.prophet::prophet(n ~ season("year", type = "multiplicative") + holiday(holidays))
-  oc_prophet_model7 <- 
-    fable.prophet::prophet(n ~ holiday(holidays))
-  oc_prophet_model8 <- 
-    fable.prophet::prophet(n)
-
-  data %>% 
-    as_tsibble(index = datename) %>% 
-    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3, 
-          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6, 
-          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
-}
-
-regionalFitsProphet <- function(data, region){
-  # Return various model objects for each region
-  region <- enquo(region)
-
-  oc_prophet_model1 <- 
-    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "additive") + holiday(holidays))
-  oc_prophet_model2 <- 
-    fable.prophet::prophet(n ~ season("year", type = "multiplicative") + holiday(holidays))
-  oc_prophet_model3 <- 
-    fable.prophet::prophet(n ~ growth("linear",) +
-                             season("year", type = "additive") + holiday(holidays))
-  oc_prophet_model3 <- 
-    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "multiplicative") + holiday(holidays))
-  oc_prophet_model5 <- 
-    fable.prophet::prophet(n ~ growth("linear",) +
-                             season("year", type = "additive") + holiday(holidays))
-  oc_prophet_model6 <- 
-    fable.prophet::prophet(n ~ season("year", type = "multiplicative") + holiday(holidays))
-  oc_prophet_model7 <- 
-    fable.prophet::prophet(n ~ holiday(holidays))
-  oc_prophet_model8 <- 
-    fable.prophet::prophet(n)
-
-  data %>% 
-    filter(regional_unit == !!region) %>% 
-    as_tsibble(index = datename) %>% 
-    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3, 
-          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6, 
-          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
-}
+source("../r_scripts/functions.r")
 
@@
   oc_monthly_quantity_gp_pre_cv19 %>% 
-  filter(regional_unit %in% sample(regions, 50))
+  filter(regional_unit %in% sample(regions, 5))
 
@@
 rm(gp)
+```
+
+```{r}
+dev_data %>% 
+  fableModels()
 ```
@@
 system.time(fit2 <- map_dfr(.x = unique(dev_data$regional_unit), 
-             .f = ~regionalFits(dev_data, .x)))
+             .f = ~regionalFableFits(dev_data, .x)))
 
@@
 fit3 <- future_map_dfr(.x = unique(dev_data$regional_unit), 
-             .f = ~regionalFits(dev_data, .x), 
+             .f = ~regionalFableFits(dev_data, .x), 
              .options = furrr_options(seed = TRUE)))
@@
 system.time(proph_fit2 <- map_dfr(.x = unique(dev_data$regional_unit), 
-             .f = ~regionalFitsProphet(dev_data, .x)))
+             .f = ~regionalProphetFits(dev_data, .x)))
 
@@
   proph_fit3 <- future_map_dfr(.x = unique(dev_data$regional_unit), 
-                               .f = ~regionalFitsProphet(dev_data, .x), 
+                               .f = ~regionalProphetFits(dev_data, .x), 
                                .options = furrr_options(seed = TRUE)))
@@
 ```{r}
-regionalFitsJoint <- function(data){
-  regions <- unique(data$regional_unit)
 
-  plan(multisession)
-  fable_fit <- 
-    future_map_dfr(.x = regions, 
-                   .f = ~regionalFits(data, .x), 
-                   .options = furrr_options(seed = TRUE)) 
-  message("fable fits")
-
-  plan(sequential)
-
-  prophet_fit <- 
-    map_dfr(.x = regions, 
-            .f = ~regionalFitsProphet(data, .x))
-  message("prophet fits")
-
-  message("prophet forecasts")
-
-  joint_fit <- 
-    left_join(fable_fit, prophet_fit, by = "regional_unit")
-
-  return(joint_fit)
-}
 ```
@@
   future_map_dfr(.x = regions,
-                  .f = ~regionalFits(filter(dev_data_tr, .id == 1), .x),
+                  .f = ~regionalFableFits(filter(dev_data_tr, .id == 1), .x),
                   .options = furrr_options(seed = TRUE))
@@
   future_map_dfr(.x = regions,
-                 .f = ~regionalFits(filter(data, .id == window), .x),
+                 .f = ~regionalFableFits(filter(data, .id == window), .x),
                  .options = furrr_options(seed = TRUE))
@@
 ```{r}
-tictoc::tic()
-regions <- unique(dev_data$regional_unit)
-cv_dist <- 6
-init <- 36
-step <- 1
-data_test <- mutate(filter(dev_data, regional_unit == regions[[1]]),
-                  datename = yearmonth(datename))
-data_tr <- dev_data %>% 
-  filter(regional_unit == regions[1]) %>% 
-  select(regional_unit, datename, n) %>% 
-  mutate(datename = yearmonth(datename)) %>% 
-  fill_gaps() %>% 
-  slice(1:(n()-cv_dist), .preserve = TRUE) %>% 
-  stretch_tsibble(.init = init, .step = step)
 
-bind_rows(data_tr %>% 
-  fableModels() %>% 
-  forecast(h = cv_dist) %>% 
-  accuracy(data_test),
-data_tr %>% 
-  prophetModels() %>% 
-  forecast(h = cv_dist) %>% 
-  accuracy(data_test)) %>% 
+fableModels(dev_data)
+regionalFableFits(dev_data, Arfon)
+
+system.time(best_models_1 <- regionalCV(dev_data))
+system.time(best_models_2 <- regionalCV(dev_data, init = 30))
+system.time(best_models_3 <- regionalCV(dev_data, step = 2))
+
+system.time(best_oc_models1 <- regionalCV(oc_monthly_quantity_gp_pre_cv19))
+
+best_oc_models1 %>% 
+  saveRDS(file = "../data/oc_gp_cv_models.rds")
+
+best_models_1 %>% 
+  group_by(regional_unit) %>% 
   arrange(RMSE, MAE) %>% 
-  slice(1)
+  slice(1, .preserve = TRUE) %>% 
+  ggplot(aes(x = RMSE)) +
+  geom_histogram()
 
-tictoc::toc()
-
-regionalCV <- function(data, region, cv_dist = 6, init = 36, step = 1){
-  # Data must be filtered outside of the function
-  data <-
-    filter(data, regional_unit == region)
-  data_test <- 
-    data %>% 
-    mutate(datename = yearmonth(datename))
-
-  data_tr <- data %>% 
-    select(regional_unit, datename, n) %>% 
-    mutate(datename = yearmonth(datename)) %>% 
-    fill_gaps() %>% 
-    slice(1:(n()-cv_dist), .preserve = TRUE) %>% 
-    stretch_tsibble(.init = init, .step = step)
-
-  plan(multisession)
-  fable_fits <- 
-    data_tr %>% 
-    fableModels() %>% 
-    forecast(h = cv_dist) %>% 
-    accuracy(data_test)
-  plan(sequential)
-
-  prophet_fits <- 
-    data_tr %>% 
-    prophetModels() %>% 
-    forecast(h = cv_dist) %>% 
-    accuracy(data_test)
-
-  bind_rows(fable_fits, prophet_fits) %>% 
+best_models_1 %>% 
+  group_by(regional_unit) %>% 
   arrange(RMSE, MAE) %>% 
-    slice(1)
-}
-
-regions <- unique(dev_data$regional_unit)
-# plan(multisession)
-system.time(best_models <- map_dfr(.x = unique(dev_data$regional_unit),
-        .f = ~regionalCV(data = dev_data, region = .x),
-        .id = "a"))
-# plan(sequential)
-
-best_models %>% 
+  slice(1, .preserve = TRUE) %>% 
   group_by(.model) %>% 
-  count %>% 
+  count() %>% 
   arrange(desc(n))
-
-best_models %>% 
-  ggplot(aes(x = MASE)) +
-  geom_histogram()
 ```
@@
   * min = 671.0648, lq = 691.4213, mean = 699.9314, median = 700.2545, uq = 710.868, max = 726.0485, 
+* 100 regional units
+  * Mean time `r mean(c(66, 61))` mins
+* 400 regional units
+  * `r lubridate::seconds_to_period(29663.27)` hours
+
+### prophet::cross_validation()
+
+```{r}
+cross_validation(select(oc_gp_cluster_fcts$fits, c(regional_unit, starts_with("oc_proph"))), horizon = .5, units = "years", initial = 3)
+```
 
@@
 bestModelFit(accuracies, rmse)
-
 ```
@@
 handlers("progress")
-
-regionalFitsJoint <- function(data){
-  regions <- unique(data$regional_unit)
-
-  plan(multisession)
-  fable_fit <- 
-    future_map_dfr(.x = regions, 
-                   .f = ~regionalFits(data, .x), 
-                   .options = furrr_options(seed = TRUE)) 
-  message("fable fits")
-
-  fable_fcst <- forecast(fable_fit, h = "5 months") %>% 
-    as_tibble()
-
-  message("fabel forecasts")
-
-  plan(sequential)
-
-  prophet_fit <- 
-    map_dfr(.x = regions, 
-            .f = ~regionalFitsProphet(data, .x))
-  message("prophet fits")
-
-  prophet_fcst <- forecast(prophet_fit, h = "5 months") %>% 
-    as_tibble()
-  message("prophet forecasts")
-
-  joint_fit <- 
-    left_join(fable_fit, prophet_fit, by = "regional_unit")
-  joint_fcst <- 
-    bind_rows(fable_fcst, prophet_fcst) %>% 
-    mutate(lb_95 = quantile(n, .025),
-           lb_80 = quantile(n, .1),
-           med = median(n),
-           ub_80 = quantile(n, .9),
-           ub_95 = quantile(n, .975),
-           n = NULL)
-
-  return(list(fits = joint_fit, forecasts = joint_fcst))
-}
 

### 2020-12-04 r_scripts/functions.R

@@ -1,0 +1,11 @@
+if(getwd() == "/Users/willhardy/OneDrive - Outreach Rescue/covid_prescribing/sercymru"){
+map(.x = list.files("r_scripts/functions"),
+    .f = ~source(paste0("r_scripts/functions/", .x)))
+} else if (getwd() == "/Users/willhardy/OneDrive - Outreach Rescue/covid_prescribing/sercymru/r_notebooks") {
+  map(.x = list.files("../r_scripts/functions"),
+      .f = ~source(paste0("../r_scripts/functions/", .x)))
+} else{
+  print("Check wd is set correctly in functions.r")
+  }
+
+

### 2020-12-04 r_scripts/functions/countRegional.R

@@ -1,0 +1,28 @@
+countRegional <- function(data, region, datename = datename, unit = Quantity){
+  # Function to create tsibble object for a count of `unit` per `datename`
+  # e.g. countRegional(oc, Locality, datename, Quantity) is the `Quantity`
+  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
+  # the number of days in each month.
+  region <- enquo(region)
+  datename <- enquo(datename)
+  unit <- enquo(unit)
+
+  data %>%
+    mutate(regional_unit = as_factor(set_names(!!region))) %>%
+    group_by(regional_unit, !!datename) %>%
+    summarise(n = sum(!!unit)) %>%
+    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
+                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
+                         str_detect(!!datename, pattern = "-03-") ~ n/31,
+                         str_detect(!!datename, pattern = "-04-") ~ n/30,
+                         str_detect(!!datename, pattern = "-05-") ~ n/31,
+                         str_detect(!!datename, pattern = "-06-") ~ n/30,
+                         str_detect(!!datename, pattern = "-07-") ~ n/31,
+                         str_detect(!!datename, pattern = "-08-") ~ n/31,
+                         str_detect(!!datename, pattern = "-09-") ~ n/30,
+                         str_detect(!!datename, pattern = "-10-") ~ n/31,
+                         str_detect(!!datename, pattern = "-11-") ~ n/30,
+                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
+    ungroup() %>%
+    as_tsibble(index = !!datename, key = regional_unit)
+}

### 2020-12-04 r_scripts/functions/fableModels.R

@@ -1,0 +1,28 @@
+fableModels <- function(data){
+  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
+
+  data %>%
+    mutate(datename = yearmonth(datename)) %>%
+    model(trend_model1 = TSLM(n ~ trend()),#time series linear model
+          trend_model2 = TSLM(n ~ trend() + season("year")),
+          ets1 = ETS(n ~ trend()),
+          ets2 = ETS(n ~ trend() + season("A")),
+          ets3 = ETS(n ~ trend() + season("M")),
+          arima = ARIMA(n, stepwise = FALSE, approximation = FALSE),
+          neur_net = NNETAR(n),
+          #fasster = FASSTER(n ~ season("1 year") + trend(1) + fourier(12)),
+          comb1 = combination_model(TSLM(n ~ trend()),
+                                    ETS(n ~ trend())),
+          comb2 = combination_model(TSLM(n ~ trend() + season("year")),
+                                    ETS(n ~ trend() + season("A"))),
+          stl_dcmp1 = decomposition_model(STL(n ~ trend(),
+                                              iterations = 1000,
+                                              robust = TRUE),
+                                          SNAIVE(season_adjust)),
+          stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
+                                              iterations = 1000,
+                                              robust = TRUE),
+                                          SNAIVE(season_adjust)),
+          s_naive = SNAIVE(n))# %>%
+    #as_tibble() # map_dfr() doesn't work on tsibble objects
+}

### 2020-12-04 r_scripts/functions/functions_forecasting.R

@@ -1,0 +1,1 @@
+#### Forecasting functions ####

### 2020-12-04 r_scripts/functions/prophetModels.R

@@ -1,0 +1,50 @@
+prophetModels <- function(data){
+  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
+
+  oc_prophet_model1 <-
+    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
+                             season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model2 <-
+    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
+                             season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model3 <-
+    fable.prophet::prophet(n ~ growth("linear") +
+                             season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model4 <-
+    fable.prophet::prophet(n ~ growth("linear") +
+                             season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model5 <-
+    fable.prophet::prophet(n ~ season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model6 <-
+    fable.prophet::prophet(n ~ season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model7 <-
+    fable.prophet::prophet(n ~ holiday(holidays))
+  oc_prophet_model8 <-
+    fable.prophet::prophet(n)
+
+  data %>%
+    mutate(datename = yearmonth(datename)) %>%
+    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
+          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
+          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
+}
+
+
+holidays <-
+  bind_rows(tibble(holiday = "christmas",
+                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
+                                  "2019-12-25", "2020-12-25", "2021-12-25")),
+                   lower_window = -1,
+                   upper_window = 1),
+
+            tibble(holiday = "easter", # Sunday
+                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
+                                  "2019-04-21", "2020-04-12", "2021-04-04")),
+                   lower_window = -2,
+                   upper_window = 1))

### 2020-12-04 r_scripts/functions/regionalCV.R

@@ -1,0 +1,71 @@
+regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
+
+  # CV accuracy for fableModels() and prophetModels()
+
+  regions <- unique(data$regional_unit) # Get unique regional_units for map()
+
+  fableCV <- function(data){ # Return CV model accuracy for fableModels()
+    data_test <-
+      data %>%
+      mutate(datename = yearmonth(datename))
+
+    data_tr <-
+      data %>%
+      select(regional_unit, datename, n) %>%
+      mutate(datename = yearmonth(datename)) %>%
+      fill_gaps() %>%
+      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
+      stretch_tsibble(.init = init, .step = step)
+
+    data_tr %>%
+      fableModels() %>%
+      forecast(h = cv_dist) %>%
+      accuracy(data_test)
+
+  }
+
+  prophetCV <- function(data){# Return CV model accuracy for prophetModels()
+    data_test <-
+      data %>%
+      mutate(datename = yearmonth(datename))
+
+    data_tr <-
+      data %>%
+      select(regional_unit, datename, n) %>%
+      mutate(datename = yearmonth(datename)) %>%
+      fill_gaps() %>%
+      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
+      stretch_tsibble(.init = init, .step = step)
+
+    data_tr %>%
+      prophetModels() %>%
+      forecast(h = cv_dist) %>%
+      accuracy(data_test)
+  }
+
+  # Prophet models won't run with plan(multisession) so need to be run
+  # sequentially. Is it worth trying to write this in Python and pass it back
+  # to R?
+
+    # Probably worth trying the prophet::cross_validation() method. If it
+    # returns RMSE and is faster it will be useful.
+  prophet_fits <-
+    map_dfr(.x =  regions,
+            .f = ~prophetCV(data = filter(data, regional_unit == .x)))
+  message("prophetModels() complete")
+
+  # Fable models will run using plan(multisession), but need to be run as below
+  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
+  # generated
+  plan(multisession) # Set up parallel processing to decrease computation time
+  fable_fits <-
+    future_map_dfr(.x =  regions,
+                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
+                   furrr_options(seed = TRUE))
[…]

### 2020-12-04 r_scripts/functions/regionalFableFits.R

@@ -1,0 +1,9 @@
+regionalFableFits <- function(data, region){
+  # Return various model objects for each region
+  print(region)
+  region <- enquo(region)
+
+  data %>%
+    filter(regional_unit == !!region) %>%
+    fableModels()
+}

### 2020-12-04 r_scripts/functions/regionalJointFcsts.R

@@ -1,0 +1,46 @@
+regionalJointFcsts <- function(data, h ="5 months"){
+  regions <- unique(data$regional_unit)
+  message("1")
+  plan(multisession)
+  message("2")
+  fable_fit <-
+    future_map_dfr(.x = regions,
+                   .f = ~fableModels(filter(data, regional_unit ==.x)),
+                   .options = furrr_options(seed = TRUE))
+  message("fable fits")
+
+  fable_fcst <- fable_fit %>%
+    forecast(h = h) %>%
+    as_tibble()
+  message("fable forecasts")
+
+  plan(sequential)
+
+  prophet_fit <-
+    map_dfr(.x = regions,
+            .f = ~prophetModels(filter(data, regional_unit ==.x)))
+  message("prophet fits")
+
+  prophet_fcst <- forecast(prophet_fit, h = h) %>%
+    as_tibble()
+# Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
+  # This may also be influencing accuracy
+
+    message("prophet forecasts")
+
+  joint_fit <-
+    left_join(fable_fit, prophet_fit, by = "regional_unit")
+  joint_fcst <-
+    bind_rows(fable_fcst, prophet_fcst) %>%
+    mutate(lb_95 = quantile(n, .025),
+           lb_80 = quantile(n, .1),
+           med = median(n),
+           ub_80 = quantile(n, .9),
+           ub_95 = quantile(n, .975),
+           sd = distributional::variance(n)^2,
+           dist = n,
+           n = NULL)
+
+  return(list(fits = joint_fit, forecasts = joint_fcst))
+}
+

### 2020-12-04 r_scripts/functions/regionalJointFits.R

@@ -1,0 +1,24 @@
+regionalJointFits <- function(data){
+  regions <- unique(data$regional_unit)
+
+  plan(multisession)
+  fable_fit <-
+    future_map_dfr(.x = regions,
+                   .f = ~fableModels(filter(data, regional_unit == .x)),
+                   .options = furrr_options(seed = TRUE))
+  message("fable fits")
+
+  plan(sequential)
+
+  prophet_fit <-
+    map_dfr(.x = regions,
+            .f = ~prophetModels(filter(data, regional_unit == .x)))
+  message("prophet fits")
+
+  message("prophet forecasts")
+
+  joint_fit <-
+    left_join(fable_fit, prophet_fit, by = "regional_unit")
+
+  return(joint_fit)
+}

### 2020-12-04 r_scripts/functions/regionalPlot.R

@@ -1,0 +1,31 @@
+regionalPlot <- function(region, data){
+
+  ## Prophet forecast - can this be taken outside of the function?
+  ## no, when it is taken outside of the model, the forecast is becomes
+  ## much worse 2020-11-14
+  df <- data %>%
+    filter(regional_unit == region & datename < ymd("2020-03-23")) %>%
+    transmute(ds = datename, y = n)
+
+  m <- prophet::prophet(df, holidays = holidays,
+                        seasonality.mode = "additive",# mcmc.samples = 1000,
+                        weekly.seasonality = FALSE, daily.seasonality = FALSE)
+  future <- make_future_dataframe(m, periods = 5, freq = 'month')
+  fcst <- predict(m, future)
+
+  ## Plotting
+  plot <- fcsts %>%
+    filter(regional_unit == region) %>%
+    fabletools::autoplot(data, level = 80) + # fable forecasts over observed data
+    geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)), # prophet prediction
+              col = "blue", lty = 3) +
+    geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower), # prophet confidence
+                    ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
+                alpha = .3, fill = "blue") +
+    geom_vline(xintercept = dmy("23-March-2020"), colour = "red") + # add line to mark the start of lockdown
+    labs(title = region)
+
+  ## Results
+  result <- list("plots" = plot)#, "prophet" = fcst)
+  return(result)
+}

### 2020-12-04 r_scripts/functions/regionalProphetFits.R

@@ -1,0 +1,37 @@
+regionalProphetFits <- function(data, region){
+  # Return various model objects for each region
+  region <- enquo(region)
+
+  oc_prophet_model1 <-
+    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
+                             season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model2 <-
+    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
+                             season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model3 <-
+    fable.prophet::prophet(n ~ growth("linear",) +
+                             season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model4 <-
+    fable.prophet::prophet(n ~ growth("linear",) +
+                             season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model5 <-
+    fable.prophet::prophet(n ~ season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model6 <-
+    fable.prophet::prophet(n ~ season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model7 <-
+    fable.prophet::prophet(n ~ holiday(holidays))
+  oc_prophet_model8 <-
+    fable.prophet::prophet(n)
+
+  data %>%
+    filter(regional_unit == !!region) %>%
+    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
+          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
+          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
+}

### 2020-12-08 r_notebooks/parallel_forecasting.Rmd
parallised prophetModels()

@@
 library(feasts)
-library(fasster)
 library(furrr)
@@
 ## Read from local file
-gp <- read_rds("../data/gp_linked_na_omit.rds")
+#gp <- read_rds("../data/gp_linked_na_omit.rds")
+gp <- read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
+  mutate(npat = N,
+         N = NULL) %>% 
+  filter(year == 2020) # do something better
 oc <- read_rds("../data/oral_contraceptives.rds")
@@
 ## Sort into monthly count data
+oc_monthly_count <- oc %>% 
+  group_by(datename) %>% 
+  summarise(n = sum(Quantity)) %>% 
+  mutate(datename = yearmonth(datename),
+         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
+                       str_detect(datename, pattern = "Feb") ~ n/28.25,
+                       str_detect(datename, pattern = "Mar") ~ n/31,
+                       str_detect(datename, pattern = "Apr") ~ n/30,
+                       str_detect(datename, pattern = "May") ~ n/31,
+                       str_detect(datename, pattern = "Jun") ~ n/30,
+                       str_detect(datename, pattern = "Jul") ~ n/31,
+                       str_detect(datename, pattern = "Aug") ~ n/31,
+                       str_detect(datename, pattern = "Sep") ~ n/30,
+                       str_detect(datename, pattern = "Oct") ~ n/31,
+                       str_detect(datename, pattern = "Nov") ~ n/30,
+                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
+  ungroup() %>% 
+  as_tsibble(index = datename)
+colnames(gp)
+
+oc_monthly_quantity_hb <- 
+  right_join(oc, select(gp, c(practiceid, hboard)), 
+             by = c("PracticeID" = "practiceid")) %>%
+  countRegional(hboard, datename, Quantity) %>% 
+  left_join(gp %>% 
+  select(c(practiceid, npat, hboard)) %>% 
+  group_by(hboard) %>% 
+  summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
+  mutate(n = 1000*n/npat) # quantity per 1000 pts
+
+oc_monthly_quantity_cluster <- 
+  right_join(oc, select(gp, c(practiceid, cluster)), 
+             by = c("PracticeID" = "practiceid")) %>%
+  countRegional(cluster, datename, Quantity) %>% 
+  left_join(gp %>% 
+  select(c(practiceid, npat, cluster)) %>% 
+  group_by(cluster) %>% 
+  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
+  mutate(n = 1000*n/npat) # quantity per 1000 pts
 
@@
   countRegional(oc, PracticeID, datename, Quantity) %>% 
-  right_join(gp, by = c("regional_unit" = "PracticeID")) %>% # want to have GPs which have recorded data for the duration, not just part of it as that would add noise
-  mutate(n = 1000*n/npat) # quantity per 1000 pts
+  right_join(select(gp, c(practiceid, npat)), 
+            by = c("regional_unit" = "practiceid")) %>% 
+  mutate(n = 1000*n/npat)
 
 ## Sort into monthly count data pre-lockdown (2020-03-23)
+oc_monthly_count_pre_cv19 <- 
+  oc_monthly_count %>% 
+  filter(datename < dmy("01-03-2020"))
+
+oc_monthly_quantity_hb_pre_cv19 <- 
+  oc_monthly_quantity_hb %>% 
+    filter(datename < dmy("01-03-2020"))
+
+oc_monthly_quantity_cluster_pre_cv19 <- 
+  oc_monthly_quantity_cluster %>% 
+    filter(datename < dmy("01-03-2020"))
 
@@
 ## Smaller GP data set to develop process
-regions <- unique(as.character(gp$PracticeID))
+regions <- unique(as.character(gp$practiceid))
 dev_data <- 
@@
 
+### future_map()
+
 ##### multisession
+
 ```{r, eval=FALSE}
@@
 
-system.time(proph_fit2 <- map_dfr(.x = unique(dev_data$regional_unit), 
-             .f = ~regionalProphetFits(dev_data, .x)))
+system.time(proph_fit2 <- future_map_dfr(.x = unique(dev_data$regional_unit), 
+             .f = ~regionalProphetFits(dev_data, .x),
+            .options = furrr_options(seed = TRUE)))
 
@@
 ```
+
+* 2020-12-07 Fails:
+
+```
+1 error encountered for oc_prophet_model1
+[1] unable to load shared object '/Library/Frameworks/R.framework/Versions/4.0/Resources/library/prophet/libs/prophet.so':
+  dlopen(/Library/Frameworks/R.framework/Versions/4.0/Resources/library/prophet/libs/prophet.so, 6): Library not loaded: @rpath/libtbb.dylib
+  Referenced from: /Library/Frameworks/R.framework/Versions/4.0/Resources/library/prophet/libs/prophet.so
+  Reason: image not found
+```
+
+* 2020-12-08 Fixed
+  * Reinstalling using `install.packages("prophet", type="source")` has resolved problem.
+  * Need to test in Windows
 

### 2020-12-08 r_scripts/functions/regionalJointFcsts.R

@@ -1,8 +1,6 @@
 regionalJointFcsts <- function(data, h ="5 months"){
   regions <- unique(data$regional_unit)
-  message("1")
   plan(multisession)
-  message("2")
   fable_fit <-
     future_map_dfr(.x = regions,
                    .f = ~fableModels(filter(data, regional_unit ==.x)),
@@ -14,19 +12,24 @@ regionalJointFcsts <- function(data, h ="5 months"){
     as_tibble()
   message("fable forecasts")
 
-  plan(sequential)
 
   prophet_fit <-
-    map_dfr(.x = regions,
-            .f = ~prophetModels(filter(data, regional_unit ==.x)))
+    future_map_dfr(.x = regions,
+                   .f = ~prophetModels(filter(data, regional_unit ==.x)),
+                   .options = furrr_options(seed = TRUE))
   message("prophet fits")
 
-  prophet_fcst <- forecast(prophet_fit, h = h) %>%
+  prophet_fcst <-
+    forecast(prophet_fit, h = h) %>%
     as_tibble()
-# Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
+  # Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
   # This may also be influencing accuracy
 
-    message("prophet forecasts")
+  message("prophet forecasts")
+  plan(sequential)
+
+  # prophetModels now being run in parallel. Needed to reinstall proophet from
+  # source
 
   joint_fit <-
     left_join(fable_fit, prophet_fit, by = "regional_unit")

### 2020-12-08 r_scripts/functions/regionalJointFcsts.R
parallised prophetModels()

@@ -1,8 +1,6 @@
 regionalJointFcsts <- function(data, h ="5 months"){
   regions <- unique(data$regional_unit)
-  message("1")
   plan(multisession)
-  message("2")
   fable_fit <-
     future_map_dfr(.x = regions,
                    .f = ~fableModels(filter(data, regional_unit ==.x)),
@@ -14,19 +12,24 @@ regionalJointFcsts <- function(data, h ="5 months"){
     as_tibble()
   message("fable forecasts")
 
-  plan(sequential)
 
   prophet_fit <-
-    map_dfr(.x = regions,
-            .f = ~prophetModels(filter(data, regional_unit ==.x)))
+    future_map_dfr(.x = regions,
+                   .f = ~prophetModels(filter(data, regional_unit ==.x)),
+                   .options = furrr_options(seed = TRUE))
   message("prophet fits")
 
-  prophet_fcst <- forecast(prophet_fit, h = h) %>%
+  prophet_fcst <-
+    forecast(prophet_fit, h = h) %>%
     as_tibble()
-# Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
+  # Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
   # This may also be influencing accuracy
 
-    message("prophet forecasts")
+  message("prophet forecasts")
+  plan(sequential)
+
+  # prophetModels now being run in parallel. Needed to reinstall prophet from
+  # source
 
   joint_fit <-
     left_join(fable_fit, prophet_fit, by = "regional_unit")

### 2020-12-08 r_scripts/functions/regionalJointFcsts.R
typos

@@ -27,12 +27,7 @@ regionalJointFcsts <- function(data, h ="5 months"){
 
   message("prophet forecasts")
   plan(sequential)
-
-<<<<<<< HEAD
   # prophetModels now being run in parallel. Needed to reinstall prophet from
-=======
-  # prophetModels now being run in parallel. Needed to reinstall proophet from
->>>>>>> 3803eb99c31ac84a5d2cc9211e7c43700fcf4b8e
   # source
 
   joint_fit <-

### 2020-12-08 r_scripts/functions/regionalCV.R
prophetModels() in parallel

@@ -43,6 +43,7 @@ regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
       accuracy(data_test)
   }
 
+  plan(multisession) # Set up parallel processing to decrease computation time
   # Prophet models won't run with plan(multisession) so need to be run
   # sequentially. Is it worth trying to write this in Python and pass it back
   # to R?
@@ -50,18 +51,18 @@ regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
     # Probably worth trying the prophet::cross_validation() method. If it
     # returns RMSE and is faster it will be useful.
   prophet_fits <-
-    map_dfr(.x =  regions,
-            .f = ~prophetCV(data = filter(data, regional_unit == .x)))
+    future_map_dfr(.x =  regions,
+            .f = ~prophetCV(data = filter(data, regional_unit == .x)),
+            .options = furrr_options(seed = TRUE))
   message("prophetModels() complete")
 
   # Fable models will run using plan(multisession), but need to be run as below
   # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
   # generated
-  plan(multisession) # Set up parallel processing to decrease computation time
   fable_fits <-
     future_map_dfr(.x =  regions,
                    .f = ~fableCV(data = filter(data, regional_unit == .x)),
-                   furrr_options(seed = TRUE))
+                   .options = furrr_options(seed = TRUE))
   plan(sequential) # Close the multiprocess function to prevent memory leakage
   message("fableModels() complete")
 

### 2020-12-11 r_notebooks/exploring_oral_anticoagulants.Rmd
Updataed gp data analyses

@@
 ---
-title: "Oral contraceptives"
+title: "Oral anticoagulants"
 output: 
@@
 ## Packages
+# devtools::install_github("https://github.com/w-hardy/serCymruTools")
 library(tidyverse)
@@
 library(furrr)
+library(serCymruTools)
 
@@
 
-## Functions
-countRegional <- function(data, region, datename = datename, unit = Quantity){
- # Function to create tsibble object for a count of `unit` per `datename`
-  # e.g. countRegional(oac, Locality, datename, Quantity) is the `Quantity`
-  # per `datename` grouped by `Locality` from `oac`. `Quantity` is corrected for
-  # the number of days in each month.
-  region <- enquo(region)
-  datename <- enquo(datename)
-  unit <- enquo(unit)
-
-  data %>% 
-  mutate(regional_unit = as_factor(set_names(!!region))) %>% 
-  group_by(regional_unit, !!datename) %>% 
-  summarise(n = sum(!!unit),
-            npat = sum(npat)) %>% 
-  mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
-                       str_detect(!!datename, pattern = "-02-") ~ n/28.25,
-                       str_detect(!!datename, pattern = "-03-") ~ n/31,
-                       str_detect(!!datename, pattern = "-04-") ~ n/30,
-                       str_detect(!!datename, pattern = "-05-") ~ n/31,
-                       str_detect(!!datename, pattern = "-06-") ~ n/30,
-                       str_detect(!!datename, pattern = "-07-") ~ n/31,
-                       str_detect(!!datename, pattern = "-08-") ~ n/31,
-                       str_detect(!!datename, pattern = "-09-") ~ n/30,
-                       str_detect(!!datename, pattern = "-10-") ~ n/31,
-                       str_detect(!!datename, pattern = "-11-") ~ n/30,
-                       str_detect(!!datename, pattern = "-12-") ~ n/31)) %>% 
-  ungroup() %>% 
-  as_tsibble(index = !!datename, key = regional_unit)
-}
-
-regionalPlot <- function(region, data){
-
-  ## Prophet forecast - can this be taken outside of the function?
-      ## no, when it is taken outside of the model, the forecast is becomes 
-      ## much worse 2020-11-14
-  df <- data %>%
-    filter(regional_unit == region & datename < ymd("2020-03-23")) %>%
-    transmute(ds = datename, y = n)
-
-  m <- prophet::prophet(df, holidays = holidays,
-                        seasonality.mode = "additive",# mcmc.samples = 1000,
-                        weekly.seasonality = FALSE, daily.seasonality = FALSE)
-  future <- make_future_dataframe(m, periods = 5, freq = 'month')
-  fcst <- predict(m, future)
-
-  ## Plotting
-  plot <- fcsts %>% 
-    filter(regional_unit == region) %>% 
-    fabletools::autoplot(data, level = 80) + # fable forecasts over observed data
-    geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)), # prophet prediction
-              col = "blue", lty = 3) +
-    geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower), # prophet confidence
-                    ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
-                alpha = .3, fill = "blue") +
-  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") + # add line to mark the start of lockdown
-    labs(title = region)
-
-  ## Results
-  result <- list("plots" = plot)#, "prophet" = fcst)
-  return(result)
-}
 ```
@@
 ## Read from local file
-gp <- read_rds("../data/gp_linked_na_omit.rds")
+gp <- read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
+  mutate(npat = N,
+         N = NULL) %>% 
+  filter(year == 2020) # do something better
 oac <- read_rds("../data/oral_anticoagulants.rds")
@@
                        str_detect(datename, pattern = "Nov") ~ n/30,
-                       str_detect(datename, pattern = "Dec") ~ n/31
-                             )) %>% 
+                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
   ungroup() %>% 
@@
 
-oac_monthly_quantity_locality <- 
-  right_join(oac, select(gp, c(PracticeID, npat, GPCluster)), 
-             by = c("PracticeID" = "PracticeID")) %>%
-  countRegional(., Locality, datename, Quantity)
+oac_monthly_quantity_hb <- 
+  right_join(oac, select(gp, c(practiceid, hboard)), 
+             by = c("PracticeID" = "practiceid")) %>%
+  countRegional(hboard, datename, Quantity) %>% 
+  left_join(gp %>% 
+  select(c(practiceid, npat, hboard)) %>% 
+  group_by(hboard) %>% 
+  summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
+  mutate(n = 1000*n/npat) # quantity per 1000 pts
 
 oac_monthly_quantity_cluster <- 
-  right_join(oac, select(gp, c(PracticeID, npat, GPCluster)), 
-             by = c("PracticeID" = "PracticeID")) %>%
-  countRegional(., GPCluster, datename, Quantity) %>% 
+  right_join(oac, select(gp, c(practiceid, cluster)), 
+             by = c("PracticeID" = "practiceid")) %>%
+  countRegional(cluster, datename, Quantity) %>% 
+  left_join(gp %>% 
+  select(c(practiceid, npat, cluster)) %>% 
+  group_by(cluster) %>% 
+  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
   mutate(n = 1000*n/npat) # quantity per 1000 pts
@@
 oac_monthly_quantity_gp <- 
-    right_join(oac, select(gp, c(PracticeID, npat, GPCluster)), 
-             by = c("PracticeID" = "PracticeID")) %>% 
-  countRegional(., PracticeID, datename, Quantity)%>% 
+  countRegional(oac, PracticeID, datename, Quantity) %>% 
+  right_join(select(gp, c(practiceid, npat)), 
+            by = c("regional_unit" = "practiceid")) %>% 
   mutate(n = 1000*n/npat)
@@
 
-oac_monthly_quantity_locality_pre_cv19 <- 
-  oac_monthly_quantity_locality %>% 
+oac_monthly_quantity_hb_pre_cv19 <- 
+  oac_monthly_quantity_hb %>% 
     filter(datename < dmy("01-03-2020"))
@@
 
-```{r oac-monthly-ts-plot, fig.cap="Total quantity of combined hormonal and progestogen only oral contraceptives prescribed per month."}
+```{r oac-monthly-ts-plot, fig.cap="Total quantity of combined oral anticoagulants prescribed per month."}
 oac %>% 
@@
 ```
-
-* General negative trend
-* Seasonality unclear
-  * Holiday effect? Drop in prescribing in Dec 2016-2019 followed by peak in Jan for 2017-2020.
 
@@
 
-*
-
-### By `Quantity`
-
-*
-
-### By `Items`
-
-*
-
-### Lag plots
-
-```{r}
-oac_monthly_count_pre_cv19 %>%
-  mutate(datename = yearmonth(datename)) %>% 
-  gg_lag(y = n, geom = "point", lags = 1:12)
-```
-
-* Here the colours indicate the month of the variable on the y-axis. The relationship is strongest at lag 3, 6, 9, and 12 suggesting seasonal data
-
 ### Autocorrelation
@@
 
-## Time series components
+## Modelling
+
+### By Health Board
+
+```{r, health-board-modelling}
+# system.time(oac_hb_cv_models <-
+#   regionalCV(data = oac_monthly_quantity_hb_pre_cv19))
+# 
+# oac_hb_cv_models %>%
+#   write_rds("../data/oac_hb_cv_models.rds")
+
+oac_hb_cv_models <- 
+  read_rds("../data/oac_hb_cv_models.rds")
+
+oac_hb_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  ggplot(aes(x = MAPE)) +
+  geom_histogram()
+
+oac_hb_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  group_by(.model) %>% 
+  count() %>% 
+  arrange(desc(n))
+
+oac_hb_cv_models %>% 
+  group_by(regional_unit) %>% 
+  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
+  geom_boxplot() +
+  theme(axis.text.x = element_text(angle = 90))
+```
+
+* 724.044 seconds with multisession prophetModels()
 
 ```{r}
-dcmp <- 
-  oac_monthly_count_pre_cv19 %>% 
-  mutate(datename = yearmonth(datename)) %>% 
-  model(STL(n))
+# system.time(oac_hb_fcsts <- regionalJointFcsts(oac_monthly_quantity_hb_pre_cv19))
+# 
+# oac_hb_fcsts %>%
+#   write_rds("../data/oac_hb_fcsts.rds")
 
-oac_monthly_count_pre_cv19 %>% 
-  mutate(datename = yearmonth(datename)) %>% 
-  autoplot(n, color = "grey") + 
-  autolayer(components(dcmp), trend, color = "red")
+oac_hb_fcsts <- 
+  read_rds("../data/oac_hb_fcsts.rds")
+```
 
-components(dcmp) %>% 
-  autoplot()
+* 194.071 seconds 2020-12-10
+
+### By GP Cluster
+
+```{r, gp-cluster-modelling}
+# system.time(oac_gp_cluster_cv_models <-
+#   regionalCV(data = oac_monthly_quantity_cluster_pre_cv19))
+# 
+# oac_gp_cluster_cv_models %>%
+#   write_rds("../data/oac_gp_cluster_cv_models.rds")
+
+oac_gp_cluster_cv_models <- 
+  read_rds("../data/oac_gp_cluster_cv_models.rds")
+
+oac_gp_cluster_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  ggplot(aes(x = MAPE)) +
+  geom_histogram()
+
+oac_gp_cluster_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  group_by(.model) %>% 
+  count() %>% 
+  arrange(desc(n))
+
+oac_gp_cluster_cv_models %>% 
+  group_by(regional_unit) %>% 
+  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
+  geom_boxplot() +
+  theme(axis.text.x = element_text(angle = 90))
+
+```
+
+* 5514.279 seconds
+
+```{r}
+# system.time(oac_gp_cluster_fcsts <- regionalJointFcsts(oac_monthly_quantity_cluster_pre_cv19))
+# 
+# oac_gp_cluster_fcsts %>%
+#   write_rds("../data/oac_gp_cluster_fcsts.rds")
+
+oac_gp_cluster_fcsts <- 
+  read_rds("../data/oac_gp_cluster_fcsts.rds")
+```
+
+* 1266.126 seconds 2020-12-10
+
+### By Practice
+
+```{r, gp-practice-modelling}
+incomplete_gp <- oac_monthly_quantity_gp_pre_cv19 %>% 
+    as_tibble() %>% 
+    group_by(regional_unit) %>% 
+    count() %>% 
+    filter(n < 50) %>% 
+    .$regional_unit %>% 
+    unique()
+
+# system.time(oac_gp_cv_models <-
+#   oac_monthly_quantity_gp_pre_cv19 %>%
+#     filter(!regional_unit %in% incomplete_gp) %>%
+#               regionalCV())
+# 
+# oac_gp_cv_models %>%
+#   write_rds("../data/oac_gp_cv_models.rds")
+
+oac_gp_cv_models <- 
+  read_rds("../data/oac_gp_cv_models.rds")
+
+oac_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  ggplot(aes(x = MAPE)) +
+  geom_histogram()
+
+oac_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  group_by(.model) %>% 
+  count() %>% 
+  arrange(desc(n))
+
+oac_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
+  geom_boxplot() +
+  theme(axis.text.x = element_text(angle = 90))
+
+```
+
+* 2.195e+04 seconds 2020-12-07
+* 25547.266 seconds 2020-12-09
+
+```{r}
+system.time(oac_gp_fcsts <-
+              oac_monthly_quantity_gp_pre_cv19 %>%
+              filter(!regional_unit %in% incomplete_gp) %>%
+              regionalJointFcsts())
+oac_gp_fcsts %>%
+  write_rds("../data/oac_gp_fcsts.rds")
+
+oac_gp_cluster_fcsts <- 
+  read_rds("../data/oac_gp_fcsts.rds")
+```
+
+## Discrepancies
+
+### By Health Board
+
+```{r, health-board-discrepancies}
+best_model_hb <- 
+  oac_hb_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE)
+
+best_model_hb %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oac_hb_fcsts$forecasts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oac_monthly_quantity_hb, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = n - .mean,
+         z_discrepancy = discrepancy/sd) %>% 
+  ggplot(aes(y = discrepancy)) +
+  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+```
+
+### By GP Cluster
+
+```{r, gp-cluster-discrepancies}
+best_model_gp_cluster <- 
+  oac_gp_cluster_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE)
+
+best_model_gp_cluster %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oac_gp_cluster_fcsts$forecasts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oac_monthly_quantity_cluster, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = n - .mean,
+         z_discrepancy = discrepancy/sd) %>% 
+  ggplot(aes(y = discrepancy)) +
+  # geom_boxplot(aes(x = as.factor(datename))) +
+  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  # scale_color_gradientn(colours = rainbow(100))+
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
 ```
@@
 ```{r}
-oac_monthly_count %>% 
-  mutate(datename = yearmonth(datename)) %>% 
-  autoplot(n, color = "grey") + 
-  autolayer(components(dcmp), season_adjust, colour = "blue") +
-  labs(title = "Seasonally adjusted")
+library(tidyLPA)
+best_model_gp_cluster %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oac_gp_cluster_fcsts$forecasts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oac_monthly_quantity_cluster, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = n - .mean,
+         z_discrepancy = discrepancy/sd)  %>%
+    select(discrepancy, regional_unit, datename) %>%
+  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
+  ungroup() %>% 
+  select(-regional_unit) %>% 
+  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
+    estimate_profiles(1:5,
+                      variances = c("equal", "varying"),
+                      covariances = c("zero", "varying")
+                      ) %>% 
+    compare_solutions(statistics = c("AIC", "BIC"))
 ```
 
-## Moving average
+### By GP Practice
 
-```{r}
-df <- oac_monthly_count %>% 
-  mutate(datename = yearmonth(datename),
-         `5-MA` = slider::slide_dbl(n, mean, .before = 2, .after = 2, 
-                                    .complete = TRUE),
-         `12-MA` = slider::slide_dbl(n, mean, .before = 5, .after = 6, 
-                                    .complete = TRUE),
-         `2x12-MA` = slider::slide_dbl(`12-MA`, mean, .before = 2, .after = 2, 
-                                    .complete = TRUE),
-         )
-df %>% 
-  autoplot(n) + 
-  autolayer(df, `5-MA`, colour = "red") +
-  autolayer(df, `2x12-MA`, colour = "blue") +
-  labs(caption = "Daily prescriptions (black) along with the 5-MA estimate of the trend-cycle (red) and 2x12-MA (blue).")
+```{r, gp-practice-discrepancies}
+best_model_gp <- 
+  oac_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE)
+
+best_model_gp %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oac_gp_fcsts$forecasts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oac_monthly_quantity_gp, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = n - .mean,
+         z_discrepancy = discrepancy/sd) %>% 
+  ggplot(aes(y = discrepancy)) +
+  # geom_boxplot(aes(x = as.factor(datename))) +
+  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
 ```
-
-## Predictions by `Locality`
-
-```{r}
-regions <- unique(as.character(oac_monthly_quantity_locality$regional_unit))
-holidays <- 
-  bind_rows(tibble(holiday = "christmas",
-                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
-                                  "2019-12-25", "2020-12-25", "2021-12-25")),
-                   lower_window = -1, 
-                   upper_window = 1),
-
-            tibble(holiday = "easter",
-                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
-                                  "2019-04-21", "2020-04-12", "2021-04-04")),
-                   lower_window = -1, 
-                   upper_window = 1))
-
-fit <- oac_monthly_quantity_locality_pre_cv19 %>% 
-  # filter(year(datename) > 2016) %>% 
-  mutate(datename = yearmonth(datename)) %>% 
-  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
-        trend_model2 = TSLM(n ~ trend() + season()),
-        #ets1 = ETS(n ~ trend()),
-        ets2 = ETS(n ~ trend() + season()),
-        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),
-        #comb1 = combination_model(TSLM(n ~ trend()), ETS(n ~ trend())),
-        comb2 = combination_model(TSLM(n ~ trend() + season()), 
-                                  ETS(n ~ trend() + season())),
-        # stl_dcmp1 = decomposition_model(STL(n ~ trend(),
-        #                                    iterations = 1000, robust = FALSE),
-        #                                NAIVE(season_adjust)),
-        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
-                                            iterations = 1000, robust = FALSE),
-        SNAIVE(season_adjust)),
-        s_naive = SNAIVE(n)
-  )
-
-fcsts <-  fit %>% 
-  forecast(h = "6 months", bootstrap = FALSE) # can use `times = x` to control the number of samples
-
-# single thread
-regional_plots <- 
-  map(.x = regions, 
-      .f = ~regionalPlot(.x, oac_monthly_quantity_locality))
-
-regional_plots
-
-left_join(accuracy(fit),
-          fit %>% 
-            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
-            report(), 
-by = c("regional_unit", ".model"))
-
-fit %>% 
-  accuracy() %>% 
-  group_by(.model) %>% 
-  summarise(across(is.numeric, .fns = ~mean(., na.rm = TRUE)))
-
-```
-
-* https://fabletools.tidyverts.org/reference/combination_model.html
-
-### Residual diagnostics
-
-```{r}
-augment(fit) %>% 
-  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
-  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
-```
-
-## Predictions by `GPCluster`
-
-```{r}
-regions <- unique(as.character(gp$GPCluster))
-holidays <- 
-  bind_rows(tibble(holiday = "christmas",
-                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
-                                  "2019-12-25", "2020-12-25", "2021-12-25")),
-                   lower_window = -1, 
-                   upper_window = 1),
-
-            tibble(holiday = "easter",
-                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
-                                  "2019-04-21", "2020-04-12", "2021-04-04")),
-                   lower_window = -1, 
-                   upper_window = 1))
-
-fit <- oac_monthly_quantity_cluster_pre_cv19 %>% 
-    filter(regional_unit %in% gp$GPCluster) %>% 
-  mutate(datename = yearmonth(datename)) %>% 
-  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
-        trend_model2 = TSLM(n ~ trend() + season()),
-        ets2 = ETS(n ~ trend() + season()),
-        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),
-
-        comb2 = combination_model(TSLM(n ~ trend() + season()), 
-                                  ETS(n ~ trend() + season())),
-        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
-                                            iterations = 1000, robust = FALSE),
-        SNAIVE(season_adjust)),
-        # s_naive = SNAIVE(n)
-  )
-
-fcsts <-  fit %>% 
-  forecast(h = "5 months", bootstrap = FALSE) # can use `times = x` to control the number of samples
-
-# single thread
-regional_plots <- 
-  map(.x = regions, 
-      .f = ~regionalPlot(.x, filter(oac_monthly_quantity_cluster, 
-                                    regional_unit %in% oac_monthly_quantity_cluster$regional_unit)))
-
-regional_plots
-
-left_join(accuracy(fit),
-          fit %>% 
-            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
-            report(), 
-by = c("regional_unit", ".model"))
-
-fit %>% 
-  accuracy() %>% 
-  group_by(.model) %>% 
-  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))
-
-```
-
-### Residual diagnostics
-
-```{r}
-augment(fit) %>% 
-  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
-  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
-```
-
-## Predictions by `PracticeID`
-
-```{r}
-regions <- unique(as.character(gp$PracticeID))
-holidays <- 
-  bind_rows(tibble(holiday = "christmas",
-                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
-                                  "2019-12-25", "2020-12-25", "2021-12-25")),
-                   lower_window = -1, 
-                   upper_window = 1),
-
-            tibble(holiday = "easter",
-                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
-                                  "2019-04-21", "2020-04-12", "2021-04-04")),
-                   lower_window = -1, 
-                   upper_window = 1))
-
-fit <- oac_monthly_quantity_gp_pre_cv19 %>% 
-    filter(regional_unit %in% gp$PracticeID) %>% 
-  mutate(datename = yearmonth(datename)) %>% 
-  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
-        trend_model2 = TSLM(n ~ trend() + season()),
-        ets2 = ETS(n ~ trend() + season()),
-        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),
-
-        comb2 = combination_model(TSLM(n ~ trend() + season()), 
-                                  ETS(n ~ trend() + season())),
-        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
-                                            iterations = 1000, robust = FALSE),
-        SNAIVE(season_adjust)),
-        # s_naive = SNAIVE(n)
-  )
-
-fcsts <-  fit %>% 
-  forecast(h = "5 months", bootstrap = FALSE) # can use `times = x` to control the number of samples
-
-# single thread
-regional_plots <- 
-  map(.x = regions, 
-      .f = ~regionalPlot(.x, filter(oac_monthly_quantity_gp, 
-                                    regional_unit %in% gp$PracticeID)))
-
-regional_plots
-
-left_join(accuracy(fit),
-          fit %>% 
-            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
-            report(), 
-by = c("regional_unit", ".model"))
-
-fit %>% 
-  accuracy() %>% 
-  group_by(.model) %>% 
-  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))
-
-```
-
-### Residual diagnostics
-
-```{r}
-augment(fit) %>% 
-  features(.resid, box_pierce, lag = 24, dof = 0) %>% 
-  mutate(sig = if_else(bp_pvalue <.05, TRUE, FALSE))
-```
-
-## Overview of each drug
-
-```{r}
-oac %>% 
-  group_by(datename, chemname) %>% 
-  summarise(n = sum(Quantity)) %>% 
-  mutate(n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
-                       str_detect(datename, pattern = "-02-") ~ n/28.25,
-                       str_detect(datename, pattern = "-03-") ~ n/31,
-                       str_detect(datename, pattern = "-04-") ~ n/30,
-                       str_detect(datename, pattern = "-05-") ~ n/31,
-                       str_detect(datename, pattern = "-06-") ~ n/30,
-                       str_detect(datename, pattern = "-07-") ~ n/31,
-                       str_detect(datename, pattern = "-08-") ~ n/31,
-                       str_detect(datename, pattern = "-09-") ~ n/30,
-                       str_detect(datename, pattern = "-10-") ~ n/31,
-                       str_detect(datename, pattern = "-11-") ~ n/30,
-                       str_detect(datename, pattern = "-12-") ~ n/31
-                             )) %>% 
-  as_tsibble(index = datename, key = chemname) %>% 
-  autoplot(n) +
-  # theme(legend.position = "none") +
-  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
-```
-
-## Modelling
-
-### Prophet
-
-```{r}
-# Prophet model
-oac_prophet_model <- 
-  fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                           season("year", type = "additive") + holiday(holidays))
-
-fit <- oac_monthly_quantity_locality_pre_cv19 %>% 
-  as_tsibble(index = datename) %>% 
-  model(oac_prophet_model)
-
-fc <- 
-  fit %>% 
-  forecast(h = "5 months")
-
-accuracy(fit)
-
-df <- oac_monthly_count_pre_cv19 %>% 
-  transmute(ds = datename, y = n)
-m <- prophet::prophet(df, seasonality.mode = "additive")
-future <- make_future_dataframe(m, periods = 6, freq = 'month')
-fcst <- predict(m, future)
-prophet_plot_components(m, fcst)
-
-oac_monthly_count %>% 
-  ggplot(aes(x = datename, y = n)) +
-  geom_line() +
-  geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower),
-                  ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
-              alpha = .1, fill = "blue") +
-  geom_line(aes(y = c(fcst[1:50,]$yhat, rep(NA, 5))),
-            col = "blue", lty = 2) +
-  geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)),
-            col = "blue", lty = 3) +
-  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
-
-perf <- cross_validation(model = m, initial = 3*52, horizon = 52, units = "weeks")
-performance_metrics(perf)
-plot_cross_validation_metric(perf, metric = "rmse")
-```
-
-## Split by practice
-
-```{r}
-oac %>% 
-  tibble %>% 
-  group_by(datename, PracticeID) %>% 
-  count %>% 
-  group_by(PracticeID) %>% 
-  summarise(n_min = min(n), 
-            n_mean = mean(n)) %>% arrange((n_min)) %>% 
-  filter(n_min >1)
-
-oac %>% filter(PracticeID == "W91626") %>% 
-  group_by(datename) %>% 
-  count() %>% 
-  as_tsibble(index = datename) %>% 
-  autoplot()
-
-```

### 2020-12-11 r_notebooks/exploring_oral_contraceptives.Rmd
Updataed gp data analyses

@@
 ## Read from local file
-gp <- read_rds("../data/gp_linked_na_omit.rds")
+#gp <- read_rds("../data/gp_linked_na_omit.rds")
+gp <- read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
+  mutate(npat = N,
+         N = NULL) %>% 
+  filter(year == 2020) # do something better
 oc <- read_rds("../data/oral_contraceptives.rds")
 
-## Sort into monthly count data
-# oc_monthly_count <- oc %>% 
-#   group_by(datename) %>% 
-#   summarise(n = sum(Quantity)) %>% 
-#   mutate(datename = yearmonth(datename),
-#          n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
-#                        str_detect(datename, pattern = "-02-") ~ n/28.25,
-#                        str_detect(datename, pattern = "-03-") ~ n/31,
-#                        str_detect(datename, pattern = "-04-") ~ n/30,
-#                        str_detect(datename, pattern = "-05-") ~ n/31,
-#                        str_detect(datename, pattern = "-06-") ~ n/30,
-#                        str_detect(datename, pattern = "-07-") ~ n/31,
-#                        str_detect(datename, pattern = "-08-") ~ n/31,
-#                        str_detect(datename, pattern = "-09-") ~ n/30,
-#                        str_detect(datename, pattern = "-10-") ~ n/31,
-#                        str_detect(datename, pattern = "-11-") ~ n/30,
-#                        str_detect(datename, pattern = "-12-") ~ n/31
-#                              )) %>% 
-#   ungroup() %>% 
-#   as_tsibble(index = datename)
-# 
-# oc_monthly_quantity_locality <- 
-#   right_join(oc, select(gp, c(PracticeID, npat, GPCluster)), 
-#              by = c("PracticeID" = "PracticeID")) %>%
-#   countRegional(., Locality, datename, Quantity)
-# 
-# oc_monthly_quantity_cluster <- 
-#   right_join(oc, select(gp, c(PracticeID, npat, GPCluster)), 
-#              by = c("PracticeID" = "PracticeID")) %>%
-#   countRegional(., GPCluster, datename, Quantity) %>% 
-#   mutate(n = 1000*n/npat) # quantity per 1000 pts
-# 
-# oc_monthly_quantity_gp <- 
-#   countRegional(oc, PracticeID, datename, Quantity) %>% 
-#   right_join(gp, by = c("regional_unit" = "PracticeID")) %>% # want to have GPs which have recorded data for the duration, not just part of it as that would add noise
-#   mutate(n = 1000*n/npat) # quantity per 1000 pts
-# 
-# ## Sort into monthly count data pre-lockdown (2020-03-23)
-# oc_monthly_count_pre_cv19 <- 
-#   oc_monthly_count %>% 
-#   filter(datename < dmy("01-03-2020"))
-# 
-# oc_monthly_quantity_locality_pre_cv19 <- 
-#   oc_monthly_quantity_locality %>% 
-#     filter(datename < dmy("01-03-2020"))
-# 
-# oc_monthly_quantity_cluster_pre_cv19 <- 
-#   oc_monthly_quantity_cluster %>% 
-#     filter(datename < dmy("01-03-2020"))
-# 
-# oc_monthly_quantity_gp_pre_cv19 <- 
-#   oc_monthly_quantity_gp %>% 
-#     filter(datename < dmy("01-03-2020"))
-
-###
 ## Sort into monthly count data
@@
                        str_detect(datename, pattern = "Nov") ~ n/30,
-                       str_detect(datename, pattern = "Dec") ~ n/31
-                             )) %>% 
+                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
   ungroup() %>% 
   as_tsibble(index = datename)
+colnames(gp)
 
-oc_monthly_quantity_locality <- 
-  right_join(oc, select(gp, c(PracticeID, npat, GPCluster)), 
-             by = c("PracticeID" = "PracticeID")) %>%
-  countRegional(., Locality, datename, Quantity)
+oc_monthly_quantity_hb <- 
+  right_join(oc, select(gp, c(practiceid, hboard)), 
+             by = c("PracticeID" = "practiceid")) %>%
+  countRegional(hboard, datename, Quantity) %>% 
+  left_join(gp %>% 
+  select(c(practiceid, npat, hboard)) %>% 
+  group_by(hboard) %>% 
+  summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
+  mutate(n = 1000*n/npat) # quantity per 1000 pts
 
 oc_monthly_quantity_cluster <- 
-  right_join(oc, select(gp, c(PracticeID, GPCluster)), 
-             by = c("PracticeID" = "PracticeID")) %>%
-  countRegional(., GPCluster, datename, Quantity) %>% 
+  right_join(oc, select(gp, c(practiceid, cluster)), 
+             by = c("PracticeID" = "practiceid")) %>%
+  countRegional(cluster, datename, Quantity) %>% 
   left_join(gp %>% 
-  select(c(PracticeID, npat, GPCluster)) %>% 
-  group_by(GPCluster) %>% 
-  summarise(npat = sum(npat)), by = c("regional_unit" = "GPCluster")) %>% 
+  select(c(practiceid, npat, cluster)) %>% 
+  group_by(cluster) %>% 
+  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
   mutate(n = 1000*n/npat) # quantity per 1000 pts
@@
 oc_monthly_quantity_gp <- 
-  oc %>% 
-  countRegional(., PracticeID, datename, Quantity) %>% 
-  left_join(select(gp, c(PracticeID, npat)), 
-            by = c("regional_unit" = "PracticeID")) %>% 
+  countRegional(oc, PracticeID, datename, Quantity) %>% 
+  right_join(select(gp, c(practiceid, npat)), 
+            by = c("regional_unit" = "practiceid")) %>% 
   mutate(n = 1000*n/npat)
@@
 
-oc_monthly_quantity_locality_pre_cv19 <- 
-  oc_monthly_quantity_locality %>% 
+oc_monthly_quantity_hb_pre_cv19 <- 
+  oc_monthly_quantity_hb %>% 
     filter(datename < dmy("01-03-2020"))
@@
 
+## Overview of each drug
+
+```{r}
+oc %>% 
+  group_by(datename, chemname) %>% 
+  summarise(n = sum(Quantity)) %>% 
+  mutate(n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
+                       str_detect(datename, pattern = "-02-") ~ n/28.25,
+                       str_detect(datename, pattern = "-03-") ~ n/31,
+                       str_detect(datename, pattern = "-04-") ~ n/30,
+                       str_detect(datename, pattern = "-05-") ~ n/31,
+                       str_detect(datename, pattern = "-06-") ~ n/30,
+                       str_detect(datename, pattern = "-07-") ~ n/31,
+                       str_detect(datename, pattern = "-08-") ~ n/31,
+                       str_detect(datename, pattern = "-09-") ~ n/30,
+                       str_detect(datename, pattern = "-10-") ~ n/31,
+                       str_detect(datename, pattern = "-11-") ~ n/30,
+                       str_detect(datename, pattern = "-12-") ~ n/31
+                             )) %>% 
+  as_tsibble(index = datename, key = chemname) %>% 
+  autoplot(n) +
+  theme(legend.position = "none") +
+  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
+```
+
 ## Time series components
@@
 
-## Moving average
-
-```{r}
-df <- oc_monthly_count_pre_cv19 %>% 
-  mutate(datename = yearmonth(datename),
-         `5-MA` = slider::slide_dbl(n, mean, .before = 2, .after = 2, 
-                                    .complete = TRUE),
-         `12-MA` = slider::slide_dbl(n, mean, .before = 5, .after = 6, 
-                                    .complete = TRUE),
-         `2x12-MA` = slider::slide_dbl(`12-MA`, mean, .before = 2, .after = 2, 
-                                    .complete = TRUE),
-         )
-df %>% 
-  autoplot(n) + 
-  autolayer(df, `5-MA`, colour = "red") +
-  autolayer(df, `2x12-MA`, colour = "blue") +
-  labs(caption = "Daily prescriptions (black) along with the 5-MA estimate of the trend-cycle (red) and 2x12-MA (blue).")
-```
-
 ## Predictions by `Locality`
 
-```{r}
+```{r, eval=FALSE}
 regions <- unique(as.character(oc_monthly_quantity_locality$regional_unit))
@@
 
-```{r}
+```{r, eval=FALSE}
 augment(fit) %>% 
@@
 
-```{r}
-# system.time(cluster_fit <- regionalJointFits(oc_monthly_quantity_cluster_pre_cv19))
+```{r, eval=FALSE}
+system.time(cluster_fit <- regionalJointFits(oc_monthly_quantity_cluster_pre_cv19))
 
@@
 
-```{r}
-augment(fit) %>% 
+```{r, eval=FALSE}
+augment(cluster_fit) %>% 
   features(.resid, box_pierce, lag = 24, dof = 0) %>% 
@@
 
-```{r}
-regions <- unique(as.character(gp$PracticeID))
-holidays <- 
-  bind_rows(tibble(holiday = "christmas",
-                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
-                                  "2019-12-25", "2020-12-25", "2021-12-25")),
-                   lower_window = -1, 
-                   upper_window = 1),
+```{r, eval=FALSE}
+gp_fit <- regionalJointFits(oc_monthly_quantity_gp_pre_cv19)
 
-            tibble(holiday = "easter",
-                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
-                                  "2019-04-21", "2020-04-12", "2021-04-04")),
-                   lower_window = -1, 
-                   upper_window = 1))
-
-fit <- oc_monthly_quantity_gp_pre_cv19 %>% 
-    filter(regional_unit %in% gp$PracticeID) %>% 
-  mutate(datename = yearmonth(datename)) %>% 
-  model(#trend_model1 = TSLM(n ~ trend()),#time series linear model
-        trend_model2 = TSLM(n ~ trend() + season()),
-        ets2 = ETS(n ~ trend() + season()),
-        arima = ARIMA(n),# stepwise = FALSE, approximation = FALSE),
-
-        comb2 = combination_model(TSLM(n ~ trend() + season()), 
-                                  ETS(n ~ trend() + season())),
-        stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
-                                            iterations = 1000, robust = FALSE),
-        SNAIVE(season_adjust)),
-        # s_naive = SNAIVE(n)
-  )
-
-fcsts <-  fit %>% 
-  forecast(h = "5 months", bootstrap = FALSE) # can use `times = x` to control the number of samples
-
-# single thread
-regional_plots <- 
-  map(.x = regions, 
-      .f = ~regionalPlot(.x, filter(oc_monthly_quantity_gp, 
-                                    regional_unit %in% gp$PracticeID)))
-
-regional_plots
-
-left_join(accuracy(fit),
-          fit %>% 
-            select(-starts_with(c("stl_dcmp", "comb"))) %>% 
-            report(), 
-by = c("regional_unit", ".model"))
-
-fit %>% 
-  accuracy() %>% 
-  group_by(.model) %>% 
-  summarise(across(where(is.numeric), .fns = ~mean(., na.rm = TRUE)))
+gp_fcsts <-  gp_fit %>% 
+  regionalJointFcsts()
 
@@
 
-## Overview of each drug
+## Modelling
+
+### By Health Board
+
+```{r, health-board-modelling}
+# system.time(oc_hb_cv_models <-
+#   regionalCV(data = oc_monthly_quantity_hb_pre_cv19))
+# 
+# oc_hb_cv_models %>%
+#   write_rds("../data/oc_hb_cv_models.rds")
+
+oc_hb_cv_models <- 
+  read_rds("../data/oc_hb_cv_models.rds")
+
+oc_hb_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  ggplot(aes(x = MAPE)) +
+  geom_histogram()
+
+oc_hb_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  group_by(.model) %>% 
+  count() %>% 
+  arrange(desc(n))
+
+oc_hb_cv_models %>% 
+  group_by(regional_unit) %>% 
+  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
+  geom_boxplot() +
+  theme(axis.text.x = element_text(angle = 90))
+```
+
+* 570.350 seconds with multisession prophetModels()
 
 ```{r}
-oc %>% 
-  group_by(datename, chemname) %>% 
-  summarise(n = sum(Quantity)) %>% 
-  mutate(n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
-                       str_detect(datename, pattern = "-02-") ~ n/28.25,
-                       str_detect(datename, pattern = "-03-") ~ n/31,
-                       str_detect(datename, pattern = "-04-") ~ n/30,
-                       str_detect(datename, pattern = "-05-") ~ n/31,
-                       str_detect(datename, pattern = "-06-") ~ n/30,
-                       str_detect(datename, pattern = "-07-") ~ n/31,
-                       str_detect(datename, pattern = "-08-") ~ n/31,
-                       str_detect(datename, pattern = "-09-") ~ n/30,
-                       str_detect(datename, pattern = "-10-") ~ n/31,
-                       str_detect(datename, pattern = "-11-") ~ n/30,
-                       str_detect(datename, pattern = "-12-") ~ n/31
-                             )) %>% 
-  as_tsibble(index = datename, key = chemname) %>% 
-  autoplot(n) +
-  theme(legend.position = "none") +
-  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
+# system.time(oc_hb_fcsts <- regionalJointFcsts(oc_monthly_quantity_hb_pre_cv19))
+# 
+# oc_hb_fcsts %>% 
+#   write_rds("../data/oc_hb_fcsts.rds")
+
+oc_hb_fcsts <- 
+  read_rds("../data/oc_hb_fcsts.rds")
 ```
 
-## Modelling
+* 158.876 seconds 2020-12-08
 
@@
 
-```{r}
+```{r, gp-cluster-modelling}
 # system.time(oc_gp_cluster_cv_models <-
@@
 
+* 4300.706 seconds
+
 ```{r}
-system.time(oc_gp_cluster_fcts <- regionalJointFcsts(oc_monthly_quantity_cluster_pre_cv19))
+# system.time(oc_gp_cluster_fcsts <- regionalJointFcsts(oc_monthly_quantity_cluster_pre_cv19))
+# 
+# oc_gp_cluster_fcsts %>%
+#   write_rds("../data/oc_gp_cluster_fcsts.rds")
 
-oc_gp_cluster_fcts
+oc_gp_cluster_fcsts <- 
+  read_rds("../data/oc_gp_cluster_fcsts.rds")
+```
+
+* 1680.611 seconds pre prophet fix 2020-12-08 
+* 1456.319 seconds post prophet fix 2020-12-08
+
+### By Practice
+
+```{r, gp-practice-modelling}
+incomplete_gp <- oc_monthly_quantity_gp_pre_cv19 %>% 
+    as_tibble() %>% 
+    group_by(regional_unit) %>% 
+    count() %>% 
+    filter(n < 50) %>% 
+    .$regional_unit %>% 
+    unique()
+
+# system.time(oc_gp_cv_models <-
+#   oc_monthly_quantity_gp_pre_cv19 %>% 
+#     filter(!regional_unit %in% incomplete_gp) %>% 
+#               regionalCV())
+# 
+# oc_gp_cv_models %>%
+#   write_rds("../data/oc_gp_cv_models.rds")
+
+oc_gp_cv_models <- 
+  read_rds("../data/oc_gp_cv_models.rds")
+
+oc_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  ggplot(aes(x = MAPE)) +
+  geom_histogram()
+
+oc_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  group_by(.model) %>% 
+  count() %>% 
+  arrange(desc(n))
+
+oc_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
+  geom_boxplot() +
+  theme(axis.text.x = element_text(angle = 90))
+
+```
+
+* 2.195e+04 seconds 2020-12-07
+* 25547.266 seconds 2020-12-09
+
+```{r}
+# system.time(oc_gp_fcsts <- 
+#               oc_monthly_quantity_gp_pre_cv19 %>% 
+#               filter(!regional_unit %in% incomplete_gp) %>% 
+#               regionalJointFcsts())
+# oc_gp_fcsts %>% 
+#   write_rds("../data/oc_gp_fcsts.rds")
+
+oc_gp_cluster_fcsts <- 
+  read_rds("../data/oc_gp_fcsts.rds")
 ```
@@
 
-```{r}
-best_model <- 
+### By Health Board
+
+```{r, health-board-discrepancies}
+best_model_hb <- 
+  oc_hb_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE)
+
+best_model_hb %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oc_hb_fcsts$forecasts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oc_monthly_quantity_hb, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = n - .mean,
+         z_discrepancy = discrepancy/sd) %>% 
+  ggplot(aes(y = discrepancy)) +
+  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none") #+
+  facet_wrap(~.model)
+```
+
+### By GP Cluster
+
+```{r, gp-cluster-discrepancies}
+best_model_gp_cluster <- 
   oc_gp_cluster_cv_models %>% 
@@
 
-best_model %>% 
+best_model_gp_cluster %>% 
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oc_gp_cluster_fcts$forecasts,
+  inner_join(mutate(oc_gp_cluster_fcsts$forecasts,
                     datename = yearmonth(datename)), 
@@
             alpha = .8, lty = 2) +
+  scale_color_gradientn(colours = rainbow(100))+
   geom_hline(aes(yintercept = 0), colour = "red") +
-  theme(legend.position = "none") #+
-#  coord_cartesian(ylim = c(-1,1)) +
-  facet_wrap(~.model)
+  theme(legend.position = "none")
 ```
@@
 library(tidyLPA)
-best_model %>% 
+best_model_gp_cluster %>% 
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oc_gp_cluster_fcts$forecasts,
+  inner_join(mutate(oc_gp_cluster_fcsts$forecasts,
                     datename = yearmonth(datename)), 
@@
   select(-regional_unit) %>% 
-  estimate_profiles(5) %>% plot_profiles()
+  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
     estimate_profiles(1:5,
@@
 
-### Plotting
+### By GP Practice
+
+```{r, gp-practice-discrepancies}
+best_model_gp <- 
+  oc_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE)
+
+best_model_gp %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oc_gp_fcsts$forecasts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oc_monthly_quantity_gp, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = n - .mean,
+         z_discrepancy = discrepancy/sd) %>% 
+  ggplot(aes(y = discrepancy)) +
+  # geom_boxplot(aes(x = as.factor(datename))) +
+  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+```
+
+## Plotting
 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oc_gp_cluster_fcts$forecasts,
+  inner_join(mutate(oc_gp_cluster_fcsts$forecasts,
                     datename = yearmonth(datename)), 
@@
 bestModelPlot(models = oc_gp_cluster_cv_models, 
-              forecasts = oc_gp_cluster_fcts$forecasts,
+              forecasts = oc_gp_cluster_fcsts$forecasts,
               data = oc_monthly_quantity_cluster,
@@
 ```
-
-## Other
-### Prophet
-
-```{r}
-# Prophet model
-oc_prophet_model <- 
-  fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                           season("year", type = "additive") + holiday(holidays))
-
-fit <- oc_monthly_quantity_locality_pre_cv19 %>% 
-  as_tsibble(index = datename) %>% 
-  model(oc_prophet_model)
-
-fc <- 
-  fit %>% 
-  forecast(h = "5 months")
-
-accuracy(fit)
-
-df <- oc_monthly_count_pre_cv19 %>% 
-  transmute(ds = datename, y = n)
-m <- prophet::prophet(df, seasonality.mode = "additive")
-future <- make_future_dataframe(m, periods = 6, freq = 'month')
-fcst <- predict(m, future)
-prophet_plot_components(m, fcst)
-
-oc_monthly_count %>% 
-  ggplot(aes(x = datename, y = n)) +
-  geom_line() +
-  geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower),
-                  ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
-              alpha = .1, fill = "blue") +
-  geom_line(aes(y = c(fcst[1:50,]$yhat, rep(NA, 5))),
-            col = "blue", lty = 2) +
-  geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)),
-            col = "blue", lty = 3) +
-  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
-
-perf <- cross_validation(model = m, initial = 3*52, horizon = 52, units = "weeks")
-performance_metrics(perf)
-plot_cross_validation_metric(perf, metric = "rmse")
-```
-
-## Split by practice
-
-```{r}
-oc %>% 
-  tibble %>% 
-  group_by(datename, PracticeID) %>% 
-  count %>% 
-  group_by(PracticeID) %>% 
-  summarise(n_min = min(n), 
-            n_mean = mean(n)) %>% arrange((n_min)) %>% 
-  filter(n_min >1)
-
-oc %>% filter(PracticeID == "W91626") %>% 
-  group_by(datename) %>% 
-  count() %>% 
-  as_tsibble(index = datename) %>% 
-  autoplot()
-
-```

### 2020-12-11 r_notebooks/exploring_oral_anticoagulants.Rmd
minor changes

@@
 oac_gp_fcsts %>%
-  write_rds("../data/oac_gp_fcsts.rds")
+  write_rds("../data/oac_gp_fcsts_1.rds")
 
 oac_gp_cluster_fcsts <- 
-  read_rds("../data/oac_gp_fcsts.rds")
+  read_rds("../data/oac_gp_fcsts_1.rds")
 ```
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_gp_fcsts$forecasts,
+  inner_join(mutate(oac_gp_fcsts,
                     datename = yearmonth(datename)), 

### 2020-12-11 r_scripts/functions/regionalJointFcsts.R

@@ -5,19 +5,19 @@ regionalJointFcsts <- function(data, h ="5 months"){
     future_map_dfr(.x = regions,
                    .f = ~fableModels(filter(data, regional_unit ==.x)),
                    .options = furrr_options(seed = TRUE))
-  message("fable fits")
+  message("fable fits complete")
 
   fable_fcst <- fable_fit %>%
     forecast(h = h) %>%
     as_tibble()
-  message("fable forecasts")
+  message("fable forecasts complete")
 
 
   prophet_fit <-
     future_map_dfr(.x = regions,
                    .f = ~prophetModels(filter(data, regional_unit ==.x)),
                    .options = furrr_options(seed = TRUE))
-  message("prophet fits")
+  message("prophet fits complete")
 
   prophet_fcst <-
     forecast(prophet_fit, h = h) %>%
@@ -25,7 +25,7 @@ regionalJointFcsts <- function(data, h ="5 months"){
   # Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
   # This may also be influencing accuracy
 
-  message("prophet forecasts")
+  message("prophet forecasts complete")
   plan(sequential)
   # prophetModels now being run in parallel. Needed to reinstall prophet from
   # source

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
adding warfarin proportion analyses

--- 2020-12-11 r_notebooks/exploring_oral_anticoagulants.Rmd
@@
     "0208020V0")
+warf <- "0208020V0"
 
@@
 oac_monthly_count <- oac %>% 
-  group_by(datename) %>% 
+  group_by(datename, bnfchem) %>% 
   summarise(n = sum(Quantity)) %>% 
+  mutate(n = n / sum(n)) %>% 
+  filter(bnfchem == warf) %>% 
   mutate(datename = yearmonth(datename),
@@
     as_tsibble(index = datename)
+```
+
+```{r prep-data}
+  propRegional <- function(data, region, datename = datename, unit = Quantity){
+  # Function to create tsibble object for a proportion of a drug by a given `unit` 
+  # per `datename`
+  # e.g. countRegional(oc, Locality, datename, Quantity) is the `Quantity`
+  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
+  # the number of days in each month.
+  region <- enquo(region)
+  datename <- enquo(datename)
+  unit <- enquo(unit)
+
+  data %>%
+    mutate(regional_unit = as_factor(set_names(!!region))) %>%
+    group_by(regional_unit, !!datename) %>%
+    summarise(n = sum(!!unit)) %>%
+    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
+                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
+                         str_detect(!!datename, pattern = "-03-") ~ n/31,
+                         str_detect(!!datename, pattern = "-04-") ~ n/30,
+                         str_detect(!!datename, pattern = "-05-") ~ n/31,
+                         str_detect(!!datename, pattern = "-06-") ~ n/30,
+                         str_detect(!!datename, pattern = "-07-") ~ n/31,
+                         str_detect(!!datename, pattern = "-08-") ~ n/31,
+                         str_detect(!!datename, pattern = "-09-") ~ n/30,
+                         str_detect(!!datename, pattern = "-10-") ~ n/31,
+                         str_detect(!!datename, pattern = "-11-") ~ n/30,
+                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
+    ungroup() %>%
+    as_tsibble(index = !!datename, key = regional_unit)
+}
 
@@
 ```{r}
+regionalJointFcsts <- function (data, h = "5 months", keep_fits = FALSE) 
+{
+  if (!is.logical(keep_fits)) {
+    stop("`keep_fits` must be of type logical")
+  }
+  regions <- unique(data$regional_unit)
+
+  cl <- parallel::makeCluster(8)
+  plan(cluster, workers = cl)
+
+  fable_fcst <- 
+    future_map_dfr(.x = regions, 
+                   .f = ~fableModels(filter(data, 
+                                            regional_unit == .x)) %>% 
+                     forecast(h = h) %>% as_tibble(), 
+                   .options = furrr_options(seed = TRUE))
+
+  message("fable fits complete, step 1/4")
+  message("fable forecasts complete, step 2/4")
+
+  prophet_fcst <- 
+    future_map_dfr(.x = regions, 
+                   .f = ~prophetModels(filter(data, 
+                                            regional_unit == .x)) %>% 
+                     forecast(h = h) %>% as_tibble(), 
+                   .options = furrr_options(seed = TRUE))
+  message("prophet fits complete, step 3/4")
+  message("prophet forecasts complete, step 4/4")
+
+  parallel::stopCluster(cl)
+  plan(sequential)
+  joint_fcst <- dplyr::bind_rows(fable_fcst, prophet_fcst) %>% 
+    dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 
+      0.1), med = median(n), ub_80 = quantile(n, 0.9), 
+      ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
+      dist = n, n = NULL)
+      return(list(forecasts = joint_fcst))
+}
+
 system.time(oac_gp_fcsts <-
@@
               filter(!regional_unit %in% incomplete_gp) %>%
-              regionalJointFcsts())
+              regionalJointFcsts(keep_fits = TRUE))
+
 oac_gp_fcsts %>%
-  write_rds("../data/oac_gp_fcsts.rds")
+  write_rds("../data/oac_gp_fcsts_2.rds")
 
 oac_gp_cluster_fcsts <- 
-  read_rds("../data/oac_gp_fcsts.rds")
+  read_rds("../data/oac_gp_fcsts_2.rds")
 ```

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants.Rmd

@@
 ```{r, health-board-modelling}
-# system.time(oac_hb_cv_models <-
-#   regionalCV(data = oac_monthly_quantity_hb_pre_cv19))
-# 
-# oac_hb_cv_models %>%
-#   write_rds("../data/oac_hb_cv_models.rds")
+plan(multisession)
+system.time(oac_hb_cv_models <-
+  regionalCV(data = oac_monthly_quantity_hb_pre_cv19))
+plan(sequential)
+
+oac_hb_cv_models %>%
+  write_rds("../data/oac_hb_cv_models.rds")
 
@@
 
-* 724.044 seconds with multisession prophetModels()
+* 476.383 seconds 2020-12-13
 
 ```{r}
-# system.time(oac_hb_fcsts <- regionalJointFcsts(oac_monthly_quantity_hb_pre_cv19))
-# 
-# oac_hb_fcsts %>%
-#   write_rds("../data/oac_hb_fcsts.rds")
+system.time(oac_hb_fcsts <- regionalJointFcsts(oac_monthly_quantity_hb_pre_cv19))
+
+oac_hb_fcsts %>%
+  write_rds("../data/oac_hb_fcsts.rds")
 
@@
 ```{r, gp-cluster-modelling}
-# system.time(oac_gp_cluster_cv_models <-
-#   regionalCV(data = oac_monthly_quantity_cluster_pre_cv19))
-# 
-# oac_gp_cluster_cv_models %>%
-#   write_rds("../data/oac_gp_cluster_cv_models.rds")
+plan(multisession)
+system.time(oac_gp_cluster_cv_models <-
+  regionalCV(data = oac_monthly_quantity_cluster_pre_cv19))
+plan(sequential)
+
+oac_gp_cluster_cv_models %>%
+  write_rds("../data/oac_gp_cluster_cv_models.rds")
 
@@
 ```{r}
-# system.time(oac_gp_cluster_fcsts <- regionalJointFcsts(oac_monthly_quantity_cluster_pre_cv19))
-# 
-# oac_gp_cluster_fcsts %>%
-#   write_rds("../data/oac_gp_cluster_fcsts.rds")
+system.time(oac_gp_cluster_fcsts <- regionalJointFcsts(oac_monthly_quantity_cluster_pre_cv19))
+
+oac_gp_cluster_fcsts %>%
+  write_rds("../data/oac_gp_cluster_fcsts.rds")
 
@@
 
-# system.time(oac_gp_cv_models <-
-#   oac_monthly_quantity_gp_pre_cv19 %>%
-#     filter(!regional_unit %in% incomplete_gp) %>%
-#               regionalCV())
-# 
-# oac_gp_cv_models %>%
-#   write_rds("../data/oac_gp_cv_models.rds")
+system.time(oac_gp_cv_models <-
+  oac_monthly_quantity_gp_pre_cv19 %>%
+    filter(!regional_unit %in% incomplete_gp) %>%
+              regionalCV())
+
+oac_gp_cv_models %>%
+  write_rds("../data/oac_gp_cv_models.rds")
 
@@
 ```{r}
-system.time(oac_gp_fcsts <-
-              oac_monthly_quantity_gp_pre_cv19 %>%
-              filter(!regional_unit %in% incomplete_gp) %>%
-              regionalJointFcsts())
-oac_gp_fcsts %>%
-  write_rds("../data/oac_gp_fcsts_1.rds")
+# plan(multisession)
+# system.time(oac_gp_fcsts <-
+#               oac_monthly_quantity_gp_pre_cv19 %>%
+#               filter(!regional_unit %in% incomplete_gp) %>%
+#               regionalJointFcsts())
+# plan(sequential)
+# oac_gp_fcsts %>%
+#   write_rds("../data/oac_gp_fcsts_1.rds")
 
-oac_gp_cluster_fcsts <- 
+oac_gp_fcsts <-
   read_rds("../data/oac_gp_fcsts_1.rds")
+
 ```
+
+* 2781.052 seconds
 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_hb_fcsts$forecasts,
+  inner_join(mutate(oac_hb_fcsts,
                     datename = yearmonth(datename)), 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_gp_cluster_fcsts$forecasts,
+  inner_join(mutate(oac_gp_cluster_fcsts,
                     datename = yearmonth(datename)), 
@@
 
-```{r}
+```{r, eval = FALSE}
 library(tidyLPA)

### 2020-12-16 r_notebooks/exploring_oral_contraceptives.Rmd

@@
 rstan_options(auto_write = TRUE)
-options(future.rng.onMisue = "ignore")
 
@@
 
-## Functions
-source("../r_scripts/functions.r")
+```
 
+```{r}
 ## Drugs of interest
@@
 ```{r}
+# plan(multisession)
 # system.time(oc_hb_fcsts <- regionalJointFcsts(oc_monthly_quantity_hb_pre_cv19))
+# plan(sequential)
 # 
@@
 ```{r}
+# plan(multisession)
 # system.time(oc_gp_cluster_fcsts <- regionalJointFcsts(oc_monthly_quantity_cluster_pre_cv19))
+# plan(sequential)
 # 
@@
 ```{r}
+# plan(multisession)
 # system.time(oc_gp_fcsts <-
@@
 #               regionalJointFcsts())
+# plan(sequential)
 # oc_gp_fcsts %>%
@@
 
-oc_gp_cluster_fcsts <- 
+oc_gp_fcsts <- 
   read_rds("../data/oc_gp_fcsts.rds")
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oc_hb_fcsts$forecasts,
+  inner_join(mutate(oc_hb_fcsts,
                     datename = yearmonth(datename)), 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oc_gp_cluster_fcsts$forecasts,
+  inner_join(mutate(oc_gp_cluster_fcsts,
                     datename = yearmonth(datename)), 
@@
             alpha = .8, lty = 2) +
-  scale_color_gradientn(colours = rainbow(100))+
+  # scale_color_gradientn(colours = rainbow(100))+
   geom_hline(aes(yintercept = 0), colour = "red") +
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oc_gp_fcsts$forecasts,
+  inner_join(mutate(oc_gp_fcsts,
                     datename = yearmonth(datename)), 
@@
 ```
-
-## Plotting
-
-```{r}
-best_model <- 
-  oc_gp_cluster_cv_models %>% 
-  group_by(regional_unit) %>% 
-  arrange(RMSE, MAE) %>% 
-  slice(1, .preserve = TRUE)
-
-best_model %>% 
-  select(.model, regional_unit) %>% 
-  inner_join(mutate(oc_gp_cluster_fcsts$forecasts,
-                    datename = yearmonth(datename)), 
-             by = c(".model", "regional_unit")) %>%
-  left_join(mutate(select(oc_monthly_quantity_cluster, 
-                          c(regional_unit, datename, n)), 
-                   datename = yearmonth(datename)),
-            by = c("datename", "regional_unit")) %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = .mean, colour = as.factor(regional_unit))) +
-  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, fill = as.factor(regional_unit),
-              alpha = .05), outline.type = "both") +
-  geom_line(aes(y = n, group = regional_unit, colour = as.factor(regional_unit)), lty = 3) +
-  coord_cartesian(ylim = c(0,50))+
-  theme(legend.position = "none") +
-  facet_wrap(~.model) + 
-  labs(caption = "Dotted line = observed data, solid line and ribbon is predicted data with 80% CIs")
-
-```
-
-```{r}
-bestModelPlot <- function(models, forecasts, data, region){
-  best_model <- 
-    models %>% 
-    group_by(regional_unit) %>% 
-    arrange(RMSE, MAE) %>% 
-    slice(1, .preserve = TRUE)
-
-  full_data <- filter(data, 
-                      datename > ymd("2020-02-28") &
-                        regional_unit == region) %>% 
-    mutate(datename = yearmonth(datename))
-
-best_model %>% 
-    select(.model, regional_unit) %>% 
-    filter(regional_unit == region) %>% 
-    inner_join(forecasts, by = c(".model", "regional_unit")) %>%
-    left_join(full_data, by = c("datename", "regional_unit")) %>% 
-    ggplot(aes(x = datename, colour = as.factor(regional_unit))) +
-    geom_line(aes(y = .mean)) +
-    geom_ribbon(aes(ymin = lb_80, ymax = ub_80, fill = as.factor(regional_unit),
-                   alpha = .1)) +
-    geom_line(aes(y = n),
-              colour = "black") +
-    theme(legend.position = "none") +
-    facet_wrap(~.model)
-}
-
-bestModelPlot(models = oc_gp_cluster_cv_models, 
-              forecasts = oc_gp_cluster_fcsts$forecasts,
-              data = oc_monthly_quantity_cluster,
-              region = "CityHealth")
-
-```

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
added propRegional to anticogulants as prop of warfarin

@@
 set.seed(32)
+
+## Function
+
+propRegional <- function(data, region, datename = datename, unit = Quantity, 
+                         bnf){
+  # Function to create tsibble object for a proportion of a drug by a given `unit` 
+  # per `datename`
+  # e.g. propRegional(oc, Locality, datename, Quantity) is the `Quantity`
+  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
+  # the number of days in each month.
+  region <- enquo(region)
+  datename <- enquo(datename)
+  unit <- enquo(unit)
+
+  data %>%
+    mutate(regional_unit = as_factor(set_names(!!region))) %>%
+    group_by(!!datename, bnfchem, regional_unit) %>% 
+    summarise(n = sum(!!unit)) %>% 
+    mutate(n = n / sum(n)) %>% 
+    filter(bnfchem == bnf) %>% 
+    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
+                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
+                         str_detect(!!datename, pattern = "-03-") ~ n/31,
+                         str_detect(!!datename, pattern = "-04-") ~ n/30,
+                         str_detect(!!datename, pattern = "-05-") ~ n/31,
+                         str_detect(!!datename, pattern = "-06-") ~ n/30,
+                         str_detect(!!datename, pattern = "-07-") ~ n/31,
+                         str_detect(!!datename, pattern = "-08-") ~ n/31,
+                         str_detect(!!datename, pattern = "-09-") ~ n/30,
+                         str_detect(!!datename, pattern = "-10-") ~ n/31,
+                         str_detect(!!datename, pattern = "-11-") ~ n/30,
+                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
+    ungroup() %>%
+    as_tsibble(index = !!datename, key = regional_unit)
+}
 
@@
 ```{r prep-data}
-  propRegional <- function(data, region, datename = datename, unit = Quantity){
-  # Function to create tsibble object for a proportion of a drug by a given `unit` 
-  # per `datename`
-  # e.g. countRegional(oc, Locality, datename, Quantity) is the `Quantity`
-  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
-  # the number of days in each month.
-  region <- enquo(region)
-  datename <- enquo(datename)
-  unit <- enquo(unit)
-
-  data %>%
-    mutate(regional_unit = as_factor(set_names(!!region))) %>%
-    group_by(regional_unit, !!datename) %>%
-    summarise(n = sum(!!unit)) %>%
-    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
-                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
-                         str_detect(!!datename, pattern = "-03-") ~ n/31,
-                         str_detect(!!datename, pattern = "-04-") ~ n/30,
-                         str_detect(!!datename, pattern = "-05-") ~ n/31,
-                         str_detect(!!datename, pattern = "-06-") ~ n/30,
-                         str_detect(!!datename, pattern = "-07-") ~ n/31,
-                         str_detect(!!datename, pattern = "-08-") ~ n/31,
-                         str_detect(!!datename, pattern = "-09-") ~ n/30,
-                         str_detect(!!datename, pattern = "-10-") ~ n/31,
-                         str_detect(!!datename, pattern = "-11-") ~ n/30,
-                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
-    ungroup() %>%
-    as_tsibble(index = !!datename, key = regional_unit)
-}
 
@@
              by = c("PracticeID" = "practiceid")) %>%
-  countRegional(hboard, datename, Quantity) %>% 
+  propRegional(region = hboard, datename = datename, unit = Quantity,
+               bnf = warf) %>% 
   left_join(gp %>% 
@@
              by = c("PracticeID" = "practiceid")) %>%
-  countRegional(cluster, datename, Quantity) %>% 
+  propRegional(cluster, datename, Quantity) %>% 
   left_join(gp %>% 
@@
 oac_monthly_quantity_gp <- 
-  countRegional(oac, PracticeID, datename, Quantity) %>% 
+  propRegional(oac, PracticeID, datename, Quantity) %>% 
   right_join(select(gp, c(practiceid, npat)), 

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
minor changes

@@
 # db.gpextract <- tbl(con, "gpextract")
-# oac <- db.gpextract %>%
+# oac_p <- db.gpextract %>%
 #   filter(bnfchem %in% oral_anticoagulants) %>%
@@
 # ## Write to local file
-# oac %>%
+# oac_p %>%
 #   write_rds("../data/oral_anticoagulants.rds")
@@
   filter(year == 2020) # do something better
-oac <- read_rds("../data/oral_anticoagulants.rds")
+oac_p <- read_rds("../data/oral_anticoagulants.rds")
 
 ## Sort into monthly count data
-oac_monthly_count <- oac %>% 
+oac_p_monthly_count <- oac_p %>% 
   group_by(datename, bnfchem) %>% 
@@
 
-oac_monthly_quantity_hb <- 
-  right_join(oac, select(gp, c(practiceid, hboard)), 
+oac_p_monthly_quantity_hb <- 
+  right_join(oac_p, select(gp, c(practiceid, hboard)), 
              by = c("PracticeID" = "practiceid")) %>%
@@
 
-oac_monthly_quantity_cluster <- 
-  right_join(oac, select(gp, c(practiceid, cluster)), 
+oac_p_monthly_quantity_cluster <- 
+  right_join(oac_p, select(gp, c(practiceid, cluster)), 
              by = c("PracticeID" = "practiceid")) %>%
@@
 
-oac_monthly_quantity_gp <- 
-  propRegional(oac, PracticeID, datename, Quantity) %>% 
+oac_p_monthly_quantity_gp <- 
+  propRegional(oac_p, PracticeID, datename, Quantity) %>% 
   right_join(select(gp, c(practiceid, npat)), 
@@
 ## Sort into monthly count data pre-lockdown (2020-03-23)
-oac_monthly_count_pre_cv19 <- 
-  oac_monthly_count %>% 
+oac_p_monthly_count_pre_cv19 <- 
+  oac_p_monthly_count %>% 
   filter(datename < dmy("01-03-2020"))
 
-oac_monthly_quantity_hb_pre_cv19 <- 
-  oac_monthly_quantity_hb %>% 
+oac_p_monthly_quantity_hb_pre_cv19 <- 
+  oac_p_monthly_quantity_hb %>% 
     filter(datename < dmy("01-03-2020"))
 
-oac_monthly_quantity_cluster_pre_cv19 <- 
-  oac_monthly_quantity_cluster %>% 
+oac_p_monthly_quantity_cluster_pre_cv19 <- 
+  oac_p_monthly_quantity_cluster %>% 
     filter(datename < dmy("01-03-2020"))
 
-oac_monthly_quantity_gp_pre_cv19 <- 
-  oac_monthly_quantity_gp %>% 
+oac_p_monthly_quantity_gp_pre_cv19 <- 
+  oac_p_monthly_quantity_gp %>% 
     filter(datename < dmy("01-03-2020"))
@@
 
-### 2016-2020 plot of all oac prescriptions
+### 2016-2020 plot of all oac_p prescriptions
 
-```{r oac-monthly-ts-plot, fig.cap="Total quantity of combined oral anticoagulants prescribed per month."}
-oac %>% 
+```{r oac_p-monthly-ts-plot, fig.cap="Total quantity of combined oral anticoagulants prescribed per month."}
+oac_p %>% 
   group_by(datename) %>% 
@@
 
-```{r oac-monthly-seasonality-plot}
-df <- oac_monthly_count_pre_cv19 %>% 
+```{r oac_p-monthly-seasonality-plot}
+df <- oac_p_monthly_count_pre_cv19 %>% 
   mutate(month = as.factor(month(datename, label = TRUE, abbr = TRUE)),
@@
 ```{r}
-oac_monthly_count_pre_cv19 %>% 
+oac_p_monthly_count_pre_cv19 %>% 
   mutate(datename = yearmonth(datename)) %>% 
@@
 ```{r}
-tseries::adf.test(oac_monthly_count$n)
-urca::ur.df(oac_monthly_count$n)
+tseries::adf.test(oac_p_monthly_count$n)
+urca::ur.df(oac_p_monthly_count$n)
 ```
@@
 ```{r}
-oac_monthly_count_pre_cv19 %>%
+oac_p_monthly_count_pre_cv19 %>%
   mutate(datename = yearmonth(datename)) %>% 
@@
 ```{r}
-oac_monthly_count_pre_cv19$n %>%
+oac_p_monthly_count_pre_cv19$n %>%
   pacf(lag.max = 24)
@@
 ```{r, health-board-modelling}
-# system.time(oac_hb_cv_models <-
-#   regionalCV(data = oac_monthly_quantity_hb_pre_cv19))
-# 
-# oac_hb_cv_models %>%
-#   write_rds("../data/oac_hb_cv_models.rds")
+system.time(oac_p_hb_cv_models <-
+  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
 
-oac_hb_cv_models <- 
-  read_rds("../data/oac_hb_cv_models.rds")
+oac_p_hb_cv_models %>%
+  write_rds("../data/oac_p_hb_cv_models.rds")
 
-oac_hb_cv_models %>% 
+oac_p_hb_cv_models <- 
+  read_rds("../data/oac_p_hb_cv_models.rds")
+
+oac_p_hb_cv_models %>% 
   group_by(regional_unit) %>% 
@@
 
-oac_hb_cv_models %>% 
+oac_p_hb_cv_models %>% 
   group_by(regional_unit) %>% 
@@
 ```{r}
-# system.time(oac_hb_fcsts <- regionalJointFcsts(oac_monthly_quantity_hb_pre_cv19))
-# 
-# oac_hb_fcsts %>%
-#   write_rds("../data/oac_hb_fcsts.rds")
+system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
 
-oac_hb_fcsts <- 
-  read_rds("../data/oac_hb_fcsts.rds")
+oac_p_hb_fcsts %>%
+  write_rds("../data/oac_p_hb_fcsts.rds")
+
+oac_p_hb_fcsts <- 
+  read_rds("../data/oac_p_hb_fcsts.rds")
 ```
@@
 ```{r, gp-cluster-modelling}
-# system.time(oac_gp_cluster_cv_models <-
-#   regionalCV(data = oac_monthly_quantity_cluster_pre_cv19))
-# 
-# oac_gp_cluster_cv_models %>%
-#   write_rds("../data/oac_gp_cluster_cv_models.rds")
+system.time(oac_p_gp_cluster_cv_models <-
+  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
 
-oac_gp_cluster_cv_models <- 
-  read_rds("../data/oac_gp_cluster_cv_models.rds")
+oac_p_gp_cluster_cv_models %>%
+  write_rds("../data/oac_p_gp_cluster_cv_models.rds")
 
-oac_gp_cluster_cv_models %>% 
+oac_p_gp_cluster_cv_models <- 
+  read_rds("../data/oac_p_gp_cluster_cv_models.rds")
+
+oac_p_gp_cluster_cv_models %>% 
   group_by(regional_unit) %>% 
@@
 
-oac_gp_cluster_cv_models %>% 
+oac_p_gp_cluster_cv_models %>% 
   group_by(regional_unit) %>% 
@@
 ```{r}
-# system.time(oac_gp_cluster_fcsts <- regionalJointFcsts(oac_monthly_quantity_cluster_pre_cv19))
-# 
-# oac_gp_cluster_fcsts %>%
-#   write_rds("../data/oac_gp_cluster_fcsts.rds")
+system.time(oac_p_gp_cluster_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
 
-oac_gp_cluster_fcsts <- 
-  read_rds("../data/oac_gp_cluster_fcsts.rds")
+oac_p_gp_cluster_fcsts %>%
+  write_rds("../data/oac_p_gp_cluster_fcsts.rds")
+
+oac_p_gp_cluster_fcsts <- 
+  read_rds("../data/oac_p_gp_cluster_fcsts.rds")
 ```
@@
 ```{r, gp-practice-modelling}
-incomplete_gp <- oac_monthly_quantity_gp_pre_cv19 %>% 
+incomplete_gp <- oac_p_monthly_quantity_gp_pre_cv19 %>% 
     as_tibble() %>% 
@@
 
-# system.time(oac_gp_cv_models <-
-#   oac_monthly_quantity_gp_pre_cv19 %>%
-#     filter(!regional_unit %in% incomplete_gp) %>%
-#               regionalCV())
-# 
-# oac_gp_cv_models %>%
-#   write_rds("../data/oac_gp_cv_models.rds")
+system.time(oac_p_gp_cv_models <-
+  oac_p_monthly_quantity_gp_pre_cv19 %>%
+    filter(!regional_unit %in% incomplete_gp) %>%
+              regionalCV())
 
-oac_gp_cv_models <- 
-  read_rds("../data/oac_gp_cv_models.rds")
+oac_p_gp_cv_models %>%
+  write_rds("../data/oac_p_gp_cv_models.rds")
 
-oac_gp_cv_models %>% 
+oac_p_gp_cv_models <- 
+  read_rds("../data/oac_p_gp_cv_models.rds")
+
+oac_p_gp_cv_models %>% 
   group_by(regional_unit) %>% 
@@
 
-oac_gp_cv_models %>% 
+oac_p_gp_cv_models %>% 
   group_by(regional_unit) %>% 
@@
 
-system.time(oac_gp_fcsts <-
-              oac_monthly_quantity_gp_pre_cv19 %>%
+system.time(oac_p_gp_fcsts <-
+              oac_p_monthly_quantity_gp_pre_cv19 %>%
               filter(!regional_unit %in% incomplete_gp) %>%
@@
 
-oac_gp_fcsts %>%
-  write_rds("../data/oac_gp_fcsts_2.rds")
+oac_p_gp_fcsts %>%
+  write_rds("../data/oac_p_gp_fcsts_2.rds")
 
-oac_gp_cluster_fcsts <- 
-  read_rds("../data/oac_gp_fcsts_2.rds")
+oac_p_gp_cluster_fcsts <- 
+  read_rds("../data/oac_p_gp_fcsts_2.rds")
 ```
@@
 best_model_hb <- 
-  oac_hb_cv_models %>% 
+  oac_p_hb_cv_models %>% 
   group_by(regional_unit) %>% 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_hb_fcsts$forecasts,
+  inner_join(mutate(oac_p_hb_fcsts$forecasts,
                     datename = yearmonth(datename)), 
              by = c(".model", "regional_unit")) %>%
-  left_join(mutate(select(oac_monthly_quantity_hb, 
+  left_join(mutate(select(oac_p_monthly_quantity_hb, 
                           c(regional_unit, datename, n)), 
@@
 best_model_gp_cluster <- 
-  oac_gp_cluster_cv_models %>% 
+  oac_p_gp_cluster_cv_models %>% 
   group_by(regional_unit) %>% 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_gp_cluster_fcsts$forecasts,
+  inner_join(mutate(oac_p_gp_cluster_fcsts$forecasts,
                     datename = yearmonth(datename)), 
              by = c(".model", "regional_unit")) %>%
-  left_join(mutate(select(oac_monthly_quantity_cluster, 
+  left_join(mutate(select(oac_p_monthly_quantity_cluster, 
                           c(regional_unit, datename, n)), 
@@
 best_model_gp <- 
-  oac_gp_cv_models %>% 
+  oac_p_gp_cv_models %>% 
   group_by(regional_unit) %>% 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_gp_fcsts$forecasts,
+  inner_join(mutate(oac_p_gp_fcsts$forecasts,
                     datename = yearmonth(datename)), 
              by = c(".model", "regional_unit")) %>%
-  left_join(mutate(select(oac_monthly_quantity_gp, 
+  left_join(mutate(select(oac_p_monthly_quantity_gp, 
                           c(regional_unit, datename, n)), 

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
typos

@@
     as_tsibble(index = datename)
-```
-
-```{r prep-data}
 
@@
              by = c("PracticeID" = "practiceid")) %>%
-  propRegional(cluster, datename, Quantity) %>% 
+  propRegional(cluster, datename, Quantity, bnf = warf) %>% 
   left_join(gp %>% 
@@
 oac_p_monthly_quantity_gp <- 
-  propRegional(oac_p, PracticeID, datename, Quantity) %>% 
+  propRegional(oac_p, PracticeID, datename, Quantity, bnf = warf) %>% 
   right_join(select(gp, c(practiceid, npat)), 

### 2021-01-07 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
Setting oac analyses as warfarin proportion of all oac

--- 2020-12-16 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
@@
     summarise(n = sum(!!unit)) %>% 
-    mutate(n = n / sum(n)) %>% 
+    mutate(n = 100 * n / sum(n),
+           log_n = log(n)) %>% 
     filter(bnfchem == bnf) %>%
-    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
-                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
-                         str_detect(!!datename, pattern = "-03-") ~ n/31,
-                         str_detect(!!datename, pattern = "-04-") ~ n/30,
-                         str_detect(!!datename, pattern = "-05-") ~ n/31,
-                         str_detect(!!datename, pattern = "-06-") ~ n/30,
-                         str_detect(!!datename, pattern = "-07-") ~ n/31,
-                         str_detect(!!datename, pattern = "-08-") ~ n/31,
-                         str_detect(!!datename, pattern = "-09-") ~ n/30,
-                         str_detect(!!datename, pattern = "-10-") ~ n/31,
-                         str_detect(!!datename, pattern = "-11-") ~ n/30,
-                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
     ungroup() %>%
@@
          N = NULL) %>% 
-  filter(year == 2020) # do something better
+  filter(year == 2020) # Do something better. Is npat important for the proportion?
+
 oac_p <- read_rds("../data/oral_anticoagulants.rds")
@@
 ## Sort into monthly count data
-oac_p_monthly_count <- oac_p %>% 
+oac_p_monthly_count <- 
+  oac_p %>% 
   group_by(datename, bnfchem) %>% 
   summarise(n = sum(Quantity)) %>% 
-  mutate(n = n / sum(n)) %>% 
+  mutate(n = 100 * n / sum(n), # make it a percentage rather than proportion
+         log_n = log(n)) %>% 
   filter(bnfchem == warf) %>% 
-  mutate(datename = yearmonth(datename),
-         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
-                       str_detect(datename, pattern = "Feb") ~ n/28.25,
-                       str_detect(datename, pattern = "Mar") ~ n/31,
-                       str_detect(datename, pattern = "Apr") ~ n/30,
-                       str_detect(datename, pattern = "May") ~ n/31,
-                       str_detect(datename, pattern = "Jun") ~ n/30,
-                       str_detect(datename, pattern = "Jul") ~ n/31,
-                       str_detect(datename, pattern = "Aug") ~ n/31,
-                       str_detect(datename, pattern = "Sep") ~ n/30,
-                       str_detect(datename, pattern = "Oct") ~ n/31,
-                       str_detect(datename, pattern = "Nov") ~ n/30,
-                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
   ungroup() %>%
   as_tsibble(index = datename)
-```
-
-```{r prep-data}
 
@@
   propRegional(region = hboard, datename = datename, unit = Quantity,
-               bnf = warf) %>% 
-  left_join(gp %>% 
-  select(c(practiceid, npat, hboard)) %>% 
-  group_by(hboard) %>% 
-  summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
-  mutate(n = 1000*n/npat) # quantity per 1000 pts
+               bnf = warf)
 
@@
              by = c("PracticeID" = "practiceid")) %>%
-  propRegional(cluster, datename, Quantity) %>% 
-  left_join(gp %>% 
-  select(c(practiceid, npat, cluster)) %>% 
-  group_by(cluster) %>% 
-  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
-  mutate(n = 1000*n/npat) # quantity per 1000 pts
+  propRegional(cluster, datename, Quantity, bnf = warf)
 
 oac_p_monthly_quantity_gp <- 
-  propRegional(oac_p, PracticeID, datename, Quantity) %>% 
-  right_join(select(gp, c(practiceid, npat)), 
-            by = c("regional_unit" = "practiceid")) %>% 
-  mutate(n = 1000*n/npat)
+  propRegional(oac_p, PracticeID, datename, Quantity, bnf = warf)
 
@@
   autoplot(n) +
+  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
+```
+
+```{r oac-p-monthly-ts-plot, fig.cap="Total quantity of combined oral anticoagulants prescribed per month."}
+oac_p_monthly_count %>% 
+  select(datename, n) %>% 
+  autoplot() +
   geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
@@
 ```{r, health-board-modelling}
-system.time(oac_p_hb_cv_models <-
-  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
-
-oac_p_hb_cv_models %>%
-  write_rds("../data/oac_p_hb_cv_models.rds")
+# system.time(oac_p_hb_cv_models <-
+#   regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
+# 
+# oac_p_hb_cv_models %>%
+#   write_rds("../data/oac_p_hb_cv_models.rds")
 
@@
 ```{r}
-system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
-
-oac_p_hb_fcsts %>%
-  write_rds("../data/oac_p_hb_fcsts.rds")
+# system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
+# 
+# oac_p_hb_fcsts %>%
+#   write_rds("../data/oac_p_hb_fcsts.rds")
 
@@
 ```{r, gp-cluster-modelling}
-system.time(oac_p_gp_cluster_cv_models <-
-  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
-
-oac_p_gp_cluster_cv_models %>%
-  write_rds("../data/oac_p_gp_cluster_cv_models.rds")
+# system.time(oac_p_gp_cluster_cv_models <-
+#   regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
+# 
+# oac_p_gp_cluster_cv_models %>%
+#   write_rds("../data/oac_p_gp_cluster_cv_models.rds")
 
@@
 ```{r}
-system.time(oac_p_gp_cluster_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
-
-oac_p_gp_cluster_fcsts %>%
-  write_rds("../data/oac_p_gp_cluster_fcsts.rds")
+# plan(multisession)
+# system.time(oac_p_gp_cluster_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
+# plan(sequential)
+# 
+# oac_p_gp_cluster_fcsts %>%
+#   write_rds("../data/oac_p_gp_cluster_fcsts.rds")
 
@@
 
-system.time(oac_p_gp_cv_models <-
-  oac_p_monthly_quantity_gp_pre_cv19 %>%
-    filter(!regional_unit %in% incomplete_gp) %>%
-              regionalCV())
-
-oac_p_gp_cv_models %>%
-  write_rds("../data/oac_p_gp_cv_models.rds")
+# system.time(oac_p_gp_cv_models <-
+#   oac_p_monthly_quantity_gp_pre_cv19 %>%
+#     filter(!regional_unit %in% incomplete_gp) %>%
+#               regionalCV())
+# 
+# oac_p_gp_cv_models %>%
+#   write_rds("../data/oac_p_gp_cv_models.rds")
 
@@
 ```{r}
-regionalJointFcsts <- function (data, h = "5 months", keep_fits = FALSE) 
-{
-  if (!is.logical(keep_fits)) {
-    stop("`keep_fits` must be of type logical")
-  }
-  regions <- unique(data$regional_unit)
+# regionalJointFcsts <- function (data, h = "5 months", keep_fits = FALSE) 
+# {
+#   if (!is.logical(keep_fits)) {
+#     stop("`keep_fits` must be of type logical")
+#   }
+#   regions <- unique(data$regional_unit)
+#   
+#   cl <- parallel::makeCluster(8)
+#   plan(cluster, workers = cl)
+#   
+#   fable_fcst <- 
+#     future_map_dfr(.x = regions, 
+#                    .f = ~fableModels(filter(data, 
+#                                             regional_unit == .x)) %>% 
+#                      forecast(h = h) %>% as_tibble(), 
+#                    .options = furrr_options(seed = TRUE))
+#   
+#   
+#   message("fable fits complete, step 1/4")
+#   message("fable forecasts complete, step 2/4")
+# 
+#   prophet_fcst <- 
+#     future_map_dfr(.x = regions, 
+#                    .f = ~prophetModels(filter(data, 
+#                                             regional_unit == .x)) %>% 
+#                      forecast(h = h) %>% as_tibble(), 
+#                    .options = furrr_options(seed = TRUE))
+#   message("prophet fits complete, step 3/4")
+#   message("prophet forecasts complete, step 4/4")
+#   
+#   parallel::stopCluster(cl)
+#   plan(sequential)
+#   joint_fcst <- dplyr::bind_rows(fable_fcst, prophet_fcst) %>% 
+#     dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 
+#       0.1), med = median(n), ub_80 = quantile(n, 0.9), 
+#       ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
+#       dist = n, n = NULL)
+#       return(list(forecasts = joint_fcst))
+# }
 
-  cl <- parallel::makeCluster(8)
-  plan(cluster, workers = cl)
+# system.time(oac_p_gp_fcsts <-
+#               oac_p_monthly_quantity_gp_pre_cv19 %>%
+#               filter(!regional_unit %in% incomplete_gp) %>%
+#               regionalJointFcsts())
+# 
+# oac_p_gp_fcsts %>%
+#   write_rds("../data/oac_p_gp_fcsts.rds")
 
-  fable_fcst <- 
-    future_map_dfr(.x = regions, 
-                   .f = ~fableModels(filter(data, 
-                                            regional_unit == .x)) %>% 
-                     forecast(h = h) %>% as_tibble(), 
-                   .options = furrr_options(seed = TRUE))
+oac_p_gp_fcsts <- 
+  read_rds("../data/oac_p_gp_fcsts.rds")
+```
 
-  message("fable fits complete, step 1/4")
-  message("fable forecasts complete, step 2/4")
-
-  prophet_fcst <- 
-    future_map_dfr(.x = regions, 
-                   .f = ~prophetModels(filter(data, 
-                                            regional_unit == .x)) %>% 
-                     forecast(h = h) %>% as_tibble(), 
-                   .options = furrr_options(seed = TRUE))
-  message("prophet fits complete, step 3/4")
-  message("prophet forecasts complete, step 4/4")
-
-  parallel::stopCluster(cl)
-  plan(sequential)
-  joint_fcst <- dplyr::bind_rows(fable_fcst, prophet_fcst) %>% 
-    dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 
-      0.1), med = median(n), ub_80 = quantile(n, 0.9), 
-      ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
-      dist = n, n = NULL)
-      return(list(forecasts = joint_fcst))
-}
-
-system.time(oac_p_gp_fcsts <-
-              oac_p_monthly_quantity_gp_pre_cv19 %>%
-              filter(!regional_unit %in% incomplete_gp) %>%
-              regionalJointFcsts(keep_fits = TRUE))
-
-oac_p_gp_fcsts %>%
-  write_rds("../data/oac_p_gp_fcsts_2.rds")
-
-oac_p_gp_cluster_fcsts <- 
-  read_rds("../data/oac_p_gp_fcsts_2.rds")
-```
+* 2020-12-18 2694 secs
 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_p_hb_fcsts$forecasts,
+  inner_join(mutate(oac_p_hb_fcsts,
                     datename = yearmonth(datename)), 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_p_gp_cluster_fcsts$forecasts,
+  inner_join(mutate(oac_p_gp_cluster_fcsts,
                     datename = yearmonth(datename)), 
@@
 
+```{r, eval = FALSE}
+# lcmm::
+
+```
+
 ```{r}
-library(tidyLPA)
 best_model_gp_cluster %>% 
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_p_gp_cluster_fcsts$forecasts,
+  inner_join(mutate(oac_p_gp_cluster_fcsts,
                     datename = yearmonth(datename)), 
@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean,
-         z_discrepancy = discrepancy/sd)  %>%
-    select(discrepancy, regional_unit, datename) %>%
+  mutate(discrepancy = (n - .mean), # Why are the numbers so small?
+         regional_unit = as.factor(regional_unit)) %>% 
+  select(regional_unit, datename, discrepancy) %>% 
   pivot_wider(names_from = datename, values_from = discrepancy) %>% 
-  ungroup() %>% 
-  select(-regional_unit) %>% 
-  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
-    estimate_profiles(1:5,
-                      variances = c("equal", "varying"),
-                      covariances = c("zero", "varying")
-                      ) %>% 
-    compare_solutions(statistics = c("AIC", "BIC"))
+  mutate(regional_unit = as.numeric(regional_unit)) %>% 
+  write_csv(file = "../data/mplus/oac_cluster_discrep.csv", col_names = FALSE)
 ```
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(oac_p_gp_fcsts$forecasts,
+  inner_join(mutate(oac_p_gp_fcsts,
                     datename = yearmonth(datename)), 
@@
   theme(legend.position = "none")
+
 ```
+
+```{r}
+best_model_gp %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oac_p_gp_fcsts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oac_p_monthly_quantity_gp, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = 1000000*(n - .mean), # Why are the numbers so small?
+         regional_unit = as.factor(regional_unit)) %>% 
+  select(regional_unit, datename, discrepancy) %>% 
+  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
+  mutate(regional_unit = as.numeric(regional_unit)) %>% 
+  na.omit() %>% .[2:5] %>% min()
+  write_csv(file = "../data/mplus/oac_gp_discrep.csv", col_names = FALSE)
+```
+
+```{r}
+source("../r_scripts/functions/mplus_plotting.R")
+mplus.view.plots("../mplus_analyses/oac_discrep_3_class_bayes.gh5")
+mplus.plot.estimated_means("../mplus_analyses/oac_discrep_3_class_bayes.gh5")
+```

### 2021-01-08 r_notebooks/parallel_forecasting.Rmd
Addibg mplus plotting functions from http://www.statmodel.com/mplus-R/

@@
 library(knitr)
+library(serCymruTools)
 
@@
 set.seed(32)
-
-# Functions ####
-
-source("../r_scripts/functions.r")
 
@@
 ```{r}
-cross_validation(select(oc_gp_cluster_fcts$fits, c(regional_unit, starts_with("oc_proph"))), horizon = .5, units = "years", initial = 3)
+cross_validation(select(oc_gp_cluster_fcts$fits, c(regional_unit, starts_with("oc_proph"))), horizon = , units = "years", initial = 3)
 ```
@@
 ```
+
+## parallel joint forecasts
+
+Why does only one part of this run in parallel?
+
+```{r}
+regionalJointFcsts <- function(data, h ="5 months"){
+  regions <- unique(data$regional_unit)
+  plan(multisession, gc = TRUE)
+  fable_fit <-
+    future_map_dfr(.x = regions,
+                   .f = ~fableModels(filter(data, regional_unit ==.x)),
+                   .options = furrr_options(seed = TRUE))
+  message("fable fits complete")
+
+  fable_fcst <- 
+    future_map_dfr(.x = regions,
+                   .f = ~as_tibble(forecast(filter(fable_fit, 
+                                                   regional_unit ==.x),
+                                  h = h)),
+                   .options = furrr_options(seed = TRUE))
+    # fable_fit %>%
+    # forecast(h = h) %>%
+    # as_tibble()
+  message("fable forecasts complete")
+
+  prophet_fit <-
+    future_map_dfr(.x = regions,
+                   .f = ~prophetModels(filter(data, regional_unit ==.x)),
+                   .options = furrr_options(seed = TRUE))
+  message("prophet fits complete")
+
+  prophet_fcst <-
+        future_map_dfr(.x = regions,
+                   .f = ~as_tibble(forecast(filter(prophet_fit, 
+                                                   regional_unit ==.x),
+                                  h = h)),
+                   .options = furrr_options(seed = TRUE))
+    # forecast(prophet_fit, h = h) %>%
+    # as_tibble()
+  # Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
+  # This may also be influencing accuracy
+
+  message("prophet forecasts complete")
+  plan(sequential)
+  # prophetModels now being run in parallel. Needed to reinstall prophet from
+  # source
+
+  joint_fcst <-
+    bind_rows(fable_fcst, prophet_fcst) %>%
+    mutate(lb_95 = quantile(n, .025),
+           lb_80 = quantile(n, .1),
+           med = median(n),
+           ub_80 = quantile(n, .9),
+           ub_95 = quantile(n, .975),
+           sd = distributional::variance(n)^2,
+           dist = n,
+           n = NULL)
+
+  return(joint_fcst)
+}
+
+system.time(regionalJointFcsts(data = dev_data))
+```
+
+84.619 seconds when opening and closing plan(multisession) over 5 regional units vs 59.108 when leaving them open

### 2021-01-08 r_notebooks/exploring_oral_contraceptives.Rmd
adding latent trajectory analyses to oc

@@
 ```
+
+```{r}
+best_model_gp %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oc_gp_fcsts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oc_monthly_quantity_gp, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = (n - .mean), # Why are the numbers so small?
+         regional_unit = as.factor(regional_unit)) %>% 
+  select(regional_unit, datename, discrepancy) %>% 
+  filter(!is.na(discrepancy)) %>% # need to remove NA before pivoting to enalable values_fill
+  pivot_wider(names_from = datename, values_from = discrepancy, values_fill = -999) %>% 
+  left_join(select(gp, c(practiceid, cluster)), by = c("regional_unit" = "practiceid")) %>% 
+  mutate(regional_unit = as.factor(regional_unit),
+         cluster = as.factor(cluster)) %>% 
+  mutate(regional_unit = as.numeric(regional_unit),
+         cluster = as.numeric(cluster)) %>% 
+  select(cluster, regional_unit, everything()) %>% 
+  write_csv(file = "../data/mplus/oc_gp_discrep.csv", col_names = FALSE)
+
+```
+
+```{r}
+source("../r_scripts/functions/mplus_plotting.R")
+mplus.view.plots("../mplus_analyses/oc_gp/oac_discrep_3_class_bayes.gh5")
+mplus.plot.estimated_means("../mplus_analyses/oc_gp/oac_discrep_3_class_bayes.gh5")
+```

### 2021-01-10 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
oac_prop_war analyses

@@
 ```{r, gp-practice-modelling}
+regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
+
+  # CV accuracy for fableModels() and prophetModels()
+
+  regions <- unique(data$regional_unit) # Get unique regional_units for map()
+
+  fableModels <- function(data){
+  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
+
+  data %>%
+    mutate(datename = yearmonth(datename)) %>%
+    model(trend_model1 = TSLM(log(n) ~ trend()),#time series linear model
+          trend_model2 = TSLM(log(n) ~ trend() + season("year")),
+          ets1 = ETS(log(n) ~ trend()),
+          ets2 = ETS(log(n) ~ trend() + season("A")),
+          ets3 = ETS(log(n) ~ trend() + season("M")),
+          arima = ARIMA(log(n), stepwise = FALSE, approximation = FALSE),
+          neur_net = NNETAR(log(n)),
+          #fasster = FASSTER(n ~ season("1 year") + trend(1) + fourier(12)),
+          comb1 = combination_model(TSLM(log(n) ~ trend()),
+                                    ETS(log(n) ~ trend())),
+          comb2 = combination_model(TSLM(log(n) ~ trend() + season("year")),
+                                    ETS(log(n) ~ trend() + season("A"))),
+          stl_dcmp1 = decomposition_model(STL(log(n) ~ trend(),
+                                              iterations = 1000,
+                                              robust = TRUE),
+                                          SNAIVE(season_adjust)),
+          stl_dcmp2 = decomposition_model(STL(log(n) ~ trend() + season(),
+                                              iterations = 1000,
+                                              robust = TRUE),
+                                          SNAIVE(season_adjust)),
+          s_naive = SNAIVE(log(n)))# %>%
+    #as_tibble() # map_dfr() doesn't work on tsibble objects
+  }
+
+  prophetModels <- function(data){
+  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
+
+  oc_prophet_model1 <-
+    fable.prophet::prophet(log(n) ~ growth("linear", n_changepoints = 0) +
+                             season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model2 <-
+    fable.prophet::prophet(log(n) ~ growth("linear", n_changepoints = 0) +
+                             season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model3 <-
+    fable.prophet::prophet(log(n) ~ growth("linear") +
+                             season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model4 <-
+    fable.prophet::prophet(log(n) ~ growth("linear") +
+                             season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model5 <-
+    fable.prophet::prophet(log(n) ~ season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model6 <-
+    fable.prophet::prophet(log(n) ~ season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model7 <-
+    fable.prophet::prophet(log(n) ~ holiday(holidays))
+  oc_prophet_model8 <-
+    fable.prophet::prophet(log(n))
+
+  data %>%
+    mutate(datename = yearmonth(datename)) %>%
+    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
+          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
+          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
+}
+
+holidays <-
+  bind_rows(tibble(holiday = "christmas",
+                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
+                                  "2019-12-25", "2020-12-25", "2021-12-25")),
+                   lower_window = -1,
+                   upper_window = 1),
+
+            tibble(holiday = "easter", # Sunday
+                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
+                                  "2019-04-21", "2020-04-12", "2021-04-04")),
+                   lower_window = -2,
+                   upper_window = 1))
+
+  fableCV <- function(data){ # Return CV model accuracy for fableModels()
+    data_test <-
+      data %>%
+      mutate(datename = yearmonth(datename))
+
+    data_tr <-
+      data %>%
+      select(regional_unit, datename, n) %>%
+      mutate(datename = yearmonth(datename)) %>%
+      fill_gaps() %>%
+      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
+      stretch_tsibble(.init = init, .step = step)
+
+    data_tr %>%
+      fableModels() %>%
+      forecast(h = cv_dist) %>%
+      accuracy(data_test)
+
+  }
+
+  prophetCV <- function(data){# Return CV model accuracy for prophetModels()
+    data_test <-
+      data %>%
+      mutate(datename = yearmonth(datename))
+
+    data_tr <-
+      data %>%
+      select(regional_unit, datename, n) %>%
+      mutate(datename = yearmonth(datename)) %>%
+      fill_gaps() %>%
+      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
+      stretch_tsibble(.init = init, .step = step)
+
+    data_tr %>%
+      prophetModels() %>%
+      forecast(h = cv_dist) %>%
+      accuracy(data_test)
+  }
+
+  plan(cluster) # Set up parallel processing to decrease computation time
+  # Prophet models won't run with plan(multisession) so need to be run
+  # sequentially. Is it worth trying to write this in Python and pass it back
+  # to R?
+
+    # Probably worth trying the prophet::cross_validation() method. If it
+    # returns RMSE and is faster it will be useful.
+  prophet_fits <-
+    future_map_dfr(.x =  regions,
+            .f = ~prophetCV(data = filter(data, regional_unit == .x)),
+            .options = furrr_options(seed = TRUE))
+  message("prophetModels() complete")
+
+  # Fable models will run using plan(multisession), but need to be run as below
+  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
+  # generated
+  fable_fits <-
+    future_map_dfr(.x =  regions,
+                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
+                   .options = furrr_options(seed = TRUE))
+  plan(sequential) # Close the multiprocess function to prevent memory leakage
+  message("fableModels() complete")
+
+  bind_rows(fable_fits, prophet_fits) %>%
+    group_by(regional_unit) %>%
+    arrange(RMSE, MAE)
+}
+
 incomplete_gp <- oac_p_monthly_quantity_gp_pre_cv19 %>% 
@@
 
-# system.time(oac_p_gp_cv_models <-
-#   oac_p_monthly_quantity_gp_pre_cv19 %>%
-#     filter(!regional_unit %in% incomplete_gp) %>%
-#               regionalCV())
-# 
-# oac_p_gp_cv_models %>%
-#   write_rds("../data/oac_p_gp_cv_models.rds")
+system.time(oac_p_gp_cv_models <-
+  oac_p_monthly_quantity_gp_pre_cv19 %>%
+    filter(!regional_unit %in% incomplete_gp) %>%
+              regionalCV())
+
+oac_p_gp_cv_models %>%
+  write_rds("../data/oac_p_gp_cv_models.rds")
 
@@
 
-# system.time(oac_p_gp_fcsts <-
-#               oac_p_monthly_quantity_gp_pre_cv19 %>%
-#               filter(!regional_unit %in% incomplete_gp) %>%
-#               regionalJointFcsts())
-# 
-# oac_p_gp_fcsts %>%
-#   write_rds("../data/oac_p_gp_fcsts.rds")
+system.time(oac_p_gp_fcsts <-
+              oac_p_monthly_quantity_gp_pre_cv19 %>%
+              filter(!regional_unit %in% incomplete_gp) %>%
+              regionalJointFcsts())
+
+oac_p_gp_fcsts %>%
+  write_rds("../data/oac_p_gp_fcsts.rds")
 
@@
 
-```{r}
+```{r, eval = FALSE}
 best_model_gp %>% 
@@
 
-```{r}
+```{r, eval = FALSE}
 source("../r_scripts/functions/mplus_plotting.R")

### 2021-01-10 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
splitting gp_practices to ease computational burden

@@
     as_tsibble(index = !!datename, key = regional_unit)
+}
+
+# Modifying functions to model log(n) as using proportion data
+regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
+
+  # CV accuracy for fableModels() and prophetModels()
+
+  regions <- unique(data$regional_unit) # Get unique regional_units for map()
+
+  fableModels <- function(data){
+    if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
+
+    data %>%
+      mutate(datename = yearmonth(datename)) %>%
+      model(trend_model1 = TSLM(log(n) ~ trend()),#time series linear model
+            trend_model2 = TSLM(log(n) ~ trend() + season("year")),
+            ets1 = ETS(log(n) ~ trend()),
+            ets2 = ETS(log(n) ~ trend() + season("A")),
+            ets3 = ETS(log(n) ~ trend() + season("M")),
+            arima = ARIMA(log(n), stepwise = FALSE, approximation = FALSE),
+            neur_net = NNETAR(log(n)),
+            comb1 = combination_model(TSLM(log(n) ~ trend()),
+                                      ETS(log(n) ~ trend())),
+            comb2 = combination_model(TSLM(log(n) ~ trend() + season("year")),
+                                      ETS(log(n) ~ trend() + season("A"))),
+            stl_dcmp1 = decomposition_model(STL(log(n) ~ trend(),
+                                                iterations = 1000,
+                                                robust = TRUE),
+                                            SNAIVE(season_adjust)),
+            stl_dcmp2 = decomposition_model(STL(log(n) ~ trend() + season(),
+                                                iterations = 1000,
+                                                robust = TRUE),
+                                            SNAIVE(season_adjust)),
+            s_naive = SNAIVE(log(n)))
+  }
+
+  prophetModels <- function(data){
+    if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
+
+    oc_prophet_model1 <-
+      fable.prophet::prophet(log(n) ~ growth("linear", n_changepoints = 0) +
+                               season("year", type = "additive") +
+                               holiday(holidays))
+    oc_prophet_model2 <-
+      fable.prophet::prophet(log(n) ~ growth("linear", n_changepoints = 0) +
+                               season("year", type = "multiplicative") +
+                               holiday(holidays))
+    oc_prophet_model3 <-
+      fable.prophet::prophet(log(n) ~ growth("linear") +
+                               season("year", type = "additive") +
+                               holiday(holidays))
+    oc_prophet_model4 <-
+      fable.prophet::prophet(log(n) ~ growth("linear") +
+                               season("year", type = "multiplicative") +
+                               holiday(holidays))
+    oc_prophet_model5 <-
+      fable.prophet::prophet(log(n) ~ season("year", type = "additive") +
+                               holiday(holidays))
+    oc_prophet_model6 <-
+      fable.prophet::prophet(log(n) ~ season("year", type = "multiplicative") +
+                               holiday(holidays))
+    oc_prophet_model7 <-
+      fable.prophet::prophet(log(n) ~ holiday(holidays))
+    oc_prophet_model8 <-
+      fable.prophet::prophet(log(n))
+
+    data %>%
+      mutate(datename = yearmonth(datename)) %>%
+      model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
+            oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
+            oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
+  }
+
+  holidays <-
+    bind_rows(tibble(holiday = "christmas",
+                     ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
+                                    "2019-12-25", "2020-12-25", "2021-12-25")),
+                     lower_window = -1,
+                     upper_window = 1),
+
+              tibble(holiday = "easter", # Sunday
+                     ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
+                                    "2019-04-21", "2020-04-12", "2021-04-04")),
+                     lower_window = -2,
+                     upper_window = 1))
+
+  fableCV <- function(data){ # Return CV model accuracy for fableModels()
+    data_test <-
+      data %>%
+      mutate(datename = yearmonth(datename))
+
+    data_tr <-
+      data %>%
+      select(regional_unit, datename, n) %>%
+      mutate(datename = yearmonth(datename)) %>%
+      fill_gaps() %>%
+      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
+      stretch_tsibble(.init = init, .step = step)
+
+    data_tr %>%
+      fableModels() %>%
+      forecast(h = cv_dist) %>%
+      accuracy(data_test)
+
+  }
+
+  prophetCV <- function(data){# Return CV model accuracy for prophetModels()
+    data_test <-
+      data %>%
+      mutate(datename = yearmonth(datename))
+
+    data_tr <-
+      data %>%
+      select(regional_unit, datename, n) %>%
+      mutate(datename = yearmonth(datename)) %>%
+      fill_gaps() %>%
+      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
+      stretch_tsibble(.init = init, .step = step)
+
+    data_tr %>%
+      prophetModels() %>%
+      forecast(h = cv_dist) %>%
+      accuracy(data_test)
+  }
+
+  # plan(cluster) # Set up parallel processing to decrease computation time
+  plan(multisession) # Set up parallel processing to decrease computation time
+  # Prophet models won't run with plan(multisession) so need to be run
+  # sequentially. Is it worth trying to write this in Python and pass it back
+  # to R?
+
+  # Probably worth trying the prophet::cross_validation() method. If it
+  # returns RMSE and is faster it will be useful.
+  prophet_fits <-
+    future_map_dfr(.x =  regions,
+                   .f = ~prophetCV(data = filter(data, regional_unit == .x)),
+                   .options = furrr_options(seed = TRUE))
+  message("prophetModels() complete")
+
+  # Fable models will run using plan(multisession), but need to be run as below
+  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
+  # generated
+  fable_fits <-
+    future_map_dfr(.x =  regions,
+                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
+                   .options = furrr_options(seed = TRUE))
+  plan(sequential) # Close the multiprocess function to prevent memory leakage
+  message("fableModels() complete")
+
+  bind_rows(fable_fits, prophet_fits) %>%
+    group_by(regional_unit) %>%
+    arrange(RMSE, MAE)
 }
@@
 ```{r, health-board-modelling}
-# system.time(oac_p_hb_cv_models <-
-#   regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
-# 
-# oac_p_hb_cv_models %>%
-#   write_rds("../data/oac_p_hb_cv_models.rds")
+system.time(oac_p_hb_cv_models <-
+  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
+
+oac_p_hb_cv_models %>%
+  write_rds("../data/oac_p_hb_cv_models.rds")
 
@@
 ```{r}
-# system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
-# 
-# oac_p_hb_fcsts %>%
-#   write_rds("../data/oac_p_hb_fcsts.rds")
+system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
+
+oac_p_hb_fcsts %>%
+  write_rds("../data/oac_p_hb_fcsts.rds")
 
@@
 ```{r, gp-cluster-modelling}
-# system.time(oac_p_gp_cluster_cv_models <-
-#   regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
-# 
-# oac_p_gp_cluster_cv_models %>%
-#   write_rds("../data/oac_p_gp_cluster_cv_models.rds")
+system.time(oac_p_gp_cluster_cv_models <-
+  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
+
+oac_p_gp_cluster_cv_models %>%
+  write_rds("../data/oac_p_gp_cluster_cv_models.rds")
 
@@
 ```{r}
-# plan(multisession)
-# system.time(oac_p_gp_cluster_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
-# plan(sequential)
-# 
-# oac_p_gp_cluster_fcsts %>%
-#   write_rds("../data/oac_p_gp_cluster_fcsts.rds")
+plan(multisession)
+system.time(oac_p_gp_cluster_fcsts <- 
+              regionalJointFcsts(oac_p_monthly_quantity_cluster_pre_cv19))
+plan(sequential)
+
+oac_p_gp_cluster_fcsts %>%
+  write_rds("../data/oac_p_gp_cluster_fcsts.rds")
 
@@
 ```{r, gp-practice-modelling}
-regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
-
-  # CV accuracy for fableModels() and prophetModels()
-
-  regions <- unique(data$regional_unit) # Get unique regional_units for map()
-
-  fableModels <- function(data){
-  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
-
-  data %>%
-    mutate(datename = yearmonth(datename)) %>%
-    model(trend_model1 = TSLM(log(n) ~ trend()),#time series linear model
-          trend_model2 = TSLM(log(n) ~ trend() + season("year")),
-          ets1 = ETS(log(n) ~ trend()),
-          ets2 = ETS(log(n) ~ trend() + season("A")),
-          ets3 = ETS(log(n) ~ trend() + season("M")),
-          arima = ARIMA(log(n), stepwise = FALSE, approximation = FALSE),
-          neur_net = NNETAR(log(n)),
-          #fasster = FASSTER(n ~ season("1 year") + trend(1) + fourier(12)),
-          comb1 = combination_model(TSLM(log(n) ~ trend()),
-                                    ETS(log(n) ~ trend())),
-          comb2 = combination_model(TSLM(log(n) ~ trend() + season("year")),
-                                    ETS(log(n) ~ trend() + season("A"))),
-          stl_dcmp1 = decomposition_model(STL(log(n) ~ trend(),
-                                              iterations = 1000,
-                                              robust = TRUE),
-                                          SNAIVE(season_adjust)),
-          stl_dcmp2 = decomposition_model(STL(log(n) ~ trend() + season(),
-                                              iterations = 1000,
-                                              robust = TRUE),
-                                          SNAIVE(season_adjust)),
-          s_naive = SNAIVE(log(n)))# %>%
-    #as_tibble() # map_dfr() doesn't work on tsibble objects
-  }
-
-  prophetModels <- function(data){
-  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
-
-  oc_prophet_model1 <-
-    fable.prophet::prophet(log(n) ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model2 <-
-    fable.prophet::prophet(log(n) ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model3 <-
-    fable.prophet::prophet(log(n) ~ growth("linear") +
-                             season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model4 <-
-    fable.prophet::prophet(log(n) ~ growth("linear") +
-                             season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model5 <-
-    fable.prophet::prophet(log(n) ~ season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model6 <-
-    fable.prophet::prophet(log(n) ~ season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model7 <-
-    fable.prophet::prophet(log(n) ~ holiday(holidays))
-  oc_prophet_model8 <-
-    fable.prophet::prophet(log(n))
-
-  data %>%
-    mutate(datename = yearmonth(datename)) %>%
-    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
-          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
-          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
-}
-
-holidays <-
-  bind_rows(tibble(holiday = "christmas",
-                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
-                                  "2019-12-25", "2020-12-25", "2021-12-25")),
-                   lower_window = -1,
-                   upper_window = 1),
-
-            tibble(holiday = "easter", # Sunday
-                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
-                                  "2019-04-21", "2020-04-12", "2021-04-04")),
-                   lower_window = -2,
-                   upper_window = 1))
-
-  fableCV <- function(data){ # Return CV model accuracy for fableModels()
-    data_test <-
-      data %>%
-      mutate(datename = yearmonth(datename))
-
-    data_tr <-
-      data %>%
-      select(regional_unit, datename, n) %>%
-      mutate(datename = yearmonth(datename)) %>%
-      fill_gaps() %>%
-      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
-      stretch_tsibble(.init = init, .step = step)
-
-    data_tr %>%
-      fableModels() %>%
-      forecast(h = cv_dist) %>%
-      accuracy(data_test)
-
-  }
-
-  prophetCV <- function(data){# Return CV model accuracy for prophetModels()
-    data_test <-
-      data %>%
-      mutate(datename = yearmonth(datename))
-
-    data_tr <-
-      data %>%
-      select(regional_unit, datename, n) %>%
-      mutate(datename = yearmonth(datename)) %>%
-      fill_gaps() %>%
-      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
-      stretch_tsibble(.init = init, .step = step)
-
-    data_tr %>%
-      prophetModels() %>%
-      forecast(h = cv_dist) %>%
-      accuracy(data_test)
-  }
-
-  plan(cluster) # Set up parallel processing to decrease computation time
-  # Prophet models won't run with plan(multisession) so need to be run
-  # sequentially. Is it worth trying to write this in Python and pass it back
-  # to R?
-
-    # Probably worth trying the prophet::cross_validation() method. If it
-    # returns RMSE and is faster it will be useful.
-  prophet_fits <-
-    future_map_dfr(.x =  regions,
-            .f = ~prophetCV(data = filter(data, regional_unit == .x)),
-            .options = furrr_options(seed = TRUE))
-  message("prophetModels() complete")
-
-  # Fable models will run using plan(multisession), but need to be run as below
-  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
-  # generated
-  fable_fits <-
-    future_map_dfr(.x =  regions,
-                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
-                   .options = furrr_options(seed = TRUE))
-  plan(sequential) # Close the multiprocess function to prevent memory leakage
-  message("fableModels() complete")
-
-  bind_rows(fable_fits, prophet_fits) %>%
-    group_by(regional_unit) %>%
-    arrange(RMSE, MAE)
-}
-
-incomplete_gp <- oac_p_monthly_quantity_gp_pre_cv19 %>% 
+incomplete_gp <- # Need to remove GP Practices with incomplete data
+  oac_p_monthly_quantity_gp_pre_cv19 %>% 
     as_tibble() %>% 
@@
 
-system.time(oac_p_gp_cv_models <-
+complete_oac_p_monthly_quantity_gp_pre_cv19 <- 
   oac_p_monthly_quantity_gp_pre_cv19 %>% 
-    filter(!regional_unit %in% incomplete_gp) %>%
+  filter(!regional_unit %in% incomplete_gp)
+
+# Splitting practices into separate analyses to ease computational burden
+seg_1 <- 
+  complete_oac_p_monthly_quantity_gp_pre_cv19$regional_unit %>% 
+           unique() %>% 
+           .[1:101] %>% 
+  as.character()
+seg_2 <- 
+  complete_oac_p_monthly_quantity_gp_pre_cv19$regional_unit %>% 
+           unique() %>% 
+           .[102:202] %>% 
+  as.character()
+seg_3 <- 
+  complete_oac_p_monthly_quantity_gp_pre_cv19$regional_unit %>% 
+           unique() %>% 
+           .[203:303] %>% 
+  as.character()
+seg_4 <- 
+  complete_oac_p_monthly_quantity_gp_pre_cv19$regional_unit %>% 
+           unique() %>% 
+           .[304:404] %>% 
+  as.character()
+
+complete_oac_p_monthly_quantity_gp_pre_cv19_1 <- 
+  complete_oac_p_monthly_quantity_gp_pre_cv19 %>% 
+  filter(regional_unit %in% seg_1)
+complete_oac_p_monthly_quantity_gp_pre_cv19_2 <- 
+  complete_oac_p_monthly_quantity_gp_pre_cv19 %>% 
+  filter(regional_unit %in% seg_2)
+complete_oac_p_monthly_quantity_gp_pre_cv19_3 <- 
+  complete_oac_p_monthly_quantity_gp_pre_cv19 %>% 
+  filter(regional_unit %in% seg_3)
+complete_oac_p_monthly_quantity_gp_pre_cv19_4 <- 
+  complete_oac_p_monthly_quantity_gp_pre_cv19 %>% 
+  filter(regional_unit %in% seg_4)
+
+# Running regionalCV() on each of the quarter of the data
+system.time(oac_p_gp_cv_models_1 <-
+  complete_oac_p_monthly_quantity_gp_pre_cv19_1 %>%
               regionalCV())
+system.time(oac_p_gp_cv_models_2 <-
+  complete_oac_p_monthly_quantity_gp_pre_cv19_2 %>%
+              regionalCV())
+system.time(oac_p_gp_cv_models_3 <-
+  complete_oac_p_monthly_quantity_gp_pre_cv19_3 %>%
+              regionalCV())
+system.time(oac_p_gp_cv_models_4 <-
+  complete_oac_p_monthly_quantity_gp_pre_cv19_4 %>%
+              regionalCV())
+
+# Joining the separated results
+oac_p_gp_cv_models <- 
+  rbind(oac_p_gp_cv_models_1,
+        oac_p_gp_cv_models_2,
+        oac_p_gp_cv_models_3,
+        oac_p_gp_cv_models_4)
 
@@
   theme(axis.text.x = element_text(angle = 90))
-
 ```

### 2021-01-10 r_notebooks/exploring_oral_contraceptives.Rmd
Added LPA analysis

@@
 
+* 2941.64 seconds 2021-01-08
+
 ## Discrepancies
@@
 ```{r}
+library(tidyLPA)
+
+gp_lpa_fit <- 
+  best_model_gp %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(oc_gp_fcsts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(oc_monthly_quantity_gp, 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = n - .mean,
+         z_discrepancy = discrepancy/sd)  %>%
+    select(discrepancy, regional_unit, datename) %>%
+  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
+  ungroup() %>% 
+  select(-regional_unit) %>% 
+  estimate_profiles(1:8, models = c(1:3, 6)
+                    #variances = c("equal", "varying"),
+                    #covariances = c("zero", "varying")
+                    )
+
+gp_lpa_fit %>% 
+  compare_solutions(statistics = c("AIC", "BIC"))
+
+gp_lpa_fit %>% 
+  compare_solutions(statistics = c("AIC", "BIC")) %>% 
+  .[[1]] %>% 
+  ggplot(aes(x = Classes, y = BIC, group = Model, colour = as.factor(Model))) +
+  geom_line()
+
+gp_lpa_fit %>%
+  plot_profiles(x = ., rawdata = FALSE)
+```
+
+```{r}
 best_model_gp %>% 
@@
 
-```{r}
+```{r, eval=FALSE}
 source("../r_scripts/functions/mplus_plotting.R")
-mplus.view.plots("../mplus_analyses/oc_gp/oac_discrep_3_class_bayes.gh5")
-mplus.plot.estimated_means("../mplus_analyses/oc_gp/oac_discrep_3_class_bayes.gh5")
+mplus.view.plots("../mplus_analyses/oc_gp/oc_discrep_2_class_ml.gh5")
+mplus.plot.estimated_means("../mplus_analyses/oc_gp/oc_discrep_2_class_ml.gh5")
+mplus_models <- MplusAutomation::readModels("../mplus_analyses/oc_gp")
+
+mplus_models$oc_discrep_1_class_bayes.out$summaries$BIC
+
+mplus_model_summaries <- 
+  MplusAutomation::readModels("../mplus_analyses/oc_gp", what = "summaries", quiet = TRUE)
+
+mplus_model_summaries$oc_discrep_1_class_bayes.out$summaries %>% 
+  squash() %>% 
+  as_tibble()
+
+length(mplus_model_summaries)
+map_dfr(.x = 1:length(mplus_model_summaries), 
+        .f = ~mplus_model_summaries[[.x]]$summaries$BIC)
 ```

### 2021-01-12 r_notebooks/exploring_oral_contraceptives.Rmd
Saving smaller .rdsfiles, LPA & k-means analysis

--- 2020-12-16 r_notebooks/exploring_oral_contraceptives.Rmd
@@
 ## Packages
-# devtools::install_github("https://github.com/w-hardy/serCymruTools")
+devtools::install_github("https://github.com/w-hardy/serCymruTools")
 library(tidyverse)
@@
 library(furrr)
+library(rebus)
+library(MplusAutomation)
+library(tidyLPA)
 library(serCymruTools)
@@
 # oc %>%
-#   write_rds("../data/oral_contraceptives.rds")
+#   saveRDS("../data/oral_contraceptives.rds")
 
@@
 ```{r, health-board-modelling}
+# plan(multisession)
 # system.time(oc_hb_cv_models <-
 #   regionalCV(data = oc_monthly_quantity_hb_pre_cv19))
+# plan(sequential)
 # 
 # oc_hb_cv_models %>%
-#   write_rds("../data/oc_hb_cv_models.rds")
+#   saveRDS("../data/oc_hb_cv_models.rds")
 
@@
 # oc_hb_fcsts %>%
-#   write_rds("../data/oc_hb_fcsts.rds")
+#   saveRDS("../data/oc_hb_fcsts.rds")
 
@@
 ```{r, gp-cluster-modelling}
+# plan(multisession)
 # system.time(oc_gp_cluster_cv_models <-
 #   regionalCV(data = oc_monthly_quantity_cluster_pre_cv19))
+# plan(sequential)
 # 
 # oc_gp_cluster_cv_models %>%
-#   write_rds("../data/oc_gp_cluster_cv_models.rds")
+#   saveRDS("../data/oc_gp_cluster_cv_models.rds")
 
@@
 # plan(multisession)
-# system.time(oc_gp_cluster_fcsts <- regionalJointFcsts(oc_monthly_quantity_cluster_pre_cv19))
+# system.time(oc_gp_cluster_fcsts <- 
+#               regionalJointFcsts(oc_monthly_quantity_cluster_pre_cv19))
 # plan(sequential)
@@
 # oc_gp_cluster_fcsts %>%
-#   write_rds("../data/oc_gp_cluster_fcsts.rds")
+#   saveRDS("../data/oc_gp_cluster_fcsts.rds")
 
@@
 
+# plan(multisession)
 # system.time(oc_gp_cv_models <-
@@
 #               regionalCV())
+# plan(sequential)
 # 
 # oc_gp_cv_models %>%
-#   write_rds("../data/oc_gp_cv_models.rds")
+#   saveRDS("../data/oc_gp_cv_models.rds")
 
@@
 
-```{r}
+```{r gp-modelling-accuracy}
+best_model_gp <- 
+  oc_gp_cv_models %>% 
+  group_by(regional_unit) %>% 
+  arrange(RMSE, MAE) %>% 
+  slice(1, .preserve = TRUE)
+
+best_model_gp %>% 
+  left_join(select(gp, practiceid, npat, ngp), 
+            by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(.model, .type)) %>% 
+  DataExplorer::plot_correlation()
+
+```
+
+```{r gp-practice-forecasts}
 # plan(multisession)
@@
 # plan(sequential)
+# 
 # oc_gp_fcsts %>%
-#   write_rds("../data/oc_gp_fcsts.rds")
+#   saveRDS("../data/oc_gp_fcsts.rds")
 
@@
   read_rds("../data/oc_gp_fcsts.rds")
+
+oc_gp_fcsts %>% 
+  group_by(.model) %>% 
+  count
+
 ```
+
+* 2941.64 seconds 2021-01-08
 
@@
 
-```{r}
-library(tidyLPA)
+```{r, eval = FALSE}
 best_model_gp_cluster %>% 
@@
   select(-regional_unit) %>% 
-  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
-    estimate_profiles(1:5,
-                      variances = c("equal", "varying"),
-                      covariances = c("zero", "varying")
-                      ) %>% 
+  estimate_profiles(1:6, models = c(1:3, 6)) %>% 
   compare_solutions(statistics = c("AIC", "BIC"))
@@
 best_model_gp %>% 
+  ggplot(aes(x = MAPE)) + 
+  geom_histogram()
+
+best_model_gp %>% 
+  group_by(if_else(MAPE < 50, TRUE, FALSE)) %>% 
+  count()
+
+median(best_model_gp$MAPE)
+
+acc_filter_value <- 50
+
+best_model_gp_discrep <- 
+  best_model_gp %>% 
+  filter(MAPE <= acc_filter_value) %>% 
   select(.model, regional_unit) %>% 
@@
   mutate(discrepancy = n - .mean,
-         z_discrepancy = discrepancy/sd) %>% 
+         z_discrepancy = discrepancy/sd)
+
+best_model_gp_discrep %>% 
   ggplot(aes(y = discrepancy)) +
-  # geom_boxplot(aes(x = as.factor(datename))) +
-  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
+  geom_line(aes(x = datename, y = discrepancy, 
+                colour = as.factor(regional_unit)),
             alpha = .8, lty = 2) +
@@
   theme(legend.position = "none")
+
 ```
+
+```{r}
+best_model_gp_discrep %>% 
+  filter(discrepancy < -40)
+
+oc_monthly_quantity_gp %>% 
+  filter(regional_unit %in% c("W97009", "W98053")) %>% 
+  as_tsibble(key = regional_unit, index = datename) %>% 
+  autoplot()
+
+gp %>% 
+  filter(practiceid %in% c("W97009", "W98053"))
+```
+
+* Based on postcodes, these are both University GPs. Or at least, given their procimity to universities, they will likely have large student populations.
+
+#### Latent profile analysis
+
+```{r gp-lpa}
+gp_lpa_fit <- 
+  best_model_gp_discrep  %>%
+  select(discrepancy, regional_unit, datename) %>%
+  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
+  ungroup() %>% 
+  select(-regional_unit) %>% 
+  estimate_profiles(1:6, models = c(1:3, 6))
+
+gp_lpa_fit %>% 
+  compare_solutions(statistics = c("AIC", "BIC"))
+
+gp_lpa_fit %>% 
+  compare_solutions(statistics = c("AIC", "BIC")) %>% 
+  .[[1]] %>% 
+  ggplot(aes(x = Classes, y = BIC, group = Model, colour = as.factor(Model))) +
+  geom_line()
+
+gp_lpa_fit %>%
+  plot_profiles(x = ., rawdata = FALSE)
+
+```
+
+#### mplus
+
+```{r, mplus-data-prep}
+best_model_gp_discrep %>% 
+  mutate(regional_unit = as.factor(regional_unit)) %>% 
+  select(regional_unit, datename, discrepancy) %>% 
+  filter(!is.na(discrepancy)) %>% # need to remove NA before pivoting to enable values_fill
+  pivot_wider(names_from = datename, values_from = discrepancy, values_fill = -999) %>% 
+  left_join(select(gp, c(practiceid, cluster)), by = c("regional_unit" = "practiceid")) %>% 
+  mutate(regional_unit = as.factor(regional_unit),
+         cluster = as.factor(cluster)) %>% 
+  mutate(regional_unit = as.numeric(regional_unit),
+         cluster = as.numeric(cluster)) %>% 
+  select(cluster, regional_unit, everything()) %>% 
+  write_csv(file = "../data/mplus/oc_gp_discrep.csv", col_names = FALSE)
+
+```
+
+```{r, mplus-anlayses}
+source("../r_scripts/functions/mplus_plotting.R")
+# mplus_models <- MplusAutomation::readModels("../mplus_analyses/oc_gp")
+
+mplus_model_summaries <- 
+  readModels("../mplus_analyses/oc_gp", what = "summaries", quiet = TRUE)
+
+best_mplus_model_summary <- 
+  mplus_model_summaries %>% 
+  flatten() %>% 
+  map(2) %>% 
+  bind_rows() %>% 
+  filter(Estimator == "MLR" & AnalysisType == "mixture") %>% 
+  arrange(BIC) %>% 
+  slice(1)
+
+best_mplus_model <- 
+  readModels(paste0("../mplus_analyses/oc_gp/", best_mplus_model_summary$Filename))
+
+oc_discrep_5_class_ml <- 
+  readModels("../mplus_analyses/oc_gp/oc_discrep_5_class_ml.out")
+
+best_mplus_model$class_counts
+
+# mplus.view.plots("../mplus_analyses/oc_gp/oc_discrep_5_class_ml.gh5")
+mplus.plot.estimated_means("../mplus_analyses/oc_gp/oc_discrep_5_class_ml.gh5")
+```
+#### kmeans
+
+```{r, gp-kmeans}
+gp_kmeans_data <- 
+  best_model_gp_discrep %>%  
+  mutate(regional_unit = as.factor(regional_unit)) %>% 
+  select(regional_unit, datename, discrepancy) %>% 
+  filter(!is.na(discrepancy)) %>% # need to remove NA before pivoting to enable values_fill
+  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
+  as_tibble() %>% 
+  na.omit()
+
+1:6 %>% 
+  map_dfr(~as.data.frame(kmeans(x = gp_kmeans_data[2:6], centers = .x, nstart = 25)$cluster), 
+          .id = "n_clusters") %>% 
+  mutate(regional_unit = rep(gp_kmeans_data$regional_unit, 6)) %>% 
+  pivot_wider(names_from = "n_clusters", id_cols = regional_unit,
+              values_from = "kmeans(x = gp_kmeans_data[2:6], centers = .x, nstart = 25)$cluster")
+
+1:6 %>% 
+  map_dfr(~as.data.frame(kmeans(x = gp_kmeans_data[2:6],
+                                centers = .x, nstart = 25)$centers), 
+          .id = "n_clusters") %>% 
+  rownames_to_column(var = "cluster") %>% 
+  mutate(cluster = 
+           str_remove_all(cluster, 
+                          pattern = DOT %R% DOT %R% DOT %R% 
+                            one_or_more(DIGIT))) %>% 
+  pivot_longer(cols = starts_with("2020 "), names_to = "datename") %>% 
+  ggplot(aes(x = yearmonth(datename), y = value, colour = as.factor(cluster))) + 
+  geom_line() +
+  facet_wrap(~n_clusters)
+
+```
+#### Comparing methods
+
+```{r}
+mplus_assignment <- 
+  read_table("../mplus_analyses/oc_gp/oc_discrep_5_class_ml_cprob.txt", col_names = FALSE, na = "*") %>% 
+  na.omit() %>% 
+  .$X17
+
+kmeans_assignment <- 
+  kmeans(x = gp_kmeans_data[2:6], centers = 5, nstart = 25)$cluster
+
+lpa_assignment <- 
+  gp_lpa_fit$model_1_class_5$model$classification
+
+df <- bind_cols(mplus_assignment, kmeans_assignment, lpa_assignment)
+
+df %>% 
+  ggplot(aes(x = mplus_assignment, y = kmeans_assignment, 
+             colour = as.factor(mplus_assignment)))+
+  geom_jitter(aes(shape = as.factor(kmeans_assignment)), alpha = .5)
+
+df %>% 
+  ggplot(aes(x = mplus_assignment, y = lpa_assignment, 
+             colour = as.factor(kmeans_assignment))) +
+  geom_jitter(alpha = .5)
+```

### 2021-01-12 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
Removed neur_net, typos

@@
 # Modifying functions to model log(n) as using proportion data
-regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
-
-  # CV accuracy for fableModels() and prophetModels()
-
-  regions <- unique(data$regional_unit) # Get unique regional_units for map()
-
 fableModels <- function(data){
@@
           arima = ARIMA(log(n), stepwise = FALSE, approximation = FALSE),
-            neur_net = NNETAR(log(n)),
           comb1 = combination_model(TSLM(log(n) ~ trend()),
@@
                    upper_window = 1))
+regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
+
+  # CV accuracy for fableModels() and prophetModels()
+
+  regions <- unique(data$regional_unit) # Get unique regional_units for map()
 
@@
       accuracy(data_test)
-
   }
@@
 
+regionalJointFcsts <- function(data, h ="5 months"){
+  regions <- unique(data$regional_unit)
+  plan(multisession)
+  fable_fit <-
+    future_map_dfr(.x = regions,
+                   .f = ~fableModels(filter(data, regional_unit ==.x)),
+                   .options = furrr_options(seed = TRUE))
+  message("fable fits complete")
+
+  fable_fcst <- fable_fit %>%
+    forecast(h = h) %>%
+    as_tibble()
+  message("fable forecasts complete")
+
+  prophet_fit <-
+    future_map_dfr(.x = regions,
+                   .f = ~prophetModels(filter(data, regional_unit ==.x)),
+                   .options = furrr_options(seed = TRUE))
+  message("prophet fits complete")
+
+  prophet_fcst <-
+    forecast(prophet_fit, h = h) %>%
+    as_tibble()
+  # Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
+  # This may also be influencing accuracy
+
+  message("prophet forecasts complete")
+  plan(sequential)
+  # prophetModels now being run in parallel. Needed to reinstall prophet from
+  # source
+
+  # joint_fit <-
+  #   left_join(fable_fit, prophet_fit, by = "regional_unit")
+  joint_fcst <-
+    bind_rows(fable_fcst, prophet_fcst) %>%
+    mutate(lb_95 = quantile(n, .025),
+           lb_80 = quantile(n, .1),
+           med = median(n),
+           ub_80 = quantile(n, .9),
+           ub_95 = quantile(n, .975),
+           sd = distributional::variance(n)^2,
+           dist = n,
+           n = NULL)
+
+  return(joint_fcst)
+}
+
 ```
@@
 # db.gpextract <- tbl(con, "gpextract")
-# oac_p <- db.gpextract %>%
+# oac <- db.gpextract %>%
 #   filter(bnfchem %in% oral_anticoagulants) %>%
@@
 # ## Write to local file
-# oac_p %>%
+# oac %>%
 #   write_rds("../data/oral_anticoagulants.rds")
@@
 
-oac_p <- read_rds("../data/oral_anticoagulants.rds")
+oac <- read_rds("../data/oral_anticoagulants.rds")
 
@@
 oac_p_monthly_count <- 
-  oac_p %>% 
+  oac %>% 
   group_by(datename, bnfchem) %>% 
@@
 oac_p_monthly_quantity_hb <- 
-  right_join(oac_p, select(gp, c(practiceid, hboard)), 
+  right_join(oac, select(gp, c(practiceid, hboard)), 
              by = c("PracticeID" = "practiceid")) %>%
@@
 oac_p_monthly_quantity_cluster <- 
-  right_join(oac_p, select(gp, c(practiceid, cluster)), 
+  right_join(oac, select(gp, c(practiceid, cluster)), 
              by = c("PracticeID" = "practiceid")) %>%
@@
 oac_p_monthly_quantity_gp <- 
-  propRegional(oac_p, PracticeID, datename, Quantity, bnf = warf)
+  propRegional(oac, PracticeID, datename, Quantity, bnf = warf)
 
@@
 ```{r oac_p-monthly-ts-plot, fig.cap="Total quantity of combined oral anticoagulants prescribed per month."}
-oac_p %>% 
+oac %>% 
   group_by(datename) %>% 
@@
 
-```{r oac-p-monthly-ts-plot, fig.cap="Total quantity of combined oral anticoagulants prescribed per month."}
+```{r oac-p-monthly-ts-plot, fig.cap="Warfarin prescribing as a percentage of all oral anticoagulants prescribed per month."}
 oac_p_monthly_count %>% 
@@
 ```{r oac_p-monthly-seasonality-plot}
-df <- oac_p_monthly_count_pre_cv19 %>% 
+df <- 
+  oac_p_monthly_count_pre_cv19 %>% 
   mutate(month = as.factor(month(datename, label = TRUE, abbr = TRUE)),
@@
 * 724.044 seconds with multisession prophetModels()
+* 418.410 seconds with neur_net removed 2021-01-11
 
 ```{r}
+plan(multisession)
 system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
-
+plan(sequential)
 oac_p_hb_fcsts %>%
@@
 * 194.071 seconds 2020-12-10
+* 71.559 seconds 2021-01-11
 
@@
 * 5514.279 seconds
+* 2059.159 seconds 2021-01-11
 
@@
 * 1266.126 seconds 2020-12-10
+* 590.595 seconds 2021-01-11
 

### 2021-01-12 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
Running analyses

@@
 
-  # plan(cluster) # Set up parallel processing to decrease computation time
-  plan(multisession) # Set up parallel processing to decrease computation time
+  plan(cluster, 8) # Set up parallel processing to decrease computation time
+  #plan(multisession) # Set up parallel processing to decrease computation time
   # Prophet models won't run with plan(multisession) so need to be run
@@
   regions <- unique(data$regional_unit)
-  plan(multisession)
+  plan(cluster)
   fable_fit <-
@@
 ```{r}
-plan(multisession)
+plan(cluster)
 system.time(oac_p_hb_fcsts <- regionalJointFcsts(oac_p_monthly_quantity_hb_pre_cv19))
@@
 ```{r}
-plan(multisession)
+plan(cluster)
 system.time(oac_p_gp_cluster_fcsts <- 

### 2021-01-12 r_notebooks/exploring_hydroxychloroquine_sulphate.nb.Rmd

---
title: "Oral contraceptives"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

```{r}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL) %>% 
  filter(year == 2020) # do something better

hcq <- read_rds("../data/presdata_updates_040121/presc_wales_HCQ.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename)))

## Sort into monthly count data
hcq_monthly_count <- hcq %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

hcq_monthly_quantity_hb <- 
  right_join(hcq, select(gp, c(practiceid, hboard)), 
             by = c("practiceid")) %>%
  countRegional(hboard, datename, Quantity) %>% 
  left_join(gp %>% 
              select(c(practiceid, npat, hboard)) %>% 
              group_by(hboard) %>% 
              summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

hcq_monthly_quantity_cluster <- 
  right_join(hcq, select(gp, c(practiceid, cluster)), 
             by = c("practiceid")) %>%
  countRegional(cluster, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, cluster)) %>% 
  group_by(cluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

hcq_monthly_quantity_gp <- 
  countRegional(hcq, practiceid, datename, Quantity) %>% 
  right_join(select(gp, c(practiceid, npat)), 
            by = c("regional_unit" = "practiceid")) %>% 
  mutate(n = 1000*n/npat)

## Sort into monthly count data pre-lockdown (2020-03-23)
hcq_monthly_count_pre_cv19 <- 
  hcq_monthly_count %>% 
  filter(datename < dmy("01-03-2020"))

hcq_monthly_quantity_hb_pre_cv19 <- 
  hcq_monthly_quantity_hb %>% 
    filter(datename < dmy("01-03-2020"))

hcq_monthly_quantity_cluster_pre_cv19 <- 
  hcq_monthly_quantity_cluster %>% 
    filter(datename < dmy("01-03-2020"))

hcq_monthly_quantity_gp_pre_cv19 <- 
  hcq_monthly_quantity_gp %>% 
    filter(datename < dmy("01-03-2020"))

```

## Overview

### 2016-2020 plot of all hcq prescriptions

```{r hcq-monthly-ts-plot, fig.cap="Total quantity of combined hormonal and progestogen only oral contraceptives prescribed per month."}
hcq %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  tsibble() %>% 
  autoplot(n) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

* General negative trend
* Seasonality unclear
  * Holiday effect? Drop in prescribing in Dec 2016-2019 followed by peak in Jan for 2017-2020.

### Seasonality

```{r hcq-monthly-seasonality-plot}
df <- hcq_monthly_count_pre_cv19 %>% 
  mutate(month = as.factor(month(datename, label = TRUE, abbr = TRUE)),
         year = as.factor(year(datename)))

df2 <- df %>% 
  as_tibble() %>% 
  filter(year(datename) != 2020) %>% 
  group_by(month) %>% 
  summarise(n = mean(n))

df %>% 
  ggplot(aes(x = month, y = n, colour = year, group = year)) +
  geom_line() +
  geom_line(data = df2, aes(x = month, y = n, group = "Avg"), 
            colour = "red", lty = 2) +
  labs(caption = "Red dashed line is mean for 2016-2019")

```
*

```{r}
hcq_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  gg_subseries(y = n, period = "year")
```

*

### Lag plots

```{r}
hcq_monthly_count_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>% 
  gg_lag(y = n, geom = "point", lags = 1:12)
```

```{r}
hcq_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  gg_lag(y = n, geom = "point", lags = 13:24)
```
*

### Autocorrelation

```{r}
tseries::adf.test(hcq_monthly_count$n)
urca::ur.df(hcq_monthly_count$n)
```

```{r}
hcq_monthly_count_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>% 
  ACF(n, lag_max = 60) %>% autoplot()
```

* Autocorrelation greatest at 2 and 12

```{r}
hcq_monthly_count_pre_cv19$n %>%
  pacf(lag.max = 60)
```

## Overview of each drug

```{r}
hcq %>% 
  group_by(datename, chemname) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
                       str_detect(datename, pattern = "-02-") ~ n/28.25,
                       str_detect(datename, pattern = "-03-") ~ n/31,
                       str_detect(datename, pattern = "-04-") ~ n/30,
                       str_detect(datename, pattern = "-05-") ~ n/31,
                       str_detect(datename, pattern = "-06-") ~ n/30,
                       str_detect(datename, pattern = "-07-") ~ n/31,
                       str_detect(datename, pattern = "-08-") ~ n/31,
                       str_detect(datename, pattern = "-09-") ~ n/30,
                       str_detect(datename, pattern = "-10-") ~ n/31,
                       str_detect(datename, pattern = "-11-") ~ n/30,
                       str_detect(datename, pattern = "-12-") ~ n/31))%>% 
  as_tsibble(index = datename, key = chemname) %>% 
  autoplot(n) +
  theme(legend.position = "none") +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

## Time series components

```{r}
dcmp <- 
  hcq_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(STL(n))

hcq_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  autoplot(n, color = "grey") + 
  autolayer(components(dcmp), trend, color = "red")

components(dcmp) %>% 
  autoplot()
```

```{r}
hcq_monthly_count %>% 
  mutate(datename = yearmonth(datename)) %>% 
  autoplot(n, color = "grey") + 
  autolayer(components(dcmp), season_adjust, colour = "blue") +
  labs(title = "Seasonally adjusted")
```

## Modelling

### By Health Board

```{r, health-board-modelling}
plan(multisession)
system.time(hcq_hb_cv_models <-
  regionalCV(data = hcq_monthly_quantity_hb_pre_cv19))
plan(sequential)

hcq_hb_cv_models %>%
  saveRDS("../data/hcq_hb_cv_models.rds")

hcq_hb_cv_models <- 
  read_rds("../data/hcq_hb_cv_models.rds")

hcq_hb_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

hcq_hb_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

hcq_hb_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))
```

* 756.556 seconds 2021-01-12

```{r}
plan(cluster)
system.time(hcq_hb_fcsts <- regionalJointFcsts(hcq_monthly_quantity_hb_pre_cv19))
plan(sequential)

hcq_hb_fcsts %>%
  saveRDS("../data/hcq_hb_fcsts.rds")

hcq_hb_fcsts <- 
  read_rds("../data/hcq_hb_fcsts.rds")
```

* 56.193 seconds 2021-01-12 multisession
* 52.902 seconds 2021-01-12 cluster
* 147.024 seconds 2021-01-12 sequential

### By GP Cluster

```{r, gp-cluster-modelling}
# plan(multisession)
# system.time(hcq_gp_cluster_cv_models <-
#   regionalCV(data = hcq_monthly_quantity_cluster_pre_cv19))
# plan(sequential)
# 
# hcq_gp_cluster_cv_models %>%
#   saveRDS("../data/hcq_gp_cluster_cv_models.rds")

hcq_gp_cluster_cv_models <- 
  read_rds("../data/hcq_gp_cluster_cv_models.rds")

hcq_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

hcq_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

hcq_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

```

*

```{r}
# plan(multisession)
# system.time(hcq_gp_cluster_fcsts <- 
#               regionalJointFcsts(hcq_monthly_quantity_cluster_pre_cv19))
# plan(sequential)
# 
# hcq_gp_cluster_fcsts %>%
#   saveRDS("../data/hcq_gp_cluster_fcsts.rds")

hcq_gp_cluster_fcsts <- 
  read_rds("../data/hcq_gp_cluster_fcsts.rds")
```

*

### By Practice

```{r, gp-practice-modelling}
incomplete_gp <- hcq_monthly_quantity_gp_pre_cv19 %>% 
    as_tibble() %>% 
    group_by(regional_unit) %>% 
    count() %>% 
    filter(n < 50) %>% 
    .$regional_unit %>% 
    unique()

plan(cluster)
system.time(hcq_gp_cv_models <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
    filter(!regional_unit %in% incomplete_gp) %>%
              regionalCV())
plan(sequential)

hcq_gp_cv_models %>%
  saveRDS("../data/hcq_gp_cv_models.rds")

hcq_gp_cv_models <- 
  read_rds("../data/hcq_gp_cv_models.rds")

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

```

*

```{r gp-modelling-accuracy}
best_model_gp <- 
  hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model_gp %>% 
  left_join(select(gp, practiceid, npat, ngp), 
            by = c("regional_unit" = "practiceid")) %>% 
  select(-c(.model, .type)) %>% 
  DataExplorer::plot_correlation()

```

```{r gp-practice-forecasts}
plan(cluster)
system.time(hcq_gp_fcsts <-
              hcq_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts())
plan(sequential)

hcq_gp_fcsts %>%
  saveRDS("../data/hcq_gp_fcsts.rds")

hcq_gp_fcsts <- 
  read_rds("../data/hcq_gp_fcsts.rds")

hcq_gp_fcsts %>% 
  group_by(.model) %>% 
  count

```

*

## Discrepancies

### By Health Board

```{r, health-board-discrepancies}
best_model_hb <- 
  hcq_hb_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model_hb %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(hcq_hb_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(hcq_monthly_quantity_hb, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

### By GP Cluster

```{r, gp-cluster-discrepancies}
best_model_gp_cluster <- 
  hcq_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(hcq_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(hcq_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  # scale_color_gradientn(colours = rainbow(100))+
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

```{r, eval = FALSE}
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(hcq_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(hcq_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
  select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  estimate_profiles(1:6, models = c(1:3, 6)) %>% 
  compare_solutions(statistics = c("AIC", "BIC"))
```

### By GP Practice

```{r, gp-practice-discrepancies}
best_model_gp <- 
  hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp %>% 
  group_by(if_else(MAPE < 50, TRUE, FALSE)) %>% 
  count()

median(best_model_gp$MAPE)

acc_filter_value <- 50

best_model_gp_discrep <- 
  best_model_gp %>% 
  filter(MAPE <= acc_filter_value) %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(hcq_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(hcq_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

```{r}
best_model_gp_discrep %>% 
  filter(discrepancy < -40)

hcq_monthly_quantity_gp %>% 
  filter(regional_unit %in% c("W97009", "W98053")) %>% 
  as_tsibble(key = regional_unit, index = datename) %>% 
  autoplot()

gp %>% 
  filter(practiceid %in% c("W97009", "W98053"))
```

* Based on postcodes, these are both University GPs. Or at least, given their procimity to universities, they will likely have large student populations.

#### Latent profile analysis

```{r gp-lpa}
gp_lpa_fit <- 
  best_model_gp_discrep  %>%
  select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  estimate_profiles(1:6, models = c(1:3, 6))

gp_lpa_fit %>% 
  compare_solutions(statistics = c("AIC", "BIC"))

gp_lpa_fit %>% 
  compare_solutions(statistics = c("AIC", "BIC")) %>% 
  .[[1]] %>% 
  ggplot(aes(x = Classes, y = BIC, group = Model, colour = as.factor(Model))) +
  geom_line()

gp_lpa_fit %>%
  plot_profiles(x = ., rawdata = FALSE)

```

#### mplus

```{r, mplus-data-prep}
best_model_gp_discrep %>% 
  mutate(regional_unit = as.factor(regional_unit)) %>% 
  select(regional_unit, datename, discrepancy) %>% 
  filter(!is.na(discrepancy)) %>% # need to remove NA before pivoting to enable values_fill
  pivot_wider(names_from = datename, values_from = discrepancy, values_fill = -999) %>% 
  left_join(select(gp, c(practiceid, cluster)), by = c("regional_unit" = "practiceid")) %>% 
  mutate(regional_unit = as.factor(regional_unit),
         cluster = as.factor(cluster)) %>% 
  mutate(regional_unit = as.numeric(regional_unit),
         cluster = as.numeric(cluster)) %>% 
  select(cluster, regional_unit, everything()) %>% 
  write_csv(file = "../data/mplus/hcq_gp_discrep.csv", col_names = FALSE)

```

```{r, mplus-anlayses}
source("../r_scripts/functions/mplus_plotting.R")
# mplus_models <- MplusAutomation::readModels("../mplus_analyses/hcq_gp")

mplus_model_summaries <- 
  readModels("../mplus_analyses/hcq_gp", what = "summaries", quiet = TRUE)

best_mplus_model_summary <- 
  mplus_model_summaries %>% 
  flatten() %>% 
  map(2) %>% 
  bind_rows() %>% 
  filter(Estimator == "MLR" & AnalysisType == "mixture") %>% 
  arrange(BIC) %>% 
  slice(1)

best_mplus_model <- 
  readModels(paste0("../mplus_analyses/hcq_gp/", best_mplus_model_summary$Filename))

hcq_discrep_5_class_ml <- 
  readModels("../mplus_analyses/hcq_gp/hcq_discrep_5_class_ml.out")

best_mplus_model$class_counts

# mplus.view.plots("../mplus_analyses/hcq_gp/hcq_discrep_5_class_ml.gh5")
mplus.plot.estimated_means("../mplus_analyses/hcq_gp/hcq_discrep_5_class_ml.gh5")
```
#### kmeans

```{r, gp-kmeans}
gp_kmeans_data <- 
  best_model_gp_discrep %>%  
  mutate(regional_unit = as.factor(regional_unit)) %>% 
  select(regional_unit, datename, discrepancy) %>% 
  filter(!is.na(discrepancy)) %>% # need to remove NA before pivoting to enable values_fill
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  as_tibble() %>% 
  na.omit()

1:6 %>% 
  map_dfr(~as.data.frame(kmeans(x = gp_kmeans_data[2:6], centers = .x, nstart = 25)$cluster), 
          .id = "n_clusters") %>% 
  mutate(regional_unit = rep(gp_kmeans_data$regional_unit, 6)) %>% 
  pivot_wider(names_from = "n_clusters", id_cols = regional_unit,
              values_from = "kmeans(x = gp_kmeans_data[2:6], centers = .x, nstart = 25)$cluster")

1:6 %>% 
  map_dfr(~as.data.frame(kmeans(x = gp_kmeans_data[2:6],
                                centers = .x, nstart = 25)$centers), 
          .id = "n_clusters") %>% 
  rownames_to_column(var = "cluster") %>% 
  mutate(cluster = 
           str_remove_all(cluster, 
                          pattern = DOT %R% DOT %R% DOT %R% 
                            one_or_more(DIGIT))) %>% 
  pivot_longer(cols = starts_with("2020 "), names_to = "datename") %>% 
  ggplot(aes(x = yearmonth(datename), y = value, colour = as.factor(cluster))) + 
  geom_line() +
  facet_wrap(~n_clusters)

```
#### Comparing methods

```{r}
mplus_assignment <- 
  read_table("../mplus_analyses/hcq_gp/hcq_discrep_5_class_ml_cprob.txt", col_names = FALSE, na = "*") %>% 
  na.omit() %>% 
  .$X17

kmeans_assignment <- 
  kmeans(x = gp_kmeans_data[2:6], centers = 5, nstart = 25)$cluster

lpa_assignment <- 
  gp_lpa_fit$model_1_class_5$model$classification

df <- bind_cols(mplus_assignment, kmeans_assignment, lpa_assignment)

df %>% 
  ggplot(aes(x = mplus_assignment, y = kmeans_assignment, 
             colour = as.factor(mplus_assignment)))+
  geom_jitter(aes(shape = as.factor(kmeans_assignment)), alpha = .5)

df %>% 
  ggplot(aes(x = mplus_assignment, y = lpa_assignment, 
             colour = as.factor(kmeans_assignment))) +
  geom_jitter(alpha = .5)

```

### 2021-01-15 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
r analyses

@@
 library(furrr)
+library(progressr)
+library(beepr)
 library(serCymruTools)
@@
 
+handlers(global = TRUE)
+handlers(
+  list(
+    handler_progress(
+      format = ":spin :current/:total (:message) [:bar] :percent in :elapsed ETA: :eta",
+      width = 60,
+      complete = "+"),
+    handler_beepr(finish   = "wilhelm",
+                  interval = 2.0)
+  )
+)
+
 ## Seed
@@
 ## Function
+# Transforming data to be bound beweent a lower and upper limit http://www.maths.bristol.ac.uk/R/web/packages/fable/vignettes/transformations.html
+scaled_logit <- function(x, lower=0, upper=1){
+  log((x-lower)/(upper-x))
+}
+inv_scaled_logit <- function(x, lower=0, upper=1){
+  (upper-lower)*exp(x)/(1+exp(x)) + lower
+}
+my_scaled_logit <- fabletools::new_transformation(scaled_logit, inv_scaled_logit)
 
@@
 
-# Modifying functions to model log(n) as using proportion data
+# Modifying functions to model my_scaled_logit(n, 0, 100) as using proportion data
 fableModels <- function(data){
@@
     mutate(datename = yearmonth(datename)) %>%
-    model(trend_model1 = TSLM(log(n) ~ trend()),#time series linear model
-          trend_model2 = TSLM(log(n) ~ trend() + season("year")),
-          ets1 = ETS(log(n) ~ trend()),
-          ets2 = ETS(log(n) ~ trend() + season("A")),
-          ets3 = ETS(log(n) ~ trend() + season("M")),
-          arima = ARIMA(log(n), stepwise = FALSE, approximation = FALSE),
-          comb1 = combination_model(TSLM(log(n) ~ trend()),
-                                    ETS(log(n) ~ trend())),
-          comb2 = combination_model(TSLM(log(n) ~ trend() + season("year")),
-                                    ETS(log(n) ~ trend() + season("A"))),
-          stl_dcmp1 = decomposition_model(STL(log(n) ~ trend(),
+    model(trend_model1 = TSLM(my_scaled_logit(n, 0, 100) ~ trend()),#time series linear model
+          trend_model2 = TSLM(my_scaled_logit(n, 0, 100) ~ trend() + season("year")),
+          ets1 = ETS(my_scaled_logit(n, 0, 100) ~ trend()),
+          ets2 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("A")),
+          ets3 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("M"), restrict = FALSE),
+          arima = ARIMA(my_scaled_logit(n, 0, 100), stepwise = FALSE, approximation = FALSE),
+          comb1 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ trend()),
+                                    ETS(my_scaled_logit(n, 0, 100) ~ trend())),
+          comb2 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ trend() + season("year")),
+                                    ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("A"))),
+          stl_dcmp1 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ trend(),
                                               iterations = 1000,
@@
                                           SNAIVE(season_adjust)),
-          stl_dcmp2 = decomposition_model(STL(log(n) ~ trend() + season(),
+          stl_dcmp2 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ trend() + season(),
                                               iterations = 1000,
@@
                                           SNAIVE(season_adjust)),
-          s_naive = SNAIVE(log(n)))
-}
-
-prophetModels <- function(data){
-  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
-
-  oc_prophet_model1 <-
-    fable.prophet::prophet(log(n) ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model2 <-
-    fable.prophet::prophet(log(n) ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model3 <-
-    fable.prophet::prophet(log(n) ~ growth("linear") +
-                             season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model4 <-
-    fable.prophet::prophet(log(n) ~ growth("linear") +
-                             season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model5 <-
-    fable.prophet::prophet(log(n) ~ season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model6 <-
-    fable.prophet::prophet(log(n) ~ season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model7 <-
-    fable.prophet::prophet(log(n) ~ holiday(holidays))
-  oc_prophet_model8 <-
-    fable.prophet::prophet(log(n))
-
-  data %>%
-    mutate(datename = yearmonth(datename)) %>%
-    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
-          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
-          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
+          s_naive = SNAIVE(my_scaled_logit(n, 0, 100)))
 }
@@
                    upper_window = 1))
+
+prophetModels <- function(data){
+  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
+
+  oc_prophet_model1 <-
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ growth("linear", n_changepoints = 0) +
+                             season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model2 <-
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ growth("linear", n_changepoints = 0) +
+                             season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model3 <-
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ growth("linear") +
+                             season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model4 <-
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ growth("linear") +
+                             season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model5 <-
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ season("year", type = "additive") +
+                             holiday(holidays))
+  oc_prophet_model6 <-
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ season("year", type = "multiplicative") +
+                             holiday(holidays))
+  oc_prophet_model7 <-
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ holiday(holidays))
+  oc_prophet_model8 <-
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100))
+
+  data %>%
+    mutate(datename = yearmonth(datename)) %>%
+    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
+          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
+          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
+}
+
 regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
@@
 
+  p <- progressr::progressor(along = regions)
+
   fableCV <- function(data){ # Return CV model accuracy for fableModels()
+    x <- data$regional_unit
+
     data_test <-
@@
       accuracy(data_test)
+
+    p()
   }
@@
   prophetCV <- function(data){# Return CV model accuracy for prophetModels()
+    x <- data$regional_unit
+
     data_test <-
@@
 
-    data_tr <-
+    data_trn <-
       data %>%
@@
 
-    data_tr %>%
+    data_trn %>% 
       prophetModels() %>%
@@
       accuracy(data_test)
+
+    p()
   }
 
-  plan(cluster, 8) # Set up parallel processing to decrease computation time
-  #plan(multisession) # Set up parallel processing to decrease computation time
-  # Prophet models won't run with plan(multisession) so need to be run
-  # sequentially. Is it worth trying to write this in Python and pass it back
-  # to R?
-
-  # Probably worth trying the prophet::cross_validation() method. If it
-  # returns RMSE and is faster it will be useful.
   prophet_fits <-
@@
                    .options = furrr_options(seed = TRUE))
-  plan(sequential) # Close the multiprocess function to prevent memory leakage
   message("fableModels() complete")
@@
   regions <- unique(data$regional_unit)
-  plan(cluster)
+
   fable_fit <-
     future_map_dfr(.x = regions,
-                   .f = ~fableModels(filter(data, regional_unit ==.x)),
-                   .options = furrr_options(seed = TRUE))
-  message("fable fits complete")
+                   .f = ~fableModels(filter(data, regional_unit ==.x)) %>%
+                    forecast(h = h),
+                   .options = furrr_options(seed = TRUE)) %>%
+    as_tibble()
 
-  fable_fcst <- fable_fit %>%
-    forecast(h = h) %>%
-    as_tibble()
   message("fable forecasts complete")
@@
     future_map_dfr(.x = regions,
-                   .f = ~prophetModels(filter(data, regional_unit ==.x)),
-                   .options = furrr_options(seed = TRUE))
-  message("prophet fits complete")
-
-  prophet_fcst <-
-    forecast(prophet_fit, h = h) %>%
+                   .f = ~prophetModels(filter(data, regional_unit ==.x)) %>%
+                    forecast(h = h),
+                   .options = furrr_options(seed = TRUE)) %>%
     as_tibble()
-  # Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
-  # This may also be influencing accuracy
 
   message("prophet forecasts complete")
-  plan(sequential)
-  # prophetModels now being run in parallel. Needed to reinstall prophet from
-  # source
 
@@
 # Running regionalCV() on each of the quarter of the data
+plan(cluster)
 system.time(oac_p_gp_cv_models_1 <-
@@
               regionalCV())
-system.time(oac_p_gp_cv_models_2 <-
+with_progress(system.time(oac_p_gp_cv_models_2 <-
   complete_oac_p_monthly_quantity_gp_pre_cv19_2 %>%
-              regionalCV())
+              regionalCV()))
 system.time(oac_p_gp_cv_models_3 <-
@@
               regionalCV())
+plan(sequential)
 
@@
 oac_p_gp_cv_models %>%
-  write_rds("../data/oac_p_gp_cv_models.rds")
+  saveRDS("../data/oac_p_gp_cv_models.rds")
 
@@
 ```{r}
-# regionalJointFcsts <- function (data, h = "5 months", keep_fits = FALSE) 
-# {
-#   if (!is.logical(keep_fits)) {
-#     stop("`keep_fits` must be of type logical")
-#   }
-#   regions <- unique(data$regional_unit)
-#   
-#   cl <- parallel::makeCluster(8)
-#   plan(cluster, workers = cl)
-#   
-#   fable_fcst <- 
-#     future_map_dfr(.x = regions, 
-#                    .f = ~fableModels(filter(data, 
-#                                             regional_unit == .x)) %>% 
-#                      forecast(h = h) %>% as_tibble(), 
-#                    .options = furrr_options(seed = TRUE))
-#   
-#   
-#   message("fable fits complete, step 1/4")
-#   message("fable forecasts complete, step 2/4")
-# 
-#   prophet_fcst <- 
-#     future_map_dfr(.x = regions, 
-#                    .f = ~prophetModels(filter(data, 
-#                                             regional_unit == .x)) %>% 
-#                      forecast(h = h) %>% as_tibble(), 
-#                    .options = furrr_options(seed = TRUE))
-#   message("prophet fits complete, step 3/4")
-#   message("prophet forecasts complete, step 4/4")
-#   
-#   parallel::stopCluster(cl)
-#   plan(sequential)
-#   joint_fcst <- dplyr::bind_rows(fable_fcst, prophet_fcst) %>% 
-#     dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 
-#       0.1), med = median(n), ub_80 = quantile(n, 0.9), 
-#       ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
-#       dist = n, n = NULL)
-#       return(list(forecasts = joint_fcst))
-# }
-
+plan(cluster, workers = 8)
 system.time(oac_p_gp_fcsts <-
@@
               regionalJointFcsts())
+plan(sequential)
 
 oac_p_gp_fcsts %>%
-  write_rds("../data/oac_p_gp_fcsts.rds")
+  saveRDS("../data/oac_p_gp_fcsts.rds")
 
@@
 * 2020-12-18 2694 secs
+
+```{r}
+oac_p_monthly_quantity_gp_pre_cv19_complete <-
+  oac_p_monthly_quantity_gp_pre_cv19 %>% 
+  filter(!regional_unit %in% incomplete_gp)
+
+plan(cluster, workers = 8)
+system.time(fable_fit <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
+                 .f = ~fableModels(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                                          regional_unit ==.x)),
+                 .options = furrr_options(seed = TRUE)) %>%
+  forecast(h = "5 months") %>%
+  as_tibble())
+
+system.time(prophet_fit <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
+                 .f = ~prophetModels(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                                            regional_unit ==.x)),
+                 .options = furrr_options(seed = TRUE)) %>%
+  forecast(h = "5 months") %>%
+  as_tibble())
+plan(sequential)
+
+joint_fcst <-
+  bind_rows(fable_fcst, prophet_fcst) %>%
+  mutate(lb_95 = quantile(n, .025),
+         lb_80 = quantile(n, .1),
+         med = median(n),
+         ub_80 = quantile(n, .9),
+         ub_95 = quantile(n, .975),
+         sd = distributional::variance(n)^2,
+         dist = n,
+         n = NULL)
+joint_fcst %>%
+  saveRDS("../data/oac_p_gp_fcsts.rds")
+
+```
 

### 2021-01-15 r_scripts/functions.R
Local functions removed

@@ -1,11 +1,0 @@
-if(getwd() == "/Users/willhardy/OneDrive - Outreach Rescue/covid_prescribing/sercymru"){
-map(.x = list.files("r_scripts/functions"),
-    .f = ~source(paste0("r_scripts/functions/", .x)))
-} else if (getwd() == "/Users/willhardy/OneDrive - Outreach Rescue/covid_prescribing/sercymru/r_notebooks") {
-  map(.x = list.files("../r_scripts/functions"),
-      .f = ~source(paste0("../r_scripts/functions/", .x)))
-} else{
-  print("Check wd is set correctly in functions.r")
-  }
-
-

### 2021-01-15 r_scripts/functions/countRegional.R

@@ -1,28 +1,0 @@
-countRegional <- function(data, region, datename = datename, unit = Quantity){
-  # Function to create tsibble object for a count of `unit` per `datename`
-  # e.g. countRegional(oc, Locality, datename, Quantity) is the `Quantity`
-  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
-  # the number of days in each month.
-  region <- enquo(region)
-  datename <- enquo(datename)
-  unit <- enquo(unit)
-
-  data %>%
-    mutate(regional_unit = as_factor(set_names(!!region))) %>%
-    group_by(regional_unit, !!datename) %>%
-    summarise(n = sum(!!unit)) %>%
-    mutate(n = case_when(str_detect(!!datename, pattern = "-01-") ~ n/31,
-                         str_detect(!!datename, pattern = "-02-") ~ n/28.25,
-                         str_detect(!!datename, pattern = "-03-") ~ n/31,
-                         str_detect(!!datename, pattern = "-04-") ~ n/30,
-                         str_detect(!!datename, pattern = "-05-") ~ n/31,
-                         str_detect(!!datename, pattern = "-06-") ~ n/30,
-                         str_detect(!!datename, pattern = "-07-") ~ n/31,
-                         str_detect(!!datename, pattern = "-08-") ~ n/31,
-                         str_detect(!!datename, pattern = "-09-") ~ n/30,
-                         str_detect(!!datename, pattern = "-10-") ~ n/31,
-                         str_detect(!!datename, pattern = "-11-") ~ n/30,
-                         str_detect(!!datename, pattern = "-12-") ~ n/31)) %>%
-    ungroup() %>%
-    as_tsibble(index = !!datename, key = regional_unit)
-}

### 2021-01-15 r_scripts/functions/fableModels.R

@@ -1,28 +1,0 @@
-fableModels <- function(data){
-  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
-
-  data %>%
-    mutate(datename = yearmonth(datename)) %>%
-    model(trend_model1 = TSLM(n ~ trend()),#time series linear model
-          trend_model2 = TSLM(n ~ trend() + season("year")),
-          ets1 = ETS(n ~ trend()),
-          ets2 = ETS(n ~ trend() + season("A")),
-          ets3 = ETS(n ~ trend() + season("M")),
-          arima = ARIMA(n, stepwise = FALSE, approximation = FALSE),
-          neur_net = NNETAR(n),
-          #fasster = FASSTER(n ~ season("1 year") + trend(1) + fourier(12)),
-          comb1 = combination_model(TSLM(n ~ trend()),
-                                    ETS(n ~ trend())),
-          comb2 = combination_model(TSLM(n ~ trend() + season("year")),
-                                    ETS(n ~ trend() + season("A"))),
-          stl_dcmp1 = decomposition_model(STL(n ~ trend(),
-                                              iterations = 1000,
-                                              robust = TRUE),
-                                          SNAIVE(season_adjust)),
-          stl_dcmp2 = decomposition_model(STL(n ~ trend() + season(),
-                                              iterations = 1000,
-                                              robust = TRUE),
-                                          SNAIVE(season_adjust)),
-          s_naive = SNAIVE(n))# %>%
-    #as_tibble() # map_dfr() doesn't work on tsibble objects
-}

### 2021-01-15 r_scripts/functions/functions_forecasting.R

@@ -1,1 +1,0 @@
-#### Forecasting functions ####

### 2021-01-15 r_scripts/functions/prophetModels.R

@@ -1,50 +1,0 @@
-prophetModels <- function(data){
-  if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
-
-  oc_prophet_model1 <-
-    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model2 <-
-    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model3 <-
-    fable.prophet::prophet(n ~ growth("linear") +
-                             season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model4 <-
-    fable.prophet::prophet(n ~ growth("linear") +
-                             season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model5 <-
-    fable.prophet::prophet(n ~ season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model6 <-
-    fable.prophet::prophet(n ~ season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model7 <-
-    fable.prophet::prophet(n ~ holiday(holidays))
-  oc_prophet_model8 <-
-    fable.prophet::prophet(n)
-
-  data %>%
-    mutate(datename = yearmonth(datename)) %>%
-    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
-          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
-          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
-}
-
-
-holidays <-
-  bind_rows(tibble(holiday = "christmas",
-                   ds = as.Date(c("2016-12-25", "2017-12-25", "2018-12-25",
-                                  "2019-12-25", "2020-12-25", "2021-12-25")),
-                   lower_window = -1,
-                   upper_window = 1),
-
-            tibble(holiday = "easter", # Sunday
-                   ds = as.Date(c("2016-03-27", "2017-04-16", "2018-04-01",
-                                  "2019-04-21", "2020-04-12", "2021-04-04")),
-                   lower_window = -2,
-                   upper_window = 1))

### 2021-01-15 r_scripts/functions/regionalCV.R

@@ -1,72 +1,0 @@
-regionalCV <- function(data, cv_dist = 6, init = 36, step = 1){
-
-  # CV accuracy for fableModels() and prophetModels()
-
-  regions <- unique(data$regional_unit) # Get unique regional_units for map()
-
-  fableCV <- function(data){ # Return CV model accuracy for fableModels()
-    data_test <-
-      data %>%
-      mutate(datename = yearmonth(datename))
-
-    data_tr <-
-      data %>%
-      select(regional_unit, datename, n) %>%
-      mutate(datename = yearmonth(datename)) %>%
-      fill_gaps() %>%
-      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
-      stretch_tsibble(.init = init, .step = step)
-
-    data_tr %>%
-      fableModels() %>%
-      forecast(h = cv_dist) %>%
-      accuracy(data_test)
-
-  }
-
-  prophetCV <- function(data){# Return CV model accuracy for prophetModels()
-    data_test <-
-      data %>%
-      mutate(datename = yearmonth(datename))
-
-    data_tr <-
-      data %>%
-      select(regional_unit, datename, n) %>%
-      mutate(datename = yearmonth(datename)) %>%
-      fill_gaps() %>%
-      slice(1:(n()-cv_dist), .preserve = TRUE) %>%
-      stretch_tsibble(.init = init, .step = step)
-
-    data_tr %>%
-      prophetModels() %>%
-      forecast(h = cv_dist) %>%
-      accuracy(data_test)
-  }
-
-  plan(multisession) # Set up parallel processing to decrease computation time
-  # Prophet models won't run with plan(multisession) so need to be run
-  # sequentially. Is it worth trying to write this in Python and pass it back
-  # to R?
-
-    # Probably worth trying the prophet::cross_validation() method. If it
-    # returns RMSE and is faster it will be useful.
-  prophet_fits <-
-    future_map_dfr(.x =  regions,
-            .f = ~prophetCV(data = filter(data, regional_unit == .x)),
-            .options = furrr_options(seed = TRUE))
-  message("prophetModels() complete")
-
-  # Fable models will run using plan(multisession), but need to be run as below
-  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
-  # generated
-  fable_fits <-
-    future_map_dfr(.x =  regions,
-                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
[…]

### 2021-01-15 r_scripts/functions/regionalFableFits.R

@@ -1,9 +1,0 @@
-regionalFableFits <- function(data, region){
-  # Return various model objects for each region
-  print(region)
-  region <- enquo(region)
-
-  data %>%
-    filter(regional_unit == !!region) %>%
-    fableModels()
-}

### 2021-01-15 r_scripts/functions/regionalJointFcsts.R

@@ -1,48 +1,0 @@
-regionalJointFcsts <- function(data, h ="5 months"){
-  regions <- unique(data$regional_unit)
-  plan(multisession)
-  fable_fit <-
-    future_map_dfr(.x = regions,
-                   .f = ~fableModels(filter(data, regional_unit ==.x)),
-                   .options = furrr_options(seed = TRUE))
-  message("fable fits complete")
-
-  fable_fcst <- fable_fit %>%
-    forecast(h = h) %>%
-    as_tibble()
-  message("fable forecasts complete")
-
-
-  prophet_fit <-
-    future_map_dfr(.x = regions,
-                   .f = ~prophetModels(filter(data, regional_unit ==.x)),
-                   .options = furrr_options(seed = TRUE))
-  message("prophet fits complete")
-
-  prophet_fcst <-
-    forecast(prophet_fit, h = h) %>%
-    as_tibble()
-  # Some prophet forecasts are giving daily forecasts. We want monthly forecasts.
-  # This may also be influencing accuracy
-
-  message("prophet forecasts complete")
-  plan(sequential)
-  # prophetModels now being run in parallel. Needed to reinstall prophet from
-  # source
-
-  joint_fit <-
-    left_join(fable_fit, prophet_fit, by = "regional_unit")
-  joint_fcst <-
-    bind_rows(fable_fcst, prophet_fcst) %>%
-    mutate(lb_95 = quantile(n, .025),
-           lb_80 = quantile(n, .1),
-           med = median(n),
-           ub_80 = quantile(n, .9),
-           ub_95 = quantile(n, .975),
-           sd = distributional::variance(n)^2,
-           dist = n,
-           n = NULL)
-
-  return(list(fits = joint_fit, forecasts = joint_fcst))
-}
-

### 2021-01-15 r_scripts/functions/regionalJointFits.R

@@ -1,24 +1,0 @@
-regionalJointFits <- function(data){
-  regions <- unique(data$regional_unit)
-
-  plan(multisession)
-  fable_fit <-
-    future_map_dfr(.x = regions,
-                   .f = ~fableModels(filter(data, regional_unit == .x)),
-                   .options = furrr_options(seed = TRUE))
-  message("fable fits")
-
-  plan(sequential)
-
-  prophet_fit <-
-    map_dfr(.x = regions,
-            .f = ~prophetModels(filter(data, regional_unit == .x)))
-  message("prophet fits")
-
-  message("prophet forecasts")
-
-  joint_fit <-
-    left_join(fable_fit, prophet_fit, by = "regional_unit")
-
-  return(joint_fit)
-}

### 2021-01-15 r_scripts/functions/regionalPlot.R

@@ -1,31 +1,0 @@
-regionalPlot <- function(region, data){
-
-  ## Prophet forecast - can this be taken outside of the function?
-  ## no, when it is taken outside of the model, the forecast is becomes
-  ## much worse 2020-11-14
-  df <- data %>%
-    filter(regional_unit == region & datename < ymd("2020-03-23")) %>%
-    transmute(ds = datename, y = n)
-
-  m <- prophet::prophet(df, holidays = holidays,
-                        seasonality.mode = "additive",# mcmc.samples = 1000,
-                        weekly.seasonality = FALSE, daily.seasonality = FALSE)
-  future <- make_future_dataframe(m, periods = 5, freq = 'month')
-  fcst <- predict(m, future)
-
-  ## Plotting
-  plot <- fcsts %>%
-    filter(regional_unit == region) %>%
-    fabletools::autoplot(data, level = 80) + # fable forecasts over observed data
-    geom_line(aes(y = c(rep(NA,50), fcst[51:55,]$yhat)), # prophet prediction
-              col = "blue", lty = 3) +
-    geom_ribbon(aes(ymin = c(rep(NA,50), fcst[51:55,]$yhat_lower), # prophet confidence
-                    ymax = c(rep(NA,50), fcst[51:55,]$yhat_upper)),
-                alpha = .3, fill = "blue") +
-    geom_vline(xintercept = dmy("23-March-2020"), colour = "red") + # add line to mark the start of lockdown
-    labs(title = region)
-
-  ## Results
-  result <- list("plots" = plot)#, "prophet" = fcst)
-  return(result)
-}

### 2021-01-15 r_scripts/functions/regionalProphetFits.R

@@ -1,37 +1,0 @@
-regionalProphetFits <- function(data, region){
-  # Return various model objects for each region
-  region <- enquo(region)
-
-  oc_prophet_model1 <-
-    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model2 <-
-    fable.prophet::prophet(n ~ growth("linear", n_changepoints = 0) +
-                             season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model3 <-
-    fable.prophet::prophet(n ~ growth("linear",) +
-                             season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model4 <-
-    fable.prophet::prophet(n ~ growth("linear",) +
-                             season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model5 <-
-    fable.prophet::prophet(n ~ season("year", type = "additive") +
-                             holiday(holidays))
-  oc_prophet_model6 <-
-    fable.prophet::prophet(n ~ season("year", type = "multiplicative") +
-                             holiday(holidays))
-  oc_prophet_model7 <-
-    fable.prophet::prophet(n ~ holiday(holidays))
-  oc_prophet_model8 <-
-    fable.prophet::prophet(n)
-
-  data %>%
-    filter(regional_unit == !!region) %>%
-    model(oc_prophet_model1, oc_prophet_model2, oc_prophet_model3,
-          oc_prophet_model4, oc_prophet_model5, oc_prophet_model6,
-          oc_prophet_model7, oc_prophet_model8, .safely = TRUE)
-}

### 2021-01-15 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
R analyses

@@
 
-handlers(global = TRUE)
-handlers(
-  list(
-    handler_progress(
-      format = ":spin :current/:total (:message) [:bar] :percent in :elapsed ETA: :eta",
-      width = 60,
-      complete = "+"),
-    handler_beepr(finish   = "wilhelm",
-                  interval = 2.0)
-  )
-)
+# handlers(global = TRUE)
+# handlers(
+#   list(
+#     handler_progress(
+#       format = ":spin :current/:total (:message) [:bar] :percent in :elapsed ETA: :eta",
+#       width = 60,
+#       complete = "+"),
+#     handler_beepr(finish   = "wilhelm",
+#                   interval = 2.0)
+#   )
+# )
 
@@
 scaled_logit <- function(x, lower=0, upper=1){
-  log((x-lower)/(upper-x))
-}
+  log((x-lower)/(upper-x))}
 inv_scaled_logit <- function(x, lower=0, upper=1){
-  (upper-lower)*exp(x)/(1+exp(x)) + lower
-}
+  (upper-lower)*exp(x)/(1+exp(x)) + lower}
 my_scaled_logit <- fabletools::new_transformation(scaled_logit, inv_scaled_logit)
@@
 # Modifying functions to model my_scaled_logit(n, 0, 100) as using proportion data
-fableModels <- function(data){
+fableModelsBound <- function(data){
   if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
@@
     mutate(datename = yearmonth(datename)) %>%
-    model(trend_model1 = TSLM(my_scaled_logit(n, 0, 100) ~ trend()),#time series linear model
-          trend_model2 = TSLM(my_scaled_logit(n, 0, 100) ~ trend() + season("year")),
+    model(trend_model1 = TSLM(my_scaled_logit(n, 0, 100) ~ 
+                                trend()),#time series linear model
+          trend_model2 = TSLM(my_scaled_logit(n, 0, 100) ~ 
+                                trend() + season("year")),
           ets1 = ETS(my_scaled_logit(n, 0, 100) ~ trend()),
           ets2 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("A")),
-          ets3 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("M"), restrict = FALSE),
-          arima = ARIMA(my_scaled_logit(n, 0, 100), stepwise = FALSE, approximation = FALSE),
+          ets3 = ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("M"), 
+                     restrict = FALSE),
+          arima = ARIMA(my_scaled_logit(n, 0, 100), 
+                        stepwise = FALSE, 
+                        approximation = FALSE),
           comb1 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ trend()),
                                     ETS(my_scaled_logit(n, 0, 100) ~ trend())),
-          comb2 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ trend() + season("year")),
-                                    ETS(my_scaled_logit(n, 0, 100) ~ trend() + season("A"))),
-          stl_dcmp1 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ trend(),
+          comb2 = combination_model(TSLM(my_scaled_logit(n, 0, 100) ~ 
+                                           trend() + season("year")),
+                                    ETS(my_scaled_logit(n, 0, 100) ~ 
+                                          trend() + season("A"))),
+          stl_dcmp1 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ 
+                                                trend(),
                                               iterations = 1000,
@@
                                           SNAIVE(season_adjust)),
-          stl_dcmp2 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ trend() + season(),
+          stl_dcmp2 = decomposition_model(STL(my_scaled_logit(n, 0, 100) ~ 
+                                                trend() + season(),
                                               iterations = 1000,
@@
                                           SNAIVE(season_adjust)),
-          s_naive = SNAIVE(my_scaled_logit(n, 0, 100)))
+          s_naive = SNAIVE(my_scaled_logit(n, 0, 100)), .safely = TRUE)
 }
@@
 
-prophetModels <- function(data){
+prophetModelsBound <- function(data){
   if(!is_tsibble(data)){data <- as_tsibble(data, index = datename)}
@@
   oc_prophet_model1 <-
-    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ growth("linear", n_changepoints = 0) +
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ 
+                             growth("linear", n_changepoints = 0) +
                              season("year", type = "additive") +
@@
   oc_prophet_model2 <-
-    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ growth("linear", n_changepoints = 0) +
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ 
+                             growth("linear", n_changepoints = 0) +
                              season("year", type = "multiplicative") +
@@
   oc_prophet_model3 <-
-    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ growth("linear") +
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ 
+                             growth("linear") +
                              season("year", type = "additive") +
@@
   oc_prophet_model4 <-
-    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ growth("linear") +
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ 
+                             growth("linear") +
                              season("year", type = "multiplicative") +
@@
   oc_prophet_model5 <-
-    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ season("year", type = "additive") +
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ 
+                             season("year", type = "additive") +
                              holiday(holidays))
   oc_prophet_model6 <-
-    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ season("year", type = "multiplicative") +
+    fable.prophet::prophet(my_scaled_logit(n, 0, 100) ~ 
+                             season("year", type = "multiplicative") +
                              holiday(holidays))
@@
 
-  # CV accuracy for fableModels() and prophetModels()
+  # CV accuracy for fableModelsBound() and prophetModelsBound()
 
@@
 
-  p <- progressr::progressor(along = regions)
+  # p <- progressr::progressor(along = regions)
 
-  fableCV <- function(data){ # Return CV model accuracy for fableModels()
+  fableCV <- function(data){ # Return CV model accuracy for fableModelsBound()
     x <- data$regional_unit
@@
 
-    data_tr <-
     data %>%
@@
       slice(1:(n()-cv_dist), .preserve = TRUE) %>%
-      stretch_tsibble(.init = init, .step = step)
-
-    data_tr %>%
-      fableModels() %>%
+      stretch_tsibble(.init = init, .step = step) %>% 
+      fableModelsBound() %>%
       forecast(h = cv_dist) %>%
@@
 
-    p()
+    # p()
   }
 
-  prophetCV <- function(data){# Return CV model accuracy for prophetModels()
+  prophetCV <- function(data){# Return CV model accuracy for prophetModelsBound()
     x <- data$regional_unit
@@
     data_trn %>% 
-      prophetModels() %>%
+      prophetModelsBound() %>%
       forecast(h = cv_dist) %>%
@@
 
-    p()
+    # p()
   }
@@
                    .options = furrr_options(seed = TRUE))
-  message("prophetModels() complete")
+  message("prophetModelsBound() complete")
 
@@
                    .options = furrr_options(seed = TRUE))
-  message("fableModels() complete")
+  message("fableModelsBound() complete")
 
@@
     future_map_dfr(.x = regions,
-                   .f = ~fableModels(filter(data, regional_unit ==.x)) %>%
+                   .f = ~fableModelsBound(filter(data, regional_unit ==.x)) %>%
                     forecast(h = h),
@@
     future_map_dfr(.x = regions,
-                   .f = ~prophetModels(filter(data, regional_unit ==.x)) %>%
+                   .f = ~prophetModelsBound(filter(data, regional_unit ==.x)) %>%
                     forecast(h = h),
@@
 ```{r, health-board-modelling}
+plan(multisession)
 system.time(oac_p_hb_cv_models <-
   regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
-
+plan(sequential)
 oac_p_hb_cv_models %>%
@@
 
-* 724.044 seconds with multisession prophetModels()
+* 724.044 seconds with multisession prophetModelsBound()
 * 418.410 seconds with neur_net removed 2021-01-11
@@
 ```{r, gp-cluster-modelling}
+plan(multisession)
 system.time(oac_p_gp_cluster_cv_models <-
   regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
+plan(sequential)
 
@@
   future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
-                 .f = ~fableModels(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                           regional_unit ==.x)),
@@
   future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
-                 .f = ~prophetModels(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
                                             regional_unit ==.x)),

### 2021-01-17 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
R analyses

@@
 
-  # Fable models will run using plan(multisession), but need to be run as below
+  # Fable models will run using plan(cluster), but need to be run as below
   # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
@@
 
-  fable_fit <-
+  fable_fcst <-
     future_map_dfr(.x = regions,
@@
 
-  prophet_fit <-
+  prophet_fcst <-
     future_map_dfr(.x = regions,
@@
 ```{r, health-board-modelling}
-plan(multisession)
+plan(cluster)
 system.time(oac_p_hb_cv_models <-
@@
 
-* 724.044 seconds with multisession prophetModelsBound()
-* 418.410 seconds with neur_net removed 2021-01-11
+* 965.17 seconds with prophetModelsBound() 2021-01-15
 
@@
 ```
-
-* 194.071 seconds 2020-12-10
-* 71.559 seconds 2021-01-11
+129.80 2021-01-15
+*
 
@@
 ```{r, gp-cluster-modelling}
-plan(multisession)
+plan(cluster)
 system.time(oac_p_gp_cluster_cv_models <-
@@
 
-* 5514.279 seconds
-* 2059.159 seconds 2021-01-11
+*
 
@@
 
-* 2.195e+04 seconds 2020-12-07
-* 25547.266 seconds 2020-12-09
+* prophetModelsBound() complete
+NaNs producedfableModelsBound() complete
+    user   system  elapsed 
+  504.83    38.03 11465.09 
+prophetModelsBound() complete                                         
+NaNs producedNaNs producedfableModelsBound() complete                 
+    user   system  elapsed 
+  520.35    40.97 11534.13 
+prophetModelsBound() complete
+fableModelsBound() complete
+    user   system  elapsed 
+  377.34    22.89 11300.13 
+prophetModelsBound() complete
+fableModelsBound() complete
+    user   system  elapsed 
+  370.35    21.11 11321.84
 
@@
   saveRDS("../data/oac_p_gp_fcsts.rds")
+
+oac_p_gp_fcsts <-
+  read_rds("../data/oac_p_gp_fcsts.rds")
 

### 2021-01-17 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
Fixed error in calculating warfarin as a percentage of all oac within GP unit.

@@
 oac_p_monthly_quantity_gp <- 
-  propRegional(oac, PracticeID, datename, Quantity, bnf = warf)
+  oac %>% 
+  group_by(PracticeID, datename, bnfchem) %>% 
+  summarise(sum_n = sum(Quantity), .groups = "drop_last") %>% 
+  mutate(p_war = 100 * sum_n / sum(sum_n)) %>% 
+  filter(bnfchem == as_name(warf)) %>% 
+  transmute(regional_unit = as.factor(PracticeID),
+            datename = datename,
+            n = p_war) %>%
+    ungroup() %>%
+    as_tsibble(index = datename, key = regional_unit)
 
@@
 
-oac_p_monthly_quantity_hb_pre_cv19 <- 
-  oac_p_monthly_quantity_hb %>% 
-    filter(datename < dmy("01-03-2020"))
-
-oac_p_monthly_quantity_cluster_pre_cv19 <- 
-  oac_p_monthly_quantity_cluster %>% 
-    filter(datename < dmy("01-03-2020"))
+# oac_p_monthly_quantity_hb_pre_cv19 <- 
+#   oac_p_monthly_quantity_hb %>% 
+#     filter(datename < dmy("01-03-2020"))
+# 
+# oac_p_monthly_quantity_cluster_pre_cv19 <- 
+#   oac_p_monthly_quantity_cluster %>% 
+#     filter(datename < dmy("01-03-2020"))
 
@@
 
-```{r, health-board-modelling}
+```{r, health-board-modelling, eval = FALSE}
 plan(cluster)
@@
 
-```{r}
+```{r health-board-forecast, eval = FALSE}
 plan(cluster)
@@
 
-```{r, gp-cluster-modelling}
+```{r, gp-cluster-modelling, eval = FALSE}
 plan(cluster)
@@
 
-```{r}
+```{r gp-cluste-forecast, eval = FALSE}
 plan(cluster)
@@
   .$regional_unit %>% 
+  as.character() %>% 
   unique()
@@
 # Running regionalCV() on each of the quarter of the data
-plan(cluster)
+plan(multisession)
 system.time(oac_p_gp_cv_models_1 <-
@@
               regionalCV())
-with_progress(system.time(oac_p_gp_cv_models_2 <-
+system.time(oac_p_gp_cv_models_2 <-
   complete_oac_p_monthly_quantity_gp_pre_cv19_2 %>%
-              regionalCV()))
+              regionalCV())
 system.time(oac_p_gp_cv_models_3 <-
@@
 
-```{r}
-plan(cluster, workers = 8)
-system.time(oac_p_gp_fcsts <-
+```{r gp-practice-forecast}
+plan(multisession)
+system.time(oac_p_gp_fcst_1 <-
   oac_p_monthly_quantity_gp_pre_cv19 %>%
-              filter(!regional_unit %in% incomplete_gp) %>%
+              filter(regional_unit %in% seg_1) %>%
+    regionalJointFcsts())
+system.time(oac_p_gp_fcst_2 <-
+  oac_p_monthly_quantity_gp_pre_cv19 %>%
+              filter(regional_unit %in% seg_2) %>%
+    regionalJointFcsts())
+system.time(oac_p_gp_fcst_3 <-
+  oac_p_monthly_quantity_gp_pre_cv19 %>%
+              filter(regional_unit %in% seg_3) %>%
+    regionalJointFcsts())
+system.time(oac_p_gp_fcst_4 <-
+  oac_p_monthly_quantity_gp_pre_cv19 %>%
+              filter(regional_unit %in% seg_4) %>%
     regionalJointFcsts())
 plan(sequential)
+
+oac_p_gp_fcsts <-
+  bind_rows(oac_p_gp_fcst_1,
+            oac_p_gp_fcst_2,
+            oac_p_gp_fcst_3,
+            oac_p_gp_fcst_4)
 
@@
 
-* 2020-12-18 2694 secs
+* NaNs producedNaNs producedfable forecasts complete
+prophet forecasts complete
+    user   system  elapsed 
+  97.430   22.773 1580.689 
+fable forecasts complete
+prophet forecasts complete
+    user   system  elapsed 
+ 106.565   84.755 1719.863 
+fable forecasts complete
+prophet forecasts complete
+    user   system  elapsed 
+ 114.419  116.874 1867.420 
+fable forecasts complete
+prophet forecasts complete
+    user   system  elapsed 
+ 113.032  124.767 1910.564
 
@@
 
-plan(cluster, workers = 8)
-system.time(fable_fit <-
-  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
+plan(multisession)
+system.time(fable_fit_1 <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[1:101],
                  .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
@@
 
-system.time(prophet_fit <-
-  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit,
+system.time(prophet_fit_1 <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[1:101],
+                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                                            regional_unit ==.x)),
+                 .options = furrr_options(seed = TRUE)) %>%
+  forecast(h = "5 months") %>%
+  as_tibble())
+system.time(fable_fit_2 <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[102:202],
+                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                                          regional_unit ==.x)),
+                 .options = furrr_options(seed = TRUE)) %>%
+  forecast(h = "5 months") %>%
+  as_tibble())
+
+system.time(prophet_fit_2 <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[102:202],
+                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                                            regional_unit ==.x)),
+                 .options = furrr_options(seed = TRUE)) %>%
+  forecast(h = "5 months") %>%
+  as_tibble())
+system.time(fable_fit_3 <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[203:303],
+                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                                          regional_unit ==.x)),
+                 .options = furrr_options(seed = TRUE)) %>%
+  forecast(h = "5 months") %>%
+  as_tibble())
+
+system.time(prophet_fit_3 <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[203:303],
+                 .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                                            regional_unit ==.x)),
+                 .options = furrr_options(seed = TRUE)) %>%
+  forecast(h = "5 months") %>%
+  as_tibble())
+system.time(fable_fit_4 <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[304:404],
+                 .f = ~fableModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
+                                          regional_unit ==.x)),
+                 .options = furrr_options(seed = TRUE)) %>%
+  forecast(h = "5 months") %>%
+  as_tibble())
+
+system.time(prophet_fit_4 <-
+  future_map_dfr(.x = oac_p_monthly_quantity_gp_pre_cv19_complete$regional_unit[304:404],
                  .f = ~prophetModelsBound(filter(oac_p_monthly_quantity_gp_pre_cv19_complete,
@@
 joint_fcst <-
-  bind_rows(fable_fcst, prophet_fcst) %>%
+  bind_rows(fable_fcst_1, prophet_fcst_1,
+            fable_fcst_2, prophet_fcst_2,
+            fable_fcst_3, prophet_fcst_3,
+            fable_fcst_4, prophet_fcst_4) %>%
   mutate(lb_95 = quantile(n, .025),
@@
 
-```{r, eval = FALSE}
+```{r}
 best_model_gp %>% 
@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = 1000000*(n - .mean), # Why are the numbers so small?
-         regional_unit = as.factor(regional_unit)) %>% 
-  select(regional_unit, datename, discrepancy) %>% 
-  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
-  mutate(regional_unit = as.numeric(regional_unit)) %>% 
-  na.omit() %>% .[2:5] %>% min()
-  write_csv(file = "../data/mplus/oac_gp_discrep.csv", col_names = FALSE)
+  mutate(discrepancy = n - .mean,
+         # regional_unit = as.character(regional_unit)
+         ) %>% 
+  ggplot(aes(x = datename, y = n, group = regional_unit)) +
+  geom_line() +
+  facet_wrap(~regional_unit)
+
+  as_tsibble(key = regional_unit, index = datename) %>% 
+  autoplot(oac_p_monthly_quantity_gp_pre_cv19 %>% 
+             select(regional_unit, datename, n) %>% 
+             as_tsibble(key = regional_unit, index = datename)) +
+  theme(legend.position = "none")
 ```
-
-```{r, eval = FALSE}
-source("../r_scripts/functions/mplus_plotting.R")
-mplus.view.plots("../mplus_analyses/oac_discrep_3_class_bayes.gh5")
-mplus.plot.estimated_means("../mplus_analyses/oac_discrep_3_class_bayes.gh5")
-```

### 2021-01-18 r_notebooks/exploring_hydroxychloroquine_sulphate.nb.Rmd
R analyses

@@
 library(serCymruTools)
+library(progressr)
+library(beepr)
+
+# handlers(global = TRUE)
+# handlers(
+#   list(
+#     handler_progress(
+#       format = ":spin :current/:total (:message) [:bar] :percent in :elapsed ETA: :eta",
+#       width = 60,
+#       complete = "+"),
+#     handler_beepr(finish   = "wilhelm",
+#                   interval = 2.0)
+#   )
+# )
 
@@
 ```{r, health-board-modelling}
-plan(multisession)
-system.time(hcq_hb_cv_models <-
-  regionalCV(data = hcq_monthly_quantity_hb_pre_cv19))
-plan(sequential)
-
-hcq_hb_cv_models %>%
-  saveRDS("../data/hcq_hb_cv_models.rds")
+# plan(multisession)
+# with_progress(system.time(hcq_hb_cv_models <-
+#   regionalCV(data = hcq_monthly_quantity_hb_pre_cv19)))
+# plan(sequential)
+# 
+# hcq_hb_cv_models %>%
+#   saveRDS("../data/hcq_hb_cv_models.rds")
 
@@
 ```{r}
-plan(cluster)
-system.time(hcq_hb_fcsts <- regionalJointFcsts(hcq_monthly_quantity_hb_pre_cv19))
-plan(sequential)
-
-hcq_hb_fcsts %>%
-  saveRDS("../data/hcq_hb_fcsts.rds")
+# plan(cluster)
+# system.time(hcq_hb_fcsts <- regionalJointFcsts(hcq_monthly_quantity_hb_pre_cv19))
+# plan(sequential)
+# 
+# hcq_hb_fcsts %>%
+#   saveRDS("../data/hcq_hb_fcsts.rds")
 
@@
 ```{r, gp-cluster-modelling}
-# plan(multisession)
-# system.time(hcq_gp_cluster_cv_models <-
-#   regionalCV(data = hcq_monthly_quantity_cluster_pre_cv19))
-# plan(sequential)
-# 
-# hcq_gp_cluster_cv_models %>%
-#   saveRDS("../data/hcq_gp_cluster_cv_models.rds")
+plan(multisession)
+system.time(hcq_gp_cluster_cv_models <-
+  regionalCV(data = hcq_monthly_quantity_cluster_pre_cv19))
+plan(sequential)
+
+hcq_gp_cluster_cv_models %>%
+  saveRDS("../data/hcq_gp_cluster_cv_models.rds")
 
@@
 ```{r}
-# plan(multisession)
-# system.time(hcq_gp_cluster_fcsts <- 
-#               regionalJointFcsts(hcq_monthly_quantity_cluster_pre_cv19))
-# plan(sequential)
-# 
-# hcq_gp_cluster_fcsts %>%
-#   saveRDS("../data/hcq_gp_cluster_fcsts.rds")
+plan(multisession)
+system.time(hcq_gp_cluster_fcsts <-
+              regionalJointFcsts(hcq_monthly_quantity_cluster_pre_cv19))
+plan(sequential)
+
+hcq_gp_cluster_fcsts %>%
+  saveRDS("../data/hcq_gp_cluster_fcsts.rds")
 
@@
 ```{r, gp-practice-modelling}
-incomplete_gp <- hcq_monthly_quantity_gp_pre_cv19 %>% 
+complete_gp <- 
+  hcq_monthly_quantity_gp_pre_cv19 %>% 
   as_tibble() %>% 
@@
   count() %>% 
-    filter(n < 50) %>% 
+  filter(n >= 62) %>% 
   .$regional_unit %>% 
@@
 
-plan(cluster)
-system.time(hcq_gp_cv_models <-
-  hcq_monthly_quantity_gp_pre_cv19 %>%
-    filter(!regional_unit %in% incomplete_gp) %>%
-              regionalCV())
-plan(sequential)
-
-hcq_gp_cv_models %>%
-  saveRDS("../data/hcq_gp_cv_models.rds")
+# plan(multisession)
+# # Chunking analyses into ~100 GPs uses ~ 23Gb of RAM
+# system.time(hcq_gp_cv_models_1 <-
+#   hcq_monthly_quantity_gp_pre_cv19 %>%
+#     filter(regional_unit %in% complete_gp[1:100]) %>% 
+#               regionalCV(init = 48))
+# system.time(hcq_gp_cv_models_2 <-
+#   hcq_monthly_quantity_gp_pre_cv19 %>%
+#     filter(regional_unit %in% complete_gp[101:200]) %>% 
+#               regionalCV(init = 48))
+# system.time(hcq_gp_cv_models_3 <-
+#   hcq_monthly_quantity_gp_pre_cv19 %>%
+#     filter(regional_unit %in% complete_gp[201:300]) %>% 
+#               regionalCV(init = 48))
+# system.time(hcq_gp_cv_models_4 <-
+#   hcq_monthly_quantity_gp_pre_cv19 %>%
+#     filter(regional_unit %in% complete_gp[301:length(complete_gp)]) %>% 
+#               regionalCV(init = 48))
+# plan(sequential)
+# 
+# hcq_gp_cv_models <- 
+#   bind_rows(hcq_gp_cv_models_1,
+#             hcq_gp_cv_models_2,
+#             hcq_gp_cv_models_3,
+#             hcq_gp_cv_models_4)
+# 
+# hcq_gp_cv_models %>%
+#   saveRDS("../data/hcq_gp_cv_models.rds")
 
@@
 
+hcq_monthly_quantity_gp_pre_cv19 %>% 
+  as_tibble() %>% 
+  group_by(regional_unit) %>% 
+  summarise(mean_quantity = mean(n))
+
+best_model_gp %>% 
+  left_join(hcq_monthly_quantity_gp_pre_cv19 %>% 
+              as_tibble() %>% 
+              group_by(regional_unit) %>% 
+              summarise(mean_quantity = mean(n)), 
+            by = c("regional_unit")) %>% 
+  select(-c(.model, .type)) %>% 
+  DataExplorer::plot_correlation()
+
 ```
@@
               hcq_monthly_quantity_gp_pre_cv19 %>%
-              filter(!regional_unit %in% incomplete_gp) %>%
+              filter(regional_unit %in% complete_gp) %>%
               regionalJointFcsts())
@@
 
-hcq_gp_fcsts %>% 
-  group_by(.model) %>% 
-  count
-
 ```
 
-*
+* 2755.011 seconds 2021-01-13
 
@@
 
-```{r}
-best_model_gp_discrep %>% 
-  filter(discrepancy < -40)
-
-hcq_monthly_quantity_gp %>% 
-  filter(regional_unit %in% c("W97009", "W98053")) %>% 
-  as_tsibble(key = regional_unit, index = datename) %>% 
-  autoplot()
-
-gp %>% 
-  filter(practiceid %in% c("W97009", "W98053"))
-```
-
-* Based on postcodes, these are both University GPs. Or at least, given their procimity to universities, they will likely have large student populations.
-
 #### Latent profile analysis
@@
   plot_profiles(x = ., rawdata = FALSE)
-
 ```
@@
 
-```{r, mplus-anlayses}
+```{r, mplus-anlayses, eval=FALSE}
 source("../r_scripts/functions/mplus_plotting.R")
@@
 
-# mplus.view.plots("../mplus_analyses/hcq_gp/hcq_discrep_5_class_ml.gh5")
-mplus.plot.estimated_means("../mplus_analyses/hcq_gp/hcq_discrep_5_class_ml.gh5")
+# mplus.view.plots("../mplus_analyses/hcq_gp/hcq_discrep_3_class_lgmm_ml.gh5")
+mplus.plot.estimated_means("../mplus_analyses/hcq_gp/hcq_discrep_3_class_lgmm_ml.gh5")
 ```
+
 #### kmeans

### 2021-01-18 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
R analyses

@@
   # e.g. propRegional(oc, Locality, datename, Quantity) is the `Quantity`
-  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
-  # the number of days in each month.
+  # per `datename` grouped by `Locality` from `oc`
+
   region <- enquo(region)
@@
     mutate(regional_unit = as_factor(set_names(!!region))) %>%
-    group_by(!!datename, bnfchem, regional_unit) %>% 
-    summarise(n = sum(!!unit)) %>% 
-    mutate(n = 100 * n / sum(n),
-           log_n = log(n)) %>% 
+    group_by(regional_unit, !!datename, bnfchem) %>% 
+    summarise(n = sum(!!unit), .groups = "drop_last") %>% 
+    mutate(n = 100 * n / sum(n)) %>% 
     filter(bnfchem == bnf) %>%
@@
            sd = distributional::variance(n)^2,
-           dist = n,
-           n = NULL)
+           n = NULL # Remove distribution from saved object
+           )
 
@@
 
-# oac_p_monthly_quantity_hb_pre_cv19 <- 
-#   oac_p_monthly_quantity_hb %>% 
-#     filter(datename < dmy("01-03-2020"))
-# 
-# oac_p_monthly_quantity_cluster_pre_cv19 <- 
-#   oac_p_monthly_quantity_cluster %>% 
-#     filter(datename < dmy("01-03-2020"))
+oac_p_monthly_quantity_hb_pre_cv19 <-
+  oac_p_monthly_quantity_hb %>%
+    filter(datename < dmy("01-03-2020"))
+
+oac_p_monthly_quantity_cluster_pre_cv19 <-
+  oac_p_monthly_quantity_cluster %>%
+    filter(datename < dmy("01-03-2020"))
 
@@
 * 965.17 seconds with prophetModelsBound() 2021-01-15
+* 966.923 seconds with prophetModelsBound() 2021-01-18
 
@@
 ```
-129.80 2021-01-15
-*
+
+* 129.80 2021-01-15
+* 107.254 2021-01-18
 
@@
 # Running regionalCV() on each of the quarter of the data
-plan(multisession)
+plan(cluster)
 system.time(oac_p_gp_cv_models_1 <-
@@
               regionalCV())
+plan(sequential)
 system.time(oac_p_gp_cv_models_3 <-

### 2021-01-18 r_notebooks/exploring_oral_contraceptives.Rmd
R analyses

@@
 ```{r, health-board-modelling}
-# plan(multisession)
-# system.time(oc_hb_cv_models <-
-#   regionalCV(data = oc_monthly_quantity_hb_pre_cv19))
-# plan(sequential)
-# 
+plan(multisession)
+system.time(oc_hb_cv_models <-
+  regionalCV(data = oc_monthly_quantity_hb_pre_cv19))
+plan(sequential)
+
 # oc_hb_cv_models %>%
 #   saveRDS("../data/oc_hb_cv_models.rds")
-
-oc_hb_cv_models <- 
-  read_rds("../data/oc_hb_cv_models.rds")
+# 
+# oc_hb_cv_models <- 
+#   read_rds("../data/oc_hb_cv_models.rds")
 
@@
 * 570.350 seconds with multisession prophetModels()
+* 278.968 seconds 2021-01-18
 
@@
 ```{r, gp-cluster-modelling}
-# plan(multisession)
-# system.time(oc_gp_cluster_cv_models <-
-#   regionalCV(data = oc_monthly_quantity_cluster_pre_cv19))
-# plan(sequential)
+plan(multisession)
+system.time(oc_gp_cluster_cv_models <-
+  regionalCV(data = oc_monthly_quantity_cluster_pre_cv19))
+plan(sequential)
 # 
@@
   ggplot(aes(x = MAPE)) +
-  geom_histogram()
+  geom_histogram() +
+  coord_cartesian(ylim = c(0,100))
 

### 2021-01-18 r_notebooks/exploring_hydroxychloroquine_sulphate.nb.Rmd
R analyses

@@
 
-```{r hcq-monthly-ts-plot, fig.cap="Total quantity of combined hormonal and progestogen only oral contraceptives prescribed per month."}
+```{r hcq-monthly-ts-plot, fig.cap="Total quantity of hcq prescribed per month."}
 hcq %>% 
@@
 
-# plan(multisession)
-# # Chunking analyses into ~100 GPs uses ~ 23Gb of RAM
-# system.time(hcq_gp_cv_models_1 <-
-#   hcq_monthly_quantity_gp_pre_cv19 %>%
-#     filter(regional_unit %in% complete_gp[1:100]) %>% 
-#               regionalCV(init = 48))
-# system.time(hcq_gp_cv_models_2 <-
-#   hcq_monthly_quantity_gp_pre_cv19 %>%
-#     filter(regional_unit %in% complete_gp[101:200]) %>% 
-#               regionalCV(init = 48))
-# system.time(hcq_gp_cv_models_3 <-
-#   hcq_monthly_quantity_gp_pre_cv19 %>%
-#     filter(regional_unit %in% complete_gp[201:300]) %>% 
-#               regionalCV(init = 48))
-# system.time(hcq_gp_cv_models_4 <-
-#   hcq_monthly_quantity_gp_pre_cv19 %>%
-#     filter(regional_unit %in% complete_gp[301:length(complete_gp)]) %>% 
-#               regionalCV(init = 48))
-# plan(sequential)
-# 
-# hcq_gp_cv_models <- 
-#   bind_rows(hcq_gp_cv_models_1,
-#             hcq_gp_cv_models_2,
-#             hcq_gp_cv_models_3,
-#             hcq_gp_cv_models_4)
-# 
-# hcq_gp_cv_models %>%
-#   saveRDS("../data/hcq_gp_cv_models.rds")
+plan(cluster)
+# Chunking analyses into ~100 GPs uses ~ 23Gb of RAM
+system.time(hcq_gp_cv_models_1 <-
+  hcq_monthly_quantity_gp_pre_cv19 %>%
+    filter(regional_unit %in% complete_gp[1:100]) %>%
+              regionalCV(init = 48))
+system.time(hcq_gp_cv_models_2 <-
+  hcq_monthly_quantity_gp_pre_cv19 %>%
+    filter(regional_unit %in% complete_gp[101:200]) %>%
+              regionalCV(init = 48))
+system.time(hcq_gp_cv_models_3 <-
+  hcq_monthly_quantity_gp_pre_cv19 %>%
+    filter(regional_unit %in% complete_gp[201:300]) %>%
+              regionalCV(init = 48))
+system.time(hcq_gp_cv_models_4 <-
+  hcq_monthly_quantity_gp_pre_cv19 %>%
+    filter(regional_unit %in% complete_gp[301:length(complete_gp)]) %>%
+              regionalCV(init = 48))
+plan(sequential)
+
+hcq_gp_cv_models <-
+  bind_rows(hcq_gp_cv_models_1,
+            hcq_gp_cv_models_2,
+            hcq_gp_cv_models_3,
+            hcq_gp_cv_models_4)
+
+hcq_gp_cv_models %>%
+  saveRDS("../data/hcq_gp_cv_models.rds")
 

### 2021-01-18 r_notebooks/exploring_adrenoceptor_agonists.Rmd
Adding hcq analyses

---
title: "Hydroxychloroquine sulphate"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

```{r}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>%
  mutate(npat = N,
         N = NULL, 
         practice_id = practiceid) %>% 
  filter(year == 2020) # do something better
gp$practiceid = NULL

adreno <- read_rds("../data/presdata_updates_040121/presc_wales_adrenoceptor-agonists.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename))) %>% 
  janitor::clean_names()

## Sort into monthly count data
adreno_monthly_count <- adreno %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

adreno_monthly_quantity_hb <- 
  right_join(adreno, select(gp, c(practice_id, hboard)), 
             by = c("practice_id")) %>%
  countRegional(hboard, datename, quantity) %>% 
  left_join(gp %>% 
              select(c(practice_id, npat, hboard)) %>% 
              group_by(hboard) %>% 
              summarise(npat = sum(npat)), by = c("regional_unit" = "hboard")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

adreno_monthly_quantity_cluster <- 
  right_join(adreno, select(gp, c(practice_id, cluster)), 
             by = c("practice_id")) %>%
  countRegional(cluster, datename, quantity) %>% 
  left_join(gp %>% 
  select(c(practice_id, npat, cluster)) %>% 
  group_by(cluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

adreno_monthly_quantity_gp <- 
  countRegional(adreno, practice_id, datename, quantity) %>% 
  right_join(select(gp, c(practice_id, npat)), 
            by = c("regional_unit" = "practice_id")) %>% 
  mutate(n = 1000*n/npat)

## Sort into monthly count data pre-lockdown (2020-03-23)
adreno_monthly_count_pre_cv19 <- 
  adreno_monthly_count %>% 
  filter(datename < dmy("01-03-2020"))

adreno_monthly_quantity_hb_pre_cv19 <- 
  adreno_monthly_quantity_hb %>% 
    filter(datename < dmy("01-03-2020"))

adreno_monthly_quantity_cluster_pre_cv19 <- 
  adreno_monthly_quantity_cluster %>% 
    filter(datename < dmy("01-03-2020"))

adreno_monthly_quantity_gp_pre_cv19 <- 
  adreno_monthly_quantity_gp %>% 
    filter(datename < dmy("01-03-2020"))

```

## Overview

### 2016-2020 plot of all adreno prescriptions

```{r adreno-monthly-ts-plot, fig.cap="Total quantity of adrenoreceptor agonists prescribed per month."}
adreno %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  tsibble() %>% 
  autoplot(n) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

*

### Seasonality

```{r adreno-monthly-seasonality-plot}
df <- adreno_monthly_count_pre_cv19 %>% 
  mutate(month = as.factor(month(datename, label = TRUE, abbr = TRUE)),
         year = as.factor(year(datename)))

df2 <- df %>% 
  as_tibble() %>% 
  filter(year(datename) != 2020) %>% 
  group_by(month) %>% 
  summarise(n = mean(n))

df %>% 
  ggplot(aes(x = month, y = n, colour = year, group = year)) +
  geom_line() +
  geom_line(data = df2, aes(x = month, y = n, group = "Avg"), 
            colour = "red", lty = 2) +
  labs(caption = "Red dashed line is mean for 2016-2019")

```
*

```{r}
adreno_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  gg_subseries(y = n, period = "year")
```

*

### Lag plots

```{r}
adreno_monthly_count_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>% 
  gg_lag(y = n, geom = "point", lags = 1:12)
```

```{r}
adreno_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  gg_lag(y = n, geom = "point", lags = 13:24)
```
*

### Autocorrelation

```{r}
tseries::adf.test(adreno_monthly_count$n)
urca::ur.df(adreno_monthly_count$n)
```

```{r}
adreno_monthly_count_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>% 
  ACF(n, lag_max = 60) %>% autoplot()
```

* Autocorrelation greatest at 2 and 12

```{r}
adreno_monthly_count_pre_cv19$n %>%
  pacf(lag.max = 60)
```

## Overview of each drug

```{r}
adreno %>% 
  group_by(datename, chemname) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(n = case_when(str_detect(datename, pattern = "-01-") ~ n/31,
                       str_detect(datename, pattern = "-02-") ~ n/28.25,
                       str_detect(datename, pattern = "-03-") ~ n/31,
                       str_detect(datename, pattern = "-04-") ~ n/30,
                       str_detect(datename, pattern = "-05-") ~ n/31,
                       str_detect(datename, pattern = "-06-") ~ n/30,
                       str_detect(datename, pattern = "-07-") ~ n/31,
                       str_detect(datename, pattern = "-08-") ~ n/31,
                       str_detect(datename, pattern = "-09-") ~ n/30,
                       str_detect(datename, pattern = "-10-") ~ n/31,
                       str_detect(datename, pattern = "-11-") ~ n/30,
                       str_detect(datename, pattern = "-12-") ~ n/31))%>% 
  as_tsibble(index = datename, key = chemname) %>% 
  autoplot(n) +
  theme(legend.position = "none") +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

## Time series components

```{r}
dcmp <- 
  adreno_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  model(STL(n))

adreno_monthly_count_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>% 
  autoplot(n, color = "grey") + 
  autolayer(components(dcmp), trend, color = "red")

components(dcmp) %>% 
  autoplot()
```

```{r}
adreno_monthly_count %>% 
  mutate(datename = yearmonth(datename)) %>% 
  autoplot(n, color = "grey") + 
  autolayer(components(dcmp), season_adjust, colour = "blue") +
  labs(title = "Seasonally adjusted")
```

## Modelling

### By Health Board

```{r, health-board-modelling}
plan(multisession)
system.time(adreno_hb_cv_models <-
  regionalCV(data = adreno_monthly_quantity_hb_pre_cv19))
plan(sequential)

adreno_hb_cv_models %>%
  saveRDS("../data/adreno_hb_cv_models.rds")

adreno_hb_cv_models <- 
  read_rds("../data/adreno_hb_cv_models.rds")

adreno_hb_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

adreno_hb_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

adreno_hb_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))
```

* 756.556 seconds 2021-01-12

```{r}
plan(cluster)
system.time(adreno_hb_fcsts <- regionalJointFcsts(adreno_monthly_quantity_hb_pre_cv19))
plan(sequential)

adreno_hb_fcsts %>%
  saveRDS("../data/adreno_hb_fcsts.rds")

adreno_hb_fcsts <- 
  read_rds("../data/adreno_hb_fcsts.rds")
```

*

### By GP Cluster

```{r, gp-cluster-modelling}
plan(multisession)
system.time(adreno_gp_cluster_cv_models <-
  regionalCV(data = adreno_monthly_quantity_cluster_pre_cv19))
plan(sequential)

adreno_gp_cluster_cv_models %>%
  saveRDS("../data/adreno_gp_cluster_cv_models.rds")

adreno_gp_cluster_cv_models <- 
  read_rds("../data/adreno_gp_cluster_cv_models.rds")

adreno_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

adreno_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

adreno_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

```

*

```{r}
plan(multisession)
system.time(adreno_gp_cluster_fcsts <-
              regionalJointFcsts(adreno_monthly_quantity_cluster_pre_cv19))
plan(sequential)

adreno_gp_cluster_fcsts %>%
  saveRDS("../data/adreno_gp_cluster_fcsts.rds")

adreno_gp_cluster_fcsts <- 
  read_rds("../data/adreno_gp_cluster_fcsts.rds")
```

*

### By Practice

```{r, gp-practice-modelling}
complete_gp <- 
  adreno_monthly_quantity_gp_pre_cv19 %>% 
  as_tibble() %>% 
  group_by(regional_unit) %>% 
  count() %>% 
  filter(n >= 62) %>% 
  .$regional_unit %>% 
  unique()

plan(cluster)
# Chunking analyses into ~100 GPs uses ~ 23Gb of RAM
system.time(adreno_gp_cv_models_1 <-
  adreno_monthly_quantity_gp_pre_cv19 %>%
    filter(regional_unit %in% complete_gp[1:100]) %>%
              regionalCV(init = 48))
system.time(adreno_gp_cv_models_2 <-
  adreno_monthly_quantity_gp_pre_cv19 %>%
    filter(regional_unit %in% complete_gp[101:200]) %>%
              regionalCV(init = 48))
system.time(adreno_gp_cv_models_3 <-
  adreno_monthly_quantity_gp_pre_cv19 %>%
    filter(regional_unit %in% complete_gp[201:300]) %>%
              regionalCV(init = 48))
system.time(adreno_gp_cv_models_4 <-
  adreno_monthly_quantity_gp_pre_cv19 %>%
    filter(regional_unit %in% complete_gp[301:length(complete_gp)]) %>%
              regionalCV(init = 48))
plan(sequential)

adreno_gp_cv_models <-
  bind_rows(adreno_gp_cv_models_1,
            adreno_gp_cv_models_2,
            adreno_gp_cv_models_3,
            adreno_gp_cv_models_4)

adreno_gp_cv_models %>%
  saveRDS("../data/adreno_gp_cv_models.rds")

adreno_gp_cv_models <- 
  read_rds("../data/adreno_gp_cv_models.rds")

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90))

```

*

```{r gp-modelling-accuracy}
best_model_gp <- 
  adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model_gp %>% 
  left_join(select(gp, practice_id, npat, ngp), 
            by = c("regional_unit" = "practice_id")) %>% 
  select(-c(.model, .type)) %>% 
  DataExplorer::plot_correlation()

adreno_monthly_quantity_gp_pre_cv19 %>% 
  as_tibble() %>% 
  group_by(regional_unit) %>% 
  summarise(mean_quantity = mean(n))

best_model_gp %>% 
  left_join(adreno_monthly_quantity_gp_pre_cv19 %>% 
              as_tibble() %>% 
              group_by(regional_unit) %>% 
              summarise(mean_quantity = mean(n)), 
            by = c("regional_unit")) %>% 
  select(-c(.model, .type)) %>% 
  DataExplorer::plot_correlation()

```

```{r gp-practice-forecasts}
plan(cluster)
system.time(adreno_gp_fcsts <-
              adreno_monthly_quantity_gp_pre_cv19 %>%
              filter(regional_unit %in% complete_gp) %>%
              regionalJointFcsts())
plan(sequential)

adreno_gp_fcsts %>%
  saveRDS("../data/adreno_gp_fcsts.rds")

adreno_gp_fcsts <- 
  read_rds("../data/adreno_gp_fcsts.rds")

```

* 2755.011 seconds 2021-01-13

## Discrepancies

### By Health Board

```{r, health-board-discrepancies}
best_model_hb <- 
  adreno_hb_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model_hb %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(adreno_hb_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(adreno_monthly_quantity_hb, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

### By GP Cluster

```{r, gp-cluster-discrepancies}
best_model_gp_cluster <- 
  adreno_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(adreno_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(adreno_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  # scale_color_gradientn(colours = rainbow(100))+
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

```{r, eval = FALSE}
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(adreno_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(adreno_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
  select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  estimate_profiles(1:6, models = c(1:3, 6)) %>% 
  compare_solutions(statistics = c("AIC", "BIC"))
```

### By GP Practice

```{r, gp-practice-discrepancies}
best_model_gp <- 
  adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp %>% 
  group_by(if_else(MAPE < 50, TRUE, FALSE)) %>% 
  count()

median(best_model_gp$MAPE)

acc_filter_value <- 50

best_model_gp_discrep <- 
  best_model_gp %>% 
  filter(MAPE <= acc_filter_value) %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(adreno_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(adreno_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

#### Latent profile analysis

```{r gp-lpa}
gp_lpa_fit <- 
  best_model_gp_discrep  %>%
  select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  estimate_profiles(1:6, models = c(1:3, 6))

gp_lpa_fit %>% 
  compare_solutions(statistics = c("AIC", "BIC"))

gp_lpa_fit %>% 
  compare_solutions(statistics = c("AIC", "BIC")) %>% 
  .[[1]] %>% 
  ggplot(aes(x = Classes, y = BIC, group = Model, colour = as.factor(Model))) +
  geom_line()

gp_lpa_fit %>%
  plot_profiles(x = ., rawdata = FALSE)
```

#### mplus

```{r, mplus-data-prep}
best_model_gp_discrep %>% 
  mutate(regional_unit = as.factor(regional_unit)) %>% 
  select(regional_unit, datename, discrepancy) %>% 
  filter(!is.na(discrepancy)) %>% # need to remove NA before pivoting to enable values_fill
  pivot_wider(names_from = datename, values_from = discrepancy, values_fill = -999) %>% 
  left_join(select(gp, c(practice_id, cluster)), by = c("regional_unit" = "practice_id")) %>% 
  mutate(regional_unit = as.factor(regional_unit),
         cluster = as.factor(cluster)) %>% 
  mutate(regional_unit = as.numeric(regional_unit),
         cluster = as.numeric(cluster)) %>% 
  select(cluster, regional_unit, everything()) %>% 
  write_csv(file = "../data/mplus/adreno_gp_discrep.csv", col_names = FALSE)

```

```{r, mplus-anlayses, eval=FALSE}
source("../r_scripts/functions/mplus_plotting.R")
# mplus_models <- MplusAutomation::readModels("../mplus_analyses/adreno_gp")

mplus_model_summaries <- 
  readModels("../mplus_analyses/adreno_gp", what = "summaries", quiet = TRUE)

best_mplus_model_summary <- 
  mplus_model_summaries %>% 
  flatten() %>% 
  map(2) %>% 
  bind_rows() %>% 
  filter(Estimator == "MLR" & AnalysisType == "mixture") %>% 
  arrange(BIC) %>% 
  slice(1)

best_mplus_model <- 
  readModels(paste0("../mplus_analyses/adreno_gp/", best_mplus_model_summary$Filename))

adreno_discrep_5_class_ml <- 
  readModels("../mplus_analyses/adreno_gp/adreno_discrep_5_class_ml.out")

best_mplus_model$class_counts

# mplus.view.plots("../mplus_analyses/adreno_gp/adreno_discrep_3_class_lgmm_ml.gh5")
mplus.plot.estimated_means("../mplus_analyses/adreno_gp/adreno_discrep_3_class_lgmm_ml.gh5")
```

#### kmeans

```{r, gp-kmeans}
gp_kmeans_data <- 
  best_model_gp_discrep %>%  
  mutate(regional_unit = as.factor(regional_unit)) %>% 
  select(regional_unit, datename, discrepancy) %>% 
  filter(!is.na(discrepancy)) %>% # need to remove NA before pivoting to enable values_fill
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  as_tibble() %>% 
  na.omit()

1:6 %>% 
  map_dfr(~as.data.frame(kmeans(x = gp_kmeans_data[2:6], centers = .x, nstart = 25)$cluster), 
          .id = "n_clusters") %>% 
  mutate(regional_unit = rep(gp_kmeans_data$regional_unit, 6)) %>% 
  pivot_wider(names_from = "n_clusters", id_cols = regional_unit,
              values_from = "kmeans(x = gp_kmeans_data[2:6], centers = .x, nstart = 25)$cluster")

1:6 %>% 
  map_dfr(~as.data.frame(kmeans(x = gp_kmeans_data[2:6],
                                centers = .x, nstart = 25)$centers), 
          .id = "n_clusters") %>% 
  rownames_to_column(var = "cluster") %>% 
  mutate(cluster = 
           str_remove_all(cluster, 
                          pattern = DOT %R% DOT %R% DOT %R% 
                            one_or_more(DIGIT))) %>% 
  pivot_longer(cols = starts_with("2020 "), names_to = "datename") %>% 
  ggplot(aes(x = yearmonth(datename), y = value, colour = as.factor(cluster))) + 
  geom_line() +
  facet_wrap(~n_clusters)

```
#### Comparing methods

```{r, eval=FALSE}
mplus_assignment <- 
  read_table("../mplus_analyses/adreno_gp/adreno_discrep_5_class_ml_cprob.txt", col_names = FALSE, na = "*") %>% 
  na.omit() %>% 
  .$X17

kmeans_assignment <- 
  kmeans(x = gp_kmeans_data[2:6], centers = 5, nstart = 25)$cluster

lpa_assignment <- 
  gp_lpa_fit$model_1_class_5$model$classification

df <- bind_cols(mplus_assignment, kmeans_assignment, lpa_assignment)

df %>% 
  ggplot(aes(x = mplus_assignment, y = kmeans_assignment, 
             colour = as.factor(mplus_assignment)))+
  geom_jitter(aes(shape = as.factor(kmeans_assignment)), alpha = .5)

df %>% 
  ggplot(aes(x = mplus_assignment, y = lpa_assignment, 
             colour = as.factor(kmeans_assignment))) +
  geom_jitter(alpha = .5)

```

### 2021-01-18 r_notebooks/exploring_hydroxychloroquine_sulphate.nb.Rmd
R analyses

@@
 ```{r, health-board-modelling}
-# plan(multisession)
-# with_progress(system.time(hcq_hb_cv_models <-
-#   regionalCV(data = hcq_monthly_quantity_hb_pre_cv19)))
-# plan(sequential)
-# 
-# hcq_hb_cv_models %>%
-#   saveRDS("../data/hcq_hb_cv_models.rds")
+plan(cluster)
+with_progress(system.time(hcq_hb_cv_models <-
+  regionalCV(data = hcq_monthly_quantity_hb_pre_cv19)))
+plan(sequential)
+
+hcq_hb_cv_models %>%
+  saveRDS("../data/hcq_hb_cv_models.rds")
 

### 2021-01-21 r_notebooks/preparing_ace_inhib.Rmd
Preparing data for clustering

---
title: "Ace inhibitors"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r ace-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

ace <- 
  read_rds("../data/presdata_updates_040121/presc_wales_ace-inhibitors.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid)) %>% 
  janitor::clean_names()

## All data sorted into monthly summary
ace_monthly_count <- 
  ace %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
ace_monthly_quantity_gp <- 
  countRegional(ace, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  ace_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
ace_monthly_quantity_gp <- 
  ace_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
ace_monthly_count_pre_cv19 <- 
  ace_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

ace_monthly_quantity_gp_pre_cv19 <- 
  ace_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
ace_monthly_count_pre_cv19 <- 
  ace_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(ace_monthly_count_pre_cv19)

ace_monthly_quantity_gp_pre_cv19 <- 
  ace_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(ace_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, ace-gp-practice-modelling}
plan(cluster)
system.time(ace_gp_cv_models <-
  ace_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

ace_gp_cv_models %>%
  saveRDS("../data/ace_gp_cv_models.rds")

ace_gp_cv_models <- 
  read_rds("../data/ace_gp_cv_models.rds")

ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r ace-gp-modelling-accuracy}
best_model_gp <- 
  ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r ace-gp-practice-forecasts}
plan(cluster)
system.time(ace_gp_fcsts <-
              ace_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

ace_gp_fcsts %>%
  saveRDS("../data/ace_gp_fcsts.rds")

ace_gp_fcsts <- 
  read_rds("../data/ace_gp_fcsts.rds")

```

## Discrepancies

```{r, ace-gp-practice-discrepancies}
best_model_gp <- 
  ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(ace_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(ace_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/ace_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-21 r_notebooks/preparing_adrenoceptor_agonists.Rmd
Preparing data for clustering

---
title: "Adrenoceptor agonists"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

* This data set seems to only have Salbutamol in it

```{r adreno-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

adreno <- 
  read_rds("../data/presdata_updates_040121/presc_wales_adrenoceptor-agonists.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename))) %>% 
  janitor::clean_names()

## All data sorted into monthly summary
adreno_monthly_count <- 
  adreno %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
adreno_monthly_quantity_gp <- 
  countRegional(adreno, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  adreno_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
adreno_monthly_quantity_gp <- 
  adreno_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
adreno_monthly_count_pre_cv19 <- 
  adreno_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

adreno_monthly_quantity_gp_pre_cv19 <- 
  adreno_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
adreno_monthly_count_pre_cv19 <- 
  adreno_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(adreno_monthly_count_pre_cv19)

adreno_monthly_quantity_gp_pre_cv19 <- 
  adreno_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(adreno_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, adreno-gp-practice-modelling}
plan(cluster)
system.time(adreno_gp_cv_models <-
  adreno_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

adreno_gp_cv_models %>%
  saveRDS("../data/adreno_gp_cv_models.rds")

adreno_gp_cv_models <- 
  read_rds("../data/adreno_gp_cv_models.rds")

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r adreno-gp-modelling-accuracy}
best_model_gp <- 
  adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r adreno-gp-practice-forecasts}
plan(cluster)
system.time(adreno_gp_fcsts <-
              adreno_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

adreno_gp_fcsts %>%
  saveRDS("../data/adreno_gp_fcsts.rds")

adreno_gp_fcsts <- 
  read_rds("../data/adreno_gp_fcsts.rds")

```

## Discrepancies

```{r, adreno-gp-practice-discrepancies}
best_model_gp <- 
  adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(adreno_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(adreno_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/adreno_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-21 r_notebooks/preparing_contra.Rmd
Preparing data for clustering

---
title: "Combined contraceptives"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r contra-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

contra <- 
  read_rds("../data/presdata_updates_040121/presc_wales_contra-combined.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practice_id))

## All data sorted into monthly summary
contra_monthly_count <- 
  contra %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
contra_monthly_quantity_gp <- 
  countRegional(contra, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  contra_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
contra_monthly_quantity_gp <- 
  contra_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
contra_monthly_count_pre_cv19 <- 
  contra_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

contra_monthly_quantity_gp_pre_cv19 <- 
  contra_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
contra_monthly_count_pre_cv19 <- 
  contra_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(contra_monthly_count_pre_cv19)

contra_monthly_quantity_gp_pre_cv19 <- 
  contra_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(contra_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, contra-gp-practice-modelling}
plan(cluster)
system.time(contra_gp_cv_models <-
  contra_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

contra_gp_cv_models %>%
  saveRDS("../data/contra_gp_cv_models.rds")

contra_gp_cv_models <- 
  read_rds("../data/contra_gp_cv_models.rds")

contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r contra-gp-modelling-accuracy}
best_model_gp <- 
  contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r contra-gp-practice-forecasts}
plan(cluster)
system.time(contra_gp_fcsts <-
              contra_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

contra_gp_fcsts %>%
  saveRDS("../data/contra_gp_fcsts.rds")

contra_gp_fcsts <- 
  read_rds("../data/contra_gp_fcsts.rds")

```

## Discrepancies

```{r, contra-gp-practice-discrepancies}
best_model_gp <- 
  contra_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(contra_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(contra_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/contra_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-21 r_notebooks/preparing_hcq.Rmd
Preparing data for clustering

---
title: "Hydroxychloroquine sulphate"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r hcq-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

hcq <- 
  read_rds("../data/presdata_updates_040121/presc_wales_HCQ.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid)) %>% 
  janitor::clean_names()

## All data sorted into monthly summary
hcq_monthly_count <- 
  hcq %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
hcq_monthly_quantity_gp <- 
  countRegional(hcq, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  hcq_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
hcq_monthly_quantity_gp <- 
  hcq_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
hcq_monthly_count_pre_cv19 <- 
  hcq_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

hcq_monthly_quantity_gp_pre_cv19 <- 
  hcq_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
hcq_monthly_count_pre_cv19 <- 
  hcq_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(hcq_monthly_count_pre_cv19)

hcq_monthly_quantity_gp_pre_cv19 <- 
  hcq_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(hcq_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, hcq-gp-practice-modelling}
plan(cluster)
system.time(hcq_gp_cv_models <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

hcq_gp_cv_models %>%
  saveRDS("../data/hcq_gp_cv_models.rds")

hcq_gp_cv_models <- 
  read_rds("../data/hcq_gp_cv_models.rds")

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r hcq-gp-modelling-accuracy}
best_model_gp <- 
  hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r hcq-gp-practice-forecasts}
plan(cluster)
system.time(hcq_gp_fcsts <-
              hcq_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

hcq_gp_fcsts %>%
  saveRDS("../data/hcq_gp_fcsts.rds")

hcq_gp_fcsts <- 
  read_rds("../data/hcq_gp_fcsts.rds")

```

## Discrepancies

```{r, hcq-gp-practice-discrepancies}
best_model_gp <- 
  hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(hcq_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(hcq_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/hcq_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-22 r_notebooks/preparing_azithro.Rmd
Preparing data for clustering

---
title: "Azithromycin"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r azithro-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

azithro <- 
  read_rds("../data/presdata_updates_040121/presc_wales_azithromycin.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

## All data sorted into monthly summary
azithro_monthly_count <- 
  azithro %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
azithro_monthly_quantity_gp <- 
  countRegional(azithro, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  azithro_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
azithro_monthly_quantity_gp <- 
  azithro_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
azithro_monthly_count_pre_cv19 <- 
  azithro_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

azithro_monthly_quantity_gp_pre_cv19 <- 
  azithro_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
azithro_monthly_count_pre_cv19 <- 
  azithro_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(azithro_monthly_count_pre_cv19)

azithro_monthly_quantity_gp_pre_cv19 <- 
  azithro_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(azithro_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, azithro-gp-practice-modelling}
plan(cluster)
system.time(azithro_gp_cv_models <-
  azithro_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

azithro_gp_cv_models %>%
  saveRDS("../data/azithro_gp_cv_models.rds")

azithro_gp_cv_models <- 
  read_rds("../data/azithro_gp_cv_models.rds")

azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r azithro-gp-modelling-accuracy}
best_model_gp <- 
  azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r azithro-gp-practice-forecasts}
plan(cluster)
system.time(azithro_gp_fcsts <-
              azithro_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

azithro_gp_fcsts %>%
  saveRDS("../data/azithro_gp_fcsts.rds")

azithro_gp_fcsts <- 
  read_rds("../data/azithro_gp_fcsts.rds")

```

## Discrepancies

```{r, azithro-gp-practice-discrepancies}
best_model_gp <- 
  azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(azithro_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(azithro_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/azithro_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-22 r_notebooks/preparing_cortico_resp.Rmd
Preparing data for clustering

---
title: "Respiratory corticosteroids"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r cortico-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

cortico <- 
  read_rds("../data/presdata_updates_040121/presc_wales_cortico-resp.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

## All data sorted into monthly summary
cortico_monthly_count <- 
  cortico %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
cortico_monthly_quantity_gp <- 
  countRegional(cortico, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  cortico_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
cortico_monthly_quantity_gp <- 
  cortico_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
cortico_monthly_count_pre_cv19 <- 
  cortico_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

cortico_monthly_quantity_gp_pre_cv19 <- 
  cortico_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
cortico_monthly_count_pre_cv19 <- 
  cortico_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(cortico_monthly_count_pre_cv19)

cortico_monthly_quantity_gp_pre_cv19 <- 
  cortico_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(cortico_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, cortico-gp-practice-modelling}
plan(cluster)
system.time(cortico_gp_cv_models <-
  cortico_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

cortico_gp_cv_models %>%
  saveRDS("../data/cortico_gp_cv_models.rds")

cortico_gp_cv_models <- 
  read_rds("../data/cortico_gp_cv_models.rds")

cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r cortico-gp-modelling-accuracy}
best_model_gp <- 
  cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r cortico-gp-practice-forecasts}
plan(cluster)
system.time(cortico_gp_fcsts <-
              cortico_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

cortico_gp_fcsts %>%
  saveRDS("../data/cortico_gp_fcsts.rds")

cortico_gp_fcsts <- 
  read_rds("../data/cortico_gp_fcsts.rds")

```

## Discrepancies

```{r, cortico-gp-practice-discrepancies}
best_model_gp <- 
  cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(cortico_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(cortico_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/cortico_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-22 r_notebooks/preparing_famot.Rmd
Preparing data for clustering

---
title: "Respiratory famotsteroids"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r famot-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

famot <- 
  read_rds("../data/presdata_updates_040121/presc_wales_famotidine.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

## All data sorted into monthly summary
famot_monthly_count <- 
  famot %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
famot_monthly_quantity_gp <- 
  countRegional(famot, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  famot_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
famot_monthly_quantity_gp <- 
  famot_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
famot_monthly_count_pre_cv19 <- 
  famot_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

famot_monthly_quantity_gp_pre_cv19 <- 
  famot_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
famot_monthly_count_pre_cv19 <- 
  famot_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(famot_monthly_count_pre_cv19)

famot_monthly_quantity_gp_pre_cv19 <- 
  famot_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(famot_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, famot-gp-practice-modelling}
plan(cluster)
system.time(famot_gp_cv_models <-
  famot_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

famot_gp_cv_models %>%
  saveRDS("../data/famot_gp_cv_models.rds")

famot_gp_cv_models <- 
  read_rds("../data/famot_gp_cv_models.rds")

famot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

famot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

famot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r famot-gp-modelling-accuracy}
best_model_gp <- 
  famot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r famot-gp-practice-forecasts}
plan(cluster)
system.time(famot_gp_fcsts <-
              famot_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

famot_gp_fcsts %>%
  saveRDS("../data/famot_gp_fcsts.rds")

famot_gp_fcsts <- 
  read_rds("../data/famot_gp_fcsts.rds")

```

## Discrepancies

```{r, famot-gp-practice-discrepancies}
best_model_gp <- 
  famot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(famot_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(famot_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/famot_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-22 r_notebooks/preparing_nicot.Rmd
Preparing data for clustering

---
title: "Respiratory nicotsteroids"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r nicot-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

nicot <- 
  read_rds("../data/presdata_updates_040121/presc_wales_nicotine.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

## All data sorted into monthly summary
nicot_monthly_count <- 
  nicot %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
nicot_monthly_quantity_gp <- 
  countRegional(nicot, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  nicot_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
nicot_monthly_quantity_gp <- 
  nicot_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
nicot_monthly_count_pre_cv19 <- 
  nicot_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

nicot_monthly_quantity_gp_pre_cv19 <- 
  nicot_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
nicot_monthly_count_pre_cv19 <- 
  nicot_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(nicot_monthly_count_pre_cv19)

nicot_monthly_quantity_gp_pre_cv19 <- 
  nicot_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(nicot_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, nicot-gp-practice-modelling}
plan(cluster)
system.time(nicot_gp_cv_models <-
  nicot_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

nicot_gp_cv_models %>%
  saveRDS("../data/nicot_gp_cv_models.rds")

nicot_gp_cv_models <- 
  read_rds("../data/nicot_gp_cv_models.rds")

nicot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

nicot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

nicot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r nicot-gp-modelling-accuracy}
best_model_gp <- 
  nicot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r nicot-gp-practice-forecasts}
plan(cluster)
system.time(nicot_gp_fcsts <-
              nicot_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

nicot_gp_fcsts %>%
  saveRDS("../data/nicot_gp_fcsts.rds")

nicot_gp_fcsts <- 
  read_rds("../data/nicot_gp_fcsts.rds")

```

## Discrepancies

```{r, nicot-gp-practice-discrepancies}
best_model_gp <- 
  nicot_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(nicot_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(nicot_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/nicot_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-22 r_notebooks/preparing_nsaid.Rmd
Preparing data for clustering

---
title: "NSAIDs"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r nsaid-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

nsaid <- 
  read_rds("../data/presdata_updates_040121/presc_wales_NSAIDs.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practice_id))

## All data sorted into monthly summary
nsaid_monthly_count <- 
  nsaid %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
nsaid_monthly_quantity_gp <- 
  countRegional(nsaid, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  nsaid_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
nsaid_monthly_quantity_gp <- 
  nsaid_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
nsaid_monthly_count_pre_cv19 <- 
  nsaid_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

nsaid_monthly_quantity_gp_pre_cv19 <- 
  nsaid_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
nsaid_monthly_count_pre_cv19 <- 
  nsaid_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(nsaid_monthly_count_pre_cv19)

nsaid_monthly_quantity_gp_pre_cv19 <- 
  nsaid_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(nsaid_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, nsaid-gp-practice-modelling}
plan(cluster)
system.time(nsaid_gp_cv_models <-
  nsaid_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

nsaid_gp_cv_models %>%
  saveRDS("../data/nsaid_gp_cv_models.rds")

nsaid_gp_cv_models <- 
  read_rds("../data/nsaid_gp_cv_models.rds")

nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r nsaid-gp-modelling-accuracy}
best_model_gp <- 
  nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r nsaid-gp-practice-forecasts}
plan(cluster)
system.time(nsaid_gp_fcsts <-
              nsaid_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

nsaid_gp_fcsts %>%
  saveRDS("../data/nsaid_gp_fcsts.rds")

nsaid_gp_fcsts <- 
  read_rds("../data/nsaid_gp_fcsts.rds")

```

## Discrepancies

```{r, nsaid-gp-practice-discrepancies}
best_model_gp <- 
  nsaid_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(nsaid_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(nsaid_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/nsaid_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-22 r_notebooks/preparing_paracet.Rmd
Preparing data for clustering

---
title: "Respiratory paracetsteroids"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r paracet-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

paracet <- 
  read_rds("../data/presdata_updates_040121/presc_wales_paracetamol.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

## All data sorted into monthly summary
paracet_monthly_count <- 
  paracet %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
paracet_monthly_quantity_gp <- 
  countRegional(paracet, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  paracet_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
paracet_monthly_quantity_gp <- 
  paracet_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
paracet_monthly_count_pre_cv19 <- 
  paracet_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

paracet_monthly_quantity_gp_pre_cv19 <- 
  paracet_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
paracet_monthly_count_pre_cv19 <- 
  paracet_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(paracet_monthly_count_pre_cv19)

paracet_monthly_quantity_gp_pre_cv19 <- 
  paracet_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(paracet_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, paracet-gp-practice-modelling}
plan(cluster)
system.time(paracet_gp_cv_models <-
  paracet_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

paracet_gp_cv_models %>%
  saveRDS("../data/paracet_gp_cv_models.rds")

paracet_gp_cv_models <- 
  read_rds("../data/paracet_gp_cv_models.rds")

paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r paracet-gp-modelling-accuracy}
best_model_gp <- 
  paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r paracet-gp-practice-forecasts}
plan(cluster)
system.time(paracet_gp_fcsts <-
              paracet_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

paracet_gp_fcsts %>%
  saveRDS("../data/paracet_gp_fcsts.rds")

paracet_gp_fcsts <- 
  read_rds("../data/paracet_gp_fcsts.rds")

```

## Discrepancies

```{r, paracet-gp-practice-discrepancies}
best_model_gp <- 
  paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(paracet_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(paracet_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/paracet_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-22 r_notebooks/preparing_vitd.Rmd
Preparing data for clustering

---
title: "Respiratory vitdsteroids"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r vitd-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

vitd <- 
  read_rds("../data/presdata_updates_040121/presc_wales_vitamind.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

## All data sorted into monthly summary
vitd_monthly_count <- 
  vitd %>% 
  group_by(datename) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>% 
  as_tsibble(index = datename)

## Monthly summary by GP
vitd_monthly_quantity_gp <- 
  countRegional(vitd, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
gp_missing <- 
  vitd_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
vitd_monthly_quantity_gp <- 
  vitd_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove)

## Sort into monthly count data pre-lockdown (March 2020) as training data
vitd_monthly_count_pre_cv19 <- 
  vitd_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

vitd_monthly_quantity_gp_pre_cv19 <- 
  vitd_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
vitd_monthly_count_pre_cv19 <- 
  vitd_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(vitd_monthly_count_pre_cv19)

vitd_monthly_quantity_gp_pre_cv19 <- 
  vitd_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(vitd_monthly_quantity_gp_pre_cv19)

```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, vitd-gp-practice-modelling}
plan(cluster)
system.time(vitd_gp_cv_models <-
  vitd_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

vitd_gp_cv_models %>%
  saveRDS("../data/vitd_gp_cv_models.rds")

vitd_gp_cv_models <- 
  read_rds("../data/vitd_gp_cv_models.rds")

vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r vitd-gp-modelling-accuracy}
best_model_gp <- 
  vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r vitd-gp-practice-forecasts}
plan(cluster)
system.time(vitd_gp_fcsts <-
              vitd_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

vitd_gp_fcsts %>%
  saveRDS("../data/vitd_gp_fcsts.rds")

vitd_gp_fcsts <- 
  read_rds("../data/vitd_gp_fcsts.rds")

```

## Discrepancies

```{r, vitd-gp-practice-discrepancies}
best_model_gp <- 
  vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(vitd_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(vitd_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/vitd_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-01-22 r_notebooks/preparing_nsaid.Rmd
Typos

@@
   mutate(datename = dmy(paste0("28-", datename)),
-         practice_id = as_factor(practice_id))
+         practice_id = as_factor(practiceid))
 

### 2021-01-25 r_notebooks/preparing_oac_prop.Rmd
Preparing data for clustering

---
title: "Respiratory oacsteroids"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r oac-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

oac <- 
  read_rds("../data/presdata_updates_040121/presc_wales_OAC.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = yearmonth(dmy(paste0("28-", datename))),
         practice_id = as_factor(practice_id))

warf <- "0208020V0"

## All data sorted into monthly summary
oac_monthly_prop <- 
  oac %>% 
  group_by(datename, bnfchem) %>% 
  summarise(n = sum(quantity)) %>% 
  mutate(n = 100 * n / sum(n)) %>%  # make it a percentage rather than proportion
  filter(bnfchem == warf) %>% 
  ungroup() %>%
  as_tsibble(index = datename)

## Monthly summary by GP
oac_monthly_prop_gp <- 
  oac %>% 
  group_by(practice_id, datename, bnfchem) %>% 
  summarise(sum_n = sum(quantity), .groups = "drop_last") %>% 
  mutate(p_war = 100 * sum_n / sum(sum_n),
         sum_oac = sum(sum_n)) %>% 
  filter(bnfchem == as_name(warf)) %>% 
  ungroup() %>% 
  transmute(regional_unit = as.factor(practice_id),
            datename = datename,
            n = p_war) %>%
  ungroup() %>%
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

oac_monthly_prop_gp_pre_cv19 <- 
  oac_monthly_prop_gp %>% 
  filter(datename < yearmonth("2020 March"))

oac_monthly_prop_gp_pre_cv19 <- 
  oac_monthly_prop_gp_pre_cv19 %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  pivot_longer(cols = `2015 Jan`:`2020 Feb`, 
               names_to = "datename", values_to = "n", 
               values_drop_na = FALSE) %>% 
  mutate(datename = yearmonth(datename)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(oac_monthly_prop_gp_pre_cv19) %>% 
  filter(!regional_unit %in% # Remove those with <62 months data
           (oac_monthly_prop_gp_pre_cv19 %>% 
              as_tibble %>% 
              ungroup() %>% 
              group_by(regional_unit) %>% 
              count() %>% 
              filter(n < 62) %>% 
              .$regional_unit) &
           !regional_unit %in% # Remove bottom 10% GPs by total oac volume 
           (oac %>% 
              group_by(practice_id) %>% 
              summarise(tot_quant = sum(quantity)) %>% 
              arrange(tot_quant) %>% 
              slice_tail(prop = .1))) 
```

```{r, eval = FALSE}
oac_monthly_prop_gp_pre_cv19 %>% 
  autoplot() +
  theme(legend.position = "none")
```

## Modelling

```{r, oac-gp-practice-modelling}
plan(cluster)
system.time(oac_gp_cv_models <-
  oac_monthly_prop_gp_pre_cv19 %>%
                  regionalCVBound(init = 48, step = 3))
plan(sequential)

oac_gp_cv_models %>%
  saveRDS("../data/oac_gp_cv_models.rds")

oac_gp_cv_models <- 
  read_rds("../data/oac_gp_cv_models.rds")

oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  ggplot(aes(x = reorder(.model, MAPE, mean), y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_cartesian(ylim = c(0,100))

```

```{r oac-gp-modelling-accuracy}
best_model_gp <- 
  oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r oac-gp-practice-forecasts}
plan(cluster)
system.time(oac_gp_fcsts <-
              oac_monthly_prop_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcstsBound(h = "6 months"))
plan(sequential)

oac_gp_fcsts %>%
  saveRDS("../data/oac_gp_fcsts.rds")

oac_gp_fcsts <- 
  read_rds("../data/oac_gp_fcsts.rds")

```

## Discrepancies

```{r, oac-gp-practice-discrepancies}
best_model_gp <- 
  oac_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_prop_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean) %>% 
  ungroup()

best_model_gp_discrep %>% 
  saveRDS("../data/differences/oac_discreps.rds")

best_model_gp_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

```

### 2021-02-16 r_notebooks/clustering_differences.Rmd
Comparing clustering methods

---
title: "Clustering differences"
author: "Will A. S. Hardy"
date: "27/01/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(tsibble)
library(tidyLPA)
library(future)
library(furrr)
library(tidymodels)
library(workflows)
library(tune)

knitr::opts_chunk$set(echo = TRUE)

set.seed(32)

gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid),
         dispensing = as_factor(dispensing),
         hboard = as_factor(hboard)) %>% 
  ungroup() %>% 
  janitor::clean_names()

differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug)) %>% 
  select(drug, regional_unit, datename, discrepancy)

```

## Data cleaning

```{r, data-problem-values, warning=FALSE}
differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  psych::describeBy(group = "drug", fast = TRUE)
```

* Problem with `oac` data

```{r, data-which-problem}
differences %>% 
  filter(drug == "oac" & 
           (is.na(discrepancy) | is.nan(discrepancy) | is.infinite(discrepancy))) %>% 
  group_by(datename) %>% 
  count()

differences %>% 
  filter(drug == "oac" & 
           (is.na(discrepancy) | is.nan(discrepancy) | is.infinite(discrepancy))) %>% 
  group_by(drug, regional_unit) %>% 
  count()
```

* Missing/inappropriate data in five practices (all in covid months)
* Removed these practices from the `oac` data

```{r, data-cleaning}
differences <- 
  differences %>% 
  anti_join(y = differences %>% 
              filter(drug == "oac" & 
                       (is.na(discrepancy) |
                          is.nan(discrepancy) | 
                          is.infinite(discrepancy))) %>% 
              group_by(drug, regional_unit) %>% 
              count(), 
            by = c("drug", "regional_unit"))
```

## k-means

### Elbow plots

```{r, k-means-elbow}
differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  nest_by(drug) %>% 
  mutate(k_means = list(map(.x = 1:10, 
                           .f = ~kmeans(x = data[2:7], centers = .x, 
                                        nstart = 5, iter.max = 50)))) %>% 
  mutate(tot_within_ss = list(map_dbl(k_means, "tot.withinss")), 
         clusters = list(map(k_means, "cluster")),
         n_clusters = list(map_dbl(clusters, max))) %>% 
  summarise(tot_within_ss = tot_within_ss,
            n_clusters = n_clusters) %>% 
  ggplot(aes(x = n_clusters, y = tot_within_ss)) +
  geom_line() +
  facet_wrap(~drug, scales = "free") +
  scale_x_continuous(breaks = seq(0, 10, by = 2))
```

* Visual inspections of elbow plots WH 2021-01-27
  * ace 3
  * adreno 3
  * azithro 3
  * contra 3
  * cortico 4
  * hcq 4
  * nsaid 3
  * oac 3
  * paracet 4
  * vitd 4

```{r, k-means-summary-plots}
drugs <- unique(as.character(differences$drug))
n_cluster <- c(3,3,3,3,4,4,3,3,4,4)

differences_wide <- 
  differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy)

best_k_means_fits <- 
  map2(.x = drugs,
       .y = n_cluster,
       .f = ~kmeans(x = filter(differences_wide, drug == .x)[3:8],
                    centers = .y,
                    nstart = 5, iter.max = 50))

best_k_means_fits %>%
  set_names(nm = drugs) %>% 
  transpose() %>% 
  pluck("size") %>% 
    modify_depth(.depth = 1, 
               .f = ~rownames_to_column(.data = as.data.frame(.), 
                                        var = "cluster")) %>% 
  bind_rows(.id = "drug") %>% 
  rename(.data = ., n = `.`) %>% 
  pivot_wider(names_from = cluster, values_from = n) %>% 
  knitr::kable()

best_k_means_fits %>%
  set_names(nm = drugs) %>% 
  transpose() %>% 
  pluck("centers") %>% 
  modify_depth(.depth = 1, 
               .f = ~rownames_to_column(.data = as.data.frame(.), 
                                        var = "cluster")) %>% 
  bind_rows(.id = "drug") %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`,
               names_to = "datename", values_to = "discrepancy") %>% 
  mutate(datename = yearmonth(datename)) %>% 
  ggplot(aes(x = datename, 
             y = discrepancy,
             group = as.factor(cluster),
             colour = as.factor(cluster))) + 
  geom_line() +
  facet_wrap(~drug, scales = "free") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# best_k_means_fits %>% 
#   set_names(drugs) %>% 
#   transpose() %>%
#   pluck("cluster")

```

## Latent profile analysis

```{r, lpa-models-nested, include=FALSE}
tictoc::tic()
lpa_analysis <- 
  differences_wide %>% 
  anti_join(y = differences_wide %>% # These cause computation issues. Look at separately.
              filter(drug == "ace" & `2020 Jul` < -50), 
            by = c("drug", "regional_unit")) %>%

  nest_by(drug) %>% 
  mutate(lpa_models = 
           list(estimate_profiles(df = data,
                                  select_vars = c("2020 Mar", "2020 Apr", 
                                                  "2020 May", "2020 Jun", 
                                                  "2020 Jul", "2020 Aug"),
                                  n_profiles = 1:8, 
                                  models = c(1:3))),
         lpa_fits = 
           list(compare_solutions(lpa_models, 
                                  statistics = c("BIC", "AIC", "SABIC", "BLRT_p",
                                                 "prob_min", "Entropy"))),
         lpa_plots = list(plot_profiles(lpa_models, 
                                        rawdata = FALSE, 
                                        sd = FALSE)),
         best_lpa_rn = as.numeric(list(lpa_fits$AHP)),
         best_lpa_fit = list(lpa_fits$fits[lpa_fits$AHP,]),
         best_lpa_model = flatten(list(lpa_models[lpa_fits$AHP])),
         best_lpa_data = list(get_data(best_lpa_model)),
         classes = list(flatten(flatten(list(lpa_models[lpa_fits$AHP])))$model$classification),
         class_count = list(table(flatten(flatten(list(lpa_models[lpa_fits$AHP])))$model$classification)),
         lpa_class = list(bind_cols(drug = drug, 
                                    regional_unit = data$regional_unit, 
                                    lpa_class = classes)))
tictoc::toc()
```

```{r, lpa-best-model-plot, include=FALSE}
lpa_analysis <- 
  lpa_analysis %>% 
  mutate(best_lpa_model_plot = list(plot_profiles(best_lpa_model, 
                                                  rawdata = FALSE, 
                                                  sd = FALSE)),
         best_lpa_model_plot_lab = list(best_lpa_model_plot + 
                                          labs(title = drug)),
         best_lpa_cprob = list(select(best_lpa_model$dff,
                                      starts_with("CPROB"), Class)))

lpa_analysis %>% 
  pluck("best_lpa_cprob") %>% 
  set_names(drugs)

```

```{r, lpa-best-model-plot-2}
lpa_analysis$lpa_fits

lpa_analysis %>% 
  pluck("class_count") %>% 
  set_names(drugs) %>% 
  bind_rows(.id = "drug")

```

```{r}
lpa_analysis$lpa_fits %>% 
  set_names(drugs) %>% 
  pluck("cortico")

lpa_analysis$lpa_models %>% 
  set_names(drugs) %>% 
  pluck("cortico")

lpa_analysis$lpa_models %>% 
  set_names(drugs) %>% 
  pluck("cortico") %>% 
  pluck("model_2_class_6") %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)
```

```{r}
lpa_analysis$lpa_fits %>% 
  set_names(drugs) %>% 
  pluck("oac")

lpa_analysis$lpa_models %>% 
  set_names(drugs) %>% 
  pluck("oac")

lpa_analysis$lpa_models %>% 
  set_names(drugs) %>% 
  pluck("oac") %>% 
  pluck("model_2_class_6") %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)
```

```{r, lpa-best-model-class-assignment}
lpa_analysis %>% 
  pluck("lpa_class") %>% 
  bind_rows() %>% 
  pivot_wider(names_from = drug, names_prefix = "lpa_class_",
              values_from = lpa_class)

lpa_analysis %>% 
  pluck("lpa_class") %>% 
  bind_rows() %>% 
  pivot_wider(names_from = drug, names_prefix = "lpa_class_",
              values_from = lpa_class) %>% 
  psych::describe()

```

### Outliers

```{r, lpa-models, eval=FALSE}
drugs <- unique(as.character(differences$drug))

differences_wide <- 
  differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy)

system.time(differences_wide %>% 
              filter(drug == "oac") %>% 
              ungroup() %>% 
              select(`2020 Mar`:`2020 Aug`) %>% 
              estimate_profiles(df = ., n_profiles = 1:5, models = c(1:3, 6)))

lpaProfiles <- function(data, filter){
  data %>% 
    filter(drug == filter) %>% 
    ungroup() %>% 
    select(`2020 Mar`:`2020 Aug`) %>% 
    estimate_profiles(df = ., n_profiles = 1:5, models = c(1:3, 6))
}

plan(cluster)
system.time(lpa_fits <- 
              future_map(.x = drugs,
                         .f = ~lpaProfiles(differences_wide, .x)))
plan(sequential)

lpa_fits %>% 
  saveRDS("../data/models/lpa_fits.rds")
```

```{r, seperate-lpa-models, eval=FALSE}
lpaProfiles <- function(data, filter){
  data %>% 
    filter(drug == filter) %>% 
    ungroup() %>% 
    select(`2020 Mar`:`2020 Aug`) %>% 
    estimate_profiles(df = ., n_profiles = 1:6, models = c(1:3, 6))
}

tictoc::tic()
system.time(oac_lpa <- lpaProfiles(differences_wide, "oac"))
print("step 1")
print("step 2")
system.time(azithro_lpa <- lpaProfiles(differences_wide, "azithro"))
print("step 3")
system.time(contra_lpa <- lpaProfiles(differences_wide, "contra"))
print("step 4")
system.time(cortico_lpa <- lpaProfiles(differences_wide, "cortico"))
print("step 5")
system.time(hcq_lpa <- lpaProfiles(differences_wide, "hcq"))
print("step 6")
system.time(nsaid_lpa <- lpaProfiles(differences_wide, "nsaid"))
print("step 7")
system.time(vitd_lpa <- lpaProfiles(differences_wide, "vitd"))
print("step 8")
system.time(paracet_lpa <- lpaProfiles(differences_wide, "paracet"))
print("step 9")
#system.time(adreno_lpa <- lpaProfiles(differences_wide, "adreno"))
system.time(ace_lpa <- differences_wide %>%
              filter(drug == "ace") %>% 
              filter(`2020 Jul` > -50) %>% # Outliers causing computation problems
              estimate_profiles(df = .[3:8], 
                                n_profiles = 1:6, 
                                models = c(1:3, 6)))
print("step 10")
lpa_sep_fits <- list(ace_lpa, azithro_lpa, contra_lpa, cortico_lpa, 
                     hcq_lpa, nsaid_lpa, oac_lpa, paracet_lpa, vitd_lpa)
tictoc::toc()

```

```{r, adreno-lpa, eval=FALSE}
system.time(differences_wide %>% 
              filter(drug == "adreno") %>% 
              # filter(`2020 Jul` > -50) %>% # Outliers causing computation problems
              estimate_profiles(df = .[c(3:8)], 
                                n_profiles = 1:5, 
                                models = c(1:3,6)) %>% 
              plot_profiles(rawdata = FALSE))

## Models 1:3
# 2708.712 secs with df = .[c(3:5)]
# 63.237 secs with df = .[c(3:6)]
# 1101.290 secs with df = .[c(3:7)]
# 1618.723 secs with df = .[c(3:8)]
## Models 1:3, 6
# 2338.966 secs with df = .[c(3:8)]

differences_wide %>% 
  filter(drug == "adreno") %>% 
  ggplot(aes(x = `2020 May`)) +
  geom_histogram()
```

## Logistic regression

### LPA profiles

```{r}
lpa_analysis %>% 
  pluck("lpa_class") %>% 
  bind_rows() %>% 
  mutate(lpa_class = as_factor(lpa_class)) %>% 
  left_join(filter(gp, year == 2020), by = c("regional_unit" = "practice_id")) %>% 
  select(drug, regional_unit, lpa_class, ngp, dispensing, where(is.numeric)) %>% 
  select(-c(easting, northing, regional_unit, year)) %>% 
  nest_by(drug) %>% 
  mutate(mod = list(glm(lpa_class ~ ., data = data, family = "binomial"))) %>% 
  summarise(broom::glance(mod), 
            list(summary(mod))) %>% 
  pluck("list(summary(mod))") %>% 
  set_names(drugs)

```

## Tidymodels

### LPA profiles

```{r, preparing-tidymodels-data}
diff_data <- 
  lpa_analysis %>% 
  pluck("lpa_class") %>% 
  bind_rows() %>% 
  mutate(lpa_class = as_factor(lpa_class)) %>% 
  left_join(filter(gp, year == 2020), by = c("regional_unit" = "practice_id")) %>% 
  select(drug, regional_unit, lpa_class, ngp, dispensing, where(is.numeric)) %>% 
  select(-c(easting, northing, regional_unit, year)) %>% 
  filter(drug == "ace") %>% 
  mutate(lpa_class = as.factor(as.numeric(lpa_class)))

diff_data_split <- 
  diff_data %>% 
  initial_split(prop = 2/3)

diff_data_train <- training(diff_data_split)
diff_data_test <- testing(diff_data_split)
diff_data_cv <- vfold_cv(diff_data_train)

diff_data_train %>% 
  write_csv("../data/weka/ace_train.csv")
diff_data_test %>% 
  write_csv("../data/weka/ace_test.csv")

```

```{r}
diff_recipe <- 
  recipe(lpa_class ~ ., data = select(ungroup(diff_data_train), -drug)) %>% 
  step_normalize(all_numeric())
```

```{r}
lr_model <- 
  # specify that the model is a random forest
  logistic_reg() %>%
  # select the engine/package that underlies the model
  set_engine("glm") %>%
  # choose either the continuous regression or binary classification mode
  set_mode("classification")

rf_model <- 
  # specify that the model is a random forest
  rand_forest() %>%
  # specify that the `mtry` parameter needs to be tuned
  set_args(mtry = tune(), trees = tune()) %>%
  # select the engine/package that underlies the model
  set_engine("ranger", importance = "impurity") %>%
  # choose either the continuous regression or binary classification mode
  set_mode("classification") 
```

```{r}
lr_workflow <- 
  workflow() %>% 
  add_recipe(diff_recipe) %>% 
  add_model(lr_model)

rf_workflow <- workflow() %>%
  # add the recipe
  add_recipe(diff_recipe) %>%
  # add the model
  add_model(rf_model)
```

```{r}
rf_grid <- expand.grid(mtry = c(3,4,5), trees = c(100, 500))
rf_tune_results <- 
  rf_workflow %>% 
  tune_grid(resamples = diff_data_cv,
            grid = rf_grid,
            metrics = metric_set(accuracy, roc_auc, spec, sens))

rf_tune_results %>% 
  collect_metrics()

lr_grid <- expand.grid(mtry = c(3,4,5))
lr_tune_results <- 
  lr_workflow %>% 
  tune_grid(resamples = diff_data_cv,
            metrics = metric_set(accuracy, roc_auc, spec, sens))

lr_tune_results %>% 
  collect_metrics()

```

### 2021-02-16 r_notebooks/differences_lpa.Rmd
LPA on differmces data

---
title: "Differences LPA"
author: "Will A. S. Hardy"
date: "27/01/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(tsibble)
library(tidyLPA)
library(future)
library(furrr)
library(tidymodels)
library(workflows)
library(tune)

knitr::opts_chunk$set(echo = TRUE)

set.seed(32)

gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid),
         dispensing = as_factor(dispensing),
         hboard = as_factor(hboard)) %>% 
  ungroup() %>% 
  janitor::clean_names()

differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug)) %>% 
  select(drug, regional_unit, datename, discrepancy)

drugs <- unique(as.character(differences$drug))

```

## Data cleaning

```{r, data-problem-values, warning=FALSE}
differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  psych::describeBy(group = "drug", fast = TRUE)
```

* Problem with `oac` data
* Infinite values have been calculated when something has been divided by zero. Is this when the total prescribing of oac has been zero, thus wafarin as a percentage of 0 is Inf?

```{r, data-which-problem}
differences %>% 
  filter(drug == "oac" & 
           (is.na(discrepancy) | is.nan(discrepancy) | is.infinite(discrepancy))) %>% 
  group_by(datename) %>% 
  count()

differences %>% 
  filter(drug == "oac" & 
           (is.na(discrepancy) | is.nan(discrepancy) | is.infinite(discrepancy))) %>% 
  group_by(drug, regional_unit) %>% 
  count()
```

* Missing/inappropriate data in five practices
* Removed these practices from the `oac` data

```{r, data-cleaning}
differences <- 
  differences %>% 
  anti_join(y = differences %>% 
              filter(drug == "oac" & 
                       (is.na(discrepancy) |
                          is.nan(discrepancy) | 
                          is.infinite(discrepancy))) %>% 
              group_by(drug, regional_unit) %>% 
              count(), 
            by = c("drug", "regional_unit"))

differences_wide <- 
  differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy)
```

## Latent profile analysis

When conducting LPA, several models are specified and then evaluated. Model selection, including class enumeration, should not be based solely on statistical criteria, but also the statistical adequacy and substantive meaning of the solutions [@Marsh2009; @Morin2016]. Indeed, relying solely on statistical criteria in large samples may lead to the inability to identify an "optimal solution" as model fit increases as the number of classes increase [@Morin2009].

In this study we inspected the Bayesian Information Criterion [BIC; @someone], the bootstrapped likelihood ratio test [BLRT; @someone], the sample adjusted BIC [SABIC; @someone], and an analytical hierarchy proposed by Akogul & Erisoglu [-@Akogul2017] which evaluates five information criteria simultaneously.

* Entropy

### ace

```{r, ace-lpa}
ace_lpa <- 
  differences_wide %>% 
  filter(drug == "ace") %>% 
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = 1:8,
                    models = c(1:3))
```

```{r, ace-fits}
ace_lpa
compare_solutions(ace_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p"))
```

```{r}
ace_lpa %>%
  plot_profiles(rawdata = FALSE, sd = FALSE)

differences_wide %>% 
  filter(drug == "ace") %>% 
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = c(4,5,6,8),
                    models = 2) %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)
```

*

```{r}
ace_lpa$model_2_class_5 %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)

ace_lpa$model_2_class_5 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  ggplot(aes(x = datename, y = difference, group = rowname, colour = rowname)) +
  geom_line(alpha = .1) +
  facet_wrap(~Class) +
  theme(legend.position = "none")

ace_lpa$model_2_class_5 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  mutate(Class = as.factor(Class)) %>% 
  ggplot(aes(x = datename, y = difference, colour = Class)) +
  geom_boxplot() +
  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75)) +
  theme(legend.position = "none")

df <- 
  ace_lpa$model_2_class_5 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  mutate(Class = as.factor(Class))

df %>% 
  ggplot(aes(x = datename, y = difference)) +
  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .1) +
  stat_summary(fun = "mean") +
  facet_wrap(~Class) +
  theme(legend.position = "none")

ace_lpa$model_2_class_5 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  # pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
  #              names_to = "datename") %>% 
  mutate(Class = as.factor(Class)) %>% 
  aov(`2020 Mar` ~ Class, data = .) %>% 
  # summary() %>% 
  TukeyHSD()
```

### adreno

```{r, adreno-lpa}
adreno_lpa <- 
  differences_wide %>% 
  filter(drug == "adreno") %>% 
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = 1:8,
                    models = c(1:3))
```

```{r}
adreno_lpa
compare_solutions(adreno_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p"))
```

```{r}
adreno_lpa %>%
  plot_profiles(rawdata = FALSE, sd = FALSE)

differences_wide %>% 
  filter(drug == "adreno") %>% 
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = c(4,5,6,8),
                    models = 2) %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)
```

* Different fit statistics suggest different models best fit the data. Increasing the number of classes does not change the shapes of the profiles, it merely splits existing profiles into smaller units.
* Retain the five class solution based on principle of parsimony and interpretability.

```{r}
adreno_lpa$model_2_class_5 %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)

adreno_lpa$model_2_class_5 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  ggplot(aes(x = datename, y = difference, group = rowname, colour = rowname)) +
  geom_line(alpha = .1) +
  facet_wrap(~Class) +
  theme(legend.position = "none")

adreno_lpa$model_2_class_5 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  mutate(Class = as.factor(Class)) %>% 
  ggplot(aes(x = datename, y = difference, colour = Class)) +
  geom_boxplot() +
  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75)) +
  theme(legend.position = "none")

df <- 
  adreno_lpa$model_2_class_5 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  mutate(Class = as.factor(Class))

df %>% 
  ggplot(aes(x = datename, y = difference)) +
  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .1) +
  stat_summary(fun = "mean") +
  facet_wrap(~Class) +
  theme(legend.position = "none")

adreno_lpa$model_2_class_5 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  # pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
  #              names_to = "datename") %>% 
  mutate(Class = as.factor(Class)) %>% 
  aov(`2020 Mar` ~ Class, data = .) %>% 
  # summary() %>% 
  TukeyHSD()
```
### azithro

### contra

### cortico

### hcq

### nsaid

### oac

```{r, oac-lpa}
oac_lpa <- 
  differences_wide %>% 
  filter(drug == "oac") %>% 
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = 1:8,
                    models = c(1:3))
```

```{r}
compare_solutions(oac_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p"))
```

```{r}
oac_lpa %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)
```

```{r}
oac_lpa$model_3_class_2 %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)

oac_lpa$model_3_class_2 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  ggplot(aes(x = datename, y = difference, group = rowname, colour = rowname)) +
  geom_line(alpha = .1) +
  facet_wrap(~Class) +
  theme(legend.position = "none")

df <- 
  oac_lpa$model_3_class_2 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  mutate(Class = as.factor(Class),
               datename = yearmonth(datename))

df %>% 
  ggplot(aes(x = as.factor(datename), y = difference, color = Class)) +
  geom_boxplot() +
  geom_point(shape = 3, alpha = .3, 
             position=position_jitterdodge(dodge.width=0.75)) +
  theme(legend.position = "none")

df %>% 
  ggplot(aes(x = datename, y = difference)) +
  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .1) +
  stat_summary(fun = "mean") +
  facet_wrap(~Class) +
  theme(legend.position = "none")

```

### paracet

### vitd

### All

```{r, lpa-models-nested, include=FALSE}
tictoc::tic()
lpa_analysis <- 
  differences_wide %>% 
  anti_join(y = differences_wide %>% # These cause computation issues. Look at separately.
              filter(drug == "ace" & `2020 Jul` < -50),
            by = c("drug", "regional_unit")) %>%
  nest_by(drug) %>% 
  mutate(lpa_models = list(estimate_profiles(df = data[2:7],
                                      n_profiles = 1:8, 
                                      models = c(1:3))),
         lpa_fits = list(compare_solutions(lpa_models, 
                                           statistics = c("BIC", "AIC", "BLRT_p", "prob_min", "Entropy"))),
         lpa_plots = list(plot_profiles(lpa_models, 
                                        rawdata = FALSE, 
                                        sd = FALSE)),
         best_lpa_rn = as.numeric(list(lpa_fits$AHP)),
         best_lpa_fit = list(lpa_fits$fits[lpa_fits$AHP,]),
         best_lpa_model = flatten(list(lpa_models[lpa_fits$AHP])),
         classes = list(flatten(flatten(list(lpa_models[lpa_fits$AHP])))$model$classification),
         class_count = list(table(flatten(flatten(list(lpa_models[lpa_fits$AHP])))$model$classification)),
         lpa_class = list(bind_cols(drug = drug, 
                                    regional_unit = data$regional_unit, 
                                    lpa_class = classes)))
tictoc::toc()
```

```{r, lpa-best-model-plot, include=FALSE}
lpa_analysis <- 
  lpa_analysis %>% 
  mutate(best_lpa_model_plot = list(plot_profiles(best_lpa_model, 
                                                  rawdata = FALSE, 
                                                  sd = FALSE)),
         best_lpa_model_plot_lab = list(best_lpa_model_plot + 
                                          labs(title = drug)),
         best_lpa_cprob = list(select(best_lpa_model$dff,
                                      starts_with("CPROB"), Class)))

lpa_analysis %>% 
  pluck("best_lpa_cprob") %>% 
  set_names(drugs)

```

```{r, lpa-best-model-plot-2}
lpa_analysis$lpa_fits

lpa_analysis %>% 
  pluck("class_count") %>% 
  set_names(drugs) %>% 
  bind_rows(.id = "drug")

```

```{r}
lpa_analysis$lpa_fits %>% 
  set_names(drugs) %>% 
  pluck("cortico")

lpa_analysis$lpa_models %>% 
  set_names(drugs) %>% 
  pluck("cortico")

lpa_analysis$lpa_models %>% 
  set_names(drugs) %>% 
  pluck("cortico") %>% 
  pluck("model_2_class_6") %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)
```

```{r, lpa-best-model-class-assignment}
lpa_analysis %>% 
  pluck("lpa_class") %>% 
  bind_rows() %>% 
  pivot_wider(names_from = drug, names_prefix = "lpa_class_",
              values_from = lpa_class)

```

### Outliers

```{r, lpa-models, eval=FALSE}
drugs <- unique(as.character(differences$drug))

differences_wide <- 
  differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy)

system.time(differences_wide %>% 
              filter(drug == "oac") %>% 
              ungroup() %>% 
              select(`2020 Mar`:`2020 Aug`) %>% 
              estimate_profiles(df = ., n_profiles = 1:5, models = c(1:3, 6)))

lpaProfiles <- function(data, filter){
  data %>% 
    filter(drug == filter) %>% 
    ungroup() %>% 
    select(`2020 Mar`:`2020 Aug`) %>% 
    estimate_profiles(df = ., n_profiles = 1:5, models = c(1:3, 6))
}

plan(cluster)
system.time(lpa_fits <- 
              future_map(.x = drugs,
                         .f = ~lpaProfiles(differences_wide, .x)))
plan(sequential)

lpa_fits %>% 
  saveRDS("../data/models/lpa_fits.rds")
```

```{r, seperate-lpa-models, eval=FALSE}
lpaProfiles <- function(data, filter){
  data %>% 
    filter(drug == filter) %>% 
    ungroup() %>% 
    select(`2020 Mar`:`2020 Aug`) %>% 
    estimate_profiles(df = ., n_profiles = 1:6, models = c(1:3, 6))
}

tictoc::tic()
system.time(oac_lpa <- lpaProfiles(differences_wide, "oac"))
print("step 1")
print("step 2")
system.time(azithro_lpa <- lpaProfiles(differences_wide, "azithro"))
print("step 3")
system.time(contra_lpa <- lpaProfiles(differences_wide, "contra"))
print("step 4")
system.time(cortico_lpa <- lpaProfiles(differences_wide, "cortico"))
print("step 5")
system.time(hcq_lpa <- lpaProfiles(differences_wide, "hcq"))
print("step 6")
system.time(nsaid_lpa <- lpaProfiles(differences_wide, "nsaid"))
print("step 7")
system.time(vitd_lpa <- lpaProfiles(differences_wide, "vitd"))
print("step 8")
system.time(paracet_lpa <- lpaProfiles(differences_wide, "paracet"))
print("step 9")
#system.time(adreno_lpa <- lpaProfiles(differences_wide, "adreno"))
system.time(ace_lpa <- differences_wide %>%
              filter(drug == "ace") %>% 
              filter(`2020 Jul` > -50) %>% # Outliers causing computation problems
              estimate_profiles(df = .[3:8], 
                                n_profiles = 1:6, 
                                models = c(1:3, 6)))
print("step 10")
lpa_sep_fits <- list(ace_lpa, azithro_lpa, contra_lpa, cortico_lpa, 
                     hcq_lpa, nsaid_lpa, oac_lpa, paracet_lpa, vitd_lpa)
tictoc::toc()

```

```{r, adreno-lpa, eval=FALSE}
system.time(differences_wide %>% 
              filter(drug == "adreno") %>% 
              # filter(`2020 Jul` > -50) %>% # Outliers causing computation problems
              estimate_profiles(df = .[c(3:8)], 
                                n_profiles = 1:5, 
                                models = c(1:3,6)) %>% 
              plot_profiles(rawdata = FALSE))

## Models 1:3
# 2708.712 secs with df = .[c(3:5)]
# 63.237 secs with df = .[c(3:6)]
# 1101.290 secs with df = .[c(3:7)]
# 1618.723 secs with df = .[c(3:8)]
## Models 1:3, 6
# 2338.966 secs with df = .[c(3:8)]

differences_wide %>% 
  filter(drug == "adreno") %>% 
  ggplot(aes(x = `2020 May`)) +
  geom_histogram()
```

### 2021-02-16 r_notebooks/gp_forecast_missingness_accuracy.Rmd
Evaluating accuracy of forecasts and missingness of data

---
title: "GP forecast missingness and accuracy"
author: "Will A. S. Hardy"
date: "25/01/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(data.table)

gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

original_files <- list.files("../data/presdata_updates_040121") %>% 
  grep("presc_wales_", x = ., value = TRUE)

names(original_files) <- 
  str_remove_all(original_files, "presc_wales_") %>% 
  str_remove_all(".rds")

drug_totals <- 
  original_files %>% 
  map_dfr(.x = ., 
          .f = ~read_rds(paste0("../data/presdata_updates_040121/", 
                                       .x)),
          .id = "drug") %>% 
  janitor::clean_names() %>% 
  group_by(drug) %>% 
  summarise(total = sum(quantity)) %>% 
  mutate(drug_code = tolower(str_sub(drug, 1, 3)))

```

Read in all gp_cv_model accuracies

```{r}
accuracy_files <-   
  list.files("../data") %>% 
  grep("gp_cv_models.rds", x = ., value = TRUE)

names(accuracy_files) <- str_remove_all(accuracy_files, "_gp_cv_models.rds")

cv_accuracy <- 
  accuracy_files %>% 
  map_dfr(.x = ., .f = ~read_rds(paste0("../data/", .x)), .id = "drug")
```

## Accuracy

### Overall accuracies

All models for all GPs

```{r}
cv_accuracy %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram(binwidth = 5) +
  coord_cartesian(xlim = c(0,100)) +
  facet_wrap(~drug)

cv_accuracy %>% 
  ggplot(aes(x = .model, y = MAPE)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 100)) 
```

### Best model accuracies

Accuracy of best model for each GP

```{r}
best_models <- 
  cv_accuracy %>% 
  group_by(drug, regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_models %>% 
    ggplot(aes(x = MAPE)) +
  geom_histogram(binwidth = 5) +
  coord_cartesian(xlim = c(0,100)) +
  facet_wrap(~drug)
```

* Models for ace, cortico, nsaid, paracet, and vitd are all *v. good*
* Models for adreno, azithro, contra, hcq, and oc are *okay*
* Models for nicot are *poor*

```{r}
df <- best_models %>% 
  group_by(drug) %>% 
  summarise(m_mape = mean(MAPE)) %>% 
  fuzzyjoin::regex_left_join(x = .,
                             y = drug_totals, 
                             by = c("drug" = "drug_code"))

df %>% 
  ggplot(aes(x = total, y = m_mape)) +
  geom_point(aes(colour = as.factor(drug.x)))

cor.test(x = df$total, y = df$m_mape, method = "spearman")

```

## Missingness

Missingness based on cross validated models

```{r}
best_models %>% 
  select(regional_unit, drug) %>% 
  mutate(missing = FALSE) %>% 
  pivot_wider(names_from = drug, values_from = missing, values_fill = TRUE) %>% 
  pivot_longer(cols = ace:vitd, names_to = "drug", values_to = "missing") %>% 
  ggplot(aes(drug, regional_unit, fill = missing)) +
  geom_tile()
```

```{r}
best_models %>%
  select(drug, regional_unit) %>% 
  ungroup() %>% 
  left_join(gp, by = c("regional_unit" = "practice_id")) %>% 
  group_by(drug) %>% 
  summarise(pct_pat = 100*sum(npat)/sum(gp$npat), .groups = "drop_last")
```

* Missing > 40% of patients for nicotene

### 2021-02-16 r_notebooks/preparing_famot.Rmd
Typos

@@
 ---
-title: "Respiratory famotsteroids"
+title: "Famotodine"
 output: 
@@
 ## Preparing data
+
+* Daily quantity per 10,000,000 patients due to low prescribing volumes
 
@@
             by = c("regional_unit" = "practice_id", "year")) %>% 
-  mutate(n = 1000*n/npat,
+  mutate(n = 10000000*n/npat,
          datename = yearmonth(datename),

### 2021-02-16 r_notebooks/preparing_oac_prop.Rmd
Typos

@@
               oac_monthly_prop_gp_pre_cv19 %>%
-              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
               regionalJointFcstsBound(h = "6 months"))

### 2021-02-16 r_scripts/library_automation.R
Copying Mendeley library from local drive to project file

@@ -1,0 +1,5 @@
+# cronR::cron_rstudioaddin()
+
+file.copy("/Users/willhardy/Dropbox/references/library.bib",
+          "/Users/willhardy/OneDrive - Outreach Rescue/covid_prescribing/sercymru/references/",
+          overwrite = TRUE)

### 2021-02-18 r_notebooks/preparing_ace_inhib.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
   read_rds("../data/presdata_updates_040121/presc_wales_ace-inhibitors.rds") %>% 
+  janitor::clean_names() %>% 
   mutate(datename = dmy(paste0("28-", datename)),
-         practice_id = as_factor(practiceid)) %>% 
-  janitor::clean_names()
+         practice_id = as_factor(practice_id))
 
@@
 
-```{r, ace-gp-practice-discrepancies}
+```{r, ace-gp-practice-discrepancies-abs}
 best_model_gp <- 
@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/ace_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+ace_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .5) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+changes_pre_covid <- c("W95007", "W91020") # Significant changes to prescribing near the end of 2019
+
+best_model_gp_discrep <- 
+  best_model_gp_discrep %>% 
+  filter(!regional_unit %in% changes_pre_covid)
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/ace_discreps.rds")
 ```
+
+* `r length(changes_pre_covid)` GPs excluded as there was a significant change to their prescribing pre-covid

### 2021-02-18 r_notebooks/preparing_adrenoceptor_agonists.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/adreno_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+adreno_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/adreno_discreps.rds")
+
 ```

### 2021-02-18 r_notebooks/preparing_azithro.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
 ```{r, azithro-gp-practice-modelling}
-plan(cluster)
-system.time(azithro_gp_cv_models <-
-  azithro_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
-plan(sequential)
-
-azithro_gp_cv_models %>%
-  saveRDS("../data/azithro_gp_cv_models.rds")
+# plan(cluster)
+# system.time(azithro_gp_cv_models <-
+#   azithro_monthly_quantity_gp_pre_cv19 %>%
+#                   regionalCV(init = 48, step = 3))
+# plan(sequential)
+# 
+# azithro_gp_cv_models %>%
+#   saveRDS("../data/azithro_gp_cv_models.rds")
 
@@
 ```{r azithro-gp-practice-forecasts}
-plan(cluster)
-system.time(azithro_gp_fcsts <-
-              azithro_monthly_quantity_gp_pre_cv19 %>%
-              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
-              regionalJointFcsts(h = "6 months"))
-plan(sequential)
-
-azithro_gp_fcsts %>%
-  saveRDS("../data/azithro_gp_fcsts.rds")
+# plan(cluster)
+# system.time(azithro_gp_fcsts <-
+#               azithro_monthly_quantity_gp_pre_cv19 %>%
+#               filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
+#               regionalJointFcsts(h = "6 months"))
+# plan(sequential)
+# 
+# azithro_gp_fcsts %>%
+#   saveRDS("../data/azithro_gp_fcsts.rds")
 
@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/azithro_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+azithro_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/azithro_discreps.rds")
+
 ```

### 2021-02-18 r_notebooks/preparing_contra.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/contra_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+contra_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/contra_discreps.rds")
+
 ```

### 2021-02-18 r_notebooks/preparing_cortico_resp.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/cortico_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+cortico_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/cortico_discreps.rds")
 ```

### 2021-02-18 r_notebooks/preparing_hcq.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/hcq_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+hcq_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/hcq_discreps.rds")
 ```

### 2021-02-18 r_notebooks/preparing_nsaid.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/nsaid_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+nsaid_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/nsaid_discreps.rds")
+
 ```

### 2021-02-18 r_notebooks/preparing_oac_prop.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/oac_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+oac_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/oac_discreps.rds")
 ```

### 2021-02-18 r_notebooks/preparing_paracet.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/paracet_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+paracet_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/paracet_discreps.rds")
+
 ```

### 2021-02-18 r_notebooks/preparing_vitd.Rmd
Added proportion scores for levels of prescribing relative to forecasted levels

@@
             by = c("datename", "regional_unit")) %>% 
-  mutate(discrepancy = n - .mean) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
   ungroup()
-
-best_model_gp_discrep %>% 
-  saveRDS("../data/differences/vitd_discreps.rds")
 
@@
 
+best_model_gp_discrep %>% 
+  ggplot(aes(y = prop)) +
+  geom_line(aes(x = datename, y = prop, 
+                colour = as.factor(regional_unit)),
+            alpha = .8, lty = 2) +
+  geom_hline(aes(yintercept = 0), colour = "red") +
+  theme(legend.position = "none")
+
+vitd_monthly_quantity_gp %>% 
+  filter(regional_unit %in%
+           (best_model_gp_discrep %>%
+           filter(prop < .25) %>%
+           .$regional_unit %>%
+           unique())) %>%
+  autoplot()
+
+gp %>% 
+    filter(practice_id %in% 
+           (best_model_gp_discrep %>% 
+           filter(prop <.25) %>% 
+           .$regional_unit %>% 
+           unique()))
+
+best_model_gp_discrep %>% 
+  saveRDS("../data/differences/vitd_discreps.rds")
+
 ```

### 2021-03-04 r_notebooks/preparing_all_prescribing.Rmd
Add "all prescribing" data

---
title: "All prescribing"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

## Seed
set.seed(32)

```

## Preparing data

```{r all-prescribing-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

all_prescribing <- 
  read_csv("../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
  mutate(datename = dmy(paste(28, datename, sep = "-")),
         datename = yearmonth(datename),
         regional_unit = factor("all")) %>% 
  as_tsibble(index = datename)

## Sort into monthly count data pre-lockdown (March 2020) as training data
all_prescribing_pre_cv19 <- 
  all_prescribing %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

```

## Modelling

```{r, all-prescribing-practice-modelling}
plan(cluster)

all_prescribing_fable_models <- 
  all_prescribing_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-6), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  fableModels()

all_prescribing_fable_forecasts <- 
  fable_models %>%
  forecast(h = 6)

all_prescribing_fable_fits <- 
  fable_forecasts %>% 
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
                           winkler = winkler_score))

all_prescribing_prophet_fits <- 
  all_prescribing_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-6), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  prophetModels() %>%
  forecast(h = 6) %>%
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
                           winkler = winkler_score))

all_prescribing_combined_fits <- 
  bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
  arrange(RMSE, MAE)
plan(sequential)

all_prescribing_cv_models <-
  all_prescribing_combined_fits

all_prescribing_cv_models %>%
  saveRDS("../data/all_prescribing_cv_models.rds")

all_prescribing_cv_models <- 
  read_rds("../data/all_prescribing_cv_models.rds")

all_prescribing_cv_models %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

all_prescribing_cv_models %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

all_prescribing_cv_models %>% 
  ggplot(aes(x = 1, y = MAPE)) + # reorder by mean of y
  geom_boxplot() +
  geom_jitter() +
  theme(axis.text.x = element_text(angle = 90))

```

```{r all-prescribing-modelling-accuracy}
best_model <- 
  all_prescribing_cv_models %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)
```

```{r all-prescribing-practice-forecasts}
plan(cluster)
all_prescribing_fcsts <-
  all_prescribing_pre_cv19 %>%
  regionalJointFcsts(h = "6 months")
plan(sequential)

all_prescribing_fcsts %>%
  saveRDS("../data/all_prescribing_fcsts.rds")

all_prescribing_fcsts <- 
  read_rds("../data/all_prescribing_fcsts.rds")

```

## Discrepancies

```{r, all-prescribing-practice-discrepancies}
best_model %>% 
  ggplot(aes(x = MAPE)) + 
  geom_histogram()

best_model_discrep <- 
  best_model %>% 
  select(.model) %>% 
  inner_join(mutate(all_prescribing_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model")) %>%
  left_join(mutate(select(all_prescribing, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename")) %>% 
  mutate(discrepancy = n - med, # observed - forecast
         prop = n / med) %>% 
  ungroup()

best_model_discrep %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

best_model_discrep %>% 
  ggplot(aes(y = prop)) +
  geom_line(aes(x = datename, y = prop, 
                colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")

best_model_discrep %>% 
  transmute(datename = datename,
            n = med,
            type = "forecast") %>% 
  bind_rows(mutate(all_prescribing, type = "observed")) %>% 
  as_tsibble(index = datename, key = type) %>% 
  autoplot()

best_model_discrep %>% 
  saveRDS("../data/differences/all_prescribing_discreps.rds")

fable_forecasts %>% 
  filter(.model == best_model$.model) %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = median(n))) +
  geom_line(aes(y = n, col = "observed"), data = all_prescribing) +
  geom_line(aes(y = med, col = "forecast"), data = best_model_discrep)

augment(fable_models) %>% 
  as_tibble() %>% 
  # filter(.model == "comb3") %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = n, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted", lty = as.factor(.id))) +
  facet_wrap(~.model)

```

### 2021-03-04 r_notebooks/gp_dimensionality.Rmd
Exploring the dimensionality of GP data

---
title: "gp_dimensionality"
author: "Will A. S. Hardy"
date: "26/02/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lavaan)

set.seed(376)
knitr::opts_chunk$set(echo = TRUE)
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid),
         dispensing = as_factor(dispensing),
         hboard = as_factor(str_remove_all(hboard, "W110000")),
         cluster = as_factor(cluster)) %>% 
  ungroup() %>% 
  filter(year == 2020) %>% 
  select(-c(practiceid, postcode, easting, northing, lsoacode, year)) %>% 
  janitor::clean_names() %>%
  mutate(across(chd:flu, .fns = ~.x*100))

gp1 <- 
  slice_sample(gp, prop = .5) 
gp2 <- 
  filter(gp, practice_id %in% gp1$practice_id)
```

```{r, inspect-data}
gp %>%
  select(chd:flu) %>% 
  psych::describe() %>% 
  arrange(sd)

gp %>%
  select(chd:flu) %>% 
  DataExplorer::plot_histogram()
```

## QOF disease register EFA

```{r}
df <- select(gp1, chd:flu)
psych::fa.parallel(df)

three_fac <- psych::fa(df, nfactors = 3, rotate = "varimax")
four_fac <- psych::fa(df, nfactors = 4, rotate = "varimax")
five_fac <- psych::fa(df, nfactors = 5, rotate = "varimax")
print(three_fac$loadings, cutoff = .2)
print(four_fac$loadings, cutoff = .2)
```

```{r}

summary(three_fac)
summary(four_fac)
summary(five_fac)
```

## QOF disease register CFA

```{r, cfa-1}
cfa1 <- 
'
  level: 1
  cardio      =~ af + chd + hf + hyp + str
  pulmonary   =~ flu + ast + copd
  cognitive   =~ dem +lrn + men
  f4          =~ diab + obi
  age         =~ can + ost + pal

  level: 2 # Saturated correlation matrix
  # af    ~~ af + chd + hf + hyp + str + flu + ast + copd
  # chd   ~~ chd + hf + hyp + str + flu + ast + copd
  # hf    ~~ hf + hyp + str + flu + ast + copd
  # hyp   ~~ hyp + str + flu + ast + copd
  # str   ~~ str + flu + ast + copd
  # flu   ~~ flu + ast + copd
  # ast   ~~ ast + copd
  # copd  ~~ copd

  af    ~~ af + chd + hf + hyp + str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
  chd   ~~ chd + hf + hyp + str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
  hf    ~~ hf + hyp + str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
  hyp   ~~ hyp + str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
  str   ~~ str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
  flu   ~~ flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
  ast   ~~ ast + copd + lrn + men + diab + obi + can + dem + ost + pal
  copd  ~~ copd + lrn + men + diab + obi + can + dem + ost + pal
  lrn   ~~ lrn + men + diab + obi + can + dem + ost + pal
  men   ~~ men + diab + obi + can + dem + ost + pal
  diab  ~~ diab + obi + can + dem + ost + pal
  obi   ~~ obi + can + dem + ost + pal
  can   ~~ can + dem + ost + pal
  dem   ~~ dem + ost + pal
  ost   ~~ ost + pal
  pal   ~~ pal
'
# rar epi

fit1 <- sem(model = cfa1, data = gp1, cluster = "cluster", estimator = "MLR")

summary(fit1, fit.measures=TRUE, standardized = TRUE)

lavInspect(fit1, "icc")
```

### 2021-03-04 writing/paper.Rmd
Add writing folder

---
title             : "Variation in Primary Care Prescribing in Wales due to COVID-19"
shorttitle        : "Welsh Primary Care COVID Prescribing"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Second Author"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Centre for Health Economics & Medicines Evaluation, Bangor University, LL55 2PZ"
  - id            : "2"
    institution   : "Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "../references/library.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "../references/apa.csl"
documentclass     : "apa7"
classoption       : "man"
output            : 
  - papaja::apa6_pdf
  - papaja::apa6_docx
---

```{r setup, include = FALSE}
## Packages
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(serCymruTools)
library(papaja)

r_refs("r-references.bib")

## Data
differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug)) %>% 
  select(drug, regional_unit, datename, discrepancy, med)

all_prescribing <- 
  read_csv("../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
  mutate(datename = dmy(paste(28, datename, sep = "-")),
         datename = yearmonth(datename),
         regional_unit = factor("all")) %>% 
  as_tsibble(index = datename) %>% 
  filter(datename < yearmonth(dmy("01-09-2020")))

all_prescribing_pre_cv19 <- 
  all_prescribing %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(32)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
```

# Methods

## Data

* Sources of data
  * GP
  * Prescribing
  * QOF
  * WIMD
* Preparing

## Identifying changes in prescribing due to COVID-19

Identifying the effects of COVID-19 is not simple, as its effects are unprecedented and its global impact prevents us from adopting a traditional treatment and control group type design. Instead, we have used time series analysis methods to create counterfactual forecasts

To understand the changes in levels of prescribing due to COVID-19, it was first necessary for us to forecast the levels of prescribing had COVID-19 not affected Wales as a baseline. To do so, we used historic data (January 2015 to December 2020) to identify from a range of time series models, one that was good fit to the data. This was done using cross-validation to reduce the likelihood of choosing a model that was overfitted to the data.

* Given the presence of seasonal variation and existing trends in levels of prescribing, we used various time series forecasting methods to account for existing trends and seasonal variation when creating the forecasts.

* For each analysis, we created a forecast that aimed to answer the question, "What would the levels of prescribing have been if COVID-19 had not affected Wales?" We then used these forecasts to estimate the changes in levels of prescribing due to COVID-19.

  * We viewed this, somewhat complex, approach as superior to more simple approaches (e.g., carrying last years levels forward, or even using the mean of the last three years).
* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
  * Using Jan 2015 to Feb 2020 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
    * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
    * Only interested in one forecast horizon: six-months
    * 
  * Having chosen the "best model" for each practice based on the pre-COVID data, we then used this to forecast the level of prescribing for each practice

* We used time series modelling to forecast Welsh primary care prescribing levels had .
    * We used the `fable` [@R-fable] and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
    * Time series linear model
    * Decomposition model
    * Seasonal naïve (with and without drift)
    * Autoregressive integrated moving average [ARIMA; @Box2015]
    * Holt-Winters Additive Model [@Chatfield1978]
    * Prophet [@Taylor2018]
    * Combination models [cf. @Thomson2019]
  * Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
  * Model selection
    * RMSE then MAE

## Identifying different prescribing behaviours - LPA

* What is LPA
  * Differences from clustering methods (e.g., k-means and hierarchical)

When conducting LPA, several models are specified and then evaluated. Model selection, including class enumeration, should not be based solely on statistical criteria, but also the statistical adequacy and substantive meaning of the solutions [@Marsh2009; @Morin2016]. Indeed, relying solely on statistical criteria in large samples may lead to the inability to identify an "optimal solution" as model fit increases as the number of classes increase [@Morin2009].

In this study we inspected the Bayesian Information Criterion [BIC; @Schwartz1978] and the bootstrapped likelihood ratio test [BLRT; @McLachlan2000] during the class enumeration process as the results of Monte-Carlo simulation study [@Nylund2007] showed them outperform other information criteria and likelihood-based tests.

* Entropy
* Posterior probabilities

## Reproducability and code

We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.

# Results

## Counterfactual forecasts

### All drugs

```{r all-prescribing-modelling, warning=FALSE}
plan(cluster)

all_prescribing_fable_models <- 
  all_prescribing_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-2), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  fableModels()

all_prescribing_fable_forecasts <- 
  all_prescribing_fable_models %>%
  forecast(h = 6, point_forecast = list(.median = median))

all_prescribing_fable_fits <- 
  all_prescribing_fable_forecasts %>% 
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
                           winkler = winkler_score))

all_prescribing_prophet_fits <- 
  all_prescribing_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-2), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  prophetModels() %>%
  forecast(h = 6, point_forecast = list(.median = median)) %>%
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
                           winkler = winkler_score))

all_prescribing_combined_fits <- 
  bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
  arrange(RMSE, MAE)

all_prescribing_best_model <- 
  all_prescribing_combined_fits %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

all_prescribing_covid_forecast <- 
  bind_rows(fableModels(all_prescribing_pre_cv19) %>% 
            forecast(h = "6 months"),
          prophetModels(all_prescribing_pre_cv19) %>% 
            forecast(h = "6 months")) %>% 
  as_tibble() %>% 
  filter(.model == all_prescribing_best_model$.model) %>% 
  dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 0.1), 
                med = median(n), ub_80 = quantile(n, 0.9), 
                ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
                n = NULL)

plan(sequential)
```

```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy"}
all_prescribing_combined_fits %>% 
  ggplot(aes(x = reorder(.model, RMSE, mean), y = RMSE)) +
  geom_col()
```

```{r, all-prescribing-cv-plot, fig.cap="All prescribing, best model CV fit"}
all_prescribing_best_cv_model <- 
  augment(all_prescribing_fable_models) %>% 
  as_tibble() %>% 
  filter(.model == all_prescribing_best_model$.model)

all_prescribing_best_cv_model %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = n/1e+06, colour = "Data")) +
  geom_line(aes(y = .fitted/1e+06, colour = "Fitted", lty = as.factor(.id))) +
  labs(lty = "CV iteration")
```

```{r, all-prescribing-forecast-plot, fig.cap="All prescribing, best model fit and forecast"}
all_prescribing %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = n, col = "Observed")) +
  geom_line(aes(y = med, col = "Forecast"), 
            data = all_prescribing_covid_forecast) +
  geom_line(aes(y = fitted, col = "Fitted"), 
            data = all_prescribing_best_cv_model %>% 
              group_by(datename) %>% 
              summarise(fitted = mean(.fitted, na.rm = TRUE))) +
  geom_vline(xintercept = ymd("2020-03-01"), lty = 3)
```

```{r, all-prescribing-pct-change-plot, fig.cap="Percentage difference in all prescribing"}
all_prescribing %>% 
  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
  ggplot(aes(x = datename, y = (100*n/med)-100)) +
  geom_line() +
  geom_hline(yintercept = 0, lty = 3)
```

### Specific drugs

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-03-04 writing/paper.tex
Add writing folder

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa7}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Variation in Primary Care Prescribing in Wales due to COVID-19},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Welsh Primary Care COVID Prescribing}
\author{First Author\textsuperscript{1}\ \& Second Author\textsuperscript{1,2}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Centre for Health Economics \& Medicines Evaluation, Bangor University, LL55 2PZ\\\textsuperscript{2} Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ}
\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: my@email.com}
\keywords{keywords\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{Variation in Primary Care Prescribing in Wales due to COVID-19}

\date{}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{data}{%
\subsection{Data}\label{data}}

\begin{itemize}
\tightlist
\item
  Sources of data

  \begin{itemize}
  \tightlist
  \item
    GP
  \item
    Prescribing
  \item
    QOF
  \item
    WIMD
  \end{itemize}
\item
  Preparing
\end{itemize}

\hypertarget{identifying-changes-in-prescribing-due-to-covid-19}{%
\subsection{Identifying changes in prescribing due to COVID-19}\label{identifying-changes-in-prescribing-due-to-covid-19}}

Identifying the effects of COVID-19 is not simple, as its effects are unprecedented and its global impact prevents us from adopting a traditional treatment and control group type design. Instead, we have used time series analysis methods to create counterfactual forecasts

To understand the changes in levels of prescribing due to COVID-19, it was first necessary for us to forecast the levels of prescribing had COVID-19 not affected Wales as a baseline. To do so, we used historic data (January 2015 to December 2020) to identify from a range of time series models, one that was good fit to the data. This was done using cross-validation to reduce the likelihood of choosing a model that was overfitted to the data.

\begin{itemize}
\item
  Given the presence of seasonal variation and existing trends in levels of prescribing, we used various time series forecasting methods to account for existing trends and seasonal variation when creating the forecasts.
\item
  For each analysis, we created a forecast that aimed to answer the question, \enquote{What would the levels of prescribing have been if COVID-19 had not affected Wales?} We then used these forecasts to estimate the changes in levels of prescribing due to COVID-19.

  \begin{itemize}
  \tightlist
  \item
    We viewed this, somewhat complex, approach as superior to more simple approaches (e.g., carrying last years levels forward, or even using the mean of the last three years).
  \end{itemize}
\item
  We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data.

  \begin{itemize}
  \tightlist
  \item
    Using Jan 2015 to Feb 2020 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.

    \begin{itemize}
    \item
      Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) \textbf{Do we want to re-run this with 1-month?}
    \item
      Only interested in one forecast horizon: six-months
    \item
    \end{itemize}
  \item
    Having chosen the \enquote{best model} for each practice based on the pre-COVID data, we then used this to forecast the level of prescribing for each practice
  \end{itemize}
\item
  We used time series modelling to forecast Welsh primary care prescribing levels had .

  \begin{itemize}
  \tightlist
  \item
    We used the \texttt{fable} (O'Hara-Wild et al., 2021a) and the \texttt{fable.prophet} (O'Hara-Wild, 2020) packages to conduct the time series analyses.
  \item
    Time series linear model
  \item
    Decomposition model
  \item
    Seasonal naïve (with and without drift)
  \item
    Autoregressive integrated moving average (ARIMA; Box et al., 2015)
  \item
    Holt-Winters Additive Model (Chatfield, 1978)
  \item
    Prophet (Taylor \& Letham, 2018)
  \item
    Combination models (cf.~Thomson et al., 2019)
  \item
    Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
  \item
    Model selection

    \begin{itemize}
    \tightlist
    \item
      RMSE then MAE
    \end{itemize}
  \end{itemize}
\end{itemize}

\hypertarget{identifying-different-prescribing-behaviours---lpa}{%
\subsection{Identifying different prescribing behaviours - LPA}\label{identifying-different-prescribing-behaviours---lpa}}

\begin{itemize}
\tightlist
\item
  What is LPA

  \begin{itemize}
  \tightlist
  \item
    Differences from clustering methods (e.g., k-means and hierarchical)
  \end{itemize}
\end{itemize}

When conducting LPA, several models are specified and then evaluated. Model selection, including class enumeration, should not be based solely on statistical criteria, but also the statistical adequacy and substantive meaning of the solutions ({\textbf{???}}; Marsh et al., 2009). Indeed, relying solely on statistical criteria in large samples may lead to the inability to identify an \enquote{optimal solution} as model fit increases as the number of classes increase ({\textbf{???}}).

In this study we inspected the Bayesian Information Criterion (BIC; Schwartz, 1978) and the bootstrapped likelihood ratio test (BLRT; McLachlan \& Peel, 2000) during the class enumeration process as the results of Monte-Carlo simulation study (Nylund et al., 2007) showed them outperform other information criteria and likelihood-based tests.

\begin{itemize}
\tightlist
\item
  Entropy
\item
  Posterior probabilities
\end{itemize}

\hypertarget{reproducability-and-code}{%
\subsection{Reproducability and code}\label{reproducability-and-code}}

We used R (Version 4.0.2; R Core Team, 2020) and the R-packages \emph{dplyr} (Version 1.0.4; Wickham, François, et al., 2021), \emph{fable} (Version 0.3.0; O'Hara-Wild et al., 2021a, 2021b; O'Hara-Wild, 2020), \emph{fable.prophet} (Version 0.1.0; O'Hara-Wild, 2020), \emph{fabletools} (Version 0.3.0; O'Hara-Wild et al., 2021b), \emph{feasts} (Version 0.1.7; O'Hara-Wild et al., 2021c), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{furrr} (Version 0.2.2; Vaughan \& Dancho, 2021), \emph{future} (Version 1.21.0; Bengtsson, 2020), \emph{ggplot2} (Version 3.3.3; Wickham, 2016), \emph{lubridate} (Version 1.7.10; Grolemund \& Wickham, 2011), \emph{MplusAutomation} (Version 0.8; Hallquist \& Wiley, 2018), \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020), \emph{prophet} (Version 0.6.1; O'Hara-Wild, 2020; Taylor \& Letham, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020a), \emph{Rcpp} (Version 1.0.6; Eddelbuettel \& François, 2011; Eddelbuettel \& Balamuta, 2018), \emph{readr} (Version 1.4.0; Wickham \& Hester, 2020), \emph{rebus} (Version 0.1.3; Cotton, 2017), \emph{rlang} (Version 0.4.10; Henry \& Wickham, 2020b), \emph{rstan} (Version 2.21.2; Stan Development Team, 2020a), \emph{serCymruTools} (Version 0.1.3; Will, 2021), \emph{StanHeaders} (Version 2.21.0.7; Stan Development Team, 2020b), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.0; Müller \& Wickham, 2021), \emph{tidyLPA} (Version 1.0.8; Rosenberg et al., 2018), \emph{tidyr} (Version 1.1.3; Wickham, 2020), \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019), and \emph{tsibble} (Version 1.0.0; Wang et al., 2020) for all our analyses, functions are available in the \texttt{serCymruTools} package (Will, 2021), and all other code is available at \url{https://github.com/w-hardy/sercymru}.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{counterfactual-forecasts}{%
\subsection{Counterfactual forecasts}\label{counterfactual-forecasts}}

\hypertarget{all-drugs}{%
\subsubsection{All drugs}\label{all-drugs}}

\begin{verbatim}
## Warning: Removed 2 rows containing missing values (position_stack).
\end{verbatim}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/all-prescribing-model-accuracy-hist-1.pdf}
\caption{\label{fig:all-prescribing-model-accuracy-hist}All prescribing, model accuracy}
\end{figure}

\begin{verbatim}
## Warning: Removed 108 row(s) containing missing values (geom_path).
\end{verbatim}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/all-prescribing-cv-plot-1.pdf}
\caption{\label{fig:all-prescribing-cv-plot}All prescribing, best model CV fit}
\end{figure}

\begin{verbatim}
## Warning: Removed 12 row(s) containing missing values (geom_path).
\end{verbatim}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/all-prescribing-forecast-plot-1.pdf}
\caption{\label{fig:all-prescribing-forecast-plot}All prescribing, best model fit and forecast}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/all-prescribing-pct-change-plot-1.pdf}
\caption{\label{fig:all-prescribing-pct-change-plot}Percentage difference in all prescribing}
\end{figure}

\hypertarget{specific-drugs}{%
\subsubsection{Specific drugs}\label{specific-drugs}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-future}{}%
Bengtsson, H. (2020). \emph{A unifying framework for parallel and distributed processing in r using futures}. \url{https://arxiv.org/abs/2008.00553}

\leavevmode\hypertarget{ref-Box2015}{}%
Box, G. E. P., Jenkins, G. M., Reinsel, G. C. .., \& Ljung, G. M. (2015). \emph{Time series analysis: forecasting and control} (5th ed.). John Wiley \& Sons.

\leavevmode\hypertarget{ref-Chatfield1978}{}%
Chatfield, C. (1978). The Holt-Winters Forecasting Procedure. \emph{Journal of the Royal Statistical Society: Series C (Applied Statistics)}, \emph{27}(3), 264--279.

\leavevmode\hypertarget{ref-R-rebus}{}%
Cotton, R. (2017). \emph{Rebus: Build regular expressions in a human readable way}. \url{https://CRAN.R-project.org/package=rebus}

\leavevmode\hypertarget{ref-R-Rcpp_b}{}%
Eddelbuettel, D., \& Balamuta, J. J. (2018). Extending extitR with extitC++: A Brief Introduction to extitRcpp. \emph{The American Statistician}, \emph{72}(1), 28--36. \url{https://doi.org/10.1080/00031305.2017.1375990}

\leavevmode\hypertarget{ref-R-Rcpp_a}{}%
Eddelbuettel, D., \& François, R. (2011). Rcpp: Seamless R and C++ integration. \emph{Journal of Statistical Software}, \emph{40}(8), 1--18. \url{https://doi.org/10.18637/jss.v040.i08}

\leavevmode\hypertarget{ref-R-lubridate}{}%
Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with lubridate. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. \url{https://www.jstatsoft.org/v40/i03/}

\leavevmode\hypertarget{ref-R-MplusAutomation}{}%
Hallquist, M. N., \& Wiley, J. F. (2018). MplusAutomation: An R package for facilitating large-scale latent variable analyses in Mplus. \emph{Structural Equation Modeling}, 1--18. \url{https://doi.org/10.1080/10705511.2017.1402334}

\leavevmode\hypertarget{ref-R-purrr}{}%
Henry, L., \& Wickham, H. (2020a). \emph{Purrr: Functional programming tools}. \url{https://CRAN.R-project.org/package=purrr}

\leavevmode\hypertarget{ref-R-rlang}{}%
Henry, L., \& Wickham, H. (2020b). \emph{Rlang: Functions for base types and core r and 'tidyverse' features}. \url{https://CRAN.R-project.org/package=rlang}

\leavevmode\hypertarget{ref-Marsh2009}{}%
Marsh, H. W., Muthén, B. O., Asparouhov, T., Lüdtke, O., Robitzsch, A., Morin, A. J. S., \& Trautwein, U. (2009). \emph{Exploratory structural equation modeling, integrating CFA and EFA: Application to students' evaluations of university teaching} (Vol. 16, pp. 439--476). \url{https://doi.org/10.1080/10705510903008220}

\leavevmode\hypertarget{ref-McLachlan2000}{}%
McLachlan, G., \& Peel, D. (2000). \emph{Finite mixture models}. Wiley.

\leavevmode\hypertarget{ref-R-tibble}{}%
Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. \url{https://CRAN.R-project.org/package=tibble}

\leavevmode\hypertarget{ref-Nylund2007}{}%
Nylund, K. L., Asparouhov, T., \& Muthén, B. O. (2007). Deciding on the number of classes in latent class analysis and growth mixture modeling: A Monte Carlo simulation study. \emph{Structural Equation Modeling}, \emph{14}(4), 535--569. \url{https://doi.org/10.1080/10705510701575396}

\leavevmode\hypertarget{ref-R-fable.prophet}{}%
O'Hara-Wild, M. (2020). \emph{Fable.prophet: Prophet modelling interface for 'fable'}. \url{https://CRAN.R-project.org/package=fable.prophet}

\leavevmode\hypertarget{ref-R-fable}{}%
O'Hara-Wild, M., Hyndman, R., \& Wang, E. (2021a). \emph{Fable: Forecasting models for tidy time series}. \url{https://CRAN.R-project.org/package=fable}

\leavevmode\hypertarget{ref-R-fabletools}{}%
O'Hara-Wild, M., Hyndman, R., \& Wang, E. (2021b). \emph{Fabletools: Core tools for packages in the 'fable' framework}. \url{https://CRAN.R-project.org/package=fabletools}

\leavevmode\hypertarget{ref-R-feasts}{}%
O'Hara-Wild, M., Hyndman, R., \& Wang, E. (2021c). \emph{Feasts: Feature extraction and statistics for time series}. \url{https://CRAN.R-project.org/package=feasts}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-R-tidyLPA}{}%
Rosenberg, J. M., Beymer, P. N., Anderson, D. J., Van Lissa, C. J., \& Schmidt, J. A. (2018). TidyLPA: An r package to easily carry out latent profile analysis (lpa) using open-source or commercial software. \emph{Journal of Open Source Software}, \emph{3}(30), 978. \url{https://doi.org/10.21105/joss.00978}

\leavevmode\hypertarget{ref-Schwartz1978}{}%
Schwartz, G. (1978). Estimating the dimesion of a model. \emph{The Annals of Statistics1}, \emph{6}(2), 461--464.

\leavevmode\hypertarget{ref-R-rstan}{}%
Stan Development Team. (2020a). \emph{RStan: The R interface to Stan}. \url{http://mc-stan.org/}

\leavevmode\hypertarget{ref-R-StanHeaders}{}%
Stan Development Team. (2020b). \emph{StanHeaders: Headers for the R interface to Stan}. \url{https://mc-stan.org/}

\leavevmode\hypertarget{ref-Taylor2018}{}%
Taylor, S. J., \& Letham, B. (2018). Forecasting at Scale. \emph{American Statistician}, \emph{72}(1), 37--45. \url{https://doi.org/10.1080/00031305.2017.1380080}

\leavevmode\hypertarget{ref-R-prophet}{}%
Taylor, S., \& Letham, B. (2020). \emph{Prophet: Automatic forecasting procedure}. \url{https://CRAN.R-project.org/package=prophet}

\leavevmode\hypertarget{ref-Thomson2019}{}%
Thomson, M. E., Pollock, A. C., Önkal, D., \& Gönül, M. S. (2019). Combining forecasts: Performance and coherence. \emph{International Journal of Forecasting}, \emph{35}(2), 474--484. \url{https://doi.org/10.1016/j.ijforecast.2018.10.006}

\leavevmode\hypertarget{ref-R-furrr}{}%
Vaughan, D., \& Dancho, M. (2021). \emph{Furrr: Apply mapping functions in parallel using futures}. \url{https://CRAN.R-project.org/package=furrr}

\leavevmode\hypertarget{ref-R-tsibble}{}%
Wang, E., Cook, D., \& Hyndman, R. J. (2020). A new tidy data structure to support exploration and modeling of temporal data. \emph{Journal of Computational and Graphical Statistics}, \emph{29}(3), 466--478. \url{https://doi.org/10.1080/10618600.2019.1695624}

\leavevmode\hypertarget{ref-R-ggplot2}{}%
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}

\leavevmode\hypertarget{ref-R-stringr}{}%
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. \url{https://CRAN.R-project.org/package=stringr}

\leavevmode\hypertarget{ref-R-tidyr}{}%
Wickham, H. (2020). \emph{Tidyr: Tidy messy data}. \url{https://CRAN.R-project.org/package=tidyr}

\leavevmode\hypertarget{ref-R-forcats}{}%
Wickham, H. (2021). \emph{Forcats: Tools for working with categorical variables (factors)}. \url{https://CRAN.R-project.org/package=forcats}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T. L., Miller, E., Bache, S. M., Müller, K., Ooms, J., Robinson, D., Seidel, D. P., Spinu, V., \ldots{} Yutani, H. (2019). Welcome to the tidyverse. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\leavevmode\hypertarget{ref-R-dplyr}{}%
Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. \url{https://CRAN.R-project.org/package=dplyr}

\leavevmode\hypertarget{ref-R-readr}{}%
Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. \url{https://CRAN.R-project.org/package=readr}

\leavevmode\hypertarget{ref-R-serCymruTools}{}%
Will, H. (2021). \emph{SerCymruTools: Tools for analysing gp prescribing data}.

\endgroup

\end{document}

### 2021-03-04 r_notebooks/ace_mlm.Rmd
Ace inhibitor multilevel modelling

---
title: "Ace inhibitors LPA"
author: "Will A. S. Hardy"
date: "27/01/2021"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
##### Packages #####
library(tidyverse) # needed for data manipulation.
library(tsibble)
library(tidyLPA)
library(future)
library(furrr)
library(tidymodels)
library(workflows)
library(tune)
library(nnet)
library(brms) # for the analysis
library(RColorBrewer) # needed for some extra colours in one of the graphs
library(ggmcmc)
library(ggthemes)
library(ggridges)
library(RcppEigen)
library(knitr)

options(mc.cores = parallel::detectCores() - 1)

knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

set.seed(32)

gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid),
         dispensing = as_factor(dispensing),
         cluster = str_replace_all(cluster, " ", "_"),
         cluster = str_remove_all(cluster, "[/&]"),
         cluster = as_factor(cluster),
         hboard = as_factor(str_remove_all(hboard, "W110000")),
         gp_load = npat/ngp) %>% 
  filter(year == 2020) %>% 
  ungroup() %>% 
  janitor::clean_names()
unique(gp$cluster)
differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug)) %>% 
  select(drug, regional_unit, datename, discrepancy)

proportions <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug),
         prop = (prop * 100) - 100) %>% 
  select(drug, regional_unit, datename, prop)

drugs <- unique(as.character(differences$drug))

#### Functions ####
# To colour code the extremes, we need to write a small function that calculates the regression lines and adds a column indicating which clusters have the most extreme.
f1 <- function(data, x, y, grouping, n.highest = 3, n.lowest = 3){
  groupinglevel <- data[,grouping]
  res           <- data.frame(coef = rep(NA, length(unique(groupinglevel))), group = unique(groupinglevel))
  names(res)    <- c("coef", grouping)
  for(i in 1:length(unique(groupinglevel))){
    data2    <- as.data.frame(data[data[,grouping] == i,])
    res[i,1] <- as.numeric(lm(data2[, y] ~ data2[, x])$coefficients[2])
  }
  top    <- res %>% top_n(n.highest, coef)
  bottom <- res %>% top_n(-n.lowest, coef)
  res    <- res %>% mutate(high_and_low = ifelse(coef %in% top$coef, "top",  ifelse(coef %in% bottom$coef, "bottom", "none")))
  data3  <- left_join(data, res)
  return(data3)
}

modelParams <- function(model){
  posterior_summary(model) %>% 
  as_tibble(rownames = NA) %>% 
  rownames_to_column(var = "Parameter") %>% 
  filter(!str_detect(Parameter, "r_team"),
         !str_detect(Parameter, "L_"),
         !str_detect(Parameter, "z_"))
}

bayesEstimate <- function(.){
  require(papaja)
  paste0(printnum(.$Estimate), "[", printnum(.$Q2.5), ",", printnum(.$Q97.5), "]")
}

plotSlopes <- function(data, resp, efflist, group) {
  require(ggplot2)
  require(purrr)
  y <- enquo(resp)
  group <- enquo(group)
  ngroups <- data %>% 
    select(!!group) %>% 
    unique() %>% 
    nrow()

  map(efflist, function(x)
    ggplot(data, aes(!!sym(x), !!y, col = as.numeric(!!group), 
                     group = !!group)) +
    geom_point(size = 1.2,
               alpha = .8,
               position = "jitter") + # to add some random noise for plotting purposes
    theme_minimal() +
    theme(legend.position = "none") +
    scale_color_gradientn(colours = rainbow(n = ngroups)) +
    geom_smooth(method = lm,
                se     = FALSE,
                size   = .5,
                alpha  = .8) + # to add regression line
    ylab(NULL)
  )
}
```

## Data cleaning

```{r, data-problem-values, warning=FALSE}
differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  psych::describeBy(group = "drug", fast = TRUE)

proportions %>% 
  pivot_wider(names_from = datename, values_from = prop) %>% 
  psych::describeBy(group = "drug", fast = TRUE)
```

* Problem with `oac` data
* Infinite values have been calculated when something has been divided by zero. Is this when the total prescribing of oac has been zero, thus wafarin as a percentage of 0 is Inf?

```{r, data-which-problem}
differences %>% 
  filter(drug == "oac" & 
           (is.na(discrepancy) | is.nan(discrepancy) | is.infinite(discrepancy))) %>% 
  group_by(datename) %>% 
  count()

differences %>% 
  filter(drug == "oac" & 
           (is.na(discrepancy) | is.nan(discrepancy) | is.infinite(discrepancy))) %>% 
  group_by(drug, regional_unit) %>% 
  count()
```

* Missing/inappropriate data in five practices
* Removed these practices from the `oac` data

```{r, data-cleaning}
differences <- 
  differences %>% 
  anti_join(y = differences %>% 
              filter(drug == "oac" & 
                       (is.na(discrepancy) |
                          is.nan(discrepancy) | 
                          is.infinite(discrepancy))) %>% 
              group_by(drug, regional_unit) %>% 
              count(), 
            by = c("drug", "regional_unit"))

differences_wide <- 
  differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy)

proportions_wide <- 
  proportions %>% 
  filter(drug == "ace") %>% 
  pivot_wider(names_from = datename, values_from = prop)
```

## MLM

```{r}
mlm_df <- 
  proportions_wide %>% 
  left_join(gp, by = c("regional_unit" = "practice_id")) %>% 
  rename(march = `2020 Mar`, april = `2020 Apr`, may = `2020 May`, 
         june = `2020 Jun`, july = `2020 Jul`, august = `2020 Aug`)
```

### March

```{r}
mlm_df %>% 
  ggplot(aes(x = gp_load, y = march, 
             col = as.numeric(cluster), group = cluster)) +
 geom_point(size = .2,
             alpha = .8,
             position = "jitter") +# to add some random noise for plotting purposes
  theme_minimal() +
  theme(legend.position = "none") +
    scale_color_gradientn(colours = rainbow(length(unique(gp$cluster)))) +
  geom_smooth(method = lm,
              se     = FALSE,
              size   = .5,
              alpha  = .8) # to add regression line
```

#### Analysis 1 {.tabset}
##### Intercept only model

```{r, mar-int-cluster-model, include=FALSE}
mar_interceptonlymodel <- 
  brm(march ~ 1 + (1|cluster),  
      data = mlm_df, 
      warmup = 1000, iter = 3000, seed = 123, save_pars = save_pars(all = TRUE))

mar_interceptonlyparams <- modelParams(mar_interceptonlymodel)

# Calculating ICC
hyp <- "sd_cluster__Intercept^2 / (sd_cluster__Intercept^2 + sigma^2) = 0"
mar_icc_test <- print(hypothesis(mar_interceptonlymodel, hyp, class = NULL))
mar_icc_est <- paste0(mar_icc_test$hypothesis$Estimate, " [", mar_icc_test$hypothesis$CI.Lower, ",",
       mar_icc_test$hypothesis$CI.Upper, "]")
```

```{r, mar-int-cluster-convergence}
mar_interceptonlymodel %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 1000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

```{r, mar-int-cluster-params}
mar_interceptonlyparams %>% 
  kable(digits = 2)
```

* Posterior mean of residual variance at team level = `r mar_interceptonlyparams[2,2]^2`
* Posterior mean of residual variance at individual level = `r mar_interceptonlyparams[3,2]^2`
* ICC: $\rho$ = `r mar_icc_est`

##### L1 predictors

```{r, mar-m1-cluster-model}
mar_mlm1 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE))

mar_mlm1_params <- modelParams(mar_mlm1)
```

```{r, mar-m1-cluster-convergence}
mar_mlm1 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_p_fem", "b_pm_65", "b_dispensingYes",
                          "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 2000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")

```

```{r, mar-m1-cluster-params}
mar_mlm1_params %>% 
  kable(digits = 2)

mar_mlm1 %>% 
  sjstats::tidy_stan()
```

##### L1 predictors with random slopes

```{r, mar-mlm2-cluster-model}
mar_mlm2 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
      control = list(max_treedepth = 15, adapt_delta = .999))

mar_mlm2_params <- modelParams(mar_mlm2)
```

```{r, mar-m2-cluster-convergence}
mar_mlm2 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_p_fem", "b_pm_65", "b_dispensingYes",
                          "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 2000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

```{r, mar-m2-cluster-params}
mar_mlm2_params %>% 
  kable(digits = 2)
```

* Removing gp_load as 0 effect and 0 variance

```{r, mar-mlm3-cluster-model}
mar_mlm3 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 +
              (1 + p_fem + pm_65 + dispensing + wimd2019|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
      control = list(max_treedepth = 15, adapt_delta = .999))

mar_mlm3_params <- modelParams(mar_mlm3)
```

```{r, mar-m3-cluster-convergence}
mar_mlm3 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_p_fem", "b_pm_65", "b_dispensingYes",
                          "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 2000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

```{r, mar-m3-cluster-params}
mar_mlm3_params %>% 
  kable(digits = 2)
```

### Apr

#### Analysis 1 {.tabset}
##### Intercept only model

```{r apr-intercept-cluster-model, include=FALSE}
apr_interceptonlymodel <- 
  brm(april ~ 1 + (1|cluster),  
      data = mlm_df, 
      warmup = 1000, iter = 3000, seed = 123, save_pars = save_pars(all = TRUE))

apr_interceptonlyparams <- modelParams(apr_interceptonlymodel)

# Calculating ICC
apr_hyp <- "sd_cluster__Intercept^2 / (sd_cluster__Intercept^2 + sigma^2) = 0"
apr_icc_test <- print(hypothesis(apr_interceptonlymodel, apr_hyp, class = NULL))
apr_icc_est <- paste0(apr_icc_test$hypothesis$Estimate, 
                  " [", apr_icc_test$hypothesis$CI.Lower, ",",
                  apr_icc_test$hypothesis$CI.Upper, "]")
```

```{r, apr-int-cluster-convergence}
apr_interceptonlymodel %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 1000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

```{r apr-intercept-cluster-params}
apr_interceptonlyparams %>% 
  kable(digits = 2)
```

* Posterior mean of residual variance at team level = `r apr_interceptonlyparams[2,2]^2`
* Posterior mean of residual variance at individual level = `r apr_interceptonlyparams[3,2]^2`
* ICC: $\rho$ = `r apr_icc_est`

##### L1 predictors

```{r, apr-m1-cluster-model, include=FALSE}
apr_mlm1 <- brm(april ~ 1 + march +
                 p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 4000, seed = 123, save_pars = save_pars(all = TRUE))

apr_mlm1_params <- modelParams(apr_mlm1)
```

```{r, apr-m1-cluster-convergence}
apr_mlm1 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_march", "b_p_fem", "b_pm_65", 
                          "b_dispensingYes", "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 2000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

```{r, apr-m1-cluster-params}
apr_mlm1_params %>% 
  kable(digits = 2)
```

##### L1 predictors with random slopes

```{r, apr-m2-cluster-model, include=FALSE}
apr_mlm2 <- brm(april ~ 1 + march +
                  p_fem + pm_65 + dispensing + wimd2019 + gp_load +
                  (1 + march +
                     p_fem + pm_65 + dispensing + wimd2019 + gp_load|cluster), 
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
      control = list(max_treedepth = 15, adapt_delta = .999))

apr_mlm2_params <- modelParams(apr_mlm2)
```

```{r, apr-m2-cluster-convergence}
apr_mlm2 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_march", "b_p_fem", "b_pm_65", 
                          "b_dispensingYes", "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 1000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

```{r, apr-m2-cluster-params}
apr_mlm2_params %>% 
  kable(digits = 2)
```

```{r}

```

### 2021-03-04 r_notebooks/ace_mlm_dan.Rmd
Ace inhibitor multilevel modelling

--- 2021-03-04 r_notebooks/ace_mlm.Rmd
@@
          dispensing = as_factor(dispensing),
-         cluster = str_replace_all(cluster, " ", "_"),
-         cluster = str_remove_all(cluster, "[/&]"),
          cluster = as_factor(cluster),
@@
          gp_load = npat/ngp) %>% 
-  filter(year == 2020) %>% 
   ungroup() %>% 
   janitor::clean_names()
-unique(gp$cluster)
+
 differences_files <- 
@@
           .id = "drug") %>% 
-  mutate(drug = as_factor(drug),
-         prop = (prop * 100) - 100) %>% 
+  mutate(drug = as_factor(drug)) %>% 
   select(drug, regional_unit, datename, prop)
@@
 
+## Disease profiles
+
+```{r}
+df <- select(filter(gp, year == "2020"), p_fem:flu)
+psych::fa.parallel(df)
+five_fac <- psych::fa(df, nfactors = 4, rotate = "varimax")
+print(five_fac$loadings, cutoff = .2)
+
+dis_pca <- psych::principal(df, nfactors = 3, scores = TRUE)
+plot(dis_pca$values)
+dis_pca$rotation
+dis_pca_scores <- bind_cols(practice_id = filter(gp, year == "2020")$practice_id, dis_pca$scores)
+
+# 2d plot
+x <- dis_pca$loadings[,1]
+y <- dis_pca$loadings[,2]
+z <- dis_pca$loadings[,3]
+
+pca_plot_df <- bind_cols(dis = names(x), x = x, y = y, z = z)
+
+ggplot(aes(x = x, y = y), data = pca_plot_df) +
+  geom_text(aes(label = dis))
+
+ggplot(aes(x = x, y = z), data = pca_plot_df) +
+  geom_text(aes(label = dis))
+
+# 3d plot
+plotly::plot_ly(x=x, y=y, z=z, data = pca_plot_df,
+                type="scatter3d", mode="text", text = ~dis)
+```
+
 ## MLM
@@
       data = mlm_df, 
-      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE))
+      warmup = 1000, iter = 3000, seed = 123, save_pars = save_pars(all = TRUE))
 
@@
   geom_line() +
-  geom_vline(xintercept = 2000) +
+  geom_vline(xintercept = 1000) +
   facet_grid(Parameter ~ .,
@@
              switch = "y")
-
 ```
@@
   kable(digits = 2)
-
-mar_mlm1 %>% 
-  sjstats::tidy_stan()
 ```
@@
       warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
-      control = list(max_treedepth = 15, adapt_delta = .999))
+      control = list(max_treedepth = 15))
 
@@
 mar_mlm2_params %>% 
-  kable(digits = 2)
-```
-
-* Removing gp_load as 0 effect and 0 variance
-
-```{r, mar-mlm3-cluster-model}
-mar_mlm3 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 +
-              (1 + p_fem + pm_65 + dispensing + wimd2019|cluster),  
-      data = mlm_df, 
-      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
-      control = list(max_treedepth = 15, adapt_delta = .999))
-
-mar_mlm3_params <- modelParams(mar_mlm3)
-```
-
-```{r, mar-m3-cluster-convergence}
-mar_mlm3 %>% 
-  ggs() %>% 
-  filter(Parameter %in% c("b_Intercept", "b_p_fem", "b_pm_65", "b_dispensingYes",
-                          "b_wimd2019", "b_gp_load")) %>% 
-  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
-  geom_line() +
-  geom_vline(xintercept = 2000) +
-  facet_grid(Parameter ~ .,
-             scale = "free_y",
-             switch = "y")
-```
-
-```{r, mar-m3-cluster-params}
-mar_mlm3_params %>% 
   kable(digits = 2)
@@
       data = mlm_df, 
-      warmup = 2000, iter = 4000, seed = 123, save_pars = save_pars(all = TRUE))
+      warmup = 1000, iter = 3000, seed = 123, save_pars = save_pars(all = TRUE))
 
@@
 ```{r, apr-m2-cluster-model, include=FALSE}
-apr_mlm2 <- brm(april ~ 1 + march +
+apr_mlm2 <- brm(march ~ 1 + march +
                   p_fem + pm_65 + dispensing + wimd2019 + gp_load +
@@
       data = mlm_df, 
-      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
-      control = list(max_treedepth = 15, adapt_delta = .999))
+      warmup = 1000, iter = 3000, seed = 123, save_pars = save_pars(all = TRUE),
+      control = list(max_treedepth = 15))
 

### 2021-03-04 r_notebooks/ace_lpa.Rmd
Ace inhibitor latent profile analysis

---
title: "Ace inhibitors LPA"
author: "Will A. S. Hardy"
date: "27/01/2021"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(tsibble)
library(tidyLPA)
library(future)
library(furrr)
library(tidymodels)
library(workflows)
library(tune)
library(nnet)

knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

set.seed(32)

gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid),
         dispensing = as_factor(dispensing),
         hboard = as_factor(str_remove_all(hboard, "W110000"))) %>% 
  ungroup() %>% 
  janitor::clean_names()

differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug)) %>% 
  select(drug, regional_unit, datename, discrepancy)

proportions <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug)) %>% 
  select(drug, regional_unit, datename, prop)

drugs <- unique(as.character(differences$drug))

```

## Data cleaning

```{r, data-problem-values, warning=FALSE}
differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  psych::describeBy(group = "drug", fast = TRUE)

proportions %>% 
  pivot_wider(names_from = datename, values_from = prop) %>% 
  psych::describeBy(group = "drug", fast = TRUE)
```

* Problem with `oac` data
* Infinite values have been calculated when something has been divided by zero. Is this when the total prescribing of oac has been zero, thus wafarin as a percentage of 0 is Inf?

```{r, data-which-problem}
differences %>% 
  filter(drug == "oac" & 
           (is.na(discrepancy) | is.nan(discrepancy) | is.infinite(discrepancy))) %>% 
  group_by(datename) %>% 
  count()

differences %>% 
  filter(drug == "oac" & 
           (is.na(discrepancy) | is.nan(discrepancy) | is.infinite(discrepancy))) %>% 
  group_by(drug, regional_unit) %>% 
  count()
```

* Missing/inappropriate data in five practices
* Removed these practices from the `oac` data

```{r, data-cleaning}
differences <- 
  differences %>% 
  anti_join(y = differences %>% 
              filter(drug == "oac" & 
                       (is.na(discrepancy) |
                          is.nan(discrepancy) | 
                          is.infinite(discrepancy))) %>% 
              group_by(drug, regional_unit) %>% 
              count(), 
            by = c("drug", "regional_unit"))

differences_wide <- 
  differences %>% 
  pivot_wider(names_from = datename, values_from = discrepancy)

proportions_wide <- 
  proportions %>% 
  pivot_wider(names_from = datename, values_from = prop)
```

## Disease profiles

```{r}
df <- select(filter(gp, year == "2020"), chd:flu) %>% 
  slice_sample(prop = .5)
psych::fa.parallel(df)
five_fac <- psych::fa(df, nfactors = 3, rotate = "varimax")
print(five_fac$loadings, cutoff = .2)

dis_pca <- psych::principal(df, nfactors = 3, scores = TRUE)
plot(dis_pca$values)
dis_pca$rotation
dis_pca_scores <- bind_cols(practice_id = filter(gp, year == "2020")$practice_id, dis_pca$scores)

# 2d plot
x <- dis_pca$loadings[,1]
y <- dis_pca$loadings[,2]
z <- dis_pca$loadings[,3]

pca_plot_df <- bind_cols(dis = names(x), x = x, y = y, z = z)

ggplot(aes(x = x, y = y), data = pca_plot_df) +
  geom_text(aes(label = dis))

ggplot(aes(x = x, y = z), data = pca_plot_df) +
  geom_text(aes(label = dis))

# 3d plot
plotly::plot_ly(x=x, y=y, z=z, data = pca_plot_df,
                type="scatter3d", mode="text", text = ~dis)
```

## Latent profile analysis

### difference
#### LPA estimation

```{r, ace-lpa-diff}
tictoc::tic()
ace_diff_lpa <- 
  differences_wide %>% 
  filter(drug == "ace" & `2020 May` > -100) %>% 
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = 1:8,
                    models = c(1:3))
tictoc::toc()
```

#### LPA model selection

```{r, ace-fits-diff}
ace_diff_lpa_fits <- 
  compare_solutions(ace_diff_lpa, statistics = 
                      c("BIC", "BLRT_p", "Entropy", "prob_min", "n_min"))
ace_diff_lpa_fits

ace_diff_lpa_fits$fits %>% 
  mutate(Model = as.factor(Model),
         Classes = as.factor(Classes)) %>% 
  pivot_longer(names_to = "IC", cols = c(BIC, Entropy, prob_min, n_min)) %>% 
  ggplot(aes(x = Classes, colour = Model, group = Model)) +
  geom_line(aes(y = value)) +
  facet_wrap(~IC, scales = "free")

```

* AIC, BIC, SABIC all suggest model 2 is best fit with 6, 4, 6 classes
* BLRT < 6 classes for model 2
  * AIC and SABIC suggest 5 classes are best when BLRT threshold applied
* Entropy decreases when increasing from 4 to 5 classes
* Selected model 2 with 4 classes.

```{r, ace-diff-prof-vis}
ace_diff_lpa %>%
  plot_profiles(rawdata = FALSE, sd = FALSE)

differences_wide %>% 
  filter(drug == "ace" & `2020 May` > -100) %>% 
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = c(3:8),
                    models = 2) %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)
```

```{r, ace-profile-vis-diff}
ace_diff_lpa$model_2_class_4 %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)

df <- 
  ace_diff_lpa$model_2_class_4 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
               names_to = "datename") %>% 
  mutate(Class = as.factor(Class),
         datename = as_factor(datename))

df %>% 
  ggplot(aes(x = datename, y = difference, colour = Class)) +
  geom_boxplot() +
  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75))

df %>% 
  ggplot(aes(x = datename, y = difference)) +
  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .1) +
  stat_summary(fun = "mean") +
  facet_wrap(~Class) +
  theme(legend.position = "none")

ace_diff_lpa$model_2_class_4 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  mutate(Class = as.factor(Class)) %>% 
  aov(`2020 Mar` ~ Class, data = .) %>% 
  summary()

ace_diff_lpa$model_2_class_4 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  mutate(Class = as.factor(Class)) %>% 
  aov(`2020 Mar` ~ Class, data = .) %>% 
  TukeyHSD()
```

* Class 1 - 
* Class 2 - 
* Class 3 - 
* Class 4 -

#### Multinomial logistic regression

```{r, ace-multinom-diff-data}
ace_multinom_data <- 
  ace_diff_lpa$model_2_class_4 %>% 
  get_data() %>% 
  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>% 
  mutate(gp_load = npat/ngp) %>% 
  select(Class, pm_65, p_fem, wimd2019, dispensing, ngp, gp_load, hboard) %>%
  mutate(Class = as.factor(Class),
         hboard = as.factor(hboard))

ace_multinom_data %>% 
  DataExplorer::plot_correlation()
```

##### Class 1 ref

```{r, ace-multinom-diff-ref1}
# Class 1 as ref class
ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "1")
ace_m1 <- 
  ace_multinom_data %>% 
  multinom(Class ~ ., family = "binomial", data = .)

summary(ace_m1)
print("relative risk"); exp(coef(ace_m1))

ace_m1_z <- summary(ace_m1)$coefficients/summary(ace_m1)$standard.errors
#ace_m1_z

# Two-tailed z-test
print("Wald test p-value")
ace_m1_p <- (1 - pnorm(abs(ace_m1_z), 0, 1)) * 2
ace_m1_p
```

##### Class 2 ref

```{r, ace-multinom-diff-ref2}
# Class 2 as ref class
ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "2")
ace_m2 <- 
  ace_multinom_data %>% 
  multinom(Class ~ ., family = "binomial", data = .)

summary(ace_m2)
print("relative risk"); exp(coef(ace_m2))

ace_m2_z <- summary(ace_m2)$coefficients/summary(ace_m2)$standard.errors
# ace_m2_z

# Two-tailed z-test
print("Wald test p-value")
ace_m2_p <- (1 - pnorm(abs(ace_m2_z), 0, 1)) * 2
ace_m2_p
```

##### Class 3 ref

```{r, ace-multinom-diff-ref3}
# Class 3 as ref class
ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "3")
ace_m3 <- 
  ace_multinom_data %>% 
  multinom(Class ~ ., family = "binomial", data = .)

summary(ace_m3)
print("relative risk"); exp(coef(ace_m3))

ace_m3_z <- summary(ace_m3)$coefficients/summary(ace_m3)$standard.errors
# ace_m3_z

# Two-tailed z-test
print("Wald test p-value")
ace_m3_p <- (1 - pnorm(abs(ace_m3_z), 0, 1)) * 2
ace_m3_p
```

```{r}
ace_multinom_data %>% 
  group_by(Class) %>% 
  summarise(dispensing = sum(if_else(as.character(dispensing) == "Yes", 1, 0))/n())
```

### proportion
#### LPA estimation

```{r, ace-prop-month-hist}
proportions %>% 
  filter(drug == "ace") %>% 
  ggplot(aes(x = prop)) + 
  geom_histogram() +
  facet_wrap(~as.factor(datename))
```

```{r, ace-lpa-prop}
tictoc::tic()
ace_prop_lpa <- 
  proportions_wide %>% 
  filter(drug == "ace") %>%
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = 1:8,
                    models = c(1:3))
tictoc::toc()
```

#### LPA model selection

```{r, ace-fits-prop}
ace_prop_lpa_fits <- 
  compare_solutions(ace_prop_lpa, 
                    c("BIC", "BLRT_p", "Entropy", "prob_min", "n_min"))

ace_prop_lpa_fits

ace_prop_lpa_fits$fits %>% 
  mutate(Model = as.factor(Model),
         Classes = as.factor(Classes)) %>% 
  pivot_longer(names_to = "IC", cols = c(BIC, Entropy, prob_min, n_min)) %>% 
  ggplot(aes(x = Classes, colour = Model, group = Model)) +
  geom_line(aes(y = value)) +
  facet_wrap(~IC, scales = "free")

```

* Selected model 2 with 6 classes.
  * BLRT suggests fewer than 5 classes
  * AIC suggests 7 classes
  * BIC favours 4 classes, but only small increase in BIC from 4 to 6 classes
  * SABIC suggests 6 classes
  * Entropy slightly between for 6 than 4 classes, but much worse than 2 classes

```{r, ace-prop-profile-plots}
ace_prop_lpa %>%
  plot_profiles(rawdata = FALSE, sd = FALSE)

differences_wide %>% 
  filter(drug == "ace" & `2020 Jul` > -50) %>% 
  estimate_profiles(df = ., 
                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
                                    "2020 Jun", "2020 Jul", "2020 Aug"),
                    n_profiles = c(3:8),
                    models = 2) %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)
```

```{r, ace-profile-vis-prop}
ace_prop_lpa$model_2_class_6 %>% 
  plot_profiles(rawdata = FALSE, sd = FALSE)

df <- 
  ace_prop_lpa$model_2_class_6 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
  rownames_to_column() %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "proportion", 
               names_to = "datename") %>% 
  mutate(Class = as.factor(Class),
         datename = as_factor(datename))

df %>% 
  ggplot(aes(x = datename, y = proportion, colour = Class)) +
  geom_boxplot() +
  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75)) +
  geom_hline(yintercept = 1, colour = "red", lty =2)

df %>% 
  ggplot(aes(x = datename, y = proportion)) +
  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .2) +
  stat_summary(fun = "mean", size = .1) +
  facet_wrap(~Class) +
  theme(legend.position = "none") +
  coord_cartesian(ylim = c(.75, 1.25)) +
  geom_hline(yintercept = 1, colour = "red", lty =2)

ace_prop_lpa$model_2_class_6 %>% 
  get_data() %>% 
  group_by(Class) %>% 
  count()
```

```{r, ace-prop-mean-vis}
ace_prop_lpa$model_2_class_6 %>% 
  get_data() %>% 
  group_by(Class) %>% 
  summarise(across(`2020 Mar`:`2020 Aug`, median)) %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, 
               names_to = "datename", values_to = "proportion") %>% 
  mutate(datename = yearmonth(datename),
         Class = as.factor(Class)) %>% 
  ggplot(aes(x = datename, y = proportion, colour = Class)) +
  geom_line() +
  geom_hline(yintercept = 1, colour = "red", lty =2)
```

```{r, ace-prop-aov}
df <- 
  ace_prop_lpa$model_2_class_6 %>% 
  get_data() %>% 
  select(-c(model_number, classes_number, starts_with("CPROB"), 
            drug)) %>% 
  mutate(Class = as.factor(Class)) %>% 
  pivot_longer(cols = `2020 Mar`:`2020 Aug`, names_to = "datename")

df %>% 
  split(.$datename) %>% 
  map(~aov(value ~ Class, data = .)) %>% 
  map_dfr(broom::tidy, .id = "month") %>% 
  mutate(month = yearmonth(month)) %>% 
  arrange(month, term)

df %>% 
  split(.$datename) %>% 
  map(~aov(value ~ Class, data = .)) %>% 
  map(TukeyHSD) %>% 
  map_dfr(broom::tidy, .id = "month") %>% 
  mutate(month = yearmonth(month)) %>% 
  select(-c(null.value, term)) %>% 
  arrange(month) %>% 
  mutate(adj.p.value = papaja::printnum(adj.p.value, zero = FALSE))
```

* Class 1
  * n = 58
  * High in Mar, slight depression for Apr & May, as forecast in Jun & Jul, low levels in Aug. Moderate variability throughout.
  * Stockpiling followed by reduced prescribing for two months before returning to "normal" for two months
* Class 2
  * n = 26
  * Very high in Mar, decreased prescribing in Apr, then extremely variable prescribing for the remaining months.
  * Very high levels of stockpiling followed by chaotic prescribing.
* Class 3
  * n = 125
  * Elevated levels of prescribing in Mar, as forecast in Apr, slight reduction in May, as forecast in Jun & Jul, then reduced prescribing in Aug. Very low levels of variability.
  * Business as usual with limited stockpiling
* Class 4
  * n = 85
  * High levels of prescribing in Mar & Apr, as forecast May, slight elevation in Jun & Jul, slight depression in Aug but still higher than others. Low levels of variability.
* Class 5
  * n = 72
  * High in Mar, as forecast in Apr, low levels in May, as forecast in Jun & Jul, low levels in Aug. Low levels of variability.
* Class 6
  * n = 36
  * High in Mar, extremely variable in Apr with prescribing as forecast, variable levels just below forecast, reduced variability and low levels of prescribing in Jun, as forecast in Jul, and low levels in Aug.

#### Multinomial logistic regression

```{r, ace-multinom-prop-data}
ace_multinom_prop_data <-
  ace_prop_lpa$model_2_class_6 %>%
  get_data() %>%
  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>%
  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>%
  mutate(gp_load = npat/ngp) %>%
  select(Class, hyp, p_fem, wimd2019, dispensing, ngp, gp_load) %>%
  mutate(Class = as.factor(Class),
        #hboard = as.factor(hboard)
        )

ace_multinom_prop_data %>% 
  DataExplorer::plot_correlation()

car::vif(lm(as.numeric(Class) ~ ., data = ace_multinom_prop_data))

```

##### Class 1 ref

```{r, ace-multinom-prop-ref1}
# Class 1 as ref class
ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "1")
ace_prop_m1 <- 
  ace_multinom_prop_data %>% 
  multinom(Class ~ ., family = "binomial", data = .)

summary(ace_prop_m1)
print("relative risk"); exp(coef(ace_prop_m1))

ace_prop_m1_z <- summary(ace_prop_m1)$coefficients/summary(ace_prop_m1)$standard.errors
#ace_m1_z

# Two-tailed z-test
print("Wald test p-value")
ace_prop_m1_p <- (1 - pnorm(abs(ace_prop_m1_z), 0, 1)) * 2
ace_prop_m1_p

ace_multinom_prop_data %>% 
  group_by(Class) %>% 
  summarise(dispensing = mean(if_else(dispensing == "Yes", 1, 0)),
            wimd = median(wimd2019),
            hyp = median(hyp))
```

```{r}
coef(ace_prop_m1) %>% 
  as_tibble(rownames = "Class") %>% 
  pivot_longer(cols = `(Intercept)`:gp_load, values_to = "coefficient",
               names_to = "variable") %>% 
  left_join(summary(ace_prop_m1)$standard.errors %>% 
  as_tibble(rownames = "Class") %>% 
  pivot_longer(cols = `(Intercept)`:gp_load, values_to = "se",
               names_to = "variable")) %>% 
  mutate(Class = as.factor(Class)) %>% 
  ggplot(aes(x = coefficient, y = variable, group = Class, colour = Class)) +
  geom_point(position = position_dodge(width = .5)) +
  geom_errorbarh(aes(xmin = coefficient - 2 * se, xmax = coefficient + 2 * se),
                 position = position_dodge(width = .5))

ace_multinom_prop_data %>% 
  # mutate(across(where(is.numeric), scale)) %>% 
  pivot_longer(cols = where(is.numeric), names_to = "variable") %>% 
  ggplot(aes(x = Class, y = value, colour = Class)) +
  geom_boxplot() +
  facet_wrap(~variable, scales = "free")

# sjPlot::plot_model(ace_prop_m1, type = "pred", terms = c("pm_65 [all]", "dispensing"))
sjPlot::plot_model(ace_prop_m1, type = "eff")
```

##### Class 2 ref

```{r, ace-multinom-prop-ref2}
# Class 2 as ref class
ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "2")
ace_prop_m2 <- 
  ace_multinom_prop_data %>% 
  multinom(Class ~ ., family = "binomial", data = .)

summary(ace_prop_m2)
print("relative risk"); exp(coef(ace_prop_m2))

ace_prop_m2_z <- summary(ace_prop_m2)$coefficients/summary(ace_prop_m2)$standard.errors

# Two-tailed z-test
print("Wald test p-value")
ace_prop_m2_p <- (1 - pnorm(abs(ace_prop_m2_z), 0, 1)) * 2
ace_prop_m2_p
```

##### Class 3 ref

```{r, ace-multinom-prop-ref3}
# Class 3 as ref class
ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "3")
ace_prop_m3 <- 
  ace_multinom_prop_data %>% 
  multinom(Class ~ ., family = "binomial", data = .)

summary(ace_prop_m3)
print("relative risk"); exp(coef(ace_prop_m3))

ace_prop_m3_z <- summary(ace_prop_m3)$coefficients/summary(ace_prop_m3)$standard.errors

# Two-tailed z-test
print("Wald test p-value")
ace_prop_m3_p <- (1 - pnorm(abs(ace_prop_m3_z), 0, 1)) * 2
ace_prop_m3_p
```

##### Class 4 ref

```{r, ace-multinom-prop-ref4}
# Class 2 as ref class
ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "4")
ace_prop_m4 <- 
  ace_multinom_prop_data %>% 
  multinom(Class ~ ., family = "binomial", data = .)

summary(ace_prop_m4)
print("relative risk"); exp(coef(ace_prop_m4))

ace_prop_m4_z <- summary(ace_prop_m4)$coefficients/summary(ace_prop_m4)$standard.errors

# Two-tailed z-test
print("Wald test p-value")
ace_prop_m4_p <- (1 - pnorm(abs(ace_prop_m4_z), 0, 1)) * 2
ace_prop_m4_p
```

##### Class 5 ref

```{r, ace-multinom-prop-ref5}
# Class 2 as ref class
ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "5")
ace_prop_m5 <- 
  ace_multinom_prop_data %>% 
  multinom(Class ~ ., family = "binomial", data = .)

summary(ace_prop_m5)
print("relative risk"); exp(coef(ace_prop_m5))

ace_prop_m5_z <- summary(ace_prop_m5)$coefficients/summary(ace_prop_m5)$standard.errors

# Two-tailed z-test
print("Wald test p-value")
ace_prop_m5_p <- (1 - pnorm(abs(ace_prop_m5_z), 0, 1)) * 2
ace_prop_m5_p
```

### 2021-03-04 writing/paper.Rmd
Method outline and all prescribing inital plots

@@
 ## Packages
+devtools::install_github("https://github.com/w-hardy/serCymruTools")
 library(tidyverse)
@@
 library(fable.prophet)
+library(fasster)
 library(feasts)
@@
 * Given the presence of seasonal variation and existing trends in levels of prescribing, we used various time series forecasting methods to account for existing trends and seasonal variation when creating the forecasts.
+* For each analysis, we created a forecast that aimed to answer the question, "What would the levels of prescribing have been if COVID-19 had not affected Wales?" We then used these forecasts to estimate the changes in levels of prescribing due to COVID-19.
+* We viewed this, somewhat complex, approach as superior to more simple approaches (e.g., carrying last years levels forward, or even using the mean of the last three years).
 
-* For each analysis, we created a forecast that aimed to answer the question, "What would the levels of prescribing have been if COVID-19 had not affected Wales?" We then used these forecasts to estimate the changes in levels of prescribing due to COVID-19.
+### Forecasting models
 
-  * We viewed this, somewhat complex, approach as superior to more simple approaches (e.g., carrying last years levels forward, or even using the mean of the last three years).
 * We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
-  * Using Jan 2015 to Feb 2020 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
-    * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
-    * Only interested in one forecast horizon: six-months
-    * 
-  * Having chosen the "best model" for each practice based on the pre-COVID data, we then used this to forecast the level of prescribing for each practice
-
-* We used time series modelling to forecast Welsh primary care prescribing levels had .
-    * We used the `fable` [@R-fable] and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
+* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
   * Time series linear model
@@
 * Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
-  * Model selection
-    * RMSE then MAE
+* Using Jan 2015 to Feb 2020 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
+  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
+    * Only interested in one forecast horizon: six-months
+
+### Model selection
+
+* Ranked by RMSE and Winkler [@Winkler1972], then the best mean ranking model is chosen
+  * RMSE is scale dependant. Is suitable for comparing models of the same data.
+  * Winkler score penalises models that have observations falling outside the prediction interval, thus rewards models with narrow intervals
+* This combination accounts for both the point and distributional accuracy of the forecasts
+
+### Forecasts
+
+* Having chosen the "best model" for each practice based on the pre-COVID data, we then used this model to forecast the level of prescribing for each practice
 
@@
                            rmse_skill = skill_score(RMSE),
-                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
+                           crps_skill = skill_score(CRPS), ACF1 = ACF1,
                            winkler = winkler_score))
@@
   bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
-  arrange(RMSE, MAE)
+  rankModels()
 
@@
   all_prescribing_combined_fits %>% 
-  arrange(RMSE, MAE) %>% 
   slice(1, .preserve = TRUE)
@@
 plan(sequential)
+
 ```
@@
 ```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy"}
-all_prescribing_combined_fits %>% 
-  ggplot(aes(x = reorder(.model, RMSE, mean), y = RMSE)) +
+p1 <- all_prescribing_combined_fits %>% 
+  na.omit() %>% 
+  ggplot(aes(x = reorder(.model, rank, sort), y = RMSE)) +
   geom_col()
+
+p2 <- all_prescribing_combined_fits %>% 
+  na.omit() %>% 
+  ggplot(aes(x = reorder(.model, rank, sort), y = winkler)) +
+  geom_col()
+
+cowplot::plot_grid(p1, p2)
 ```
@@
   ggplot(aes(x = datename)) +
-  geom_line(aes(y = n, col = "Observed")) +
-  geom_line(aes(y = med, col = "Forecast"), 
+  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
+  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
             data = all_prescribing_covid_forecast) +
-  geom_line(aes(y = fitted, col = "Fitted"), 
+  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
+                   fill = "Forecast"), alpha = .5,
+              data = all_prescribing_covid_forecast) +
+  geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
             data = all_prescribing_best_cv_model %>% 
               group_by(datename) %>% 
-              summarise(fitted = mean(.fitted, na.rm = TRUE))) +
+              summarise(fitted = median(.fitted, na.rm = TRUE))) +
   geom_vline(xintercept = ymd("2020-03-01"), lty = 3)

### 2021-03-04 writing/paper.tex
Method outline and all prescribing inital plots

@@
   \item
-    We used the \texttt{fable} (O'Hara-Wild et al., 2021a) and the \texttt{fable.prophet} (O'Hara-Wild, 2020) packages to conduct the time series analyses.
+    We used the \texttt{fable} (O'Hara-Wild et al., 2021a), \texttt{fasster} (O'Hara-Wild \& Hyndman, 2021), and the \texttt{fable.prophet} (O'Hara-Wild, 2020) packages to conduct the time series analyses.
   \item
@@
     \item
-      RMSE then MAE
+      Ranked by RMSE and Winkler ({\textbf{???}}), then the best mean ranking model is chosen
+
+      \begin{itemize}
+      \tightlist
+      \item
+        Winkler score penalises models that have observations falling outside the prediction interval, thus rewards models with narrow intervals
+      \end{itemize}
+    \item
+      This combination accounts for both the point and distributional accuracy of the forecasts
     \end{itemize}
@@
 
-We used R (Version 4.0.2; R Core Team, 2020) and the R-packages \emph{dplyr} (Version 1.0.4; Wickham, François, et al., 2021), \emph{fable} (Version 0.3.0; O'Hara-Wild et al., 2021a, 2021b; O'Hara-Wild, 2020), \emph{fable.prophet} (Version 0.1.0; O'Hara-Wild, 2020), \emph{fabletools} (Version 0.3.0; O'Hara-Wild et al., 2021b), \emph{feasts} (Version 0.1.7; O'Hara-Wild et al., 2021c), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{furrr} (Version 0.2.2; Vaughan \& Dancho, 2021), \emph{future} (Version 1.21.0; Bengtsson, 2020), \emph{ggplot2} (Version 3.3.3; Wickham, 2016), \emph{lubridate} (Version 1.7.10; Grolemund \& Wickham, 2011), \emph{MplusAutomation} (Version 0.8; Hallquist \& Wiley, 2018), \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020), \emph{prophet} (Version 0.6.1; O'Hara-Wild, 2020; Taylor \& Letham, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020a), \emph{Rcpp} (Version 1.0.6; Eddelbuettel \& François, 2011; Eddelbuettel \& Balamuta, 2018), \emph{readr} (Version 1.4.0; Wickham \& Hester, 2020), \emph{rebus} (Version 0.1.3; Cotton, 2017), \emph{rlang} (Version 0.4.10; Henry \& Wickham, 2020b), \emph{rstan} (Version 2.21.2; Stan Development Team, 2020a), \emph{serCymruTools} (Version 0.1.3; Will, 2021), \emph{StanHeaders} (Version 2.21.0.7; Stan Development Team, 2020b), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.0; Müller \& Wickham, 2021), \emph{tidyLPA} (Version 1.0.8; Rosenberg et al., 2018), \emph{tidyr} (Version 1.1.3; Wickham, 2020), \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019), and \emph{tsibble} (Version 1.0.0; Wang et al., 2020) for all our analyses, functions are available in the \texttt{serCymruTools} package (Will, 2021), and all other code is available at \url{https://github.com/w-hardy/sercymru}.
+We used R (Version 4.0.2; R Core Team, 2020) and the R-packages \emph{dplyr} (Version 1.0.4; Wickham, François, et al., 2021), \emph{fable} (Version 0.3.0; O'Hara-Wild et al., 2021a, 2021b; O'Hara-Wild, 2020), \emph{fable.prophet} (Version 0.1.0; O'Hara-Wild, 2020), \emph{fabletools} (Version 0.3.0; O'Hara-Wild et al., 2021b), \emph{fasster} (Version 0.1.0.9100; O'Hara-Wild \& Hyndman, 2021), \emph{feasts} (Version 0.1.7; O'Hara-Wild et al., 2021c), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{furrr} (Version 0.2.2; Vaughan \& Dancho, 2021), \emph{future} (Version 1.21.0; Bengtsson, 2020), \emph{ggplot2} (Version 3.3.3; Wickham, 2016), \emph{lubridate} (Version 1.7.10; Grolemund \& Wickham, 2011), \emph{MplusAutomation} (Version 0.8; Hallquist \& Wiley, 2018), \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020), \emph{prophet} (Version 0.6.1; O'Hara-Wild, 2020; Taylor \& Letham, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020a), \emph{Rcpp} (Version 1.0.6; Eddelbuettel \& François, 2011; Eddelbuettel \& Balamuta, 2018), \emph{readr} (Version 1.4.0; Wickham \& Hester, 2020), \emph{rebus} (Version 0.1.3; Cotton, 2017), \emph{rlang} (Version 0.4.10; Henry \& Wickham, 2020b), \emph{rstan} (Version 2.21.2; Stan Development Team, 2020a), \emph{serCymruTools} (Version 0.1.3; Will, 2021), \emph{StanHeaders} (Version 2.21.0.7; Stan Development Team, 2020b), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.0; Müller \& Wickham, 2021), \emph{tidyLPA} (Version 1.0.8; Rosenberg et al., 2018), \emph{tidyr} (Version 1.1.3; Wickham, 2020), \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019), and \emph{tsibble} (Version 1.0.0; Wang et al., 2020) for all our analyses, functions are available in the \texttt{serCymruTools} package (Will, 2021), and all other code is available at \url{https://github.com/w-hardy/sercymru}.
 
@@
 
-\begin{verbatim}
-## Warning: Removed 2 rows containing missing values (position_stack).
-\end{verbatim}
+\includegraphics{paper_files/figure-latex/all-prescribing-modelling-1.pdf}
 
@@
 \end{figure}
+
+\begin{verbatim}
+## Warning: Ignoring unknown aesthetics: fill
+
+## Warning: Ignoring unknown aesthetics: fill
+
+## Warning: Ignoring unknown aesthetics: fill
+\end{verbatim}
 
@@
 
+\leavevmode\hypertarget{ref-R-fasster}{}%
+O'Hara-Wild, M., \& Hyndman, R. (2021). \emph{Fasster: Fast additive switching of seasonality, trend and exogenous regressors}. \url{https://github.com/mitchelloharawild/fasster}
+
 \leavevmode\hypertarget{ref-R-fable}{}%

### 2021-03-04 r_notebooks/oac_lpa.Rmd
Oral antigoagulant latent profile analysis

--- 2021-03-04 r_notebooks/ace_lpa.Rmd
@@
 ---
-title: "Ace inhibitors LPA"
+title: "oac inhibitors LPA"
 author: "Will A. S. Hardy"
@@
   pivot_wider(names_from = datename, values_from = discrepancy)
-
-proportions_wide <- 
-  proportions %>% 
-  pivot_wider(names_from = datename, values_from = prop)
 ```
@@
 ```{r}
-df <- select(filter(gp, year == "2020"), chd:flu) %>% 
-  slice_sample(prop = .5)
+df <- select(filter(gp, year == "2020"), p_fem:flu)
 psych::fa.parallel(df)
-five_fac <- psych::fa(df, nfactors = 3, rotate = "varimax")
+five_fac <- psych::fa(df, nfactors = 4, rotate = "varimax")
 print(five_fac$loadings, cutoff = .2)
@@
 
-```{r, ace-lpa-diff}
+```{r, oac-lpa-diff}
 tictoc::tic()
-ace_diff_lpa <- 
+oac_diff_lpa <- 
   differences_wide %>% 
-  filter(drug == "ace" & `2020 May` > -100) %>% 
+  filter(drug == "oac" & `2020 May` > -100) %>% 
   estimate_profiles(df = ., 
@@
 
-```{r, ace-fits-diff}
-ace_diff_lpa_fits <- 
-  compare_solutions(ace_diff_lpa, statistics = 
+```{r, oac-fits-diff}
+oac_diff_lpa_fits <- 
+  compare_solutions(oac_diff_lpa, statistics = 
                       c("BIC", "BLRT_p", "Entropy", "prob_min", "n_min"))
-ace_diff_lpa_fits
+oac_diff_lpa_fits
 
-ace_diff_lpa_fits$fits %>% 
+oac_diff_lpa_fits$fits %>% 
   mutate(Model = as.factor(Model),
@@
 
-```{r, ace-diff-prof-vis}
-ace_diff_lpa %>%
+```{r, oac-diff-prof-vis}
+oac_diff_lpa %>%
   plot_profiles(rawdata = FALSE, sd = FALSE)
@@
 differences_wide %>% 
-  filter(drug == "ace" & `2020 May` > -100) %>% 
+  filter(drug == "oac" & `2020 May` > -100) %>% 
   estimate_profiles(df = ., 
@@
 
-```{r, ace-profile-vis-diff}
-ace_diff_lpa$model_2_class_4 %>% 
+```{r, oac-profile-vis-diff}
+oac_diff_lpa$model_2_class_4 %>% 
   plot_profiles(rawdata = FALSE, sd = FALSE)
@@
 df <- 
-  ace_diff_lpa$model_2_class_4 %>% 
+  oac_diff_lpa$model_2_class_4 %>% 
   get_data() %>% 
@@
 
-ace_diff_lpa$model_2_class_4 %>% 
+oac_diff_lpa$model_2_class_4 %>% 
   get_data() %>% 
@@
 
-* Class 1 - 
-* Class 2 - 
-* Class 3 - 
-* Class 4 -
+* Class 1 - Reduced switching
+* Class 2 - Reduced switching Mar then normal switching
+* Class 3 - Increased switching Apr & May
+* Class 4 - Greatly increased switching Apr & May
 
@@
 
-```{r, ace-multinom-diff-data}
-ace_multinom_data <- 
-  ace_diff_lpa$model_2_class_4 %>% 
+```{r, oac-multinom-data}
+oac_multinom_data <- 
+  oac_diff_lpa$model_2_class_4 %>% 
   get_data() %>% 
@@
   mutate(gp_load = npat/ngp) %>% 
-  select(Class, pm_65, p_fem, wimd2019, dispensing, ngp, gp_load, hboard) %>%
+  select(Class, p_fem, af, wimd2019, dispensing, ngp, gp_load, hboard) %>%
   mutate(Class = as.factor(Class),
@@
 
-ace_multinom_data %>% 
+oac_multinom_data %>% 
   DataExplorer::plot_correlation()
@@
 
-```{r, ace-multinom-diff-ref1}
+```{r, oac_multinom_data-ref1}
 # Class 1 as ref class
-ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "1")
-ace_m1 <- 
-  ace_multinom_data %>% 
+oac_multinom_data$Class <- relevel(oac_multinom_data$Class, ref = "1")
+oac_diff_m1 <- 
+  oac_multinom_data %>% 
   multinom(Class ~ ., family = "binomial", data = .)
 
-summary(ace_m1)
-print("relative risk"); exp(coef(ace_m1))
+summary(oac_diff_m1)
+print("relative risk"); exp(coef(oac_diff_m1))
 
-ace_m1_z <- summary(ace_m1)$coefficients/summary(ace_m1)$standard.errors
-#ace_m1_z
+oac_diff_m1_z <- summary(oac_diff_m1)$coefficients/summary(oac_diff_m1)$standard.errors
 
@@
 print("Wald test p-value")
-ace_m1_p <- (1 - pnorm(abs(ace_m1_z), 0, 1)) * 2
-ace_m1_p
-```
+oac_diff_m1_p <- (1 - pnorm(abs(oac_diff_m1_z), 0, 1)) * 2
+oac_diff_m1_p
 
-##### Class 2 ref
-
-```{r, ace-multinom-diff-ref2}
-# Class 2 as ref class
-ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "2")
-ace_m2 <- 
-  ace_multinom_data %>% 
-  multinom(Class ~ ., family = "binomial", data = .)
-
-summary(ace_m2)
-print("relative risk"); exp(coef(ace_m2))
-
-ace_m2_z <- summary(ace_m2)$coefficients/summary(ace_m2)$standard.errors
-# ace_m2_z
-
-# Two-tailed z-test
-print("Wald test p-value")
-ace_m2_p <- (1 - pnorm(abs(ace_m2_z), 0, 1)) * 2
-ace_m2_p
-```
-
-##### Class 3 ref
-
-```{r, ace-multinom-diff-ref3}
-# Class 3 as ref class
-ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "3")
-ace_m3 <- 
-  ace_multinom_data %>% 
-  multinom(Class ~ ., family = "binomial", data = .)
-
-summary(ace_m3)
-print("relative risk"); exp(coef(ace_m3))
-
-ace_m3_z <- summary(ace_m3)$coefficients/summary(ace_m3)$standard.errors
-# ace_m3_z
-
-# Two-tailed z-test
-print("Wald test p-value")
-ace_m3_p <- (1 - pnorm(abs(ace_m3_z), 0, 1)) * 2
-ace_m3_p
+oac_multinom_data %>% 
+  group_by(Class) %>% 
+  summarise(dispensing = mean(if_else(dispensing == "Yes", 1, 0)),
+            wimd = median(wimd2019),
+           # pm_65 = median(pm_65),
+            n = n())
 ```
@@
 ```{r}
-ace_multinom_data %>% 
-  group_by(Class) %>% 
-  summarise(dispensing = sum(if_else(as.character(dispensing) == "Yes", 1, 0))/n())
-```
-
-### proportion
-#### LPA estimation
-
-```{r, ace-prop-month-hist}
-proportions %>% 
-  filter(drug == "ace") %>% 
-  ggplot(aes(x = prop)) + 
-  geom_histogram() +
-  facet_wrap(~as.factor(datename))
-```
-
-```{r, ace-lpa-prop}
-tictoc::tic()
-ace_prop_lpa <- 
-  proportions_wide %>% 
-  filter(drug == "ace") %>%
-  estimate_profiles(df = ., 
-                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
-                                    "2020 Jun", "2020 Jul", "2020 Aug"),
-                    n_profiles = 1:8,
-                    models = c(1:3))
-tictoc::toc()
-```
-
-#### LPA model selection
-
-```{r, ace-fits-prop}
-ace_prop_lpa_fits <- 
-  compare_solutions(ace_prop_lpa, 
-                    c("BIC", "BLRT_p", "Entropy", "prob_min", "n_min"))
-
-ace_prop_lpa_fits
-
-ace_prop_lpa_fits$fits %>% 
-  mutate(Model = as.factor(Model),
-         Classes = as.factor(Classes)) %>% 
-  pivot_longer(names_to = "IC", cols = c(BIC, Entropy, prob_min, n_min)) %>% 
-  ggplot(aes(x = Classes, colour = Model, group = Model)) +
-  geom_line(aes(y = value)) +
-  facet_wrap(~IC, scales = "free")
-
-```
-
-* Selected model 2 with 6 classes.
-  * BLRT suggests fewer than 5 classes
-  * AIC suggests 7 classes
-  * BIC favours 4 classes, but only small increase in BIC from 4 to 6 classes
-  * SABIC suggests 6 classes
-  * Entropy slightly between for 6 than 4 classes, but much worse than 2 classes
-
-```{r, ace-prop-profile-plots}
-ace_prop_lpa %>%
-  plot_profiles(rawdata = FALSE, sd = FALSE)
-
-differences_wide %>% 
-  filter(drug == "ace" & `2020 Jul` > -50) %>% 
-  estimate_profiles(df = ., 
-                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
-                                    "2020 Jun", "2020 Jul", "2020 Aug"),
-                    n_profiles = c(3:8),
-                    models = 2) %>% 
-  plot_profiles(rawdata = FALSE, sd = FALSE)
-```
-
-```{r, ace-profile-vis-prop}
-ace_prop_lpa$model_2_class_6 %>% 
-  plot_profiles(rawdata = FALSE, sd = FALSE)
-
-df <- 
-  ace_prop_lpa$model_2_class_6 %>% 
-  get_data() %>% 
-  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
-  rownames_to_column() %>% 
-  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "proportion", 
-               names_to = "datename") %>% 
-  mutate(Class = as.factor(Class),
-         datename = as_factor(datename))
-
-df %>% 
-  ggplot(aes(x = datename, y = proportion, colour = Class)) +
-  geom_boxplot() +
-  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75)) +
-  geom_hline(yintercept = 1, colour = "red", lty =2)
-
-df %>% 
-  ggplot(aes(x = datename, y = proportion)) +
-  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .2) +
-  stat_summary(fun = "mean", size = .1) +
-  facet_wrap(~Class) +
-  theme(legend.position = "none") +
-  coord_cartesian(ylim = c(.75, 1.25)) +
-  geom_hline(yintercept = 1, colour = "red", lty =2)
-
-ace_prop_lpa$model_2_class_6 %>% 
-  get_data() %>% 
-  group_by(Class) %>% 
-  count()
-```
-
-```{r, ace-prop-mean-vis}
-ace_prop_lpa$model_2_class_6 %>% 
-  get_data() %>% 
-  group_by(Class) %>% 
-  summarise(across(`2020 Mar`:`2020 Aug`, median)) %>% 
-  pivot_longer(cols = `2020 Mar`:`2020 Aug`, 
-               names_to = "datename", values_to = "proportion") %>% 
-  mutate(datename = yearmonth(datename),
-         Class = as.factor(Class)) %>% 
-  ggplot(aes(x = datename, y = proportion, colour = Class)) +
-  geom_line() +
-  geom_hline(yintercept = 1, colour = "red", lty =2)
-```
-
-```{r, ace-prop-aov}
-df <- 
-  ace_prop_lpa$model_2_class_6 %>% 
-  get_data() %>% 
-  select(-c(model_number, classes_number, starts_with("CPROB"), 
-            drug)) %>% 
-  mutate(Class = as.factor(Class)) %>% 
-  pivot_longer(cols = `2020 Mar`:`2020 Aug`, names_to = "datename")
-
-df %>% 
-  split(.$datename) %>% 
-  map(~aov(value ~ Class, data = .)) %>% 
-  map_dfr(broom::tidy, .id = "month") %>% 
-  mutate(month = yearmonth(month)) %>% 
-  arrange(month, term)
-
-df %>% 
-  split(.$datename) %>% 
-  map(~aov(value ~ Class, data = .)) %>% 
-  map(TukeyHSD) %>% 
-  map_dfr(broom::tidy, .id = "month") %>% 
-  mutate(month = yearmonth(month)) %>% 
-  select(-c(null.value, term)) %>% 
-  arrange(month) %>% 
-  mutate(adj.p.value = papaja::printnum(adj.p.value, zero = FALSE))
-```
-
-* Class 1
-  * n = 58
-  * High in Mar, slight depression for Apr & May, as forecast in Jun & Jul, low levels in Aug. Moderate variability throughout.
-  * Stockpiling followed by reduced prescribing for two months before returning to "normal" for two months
-* Class 2
-  * n = 26
-  * Very high in Mar, decreased prescribing in Apr, then extremely variable prescribing for the remaining months.
-  * Very high levels of stockpiling followed by chaotic prescribing.
-* Class 3
-  * n = 125
-  * Elevated levels of prescribing in Mar, as forecast in Apr, slight reduction in May, as forecast in Jun & Jul, then reduced prescribing in Aug. Very low levels of variability.
-  * Business as usual with limited stockpiling
-* Class 4
-  * n = 85
-  * High levels of prescribing in Mar & Apr, as forecast May, slight elevation in Jun & Jul, slight depression in Aug but still higher than others. Low levels of variability.
-* Class 5
-  * n = 72
-  * High in Mar, as forecast in Apr, low levels in May, as forecast in Jun & Jul, low levels in Aug. Low levels of variability.
-* Class 6
-  * n = 36
-  * High in Mar, extremely variable in Apr with prescribing as forecast, variable levels just below forecast, reduced variability and low levels of prescribing in Jun, as forecast in Jul, and low levels in Aug.
-
-#### Multinomial logistic regression
-
-```{r, ace-multinom-prop-data}
-ace_multinom_prop_data <-
-  ace_prop_lpa$model_2_class_6 %>%
-  get_data() %>%
-  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>%
-  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>%
-  mutate(gp_load = npat/ngp) %>%
-  select(Class, hyp, p_fem, wimd2019, dispensing, ngp, gp_load) %>%
-  mutate(Class = as.factor(Class),
-        #hboard = as.factor(hboard)
-        )
-
-ace_multinom_prop_data %>% 
-  DataExplorer::plot_correlation()
-
-car::vif(lm(as.numeric(Class) ~ ., data = ace_multinom_prop_data))
-
-```
-
-##### Class 1 ref
-
-```{r, ace-multinom-prop-ref1}
-# Class 1 as ref class
-ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "1")
-ace_prop_m1 <- 
-  ace_multinom_prop_data %>% 
-  multinom(Class ~ ., family = "binomial", data = .)
-
-summary(ace_prop_m1)
-print("relative risk"); exp(coef(ace_prop_m1))
-
-ace_prop_m1_z <- summary(ace_prop_m1)$coefficients/summary(ace_prop_m1)$standard.errors
-#ace_m1_z
-
-# Two-tailed z-test
-print("Wald test p-value")
-ace_prop_m1_p <- (1 - pnorm(abs(ace_prop_m1_z), 0, 1)) * 2
-ace_prop_m1_p
-
-ace_multinom_prop_data %>% 
-  group_by(Class) %>% 
-  summarise(dispensing = mean(if_else(dispensing == "Yes", 1, 0)),
-            wimd = median(wimd2019),
-            hyp = median(hyp))
-```
-
-```{r}
-coef(ace_prop_m1) %>% 
+coef(oac_diff_m1) %>% 
   as_tibble(rownames = "Class") %>% 
@@
                names_to = "variable") %>% 
-  left_join(summary(ace_prop_m1)$standard.errors %>% 
+  left_join(summary(oac_diff_m1)$standard.errors %>% 
   as_tibble(rownames = "Class") %>% 
@@
 
-ace_multinom_prop_data %>% 
+oac_multinom_data %>% 
   # mutate(across(where(is.numeric), scale)) %>% 
@@
 
-# sjPlot::plot_model(ace_prop_m1, type = "pred", terms = c("pm_65 [all]", "dispensing"))
-sjPlot::plot_model(ace_prop_m1, type = "eff")
+# sjPlot::plot_model(oac_diff_m1, type = "pred", terms = c("pm_65 [all]", "dispensing"))
+sjPlot::plot_model(oac_diff_m1, type = "eff")
 ```
-
-##### Class 2 ref
-
-```{r, ace-multinom-prop-ref2}
-# Class 2 as ref class
-ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "2")
-ace_prop_m2 <- 
-  ace_multinom_prop_data %>% 
-  multinom(Class ~ ., family = "binomial", data = .)
-
-summary(ace_prop_m2)
-print("relative risk"); exp(coef(ace_prop_m2))
-
-ace_prop_m2_z <- summary(ace_prop_m2)$coefficients/summary(ace_prop_m2)$standard.errors
-
-# Two-tailed z-test
-print("Wald test p-value")
-ace_prop_m2_p <- (1 - pnorm(abs(ace_prop_m2_z), 0, 1)) * 2
-ace_prop_m2_p
-```
-
-##### Class 3 ref
-
-```{r, ace-multinom-prop-ref3}
-# Class 3 as ref class
-ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "3")
-ace_prop_m3 <- 
-  ace_multinom_prop_data %>% 
-  multinom(Class ~ ., family = "binomial", data = .)
-
-summary(ace_prop_m3)
-print("relative risk"); exp(coef(ace_prop_m3))
-
-ace_prop_m3_z <- summary(ace_prop_m3)$coefficients/summary(ace_prop_m3)$standard.errors
-
-# Two-tailed z-test
-print("Wald test p-value")
-ace_prop_m3_p <- (1 - pnorm(abs(ace_prop_m3_z), 0, 1)) * 2
-ace_prop_m3_p
-```
-
-##### Class 4 ref
-
-```{r, ace-multinom-prop-ref4}
-# Class 2 as ref class
-ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "4")
-ace_prop_m4 <- 
-  ace_multinom_prop_data %>% 
-  multinom(Class ~ ., family = "binomial", data = .)
-
-summary(ace_prop_m4)
-print("relative risk"); exp(coef(ace_prop_m4))
-
-ace_prop_m4_z <- summary(ace_prop_m4)$coefficients/summary(ace_prop_m4)$standard.errors
-
-# Two-tailed z-test
-print("Wald test p-value")
-ace_prop_m4_p <- (1 - pnorm(abs(ace_prop_m4_z), 0, 1)) * 2
-ace_prop_m4_p
-```
-
-##### Class 5 ref
-
-```{r, ace-multinom-prop-ref5}
-# Class 2 as ref class
-ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "5")
-ace_prop_m5 <- 
-  ace_multinom_prop_data %>% 
-  multinom(Class ~ ., family = "binomial", data = .)
-
-summary(ace_prop_m5)
-print("relative risk"); exp(coef(ace_prop_m5))
-
-ace_prop_m5_z <- summary(ace_prop_m5)$coefficients/summary(ace_prop_m5)$standard.errors
-
-# Two-tailed z-test
-print("Wald test p-value")
-ace_prop_m5_p <- (1 - pnorm(abs(ace_prop_m5_z), 0, 1)) * 2
-ace_prop_m5_p
-```

### 2021-03-05 r_notebooks/differences_lpa.Rmd
Removed LPA section from paper

@@
 library(tune)
+library(nnet)
 
@@
          dispensing = as_factor(dispensing),
-         hboard = as_factor(hboard)) %>% 
+         hboard = as_factor(str_remove_all(hboard, "W110000"))) %>% 
   ungroup() %>% 
@@
 
+proportions <- 
+  map_dfr(.x = differences_files,
+          .f = ~read_rds(paste0("../data/differences/", .x)),
+          .id = "drug") %>% 
+  mutate(drug = as_factor(drug)) %>% 
+  select(drug, regional_unit, datename, prop)
+
 drugs <- unique(as.character(differences$drug))
@@
 ```
+
+## Identifying different prescribing behaviours - LPA
+
+* What is LPA
+  * Differences from clustering methods (e.g., k-means and hierarchical)
+
+When conducting LPA, several models are specified and then evaluated.
+Model selection, including class enumeration, should not be based solely on statistical criteria, but also the statistical adequacy and substantive meaning of the solutions [@Marsh2009; @Morin2016].
+Indeed, relying solely on statistical criteria in large samples may lead to the inability to identify an "optimal solution" as model fit increases as the number of classes increase [@Morin2009].
+
+In this study we inspected the Bayesian Information Criterion [BIC; @Schwartz1978] and the bootstrapped likelihood ratio test [BLRT; @McLachlan2000] during the class enumeration process as the results of Monte-Carlo simulation study [@Nylund2007] showed them outperform other information criteria and likelihood-based tests.
+
+* Entropy
+* Posterior probabilities
 
@@
   pivot_wider(names_from = datename, values_from = discrepancy) %>% 
+  psych::describeBy(group = "drug", fast = TRUE)
+
+proportions %>% 
+  pivot_wider(names_from = datename, values_from = prop) %>% 
   psych::describeBy(group = "drug", fast = TRUE)
@@
   pivot_wider(names_from = datename, values_from = discrepancy)
+
+proportions_wide <- 
+  proportions %>% 
+  pivot_wider(names_from = datename, values_from = prop)
+```
+
+## Disease profiles
+
+```{r}
+df <- select(filter(gp, year == "2020"), chd:flu)
+psych::fa.parallel(df)
+five_fac <- psych::fa(df, nfactors = 3, rotate = "varimax")
+print(five_fac$loadings, cutoff = .2)
+
+dis_pca <- psych::principal(df, nfactors = 3, scores = TRUE)
+plot(dis_pca$values)
+dis_pca$rotation
+dis_pca_scores <- bind_cols(practice_id = filter(gp, year == "2020")$practice_id, dis_pca$scores)
+
+# 2d plot
+x <- dis_pca$loadings[,1]
+y <- dis_pca$loadings[,2]
+z <- dis_pca$loadings[,3]
+
+pca_plot_df <- bind_cols(dis = names(x), x = x, y = y, z = z)
+
+ggplot(aes(x = x, y = y), data = pca_plot_df) +
+  geom_text(aes(label = dis))
+
+ggplot(aes(x = x, y = z), data = pca_plot_df) +
+  geom_text(aes(label = dis))
+
+# 3d plot
+plotly::plot_ly(x=x, y=y, z=z, data = pca_plot_df,
+                type="scatter3d", mode="markers", color="dis")
 ```
@@
 
-```{r, ace-lpa}
+#### difference
+##### LPA estimation
+
+```{r, ace-lpa-diff}
+tictoc::tic()
 ace_lpa <- 
   differences_wide %>% 
+  filter(drug == "ace" & `2020 May` > -100) %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = 1:6,
+                    models = c(1:3))
+tictoc::toc()
+```
+
+##### LPA model selection
+
+```{r, ace-fits-diff}
+ace_lpa
+
+ace_lpa_fits <- compare_solutions(ace_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p", "Entropy"))
+ace_lpa_fits
+
+ace_lpa_fits$fits %>% 
+  mutate(Model = as.factor(Model),
+         Classes = as.factor(Classes)) %>% 
+  pivot_longer(names_to = "IC", cols = c(AIC, BIC, SABIC, Entropy, prob_min, n_min)) %>% 
+  select(-c(LogLik, AWE, CAIC, CLC, KIC, ICL)) %>% 
+  ggplot(aes(x = Classes, colour = Model, group = Model)) +
+  geom_line(aes(y = value)) +
+  facet_wrap(~IC, scales = "free")
+
+```
+
+* AIC, BIC, SABIC all suggest model 2 is best fit with 6, 4, 6 classes
+* BLRT < 6 classes for model 2
+  * AIC and SABIC suggest 5 classes are best when BLRT threshold applied
+* Entropy decreases when increasing from 4 to 5 classes
+* Selected model 2 with 4 classes.
+
+```{r}
+ace_lpa %>%
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+differences_wide %>% 
+  filter(drug == "ace" & `2020 May` > -100) %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = c(3:8),
+                    models = 2) %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+```
+
+```{r, ace-profile-vis-diff}
+ace_lpa$model_2_class_4 %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+df <- 
+  ace_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
+               names_to = "datename") %>% 
+  mutate(Class = as.factor(Class),
+         datename = as_factor(datename))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference, colour = Class)) +
+  geom_boxplot() +
+  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference)) +
+  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .1) +
+  stat_summary(fun = "mean") +
+  facet_wrap(~Class) +
+  theme(legend.position = "none")
+
+ace_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  summary()
+
+ace_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  TukeyHSD()
+```
+
+* Class 1 - 
+* Class 2 - 
+* Class 3 - 
+* Class 4 -
+
+##### Weka data
+
+```{r, ace-weka-diff}
+ace_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number:year, where(is.character), practice_id), Class) %>% 
+  mutate(across(where(is.numeric), scale)) %>% 
+  write_csv("../data/weka/ace.csv")
+```
+
+##### Multinomial logistic regression
+
+```{r, ace-multinom-diff-data}
+normalize <- function(x) {
+return ((x - min(x)) / (max(x) - min(x)))
+}
+
+ace_multinom_data <- 
+  ace_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>% 
+  mutate(gp_load = npat/ngp) %>% 
+  select(Class, pm_65, p_fem, hyp, ast, wimd2019, dispensing, ngp, gp_load, hboard) %>% # Removed chd, p_male, pf_65, pm_65, npat to reduce multicollinearity issues
+  mutate(Class = as.factor(Class),
+         hboard = as.factor(hboard),
+         across(where(is.numeric), ~normalize(.)))
+
+ace_multinom_data %>% 
+  DataExplorer::plot_correlation()
+```
+
+###### Class 1 ref
+
+```{r, ace-multinom-diff-ref1}
+# Class 1 as ref class
+ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "1")
+ace_m1 <- 
+  ace_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(ace_m1)
+print("relative risk"); exp(coef(ace_m1))
+
+ace_m1_z <- summary(ace_m1)$coefficients/summary(ace_m1)$standard.errors
+#ace_m1_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+ace_m1_p <- (1 - pnorm(abs(ace_m1_z), 0, 1)) * 2
+ace_m1_p
+```
+
+###### Class 2 ref
+
+```{r, ace-multinom-diff-ref2}
+# Class 2 as ref class
+ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "2")
+ace_m2 <- 
+  ace_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(ace_m2)
+print("relative risk"); exp(coef(ace_m2))
+
+ace_m2_z <- summary(ace_m2)$coefficients/summary(ace_m2)$standard.errors
+# ace_m2_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+ace_m2_p <- (1 - pnorm(abs(ace_m2_z), 0, 1)) * 2
+ace_m2_p
+```
+
+###### Class 3 ref
+
+```{r, ace-multinom-diff-ref3}
+# Class 3 as ref class
+ace_multinom_data$Class <- relevel(ace_multinom_data$Class, ref = "3")
+ace_m3 <- 
+  ace_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(ace_m3)
+print("relative risk"); exp(coef(ace_m3))
+
+ace_m3_z <- summary(ace_m3)$coefficients/summary(ace_m3)$standard.errors
+# ace_m3_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+ace_m3_p <- (1 - pnorm(abs(ace_m3_z), 0, 1)) * 2
+ace_m3_p
+```
+
+```{r}
+ace_multinom_data %>% 
+  group_by(Class) %>% 
+  summarise(dispensing = sum(if_else(as.character(dispensing) == "Yes", 1, 0))/n())
+```
+
+#### proportion
+##### LPA estimation
+
+```{r}
+proportions %>% 
+  filter(drug == "ace") %>% 
+  ggplot(aes(x = prop)) + 
+  geom_histogram() +
+  facet_wrap(~as.factor(datename))
+```
+
+```{r, ace-lpa-prop}
+tictoc::tic()
+ace_prop_lpa <- 
+  proportions_wide %>% 
   filter(drug == "ace") %>%
@@
                     models = c(1:3))
-```
-
-```{r, ace-fits}
-ace_lpa
-compare_solutions(ace_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p"))
-```
-
-```{r}
-ace_lpa %>%
+tictoc::toc()
+```
+
+##### LPA model selection
+
+```{r, ace-fits-prop}
+ace_prop_lpa
+
+ace_prop_lpa_fits <- compare_solutions(ace_prop_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p", "Entropy"))
+ace_prop_lpa_fits
+
+ace_prop_lpa_fits$fits %>% 
+  mutate(Model = as.factor(Model),
+         Classes = as.factor(Classes)) %>% 
+  pivot_longer(names_to = "IC", cols = c(AIC, BIC, SABIC, Entropy, prob_min, n_min)) %>% 
+  select(-c(LogLik, AWE, CAIC, CLC, KIC, ICL)) %>% 
+  ggplot(aes(x = Classes, colour = Model, group = Model)) +
+  geom_line(aes(y = value)) +
+  facet_wrap(~IC, scales = "free")
+
+```
+
+* Selected model 2 with 6 classes.
+
+```{r, ace-prop-profile-plots}
+ace_prop_lpa %>%
   plot_profiles(rawdata = FALSE, sd = FALSE)
@@
 differences_wide %>% 
-  filter(drug == "ace") %>% 
+  filter(drug == "ace" & `2020 Jul` > -50) %>% 
   estimate_profiles(df = ., 
@@
                                     "2020 Jun", "2020 Jul", "2020 Aug"),
-                    n_profiles = c(4,5,6,8),
+                    n_profiles = c(3:8),
                     models = 2) %>% 
@@
 
-*
-
-```{r}
-ace_lpa$model_2_class_5 %>% 
-  plot_profiles(rawdata = FALSE, sd = FALSE)
-
-ace_lpa$model_2_class_5 %>% 
+```{r, ace-profile-vis-prop}
+ace_prop_lpa$model_2_class_6 %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+df <- 
+  ace_prop_lpa$model_2_class_6 %>% 
   get_data() %>% 
@@
                names_to = "datename") %>% 
-  ggplot(aes(x = datename, y = difference, group = rowname, colour = rowname)) +
-  geom_line(alpha = .1) +
+  mutate(Class = as.factor(Class),
+         datename = as_factor(datename))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference, colour = Class)) +
+  geom_boxplot() +
+  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference)) +
+  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .2) +
+  stat_summary(fun = "mean", size = .1) +
   facet_wrap(~Class) +
-  theme(legend.position = "none")
-
-ace_lpa$model_2_class_5 %>% 
+  theme(legend.position = "none") +
+  coord_cartesian(ylim = c(.5, 1.5))
+
+ace_prop_lpa$model_2_class_6 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Jul` ~ Class, data = .) %>% 
+  summary()
+
+ace_prop_lpa$model_2_class_6 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Jul` ~ Class, data = .) %>% 
+  TukeyHSD()
+
+ace_prop_lpa$model_2_class_6 %>% 
+  get_data() %>% 
+  group_by(Class) %>% 
+  count()
+```
+
+```{r}
+ace_prop_lpa$model_2_class_6 %>% 
+  get_data() %>% 
+  group_by(Class) %>% 
+  summarise(across(`2020 Mar`:`2020 Aug`, median)) %>% 
+  pivot_longer(cols = `2020 Mar`:`2020 Aug`, names_to = "datename") %>% 
+  mutate(datename = yearmonth(datename),
+         Class = as.factor(Class)) %>% 
+  ggplot(aes(x = datename, y = value, colour = Class)) +
+  geom_line()
+```
+
+```{r}
+df <- 
+  ace_prop_lpa$model_2_class_6 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"), 
+            drug)) %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  pivot_longer(cols = `2020 Mar`:`2020 Aug`, names_to = "datename")
+
+df %>% 
+  split(.$datename) %>% 
+  map(~aov(value ~ Class, data = df)) %>% 
+  map(summary)
+
+df %>% 
+  split(.$datename) %>% 
+  map(~aov(value ~ Class, data = df)) %>% 
+  map(TukeyHSD)
+```
+
+* Class 1
+  * n = 58
+  * High in Mar, slight depression for Apr & May, as forecast in Jun & Jul, low levels in Aug. Moderate variability throughout.
+  * Stockpiling followed by reduced prescribing for two months before returning to "normal" for two months
+* Class 2
+  * n = 26
+  * Very high in Mar, decreased prescribing in Apr, then extremely variable prescribing for the remaining months.
+  * Very high levels of stockpiling followed by chaotic prescribing.
+* Class 3
+  * n = 125
+  * Elevated levels of prescribing in Mar, as forecast in Apr, slight reduction in May, as forecast in Jun & Jul, then reduced prescribing in Aug. Very low levels of variability.
+  * Business as usual with limited stockpiling
+* Class 4
+  * n = 85
+  * High levels of prescribing in Mar & Apr, as forecast May, slight elevation in Jun & Jul, slight depression in Aug but still higher than others. Low levels of variability.
+* Class 5
+  * n = 72
+  * High in Mar, as forecast in Apr, low levels in May, as forecast in Jun & Jul, low levels in Aug. Low levels of variability.
+* Class 6
+  * n = 36
+  * High in Mar, extremely variable in Apr with prescribing as forecast, variable levels just below forecast, reduced variability and low levels of prescribing in Jun, as forecast in Jul, and low levels in Aug.
+
+##### Weka data
+
+```{r, ace-weka-prop}
+ace_prop_lpa$model_2_class_6 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number:year, is.character, practice_id), Class) %>% 
+  mutate(across(is.numeric, scale)) %>% 
+  write_csv("../data/weka/ace_prop.csv")
+```
+
+##### Multinomial logistic regression
+
+```{r, ace-multinom-prop-data}
+normalize <- function(x) {
+return ((x - min(x)) / (max(x) - min(x)))
+}
+
+ace_multinom_prop_data <-
+  ace_prop_lpa$model_2_class_6 %>%
+  get_data() %>%
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>%
+  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>%
+  mutate(gp_load = npat/ngp) %>%
+  select(Class, pm_65, p_fem, wimd2019, dispensing, ngp, gp_load, hboard) %>%
+  mutate(Class = as.factor(Class),
+        hboard = as.factor(hboard),
+        # across(where(is.numeric), ~normalize(.))
+        )
+
+# ace_multinom_prop_data <-
+#   ace_prop_lpa$model_2_class_6 %>%
+#   get_data() %>%
+#   inner_join(dis_pca_scores, by = c("regional_unit" = "practice_id")) %>%
+#   inner_join(select(filter(gp, year == 2020), 
+#                     c(practiceid, hboard, wimd2019, dispensing, ngp, npat, p_fem, pm_65)), 
+#              by = c("regional_unit" = "practiceid")) %>%
+#   select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"), drug, regional_unit)) %>%
+#   mutate(Class = as.factor(Class),
+#          gp_load = npat/ngp,
+#          ngp = NULL,
+#          across(where(is.numeric), ~normalize(.)))
+
+ace_multinom_prop_data %>% 
+  DataExplorer::plot_correlation()
+
+car::vif(lm(as.numeric(Class) ~ ., data = ace_multinom_prop_data))
+
+```
+
+###### Class 1 ref
+
+```{r, ace-multinom-prop-ref1}
+# Class 1 as ref class
+ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "1")
+ace_prop_m1 <- 
+  ace_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(ace_prop_m1)
+print("relative risk"); exp(coef(ace_prop_m1))
+
+ace_prop_m1_z <- summary(ace_prop_m1)$coefficients/summary(ace_prop_m1)$standard.errors
+#ace_m1_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+ace_prop_m1_p <- (1 - pnorm(abs(ace_prop_m1_z), 0, 1)) * 2
+ace_prop_m1_p
+```
+
+```{r}
+coef(ace_prop_m1) %>% 
+  as_tibble(rownames = "Class") %>% 
+  pivot_longer(cols = `(Intercept)`:hboard29, values_to = "coefficient",
+               names_to = "variable") %>% 
+  left_join(summary(ace_prop_m1)$standard.errors %>% 
+  as_tibble(rownames = "Class") %>% 
+  pivot_longer(cols = `(Intercept)`:hboard29, values_to = "se",
+               names_to = "variable")) %>% 
+  ggplot(aes(x = coefficient, y = variable, group = as.factor(Class), colour = as.factor(Class))) +
+  geom_point(position = position_dodge(width = .5)) +
+  geom_errorbarh(aes(xmin = coefficient - 2 * se, xmax = coefficient + 2 * se),
+                 position = position_dodge(width = .5))
+
+ace_multinom_prop_data %>% 
+  mutate(across(is.numeric, scale)) %>% 
+  pivot_longer(cols = where(is.numeric), names_to = "variable") %>% 
+  ggplot(aes(x = variable, y = value, colour = Class)) +
+  geom_boxplot()
+
+sjPlot::plot_model(ace_prop_m1, type = "pred", terms = c("pm_65 [all]", "dispensing"))
+sjPlot::plot_model(ace_prop_m1, type = "eff")
+```
+
+###### Class 2 ref
+
+```{r, ace-multinom-prop-ref2}
+# Class 2 as ref class
+ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "2")
+ace_prop_m2 <- 
+  ace_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(ace_prop_m2)
+print("relative risk"); exp(coef(ace_prop_m2))
+
+ace_prop_m2_z <- summary(ace_prop_m2)$coefficients/summary(ace_prop_m2)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+ace_prop_m2_p <- (1 - pnorm(abs(ace_prop_m2_z), 0, 1)) * 2
+ace_prop_m2_p
+```
+
+###### Class 3 ref
+
+```{r, ace-multinom-prop-ref3}
+# Class 3 as ref class
+ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "3")
+ace_prop_m3 <- 
+  ace_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(ace_prop_m3)
+print("relative risk"); exp(coef(ace_prop_m3))
+
+ace_prop_m3_z <- summary(ace_prop_m3)$coefficients/summary(ace_prop_m3)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+ace_prop_m3_p <- (1 - pnorm(abs(ace_prop_m3_z), 0, 1)) * 2
+ace_prop_m3_p
+```
+
+###### Class 4 ref
+
+```{r, ace-multinom-prop-ref4}
+# Class 2 as ref class
+ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "4")
+ace_prop_m4 <- 
+  ace_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(ace_prop_m4)
+print("relative risk"); exp(coef(ace_prop_m4))
+
+ace_prop_m4_z <- summary(ace_prop_m4)$coefficients/summary(ace_prop_m4)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+ace_prop_m4_p <- (1 - pnorm(abs(ace_prop_m4_z), 0, 1)) * 2
+ace_prop_m4_p
+```
+
+###### Class 5 ref
+
+```{r, ace-multinom-prop-ref5}
+# Class 2 as ref class
+ace_multinom_prop_data$Class <- relevel(ace_multinom_prop_data$Class, ref = "5")
+ace_prop_m5 <- 
+  ace_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(ace_prop_m5)
+print("relative risk"); exp(coef(ace_prop_m5))
+
+ace_prop_m5_z <- summary(ace_prop_m5)$coefficients/summary(ace_prop_m5)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+ace_prop_m5_p <- (1 - pnorm(abs(ace_prop_m5_z), 0, 1)) * 2
+ace_prop_m5_p
+```
+
+### adreno
+#### difference
+##### LPA estimation
+
+```{r, adreno-lpa-diff}
+tictoc::tic()
+adreno_lpa <- 
+  differences_wide %>% 
+  filter(drug == "adreno") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = 1:6,
+                    models = c(1:3))
+tictoc::toc()
+```
+
+##### LPA model selection
+
+```{r, adreno-fits-diff}
+adreno_lpa
+
+adreno_lpa_fits <- compare_solutions(adreno_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p", "Entropy"))
+adreno_lpa_fits
+
+adreno_lpa_fits$fits %>% 
+  mutate(Model = as.factor(Model),
+         Classes = as.factor(Classes)) %>% 
+  pivot_longer(names_to = "IC", cols = c(AIC, BIC, SABIC, Entropy, prob_min, n_min)) %>% 
+  select(-c(LogLik, AWE, CAIC, CLC, KIC, ICL)) %>% 
+  ggplot(aes(x = Classes, colour = Model, group = Model)) +
+  geom_line(aes(y = value)) +
+  facet_wrap(~IC, scales = "free")
+
+```
+
+* AIC, BIC, SABIC suggest 6, 5, 6 classes with model 2 being the best fit
+* BLRT suggests < 6 classes
+  * AIC and SABIC suggest 5 classes when BLRT threshold applied
+* Entropy suggests 
+* Selected model 2 with 5 classes.
+
+```{r}
+adreno_lpa %>%
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+differences_wide %>% 
+  filter(drug == "adreno") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = c(3:8),
+                    models = 2) %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+```
+
+```{r, adreno-profile-vis-diff}
+adreno_lpa$model_2_class_5 %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+df <- 
+  adreno_lpa$model_2_class_5 %>% 
   get_data() %>% 
@@
                names_to = "datename") %>% 
-  mutate(Class = as.factor(Class)) %>% 
+  mutate(Class = as.factor(Class),
+         datename = as_factor(datename))
+
+df %>% 
   ggplot(aes(x = datename, y = difference, colour = Class)) +
   geom_boxplot() +
-  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75)) +
-  theme(legend.position = "none")
-
-df <- 
-  ace_lpa$model_2_class_5 %>% 
-  get_data() %>% 
-  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
-  rownames_to_column() %>% 
-  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
-               names_to = "datename") %>% 
-  mutate(Class = as.factor(Class))
+  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75))
 
@@
 
-ace_lpa$model_2_class_5 %>% 
-  get_data() %>% 
-  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
-  rownames_to_column() %>% 
-  # pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
-  #              names_to = "datename") %>% 
+adreno_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
   mutate(Class = as.factor(Class)) %>% 
   aov(`2020 Mar` ~ Class, data = .) %>% 
-  # summary() %>% 
+  summary()
+
+adreno_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
   TukeyHSD()
@@
 
-### adreno
+* Class 1 - 
+* Class 2 - 
+* Class 3 - 
+* Class 4 -
+
+##### Weka data
+
+```{r, adreno-weka-diff}
+adreno_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number:year, where(is.character), practice_id), Class) %>% 
+  mutate(across(where(is.numeric), scale)) %>% 
+  write_csv("../data/weka/adreno.csv")
+```
+
+##### Multinomial logistic regression
+
+```{r, adreno-multinom-diff-data}
+normalize <- function(x) {
+return ((x - min(x)) / (max(x) - min(x)))
+}
+
+adreno_multinom_data <- 
+  adreno_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>% 
+  mutate(gp_load = npat/ngp) %>% 
+  select(Class, pm_65, p_fem, hyp, ast, wimd2019, dispensing, ngp, gp_load, hboard) %>% 
+  mutate(Class = as.factor(Class),
+         hboard = as.factor(hboard),
+         across(where(is.numeric), ~normalize(.)))
+
+adreno_multinom_data %>% 
+  DataExplorer::plot_correlation()
+
+```
+
+###### Class 1 ref
+
+```{r, adreno-multinom-diff-ref1}
+# Class 1 as ref class
+adreno_multinom_data$Class <- relevel(adreno_multinom_data$Class, ref = "1")
+adreno_m1 <- 
+  adreno_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_m1)
+print("relative risk"); exp(coef(adreno_m1))
+
+adreno_m1_z <- summary(adreno_m1)$coefficients/summary(adreno_m1)$standard.errors
+#adreno_m1_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_m1_p <- (1 - pnorm(abs(adreno_m1_z), 0, 1)) * 2
+adreno_m1_p
+```
+
+###### Class 2 ref
+
+```{r, adreno-multinom-diff-ref2}
+# Class 2 as ref class
+adreno_multinom_data$Class <- relevel(adreno_multinom_data$Class, ref = "2")
+adreno_m2 <- 
+  adreno_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_m2)
+print("relative risk"); exp(coef(adreno_m2))
+
+adreno_m2_z <- summary(adreno_m2)$coefficients/summary(adreno_m2)$standard.errors
+# adreno_m2_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_m2_p <- (1 - pnorm(abs(adreno_m2_z), 0, 1)) * 2
+adreno_m2_p
+```
+
+###### Class 3 ref
+
+```{r, adreno-multinom-diff-ref3}
+# Class 3 as ref class
+adreno_multinom_data$Class <- relevel(adreno_multinom_data$Class, ref = "3")
+adreno_m3 <- 
+  adreno_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_m3)
+print("relative risk"); exp(coef(adreno_m3))
+
+adreno_m3_z <- summary(adreno_m3)$coefficients/summary(adreno_m3)$standard.errors
+# adreno_m3_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_m3_p <- (1 - pnorm(abs(adreno_m3_z), 0, 1)) * 2
+adreno_m3_p
+```
+
+###### Class 4 ref
+
+```{r, adreno-multinom-diff-ref4}
+# Class 4 as ref class
+adreno_multinom_data$Class <- relevel(adreno_multinom_data$Class, ref = "4")
+adreno_m4 <- 
+  adreno_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_m4)
+print("relative risk"); exp(coef(adreno_m4))
+
+adreno_m4_z <- summary(adreno_m4)$coefficients/summary(adreno_m4)$standard.errors
+# adreno_m4_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_m4_p <- (1 - pnorm(abs(adreno_m4_z), 0, 1)) * 2
+adreno_m4_p
+```
+
+```{r}
+adreno_multinom_data %>% 
+  group_by(Class) %>% 
+  summarise(dispensing = sum(if_else(as.character(dispensing) == "Yes", 1, 0))/n())
+```
+
+####
 
@@
 ```
-### azithro
-
-### contra
-
-### cortico
-
-### hcq
-
-### nsaid
-
-### oac
-
-```{r, oac-lpa}
-oac_lpa <- 
-  differences_wide %>% 
-  filter(drug == "oac") %>% 
+
+#### proportion
+##### LPA estimation
+
+```{r}
+proportions %>% 
+  filter(drug == "adreno") %>% 
+  ggplot(aes(x = prop)) + 
+  geom_histogram() +
+  facet_wrap(~as.factor(datename))
+```
+
+```{r, adreno-lpa-prop}
+tictoc::tic()
+adreno_prop_lpa <- 
+  proportions_wide %>% 
+  filter(drug == "adreno") %>%
   estimate_profiles(df = ., 
@@
                     models = c(1:3))
+tictoc::toc()
+```
+
+##### LPA model selection
+
+```{r, adreno-fits-prop}
+adreno_prop_lpa
+
+adreno_prop_lpa_fits <- compare_solutions(adreno_prop_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p", "Entropy"))
+adreno_prop_lpa_fits
+
+adreno_prop_lpa_fits$fits %>% 
+  mutate(Model = as.factor(Model),
+         Classes = as.factor(Classes)) %>% 
+  pivot_longer(names_to = "IC", cols = c(AIC, BIC, SABIC, Entropy, prob_min, n_min)) %>% 
+  select(-c(LogLik, AWE, CAIC, CLC, KIC, ICL)) %>% 
+  ggplot(aes(x = Classes, colour = Model, group = Model)) +
+  geom_line(aes(y = value)) +
+  facet_wrap(~IC, scales = "free")
+
+```
+
+* Selected model 2 with 4 classes.
+
+```{r, adreno-prop-plots}
+adreno_prop_lpa %>%
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+differences_wide %>% 
+  filter(drug == "adreno") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = c(3:8),
+                    models = 2) %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+```
+
+```{r, adreno-profile-vis-prop}
+adreno_prop_lpa$model_2_class_4 %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+df <- 
+  adreno_prop_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
+               names_to = "datename") %>% 
+  mutate(Class = as.factor(Class),
+         datename = as_factor(datename))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference, colour = Class)) +
+  geom_boxplot() +
+  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference)) +
+  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .1) +
+  stat_summary(fun = "mean") +
+  facet_wrap(~Class) +
+  theme(legend.position = "none")
+
+adreno_prop_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  summary()
+
+adreno_prop_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  TukeyHSD()
+```
+
+* Class 1 - 
+* Class 2 - 
+* Class 3 - 
+* Class 4 -
+
+##### Weka data
+
+```{r, adreno-weka-prop}
+adreno_prop_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number:year, is.character, practice_id), Class) %>% 
+  mutate(across(is.numeric, scale)) %>% 
+  write_csv("../data/weka/adreno_prop.csv")
+```
+
+##### Multinomial logistic regression
+
+```{r, adreno-multinom-prop-data}
+normalize <- function(x) {
+return ((x - min(x)) / (max(x) - min(x)))
+}
+
+adreno_multinom_prop_data <-
+  adreno_prop_lpa$model_2_class_6 %>%
+  get_data() %>%
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>%
+  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>%
+  mutate(gp_load = npat/ngp) %>%
+  select(Class, pm_65, p_fem, hyp, hf, chd, ast, wimd2019, dispensing, ngp, gp_load, hboard) %>%
+  mutate(Class = as.factor(Class),
+         hboard = as.factor(hboard),
+         across(where(is.numeric), ~normalize(.)))
+
+adreno_multinom_prop_data %>% 
+  DataExplorer::plot_correlation()
+
+car::vif(lm(as.numeric(Class) ~ ., data = adreno_multinom_prop_data))
+
+```
+
+###### Class 1 ref
+
+```{r, adreno-multinom-prop-ref1}
+# Class 1 as ref class
+adreno_multinom_prop_data$Class <- relevel(adreno_multinom_prop_data$Class, ref = "1")
+adreno_prop_m1 <- 
+  adreno_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_prop_m1)
+print("relative risk"); exp(coef(adreno_prop_m1))
+
+adreno_prop_m1_z <- summary(adreno_prop_m1)$coefficients/summary(adreno_prop_m1)$standard.errors
+#adreno_m1_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_prop_m1_p <- (1 - pnorm(abs(adreno_prop_m1_z), 0, 1)) * 2
+adreno_prop_m1_p
+
+```
+
+###### Class 2 ref
+
+```{r, adreno-multinom-prop-ref2}
+# Class 2 as ref class
+adreno_multinom_prop_data$Class <- relevel(adreno_multinom_prop_data$Class, ref = "2")
+adreno_prop_m2 <- 
+  adreno_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_prop_m2)
+print("relative risk"); exp(coef(adreno_prop_m2))
+
+adreno_prop_m2_z <- summary(adreno_prop_m2)$coefficients/summary(adreno_prop_m2)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_prop_m2_p <- (1 - pnorm(abs(adreno_prop_m2_z), 0, 1)) * 2
+adreno_prop_m2_p
+```
+
+###### Class 3 ref
+
+```{r, adreno-multinom-prop-ref3}
+# Class 3 as ref class
+adreno_multinom_prop_data$Class <- relevel(adreno_multinom_prop_data$Class, ref = "3")
+adreno_prop_m3 <- 
+  adreno_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_prop_m3)
+print("relative risk"); exp(coef(adreno_prop_m3))
+
+adreno_prop_m3_z <- summary(adreno_prop_m3)$coefficients/summary(adreno_prop_m3)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_prop_m3_p <- (1 - pnorm(abs(adreno_prop_m3_z), 0, 1)) * 2
+adreno_prop_m3_p
+```
+
+###### Class 4 ref
+
+```{r, adreno-multinom-prop-ref4}
+# Class 2 as ref class
+adreno_multinom_prop_data$Class <- relevel(adreno_multinom_prop_data$Class, ref = "4")
+adreno_prop_m4 <- 
+  adreno_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_prop_m4)
+print("relative risk"); exp(coef(adreno_prop_m4))
+
+adreno_prop_m4_z <- summary(adreno_prop_m4)$coefficients/summary(adreno_prop_m4)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_prop_m4_p <- (1 - pnorm(abs(adreno_prop_m4_z), 0, 1)) * 2
+adreno_prop_m4_p
+```
+
+###### Class 5 ref
+
+```{r, adreno-multinom-prop-ref5}
+# Class 2 as ref class
+adreno_multinom_prop_data$Class <- relevel(adreno_multinom_prop_data$Class, ref = "5")
+adreno_prop_m5 <- 
+  adreno_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(adreno_prop_m5)
+print("relative risk"); exp(coef(adreno_prop_m5))
+
+adreno_prop_m5_z <- summary(adreno_prop_m5)$coefficients/summary(adreno_prop_m5)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+adreno_prop_m5_p <- (1 - pnorm(abs(adreno_prop_m5_z), 0, 1)) * 2
+adreno_prop_m5_p
+```
+
+### azithro
+
+```{r, azithro-lpa}
+azithro_lpa <- 
+  differences_wide %>% 
+  filter(drug == "azithro") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = 1:8,
+                    models = c(1:3))
+```
+
+```{r, azithro-fits}
+azithro_lpa
+compare_solutions(azithro_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p"))
 ```
@@
 ```{r}
-compare_solutions(oac_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p"))
-```
+azithro_lpa %>%
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+differences_wide %>% 
+  filter(drug == "azithro") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = c(3:6),
+                    models = 2) %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+```
+
+*
+
+```{r, ac-profile-vis}
+azithro_lpa$model_2_class_4 %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+df <- 
+  azithro_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
+               names_to = "datename") %>% 
+  mutate(Class = as.factor(Class),
+         datename = as_factor(datename))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference, colour = Class)) +
+  geom_boxplot() +
+  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75)) +
+  theme(legend.position = "none")
+
+df %>% 
+  ggplot(aes(x = datename, y = difference)) +
+  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .1) +
+  stat_summary(fun = "mean") +
+  facet_wrap(~Class) +
+  theme(legend.position = "none")
+
+azithro_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  summary()
+
+azithro_lpa$model_2_class_4 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  TukeyHSD()
+```
+
+### contra
+#### difference
+##### LPA estimation
+
+```{r, contra-lpa-diff}
+tictoc::tic()
+contra_lpa <- 
+  differences_wide %>% 
+  filter(drug == "contra") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = 1:6,
+                    models = c(1:3))
+tictoc::toc()
+```
+
+##### LPA model selection
+
+```{r, contra-fits-diff}
+contra_lpa
+
+contra_lpa_fits <- compare_solutions(contra_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p", "Entropy"))
+contra_lpa_fits
+
+contra_lpa_fits$fits %>% 
+  mutate(Model = as.factor(Model),
+         Classes = as.factor(Classes)) %>% 
+  pivot_longer(names_to = "IC", cols = c(AIC, BIC, SABIC, Entropy, prob_min, n_min)) %>% 
+  select(-c(LogLik, AWE, CAIC, CLC, KIC, ICL)) %>% 
+  ggplot(aes(x = Classes, colour = Model, group = Model)) +
+  geom_line(aes(y = value)) +
+  facet_wrap(~IC, scales = "free")
+
+```
+
+* AIC, BIC, SABIC suggest 6, 5, 6 classes with model 2 being the best fit
+* BLRT suggests < 6 classes
+  * AIC and SABIC suggest 5 classes when BLRT threshold applied
+* Entropy suggests 
+* Selected model 2 with 3 classes.
 
 ```{r}
-oac_lpa %>% 
-  plot_profiles(rawdata = FALSE, sd = FALSE)
+contra_lpa %>%
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+differences_wide %>% 
+  filter(drug == "contra") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = c(3:8),
+                    models = 2) %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+```
+
+```{r, contra-profile-vis-diff}
+contra_lpa$model_2_class_3 %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+df <- 
+  contra_lpa$model_2_class_3 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
+               names_to = "datename") %>% 
+  mutate(Class = as.factor(Class),
+         datename = as_factor(datename))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference, colour = Class)) +
+  geom_boxplot() +
+  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference)) +
+  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .1) +
+  stat_summary(fun = "mean") +
+  facet_wrap(~Class) +
+  theme(legend.position = "none")
+
+contra_lpa$model_2_class_3 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  summary()
+
+contra_lpa$model_2_class_3 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  TukeyHSD()
+```
+
+* Class 1 - 
+* Class 2 - 
+* Class 3 - 
+* Class 4 -
+
+##### Weka data
+
+```{r, contra-weka-diff}
+contra_lpa$model_2_class_3 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number:year, where(is.character), practice_id), Class) %>% 
+  mutate(across(where(is.numeric), scale)) %>% 
+  write_csv("../data/weka/contra.csv")
+```
+
+##### Multinomial logistic regression
+
+```{r, contra-multinom-diff-data}
+normalize <- function(x) {
+return ((x - min(x)) / (max(x) - min(x)))
+}
+
+contra_multinom_data <- 
+  contra_lpa$model_2_class_3 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>% 
+  mutate(gp_load = npat/ngp) %>% 
+  select(Class, pm_65, p_fem, hyp, ast, wimd2019, dispensing, ngp, gp_load, hboard) %>% 
+  mutate(Class = as.factor(Class),
+         hboard = as.factor(hboard),
+         across(where(is.numeric), ~normalize(.)))
+
+contra_multinom_data %>% 
+  DataExplorer::plot_correlation()
+
+```
+
+###### Class 1 ref
+
+```{r, contra-multinom-diff-ref1}
+# Class 1 as ref class
+contra_multinom_data$Class <- relevel(contra_multinom_data$Class, ref = "1")
+contra_m1 <- 
+  contra_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_m1)
+print("relative risk"); exp(coef(contra_m1))
+
+contra_m1_z <- summary(contra_m1)$coefficients/summary(contra_m1)$standard.errors
+#contra_m1_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_m1_p <- (1 - pnorm(abs(contra_m1_z), 0, 1)) * 2
+contra_m1_p
+```
+
+###### Class 2 ref
+
+```{r, contra-multinom-diff-ref2}
+# Class 2 as ref class
+contra_multinom_data$Class <- relevel(contra_multinom_data$Class, ref = "2")
+contra_m2 <- 
+  contra_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_m2)
+print("relative risk"); exp(coef(contra_m2))
+
+contra_m2_z <- summary(contra_m2)$coefficients/summary(contra_m2)$standard.errors
+# contra_m2_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_m2_p <- (1 - pnorm(abs(contra_m2_z), 0, 1)) * 2
+contra_m2_p
+```
+
+###### Class 3 ref
+
+```{r, contra-multinom-diff-ref3}
+# Class 3 as ref class
+contra_multinom_data$Class <- relevel(contra_multinom_data$Class, ref = "3")
+contra_m3 <- 
+  contra_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_m3)
+print("relative risk"); exp(coef(contra_m3))
+
+contra_m3_z <- summary(contra_m3)$coefficients/summary(contra_m3)$standard.errors
+# contra_m3_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_m3_p <- (1 - pnorm(abs(contra_m3_z), 0, 1)) * 2
+contra_m3_p
+```
+
+###### Class 4 ref
+
+```{r, contra-multinom-diff-ref4}
+# Class 4 as ref class
+contra_multinom_data$Class <- relevel(contra_multinom_data$Class, ref = "4")
+contra_m4 <- 
+  contra_multinom_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_m4)
+print("relative risk"); exp(coef(contra_m4))
+
+contra_m4_z <- summary(contra_m4)$coefficients/summary(contra_m4)$standard.errors
+# contra_m4_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_m4_p <- (1 - pnorm(abs(contra_m4_z), 0, 1)) * 2
+contra_m4_p
 ```
@@
 ```{r}
-oac_lpa$model_3_class_2 %>% 
-  plot_profiles(rawdata = FALSE, sd = FALSE)
-
-oac_lpa$model_3_class_2 %>% 
+contra_multinom_data %>% 
+  group_by(Class) %>% 
+  summarise(dispensing = sum(if_else(as.character(dispensing) == "Yes", 1, 0))/n())
+```
+
+####
+
+```{r, contra-lpa}
+contra_lpa <- 
+  differences_wide %>% 
+  filter(drug == "contra") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = 1:8,
+                    models = c(1:3))
+```
+
+```{r}
+contra_lpa
+compare_solutions(contra_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p"))
+```
+
+```{r}
+contra_lpa %>%
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+differences_wide %>% 
+  filter(drug == "contra") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = c(4,5,6,8),
+                    models = 2) %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+```
+
+* Different fit statistics suggest different models best fit the data.
+Increasing the number of classes does not change the shapes of the profiles, it merely splits existing profiles into smaller units.
+* Retain the five class solution based on principle of parsimony and interpretability.
+
+```{r}
+contra_lpa$model_2_class_5 %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+contra_lpa$model_2_class_5 %>% 
   get_data() %>% 
@@
 
-df <- 
-  oac_lpa$model_3_class_2 %>% 
+contra_lpa$model_2_class_5 %>% 
   get_data() %>% 
@@
                names_to = "datename") %>% 
-  mutate(Class = as.factor(Class),
-               datename = yearmonth(datename))
-
-df %>% 
-  ggplot(aes(x = as.factor(datename), y = difference, color = Class)) +
+  mutate(Class = as.factor(Class)) %>% 
+  ggplot(aes(x = datename, y = difference, colour = Class)) +
   geom_boxplot() +
-  geom_point(shape = 3, alpha = .3, 
-             position=position_jitterdodge(dodge.width=0.75)) +
+  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75)) +
   theme(legend.position = "none")
+
+df <- 
+  contra_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
+               names_to = "datename") %>% 
+  mutate(Class = as.factor(Class))
 
@@
 
-```
-
-### paracet
-
-### vitd
+contra_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  # pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
+  #              names_to = "datename") %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  # summary() %>% 
+  TukeyHSD()
+```
+
+#### proportion
+##### LPA estimation
+
+```{r}
+proportions %>% 
+  filter(drug == "contra") %>% 
+  ggplot(aes(x = prop)) + 
+  geom_histogram() +
+  facet_wrap(~as.factor(datename))
+```
+
+```{r, contra-lpa-prop}
+tictoc::tic()
+contra_prop_lpa <- 
+  proportions_wide %>% 
+  filter(drug == "contra") %>%
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = 1:8,
+                    models = c(1:3))
+tictoc::toc()
+```
+
+##### LPA model selection
+
+```{r, contra-fits-prop}
+contra_prop_lpa
+
+contra_prop_lpa_fits <- compare_solutions(contra_prop_lpa, statistics = c("BIC", "AIC", "SABIC", "BLRT_p", "Entropy"))
+contra_prop_lpa_fits
+
+contra_prop_lpa_fits$fits %>% 
+  mutate(Model = as.factor(Model),
+         Classes = as.factor(Classes)) %>% 
+  pivot_longer(names_to = "IC", cols = c(AIC, BIC, SABIC, Entropy, prob_min, n_min)) %>% 
+  select(-c(LogLik, AWE, CAIC, CLC, KIC, ICL)) %>% 
+  ggplot(aes(x = Classes, colour = Model, group = Model)) +
+  geom_line(aes(y = value)) +
+  facet_wrap(~IC, scales = "free")
+
+```
+
+* Selected model 2 with 3 classes.
+
+```{r, contra-prop-plots}
+contra_prop_lpa %>%
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+differences_wide %>% 
+  filter(drug == "contra") %>% 
+  estimate_profiles(df = ., 
+                    select_vars = c("2020 Mar", "2020 Apr", "2020 May", 
+                                    "2020 Jun", "2020 Jul", "2020 Aug"),
+                    n_profiles = c(3:8),
+                    models = 2) %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+```
+
+```{r, contra-profile-vis-prop}
+contra_prop_lpa$model_2_class_5 %>% 
+  plot_profiles(rawdata = FALSE, sd = FALSE)
+
+df <- 
+  contra_prop_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  pivot_longer(cols = `2020 Mar`:`2020 Aug`, values_to = "difference", 
+               names_to = "datename") %>% 
+  mutate(Class = as.factor(Class),
+         datename = as_factor(datename))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference, colour = Class)) +
+  geom_boxplot() +
+  geom_point(alpha = .1, position=position_jitterdodge(dodge.width=0.75))
+
+df %>% 
+  ggplot(aes(x = datename, y = difference)) +
+  geom_line(aes(colour = as.factor(rowname), group = rowname), alpha = .2) +
+  stat_summary(fun = "mean") +
+  facet_wrap(~Class) +
+  theme(legend.position = "none")
+
+contra_prop_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  summary()
+
+contra_prop_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  select(-c(model_number, classes_number, starts_with("CPROB"))) %>% 
+  rownames_to_column() %>% 
+  mutate(Class = as.factor(Class)) %>% 
+  aov(`2020 Mar` ~ Class, data = .) %>% 
+  TukeyHSD()
+```
+
+* Class 1 - 
+* Class 2 - 
+* Class 3 - 
+* Class 4 -
+
+##### Weka data
+
+```{r, contra-weka-prop}
+contra_prop_lpa$model_2_class_5 %>% 
+  get_data() %>% 
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>% 
+  select(-c(model_number:year, is.character, practice_id), Class) %>% 
+  mutate(across(is.numeric, scale)) %>% 
+  write_csv("../data/weka/contra_prop.csv")
+```
+
+##### Multinomial logistic regression
+
+```{r, contra-multinom-prop-data}
+normalize <- function(x) {
+return ((x - min(x)) / (max(x) - min(x)))
+}
+
+contra_multinom_prop_data <-
+  contra_prop_lpa$model_2_class_5 %>%
+  get_data() %>%
+  inner_join(filter(gp, year == 2020), by = c("regional_unit" = "practiceid")) %>%
+  select(-c(model_number, classes_number, starts_with("2020 "), starts_with("CPROB"))) %>%
+  mutate(gp_load = npat/ngp) %>%
+  select(Class, pm_65, p_fem, hyp, hf, chd, ast, wimd2019, dispensing, ngp, gp_load, hboard) %>%
+  mutate(Class = as.factor(Class),
+         hboard = as.factor(hboard),
+         across(where(is.numeric), ~normalize(.)))
+
+contra_multinom_prop_data %>% 
+  DataExplorer::plot_correlation()
+
+car::vif(lm(as.numeric(Class) ~ ., data = contra_multinom_prop_data))
+
+```
+
+###### Class 1 ref
+
+```{r, contra-multinom-prop-ref1}
+# Class 1 as ref class
+contra_multinom_prop_data$Class <- relevel(contra_multinom_prop_data$Class, ref = "1")
+contra_prop_m1 <- 
+  contra_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_prop_m1)
+print("relative risk"); exp(coef(contra_prop_m1))
+
+contra_prop_m1_z <- summary(contra_prop_m1)$coefficients/summary(contra_prop_m1)$standard.errors
+#contra_m1_z
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_prop_m1_p <- (1 - pnorm(abs(contra_prop_m1_z), 0, 1)) * 2
+contra_prop_m1_p
+
+```
+
+###### Class 2 ref
+
+```{r, contra-multinom-prop-ref2}
+# Class 2 as ref class
+contra_multinom_prop_data$Class <- relevel(contra_multinom_prop_data$Class, ref = "2")
+contra_prop_m2 <- 
+  contra_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_prop_m2)
+print("relative risk"); exp(coef(contra_prop_m2))
+
+contra_prop_m2_z <- summary(contra_prop_m2)$coefficients/summary(contra_prop_m2)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_prop_m2_p <- (1 - pnorm(abs(contra_prop_m2_z), 0, 1)) * 2
+contra_prop_m2_p
+```
+
+###### Class 3 ref
+
+```{r, contra-multinom-prop-ref3}
+# Class 3 as ref class
+contra_multinom_prop_data$Class <- relevel(contra_multinom_prop_data$Class, ref = "3")
+contra_prop_m3 <- 
+  contra_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_prop_m3)
+print("relative risk"); exp(coef(contra_prop_m3))
+
+contra_prop_m3_z <- summary(contra_prop_m3)$coefficients/summary(contra_prop_m3)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_prop_m3_p <- (1 - pnorm(abs(contra_prop_m3_z), 0, 1)) * 2
+contra_prop_m3_p
+```
+
+###### Class 4 ref
+
+```{r, contra-multinom-prop-ref4}
+# Class 2 as ref class
+contra_multinom_prop_data$Class <- relevel(contra_multinom_prop_data$Class, ref = "4")
+contra_prop_m4 <- 
+  contra_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_prop_m4)
+print("relative risk"); exp(coef(contra_prop_m4))
+
+contra_prop_m4_z <- summary(contra_prop_m4)$coefficients/summary(contra_prop_m4)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_prop_m4_p <- (1 - pnorm(abs(contra_prop_m4_z), 0, 1)) * 2
+contra_prop_m4_p
+```
+
+###### Class 5 ref
+
+```{r, contra-multinom-prop-ref5}
+# Class 2 as ref class
+contra_multinom_prop_data$Class <- relevel(contra_multinom_prop_data$Class, ref = "5")
+contra_prop_m5 <- 
+  contra_multinom_prop_data %>% 
+  multinom(Class ~ ., family = "binomial", data = .)
+
+summary(contra_prop_m5)
+print("relative risk"); exp(coef(contra_prop_m5))
+
+contra_prop_m5_z <- summary(contra_prop_m5)$coefficients/summary(contra_prop_m5)$standard.errors
+
+# Two-tailed z-test
+print("Wald test p-value")
+contra_prop_m5_p <- (1 - pnorm(abs(contra_prop_m5_z), 0, 1)) * 2
+contra_prop_m5_p
+```
 

### 2021-03-05 writing/paper.Rmd
Removed LPA section from paper

@@
 * Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
-* Using Jan 2015 to Feb 2020 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
+* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
   * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
@@
 
-## Identifying different prescribing behaviours - LPA
-
-* What is LPA
-  * Differences from clustering methods (e.g., k-means and hierarchical)
-
-When conducting LPA, several models are specified and then evaluated.
-Model selection, including class enumeration, should not be based solely on statistical criteria, but also the statistical adequacy and substantive meaning of the solutions [@Marsh2009; @Morin2016].
-Indeed, relying solely on statistical criteria in large samples may lead to the inability to identify an "optimal solution" as model fit increases as the number of classes increase [@Morin2009].
-
-In this study we inspected the Bayesian Information Criterion [BIC; @Schwartz1978] and the bootstrapped likelihood ratio test [BLRT; @McLachlan2000] during the class enumeration process as the results of Monte-Carlo simulation study [@Nylund2007] showed them outperform other information criteria and likelihood-based tests.
-
-* Entropy
-* Posterior probabilities
-
 ## Reproducability and code
@@
 
-### All drugs
+### All prescribing
 

### 2021-03-06 r_notebooks/gp_dimensionality.Rmd
CFA work for QOF disease register

@@
 
-set.seed(376)
+set.seed(32)
 knitr::opts_chunk$set(echo = TRUE)
@@
 gp1 <- 
-  slice_sample(gp, prop = .5) 
+  gp %>% 
+  mutate(block = randomizr::block_ra(blocks = as.character(gp$cluster), prob = .4)) %>% # Try cluster_ra() and then all practices from a cluster will be in one dataset.
+Could also then stratify (block) by heatlh board
+  filter(block == 0)
+
 gp2 <- 
-  filter(gp, practice_id %in% gp1$practice_id)
+  filter(gp, !practice_id %in% gp1$practice_id) %>% 
+  mutate(across(chd:flu, scale))
 ```
@@
 ```{r, inspect-data}
-gp %>%
+gp1 %>%
   select(chd:flu) %>% 
@@
 
+gp1 %>%
+  select(chd:flu) %>% 
+  DataExplorer::plot_histogram()
+
 gp %>%
   select(chd:flu) %>% 
+  DataExplorer::plot_correlation()
+
+gp1 %>% 
+  group_by(cluster) %>%
+  summarise(across(chd:flu, sd))
+
+gp1 %>% 
+  group_by(county) %>%
+  summarise(across(chd:flu, sd))
+
+gp1 %>% 
+  group_by(hboard) %>%
+  summarise(across(chd:flu, sd))
+
+gp2 %>% 
+  select(chd:flu) %>% 
   DataExplorer::plot_histogram()
+
 ```
 
-## QOF disease register EFA
+## EFA
 
 ```{r}
-df <- select(gp1, chd:flu)
+df <- select(gp1, chd:flu, -epi)
 psych::fa.parallel(df)
@@
 five_fac <- psych::fa(df, nfactors = 5, rotate = "varimax")
-print(three_fac$loadings, cutoff = .2)
-print(four_fac$loadings, cutoff = .2)
+print(three_fac$loadings, cutoff = .3)
+print(four_fac$loadings, cutoff = .3)
+```
+
+* Retain items with single loading >.5 and not cross-loadings >.3
+
+```{r, three-fac-cfa-1}
+one_level_three_fac_cfa1 <- 
+'
+  f1 =~ copd + diab + hyp + obi + can
+  f2 =~ dem + hf + ost + pal + str + af
+  f3 =~ lrn + men
+'
+
+three_fac_fit1 <- sem(model = one_level_three_fac_cfa1, data = gp1, estimator = "MLR")
+
+summary(three_fac_fit1, fit.measures = TRUE, standardized = TRUE)
+
+modindices(three_fac_fit1, sort. = TRUE)
+
+```
+
+```{r, four-fac-cfa-1}
+one_level_four_fac_cfa1 <- 
+'
+  f1 =~ str + af + flu
+  f2 =~ obi + ast + copd
+  f3 =~ lrn + men
+  f4 =~ ost + pal + dem
+'
+
+four_fac_fit1 <- sem(model = one_level_four_fac_cfa1, data = gp1, estimator = "MLR")
+
+summary(four_fac_fit1, fit.measures = TRUE, standardized = TRUE)
+
+modindices(four_fac_fit1, sort. = TRUE)
+
 ```
@@
 ```{r}
-
 summary(three_fac)
@@
 
-## QOF disease register CFA
+## CFA
 
-```{r, cfa-1}
-cfa1 <- 
+### Cardiovascular factor
+
+```{r, cfa-cardiovascular}
+cv_one_level_cfa1 <- 
+  '
+  cardio      =~ af + chd + hf + str
+  '
+
+cv_two_level_cfa1 <- 
 '
   level: 1
-  cardio      =~ af + chd + hf + hyp + str
-  pulmonary   =~ flu + ast + copd
-  cognitive   =~ dem +lrn + men
-  f4          =~ diab + obi
-  age         =~ can + ost + pal
+  cardio      =~ af + chd + hf + str
 
   level: 2 # Saturated correlation matrix
-  # af    ~~ af + chd + hf + hyp + str + flu + ast + copd
-  # chd   ~~ chd + hf + hyp + str + flu + ast + copd
-  # hf    ~~ hf + hyp + str + flu + ast + copd
-  # hyp   ~~ hyp + str + flu + ast + copd
-  # str   ~~ str + flu + ast + copd
-  # flu   ~~ flu + ast + copd
-  # ast   ~~ ast + copd
-  # copd  ~~ copd
 
-  af    ~~ af + chd + hf + hyp + str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
-  chd   ~~ chd + hf + hyp + str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
-  hf    ~~ hf + hyp + str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
-  hyp   ~~ hyp + str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
-  str   ~~ str + flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
-  flu   ~~ flu + ast + copd + lrn + men + diab + obi + can + dem + ost + pal
-  ast   ~~ ast + copd + lrn + men + diab + obi + can + dem + ost + pal
-  copd  ~~ copd + lrn + men + diab + obi + can + dem + ost + pal
-  lrn   ~~ lrn + men + diab + obi + can + dem + ost + pal
-  men   ~~ men + diab + obi + can + dem + ost + pal
-  diab  ~~ diab + obi + can + dem + ost + pal
-  obi   ~~ obi + can + dem + ost + pal
-  can   ~~ can + dem + ost + pal
+  af    ~~ af + chd + hf + str
+  chd   ~~ chd + hf + str
+  hf    ~~ hf + str
+  str   ~~ str
+'
+
+cv_one_level_fit1 <- cfa(model = cv_one_level_cfa1, data = gp1, estimator = "MLR")
+cv_two_level_fit1 <- cfa(model = cv_two_level_cfa1, data = gp1, cluster = "cluster", estimator = "MLR")
+
+summary(cv_one_level_fit1, fit.measures = TRUE, standardized = TRUE)
+modindices(cv_one_level_fit1, sort. = TRUE)
+
+summary(cv_two_level_fit1, fit.measures = TRUE, standardized = TRUE)
+modindices(cv_two_level_fit1, sort. = TRUE)
+
+lavInspect(cv_two_level_fit1, "icc")
+```
+
+### Lifestyle factor
+
+```{r, cfa-lifestyle}
+life_one_level_cfa1 <- 
+  '
+  life      =~ diab + copd + obi + can
+  '
+
+life_two_level_cfa1 <- 
+'
+  level: 1
+  life      =~ diab + copd + obi + can
+
+  level: 2 # Saturated correlation matrix
+
+  diab  ~~ diab + copd + obi + can
+  copd  ~~ copd + obi + can
+  obi   ~~ obi + can
+  can   ~~ can
+'
+
+life_one_level_fit1 <- cfa(model = life_one_level_cfa1, data = gp1, estimator = "MLR")
+life_two_level_fit1 <- cfa(model = life_two_level_cfa1, data = gp1, cluster = "cluster", estimator = "MLR")
+
+summary(life_one_level_fit1, fit.measures = TRUE, standardized = TRUE)
+modindices(life_one_level_fit1, sort. = TRUE)
+
+summary(life_two_level_fit1, fit.measures = TRUE, standardized = TRUE)
+modindices(life_two_level_fit1, sort. = TRUE)
+
+lavInspect(life_two_level_fit1, "icc")
+```
+
+```{r, cfa-age}
+age_two_level_cfa1 <- 
+'
+  level: 1
+  age      =~ dem + rar + pal + ost
+
+  level: 2 # Saturated correlation matrix
+  dem ~~ dem + rar + pal + ost 
+  rar ~~ rar + pal + ost 
+  pal ~~ pal + ost 
+  ost ~~ ost
+'
+
+age_two_level_fit1 <- cfa(model = age_two_level_cfa1, data = gp1, cluster = "cluster", estimator = "MLR")
+
+summary(age_two_level_fit1, fit.measures = TRUE, standardized = TRUE)
+modindices(age_two_level_fit1, sort. = TRUE)
+
+lavInspect(age_two_level_fit1, "icc")
+
+# rar ns and low loading
+age_two_level_cfa2 <- 
+'
+  level: 1
+  age  =~ dem + ost + pal
+
+  level: 2 # Saturated correlation matrix
   dem ~~ dem + ost + pal
@@
 '
-# rar epi
 
-fit1 <- sem(model = cfa1, data = gp1, cluster = "cluster", estimator = "MLR")
+age_two_level_fit2 <- cfa(model = age_two_level_cfa2, data = gp1, cluster = "cluster", estimator = "MLR")
 
-summary(fit1, fit.measures=TRUE, standardized = TRUE)
+summary(age_two_level_fit2, fit.measures = TRUE, standardized = TRUE)
+modindices(age_two_level_fit2, sort. = TRUE)
 
-lavInspect(fit1, "icc")
+lavInspect(age_two_level_fit2, "icc")
+
 ```
+
+* Too few df to calculate model fit
+
+### Cardiovascular and lifestyle
+
+```{r, cfa-cv-lifestyle}
+cv_life_two_level_cfa1 <- 
+'
+  level: 1
+  cardio    =~ af + chd + hf + str
+  life      =~ diab + copd + obi + can
+
+  level: 2 # Saturated correlation matrix
+  af    ~~ af + chd + hf + str + diab + copd + obi + can
+  chd   ~~ chd + hf + str + diab + copd + obi + can
+  hf    ~~ hf + str + diab + copd + obi + can
+  str   ~~ str + diab + copd + obi + can
+  diab  ~~ diab + copd + obi + can
+  copd  ~~ copd + obi + can
+  obi   ~~ obi + can
+  can   ~~ can
+'
+
+cv_life_two_level_fit1 <- cfa(model = cv_life_two_level_cfa1, data = gp1, cluster = "cluster", estimator = "MLR")
+
+summary(cv_life_two_level_fit1, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+modindices(cv_life_two_level_fit1, sort. = TRUE)
+
+lavInspect(cv_life_two_level_fit1, "icc")
+
+# Removed cancer as had highest mi (46.793)
+cv_life_two_level_cfa2 <- 
+'
+  level: 1
+  cardio    =~ af + chd + hf + str
+  life      =~ diab + copd + obi
+
+  level: 2 # Saturated correlation matrix
+  af    ~~ af + chd + hf + str + diab + copd + obi
+  chd   ~~ chd + hf + str + diab + copd + obi
+  hf    ~~ hf + str + diab + copd + obi
+  str   ~~ str + diab + copd + obi
+  diab  ~~ diab + copd + obi
+  copd  ~~ copd + obi
+  obi   ~~ obi
+'
+
+cv_life_two_level_fit2 <- cfa(model = cv_life_two_level_cfa2, data = gp1, cluster = "cluster", estimator = "MLR")
+summary(cv_life_two_level_fit2, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+modindices(cv_life_two_level_fit2, sort. = TRUE)
+
+# Removed diab 
+cv_life_two_level_cfa3 <- 
+'
+  level: 1
+  cardio    =~ af + chd + hf + str
+  life      =~ copd + obi
+
+  level: 2 # Saturated correlation matrix
+  af    ~~ af + chd + hf + str + copd + obi
+  chd   ~~ chd + hf + str + copd + obi
+  hf    ~~ hf + str + copd + obi
+  str   ~~ str + copd + obi
+  copd  ~~ copd + obi
+  obi   ~~ obi
+'
+
+cv_life_two_level_fit3 <- cfa(model = cv_life_two_level_cfa3, data = gp1, cluster = "cluster", estimator = "MLR")
+summary(cv_life_two_level_fit3, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+modindices(cv_life_two_level_fit3, sort. = TRUE)
+
+## test final model on unseen data
+cv_life_two_level_test <- 
+  cfa(model = cv_life_two_level_cfa3, data = gp2, cluster = "cluster", estimator = "MLR")
+summary(cv_life_two_level_test, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+
+```
+
+### Cardiovascular, lifestyle, and age
+
+```{r, cfa-cv-lifestyle-age}
+cv_life_age_two_level_cfa1 <- 
+'
+  level: 1
+  cardio    =~ af + chd + hf + str
+  life      =~ copd + obi
+  age       =~ dem + ost
+
+  level: 2 # Saturated correlation matrix
+  af    ~~ af + chd + hf + str + copd + obi + dem + ost
+  chd   ~~ chd + hf + str + copd + obi + dem + ost
+  hf    ~~ hf + str + copd + obi + dem + ost
+  str   ~~ str + copd + obi + dem + ost
+  copd  ~~ copd + obi + dem + ost
+  obi   ~~ obi + dem + ost
+  dem   ~~ dem + ost
+  ost   ~~ ost
+'
+
+cv_life_age_two_level_fit1 <- 
+  cfa(model = cv_life_age_two_level_cfa1, data = gp1, cluster = "cluster", estimator = "MLR")
+
+summary(cv_life_age_two_level_fit1, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+modindices(cv_life_age_two_level_fit1, sort. = TRUE)
+
+lavInspect(cv_life_age_two_level_fit1, "icc")
+lavInspect(cv_life_age_two_level_fit1, "cov.lv")
+
+## test final model on unseen data
+cv_life_two_level_test <- 
+  cfa(model = cv_life_age_two_level_cfa1, data = gp2, cluster = "cluster", estimator = "MLR")
+summary(cv_life_two_level_test, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+
+```
+
+### Cardiovascular, lifestyle, and age
+
+```{r, cfa-cv-lifestyle-age-men}
+cv_life_age_cog_two_level_cfa1 <- 
+'
+  level: 1
+  cardio    =~ af + chd + hf + str
+  life      =~ copd + obi
+  age       =~ dem + ost
+  cog       =~ lrn + men
+
+  level: 2 # Saturated correlation matrix
+  af    ~~ af + chd + hf + str + copd + obi + dem + ost + lrn + men
+  chd   ~~ chd + hf + str + copd + obi + dem + ost + lrn + men
+  hf    ~~ hf + str + copd + obi + dem + ost + lrn + men
+  str   ~~ str + copd + obi + dem + ost + lrn + men
+  copd  ~~ copd + obi + dem + ost + lrn + men
+  obi   ~~ obi + dem + ost + lrn + men
+  dem   ~~ dem + ost + lrn + men
+  ost   ~~ ost + lrn + men
+  lrn   ~~ lrn + men
+  men   ~~ men
+'
+
+cv_life_age_cog_two_level_fit1 <- 
+  cfa(model = cv_life_age_cog_two_level_cfa1, data = gp1, cluster = "cluster", estimator = "MLR")
+
+summary(cv_life_age_cog_two_level_fit1, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+modindices(cv_life_age_cog_two_level_fit1, sort. = TRUE)
+
+lavInspect(cv_life_age_cog_two_level_fit1, "icc")
+lavInspect(cv_life_age_cog_two_level_fit1, "cov.lv")
+
+## test final model on unseen data
+cv_life_age_cog_two_level_test <- 
+  cfa(model = cv_life_age_cog_two_level_cfa1, data = gp2, cluster = "cluster", estimator = "MLR")
+summary(cv_life_age_cog_two_level_test, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+
+```
+
+## Factor scores
+
+```{r}
+m1 <- cfa(model = cv_life_age_two_level_cfa1, data = gp, cluster = "cluster", estimator = "MLR")
+summary(m1,fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
+
+new_df <- bind_cols(gp, as_tibble(predict(m1)))
+summary(lm(flu ~ cardio + life + age, data = new_df))
+car::vif(lm(flu ~ cardio + life, data = new_df))
+```
+
+## PCA
+
+```{r}
+psych::fa.parallel(select(gp1, chd:flu))
+five_fac <- psych::fa(select(gp1, chd:flu), nfactors = 3, rotate = "varimax")
+print(five_fac$loadings, cutoff = .2)
+
+dis_pca <- psych::principal(select(gp1, chd:flu), nfactors = 3, scores = TRUE)
+plot(dis_pca$values)
+dis_pca$rotation
+dis_pca_scores <- bind_cols(practice_id = gp1$practice_id, dis_pca$scores)
+
+# 2d plot
+x <- dis_pca$loadings[,1]
+y <- dis_pca$loadings[,2]
+z <- dis_pca$loadings[,3]
+
+pca_plot_df <- bind_cols(dis = names(x), x = x, y = y, z = z)
+
+ggplot(aes(x = x, y = y), data = pca_plot_df) +
+  geom_text(aes(label = dis))
+
+ggplot(aes(x = x, y = z), data = pca_plot_df) +
+  geom_text(aes(label = dis))
+
+# 3d plot
+plotly::plot_ly(x=x, y=y, z=z, data = pca_plot_df,
+                type="scatter3d", mode="text", text = ~dis)
+```

### 2021-03-06 r_scripts/run_all_preparing_diffs.R
Added script to run all preparing differences files

@@ -1,0 +1,8 @@
+library(tidyverse)
+library(rmarkdown)
+
+rmd_files <- list.files("r_notebooks/preparing_differences")[grep(".Rmd", list.files("r_notebooks/preparing_differences"))]
+
+map(.x = rmd_files,
+    .f = ~render(paste0("r_notebooks/preparing_differences/", .x)))
+

### 2021-03-06 r_notebooks/preparing_differences/preparing_ace_inhib.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_ace_inhib.Rmd
@@
 gp <- 
-  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
+  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
   mutate(npat = N,
@@
 ace <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_ace-inhibitors.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_ace-inhibitors.rds") %>% 
   janitor::clean_names() %>% 
@@
   filter(miss_covid > 0 | miss_non_covid > 0) %>% 
-  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))
+  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))
 
@@
   ace_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   ace_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   ace_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(mean = ARIMA(log(n))) %>%
   interpolate(ace_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(mean = ARIMA(log(n))) %>% 
   interpolate(ace_monthly_quantity_gp_pre_cv19)
@@
   ace_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
+                  regionalCV(init = 36, step = 3))
 plan(sequential)
@@
 ace_gp_cv_models %>%
-  saveRDS("../data/ace_gp_cv_models.rds")
+  saveRDS("../../data/ace_gp_cv_models.rds")
 
 ace_gp_cv_models <- 
-  read_rds("../data/ace_gp_cv_models.rds")
+  read_rds("../../data/ace_gp_cv_models.rds")
 
@@
   group_by(regional_unit) %>% 
-  arrange(RMSE, MAE) %>% 
+  rankModels() %>% 
   slice(1, .preserve = TRUE) %>% 
@@
   group_by(regional_unit) %>% 
-  arrange(RMSE, MAE) %>% 
+  rankModels() %>% 
   slice(1, .preserve = TRUE)
@@
               filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
-              regionalJointFcsts(h = "6 months"))
+              regionalJointFcsts(h = "8 months"))
 plan(sequential)
@@
 ace_gp_fcsts %>%
-  saveRDS("../data/ace_gp_fcsts.rds")
+  saveRDS("../../data/ace_gp_fcsts.rds")
 
 ace_gp_fcsts <- 
-  read_rds("../data/ace_gp_fcsts.rds")
+  read_rds("../../data/ace_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/ace_discreps.rds")
+  saveRDS("../../data/differences/ace_discreps.rds")
 ```

### 2021-03-06 r_notebooks/preparing_differences/preparing_adrenoceptor_agonists.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_adrenoceptor_agonists.Rmd
@@
 adreno <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_adrenoceptor-agonists.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_adrenoceptor-agonists.rds") %>% 
   mutate(datename = dmy(paste0("28-", datename))) %>% 
@@
   adreno_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   adreno_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   adreno_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(arima = ARIMA(n)) %>%
   interpolate(adreno_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(adreno_monthly_quantity_gp_pre_cv19)
@@
   adreno_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
+                  regionalCV(init = 36, step = 3))
 plan(sequential)
@@
 adreno_gp_cv_models %>%
-  saveRDS("../data/adreno_gp_cv_models.rds")
+  saveRDS("../../data/adreno_gp_cv_models.rds")
 
 adreno_gp_cv_models <- 
-  read_rds("../data/adreno_gp_cv_models.rds")
+  read_rds("../../data/adreno_gp_cv_models.rds")
 
@@
 adreno_gp_fcsts %>%
-  saveRDS("../data/adreno_gp_fcsts.rds")
+  saveRDS("../../data/adreno_gp_fcsts.rds")
 
 adreno_gp_fcsts <- 
-  read_rds("../data/adreno_gp_fcsts.rds")
+  read_rds("../../data/adreno_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/adreno_discreps.rds")
+  saveRDS("../../data/differences/adreno_discreps.rds")
 

### 2021-03-06 r_notebooks/preparing_differences/preparing_all_prescribing.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-03-04 r_notebooks/preparing_all_prescribing.Rmd
@@
 all_prescribing <- 
-  read_csv("../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
+  read_csv("../../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
   mutate(datename = dmy(paste(28, datename, sep = "-")),
@@
   all_prescribing %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   fill_gaps() %>%
-  slice(1:(n()-6), .preserve = TRUE) %>%
+  slice(1:(n()-8), .preserve = TRUE) %>%
   stretch_tsibble(.init = 36, .step = 3) %>%
@@
 all_prescribing_fable_forecasts <- 
-  fable_models %>%
-  forecast(h = 6)
+  all_prescribing_fable_models %>%
+  forecast(h = 8)
 
 all_prescribing_fable_fits <- 
-  fable_forecasts %>% 
+  all_prescribing_fable_forecasts %>% 
   accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
@@
   fill_gaps() %>%
-  slice(1:(n()-6), .preserve = TRUE) %>%
+  slice(1:(n()-8), .preserve = TRUE) %>%
   stretch_tsibble(.init = 36, .step = 3) %>%
   prophetModels() %>%
-  forecast(h = 6) %>%
+  forecast(h = 8) %>%
   accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
@@
   bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
-  arrange(RMSE, MAE)
+  rankModels()
 plan(sequential)
@@
 all_prescribing_cv_models %>%
-  saveRDS("../data/all_prescribing_cv_models.rds")
+  saveRDS("../../data/all_prescribing_cv_models.rds")
 
 all_prescribing_cv_models <- 
-  read_rds("../data/all_prescribing_cv_models.rds")
+  read_rds("../../data/all_prescribing_cv_models.rds")
 
 all_prescribing_cv_models %>% 
-  arrange(RMSE, MAE) %>% 
+  rankModels() %>% 
   slice(1, .preserve = TRUE) %>% 
@@
 all_prescribing_cv_models %>% 
-  arrange(RMSE, MAE) %>% 
+  rankModels() %>% 
   slice(1, .preserve = TRUE) %>% 
@@
   all_prescribing_cv_models %>% 
-  arrange(RMSE, MAE) %>% 
+  rankModels() %>% 
   slice(1, .preserve = TRUE)
@@
   all_prescribing_pre_cv19 %>%
-  regionalJointFcsts(h = "6 months")
+  regionalJointFcsts(h = "8 months")
 plan(sequential)
@@
 all_prescribing_fcsts %>%
-  saveRDS("../data/all_prescribing_fcsts.rds")
+  saveRDS("../../data/all_prescribing_fcsts.rds")
 
 all_prescribing_fcsts <- 
-  read_rds("../data/all_prescribing_fcsts.rds")
+  read_rds("../../data/all_prescribing_fcsts.rds")
 
@@
 best_model_discrep %>% 
-  saveRDS("../data/differences/all_prescribing_discreps.rds")
+  saveRDS("../../data/differences/all_prescribing_discreps.rds")
 

### 2021-03-06 r_notebooks/preparing_differences/preparing_azithro.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_azithro.Rmd
@@
 azithro <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_azithromycin.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_azithromycin.rds") %>% 
   janitor::clean_names() %>% 
@@
   azithro_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   azithro_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   azithro_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(arima = ARIMA(n)) %>%
   interpolate(azithro_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(azithro_monthly_quantity_gp_pre_cv19)
@@
 #   azithro_monthly_quantity_gp_pre_cv19 %>%
-#                   regionalCV(init = 48, step = 3))
+#                   regionalCV(init = 36, step = 3))
 # plan(sequential)
@@
 # azithro_gp_cv_models %>%
-#   saveRDS("../data/azithro_gp_cv_models.rds")
+#   saveRDS("../../data/azithro_gp_cv_models.rds")
 
 azithro_gp_cv_models <- 
-  read_rds("../data/azithro_gp_cv_models.rds")
+  read_rds("../../data/azithro_gp_cv_models.rds")
 
@@
 #               filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
-#               regionalJointFcsts(h = "6 months"))
+#               regionalJointFcsts(h = "8 months"))
 # plan(sequential)
@@
 # azithro_gp_fcsts %>%
-#   saveRDS("../data/azithro_gp_fcsts.rds")
+#   saveRDS("../../data/azithro_gp_fcsts.rds")
 
 azithro_gp_fcsts <- 
-  read_rds("../data/azithro_gp_fcsts.rds")
+  read_rds("../../data/azithro_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/azithro_discreps.rds")
+  saveRDS("../../data/differences/azithro_discreps.rds")
 

### 2021-03-06 r_notebooks/preparing_differences/preparing_contra.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_contra.Rmd
@@
 contra <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_contra-combined.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_contra-combined.rds") %>% 
   janitor::clean_names() %>% 
@@
   contra_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   contra_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   contra_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(arima = ARIMA(n)) %>%
   interpolate(contra_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(contra_monthly_quantity_gp_pre_cv19)
@@
   contra_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
+                  regionalCV(init = 36, step = 3))
 plan(sequential)
@@
 contra_gp_cv_models %>%
-  saveRDS("../data/contra_gp_cv_models.rds")
+  saveRDS("../../data/contra_gp_cv_models.rds")
 
 contra_gp_cv_models <- 
-  read_rds("../data/contra_gp_cv_models.rds")
+  read_rds("../../data/contra_gp_cv_models.rds")
 
@@
 contra_gp_fcsts %>%
-  saveRDS("../data/contra_gp_fcsts.rds")
+  saveRDS("../../data/contra_gp_fcsts.rds")
 
 contra_gp_fcsts <- 
-  read_rds("../data/contra_gp_fcsts.rds")
+  read_rds("../../data/contra_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/contra_discreps.rds")
+  saveRDS("../../data/differences/contra_discreps.rds")
 

### 2021-03-06 r_notebooks/preparing_differences/preparing_nsaid.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_nsaid.Rmd
@@
 nsaid <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_NSAIDs.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_NSAIDs.rds") %>% 
   janitor::clean_names() %>% 
@@
   nsaid_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   nsaid_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   nsaid_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(arima = ARIMA(n)) %>%
   interpolate(nsaid_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(nsaid_monthly_quantity_gp_pre_cv19)
@@
   nsaid_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
+                  regionalCV(init = 36, step = 3))
 plan(sequential)
@@
 nsaid_gp_cv_models %>%
-  saveRDS("../data/nsaid_gp_cv_models.rds")
+  saveRDS("../../data/nsaid_gp_cv_models.rds")
 
 nsaid_gp_cv_models <- 
-  read_rds("../data/nsaid_gp_cv_models.rds")
+  read_rds("../../data/nsaid_gp_cv_models.rds")
 
@@
 nsaid_gp_fcsts %>%
-  saveRDS("../data/nsaid_gp_fcsts.rds")
+  saveRDS("../../data/nsaid_gp_fcsts.rds")
 
 nsaid_gp_fcsts <- 
-  read_rds("../data/nsaid_gp_fcsts.rds")
+  read_rds("../../data/nsaid_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/nsaid_discreps.rds")
+  saveRDS("../../data/differences/nsaid_discreps.rds")
 

### 2021-03-06 r_notebooks/preparing_differences/preparing_oac_prop.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_oac_prop.Rmd
@@
 oac <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_OAC.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_OAC.rds") %>% 
   janitor::clean_names() %>% 
@@
   oac_monthly_prop_gp %>% 
-  filter(datename < yearmonth("2020 March"))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(oac_monthly_prop_gp_pre_cv19) %>% 
-  filter(!regional_unit %in% # Remove those with <62 months data
+  filter(!regional_unit %in% # Remove those with <60 months data
            (oac_monthly_prop_gp_pre_cv19 %>% 
@@
               count() %>% 
-              filter(n < 62) %>% 
+              filter(n < 60) %>% 
               .$regional_unit) &
@@
   oac_monthly_prop_gp_pre_cv19 %>%
-                  regionalCVBound(init = 48, step = 3))
+                  regionalCVBound(init = 36, step = 3))
 plan(sequential)
@@
 oac_gp_cv_models %>%
-  saveRDS("../data/oac_gp_cv_models.rds")
+  saveRDS("../../data/oac_gp_cv_models.rds")
 
 oac_gp_cv_models <- 
-  read_rds("../data/oac_gp_cv_models.rds")
+  read_rds("../../data/oac_gp_cv_models.rds")
 
@@
               oac_monthly_prop_gp_pre_cv19 %>%
-              regionalJointFcstsBound(h = "6 months"))
+              regionalJointFcstsBound(h = "8 months"))
 plan(sequential)
@@
 oac_gp_fcsts %>%
-  saveRDS("../data/oac_gp_fcsts.rds")
+  saveRDS("../../data/oac_gp_fcsts.rds")
 
 oac_gp_fcsts <- 
-  read_rds("../data/oac_gp_fcsts.rds")
+  read_rds("../../data/oac_gp_fcsts.rds")
 
@@
 
-oac_monthly_quantity_gp %>% 
+oac_monthly_prop_gp %>% 
   filter(regional_unit %in%
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/oac_discreps.rds")
+  saveRDS("../../data/differences/oac_discreps.rds")
 ```

### 2021-03-06 r_notebooks/preparing_differences/preparing_cortico_resp.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_cortico_resp.Rmd
@@
 cortico <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_cortico-resp.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_cortico-resp.rds") %>% 
   janitor::clean_names() %>% 
@@
   cortico_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   cortico_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   cortico_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(arima = ARIMA(n)) %>%
   interpolate(cortico_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(cortico_monthly_quantity_gp_pre_cv19)
@@
   cortico_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
+                  regionalCV(init = 36, step = 3))
 plan(sequential)
@@
 cortico_gp_cv_models %>%
-  saveRDS("../data/cortico_gp_cv_models.rds")
+  saveRDS("../../data/cortico_gp_cv_models.rds")
 
 cortico_gp_cv_models <- 
-  read_rds("../data/cortico_gp_cv_models.rds")
+  read_rds("../../data/cortico_gp_cv_models.rds")
 
@@
 cortico_gp_fcsts %>%
-  saveRDS("../data/cortico_gp_fcsts.rds")
+  saveRDS("../../data/cortico_gp_fcsts.rds")
 
 cortico_gp_fcsts <- 
-  read_rds("../data/cortico_gp_fcsts.rds")
+  read_rds("../../data/cortico_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/cortico_discreps.rds")
+  saveRDS("../../data/differences/cortico_discreps.rds")
 ```

### 2021-03-06 r_notebooks/preparing_differences/preparing_hcq.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_hcq.Rmd
@@
 hcq <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_HCQ.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_HCQ.rds") %>% 
   mutate(datename = dmy(paste0("28-", datename)),
@@
   hcq_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   hcq_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   hcq_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(arima = ARIMA(n)) %>%
   interpolate(hcq_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(hcq_monthly_quantity_gp_pre_cv19)
@@
   hcq_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
+                  regionalCV(init = 36, step = 3))
 plan(sequential)
@@
 hcq_gp_cv_models %>%
-  saveRDS("../data/hcq_gp_cv_models.rds")
+  saveRDS("../../data/hcq_gp_cv_models.rds")
 
 hcq_gp_cv_models <- 
-  read_rds("../data/hcq_gp_cv_models.rds")
+  read_rds("../../data/hcq_gp_cv_models.rds")
 
@@
 hcq_gp_fcsts %>%
-  saveRDS("../data/hcq_gp_fcsts.rds")
+  saveRDS("../../data/hcq_gp_fcsts.rds")
 
 hcq_gp_fcsts <- 
-  read_rds("../data/hcq_gp_fcsts.rds")
+  read_rds("../../data/hcq_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/hcq_discreps.rds")
+  saveRDS("../../data/differences/hcq_discreps.rds")
 ```

### 2021-03-06 r_notebooks/preparing_differences/preparing_paracet.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_paracet.Rmd
@@
 paracet <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_paracetamol.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_paracetamol.rds") %>% 
   janitor::clean_names() %>% 
@@
   paracet_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   paracet_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   paracet_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(arima = ARIMA(n)) %>%
   interpolate(paracet_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(paracet_monthly_quantity_gp_pre_cv19)
@@
   paracet_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
+                  regionalCV(init = 36, step = 3))
 plan(sequential)
@@
 paracet_gp_cv_models %>%
-  saveRDS("../data/paracet_gp_cv_models.rds")
+  saveRDS("../../data/paracet_gp_cv_models.rds")
 
 paracet_gp_cv_models <- 
-  read_rds("../data/paracet_gp_cv_models.rds")
+  read_rds("../../data/paracet_gp_cv_models.rds")
 
@@
 paracet_gp_fcsts %>%
-  saveRDS("../data/paracet_gp_fcsts.rds")
+  saveRDS("../../data/paracet_gp_fcsts.rds")
 
 paracet_gp_fcsts <- 
-  read_rds("../data/paracet_gp_fcsts.rds")
+  read_rds("../../data/paracet_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/paracet_discreps.rds")
+  saveRDS("../../data/differences/paracet_discreps.rds")
 

### 2021-03-06 r_notebooks/preparing_differences/preparing_vitd.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

--- 2021-02-18 r_notebooks/preparing_vitd.Rmd
@@
 vitd <- 
-  read_rds("../data/presdata_updates_040121/presc_wales_vitamind.rds") %>% 
+  read_rds("../../data/presdata_updates_040121/presc_wales_vitamind.rds") %>% 
   janitor::clean_names() %>% 
@@
   vitd_monthly_count %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   vitd_monthly_quantity_gp %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  filter(datename < yearmonth(dmy("01-01-2020")))
 
@@
   vitd_monthly_count_pre_cv19 %>% 
-  model(mean = MEAN(n)) %>%
+  model(arima = ARIMA(n)) %>%
   interpolate(vitd_monthly_count_pre_cv19)
@@
   group_by(regional_unit) %>% 
-  model(mean = MEAN(n)) %>% 
+  model(arima = ARIMA(n)) %>% 
   interpolate(vitd_monthly_quantity_gp_pre_cv19)
@@
   vitd_monthly_quantity_gp_pre_cv19 %>%
-                  regionalCV(init = 48, step = 3))
+                  regionalCV(init = 36, step = 3))
 plan(sequential)
@@
 vitd_gp_cv_models %>%
-  saveRDS("../data/vitd_gp_cv_models.rds")
+  saveRDS("../../data/vitd_gp_cv_models.rds")
 
 vitd_gp_cv_models <- 
-  read_rds("../data/vitd_gp_cv_models.rds")
+  read_rds("../../data/vitd_gp_cv_models.rds")
 
@@
 vitd_gp_fcsts %>%
-  saveRDS("../data/vitd_gp_fcsts.rds")
+  saveRDS("../../data/vitd_gp_fcsts.rds")
 
 vitd_gp_fcsts <- 
-  read_rds("../data/vitd_gp_fcsts.rds")
+  read_rds("../../data/vitd_gp_fcsts.rds")
 
@@
 best_model_gp_discrep %>% 
-  saveRDS("../data/differences/vitd_discreps.rds")
+  saveRDS("../../data/differences/vitd_discreps.rds")
 

### 2021-04-01 OneDrive/3_rscripts/01_gpextract_processraw.R
Unlinked OneDrive

@@ -1,116 +1,0 @@
-
-## Name: 01_Processraw.R
-## Date: 16/09/2020
-
-## Clear
-rm(list=ls())
-
-## Packages
-library(dplyr)
-library(dbplyr)
-
-##
-## PART 1: Preliminaries
-##
-
-## Directory for source files
-dir_data <- "C:/Users/Dan/Documents/BCUHB"
-
-## Month number and date name lookups
-monthlookup <- read.csv("2_interimdata/_misc/monthlookup.csv", stringsAsFactors = F)
-head(monthlookup)
-
-## BNF chemical code to chemical name lookup
-chemlookup <- read.csv("1_data/bnfchemsubs_lookup.csv", stringsAsFactors = F)
-head(chemlookup)
-
-## Function: Read single GP extract
-readfile <- function(x, dir) {
-  
-  ## Define path and read data
-  fname <- paste(dir,x,"/",x,".csv",sep="")
-  fulldata <- read.csv(fname,stringsAsFactors = F)
-  
-  ## If columns = 12 add two blanks
-  if(length(fulldata)==12) {
-    fulldata <- fulldata %>%
-      mutate(DDD=NA) %>%
-      mutate(ADQ=NA)
-  }
-  return(fulldata)
-}  
-
-##
-## PART 2: Read prescribing data
-##
-
-## NHS Shared Services Partnership data directory
-nhs.ssp.dir <- paste(dir_data,"/nhswssp/GP Data Extract/",sep="")
-
-## List file names
-filenames_all <- list.files(nhs.ssp.dir)
-
-## Subset years 2016-20
-filenames_set1 <- c(filenames_all[grepl("2020", filenames_all)],
-                    filenames_all[grepl("2019", filenames_all)],
-                    filenames_all[grepl("2018", filenames_all)],
-                    filenames_all[grepl("2017", filenames_all)],
-                    filenames_all[grepl("2016", filenames_all)])
-
-
-## Create list GP extracts
-lgpdata <- filenames_set1 %>%
-  purrr::map(readfile, dir=nhs.ssp.dir)
-
-## Convert GP data list to DF
-gppresdata <- do.call(rbind.data.frame, lgpdata)
-rm(lgpdata)
-
-## Checks
-str(gppresdata)
-sum(is.na(gppresdata$BNFCode)==T)
-
-## Merge in DDD multipliers
-gppresdata2 <- gppresdata %>% 
[…]

### 2021-04-01 OneDrive/3_rscripts/02_gpextract_splitcases.R

@@ -1,256 +1,0 @@
-
-## Name: 02_splitcases.R
-## Date: 16/09/2020
-
-## Clear
-rm(list=ls())
-
-## Packages
-library(dplyr)
-library(VIM)
-library(ggplot2)
-
-## Plotting functions
-source("3_rscripts/99_UtilityFunctions.R")
-
-##
-## PART 1: LOAD DATA
-##
-
-## Connect to database
-con <- DBI::dbConnect(RSQLite::SQLite(), "C:/Users/Dan/Documents/BCUHB/db-gpextract.sqlite")
-db.gpextract <- tbl(con, "gpextract")
-
-## Month number and date name lookups
-monthlookup <- read.csv("C:/Users/Dan/OneDrive/PROJECTS/SERCYMRU/2_interimdata/_misc/monthlookup.csv", stringsAsFactors = F)
-head(monthlookup); tail(monthlookup)
-
-## Observation window
-startmonth <- 73 # Jan-18
-len <- length(73:103) # Jan-18 - 	Jul-20
-
-## Create a vector of month names for plots
-months <- monthlookup %>%
-  filter(month2%in%c(startmonth:103)) %>%
-  arrange(month2) %>%
-  select(datename)
-
-##
-## PART 2: SUBSET CASES
-##
-
-##
-## Chloroquine
-##
-
-## Treatment name
-name <- "Chloroquine"
-
-## Subset 1
-chlor <- c("0504010F0", "1001030C0", "0504010G0", "0504010Z0")
-subdf_chlor <- filter(db.gpextract, bnfchem%in%chlor) %>% collect()
-fn_plotbnf(subdf_chlor, name) # Focus on 1001030C0
-
-## Subset 2
-chlor <- c("1001030C0")
-subdf_chlor <- filter(db.gpextract, bnfchem%in%chlor) %>% collect()
-fn_plotbnf(subdf_chlor, name)
-
-## Outputs
-ggsave(paste("C:/Users/Dan/Documents/SERCYMRU/4_outputs/plot4/trends/plot_", name, ".tiff",sep=""), dpi=200, width = 16, height = 6, units = "cm")
-saveRDS(subdf_chlor, paste("C:/Users/Dan/Documents/SERCYMRU/3_data/presc_wales_",name,".rds",sep=""))
-
-##
-## Azithromycin & Famotidine 
-## 
-
-## Azithromycin
-name <- "Azithromycin"
[…]

### 2021-04-01 OneDrive/3_rscripts/03_gpdata_prep.R

@@ -1,133 +1,0 @@
-
-## Name: 01_gpsummary.R
-## Date: 08/12/19
-
-## Clear
-rm(list=ls())
-
-## Packages
-library(readr)
-library(dplyr)
-library(VIM)
-
-##
-## PART 1: GP PRACTICE ANALYSIS
-##
-
-## Local data directory
-dir_data <- "C:/Users/Dan/Documents/BCUHB"
-
-## NHS Shared Services Partnership data directory
-nhssspdir <- paste(dir_data,"/nhswssp/GP Practice Analysis/",sep="")
-
-## List file names
-filenames <- list.files(nhssspdir)[-9] # removes 'original' folder
-
-## Function: Read single GP extract
-readfile <- function(x) {
-  
-  ## year
-  year <- substr(x,nchar(x)-7,nchar(x)-4)
-  
-  ## Define path and read data
-  fname <- paste(nhssspdir,x,sep="")
-  fulldata <- read.csv(fname,stringsAsFactors = F)
-  fulldata$year <- as.numeric(year)
-  return(fulldata)
-}  
-
-## Create list GP extracts
-gpdata <- filenames %>%
-  purrr::map(readfile)
-
-## Convert GP data list to DF
-dfgpdata <- do.call(rbind.data.frame, gpdata) %>%
-  dplyr::select(PracticeID,LHBName,year,ngp,postcode,dispensing,nprespats,ndisppats) %>%
-  arrange(year,PracticeID)
-
-##
-## PART 2: CHECK DUPLICATES
-##
-
-## Inspect
-head(dfgpdata)
-table(dfgpdata$year) # How much data by year
-str(dfgpdata)
-
-## Check for duplicate ID codes
-dfgpdata %>%
-  group_by(year) %>%
-  dplyr::summarise(n.unique = length(unique(PracticeID)),
-            n.all = length(PracticeID))
-# There are 17 duplicates for 2019
-
-## Obtain duplicate practice IDs
-dup.ids <- dfgpdata %>% 
-  filter(year==2019) %>%
-  mutate(dup.flag = duplicated(PracticeID)) %>%
-  filter(dup.flag==T) %>%
-  select(PracticeID, year, dup.flag)
-
-## View duplicate IDs
-dfgpdata %>% 
-  filter(year==2019) %>%
[…]

### 2021-04-01 OneDrive/3_rscripts/04_agesexmix_prep.R

@@ -1,131 +1,0 @@
-
-## Name: 01_gpsummary.R
-## Date: 08/12/19
-
-## Clear
-rm(list=ls())
-
-## Packages
-library(readr)
-library(dplyr)
-library(VIM)
-
-##
-## Step 5: AGE SEX MIX (2017-2018)
-##
-
-## Function to combine data from two years
-fn_combine <- function(dat_new, dat_old) {
-  tmpdat <- full_join(dat_new, dat_old, by="PracticeID") # do a 'full' join
-  newdat <- tmpdat %>% # coalesce to keep newer data where possible
-    mutate(GPCluster = coalesce(GPCluster.x, GPCluster.y),
-           npat  = coalesce(npat.x, npat.y),
-           npat_male = coalesce(npat_male.x, npat_male.y),
-           npat_fem  = coalesce(npat_fem.x, npat_fem.y),
-           nm_0_4  = coalesce(nm_0_4.x, nm_0_4.y),
-           nm_5_14 = coalesce(nm_5_14.x, nm_5_14.y),
-           nm_15_44 = coalesce(nm_15_44.x, nm_15_44.y),
-           nm_45_64 = coalesce(nm_45_64.x, nm_45_64.y),
-           nm_65_74 = coalesce(nm_65_74.x, nm_65_74.y),
-           nm_75_84 = coalesce(nm_75_84.x, nm_75_84.y),
-           nm_85 = coalesce(nm_85.x, nm_85.y),
-           nf_0_4  = coalesce(nf_0_4.x, nf_0_4.y),
-           nf_5_14 = coalesce(nf_5_14.x, nf_5_14.y),
-           nf_15_44 = coalesce(nf_15_44.x, nf_15_44.y),
-           nf_45_64 = coalesce(nf_45_64.x, nf_45_64.y),
-           nf_65_74 = coalesce(nf_65_74.x, nf_65_74.y),
-           nf_75_84 = coalesce(nf_75_84.x, nf_75_84.y),
-           nf_85 = coalesce(nf_85.x, nf_85.y)) %>%
-    select(-c(npat.x:nf_85.y))
-  return(
-    newdat
-  )
-}
-
-## Read data
-gp_agesexdata_2018 <- read_csv(paste("2_interimdata/5_agesexdata","gp_agesexdata_2018.csv",sep="/"), col_names = TRUE) %>% 
-  select(-year,-lhb,-la) %>%
[…]

### 2021-04-01 OneDrive/3_rscripts/05_setupmaps.R

@@ -1,75 +1,0 @@
-
-## Name: 01_setupmap.R
-## Date: 08/09/20
-
-## Clear
-rm(list=ls())
-
-## Packages
-library(broom)
-library(readr)
-library(dplyr)
-library(rgdal)
-library(rgeos)
-library(VIM)
-library(ggplot2)
-
-## Local data directory
-dir_data <- "C:/Users/Dan/Documents/BCUHB"
-
-## Wales local admin units
-laus_wales <- c("Monmouthshire",
-                "Powys",
-                "Ceredigion",
-                "Carmarthenshire",
-                "Gwynedd",
-                "Conwy",
-                "Denbighshire",
-                "Flintshire",
-                "Wrexham",
-                "Isle of Anglesey",
-                "Pembrokeshire",
-                "Swansea",
-                "Neath Port Talbot",
-                "Bridgend",
-                "Merthyr Tydfil",
-                "Rhondda Cynon Taf",
-                "Vale of Glamorgan",
-                "Cardiff",
-                "Caerphilly",
-                "Blaenau Gwent",
-                "Torfaen",
-                "Newport")
-
-##
-## Step 1: A shapefile for BCUHB mapping
-##
-
-## Load the shapefile
-shapefile <- readOGR(dsn="C:/Users/Dan/Documents/BCUHB/shapefiles/map1", 
-                     layer="Local_Administrative_Units_Level_1_December_2015_Full_Extent_Boundaries_in_England_and_Wales")
-
-## Reshape for ggplot2 using the Broom package
-mapdata_wales <- broom::tidy(shapefile, region="lau115nm") %>%
-  filter(id %in% laus_wales) %>%
-  `colnames<-`(c("long","lat","order","hole","piece","county","id"))
-
-## Save
-write.csv(mapdata_wales,"2_interimdata/4_areadata/mapdata_wales.csv",row.names = F)
-
-## Test map
-mapdata_wales %>%
-  ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group=county), fill = "#333333", color="#cccccc", size = 0.25) + # Plot the map
-  coord_fixed(1) + 
-  theme_minimal() +
-  theme(axis.text.x=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.title.x = element_blank(),
-        axis.text.y=element_blank(),
-        axis.ticks.y=element_blank(),
-        axis.title.y = element_blank())
-
-##
-## END
-##

### 2021-04-01 OneDrive/3_rscripts/06_analysis_cs1_descriptive.R

@@ -1,286 +1,0 @@
-
-## Name: 06_analysis_expl_1.R
-## Date: 08/12/19
-
-## Clear
-rm(list=ls())
-
-## Packages
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(ggbiplot)
-
-##
-source("3_rscripts/99_UtilityFunctions.R")
-
-##
-## PART 1: Read datasets
-##
-
-## Mapping data
-mapdata_wales <- read.csv("2_interimdata/4_areadata/mapdata_wales.csv", stringsAsFactors = F) 
-
-## Month number and date name lookups
-monthlookup <- read.csv("2_interimdata/_misc/monthlookup.csv", stringsAsFactors = F)
-head(monthlookup)
-
-## GP practice data
-df.gpsummary <- readRDS("2_interimdata/2_gpanalysis/gpanalysis1.rds")
-head(df.gpsummary)
-
-## Create a vector of month names for plots
-months <- monthlookup %>%
-  filter(month2%in%c(49:102)) %>%
-  arrange(month2) %>%
-  select(datename)
-
-## Prescribing data
-df.contraception <- readRDS("C:/Users/Dan/Documents/SERCYMRU/3_data/presc_wales_Contraceptives combined.rds")
-head(df.contraception)
-
-##
-## Plot all GP time series
-##
-
-for (i in unique(df.contraception$PracticeID)) {
-  fn_plot1gp(df.contraception, i)
-  ggsave(paste("C:/Users/Dan/Documents/SERCYMRU/4_outputs/case1/",i,".tiff",sep=""),
-         dpi=200, width = 25, height = 12, units = "cm")
-}
-
-##
-## Create dataset of pre- and post-COVID prescribing 
-##
-
-## 
-df1 <- df.contraception %>%
-  filter(grepl("Mar|Apr|May|Jun",datename)) %>%
-  group_by(PracticeID, HB, Locality, year, month2, month) %>%
-  dplyr::summarise(sumq = sum(Quantity, na.rm = T)) %>%
-  #mutate(sumq_pp = sumq/nprespats) %>%
-  mutate(control = ifelse(year=="2020","covid","baseline")) %>%
-  group_by(PracticeID, control, month) %>%
-  dplyr::summarise(meanq_sumq = mean(sumq, na.rm = T)) %>%
-  pivot_wider(names_from = control, values_from = meanq_sumq) %>%
-  mutate(pcdiff = (covid - baseline)/baseline) %>%
-  ungroup()
-head(df1)
-
-##
[…]

### 2021-04-01 OneDrive/3_rscripts/07_analysis_cs1_cluster.R

@@ -1,290 +1,0 @@
-
-## Name: 06_analysis_expl_1.R
-## Date: 08/12/19
-
-## Clear
-rm(list=ls())
-
-## Packages
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(ggbiplot)
-
-##
-source("3_rscripts/99_UtilityFunctions.R")
-
-##
-## PART 1: Read datasets
-##
-
-## Mapping data
-mapdata_wales <- read.csv("2_interimdata/4_areadata/mapdata_wales.csv", stringsAsFactors = F) 
-
-## Month number and date name lookups
-monthlookup <- read.csv("2_interimdata/_misc/monthlookup.csv", stringsAsFactors = F)
-head(monthlookup)
-
-## Create a vector of month names for plots
-months <- monthlookup %>%
-  filter(month2%in%c(49:102)) %>%
-  arrange(month2) %>%
-  select(datename)
-
-## GP practice data
-df.gpsummary <- readRDS("2_interimdata/2_gpanalysis/gpanalysis1.rds") %>%
-  select(PracticeID, year, )
-head(df.gpsummary)
-
-## Prescribing data
-df.contraception <- readRDS("C:/Users/Dan/Documents/SERCYMRU/3_data/presc_wales_Contraceptives combined.rds")
-head(df.contraception)
-
-##
-## Create dataset of pre- and post-COVID prescribing 
-##
-
-## 
-df1 <- df.contraception %>%
-  left_join(filter(df.gpsummary,year==2020)%>%select(-year), by = "PracticeID") %>%
-  filter(grepl("Mar|Apr|May|Jun",datename)) %>%
-  group_by(PracticeID, HB, nprespats, Locality, year, month2, month) %>%
-  dplyr::summarise(sumq = sum(Quantity, na.rm = T)) %>%
-  mutate(sumq_pp = sumq/nprespats) %>%
-  mutate(control = ifelse(year=="2020","covid","baseline")) %>%
-  group_by(PracticeID, control, month) %>%
-  dplyr::summarise(meanq_sumq = mean(sumq_pp, na.rm = T)) %>%
-  pivot_wider(names_from = control, values_from = meanq_sumq) %>%
-  mutate(pcdiff = (covid - baseline)/baseline) %>%
-  ungroup()
[…]

### 2021-04-01 OneDrive/3_rscripts/07_analysis_cs1_regression.R

@@ -1,375 +1,0 @@
-
-## Name: 07_analysis_cs1_regression.R
-## Date: 02/10/2020
-
-## Clear
-rm(list=ls())
-
-## Packages
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(ggbiplot)
-library(VIM)
-
-##
-source("3_rscripts/99_UtilityFunctions.R")
-
-##
-## PART 1: Read datasets
-##
-
-## Mapping data
-mapdata_wales <- read.csv("2_interimdata/4_areadata/mapdata_wales.csv", stringsAsFactors = F) 
-
-## Month number and date name lookups
-monthlookup <- read.csv("2_interimdata/_misc/monthlookup.csv", stringsAsFactors = F)
-head(monthlookup)
-
-## Create a vector of month names for plots
-months <- monthlookup %>%
-  filter(month2%in%c(49:102)) %>%
-  arrange(month2) %>%
-  select(datename)
-
-## GP practice data
-df.gpsummary <- readRDS("2_interimdata/2_gpanalysis/gpanalysis1.rds") %>%
-  filter(year==2019)
-head(df.gpsummary)
-
-##
-df.gpattributes <- readRDS("2_interimdata/5_agesexdata/gp_agesexdata_combined.rds")
-df.gpqof <- readRDS("2_interimdata/6_qof/gp_qof_dregs_combined.rds")
-df.gpphwo <- read.csv("2_interimdata/7_phwodata/gp_phwo_summary_2015.csv", stringsAsFactors = F)
-
-##
-df2_kmean <- readRDS( "2_interimdata/1_gpextract/df_cs1_kmeanclust.rds")
-
-##
-## Linkd data
-##
-
-df2_clust_comb <- df2_kmean %>%
-  left_join(df.gpsummary, by="PracticeID") %>%
-  left_join(df.gpattributes, by="PracticeID") %>%
-  left_join(df.gpqof, by="PracticeID") %>%
-  left_join(df.gpphwo, by="PracticeID") 
-
-## Look at missingness
-df2_clust_comb %>% aggr(numbers = TRUE, prop = c(FALSE, FALSE),bars=F,combined=T,oma = c(10,5,5,3))
-
-##
-## IMD
[…]

### 2021-04-01 OneDrive/3_rscripts/99_UtilityFunctions.R

@@ -1,63 +1,0 @@
-
-## Function to plot quantity by month
-fn_plot1gp <- function(data, pracid) {
-  
-  ## Select codes and timeframe
-  tmpdata <- data %>%
-    filter(PracticeID == pracid) %>%
-    group_by(bnfchem,chemname,month2) %>%
-    dplyr::summarise(sumq = sum(Quantity)) 
-  
-  ##
-  tmpdata %>%
-    ggplot() + 
-    geom_line(aes(x=month2, y=sumq, color=chemname)) + 
-    annotate("rect", xmin=99, xmax=101, ymin=min(tmpdata$sumq), ymax=max(tmpdata$sumq), alpha=0.2, fill="red") +
-    xlab("Month") + 
-    ylab("Sum Quantities (monthly)") +
-    scale_x_continuous(breaks = c(50:102)[seq(1,53,by=2)],
-                       labels = months$datename[seq(1,53,by=2)]) + 
-    ggtitle(pracid) +
-    scale_y_continuous(labels = scales::comma) +
-    scale_color_discrete(name = "Chemical Name") +
-    theme_classic() +
-    theme(legend.position = "right",
-      axis.text.x = element_text(size=10, angle=90, hjust=1, vjust=0.5),
-          axis.text.y = element_text(size=10),
-          legend.text = element_text(size=10),
-          legend.title = element_text(size=10),
-          axis.title = element_text(size=10))
-}
-
-
-## Function to plot quantity by month
-fn_plotbnf <- function(data, title) {
-  
-  ## Select codes and timeframe
-  tmpdata <- data %>%
-    filter(month2 > startmonth) %>%
-    group_by(bnfchem,month2) %>%
-    dplyr::summarise(sumq = sum(Items),
-                     chemname = first(chemname)) 
-  ##
-  tmpdata %>%
-    #filter(sumq>100000) %>%
-    ggplot() + 
-    geom_line(aes(x=month2, y=sumq, color=chemname)) + 
-    annotate("rect", xmin=99, xmax=101, ymin=0, ymax=max(tmpdata$sumq), alpha=0.1, fill="red") +
-    #annotate("rect", xmin=99, xmax=101, ymin=min(tmpdata$sumq), ymax=max(tmpdata$sumq), alpha=0.1, fill="red") +
-    xlab("Month") + ylab("Sum Items (monthly)") +expand_limits( y = 0) +
[…]

### 2021-04-01 r_notebooks/preparing_differences/preparing_differences_template.Rmd
Change to "mapping" across data files to create difference files

---
title: "`r paste(params$drug, params$iteration)`"
params: 
  data: data
  drug: drug
  practices: practices
  iteration: iteration
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, setup, message=FALSE}
## Packages
# devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(fable)
library(feasts)
library(fasster)
library(furrr)
library(rebus)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = FALSE)
options(mc.cores = parallel::detectCores() - 1)

## Seed
set.seed(32)

## Params

drug <- params$data %>%
    str_remove_all("data/prescribing_data/") %>%
    str_remove_all(".rds")
practices <- unlist(params$practices)
data <- params$data

```

## Preparing data

```{r gp-data, message=FALSE}
gp <- 
  read_rds("data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat) %>% 
  filter(practice_id %in% practices)

```

```{r, prescribing-data, message=FALSE}
message(paste0("../../", data))

prescribing <- 
  read_rds(paste0("../../", data)) %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as.character(practice_id)) %>% 
  filter(practice_id %in% practices)

## Monthly summary by GP
prescribing_monthly_quantity_gp <- 
  countRegional(prescribing, practice_id, datename, quantity) %>% 
  mutate(year = year(datename)) %>%
  as_tibble() %>% 
  inner_join(gp, 
            by = c("regional_unit" = "practice_id", "year")) %>% 
  mutate(n = 1000*n/npat,
         datename = yearmonth(datename),
         regional_unit = as_factor(regional_unit)) %>% 
  select(-c(npat, year)) %>% 
  as_tsibble(index = datename, key = regional_unit) %>% 
  fill_gaps()

## Identify GPs with missing data 
months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
            "2015 Jul","2015 Aug","2015 Sep","2015 Oct","2015 Nov","2015 Dec",
            "2016 Jan","2016 Feb","2016 Mar","2016 Apr","2016 May","2016 Jun",
            "2016 Jul","2016 Aug","2016 Sep","2016 Oct","2016 Nov","2016 Dec",
            "2017 Jan","2017 Feb","2017 Mar","2017 Apr","2017 May","2017 Jun",
            "2017 Jul","2017 Aug","2017 Sep","2017 Oct","2017 Nov","2017 Dec",
            "2018 Jan","2018 Feb","2018 Mar","2018 Apr","2018 May","2018 Jun",
            "2018 Jul","2018 Aug","2018 Sep","2018 Oct","2018 Nov","2018 Dec",
            "2019 Jan","2019 Feb","2019 Mar","2019 Apr","2019 May","2019 Jun",
            "2019 Jul","2019 Aug","2019 Sep","2019 Oct","2019 Nov","2019 Dec",
            "2020 Jan","2020 Feb","2020 Mar","2020 Apr","2020 May","2020 Jun",
            "2020 Jul","2020 Aug")

gp_missing <- 
  prescribing_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  select(all_of(months), everything()) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
            miss_covid = sum(c_across(`2020 Jan`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

gp_miss_remove <- 
  gp_missing %>% 
  filter(miss_covid > 0 | miss_10_non_covid == TRUE) %>% 
  .$regional_unit

## Remove GPs with missing data in covid months and >10% of non-covid months
prescribing_monthly_quantity_gp <- 
  prescribing_monthly_quantity_gp %>% 
  filter(!regional_unit %in% gp_miss_remove) %>% 
  group_by(regional_unit)

## Sort into monthly count data pre-lockdown (March 2020) as training data

prescribing_monthly_quantity_gp_pre_cv19 <- 
  prescribing_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  group_by(regional_unit)

```

```{r}
if (sum(is.na(prescribing_monthly_quantity_gp_pre_cv19$n) > 0)) {
  ## Replace missing values in training data
  prescribing_monthly_quantity_gp_pre_cv19 <- 
    prescribing_monthly_quantity_gp_pre_cv19 %>% 
    model(arima = ARIMA(log(n))) %>% 
    interpolate(prescribing_monthly_quantity_gp_pre_cv19)
}
```

```{r}
gp_missing %>% 
  knitr::kable()
```

* `r length(gp_miss_remove)` GPs removed as they had missing data in the COVID months (Mar-Aug 2020) or >10% missing data pre-covid

## Modelling

```{r, prescribing-gp-practice-modelling}
plan(cluster)

if(str_detect(drug, "oac")){
system.time(prescribing_gp_cv_models <-
  prescribing_monthly_quantity_gp_pre_cv19 %>%
                  regionalCVBound(cv_dist = 8, init = 36, step = 3))  
} else {
system.time(prescribing_gp_cv_models <-
  prescribing_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(cv_dist = 8, init = 36, step = 3))
}

plan(sequential)
```

```{r}
if (file.exists(paste0("../../data/gp_cv_models", drug, "_gp_cv_models.rds"))) {
  read_rds(paste0("../../data/gp_cv_models", drug, "_gp_cv_models.rds")) %>% 
    bind_rows(prescribing_gp_cv_models) %>% 
    saveRDS(paste0("../../data/gp_cv_models", drug, "_gp_cv_models.rds"))
} else {
  prescribing_gp_cv_models %>%
    saveRDS(paste0("../../data/gp_cv_models", drug, "_gp_cv_models.rds"))
}
```

```{r prescribing-gp-modelling-accuracy}
best_model_gp <- 
  prescribing_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model_gp %>% 
  filter(MAPE > 50)

```

* `r nrow(best_mape_over_50)` GPs excluded as MAPE >50%

```{r prescribing-gp-practice-forecasts}
plan(cluster)

if(str_detect(drug, "oac")){
system.time(prescribing_gp_fcsts <-
              prescribing_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcstsBound())  
} else {
system.time(prescribing_gp_fcsts <-
              prescribing_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts())
}

plan(sequential)

if (file.exists(paste0("../../data/gp_forecasts", drug, "_gp_fcsts.rds"))) {
  read_rds(paste0("../../data/gp_forecasts", drug, "_gp_fcsts.rds")) %>% 
    bind_rows(prescribing_gp_cv_models) %>% 
    saveRDS(paste0("../../data/gp_forecasts", drug, "_gp_fcsts.rds"))
} else {
  prescribing_gp_cv_models %>%
    saveRDS(paste0("../../data/gp_forecasts", drug, "_gp_fcsts.rds"))
}
```

## Discrepancies

```{r, prescribing-gp-practice-discrepancies}
best_model_gp <- 
  prescribing_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

best_model_gp_discrep <- 
  best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(prescribing_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(prescribing_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - med, # observed - forecast
         prop = n / med) %>% 
  ungroup()

gp %>% 
    filter(practice_id %in% 
           (best_model_gp_discrep %>% 
           filter(prop <.25) %>% 
           .$regional_unit %>% 
           unique()))

if (file.exists(paste0("../../data/differences/", drug, "_discreps.rds"))) {
  read_rds(paste0("../../data/differences/", drug, "_discreps.rds")) %>% 
    bind_rows(best_model_gp_discrep) %>% 
    saveRDS(paste0("../../data/differences/", drug, "_discreps.rds"))
} else {
  best_model_gp_discrep %>%
    saveRDS(paste0("../../data/differences/", drug, "_discreps.rds"))
}
```

### 2021-04-01 r_scripts/run_all_preparing_diffs.R

@@ -1,8 +1,0 @@
-library(tidyverse)
-library(rmarkdown)
-
-rmd_files <- list.files("r_notebooks/preparing_differences")[grep(".Rmd", list.files("r_notebooks/preparing_differences"))]
-
-map(.x = rmd_files,
-    .f = ~render(paste0("r_notebooks/preparing_differences/", .x)))
-

### 2021-04-01 r_scripts/run_chunked_preparing_diffs.R

@@ -1,0 +1,48 @@
+library(tidyverse)
+library(rmarkdown)
+
+### Data
+
+# Prescribing
+data_files <-
+  paste0("data/prescribing_data/", list.files("data/prescribing_data"))
+
+
+# GP practice
+gp <-
+  read_rds("OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>%
+  mutate(practice_id = as_factor(practiceid)) %>%
+  ungroup() %>%
+  janitor::clean_names() %>%
+  select(practice_id, year)
+
+
+# GP practice chunks of <= 20
+unique_gp_ids <- as.character(unique(gp$practice_id))
+
+split_gp_ids <-
+  split(unique_gp_ids, ceiling(seq_along(unique_gp_ids) / 20)) %>% # Reduce this number if RAM requirements are too high
+  map(unlist)
+
+### Functions
+
+render_files <- function(data){
+  drug <- data %>%
+    str_remove_all("data/prescribing_data/") %>%
+    str_remove_all(".rds")
+
+    map(.x = 1:length(split_gp_ids),
+        .f = ~rmarkdown::render(input = "r_notebooks/preparing_differences/preparing_differences_template.Rmd",
+                                output_file = paste0(drug, "_", .x, ".html"),
+                                params =  list(data = data,
+                                               drug = drug,
+                                               practices = split_gp_ids[.x],
+                                               iteration = .x)))}
+
+
+### Map across combination of drugs and practices
+
+# Dan
+map(.x = data_files[3],
+    .f = ~render_files(data = .x))
+

### 2021-05-22 writing/paper.Rmd
Change from sample_bound to composite_sd

@@
 author: 
-  - name          : "First Author"
-    affiliation   : "1"
+  - name          : "Will Hardy"
+    affiliation   : "1,2"
     corresponding : yes    # Define only one corresponding author
@@
     email         : "my@email.com"
-  - name          : "Second Author"
-    affiliation   : "1,2"
+  - name          : "Susan Murphy"
+    affiliation   : "3"
+  - name          : "Dyfrig Hughes"
+    affiliation   : "1"
+  - name          : "Daniel Hill-McManus"
+    affiliation   : "1"
 
@@
     institution   : "Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ"
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  - id            : "3"
+    institution   : "Betsi Cadwaladr University Health Board"
 
@@
 
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
+header-includes:
+   - \usepackage{caption}
+csl               : "../references/apa.csl"
+always_allow_html : true
+output            : 
+  - html_document
 
-csl               : "../references/apa.csl"
-documentclass     : "apa7"
-classoption       : "man"
-output            : 
-  - papaja::apa6_pdf
-  - papaja::apa6_docx
 ---
@@
 ## Packages
-devtools::install_github("https://github.com/w-hardy/serCymruTools")
+# devtools::install_github("https://github.com/w-hardy/serCymruTools")
 library(tidyverse)
@@
 library(serCymruTools)
+library(knitr)
+library(kableExtra)
+library(geepack)
 library(papaja)
@@
 ## Data
+gp <- 
+  read_rds("../data/gp_agesex_qof_combined.rds") %>% 
+  mutate(npat = N,
+         N = NULL,
+         practice_id = as.character(practiceid)) %>% 
+  ungroup() %>% 
+  janitor::clean_names() %>% 
+  select(practice_id, year, npat)
+
+# CV model accuracies
+cv_model_files <- 
+  paste0("../data/gp_cv_models/", 
+         list.files("../data/gp_cv_models/"))
+names(cv_model_files) <- 
+  cv_model_files %>% 
+  str_remove_all("../data/gp_cv_models/") %>% 
+  str_remove_all("_gp_cv_models.rds")
+
+# Forecast - observed
 differences_files <- 
@@
           .id = "drug") %>% 
-  mutate(drug = as_factor(drug)) %>% 
-  select(drug, regional_unit, datename, discrepancy, med)
+  mutate(drug = relevel(as_factor(drug), ref = "all_drugs"),
+         sd = sd^.25)
 
-all_prescribing <- 
-  read_csv("../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
-  mutate(datename = dmy(paste(28, datename, sep = "-")),
-         datename = yearmonth(datename),
-         regional_unit = factor("all")) %>% 
-  as_tsibble(index = datename) %>% 
-  filter(datename < yearmonth(dmy("01-09-2020")))
+# GP extract data
+data_files <-
+  paste0("../data/prescribing_data/", list.files("../data/prescribing_data")) 
+names(data_files) <- 
+  str_remove_all(list.files("../data/prescribing_data"), ".rds")
 
-all_prescribing_pre_cv19 <- 
-  all_prescribing %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
-
+gp_extract <- 
+  map_dfr(.x = data_files,
+          .f = ~(read_rds(.x) %>% 
+            filter(practice_id %in% unique(differences$regional_unit))),
+          .id = "drug") 
 ```
 
-```{r analysis-preferences}
+```{r, analysis-preferences}
 # Seed for random number generation
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
+kable_opts <- options(knitr.kable.NA = "-")
 ```
+
+# Introduction
 
@@
 
-* Sources of data
-  * GP
-  * Prescribing
-  * QOF
-  * WIMD
-* Preparing
+```{r, figure-1, fig.cap="Data processing flow."}
+include_graphics("figures/data_flow.pdf")
+```
 
-## Identifying changes in prescribing due to COVID-19
-
-Identifying the effects of COVID-19 is not simple, as its effects are unprecedented and its global impact prevents us from adopting a traditional treatment and control group type design.
-Instead, we have used time series analysis methods to create counterfactual forecasts
-
-To understand the changes in levels of prescribing due to COVID-19, it was first necessary for us to forecast the levels of prescribing had COVID-19 not affected Wales as a baseline.
-To do so, we used historic data (January 2015 to December 2020) to identify from a range of time series models, one that was good fit to the data.
-This was done using cross-validation to reduce the likelihood of choosing a model that was overfitted to the data.
-
-* Given the presence of seasonal variation and existing trends in levels of prescribing, we used various time series forecasting methods to account for existing trends and seasonal variation when creating the forecasts.
-* For each analysis, we created a forecast that aimed to answer the question, "What would the levels of prescribing have been if COVID-19 had not affected Wales?" We then used these forecasts to estimate the changes in levels of prescribing due to COVID-19.
-* We viewed this, somewhat complex, approach as superior to more simple approaches (e.g., carrying last years levels forward, or even using the mean of the last three years).
-
-### Forecasting models
-
-* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
-* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
-  * Time series linear model
-  * Decomposition model
-  * Seasonal naïve (with and without drift)
-  * Autoregressive integrated moving average [ARIMA; @Box2015]
-  * Holt-Winters Additive Model [@Chatfield1978]
-  * Prophet [@Taylor2018]
-  * Combination models [cf. @Thomson2019]
-* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
-* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
-  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
-    * Only interested in one forecast horizon: six-months
-
-### Model selection
-
-* Ranked by RMSE and Winkler [@Winkler1972], then the best mean ranking model is chosen
-  * RMSE is scale dependant. Is suitable for comparing models of the same data.
-  * Winkler score penalises models that have observations falling outside the prediction interval, thus rewards models with narrow intervals
-* This combination accounts for both the point and distributional accuracy of the forecasts
-
-### Forecasts
-
-* Having chosen the "best model" for each practice based on the pre-COVID data, we then used this model to forecast the level of prescribing for each practice
-
-## Reproducability and code
-
-We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.
+```{r, table-2}
+read_rds("../data/gp_agesex_qof_combined.rds") %>% 
+  mutate(npat = N,
+         N = NULL,
+         practice_id = as.character(practiceid)) %>% 
+  ungroup() %>% 
+  janitor::clean_names() %>%  
+  filter(year == 2020) %>% 
+  select(npat, ngp, dispensing, wimd2019:flu) %>% 
+  mutate(across(p_male:flu, ~.x*100)) %>% 
+  psych::describe() %>% 
+  select(mean, sd, median, min, max) %>% 
+  kable(digits = 2)
+```
 
@@
 
-## Counterfactual forecasts
+```{r, figure-2, fig.cap="Distribution of the difference between observed and forecast prescribing, expressed as a percentage of forecast prescribing.
+Grey line marks forecast level of prescribing.
+Pink shading covers duration of Wales' \"stay at home\" order.
+Please note the difference y-axis scales across the plots.", dpi=450}
+differences_quantiles <- 
+  differences %>% 
+  na.omit() %>% 
+  group_by(datename, drug) %>% 
+  summarise(mean_prop = mean(prop, na.rm = T),
+            med_prop = median(prop, na.rm = T),
+            sd_prop = sd(prop, na.rm = T),
+            se_prop = sd(prop, na.rm = T)/sqrt(length(prop)),
+            enframe(quantile(prop, seq(.1,.9,.2)), 
+                    "Percentile", "prop"),
+            .groups = "drop") %>% 
+  mutate(datename = month(datename),
+         prop = 100*(prop - 1)) # Percentage change instead of proportion
 
-### All prescribing
+differences_quantiles %>%
+  mutate(datename = factor(x = datename, levels = 1:8, 
+                           labels = month.abb[1:8])) %>% 
+  mutate(drug = case_when(drug == "all_drugs" ~ "All",
+                          drug == "ace" ~ "ACE inhibitors",
+                          drug == "adreno" ~ "Adrenoceptor agonists",
+                          drug == "azithro" ~ "Azithromycin",
+                          drug == "contra" ~ "Oral contraceptives",
+                          drug == "cortico" ~ "Corticosteroids",
+                          drug == "hcq" ~ "Hydroxycholoroquine",
+                          drug == "nsaid" ~ "NSAIDs",
+                          drug == "paracet" ~ "Paracetamol",
+                          drug == "ssri" ~ "SSRIs",
+                          drug == "vitd" ~ "Vitamin D",
+                          drug == "warfarin" ~ "Warfarin"),
+         drug = relevel(as_factor(drug), ref = "All")) %>%
+  ggplot(aes(x = datename, col = drug, 
+             group = Percentile)) +
+  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
+            fill = 'pink', col = 0,alpha = 0.03) +
+  geom_line(aes(y = prop, lty = Percentile)) +
+  geom_hline(aes(yintercept = 0), alpha = .5) +
+  facet_wrap(~drug, scales = "free") + 
+  guides(size = "legend", colour = "none") + 
+  theme(legend.position = "bottom", text = element_text(size = 10)) +
+  scale_linetype_manual(breaks = c("10%", "30%", "50%"), # Remove 70% and 90% from legend
+                        values = c(3,2,1,2,3), # Replicate line type
+                        labels = c("10% lower; 90% upper", # Amalgamate line type labels
+                                   "30% lower; 70% uppper", "50%")) +
+  xlab("Month") +
+  ylab("Percentage difference from forecast prescribing")
 
-```{r all-prescribing-modelling, warning=FALSE}
-plan(cluster)
-
-all_prescribing_fable_models <- 
-  all_prescribing_pre_cv19 %>% 
-  mutate(datename = yearmonth(datename)) %>%
-  fill_gaps() %>%
-  slice(1:(n()-2), .preserve = TRUE) %>%
-  stretch_tsibble(.init = 36, .step = 3) %>%
-  fableModels()
-
-all_prescribing_fable_forecasts <- 
-  all_prescribing_fable_models %>%
-  forecast(h = 6, point_forecast = list(.median = median))
-
-all_prescribing_fable_fits <- 
-  all_prescribing_fable_forecasts %>% 
-  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
-                           rmse_skill = skill_score(RMSE),
-                           crps_skill = skill_score(CRPS), ACF1 = ACF1,
-                           winkler = winkler_score))
-
-all_prescribing_prophet_fits <- 
-  all_prescribing_pre_cv19 %>%
-  mutate(datename = yearmonth(datename)) %>%
-  fill_gaps() %>%
-  slice(1:(n()-2), .preserve = TRUE) %>%
-  stretch_tsibble(.init = 36, .step = 3) %>%
-  prophetModels() %>%
-  forecast(h = 6, point_forecast = list(.median = median)) %>%
-  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
-                           rmse_skill = skill_score(RMSE),
-                           crps_skill = skill_score(CRPS), ACF1 = ACF1,
-                           winkler = winkler_score))
-
-all_prescribing_combined_fits <- 
-  bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
-  rankModels()
-
-all_prescribing_best_model <- 
-  all_prescribing_combined_fits %>% 
-  slice(1, .preserve = TRUE)
-
-all_prescribing_covid_forecast <- 
-  bind_rows(fableModels(all_prescribing_pre_cv19) %>% 
-            forecast(h = "6 months"),
-          prophetModels(all_prescribing_pre_cv19) %>% 
-            forecast(h = "6 months")) %>% 
-  as_tibble() %>% 
-  filter(.model == all_prescribing_best_model$.model) %>% 
-  dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 0.1), 
-                med = median(n), ub_80 = quantile(n, 0.9), 
-                ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
-                n = NULL)
-
-plan(sequential)
+  ggsave(filename = "Draft 2/Figures/Figure 2.png", device = "png",
+         width = 10.5)
 
@@
 
-```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy"}
-p1 <- all_prescribing_combined_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, rank, sort), y = RMSE)) +
-  geom_col()
+```{r}
+avg <- function(samples){
+  if (length(samples) >= 1){
+    return(sum(samples) / length(samples))
+  }
+  else{return(NaN)}
+}
 
-p2 <- all_prescribing_combined_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, rank, sort), y = winkler)) +
-  geom_col()
+sample_SD <- function(samples){
+  # Input is an vector of samples; result is the standard deviation
+  mean = avg(samples)
+  sum_of_squared_deviations <-  0
+  sd <-  0
+  if(length(samples) >= 2){
+    for (datum in samples){
+      sum_of_squared_deviations <- 
+        sum_of_squared_deviations + ((datum - mean) * (datum - mean))
+      sd = sqrt(sum_of_squared_deviations / (length(samples)-1))
+    }
+      return(sd)
+  }
+}
 
-cowplot::plot_grid(p1, p2)
+set.seed(134)
+vec <- c(rnorm(n = 100), rnorm(n = 100))
+vec_sd <- sd(vec)
+sample_SD(vec)
+compositeSD()
+
+vec
+compositeSD <- function(means, SDs, ncounts){
+  #Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
+  # See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
+  #    Inputs are:
+  #      means, the array of group means
+  #      SDs, the array of group standard deviations
+  #      ncounts, number of samples in each group (can be scalar
+  #               if all groups have same number of samples)
+  #    Result is the overall standard deviation.
+  G <- length(means) # number of groups
+  if(G != length(SDs)) stop("Inconsistent lengths (means & sds")
+  if(!is.numeric(ncounts)) {(as.numeric(ncounts))}
+  if(G != length(ncounts)) stop("Inconsistent lengths (means & ncounts)")
+
+  # Calculate total number of samples, N, and grand mean, GM
+  N = sum(ncounts)  # total number of samples
+  if (N <= 1) stop(paste("Warning: only ", N, " samples, SD is incalculable"))
+  GM <-  0.0
+  for (i in 1:G){
+    GM <- GM + means[i] * ncounts[i]
+  }
+  GM <- GM / N  # grand mean
+
+  # calculate Error Sum of Squares
+  ESS <-  0.0
+  for (i in 1:G){
+    ESS <- ESS + ((SDs[i])**2) * (ncounts[i] - 1)
+  }
+
+  # calculate Total Group Sum of Squares
+  TGSS <-  0.0
+  for (i in 1:G){
+    TGSS <- TGSS + ((means[i]-GM)**2) * ncounts[i]
+  }
+
+  # calculate standard deviation as square root of grand variance
+  result <- sqrt((ESS+TGSS)/(N-1))
+  return(result)
+}
+
+samples = 0:9
+print(paste("avg =", avg(samples)))
+sd = sample_SD(samples)
+print(paste("sd =", sd))
+pt1 = c(0,1,2)
+pt2 = c(3,4)
+pt3 = c(5,6,7,8,9)
+means <- c(avg(pt1), avg(pt2), avg(pt3))
+SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
+ncounts <- c(length(pt1), length(pt2), length(pt3))
+sd2 <- compositeSD(means, SDs, ncounts)
+print(paste("sd2 =", sd2))
+
+samples = 0:8
+print(paste("avg =", avg(samples)))
+sd = sample_SD(samples)
+print(paste("sd =", sd))
+pt1 = c(0,1,2)
+pt2 = c(3,4,5)
+pt3 = c(6,7,8)
+means <- c(avg(pt1), avg(pt2), avg(pt3))
+SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
+ncounts <- c(length(pt1), length(pt2), length(pt3))
+sd2 <- compositeSD(means, SDs, ncounts)
+print(paste("sd2 =", sd2))
+
 ```
 
-```{r, all-prescribing-cv-plot, fig.cap="All prescribing, best model CV fit"}
-all_prescribing_best_cv_model <- 
-  augment(all_prescribing_fable_models) %>% 
-  as_tibble() %>% 
-  filter(.model == all_prescribing_best_model$.model)
+```{python}
 
-all_prescribing_best_cv_model %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = n/1e+06, colour = "Data")) +
-  geom_line(aes(y = .fitted/1e+06, colour = "Fitted", lty = as.factor(.id))) +
-  labs(lty = "CV iteration")
+from __future__ import print_function, division  # requires python 2.6 or later (2.7 or later preferred)
+import math
+
+__all__ = ['iterable', 'avg', 'sample_SD', 'composite_SD']
+
+def iterable(obj):
+    '''True iff obj is iterable: a list, tuple, or string.'''
+    return hasattr(obj, '__contains__')
+
+def avg(samples):
+    if len(samples) >= 1:
+        return sum(samples) / len(samples)
+    return float('nan')
+
+def sample_SD(samples):
+    '''input is an array of samples; result is the standard deviation'''
+    mean = avg(samples)
+    sum_of_squared_deviations = 0;
+    sd = 0
+    if len(samples) >= 2:
+        for datum in samples:
+            sum_of_squared_deviations += ((datum - mean) * (datum - mean));
+        sd = math.sqrt(sum_of_squared_deviations / (len(samples)-1) );
+    return sd
+
+def composite_SD(means, SDs, ncounts):
+    '''Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
+       See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
+       Inputs are:
+         means, the array of group means
+         SDs, the array of group standard deviations
+         ncounts, number of samples in each group (can be scalar
+                  if all groups have same number of samples)
+       Result is the overall standard deviation.
+    '''
+    G = len(means)  # number of groups
+    if G != len(SDs):
+        raise Exception('inconsistent list lengths')
+    if not iterable(ncounts):
+        ncounts = [ncounts] * G  # convert scalar ncounts to array
+    elif G != len(ncounts):
+        raise Exception('wrong ncounts list length')
+
+    # calculate total number of samples, N, and grand mean, GM
+    N = sum(ncounts)  # total number of samples
+    if N <= 1:
+        raise Exception("Warning: only " + str(N) + " samples, SD is incalculable")
+    GM = 0.0
+    for i in range(G):
+        GM += means[i] * ncounts[i]
+    GM /= N  # grand mean
+
+    # calculate Error Sum of Squares
+    ESS = 0.0
+    for i in range(G):
+        ESS += ((SDs[i])**2) * (ncounts[i] - 1)
+
+    # calculate Total Group Sum of Squares
+    TGSS = 0.0
+    for i in range(G):
+        TGSS += ((means[i]-GM)**2) * ncounts[i]
+
+    # calculate standard deviation as square root of grand variance
+    result = math.sqrt((ESS+TGSS)/(N-1))
+    return result
+
+samples = range(10)
+print(samples)
+print('avg=', avg(samples))
+sd = sample_SD(samples)
+print('sd=', sd)
+pt1 = [0,1,2]
+pt2 = [3,4]
+pt3 = [5,6,7,8,9]
+means = [avg(pt1), avg(pt2), avg(pt3)]
+SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
+ncounts = [len(pt1), len(pt2), len(pt3)]
+sd2 = composite_SD(means, SDs, ncounts)
+print('sd2=', sd2)
+
+samples = range(9)
+print('avg=', avg(samples))
+sd = sample_SD(samples)
+print('sd=', sd)
+pt1 = [0,1,2]
+pt2 = [3,4,5]
+pt3 = [6,7,8]
+means = [avg(pt1), avg(pt2), avg(pt3)]
+SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
+ncounts = 3
+sd2 = composite_SD(means, SDs, ncounts)
+print('sd2=', sd2)
 ```
 
-```{r, all-prescribing-forecast-plot, fig.cap="All prescribing, best model fit and forecast"}
-all_prescribing %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
-  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
-            data = all_prescribing_covid_forecast) +
-  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
-                   fill = "Forecast"), alpha = .5,
-              data = all_prescribing_covid_forecast) +
-  geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
-            data = all_prescribing_best_cv_model %>% 
-              group_by(datename) %>% 
-              summarise(fitted = median(.fitted, na.rm = TRUE))) +
-  geom_vline(xintercept = ymd("2020-03-01"), lty = 3)
+```{r, table-3-single-fcts}
+nat_data <- 
+  data_files %>% 
+  map_dfr(read_rds, .id = "drug") %>% 
+  group_by(drug, datename) %>% 
+  summarise(n = sum(quantity), .groups = "drop")
+
+plan(multisession)
+precribing_cv_models <- 
+  nat_data %>% 
+  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
+         regional_unit = as.factor(drug)) %>% 
+  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
+  as_tsibble(index = "datename", key = "regional_unit") %>% 
+  serCymruTools::regionalCV(cv_dist = 8, init = 36, step = 3)
+plan(sequential)
+
+precribing_cv_models
+
+best_model <- 
+  precribing_cv_models %>% 
+  group_by(regional_unit) %>% 
+  rankModels() %>% 
+  slice(1, .preserve = TRUE)
+
+best_mape_over_50 <- 
+  best_model %>% 
+  filter(MAPE > 50)
+
+plan(cluster)
+system.time(prescribing_fcsts <-
+                nat_data %>% 
+  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
+         regional_unit = as.factor(drug)) %>% 
+  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
+  as_tsibble(index = "datename", key = "regional_unit") %>%
+              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
+              regionalJointFcsts())  
+plan(sequential)
+
+best_model_discrep <- 
+  best_model %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(mutate(prescribing_fcsts,
+                    datename = yearmonth(datename)), 
+             by = c(".model", "regional_unit")) %>%
+  left_join(mutate(select(                nat_data %>% 
+  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
+         regional_unit = as.factor(drug)) , 
+                          c(regional_unit, datename, n)), 
+                   datename = yearmonth(datename)),
+            by = c("datename", "regional_unit")) %>% 
+  mutate(discrepancy = n - med, # observed - forecast
+         prop = n / med) %>% 
+  ungroup()
+
+best_model_discrep %>% 
+  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
+  summarise(n = sum(n),
+            sd = compositeSD(.mean, sd, rep(1,nrow(.))),
+            .mean = sum(.mean)
+  )
+
+best_model_discrep %>% 
+  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
+  group_by(regional_unit) %>% 
+  summarise(n = sum(n),
+            sd = compositeSD(.mean, sd, rep(1,5)),
+            .mean = sum(.mean),
+            ) %>% 
+  mutate(lb = .mean - 1.96*sd,
+         ub = .mean + 1.96*sd,
+         lb_mean_pct_change = (100 * (n - ub)/ ub),
+         mean_pct_change = (100 * (n - .mean)/ .mean),
+         ub_mean_pct_change = (100 * (n - lb)/ lb),
+         ) %>% 
+  select(regional_unit, lb_mean_pct_change, mean_pct_change, ub_mean_pct_change)
+  ggplot(aes(x = regional_unit, y = mean_pct_change)) +
+  geom_col() +
+  geom_errorbar(aes(ymin = lb_mean_pct_change, ymax = ub_mean_pct_change))
 ```
 
-```{r, all-prescribing-pct-change-plot, fig.cap="Percentage difference in all prescribing"}
-all_prescribing %>% 
-  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
-  ggplot(aes(x = datename, y = (100*n/med)-100)) +
-  geom_line() +
-  geom_hline(yintercept = 0, lty = 3)
+```{r, table-3}
+# https://stats.stackexchange.com/questions/454120/how-can-i-calculate-uncertainty-of-the-mean-of-a-set-of-samples-with-different-u
+
+#
+# An iterative procedure to estimate mean and variance from a set of 
+# measurements `x` made with known measurement errors `sigma.i`.
+#
+var.wt <- function(x, sigma.i, thresh=1e-6, iter.max=1e4) { # Changed from values in example (1e-6, 200)
+  #
+  # To avoid giving undue weight to any subset, all SDs should be nonzero.
+  #
+  if (missing(sigma.i)) sigma.i <- rep(0, length(x)) # No measurement error
+  tol <- sum(abs(x)) * 1e-16
+  sigma.i[sigma.i <= 0] <- min(c(tol, sigma.i[sigma.i > 0])) / 2
+  #
+  # Initialize.
+  #
+  v <- var(x)
+  n <- length(x)
+  S <- mean(sigma.i^2) # Avoids recomputing this constant within the loop
+  for (i in 1:iter.max) {
+    w <- 1/(v + sigma.i^2); w <- w / sum(w)
+    m <- sum(x * w)
+    v.0 <- max(0, sum((x-m)^2 * w) * n / (n-1) - S) 
+    if (v <= v.0 * (1+thresh) && v.0 <= v * (1+thresh)) break
+    v <- v.0
+  }
+  if (i >= iter.max) warning("Maximum iteration count exceeded.")
+  list(Variance=v, Mean=m, Iterations=i)
+}
+
+sample_bound <- function(mean = ".mean", variance = "sd", 
+                         bound = c(.975, .5, .025), data = .){
+
+  # The data in the question.
+  #
+  x <- data[[mean]]
+  sigma.i <- data[[variance]]
+  (s <- var.wt(x, sigma.i))
+  #
+  # A parametric bootstrap.
+  #
+  n <- length(x)
+  sigma <- sqrt(s$Variance)
+  mu <- s$Mean
+  set.seed(17)
+  X <- replicate(5e3, {
+    y <- rnorm(n, mu, sigma)
+    epsilon <- rnorm(n, 0, sigma.i)
+    x <- y + epsilon
+    var.wt(x, sigma.i)
+  })
+  X <- matrix(unlist(X), 3)
+
+  return(quantile(X[2,], bound))
+}
+
+monthly_diffs <- 
+  differences %>% 
+  select(drug, datename, .mean, sd, n) %>% 
+  na.omit() %>% 
+  group_by(drug, datename) %>% 
+  group_modify(~ {
+    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
+      tibble::enframe(name = "bound", value = "value")
+  }) %>% 
+  left_join(differences %>% 
+              select(drug, datename, .mean, sd, n) %>% 
+              na.omit() %>% 
+              group_by(drug, datename) %>% 
+              summarise(n = mean(n, na.rm = TRUE),
+                        .mean = mean(.mean, na.rm = TRUE),
+                        .group = "drop"), 
+            by = c("drug", "datename")) %>% 
+  mutate(p_change = 100*n / value) %>% # Difference as a proportion
+  pivot_wider(id_cols = c("drug", "datename", "n", ".mean"), 
+              names_from = "bound", values_from ="value") %>% 
+  mutate(across(`97.5%`:`2.5%`, .fns = ~(100*n/.x)-100)) %>% # Proportion as percentage change
+  rename("LB" = `97.5%`,
+         "Mean" = `50%`,
+         "UB" = `2.5%`) %>% 
+  mutate(datename = month(datename),
+         pct_change = paste0(printnum(Mean), 
+                             "[", printnum(LB), ",", printnum(UB), "]"))
+
+lockdown_diff_bounds <- 
+  differences %>% 
+  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
+  select(drug, datename, .mean, sd, n) %>% 
+  na.omit() %>% 
+  group_by(drug) %>% 
+  group_modify(~ {
+    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
+      tibble::enframe(name = "bound", value = "value")
+  })
+
+lockdown_diff_bounds_wide <- 
+  lockdown_diff_bounds %>% 
+  pivot_wider(id_cols = "drug", names_from = "bound", values_from = "value") %>% 
+  rename("lb" = `97.5%`,
+         "mean" = `50%`,
+         "ub" = `2.5%`) # returns mean quantity forecast per month in lockdown
+
+lockdown_diff_obs <- 
+  differences %>% 
+  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
+  select(drug, datename, .mean, sd, n, med) %>% 
+  na.omit() %>% 
+  group_by(drug) %>% 
+  summarise(n = mean(n, na.rm = FALSE),
+            .mean = mean(.mean, na.rm = FALSE),
+            med_med = median(med),
+            mean_med = mean(med),
+            .groups = "drop")
+
+left_join(lockdown_diff_obs, lockdown_diff_bounds_wide) %>% 
+  mutate(across(.mean:ub, ~(n-.x)/.x))
+
+###
+lockdown_diffs <- 
+  differences %>% 
+  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
+  select(drug, datename, .mean, sd, n) %>% 
+  na.omit() %>% 
+  group_by(drug) %>% 
+  group_modify(~ {
+    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
+      tibble::enframe(name = "bound", value = "value")
+  }) %>% 
+  left_join(differences %>% 
+              filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
+              select(drug, datename, .mean, sd, n) %>% 
+              na.omit() %>% 
+              group_by(drug) %>% 
+              summarise(n = mean(n, na.rm = TRUE),
+                        .mean = mean(.mean, na.rm = TRUE),
+                        .groups = "drop"), 
+            by = c("drug")) %>% 
+  mutate(p_change = 100 * n / value) %>% # Difference as a proportion
+  pivot_wider(id_cols = c("drug", "n", ".mean"), 
+              names_from = "bound", values_from ="value") %>% 
+  mutate(across(`97.5%`:`2.5%`, .fns = ~(100*n/.x)-100)) %>% # Proportion as percentage change
+  rename("LB" = `97.5%`,
+         "Mean" = `50%`,
+         "UB" = `2.5%`) %>% 
+    mutate(lockdown = paste0(printnum(Mean), 
+                             "[", printnum(LB), ",", printnum(UB), "]"))
+
+lockdown_diffs %>% 
+  select(drug, lockdown) %>% 
+  left_join(monthly_diffs %>% 
+              pivot_wider(id_cols = "drug", names_from = "datename", 
+                          values_from = "pct_change"), by = "drug") %>% 
+  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
+        align = "lrrrrrrrrr",
+        booktabs = TRUE,
+        caption = "Monthly percentage change in prescribing") %>% 
+  add_header_above(header = c(" " = 1, 
+                              "Mean percentage change [95% CI]" = 9)) %>% 
+  landscape()
 ```
 
-### Specific drugs
+```{r}
+differences %>% 
+  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
+  group_by(drug) %>% 
+  summarise(n = sum(n),
+            .mean = sum(.mean)) %>% 
+  mutate(pct_change = 100 * (n - .mean ) / .mean)
+```
+
+```{r, eval=FALSE}
+differences %>% 
+  select(drug, datename, .mean, sd, n) %>% 
+  na.omit() %>% 
+  group_by(drug) %>% 
+  summarise(across(where(is.numeric),.fns = max))
+```
+
+```{r}
+gp_extract %>% 
+  filter(str_detect(datename, "-19")) %>% 
+  group_by(drug) %>% 
+  summarise(n = sum(quantity)/1e6) %>% 
+  left_join(lockdown_diffs %>% 
+  select(drug, lockdown), by = "drug")
+```
+
+```{r, mean-change-plot}
+monthly_diffs %>% 
+  ggplot(aes(x = datename, group = drug)) +
+  geom_line(aes(y = Mean)) +
+  geom_ribbon(aes(ymin = LB, ymax = UB, fill = drug), alpha = .4) +
+  facet_wrap(~drug, scales = "free")
+
+```
+
+```{r}
+differences %>% 
+  group_by(drug) %>% 
+  summarise(discrepancy = sum(discrepancy, na.rm = TRUE),
+            n = sum(n, na.rm = TRUE),
+            pct = 100*discrepancy / n)
+
+differences %>% 
+  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
+  group_by(drug) %>% 
+  summarise(discrepancy = sum(discrepancy, na.rm = TRUE),
+            n = sum(n, na.rm = TRUE),
+            pct = 100*discrepancy / n) %>% 
+  ggplot(aes(x = reorder(drug, pct), y = pct)) +
+  geom_col()
+```
 
@@
 \endgroup
+
+\newpage
+
+<div custom-style='Title'>Appendix </div>
+
+\renewcommand{\appendixname}{Supplementary Material}
+\renewcommand{\thefigure}{SI\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{SI\arabic{table}} \setcounter{table}{0}
+\renewcommand{\theequation}{SI\arabic{table}} \setcounter{equation}{0}
+
+# Forecasting
+
+### Forecasting models
+
+* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
+* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
+  * Simple methods
+      * Naïve (with and without drift)
+        * $\hat{y}_{T+h|T} = y_T$
+      * Seasonal naïve (with and without drift)
+        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where m = seasonal period and k is the complete years in $T+h$
+  * STL Decomposition model [@Cleveland1990]
+    * Fixed and variable seasonality
+  * Time series linear model
+    * $y_t = \beta_0 + \beta_1x_t + \varepsilon_t$
+  * Autoregressive integrated moving average [ARIMA; @Box2015]
+    * Using a version of the Hyndman-Khandakar algorithm [@Hyndman2008]
+  * Exponential smoothing [@Holt2004; @Winters1960]
+    * Simple exponential smoothing
+    * Holt-Winters Additive Model [@Chatfield1978]
+  * Forecasting with Additive Switching of Seasonality, Trends and Exogenous Regressors [fasster; @R-fasster]
+    * State space model
+  * Prophet [@Taylor2018]
+  * Combination models [cf. @Bates1969; @Clemen1989; @Thomson2019]
+* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
+* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
+  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to keep run-times manageable)
+    * Only interested in one forecast horizon: six-months
+
+## All prescribing
+
+```{r, all-prescribing-model-accuracy-hist1, fig.cap="All prescribing, model accuracy", eval=FALSE}
+p1 <- all_prescribing_fable_fits %>% 
+  na.omit() %>% 
+  ggplot(aes(x = reorder(.model, RMSE, sort), y = RMSE)) +
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 90))
+
+p2 <- all_prescribing_fable_fits %>% 
+  na.omit() %>% 
+  ggplot(aes(x = reorder(.model, winkler, sort), y = winkler)) +
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 90))
+
+cowplot::plot_grid(p1, p2)
+```
+
+```{r, all-prescribing-cv-plot, fig.cap="All prescribing, best model CV fit", eval=FALSE}
+all_prescribing_best_cv_model <- 
+  augment(all_prescribing_fable_models) %>% 
+  as_tibble() %>% 
+  filter(.model == all_prescribing_best_model$.model)
+
+all_prescribing_best_cv_model %>% 
+  ggplot(aes(x = datename)) +
+  geom_line(aes(y = n/1e+06, colour = "Data")) +
+  geom_line(aes(y = .fitted/1e+06, colour = "Fitted", lty = as.factor(.id))) +
+  labs(lty = "CV iteration")
+```
+
+```{r, all-prescribing-forecast-plot, warning=FALSE, fig.cap="All prescribing, best model fit and forecast.", eval=FALSE}
+plan(cluster)
+all_prescribing %>% 
+  ggplot(aes(x = datename)) +
+  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
+  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
+            data = all_prescribing_covid_forecast) +
+  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
+                  fill = "Forecast"), alpha = .2,
+              data = all_prescribing_covid_forecast) +
+  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, 
+                  fill = "Forecast"), alpha = .3,
+              data = all_prescribing_covid_forecast) +
+  # geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
+  #           data = fableModels(all_prescribing_pre_cv19) %>% 
+  #             augment() %>% 
+  #             as_tibble() %>% 
+  #             filter(.model == all_prescribing_best_model$.model) %>% 
+  #             group_by(datename) %>% 
+  #             summarise(fitted = median(.fitted, na.rm = TRUE))) +
+  geom_vline(xintercept = ymd("2020-03-01"), lty = 3) +
+  coord_cartesian(xlim = c(dmy("01-11-2018"), dmy("01-08-2020"))) +
+  scale_x_yearmonth(breaks = "6 months", minor_breaks = "1 months")+
+  xlab("Date") +
+  ylab("Mean daily prescribing volume")
+
+plan(sequential)
+```
+
+```{r, all-prescribing-pct-change-plot, fig.cap="Percentage difference in all prescribing.", eval=FALSE}
+all_prescribing %>% 
+  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
+  ggplot(aes(x = datename, y = (100*n/med)-100)) +
+  geom_line() +
+  geom_hline(yintercept = 0, lty = 3)
+```
+
+## Excluded practices
+
+Table with a row for each drug and a column for each reason a practice could be excluded, with a total column at the end
+
+(a) missing any data in the COVID months, (b) more than 10% of the pre-COVID data (i.e., 6 months) missing, (c) significant changes to prescribing in the six months pre-COVID (e.g., changes that suggested the practice had closed), or (d) MAPE >50.
+
+```{r, excluded-practices-tab}
+months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
+            "2015 Jul","2015 Aug","2015 Sep","2015 Oct","2015 Nov","2015 Dec",
+            "2016 Jan","2016 Feb","2016 Mar","2016 Apr","2016 May","2016 Jun",
+            "2016 Jul","2016 Aug","2016 Sep","2016 Oct","2016 Nov","2016 Dec",
+            "2017 Jan","2017 Feb","2017 Mar","2017 Apr","2017 May","2017 Jun",
+            "2017 Jul","2017 Aug","2017 Sep","2017 Oct","2017 Nov","2017 Dec",
+            "2018 Jan","2018 Feb","2018 Mar","2018 Apr","2018 May","2018 Jun",
+            "2018 Jul","2018 Aug","2018 Sep","2018 Oct","2018 Nov","2018 Dec",
+            "2019 Jan","2019 Feb","2019 Mar","2019 Apr","2019 May","2019 Jun",
+            "2019 Jul","2019 Aug","2019 Sep","2019 Oct","2019 Nov","2019 Dec",
+            "2020 Jan","2020 Feb","2020 Mar","2020 Apr","2020 May","2020 Jun",
+            "2020 Jul","2020 Aug")
+
+monthlyPrescribing <- 
+  function(data){
+    data %>% 
+      janitor::clean_names() %>% 
+      mutate(datename = dmy(paste0("28-", datename)),
+             practice_id = as.character(practice_id)) %>% 
+      countRegional(practice_id, datename, quantity) %>% 
+      mutate(year = year(datename)) %>%
+      as_tibble() %>% 
+      inner_join(gp, 
+                 by = c("regional_unit" = "practice_id", "year")) %>% 
+      mutate(n = 1000*n/npat,
+             datename = yearmonth(datename),
+             regional_unit = as_factor(regional_unit)) %>% 
+      select(-c(npat, year)) %>% 
+      as_tsibble(index = datename, key = regional_unit) %>% 
+      fill_gaps()
+  }
+
+gpMissing <- 
+  function(data){
+    data %>% 
+      as_tibble() %>% 
+      pivot_wider(id_cols = regional_unit, names_from = datename,
+                  values_from = n, values_fill = NA) %>% 
+      select(all_of(months), everything()) %>% 
+      rowwise() %>% 
+      mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
+      group_by(regional_unit) %>% 
+      summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
+                miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
+      filter(miss_covid > 0 | miss_non_covid > 0) %>% 
+      mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))
+  }
+
+missRemove <- 
+  function(data){
+    data %>% 
+      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), TRUE, FALSE)) %>% 
+      summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
+                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE, FALSE)),
+                miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
+  }
+
+n_practices <- 
+  data_files %>% 
+  map(read_rds) %>% 
+  map(pluck("practice_id")) %>% 
+  map(unique) %>% 
+  map_dfr(length) %>% 
+  pivot_longer(cols = everything(), names_to = "drug", values_to = "n")
+
+missing_raw_data <- 
+  data_files %>% 
+  map(read_rds) %>% 
+  map(monthlyPrescribing) %>% 
+  map(gpMissing) %>% 
+  map_dfr(missRemove, .id = "drug")
+
+poor_forcasts <- 
+  cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE >= 50) %>% 
+  group_by(drug) %>% 
+  summarise(mape_over_50 = n())
+
+n_practices %>% 
+  left_join(missing_raw_data, by = "drug") %>% 
+  left_join(poor_forcasts, by = "drug") %>% 
+  rowwise() %>% 
+  mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
+         total_removed = miss_either + mape_over_50) %>% 
+  knitr::kable(booktabs = TRUE, linesep = "",
+               caption = "Summary of GP practices removed for each drug.") %>% 
+  footnote(general = "The total is not always equal to the row sum, as a single practice may be missing both data in covid months and more than 10\\% of data in the non-covid months, but will only be excluded once.",
+           threeparttable = TRUE)
+
+n_practices %>% 
+  summarise(sum(n))
+
+length(unique(gp$practice_id))
+```
+
+\renewcommand{\appendixname}{Supplementary Material}
+\renewcommand{\thefigure}{SI\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{SI\arabic{table}} \setcounter{table}{0}
+\renewcommand{\theequation}{SI\arabic{table}} \setcounter{equation}{0}
+
+# Forecasting
+
+### Forecasting models
+
+* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
+* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
+  * Simple methods
+      * Naïve (with and without drift)
+        * $\hat{y}_{T+h|T} = y_T$
+      * Seasonal naïve (with and without drift)
+        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where m = seasonal period and k is the complete years in $T+h$
+  * STL Decomposition model [@Cleveland1990]
+    * Fixed and variable seasonality
+  * Time series linear model
+    * $y_t = \beta_0 + \beta_1x_t + \varepsilon_t$
+  * Autoregressive integrated moving average [ARIMA; @Box2015]
+    * Using a version of the Hyndman-Khandakar algorithm [@Hyndman2008]
+  * Exponential smoothing [@Holt2004; @Winters1960]
+    * Simple exponential smoothing
+    * Holt-Winters Additive Model [@Chatfield1978]
+  * Forecasting with Additive Switching of Seasonality, Trends and Exogenous Regressors [fasster; @R-fasster]
+    * State space model
+  * Prophet [@Taylor2018]
+  * Combination models [cf. @Bates1969; @Clemen1989; @Thomson2019]
+* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
+* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
+  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to keep run-times manageable)
+    * Only interested in one forecast horizon: six-months
+
+## All prescribing
+
+```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy", eval=FALSE}
+p1 <- all_prescribing_fable_fits %>% 
+  na.omit() %>% 
+  ggplot(aes(x = reorder(.model, RMSE, sort), y = RMSE)) +
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 90))
+
+p2 <- all_prescribing_fable_fits %>% 
+  na.omit() %>% 
+  ggplot(aes(x = reorder(.model, winkler, sort), y = winkler)) +
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 90))
+
+cowplot::plot_grid(p1, p2)
+```
+
+```{r, all-prescribing-cv-plot1, fig.cap="All prescribing, best model CV fit", eval=FALSE}
+all_prescribing_best_cv_model <- 
+  augment(all_prescribing_fable_models) %>% 
+  as_tibble() %>% 
+  filter(.model == all_prescribing_best_model$.model)
+
+all_prescribing_best_cv_model %>% 
+  ggplot(aes(x = datename)) +
+  geom_line(aes(y = n/1e+06, colour = "Data")) +
+  geom_line(aes(y = .fitted/1e+06, colour = "Fitted", lty = as.factor(.id))) +
+  labs(lty = "CV iteration")
+```
+
+```{r, all-prescribing-forecast-plot1, warning=FALSE, fig.cap="All prescribing, best model fit and forecast.", eval=FALSE}
+plan(cluster)
+all_prescribing %>% 
+  ggplot(aes(x = datename)) +
+  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
+  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
+            data = all_prescribing_covid_forecast) +
+  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
+                  fill = "Forecast"), alpha = .2,
+              data = all_prescribing_covid_forecast) +
+  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, 
+                  fill = "Forecast"), alpha = .3,
+              data = all_prescribing_covid_forecast) +
+  # geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
+  #           data = fableModels(all_prescribing_pre_cv19) %>% 
+  #             augment() %>% 
+  #             as_tibble() %>% 
+  #             filter(.model == all_prescribing_best_model$.model) %>% 
+  #             group_by(datename) %>% 
+  #             summarise(fitted = median(.fitted, na.rm = TRUE))) +
+  geom_vline(xintercept = ymd("2020-03-01"), lty = 3) +
+  coord_cartesian(xlim = c(dmy("01-11-2018"), dmy("01-08-2020"))) +
+  scale_x_yearmonth(breaks = "6 months", minor_breaks = "1 months")+
+  xlab("Date") +
+  ylab("Mean daily prescribing volume")
+
+plan(sequential)
+```
+
+```{r, all-prescribing-pct-change-plot1, fig.cap="Percentage difference in all prescribing.", eval=FALSE}
+all_prescribing %>% 
+  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
+  ggplot(aes(x = datename, y = (100*n/med)-100)) +
+  geom_line() +
+  geom_hline(yintercept = 0, lty = 3)
+```
+
+## Excluded practices
+
+Table with a row for each drug and a column for each reason a practice could be excluded, with a total column at the end
+
+(a) missing any data in the COVID months, (b) more than 10% of the pre-COVID data (i.e., 6 months) missing, (c) significant changes to prescribing in the six months pre-COVID (e.g., changes that suggested the practice had closed), or (d) MAPE >50.
+
+```{r, excluded-practices-tab1}
+months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
+            "2015 Jul","2015 Aug","2015 Sep","2015 Oct","2015 Nov","2015 Dec",
+            "2016 Jan","2016 Feb","2016 Mar","2016 Apr","2016 May","2016 Jun",
+            "2016 Jul","2016 Aug","2016 Sep","2016 Oct","2016 Nov","2016 Dec",
+            "2017 Jan","2017 Feb","2017 Mar","2017 Apr","2017 May","2017 Jun",
+            "2017 Jul","2017 Aug","2017 Sep","2017 Oct","2017 Nov","2017 Dec",
+            "2018 Jan","2018 Feb","2018 Mar","2018 Apr","2018 May","2018 Jun",
+            "2018 Jul","2018 Aug","2018 Sep","2018 Oct","2018 Nov","2018 Dec",
+            "2019 Jan","2019 Feb","2019 Mar","2019 Apr","2019 May","2019 Jun",
+            "2019 Jul","2019 Aug","2019 Sep","2019 Oct","2019 Nov","2019 Dec",
+            "2020 Jan","2020 Feb","2020 Mar","2020 Apr","2020 May","2020 Jun",
+            "2020 Jul","2020 Aug")
+
+monthlyPrescribing <- 
+  function(data){
+    data %>% 
+      janitor::clean_names() %>% 
+      mutate(datename = dmy(paste0("28-", datename)),
+             practice_id = as.character(practice_id)) %>% 
+      countRegional(practice_id, datename, quantity) %>% 
+      mutate(year = year(datename)) %>%
+      as_tibble() %>% 
+      inner_join(gp, 
+                 by = c("regional_unit" = "practice_id", "year")) %>% 
+      mutate(n = 1000*n/npat,
+             datename = yearmonth(datename),
+             regional_unit = as_factor(regional_unit)) %>% 
+      select(-c(npat, year)) %>% 
+      as_tsibble(index = datename, key = regional_unit) %>% 
+      fill_gaps()
+  }
+
+gpMissing <- 
+  function(data){
+    data %>% 
+      as_tibble() %>% 
+      pivot_wider(id_cols = regional_unit, names_from = datename,
+                  values_from = n, values_fill = NA) %>% 
+      select(all_of(months), everything()) %>% 
+      rowwise() %>% 
+      mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
+      group_by(regional_unit) %>% 
+      summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
+                miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
+      filter(miss_covid > 0 | miss_non_covid > 0) %>% 
+      mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))
+  }
+
+missRemove <- 
+  function(data){
+    data %>% 
+      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), TRUE, FALSE)) %>% 
+      summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
+                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE, FALSE)),
+                miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
+  }
+
+n_practices <- 
+  data_files %>% 
+  map(read_rds) %>% 
+  map(pluck("practice_id")) %>% 
+  map(unique) %>% 
+  map_dfr(length) %>% 
+  pivot_longer(cols = everything(), names_to = "drug", values_to = "n")
+
+missing_raw_data <- 
+  data_files %>% 
+  map(read_rds) %>% 
+  map(monthlyPrescribing) %>% 
+  map(gpMissing) %>% 
+  map_dfr(missRemove, .id = "drug")
+
+poor_forcasts <- 
+  cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE >= 50) %>% 
+  group_by(drug) %>% 
+  summarise(mape_over_50 = n())
+
+n_practices %>% 
+  left_join(missing_raw_data, by = "drug") %>% 
+  left_join(poor_forcasts, by = "drug") %>% 
+  rowwise() %>% 
+  mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
+         total_removed = miss_either + mape_over_50) %>% 
+  knitr::kable(booktabs = TRUE, linesep = "",
+               caption = "Summary of GP practices removed for each drug.") %>% 
+  footnote(general = "The total is not always equal to the row sum, as a single practice may be missing both data in covid months and more than 10\\% of data in the non-covid months, but will only be excluded once.",
+           threeparttable = TRUE)
+
+n_practices %>% 
+  summarise(sum(n))
+
+length(unique(gp$practice_id))
+```
+
+## Cross-validated model accuracy
+
+```{r, cv-model-accuracy-by-drug-tab}
+cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE < 50) %>% 
+  group_by(drug) %>% 
+  summarise(n_practice_retained = n(),
+            mape_mean = mean(MAPE),
+            mape_sd = sd(MAPE)) %>% 
+  kable(caption = "Accuaracy of cross-validated models retained for forecasting.",
+               digits = 2)
+```
+
+```{r, individual-drug-accuracy-plot, fig.cap="Accuracy of best model for each regional unit by drug, as measured by mean absoloute percentage error (MAPE). Models with MAPE > 50 have been removed."}
+cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE < 50) %>% 
+  mutate(drug = as.factor(drug),
+         drug = relevel(as_factor(drug), ref = "all_drugs")) %>% 
+  ggplot(aes(x = drug, y = MAPE, col = drug)) +
+  geom_violin() +
+  geom_jitter(alpha = .1) +
+  xlab("Medicine group")+
+  theme(legend.position = "none")
+```
+
+```{r best-cv-model-type, fig.cap="Performance by model type."}
+cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE < 50) %>% 
+  ggplot(aes(x = as.factor(.model))) +
+  geom_bar() +
+  xlab("Model") +
+  theme(axis.text.x = element_text(angle = 90))
+```
+
+## Warfarin
+
+```{r, oac-gen-trend, eval = FALSE}
+oac <- read_rds(data_files[9])
+
+oac %>% 
+  mutate(warfarin = if_else(bnfchem == "0208020V0", TRUE, FALSE)) %>% 
+  group_by(warfarin, datename) %>% 
+  summarise(quantity = sum(quantity), .groups = "drop") %>% 
+  pivot_wider(id_cols = datename, values_from = quantity, names_from = warfarin) %>% 
+  mutate(prop = `TRUE` / (`TRUE` + `FALSE`),
+         datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
+  tsibble() %>% 
+  autoplot(prop) +
+  xlab("Date") +
+  ylab("Warfarin as a proportion of all oral anticoagulant prescribing")
+
+```
+
+\newpage
+
+## SM References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup
+
+\newpage

### 2021-06-01 writing/appendix_a.Rmd
Draft appendix

--- 2021-03-05 writing/paper.Rmd
@@
 ---
-title             : "Variation in Primary Care Prescribing in Wales due to COVID-19"
-shorttitle        : "Welsh Primary Care COVID Prescribing"
-
-author: 
-  - name          : "First Author"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-  - name          : "Second Author"
-    affiliation   : "1,2"
-
-affiliation:
-  - id            : "1"
-    institution   : "Centre for Health Economics & Medicines Evaluation, Bangor University, LL55 2PZ"
-  - id            : "2"
-    institution   : "Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ"
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
-
+title: Supplementary Information
+short_title: COVID-19 Prescribing
 bibliography      : ["r-references.bib", "../references/library.bib"]
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-csl               : "../references/apa.csl"
-documentclass     : "apa7"
-classoption       : "man"
-output            : 
-  - papaja::apa6_pdf
-  - papaja::apa6_docx
+ouput: html_document
 ---
@@
 ## Data
+gp <- 
+  read_rds("../data/gp_agesex_qof_combined.rds") %>% 
+  mutate(npat = N,
+         N = NULL,
+         practice_id = as.character(practiceid)) %>% 
+  ungroup() %>% 
+  janitor::clean_names() %>% 
+  select(practice_id, year, npat)
+
+# GP extract data
+data_files <-
+  paste0("../data/prescribing_data/", list.files("../data/prescribing_data")) 
+names(data_files) <- 
+  str_remove_all(list.files("../data/prescribing_data"), ".rds")
+
+# CV model accuracies
+cv_model_files <- 
+  paste0("../data/gp_cv_models/", 
+         list.files("../data/gp_cv_models/"))
+names(cv_model_files) <- 
+  cv_model_files %>% 
+  str_remove_all("../data/gp_cv_models/") %>% 
+  str_remove_all("_gp_cv_models.rds")
+
+# Forecast - observed
 differences_files <- 
@@
           .id = "drug") %>% 
-  mutate(drug = as_factor(drug)) %>% 
-  select(drug, regional_unit, datename, discrepancy, med)
-
-all_prescribing <- 
-  read_csv("../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
-  mutate(datename = dmy(paste(28, datename, sep = "-")),
-         datename = yearmonth(datename),
-         regional_unit = factor("all")) %>% 
-  as_tsibble(index = datename) %>% 
-  filter(datename < yearmonth(dmy("01-09-2020")))
-
-all_prescribing_pre_cv19 <- 
-  all_prescribing %>% 
-  filter(datename < yearmonth(dmy("01-03-2020")))
+  mutate(drug = relevel(as_factor(drug), ref = "all_drugs"))
 
@@
 
-```{r analysis-preferences}
+```{r, analysis-preferences}
 # Seed for random number generation
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
+kable_opts <- options(knitr.kable.NA = "-")
 ```
 
-# Methods
+\renewcommand{\appendixname}{Supplementary Material}
+\renewcommand{\thefigure}{SI\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{SI\arabic{table}} \setcounter{table}{0}
+\renewcommand{\theequation}{SI\arabic{table}} \setcounter{equation}{0}
 
-## Data
+## Reproducability and code
 
-* Sources of data
-  * GP
-  * Prescribing
-  * QOF
-  * WIMD
-* Preparing
+We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.
 
-## Identifying changes in prescribing due to COVID-19
-
-Identifying the effects of COVID-19 is not simple, as its effects are unprecedented and its global impact prevents us from adopting a traditional treatment and control group type design.
-Instead, we have used time series analysis methods to create counterfactual forecasts
-
-To understand the changes in levels of prescribing due to COVID-19, it was first necessary for us to forecast the levels of prescribing had COVID-19 not affected Wales as a baseline.
-To do so, we used historic data (January 2015 to December 2020) to identify from a range of time series models, one that was good fit to the data.
-This was done using cross-validation to reduce the likelihood of choosing a model that was overfitted to the data.
-
-* Given the presence of seasonal variation and existing trends in levels of prescribing, we used various time series forecasting methods to account for existing trends and seasonal variation when creating the forecasts.
-* For each analysis, we created a forecast that aimed to answer the question, "What would the levels of prescribing have been if COVID-19 had not affected Wales?" We then used these forecasts to estimate the changes in levels of prescribing due to COVID-19.
-* We viewed this, somewhat complex, approach as superior to more simple approaches (e.g., carrying last years levels forward, or even using the mean of the last three years).
+## Forecasting
 
@@
 * We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
+  * Simple methods
+      * Naïve (with and without drift)
+        * $\hat{y}_{T+h|T} = y_T$
+      * Seasonal naïve (with and without drift)
+        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where m = seasonal period and k is the complete years in $T+h$
+  * STL Decomposition model [@Cleveland1990]
+    * Fixed and variable seasonality
   * Time series linear model
-  * Decomposition model
-  * Seasonal naïve (with and without drift)
+    * $y_t = \beta_0 + \beta_1x_t + \varepsilon_t$
   * Autoregressive integrated moving average [ARIMA; @Box2015]
+    * Using a version of the Hyndman-Khandakar algorithm [@Hyndman2008]
+  * Exponential smoothing [@Holt2004; @Winters1960]
+    * Simple exponential smoothing
     * Holt-Winters Additive Model [@Chatfield1978]
+  * Forecasting with Additive Switching of Seasonality, Trends and Exogenous Regressors [fasster; @R-fasster]
+    * State space model
   * Prophet [@Taylor2018]
-  * Combination models [cf. @Thomson2019]
+  * Combination models [cf. @Bates1969; @Clemen1989; @Thomson2019]
 * Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
 * Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
-  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
+  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to keep run-times manageable)
     * Only interested in one forecast horizon: six-months
 
-### Model selection
+## All prescribing
 
-* Ranked by RMSE and Winkler [@Winkler1972], then the best mean ranking model is chosen
-  * RMSE is scale dependant. Is suitable for comparing models of the same data.
-  * Winkler score penalises models that have observations falling outside the prediction interval, thus rewards models with narrow intervals
-* This combination accounts for both the point and distributional accuracy of the forecasts
+```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy", eval=FALSE}
+p1 <- all_prescribing_fable_fits %>% 
+  na.omit() %>% 
+  ggplot(aes(x = reorder(.model, RMSE, sort), y = RMSE)) +
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 90))
 
-### Forecasts
-
-* Having chosen the "best model" for each practice based on the pre-COVID data, we then used this model to forecast the level of prescribing for each practice
-
-## Reproducability and code
-
-We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.
-
-# Results
-
-## Counterfactual forecasts
-
-### All prescribing
-
-```{r all-prescribing-modelling, warning=FALSE}
-plan(cluster)
-
-all_prescribing_fable_models <- 
-  all_prescribing_pre_cv19 %>% 
-  mutate(datename = yearmonth(datename)) %>%
-  fill_gaps() %>%
-  slice(1:(n()-2), .preserve = TRUE) %>%
-  stretch_tsibble(.init = 36, .step = 3) %>%
-  fableModels()
-
-all_prescribing_fable_forecasts <- 
-  all_prescribing_fable_models %>%
-  forecast(h = 6, point_forecast = list(.median = median))
-
-all_prescribing_fable_fits <- 
-  all_prescribing_fable_forecasts %>% 
-  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
-                           rmse_skill = skill_score(RMSE),
-                           crps_skill = skill_score(CRPS), ACF1 = ACF1,
-                           winkler = winkler_score))
-
-all_prescribing_prophet_fits <- 
-  all_prescribing_pre_cv19 %>%
-  mutate(datename = yearmonth(datename)) %>%
-  fill_gaps() %>%
-  slice(1:(n()-2), .preserve = TRUE) %>%
-  stretch_tsibble(.init = 36, .step = 3) %>%
-  prophetModels() %>%
-  forecast(h = 6, point_forecast = list(.median = median)) %>%
-  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
-                           rmse_skill = skill_score(RMSE),
-                           crps_skill = skill_score(CRPS), ACF1 = ACF1,
-                           winkler = winkler_score))
-
-all_prescribing_combined_fits <- 
-  bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
-  rankModels()
-
-all_prescribing_best_model <- 
-  all_prescribing_combined_fits %>% 
-  slice(1, .preserve = TRUE)
-
-all_prescribing_covid_forecast <- 
-  bind_rows(fableModels(all_prescribing_pre_cv19) %>% 
-            forecast(h = "6 months"),
-          prophetModels(all_prescribing_pre_cv19) %>% 
-            forecast(h = "6 months")) %>% 
-  as_tibble() %>% 
-  filter(.model == all_prescribing_best_model$.model) %>% 
-  dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 0.1), 
-                med = median(n), ub_80 = quantile(n, 0.9), 
-                ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
-                n = NULL)
-
-plan(sequential)
-
-```
-
-```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy"}
-p1 <- all_prescribing_combined_fits %>% 
+p2 <- all_prescribing_fable_fits %>% 
   na.omit() %>% 
-  ggplot(aes(x = reorder(.model, rank, sort), y = RMSE)) +
-  geom_col()
-
-p2 <- all_prescribing_combined_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, rank, sort), y = winkler)) +
-  geom_col()
+  ggplot(aes(x = reorder(.model, winkler, sort), y = winkler)) +
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 90))
 
@@
 
-```{r, all-prescribing-cv-plot, fig.cap="All prescribing, best model CV fit"}
+```{r, all-prescribing-cv-plot, fig.cap="All prescribing, best model CV fit", eval=FALSE}
 all_prescribing_best_cv_model <- 
@@
 
-```{r, all-prescribing-forecast-plot, fig.cap="All prescribing, best model fit and forecast"}
+```{r, all-prescribing-forecast-plot, warning=FALSE, fig.cap="All prescribing, best model fit and forecast.", eval=FALSE}
+plan(cluster)
 all_prescribing %>% 
@@
   geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
-                   fill = "Forecast"), alpha = .5,
+                  fill = "Forecast"), alpha = .2,
               data = all_prescribing_covid_forecast) +
-  geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
-            data = all_prescribing_best_cv_model %>% 
-              group_by(datename) %>% 
-              summarise(fitted = median(.fitted, na.rm = TRUE))) +
-  geom_vline(xintercept = ymd("2020-03-01"), lty = 3)
+  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, 
+                  fill = "Forecast"), alpha = .3,
+              data = all_prescribing_covid_forecast) +
+  # geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
+  #           data = fableModels(all_prescribing_pre_cv19) %>% 
+  #             augment() %>% 
+  #             as_tibble() %>% 
+  #             filter(.model == all_prescribing_best_model$.model) %>% 
+  #             group_by(datename) %>% 
+  #             summarise(fitted = median(.fitted, na.rm = TRUE))) +
+  geom_vline(xintercept = ymd("2020-03-01"), lty = 3) +
+  coord_cartesian(xlim = c(dmy("01-11-2018"), dmy("01-08-2020"))) +
+  scale_x_yearmonth(breaks = "6 months", minor_breaks = "1 months")+
+  xlab("Date") +
+  ylab("Mean daily prescribing volume")
+
+plan(sequential)
 ```
 
-```{r, all-prescribing-pct-change-plot, fig.cap="Percentage difference in all prescribing"}
+```{r, all-prescribing-pct-change-plot, fig.cap="Percentage difference in all prescribing.", eval=FALSE}
 all_prescribing %>% 
@@
 
-### Specific drugs
+## Excluded practices
 
-# Discussion
+Table with a row for each drug and a column for each reason a practice could be excluded, with a total column at the end
+
+(a) missing any data in the COVID months, (b) more than 10% of the pre-COVID data (i.e., 6 months) missing, (c) significant changes to prescribing in the six months pre-COVID (e.g., changes that suggested the practice had closed), or (d) MAPE >50.
+
+```{r, excluded-practices-tab}
+months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
+            "2015 Jul","2015 Aug","2015 Sep","2015 Oct","2015 Nov","2015 Dec",
+            "2016 Jan","2016 Feb","2016 Mar","2016 Apr","2016 May","2016 Jun",
+            "2016 Jul","2016 Aug","2016 Sep","2016 Oct","2016 Nov","2016 Dec",
+            "2017 Jan","2017 Feb","2017 Mar","2017 Apr","2017 May","2017 Jun",
+            "2017 Jul","2017 Aug","2017 Sep","2017 Oct","2017 Nov","2017 Dec",
+            "2018 Jan","2018 Feb","2018 Mar","2018 Apr","2018 May","2018 Jun",
+            "2018 Jul","2018 Aug","2018 Sep","2018 Oct","2018 Nov","2018 Dec",
+            "2019 Jan","2019 Feb","2019 Mar","2019 Apr","2019 May","2019 Jun",
+            "2019 Jul","2019 Aug","2019 Sep","2019 Oct","2019 Nov","2019 Dec",
+            "2020 Jan","2020 Feb","2020 Mar","2020 Apr","2020 May","2020 Jun",
+            "2020 Jul","2020 Aug")
+
+monthlyPrescribing <- 
+  function(data){
+    data %>% 
+      janitor::clean_names() %>% 
+      mutate(datename = dmy(paste0("28-", datename)),
+             practice_id = as.character(practice_id)) %>% 
+      countRegional(practice_id, datename, quantity) %>% 
+      mutate(year = year(datename)) %>%
+      as_tibble() %>% 
+      inner_join(gp, 
+                 by = c("regional_unit" = "practice_id", "year")) %>% 
+      mutate(n = 1000*n/npat,
+             datename = yearmonth(datename),
+             regional_unit = as_factor(regional_unit)) %>% 
+      select(-c(npat, year)) %>% 
+      as_tsibble(index = datename, key = regional_unit) %>% 
+      fill_gaps()
+  }
+
+gpMissing <- 
+  function(data){
+    data %>% 
+      as_tibble() %>% 
+      pivot_wider(id_cols = regional_unit, names_from = datename,
+                  values_from = n, values_fill = NA) %>% 
+      select(all_of(months), everything()) %>% 
+      rowwise() %>% 
+      mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
+      group_by(regional_unit) %>% 
+      summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
+                miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
+      filter(miss_covid > 0 | miss_non_covid > 0) %>% 
+      mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))
+  }
+
+missRemove <- 
+  function(data){
+    data %>% 
+      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), TRUE, FALSE)) %>% 
+      summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
+                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE, FALSE)),
+                miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
+  }
+
+n_practices <- 
+  data_files %>% 
+  map(read_rds) %>% 
+  map(pluck("practice_id")) %>% 
+  map(unique) %>% 
+  map_dfr(length) %>% 
+  pivot_longer(cols = everything(), names_to = "drug", values_to = "n")
+
+missing_raw_data <- 
+  data_files %>% 
+  map(read_rds) %>% 
+  map(monthlyPrescribing) %>% 
+  map(gpMissing) %>% 
+  map_dfr(missRemove, .id = "drug")
+
+poor_forcasts <- 
+  cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE >= 50) %>% 
+  group_by(drug) %>% 
+  summarise(mape_over_50 = n())
+
+n_practices %>% 
+  left_join(missing_raw_data, by = "drug") %>% 
+  left_join(poor_forcasts, by = "drug") %>% 
+  rowwise() %>% 
+  mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
+         total_removed = miss_either + mape_over_50) %>% 
+  knitr::kable(booktabs = TRUE, linesep = "",
+               caption = "Summary of GP practices removed for each drug.") %>% 
+  footnote(general = "The total is not always equal to the row sum, as a single practice may be missing both data in covid months and more than 10\\% of data in the non-covid months, but will only be excluded once.",
+           threeparttable = TRUE)
+
+n_practices %>% 
+  summarise(sum(n))
+
+length(unique(gp$practice_id))
+```
+
+## Cross-validated model accuracy
+
+```{r, cv-model-accuracy-by-drug-tab}
+cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE < 50) %>% 
+  group_by(drug) %>% 
+  summarise(n_practice_retained = n(),
+            mape_mean = mean(MAPE),
+            mape_sd = sd(MAPE)) %>% 
+  kable(caption = "Accuaracy of cross-validated models retained for forecasting.",
+               digits = 2)
+```
+
+```{r, individual-drug-accuracy-plot, fig.cap="Accuracy of best model for each regional unit by drug, as measured by mean absoloute percentage error (MAPE). Models with MAPE > 50 have been removed."}
+cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE < 50) %>% 
+  mutate(drug = as.factor(drug),
+         drug = relevel(as_factor(drug), ref = "all_drugs")) %>% 
+  ggplot(aes(x = drug, y = MAPE, col = drug)) +
+  geom_violin() +
+  geom_jitter(alpha = .1) +
+  xlab("Medicine group")+
+  theme(legend.position = "none")
+```
+
+```{r best-cv-model-type, fig.cap="Performance by model type."}
+cv_model_files %>% 
+  map_dfr(.id = "drug", .f = read_rds) %>% 
+  rankModels() %>% 
+  group_by(drug, regional_unit) %>% 
+  slice(1, .preserve = TRUE) %>% 
+  filter(MAPE < 50) %>% 
+  ggplot(aes(x = as.factor(.model))) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 90))
+```
+
+## Warfarin
+
+```{r, oac-gen-trend, eval=FALSE}
+oac <- read_rds(data_files[9])
+
+oac %>% 
+  mutate(warfarin = if_else(bnfchem == "0208020V0", TRUE, FALSE)) %>% 
+  group_by(warfarin, datename) %>% 
+  summarise(quantity = sum(quantity), .groups = "drop") %>% 
+  pivot_wider(id_cols = datename, values_from = quantity, names_from = warfarin) %>% 
+  mutate(prop = `TRUE` / (`TRUE` + `FALSE`),
+         datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
+  tsibble() %>% 
+  autoplot(prop) +
+  xlab("Date") +
+  ylab("Warfarin as a proportion of all oral anticoagulant prescribing")
+
+```
 
@@
 
-# References
+## SM References
 
@@
 \endgroup
+
+\newpage

### 2021-06-01 writing/appendix_a.tex
Draft appendix

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\renewcommand{\appendixname}{Supplementary Material}
\renewcommand{\thefigure}{SI\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{SI\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{SI\arabic{table}} \setcounter{equation}{0}

\hypertarget{forecasting}{%
\section{Forecasting}\label{forecasting}}

\hypertarget{forecasting-models}{%
\subsubsection{Forecasting models}\label{forecasting-models}}

\begin{itemize}
\tightlist
\item
  We did not assume that the existing processes would be the same for
  all drugs or all GP practices, therefore, we investigated the fit of
  several different time series models to the pre-COVID data.
\item
  We used the \texttt{fable} (O'Hara-Wild et al., 2021),
  \texttt{fasster} (O'Hara-Wild \& Hyndman, 2021), and the
  \texttt{fable.prophet} (O'Hara-Wild, 2020) packages to conduct the
  time series analyses.

  \begin{itemize}
  \tightlist
  \item
    Simple methods

    \begin{itemize}
    \tightlist
    \item
      Naïve (with and without drift)

      \begin{itemize}
      \tightlist
      \item
        \(\hat{y}_{T+h|T} = y_T\)
      \end{itemize}
    \item
      Seasonal naïve (with and without drift)

      \begin{itemize}
      \tightlist
      \item
        \(\hat{y}_{T+h|T} = y_{T-m(k+1)}\) where m = seasonal period and
        k is the complete years in \(T+h\)
      \end{itemize}
    \end{itemize}
  \item
    STL Decomposition model (Cleveland et al., 1990)

    \begin{itemize}
    \tightlist
    \item
      Fixed and variable seasonality
    \end{itemize}
  \item
    Time series linear model

    \begin{itemize}
    \tightlist
    \item
      \(y_t = \beta_0 + \beta_1x_t + \varepsilon_t\)
    \end{itemize}
  \item
    Autoregressive integrated moving average (ARIMA; Box et al., 2015)

    \begin{itemize}
    \tightlist
    \item
      Using a version of the Hyndman-Khandakar algorithm (Hyndman \&
      Khandakar, 2008)
    \end{itemize}
  \item
    Exponential smoothing (Holt, 2004; Winters, 1960)

    \begin{itemize}
    \tightlist
    \item
      Simple exponential smoothing
    \item
      Holt-Winters Additive Model (Chatfield, 1978)
    \end{itemize}
  \item
    Forecasting with Additive Switching of Seasonality, Trends and
    Exogenous Regressors (fasster; O'Hara-Wild \& Hyndman, 2021)

    \begin{itemize}
    \tightlist
    \item
      State space model
    \end{itemize}
  \item
    Prophet (Taylor \& Letham, 2018)
  \item
    Combination models (cf.~{\textbf{???}}; Clemen, 1989; Thomson et
    al., 2019)
  \end{itemize}
\item
  Prescribing quantities log transformed and forecasts use median values
  to reduce bias that back transformation would introduce when using the
  mean
\item
  Using Jan 2015 to Dec 2019 data, we fitted several different models
  and assessed their accuracy using a cross-validated process to reduce
  the likelihood of overfitting models to the data.

  \begin{itemize}
  \tightlist
  \item
    Started with 36 months of data, used 6-month horizon as this was the
    horizon we would be using for the forecasts, 3-month step (to keep
    run-times manageable)

    \begin{itemize}
    \tightlist
    \item
      Only interested in one forecast horizon: six-months
    \end{itemize}
  \end{itemize}
\end{itemize}

\hypertarget{all-prescribing}{%
\subsection{All prescribing}\label{all-prescribing}}

\hypertarget{excluded-practices}{%
\subsection{Excluded practices}\label{excluded-practices}}

Table with a row for each drug and a column for each reason a practice
could be excluded, with a total column at the end

\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\tightlist
\item
  missing any data in the COVID months, (b) more than 10\% of the
  pre-COVID data (i.e., 6 months) missing, (c) significant changes to
  prescribing in the six months pre-COVID (e.g., changes that suggested
  the practice had closed), or (d) MAPE \textgreater50.
\end{enumerate}

\begin{table}

\caption{(\#tab:excluded-practices-tab)Summary of GP practices removed for each drug.}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lrrrrrr}
\toprule
drug & n & miss\_covid & miss\_10\_non\_covid & miss\_either & mape\_over\_50 & total\_removed\\
\midrule
ace & 531 & 6 & 1 & 7 & 0 & 7\\
adreno & 545 & 9 & 2 & 10 & 12 & 22\\
all\_drugs & 643 & 2 & 1 & 3 & 3 & 6\\
azithro & 488 & 26 & 29 & 41 & 85 & 126\\
contra & 494 & 9 & 5 & 10 & 4 & 14\\
cortico & 537 & 9 & 2 & 10 & 0 & 10\\
hcq & 480 & 13 & 15 & 22 & 14 & 36\\
nsaid & 537 & 9 & 2 & 10 & 1 & 11\\
oac & 511 & 9 & 3 & 11 & 0 & 11\\
paracet & 559 & 9 & 1 & 10 & 1 & 11\\
ssri & 543 & 9 & 1 & 10 & 0 & 10\\
vitd & 509 & 9 & 2 & 10 & 0 & 10\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item The total is not always equal to the row sum, as a single practice may be missing both data in covid months and more than 10\textbackslash{}\% of data in the non-covid months, but will only be excluded once.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{verbatim}
## # A tibble: 1 x 1
##   `sum(n)`
##      <int>
## 1     6377
\end{verbatim}

\begin{verbatim}
## [1] 412
\end{verbatim}

\hypertarget{cross-validated-model-accuracy}{%
\subsection{Cross-validated model
accuracy}\label{cross-validated-model-accuracy}}

\begin{table}

\caption{(\#tab:cv-model-accuracy-by-drug-tab)Accuaracy of cross-validated models retained for forecasting.}
\centering
\begin{tabular}[t]{l|r|r|r}
\hline
drug & n\_practice\_retained & mape\_mean & mape\_sd\\
\hline
ace & 405 & 4.56 & 3.98\\
\hline
adreno & 390 & 18.66 & 7.37\\
\hline
all\_drugs & 406 & 6.86 & 3.61\\
\hline
azithro & 286 & 26.83 & 10.05\\
\hline
contra & 398 & 19.97 & 8.09\\
\hline
cortico & 402 & 8.75 & 5.64\\
\hline
hcq & 373 & 20.11 & 8.95\\
\hline
nsaid & 401 & 9.75 & 5.24\\
\hline
oac & 401 & 7.38 & 3.86\\
\hline
paracet & 401 & 6.40 & 3.95\\
\hline
ssri & 402 & 5.19 & 3.19\\
\hline
vitd & 402 & 7.71 & 4.50\\
\hline
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/individual-drug-accuracy-plot-1.pdf}
\caption{(\#fig:individual-drug-accuracy-plot)Accuracy of best model for
each regional unit by drug, as measured by mean absoloute percentage
error (MAPE). Models with MAPE \textgreater{} 50 have been removed.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/best-cv-model-type-1.pdf}
\caption{(\#fig:best-cv-model-type)Performance by model type.}
\end{figure}

\newpage

\hypertarget{sm-references}{%
\subsection{SM References}\label{sm-references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Box2015}{}%
Box, G. E. P., Jenkins, G. M., Reinsel, G. C. .., \& Ljung, G. M.
(2015). \emph{Time series analysis: forecasting and control} (5th ed.).
John Wiley \& Sons.

\leavevmode\hypertarget{ref-Chatfield1978}{}%
Chatfield, C. (1978). The Holt-Winters Forecasting Procedure.
\emph{Journal of the Royal Statistical Society: Series C (Applied
Statistics)}, \emph{27}(3), 264--279.

\leavevmode\hypertarget{ref-Clemen1989}{}%
Clemen, R. T. (1989). Combining forecasts: A review and annotated
bibliography. \emph{International Journal of Forecasting}, \emph{5}(4),
559--583. \url{https://doi.org/10.1016/0169-2070(89)90012-5}

\leavevmode\hypertarget{ref-Cleveland1990}{}%
Cleveland, R. B., Cleveland, W. S., McRae, J. E., \& Terpenning, I.
(1990). STL: A seasonal-trend decompostion procedure based on loess.
\emph{Journal of Official Statistics}, \emph{6}(1), 3--73.

\leavevmode\hypertarget{ref-Holt2004}{}%
Holt, C. C. (2004). Forecasting seasonals and trends by exponentially
weighted moving averages. \emph{International Journal of Forecasting},
\emph{20}(1), 5--10.
\url{https://doi.org/10.1016/j.ijforecast.2003.09.015}

\leavevmode\hypertarget{ref-Hyndman2008}{}%
Hyndman, R. J., \& Khandakar, Y. (2008). Automatic Time Series
Forecasting: The forecast Package for R. \emph{Journal of Statistical
Software}, \emph{27}(3), 1--22.
\url{http://www.jstatsoft.org/v27/i03/paper}

\leavevmode\hypertarget{ref-R-fable.prophet}{}%
O'Hara-Wild, M. (2020). \emph{Fable.prophet: Prophet modelling interface
for 'fable'}. \url{https://CRAN.R-project.org/package=fable.prophet}

\leavevmode\hypertarget{ref-R-fasster}{}%
O'Hara-Wild, M., \& Hyndman, R. (2021). \emph{Fasster: Fast additive
switching of seasonality, trend and exogenous regressors}.
\url{https://github.com/mitchelloharawild/fasster}

\leavevmode\hypertarget{ref-R-fable}{}%
O'Hara-Wild, M., Hyndman, R., \& Wang, E. (2021). \emph{Fable:
Forecasting models for tidy time series}.
\url{https://CRAN.R-project.org/package=fable}

\leavevmode\hypertarget{ref-Taylor2018}{}%
Taylor, S. J., \& Letham, B. (2018). Forecasting at Scale.
\emph{American Statistician}, \emph{72}(1), 37--45.
\url{https://doi.org/10.1080/00031305.2017.1380080}

\leavevmode\hypertarget{ref-Thomson2019}{}%
Thomson, M. E., Pollock, A. C., Önkal, D., \& Gönül, M. S. (2019).
Combining forecasts: Performance and coherence. \emph{International
Journal of Forecasting}, \emph{35}(2), 474--484.
\url{https://doi.org/10.1016/j.ijforecast.2018.10.006}

\leavevmode\hypertarget{ref-Winters1960}{}%
Winters, P. R. (1960). Forecasting Sales by Exponentially Weighted
Moving Averages. \emph{Management Science}, \emph{6}(3), 324--342.
\url{https://doi.org/10.1287/mnsc.6.3.324}

\endgroup

\newpage
\end{appendix}

### 2021-06-01 writing/appendix_a.Rmd
Paper v2.1

@@
 ---
-title: Supplementary Information
+title: "Supplementary Information"
 short_title: COVID-19 Prescribing
-bibliography      : ["r-references.bib", "../references/library.bib"]
-ouput: html_document
+bibliography:
+- r-references.bib
+- ../references/library.bib
+output: pdf_document
+ouput: pdf_document
 ---
@@
 
-```
-
-```{r, analysis-preferences}
 # Seed for random number generation
 set.seed(32)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE, echo = FALSE)
 kable_opts <- options(knitr.kable.NA = "-")
@@
 * We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
-* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
+* We used the `fable` [@R-fable] and `fasster` [@R-fasster] packages to conduct the time series analyses.
   * Simple methods
@@
       * Seasonal naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where m = seasonal period and k is the complete years in $T+h$
+        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where $m$ = seasonal period and $k$ is the complete years in $T+h$
   * STL Decomposition model [@Cleveland1990]
@@
     * State space model
-  * Prophet [@Taylor2018]
-  * Combination models [cf. @Bates1969; @Clemen1989; @Thomson2019]
-* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
-* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
+  * Combination models [cf. @Clemen1989; @Thomson2019]
+* Prescribing quantities were log transformed and the forecasts use median estimates of prescribing to reduce bias that back transformation would introduce when using the mean
+* Using January 2015 to December 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
   * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to keep run-times manageable)
     * Only interested in one forecast horizon: six-months
-
-## All prescribing
-
-```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy", eval=FALSE}
-p1 <- all_prescribing_fable_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, RMSE, sort), y = RMSE)) +
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 90))
-
-p2 <- all_prescribing_fable_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, winkler, sort), y = winkler)) +
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 90))
-
-cowplot::plot_grid(p1, p2)
-```
-
-```{r, all-prescribing-cv-plot, fig.cap="All prescribing, best model CV fit", eval=FALSE}
-all_prescribing_best_cv_model <- 
-  augment(all_prescribing_fable_models) %>% 
-  as_tibble() %>% 
-  filter(.model == all_prescribing_best_model$.model)
-
-all_prescribing_best_cv_model %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = n/1e+06, colour = "Data")) +
-  geom_line(aes(y = .fitted/1e+06, colour = "Fitted", lty = as.factor(.id))) +
-  labs(lty = "CV iteration")
-```
-
-```{r, all-prescribing-forecast-plot, warning=FALSE, fig.cap="All prescribing, best model fit and forecast.", eval=FALSE}
-plan(cluster)
-all_prescribing %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
-  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
-            data = all_prescribing_covid_forecast) +
-  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
-                  fill = "Forecast"), alpha = .2,
-              data = all_prescribing_covid_forecast) +
-  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, 
-                  fill = "Forecast"), alpha = .3,
-              data = all_prescribing_covid_forecast) +
-  # geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
-  #           data = fableModels(all_prescribing_pre_cv19) %>% 
-  #             augment() %>% 
-  #             as_tibble() %>% 
-  #             filter(.model == all_prescribing_best_model$.model) %>% 
-  #             group_by(datename) %>% 
-  #             summarise(fitted = median(.fitted, na.rm = TRUE))) +
-  geom_vline(xintercept = ymd("2020-03-01"), lty = 3) +
-  coord_cartesian(xlim = c(dmy("01-11-2018"), dmy("01-08-2020"))) +
-  scale_x_yearmonth(breaks = "6 months", minor_breaks = "1 months")+
-  xlab("Date") +
-  ylab("Mean daily prescribing volume")
-
-plan(sequential)
-```
-
-```{r, all-prescribing-pct-change-plot, fig.cap="Percentage difference in all prescribing.", eval=FALSE}
-all_prescribing %>% 
-  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
-  ggplot(aes(x = datename, y = (100*n/med)-100)) +
-  geom_line() +
-  geom_hline(yintercept = 0, lty = 3)
-```
 
@@
            threeparttable = TRUE)
-
-n_practices %>% 
-  summarise(sum(n))
-
-length(unique(gp$practice_id))
 ```
@@
 
-```{r, cv-model-accuracy-by-drug-tab}
+```{r, cv-model-accuracy-by-drug-tab, eval=FALSE}
 cv_model_files %>% 
@@
 
-```{r, oac-gen-trend, eval=FALSE}
-oac <- read_rds(data_files[9])
+```{r, oac-gen-trend, fig.cap="Warfarin as a percentage of all oral anticoagulant prescribing in Wales. Pink shading covers duration of Wales' \"stay at home\" order."}
+oac <- read_rds(data_files[12])
 
@@
          datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
-  tsibble() %>% 
-  autoplot(prop) +
+  tsibble(index = datename) %>% 
+  ggplot(aes(x = datename)) + 
+  geom_line(aes(y = prop))+
+  geom_vline(aes(xintercept = dmy("01-03-2020")), lty = 2, col = "red") +
+  geom_rect(aes(xmin = dmy("01-03-2020"), xmax = dmy("31-07-2020"), 
+                ymin = -Inf, ymax = Inf),
+            fill = 'pink', col = 0,alpha = 0.03) +
   xlab("Date") +

### 2021-06-01 writing/paper.Rmd
Paper v2.1

@@
           .id = "drug") %>% 
-  mutate(drug = relevel(as_factor(drug), ref = "all_drugs"),
-         sd = sd^.25)
+  mutate(drug = case_when(drug == "contra" ~ "oral",
+                          !drug == "contra" ~ drug),
+         drug = relevel(as_factor(drug), ref = "all_drugs"),
+         sd = sd^.25) # Error in serCymruTools when calculated
 
@@
 
-# Introduction
-
-# Methods
-
-## Data
+## Figure 1
 
@@
 ```
+
+## Table 2
 
@@
 
-# Results
+## Figure 2
 
@@
 ```
-
 ```{r}
-avg <- function(samples){
-  if (length(samples) >= 1){
-    return(sum(samples) / length(samples))
-  }
-  else{return(NaN)}
-}
-
-sample_SD <- function(samples){
-  # Input is an vector of samples; result is the standard deviation
-  mean = avg(samples)
-  sum_of_squared_deviations <-  0
-  sd <-  0
-  if(length(samples) >= 2){
-    for (datum in samples){
-      sum_of_squared_deviations <- 
-        sum_of_squared_deviations + ((datum - mean) * (datum - mean))
-      sd = sqrt(sum_of_squared_deviations / (length(samples)-1))
-    }
-      return(sd)
-  }
-}
-
-set.seed(134)
-vec <- c(rnorm(n = 100), rnorm(n = 100))
-vec_sd <- sd(vec)
-sample_SD(vec)
-compositeSD()
-
-vec
-compositeSD <- function(means, SDs, ncounts){
-  #Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
-  # See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
-  #    Inputs are:
-  #      means, the array of group means
-  #      SDs, the array of group standard deviations
-  #      ncounts, number of samples in each group (can be scalar
-  #               if all groups have same number of samples)
-  #    Result is the overall standard deviation.
-  G <- length(means) # number of groups
-  if(G != length(SDs)) stop("Inconsistent lengths (means & sds")
-  if(!is.numeric(ncounts)) {(as.numeric(ncounts))}
-  if(G != length(ncounts)) stop("Inconsistent lengths (means & ncounts)")
-
-  # Calculate total number of samples, N, and grand mean, GM
-  N = sum(ncounts)  # total number of samples
-  if (N <= 1) stop(paste("Warning: only ", N, " samples, SD is incalculable"))
-  GM <-  0.0
-  for (i in 1:G){
-    GM <- GM + means[i] * ncounts[i]
-  }
-  GM <- GM / N  # grand mean
-
-  # calculate Error Sum of Squares
-  ESS <-  0.0
-  for (i in 1:G){
-    ESS <- ESS + ((SDs[i])**2) * (ncounts[i] - 1)
-  }
-
-  # calculate Total Group Sum of Squares
-  TGSS <-  0.0
-  for (i in 1:G){
-    TGSS <- TGSS + ((means[i]-GM)**2) * ncounts[i]
-  }
-
-  # calculate standard deviation as square root of grand variance
-  result <- sqrt((ESS+TGSS)/(N-1))
-  return(result)
-}
-
-samples = 0:9
-print(paste("avg =", avg(samples)))
-sd = sample_SD(samples)
-print(paste("sd =", sd))
-pt1 = c(0,1,2)
-pt2 = c(3,4)
-pt3 = c(5,6,7,8,9)
-means <- c(avg(pt1), avg(pt2), avg(pt3))
-SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
-ncounts <- c(length(pt1), length(pt2), length(pt3))
-sd2 <- compositeSD(means, SDs, ncounts)
-print(paste("sd2 =", sd2))
-
-samples = 0:8
-print(paste("avg =", avg(samples)))
-sd = sample_SD(samples)
-print(paste("sd =", sd))
-pt1 = c(0,1,2)
-pt2 = c(3,4,5)
-pt3 = c(6,7,8)
-means <- c(avg(pt1), avg(pt2), avg(pt3))
-SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
-ncounts <- c(length(pt1), length(pt2), length(pt3))
-sd2 <- compositeSD(means, SDs, ncounts)
-print(paste("sd2 =", sd2))
+differences_quantiles %>%
+  mutate(datename = factor(x = datename, levels = 1:8, 
+                           labels = month.abb[1:8])) %>% 
+  mutate(drug = case_when(drug == "all_drugs" ~ "All",
+                          drug == "ace" ~ "ACE inhibitors",
+                          drug == "adreno" ~ "Adrenoceptor agonists",
+                          drug == "azithro" ~ "Azithromycin",
+                          drug == "contra" ~ "Oral contraceptives",
+                          drug == "cortico" ~ "Corticosteroids",
+                          drug == "hcq" ~ "Hydroxycholoroquine",
+                          drug == "nsaid" ~ "NSAIDs",
+                          drug == "paracet" ~ "Paracetamol",
+                          drug == "ssri" ~ "SSRIs",
+                          drug == "vitd" ~ "Vitamin D",
+                          drug == "warfarin" ~ "Warfarin"),
+         drug = relevel(as_factor(drug), ref = "All")) %>% 
+  filter(drug == "Adrenoceptor agonists" & 
+           datename == "Mar")
 
@@
 
-```{python}
+## Table 3
+
+```{python, composite-sd-function-py, eval=FALSE}
 
@@
 
-```{r, table-3-single-fcts}
+```{r, composite-sd-function-r, echo=FALSE}
+avg <- function(samples){
+  if (length(samples) >= 1){
+    return(sum(samples) / length(samples))
+  }
+  else{return(NaN)}
+}
+
+sample_SD <- function(samples){
+  # Input is an vector of samples; result is the standard deviation
+  mean = avg(samples)
+  sum_of_squared_deviations <-  0
+  sd <-  0
+  if(length(samples) >= 2){
+    for (datum in samples){
+      sum_of_squared_deviations <- 
+        sum_of_squared_deviations + ((datum - mean) * (datum - mean))
+      sd = sqrt(sum_of_squared_deviations / (length(samples)-1))
+    }
+      return(sd)
+  }
+}
+
+compositeSD <- function(means, SDs, ncounts){
+  #Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
+  # See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
+  #    Inputs are:
+  #      means, the array of group means
+  #      SDs, the array of group standard deviations
+  #      ncounts, number of samples in each group (can be scalar
+  #               if all groups have same number of samples)
+  #    Result is the overall standard deviation.
+  G <- length(means) # number of groups
+  if(G != length(SDs)) stop("Inconsistent lengths (means & sds")
+  if(!is.numeric(ncounts)) {(as.numeric(ncounts))}
+  if(G != length(ncounts)) stop("Inconsistent lengths (means & ncounts)")
+
+  # Calculate total number of samples, N, and grand mean, GM
+  N = sum(ncounts)  # total number of samples
+  if (N <= 1) stop(paste("Warning: only ", N, " samples, SD is incalculable"))
+  GM <-  0.0
+  for (i in 1:G){
+    GM <- GM + means[i] * ncounts[i]
+  }
+  GM <- GM / N  # grand mean
+
+  # calculate Error Sum of Squares
+  ESS <-  0.0
+  for (i in 1:G){
+    ESS <- ESS + ((SDs[i])**2) * (ncounts[i] - 1)
+  }
+
+  # calculate Total Group Sum of Squares
+  TGSS <-  0.0
+  for (i in 1:G){
+    TGSS <- TGSS + ((means[i]-GM)**2) * ncounts[i]
+  }
+
+  # calculate standard deviation as square root of grand variance
+  result <- sqrt((ESS+TGSS)/(N-1))
+  return(result)
+}
+
+samples = 0:9
+print(paste("avg =", avg(samples)))
+sd = sample_SD(samples)
+print(paste("sd =", sd))
+pt1 = c(0,1,2)
+pt2 = c(3,4)
+pt3 = c(5,6,7,8,9)
+means <- c(avg(pt1), avg(pt2), avg(pt3))
+SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
+ncounts <- c(length(pt1), length(pt2), length(pt3))
+sd2 <- compositeSD(means, SDs, ncounts)
+print(paste("sd2 =", sd2))
+
+samples = 0:8
+print(paste("avg =", avg(samples)))
+sd = sample_SD(samples)
+print(paste("sd =", sd))
+pt1 = c(0,1,2)
+pt2 = c(3,4,5)
+pt3 = c(6,7,8)
+means <- c(avg(pt1), avg(pt2), avg(pt3))
+SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
+ncounts <- c(length(pt1), length(pt2), length(pt3))
+sd2 <- compositeSD(means, SDs, ncounts)
+print(paste("sd2 =", sd2))
+
+```
+
+```{r, table-3-single-fcts, eval=FALSE}
 nat_data <- 
@@
   filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
-  summarise(n = sum(n),
-            sd = compositeSD(.mean, sd, rep(1,nrow(.))),
-            .mean = sum(.mean)
-  )
-
-best_model_discrep %>% 
-  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
   group_by(regional_unit) %>% 
   summarise(n = sum(n),
-            sd = compositeSD(.mean, sd, rep(1,5)),
-            .mean = sum(.mean),
-            ) %>% 
+            sd = compositeSD(.mean, sd, rep(1, length(sd))),
+            .mean = sum(.mean)) %>% 
   mutate(lb = .mean - 1.96*sd,
@@
          mean_pct_change = (100 * (n - .mean)/ .mean),
-         ub_mean_pct_change = (100 * (n - lb)/ lb),
-         ) %>% 
-  select(regional_unit, lb_mean_pct_change, mean_pct_change, ub_mean_pct_change)
-  ggplot(aes(x = regional_unit, y = mean_pct_change)) +
-  geom_col() +
-  geom_errorbar(aes(ymin = lb_mean_pct_change, ymax = ub_mean_pct_change))
+         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
+  select(regional_unit, lb_mean_pct_change, mean_pct_change, ub_mean_pct_change) %>% 
+  mutate(pct_change = paste0(printnum(mean_pct_change), 
+                             "[", printnum(lb_mean_pct_change), ",", 
+                             printnum(ub_mean_pct_change), "]")) %>% 
+  select(regional_unit, pct_change)
+
+best_model_discrep %>% 
+  mutate(prop = 100*(prop-1)) %>% 
+  pivot_wider(id_cols = regional_unit, names_from = datename, values_from = prop) %>% 
+  kable(digits = 2)
 ```
@@
 ```{r, table-3}
-# https://stats.stackexchange.com/questions/454120/how-can-i-calculate-uncertainty-of-the-mean-of-a-set-of-samples-with-different-u
-
-#
-# An iterative procedure to estimate mean and variance from a set of 
-# measurements `x` made with known measurement errors `sigma.i`.
-#
-var.wt <- function(x, sigma.i, thresh=1e-6, iter.max=1e4) { # Changed from values in example (1e-6, 200)
-  #
-  # To avoid giving undue weight to any subset, all SDs should be nonzero.
-  #
-  if (missing(sigma.i)) sigma.i <- rep(0, length(x)) # No measurement error
-  tol <- sum(abs(x)) * 1e-16
-  sigma.i[sigma.i <= 0] <- min(c(tol, sigma.i[sigma.i > 0])) / 2
-  #
-  # Initialize.
-  #
-  v <- var(x)
-  n <- length(x)
-  S <- mean(sigma.i^2) # Avoids recomputing this constant within the loop
-  for (i in 1:iter.max) {
-    w <- 1/(v + sigma.i^2); w <- w / sum(w)
-    m <- sum(x * w)
-    v.0 <- max(0, sum((x-m)^2 * w) * n / (n-1) - S) 
-    if (v <= v.0 * (1+thresh) && v.0 <= v * (1+thresh)) break
-    v <- v.0
-  }
-  if (i >= iter.max) warning("Maximum iteration count exceeded.")
-  list(Variance=v, Mean=m, Iterations=i)
-}
-
-sample_bound <- function(mean = ".mean", variance = "sd", 
-                         bound = c(.975, .5, .025), data = .){
-
-  # The data in the question.
-  #
-  x <- data[[mean]]
-  sigma.i <- data[[variance]]
-  (s <- var.wt(x, sigma.i))
-  #
-  # A parametric bootstrap.
-  #
-  n <- length(x)
-  sigma <- sqrt(s$Variance)
-  mu <- s$Mean
-  set.seed(17)
-  X <- replicate(5e3, {
-    y <- rnorm(n, mu, sigma)
-    epsilon <- rnorm(n, 0, sigma.i)
-    x <- y + epsilon
-    var.wt(x, sigma.i)
-  })
-  X <- matrix(unlist(X), 3)
-
-  return(quantile(X[2,], bound))
-}
-
 monthly_diffs <- 
@@
   group_by(drug, datename) %>% 
-  group_modify(~ {
-    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
-      tibble::enframe(name = "bound", value = "value")
-  }) %>% 
-  left_join(differences %>% 
-              select(drug, datename, .mean, sd, n) %>% 
-              na.omit() %>% 
-              group_by(drug, datename) %>% 
-              summarise(n = mean(n, na.rm = TRUE),
-                        .mean = mean(.mean, na.rm = TRUE),
-                        .group = "drop"), 
-            by = c("drug", "datename")) %>% 
-  mutate(p_change = 100*n / value) %>% # Difference as a proportion
-  pivot_wider(id_cols = c("drug", "datename", "n", ".mean"), 
-              names_from = "bound", values_from ="value") %>% 
-  mutate(across(`97.5%`:`2.5%`, .fns = ~(100*n/.x)-100)) %>% # Proportion as percentage change
-  rename("LB" = `97.5%`,
-         "Mean" = `50%`,
-         "UB" = `2.5%`) %>% 
+  summarise(n = sum(n),
+            sd = compositeSD(.mean, sd, rep(nrow(.),length(.mean))),
+            .mean = sum(.mean),
+            .groups = "drop") %>% 
+  mutate(lb = .mean - 1.96*sd,
+         ub = .mean + 1.96*sd,
+         lb_mean_pct_change = (100 * (n - ub)/ ub),
+         mean_pct_change = (100 * (n - .mean)/ .mean),
+         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
   mutate(datename = month(datename),
-         pct_change = paste0(printnum(Mean), 
-                             "[", printnum(LB), ",", printnum(UB), "]"))
+         pct_change = paste0(printnum(mean_pct_change), 
+                             "[", printnum(lb_mean_pct_change), ",", 
+                             printnum(ub_mean_pct_change), "]")) %>% 
+  pivot_wider(id_cols = drug, names_from = datename, values_from = pct_change)
 
-lockdown_diff_bounds <- 
-  differences %>% 
-  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
-  select(drug, datename, .mean, sd, n) %>% 
-  na.omit() %>% 
-  group_by(drug) %>% 
-  group_modify(~ {
-    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
-      tibble::enframe(name = "bound", value = "value")
-  })
-
-lockdown_diff_bounds_wide <- 
-  lockdown_diff_bounds %>% 
-  pivot_wider(id_cols = "drug", names_from = "bound", values_from = "value") %>% 
-  rename("lb" = `97.5%`,
-         "mean" = `50%`,
-         "ub" = `2.5%`) # returns mean quantity forecast per month in lockdown
-
-lockdown_diff_obs <- 
-  differences %>% 
-  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
-  select(drug, datename, .mean, sd, n, med) %>% 
-  na.omit() %>% 
-  group_by(drug) %>% 
-  summarise(n = mean(n, na.rm = FALSE),
-            .mean = mean(.mean, na.rm = FALSE),
-            med_med = median(med),
-            mean_med = mean(med),
-            .groups = "drop")
-
-left_join(lockdown_diff_obs, lockdown_diff_bounds_wide) %>% 
-  mutate(across(.mean:ub, ~(n-.x)/.x))
-
-###
 lockdown_diffs <- 
@@
   group_by(drug) %>% 
-  group_modify(~ {
-    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
-      tibble::enframe(name = "bound", value = "value")
-  }) %>% 
-  left_join(differences %>% 
-              filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
-              select(drug, datename, .mean, sd, n) %>% 
-              na.omit() %>% 
-              group_by(drug) %>% 
-              summarise(n = mean(n, na.rm = TRUE),
-                        .mean = mean(.mean, na.rm = TRUE),
-                        .groups = "drop"), 
-            by = c("drug")) %>% 
-  mutate(p_change = 100 * n / value) %>% # Difference as a proportion
-  pivot_wider(id_cols = c("drug", "n", ".mean"), 
-              names_from = "bound", values_from ="value") %>% 
-  mutate(across(`97.5%`:`2.5%`, .fns = ~(100*n/.x)-100)) %>% # Proportion as percentage change
-  rename("LB" = `97.5%`,
-         "Mean" = `50%`,
-         "UB" = `2.5%`) %>% 
-    mutate(lockdown = paste0(printnum(Mean), 
-                             "[", printnum(LB), ",", printnum(UB), "]"))
+  summarise(n = sum(n),
+            sd = compositeSD(.mean, sd, rep(1,length(.mean))),
+            .mean = sum(.mean),
+            .groups = "drop") %>% 
+  mutate(lb = .mean - 1.96*sd,
+         ub = .mean + 1.96*sd,
+         lb_mean_pct_change = (100 * (n - ub)/ ub),
+         mean_pct_change = (100 * (n - .mean)/ .mean),
+         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
+  mutate(pct_change = paste0(printnum(mean_pct_change), 
+                             "[", printnum(lb_mean_pct_change), ",", 
+                             printnum(ub_mean_pct_change), "]")) %>% 
+  select(drug, pct_change)
 
-lockdown_diffs %>% 
-  select(drug, lockdown) %>% 
-  left_join(monthly_diffs %>% 
-              pivot_wider(id_cols = "drug", names_from = "datename", 
-                          values_from = "pct_change"), by = "drug") %>% 
+left_join(lockdown_diffs, monthly_diffs) %>%
   kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
@@
 
-```{r}
+```{r, eval=FALSE}
+differences %>% 
+  filter(drug == "adreno" &
+           datename == yearmonth("2020 Mar")) %>% 
+  ggplot(aes(x = prop-1)) +
+  geom_histogram() +
+  geom_vline(aes(xintercept = mean(prop-1)))
+
+differences %>% 
+  select(drug, datename, .mean, sd, n) %>% 
+  na.omit() %>% 
+  group_by(drug, datename) %>% 
+  summarise(n = sum(n),
+            sd = compositeSD(.mean, sd, rep(nrow(.),length(.mean))),
+            .mean = sum(.mean),
+            .groups = "drop") %>% 
+  filter(drug == "adreno" &
+           datename == yearmonth("2020 Mar"))
+
+differences %>% 
+  filter(drug == "adreno" &
+           datename == yearmonth("2020 Mar")) %>% 
+  summarise(.mean = sum(.mean),
+            n = sum(n),
+            prop = mean(prop))
+
+differences %>% 
+  filter(drug == "adreno" &
+           datename == yearmonth("2020 Mar")) %>% 
+  mutate(prop_correct = if_else(prop == n/med, TRUE, FALSE))
+```
+
+```{r, eval=FALSE}
 differences %>% 
@@
 
-```{r}
+```{r, eval=FALSE}
 gp_extract %>% 
@@
   left_join(lockdown_diffs %>% 
-  select(drug, lockdown), by = "drug")
+  select(drug, pct_change), by = "drug")
 ```
 
-```{r, mean-change-plot}
-monthly_diffs %>% 
-  ggplot(aes(x = datename, group = drug)) +
-  geom_line(aes(y = Mean)) +
-  geom_ribbon(aes(ymin = LB, ymax = UB, fill = drug), alpha = .4) +
-  facet_wrap(~drug, scales = "free")
-
-```
-
-```{r}
+```{r, eval=FALSE}
 differences %>% 
@@
 ```
-
-# Discussion
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-
-<div custom-style='Title'>Appendix </div>
-
-\renewcommand{\appendixname}{Supplementary Material}
-\renewcommand{\thefigure}{SI\arabic{figure}} \setcounter{figure}{0}
-\renewcommand{\thetable}{SI\arabic{table}} \setcounter{table}{0}
-\renewcommand{\theequation}{SI\arabic{table}} \setcounter{equation}{0}
-
-# Forecasting
-
-### Forecasting models
-
-* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
-* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
-  * Simple methods
-      * Naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_T$
-      * Seasonal naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where m = seasonal period and k is the complete years in $T+h$
-  * STL Decomposition model [@Cleveland1990]
-    * Fixed and variable seasonality
-  * Time series linear model
-    * $y_t = \beta_0 + \beta_1x_t + \varepsilon_t$
-  * Autoregressive integrated moving average [ARIMA; @Box2015]
-    * Using a version of the Hyndman-Khandakar algorithm [@Hyndman2008]
-  * Exponential smoothing [@Holt2004; @Winters1960]
-    * Simple exponential smoothing
-    * Holt-Winters Additive Model [@Chatfield1978]
-  * Forecasting with Additive Switching of Seasonality, Trends and Exogenous Regressors [fasster; @R-fasster]
-    * State space model
-  * Prophet [@Taylor2018]
-  * Combination models [cf. @Bates1969; @Clemen1989; @Thomson2019]
-* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
-* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
-  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to keep run-times manageable)
-    * Only interested in one forecast horizon: six-months
-
-## All prescribing
-
-```{r, all-prescribing-model-accuracy-hist1, fig.cap="All prescribing, model accuracy", eval=FALSE}
-p1 <- all_prescribing_fable_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, RMSE, sort), y = RMSE)) +
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 90))
-
-p2 <- all_prescribing_fable_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, winkler, sort), y = winkler)) +
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 90))
-
-cowplot::plot_grid(p1, p2)
-```
-
-```{r, all-prescribing-cv-plot, fig.cap="All prescribing, best model CV fit", eval=FALSE}
-all_prescribing_best_cv_model <- 
-  augment(all_prescribing_fable_models) %>% 
-  as_tibble() %>% 
-  filter(.model == all_prescribing_best_model$.model)
-
-all_prescribing_best_cv_model %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = n/1e+06, colour = "Data")) +
-  geom_line(aes(y = .fitted/1e+06, colour = "Fitted", lty = as.factor(.id))) +
-  labs(lty = "CV iteration")
-```
-
-```{r, all-prescribing-forecast-plot, warning=FALSE, fig.cap="All prescribing, best model fit and forecast.", eval=FALSE}
-plan(cluster)
-all_prescribing %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
-  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
-            data = all_prescribing_covid_forecast) +
-  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
-                  fill = "Forecast"), alpha = .2,
-              data = all_prescribing_covid_forecast) +
-  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, 
-                  fill = "Forecast"), alpha = .3,
-              data = all_prescribing_covid_forecast) +
-  # geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
-  #           data = fableModels(all_prescribing_pre_cv19) %>% 
-  #             augment() %>% 
-  #             as_tibble() %>% 
-  #             filter(.model == all_prescribing_best_model$.model) %>% 
-  #             group_by(datename) %>% 
-  #             summarise(fitted = median(.fitted, na.rm = TRUE))) +
-  geom_vline(xintercept = ymd("2020-03-01"), lty = 3) +
-  coord_cartesian(xlim = c(dmy("01-11-2018"), dmy("01-08-2020"))) +
-  scale_x_yearmonth(breaks = "6 months", minor_breaks = "1 months")+
-  xlab("Date") +
-  ylab("Mean daily prescribing volume")
-
-plan(sequential)
-```
-
-```{r, all-prescribing-pct-change-plot, fig.cap="Percentage difference in all prescribing.", eval=FALSE}
-all_prescribing %>% 
-  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
-  ggplot(aes(x = datename, y = (100*n/med)-100)) +
-  geom_line() +
-  geom_hline(yintercept = 0, lty = 3)
-```
-
-## Excluded practices
-
-Table with a row for each drug and a column for each reason a practice could be excluded, with a total column at the end
-
-(a) missing any data in the COVID months, (b) more than 10% of the pre-COVID data (i.e., 6 months) missing, (c) significant changes to prescribing in the six months pre-COVID (e.g., changes that suggested the practice had closed), or (d) MAPE >50.
-
-```{r, excluded-practices-tab}
-months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
-            "2015 Jul","2015 Aug","2015 Sep","2015 Oct","2015 Nov","2015 Dec",
-            "2016 Jan","2016 Feb","2016 Mar","2016 Apr","2016 May","2016 Jun",
-            "2016 Jul","2016 Aug","2016 Sep","2016 Oct","2016 Nov","2016 Dec",
-            "2017 Jan","2017 Feb","2017 Mar","2017 Apr","2017 May","2017 Jun",
-            "2017 Jul","2017 Aug","2017 Sep","2017 Oct","2017 Nov","2017 Dec",
-            "2018 Jan","2018 Feb","2018 Mar","2018 Apr","2018 May","2018 Jun",
-            "2018 Jul","2018 Aug","2018 Sep","2018 Oct","2018 Nov","2018 Dec",
-            "2019 Jan","2019 Feb","2019 Mar","2019 Apr","2019 May","2019 Jun",
-            "2019 Jul","2019 Aug","2019 Sep","2019 Oct","2019 Nov","2019 Dec",
-            "2020 Jan","2020 Feb","2020 Mar","2020 Apr","2020 May","2020 Jun",
-            "2020 Jul","2020 Aug")
-
-monthlyPrescribing <- 
-  function(data){
-    data %>% 
-      janitor::clean_names() %>% 
-      mutate(datename = dmy(paste0("28-", datename)),
-             practice_id = as.character(practice_id)) %>% 
-      countRegional(practice_id, datename, quantity) %>% 
-      mutate(year = year(datename)) %>%
-      as_tibble() %>% 
-      inner_join(gp, 
-                 by = c("regional_unit" = "practice_id", "year")) %>% 
-      mutate(n = 1000*n/npat,
-             datename = yearmonth(datename),
-             regional_unit = as_factor(regional_unit)) %>% 
-      select(-c(npat, year)) %>% 
-      as_tsibble(index = datename, key = regional_unit) %>% 
-      fill_gaps()
-  }
-
-gpMissing <- 
-  function(data){
-    data %>% 
-      as_tibble() %>% 
-      pivot_wider(id_cols = regional_unit, names_from = datename,
-                  values_from = n, values_fill = NA) %>% 
-      select(all_of(months), everything()) %>% 
-      rowwise() %>% 
-      mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
-      group_by(regional_unit) %>% 
-      summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
-                miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
-      filter(miss_covid > 0 | miss_non_covid > 0) %>% 
-      mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))
-  }
-
-missRemove <- 
-  function(data){
-    data %>% 
-      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), TRUE, FALSE)) %>% 
-      summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
-                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE, FALSE)),
-                miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
-  }
-
-n_practices <- 
-  data_files %>% 
-  map(read_rds) %>% 
-  map(pluck("practice_id")) %>% 
-  map(unique) %>% 
-  map_dfr(length) %>% 
-  pivot_longer(cols = everything(), names_to = "drug", values_to = "n")
-
-missing_raw_data <- 
-  data_files %>% 
-  map(read_rds) %>% 
-  map(monthlyPrescribing) %>% 
-  map(gpMissing) %>% 
-  map_dfr(missRemove, .id = "drug")
-
-poor_forcasts <- 
-  cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE >= 50) %>% 
-  group_by(drug) %>% 
-  summarise(mape_over_50 = n())
-
-n_practices %>% 
-  left_join(missing_raw_data, by = "drug") %>% 
-  left_join(poor_forcasts, by = "drug") %>% 
-  rowwise() %>% 
-  mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
-         total_removed = miss_either + mape_over_50) %>% 
-  knitr::kable(booktabs = TRUE, linesep = "",
-               caption = "Summary of GP practices removed for each drug.") %>% 
-  footnote(general = "The total is not always equal to the row sum, as a single practice may be missing both data in covid months and more than 10\\% of data in the non-covid months, but will only be excluded once.",
-           threeparttable = TRUE)
-
-n_practices %>% 
-  summarise(sum(n))
-
-length(unique(gp$practice_id))
-```
-
-\renewcommand{\appendixname}{Supplementary Material}
-\renewcommand{\thefigure}{SI\arabic{figure}} \setcounter{figure}{0}
-\renewcommand{\thetable}{SI\arabic{table}} \setcounter{table}{0}
-\renewcommand{\theequation}{SI\arabic{table}} \setcounter{equation}{0}
-
-# Forecasting
-
-### Forecasting models
-
-* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
-* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
-  * Simple methods
-      * Naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_T$
-      * Seasonal naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where m = seasonal period and k is the complete years in $T+h$
-  * STL Decomposition model [@Cleveland1990]
-    * Fixed and variable seasonality
-  * Time series linear model
-    * $y_t = \beta_0 + \beta_1x_t + \varepsilon_t$
-  * Autoregressive integrated moving average [ARIMA; @Box2015]
-    * Using a version of the Hyndman-Khandakar algorithm [@Hyndman2008]
-  * Exponential smoothing [@Holt2004; @Winters1960]
-    * Simple exponential smoothing
-    * Holt-Winters Additive Model [@Chatfield1978]
-  * Forecasting with Additive Switching of Seasonality, Trends and Exogenous Regressors [fasster; @R-fasster]
-    * State space model
-  * Prophet [@Taylor2018]
-  * Combination models [cf. @Bates1969; @Clemen1989; @Thomson2019]
-* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
-* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
-  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to keep run-times manageable)
-    * Only interested in one forecast horizon: six-months
-
-## All prescribing
-
-```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy", eval=FALSE}
-p1 <- all_prescribing_fable_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, RMSE, sort), y = RMSE)) +
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 90))
-
-p2 <- all_prescribing_fable_fits %>% 
-  na.omit() %>% 
-  ggplot(aes(x = reorder(.model, winkler, sort), y = winkler)) +
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 90))
-
-cowplot::plot_grid(p1, p2)
-```
-
-```{r, all-prescribing-cv-plot1, fig.cap="All prescribing, best model CV fit", eval=FALSE}
-all_prescribing_best_cv_model <- 
-  augment(all_prescribing_fable_models) %>% 
-  as_tibble() %>% 
-  filter(.model == all_prescribing_best_model$.model)
-
-all_prescribing_best_cv_model %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = n/1e+06, colour = "Data")) +
-  geom_line(aes(y = .fitted/1e+06, colour = "Fitted", lty = as.factor(.id))) +
-  labs(lty = "CV iteration")
-```
-
-```{r, all-prescribing-forecast-plot1, warning=FALSE, fig.cap="All prescribing, best model fit and forecast.", eval=FALSE}
-plan(cluster)
-all_prescribing %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
-  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
-            data = all_prescribing_covid_forecast) +
-  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
-                  fill = "Forecast"), alpha = .2,
-              data = all_prescribing_covid_forecast) +
-  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, 
-                  fill = "Forecast"), alpha = .3,
-              data = all_prescribing_covid_forecast) +
-  # geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
-  #           data = fableModels(all_prescribing_pre_cv19) %>% 
-  #             augment() %>% 
-  #             as_tibble() %>% 
-  #             filter(.model == all_prescribing_best_model$.model) %>% 
-  #             group_by(datename) %>% 
-  #             summarise(fitted = median(.fitted, na.rm = TRUE))) +
-  geom_vline(xintercept = ymd("2020-03-01"), lty = 3) +
-  coord_cartesian(xlim = c(dmy("01-11-2018"), dmy("01-08-2020"))) +
-  scale_x_yearmonth(breaks = "6 months", minor_breaks = "1 months")+
-  xlab("Date") +
-  ylab("Mean daily prescribing volume")
-
-plan(sequential)
-```
-
-```{r, all-prescribing-pct-change-plot1, fig.cap="Percentage difference in all prescribing.", eval=FALSE}
-all_prescribing %>% 
-  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
-  ggplot(aes(x = datename, y = (100*n/med)-100)) +
-  geom_line() +
-  geom_hline(yintercept = 0, lty = 3)
-```
-
-## Excluded practices
-
-Table with a row for each drug and a column for each reason a practice could be excluded, with a total column at the end
-
-(a) missing any data in the COVID months, (b) more than 10% of the pre-COVID data (i.e., 6 months) missing, (c) significant changes to prescribing in the six months pre-COVID (e.g., changes that suggested the practice had closed), or (d) MAPE >50.
-
-```{r, excluded-practices-tab1}
-months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
-            "2015 Jul","2015 Aug","2015 Sep","2015 Oct","2015 Nov","2015 Dec",
-            "2016 Jan","2016 Feb","2016 Mar","2016 Apr","2016 May","2016 Jun",
-            "2016 Jul","2016 Aug","2016 Sep","2016 Oct","2016 Nov","2016 Dec",
-            "2017 Jan","2017 Feb","2017 Mar","2017 Apr","2017 May","2017 Jun",
-            "2017 Jul","2017 Aug","2017 Sep","2017 Oct","2017 Nov","2017 Dec",
-            "2018 Jan","2018 Feb","2018 Mar","2018 Apr","2018 May","2018 Jun",
-            "2018 Jul","2018 Aug","2018 Sep","2018 Oct","2018 Nov","2018 Dec",
-            "2019 Jan","2019 Feb","2019 Mar","2019 Apr","2019 May","2019 Jun",
-            "2019 Jul","2019 Aug","2019 Sep","2019 Oct","2019 Nov","2019 Dec",
-            "2020 Jan","2020 Feb","2020 Mar","2020 Apr","2020 May","2020 Jun",
-            "2020 Jul","2020 Aug")
-
-monthlyPrescribing <- 
-  function(data){
-    data %>% 
-      janitor::clean_names() %>% 
-      mutate(datename = dmy(paste0("28-", datename)),
-             practice_id = as.character(practice_id)) %>% 
-      countRegional(practice_id, datename, quantity) %>% 
-      mutate(year = year(datename)) %>%
-      as_tibble() %>% 
-      inner_join(gp, 
-                 by = c("regional_unit" = "practice_id", "year")) %>% 
-      mutate(n = 1000*n/npat,
-             datename = yearmonth(datename),
-             regional_unit = as_factor(regional_unit)) %>% 
-      select(-c(npat, year)) %>% 
-      as_tsibble(index = datename, key = regional_unit) %>% 
-      fill_gaps()
-  }
-
-gpMissing <- 
-  function(data){
-    data %>% 
-      as_tibble() %>% 
-      pivot_wider(id_cols = regional_unit, names_from = datename,
-                  values_from = n, values_fill = NA) %>% 
-      select(all_of(months), everything()) %>% 
-      rowwise() %>% 
-      mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
-      group_by(regional_unit) %>% 
-      summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
-                miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
-      filter(miss_covid > 0 | miss_non_covid > 0) %>% 
-      mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))
-  }
-
-missRemove <- 
-  function(data){
-    data %>% 
-      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), TRUE, FALSE)) %>% 
-      summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
-                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE, FALSE)),
-                miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
-  }
-
-n_practices <- 
-  data_files %>% 
-  map(read_rds) %>% 
-  map(pluck("practice_id")) %>% 
-  map(unique) %>% 
-  map_dfr(length) %>% 
-  pivot_longer(cols = everything(), names_to = "drug", values_to = "n")
-
-missing_raw_data <- 
-  data_files %>% 
-  map(read_rds) %>% 
-  map(monthlyPrescribing) %>% 
-  map(gpMissing) %>% 
-  map_dfr(missRemove, .id = "drug")
-
-poor_forcasts <- 
-  cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE >= 50) %>% 
-  group_by(drug) %>% 
-  summarise(mape_over_50 = n())
-
-n_practices %>% 
-  left_join(missing_raw_data, by = "drug") %>% 
-  left_join(poor_forcasts, by = "drug") %>% 
-  rowwise() %>% 
-  mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
-         total_removed = miss_either + mape_over_50) %>% 
-  knitr::kable(booktabs = TRUE, linesep = "",
-               caption = "Summary of GP practices removed for each drug.") %>% 
-  footnote(general = "The total is not always equal to the row sum, as a single practice may be missing both data in covid months and more than 10\\% of data in the non-covid months, but will only be excluded once.",
-           threeparttable = TRUE)
-
-n_practices %>% 
-  summarise(sum(n))
-
-length(unique(gp$practice_id))
-```
-
-## Cross-validated model accuracy
-
-```{r, cv-model-accuracy-by-drug-tab}
-cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE < 50) %>% 
-  group_by(drug) %>% 
-  summarise(n_practice_retained = n(),
-            mape_mean = mean(MAPE),
-            mape_sd = sd(MAPE)) %>% 
-  kable(caption = "Accuaracy of cross-validated models retained for forecasting.",
-               digits = 2)
-```
-
-```{r, individual-drug-accuracy-plot, fig.cap="Accuracy of best model for each regional unit by drug, as measured by mean absoloute percentage error (MAPE). Models with MAPE > 50 have been removed."}
-cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE < 50) %>% 
-  mutate(drug = as.factor(drug),
-         drug = relevel(as_factor(drug), ref = "all_drugs")) %>% 
-  ggplot(aes(x = drug, y = MAPE, col = drug)) +
-  geom_violin() +
-  geom_jitter(alpha = .1) +
-  xlab("Medicine group")+
-  theme(legend.position = "none")
-```
-
-```{r best-cv-model-type, fig.cap="Performance by model type."}
-cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE < 50) %>% 
-  ggplot(aes(x = as.factor(.model))) +
-  geom_bar() +
-  xlab("Model") +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-## Warfarin
-
-```{r, oac-gen-trend, eval = FALSE}
-oac <- read_rds(data_files[9])
-
-oac %>% 
-  mutate(warfarin = if_else(bnfchem == "0208020V0", TRUE, FALSE)) %>% 
-  group_by(warfarin, datename) %>% 
-  summarise(quantity = sum(quantity), .groups = "drop") %>% 
-  pivot_wider(id_cols = datename, values_from = quantity, names_from = warfarin) %>% 
-  mutate(prop = `TRUE` / (`TRUE` + `FALSE`),
-         datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
-  tsibble() %>% 
-  autoplot(prop) +
-  xlab("Date") +
-  ylab("Warfarin as a proportion of all oral anticoagulant prescribing")
-
-```
-
-\newpage
-
-## SM References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage

### 2021-09-09 writing/appendix_a.Rmd

@@
 - ../references/library.bib
-output: pdf_document
-ouput: pdf_document
+output:
+  pdf_document: default
+  html_document:
+    df_print: paged
+ouput: html_document
 ---
@@
 ## Packages
-# devtools::install_github("https://github.com/w-hardy/serCymruTools")
+# devtools::install_github("w-hardy/serCymruTools")
+library(plyr); library(dplyr)
+library(rms)
+library(nlme)
 library(tidyverse)
@@
 library(tsibble)
-library(rstan) # needed to load prophet
-library(prophet)
 library(fable)
-library(fable.prophet)
-library(fasster)
 library(feasts)
@@
 library(papaja)
+library(fuzzyjoin)
+library(ggbiplot)
 
@@
          N = NULL,
-         practice_id = as.character(practiceid)) %>% 
+         practice_id = as.character(practiceid),
+         hboard = case_when(hboard == "W11000023" ~ 
+                              "Betsi Cadwaladr",
+                            hboard == "W11000024" ~ 
+                              "Powys",
+                            hboard == "W11000025" ~ 
+                              "Hywel Dda",
+                            hboard == "W11000028" ~ 
+                              "Aneurin Bevan",
+                            hboard == "W11000029" ~ 
+                              "Cardiff and Vale",
+                            hboard == "W11000030" ~ 
+                              "Cwm Taf Morgannwg",
+                            hboard == "W11000031" ~ 
+                              "Swansea Bay")) %>% 
   ungroup() %>% 
   janitor::clean_names() %>% 
-  select(practice_id, year, npat)
+  mutate(dispensing = case_when(tolower(dispensing) == "yes" ~ TRUE, 
+                                tolower(dispensing) == "no" ~ FALSE),
+         hboard = as.factor(hboard))
 
@@
 
+plan(cluster)
 differences <- 
-  map_dfr(.x = differences_files,
+  furrr::future_map_dfr(.x = differences_files,
                         .f = ~read_rds(paste0("../data/differences/", .x)),
                         .id = "drug") %>% 
-  mutate(drug = relevel(as_factor(drug), ref = "all_drugs"))
+  mutate(drug = relevel(as_factor(drug), ref = "quant_all_drugs"),
+         drug = str_remove_all(drug, "ddd_"),
+         drug = str_remove_all(drug, "quant_"),
+         drug = str_remove_all(drug, "_ddd")) %>% 
+  filter(regional_unit != "W95636") #https://abuhb.nhs.wales/news/news/important-information-regarding-lansbury-surgery-caerphilly/
+
+plan(sequential)
 
@@
 set.seed(32)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE, echo = FALSE)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = FALSE, 
+                      echo = FALSE, fig.pos = 'H')
 kable_opts <- options(knitr.kable.NA = "-")
@@
 
-## Reproducability and code
+## GP PCA
 
-We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.
+```{r, gp-pca, fig.cap="Variance of QoF variables explained by individual principal components (lines) with cumulative proportion of variance explained (text)."}
+#### Data ####
+gp_2020 <- filter(gp, year == 2020)
 
-## Forecasting
+#### Functions ####
+# Add cumulative fraction of variance explained
+addScree <- function(x, npcs=min(10, length(x$sdev)),
+                     plotv = FALSE,
+                     col = 1, offset = .8, adj = 0, pr = FALSE){
+  vars <- x$sdev^2
+  cumv <- cumsum(vars)/sum(vars)
+  if(pr) print(cumv)
+  text(1:npcs, vars[1:npcs] + offset*par("cxy")[2],
+       as.character(round(cumv[1:npcs], 2)),
+       srt = 45, adj = adj, cex = .65, xpd = NA, col = col)
+}
 
-### Forecasting models
+#### Analysis ####
+gp_pca <- 
+  prcomp(select(gp_2020, chd:flu), center = TRUE, scale. = TRUE)
 
-* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
-* We used the `fable` [@R-fable] and `fasster` [@R-fasster] packages to conduct the time series analyses.
-  * Simple methods
-      * Naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_T$
-      * Seasonal naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where $m$ = seasonal period and $k$ is the complete years in $T+h$
-  * STL Decomposition model [@Cleveland1990]
-    * Fixed and variable seasonality
-  * Time series linear model
-    * $y_t = \beta_0 + \beta_1x_t + \varepsilon_t$
-  * Autoregressive integrated moving average [ARIMA; @Box2015]
-    * Using a version of the Hyndman-Khandakar algorithm [@Hyndman2008]
-  * Exponential smoothing [@Holt2004; @Winters1960]
-    * Simple exponential smoothing
-    * Holt-Winters Additive Model [@Chatfield1978]
-  * Forecasting with Additive Switching of Seasonality, Trends and Exogenous Regressors [fasster; @R-fasster]
-    * State space model
-  * Combination models [cf. @Clemen1989; @Thomson2019]
-* Prescribing quantities were log transformed and the forecasts use median estimates of prescribing to reduce bias that back transformation would introduce when using the mean
-* Using January 2015 to December 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
-  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to keep run-times manageable)
-    * Only interested in one forecast horizon: six-months
+plot(gp_pca, type = "lines", main = " ")
+addScree(gp_pca)
+abline(h = 1, col = "blue")
+
+```
+
+```{r, gp-pca-direction, fig.cap="QoF disease register loadings on PC1 and PC2"}
+ggbiplot(gp_pca, ellipse = TRUE, groups = gp_2020$hboard, obs.scale = 1, 
+         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)
+
+gp_2020 <- 
+  gp_2020 %>% 
+  left_join(bind_cols(practice_id = gp_2020$practice_id, gp_pca$x), 
+            by = "practice_id") %>% 
+  select(regional_unit = practice_id, everything(),
+         -c(practiceid, county, cluster, postcode, lsoacode, easting, northing,
+            chd:flu, PC4:PC18, year))
+```
 
@@
 
-(a) missing any data in the COVID months, (b) more than 10% of the pre-COVID data (i.e., 6 months) missing, (c) significant changes to prescribing in the six months pre-COVID (e.g., changes that suggested the practice had closed), or (d) MAPE >50.
+(a) missing any data in the COVID months, (b) more than 10% of the pre-COVID data (i.e., 6 months) missing, or (c) MAPE >50.
 
-```{r, excluded-practices-tab}
+```{r, excluded-practices-tab, eval=TRUE}
 months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
@@
       as_tibble() %>% 
-      inner_join(gp, 
+      inner_join(gp %>% 
+                   select(practice_id, year, npat), 
                  by = c("regional_unit" = "practice_id", "year")) %>% 
@@
     data %>% 
-      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), TRUE, FALSE)) %>% 
+      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), 
+                              TRUE, FALSE)) %>% 
       summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
-                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE, FALSE)),
+                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE,
+                                                FALSE)),
                 miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
@@
 
+plan(cluster)
+
+full_data <- 
+  data_files[c(1:10,12)] %>% 
+  furrr::future_map(read_rds)
+
 n_practices <- 
-  data_files %>% 
-  map(read_rds) %>% 
+  full_data %>% 
   map(pluck("practice_id")) %>% 
@@
 
+missing_gp  <-
+  full_data %>% 
+  map(pluck("practice_id")) %>% 
+  map(unique) %>% 
+  map_dfr(~length(.)-sum(. %in% gp$practice_id), .id = "drug") %>% 
+  pivot_longer(cols = everything(), names_to = "drug", 
+               values_to = "missing_gp")
+
 missing_raw_data <- 
-  data_files %>% 
-  map(read_rds) %>% 
-  map(monthlyPrescribing) %>% 
-  map(gpMissing) %>% 
-  map_dfr(missRemove, .id = "drug")
+  full_data %>% 
+  furrr::future_map(monthlyPrescribing) %>% 
+  furrr::future_map(gpMissing) %>% 
+  furrr::future_map_dfr(missRemove, .id = "drug")
 
@@
   summarise(mape_over_50 = n())
+plan(sequential)
 
 n_practices %>% 
+  left_join(missing_gp, by = "drug") %>% 
   left_join(missing_raw_data, by = "drug") %>% 
   left_join(poor_forcasts, by = "drug") %>% 
+  mutate(drug = str_remove_all(drug, "ddd_"),
+         drug = str_remove_all(drug, "quant_"),
+         drug = str_remove_all(drug, "_ddd"),
+         drug = relevel(as_factor(drug), ref = "all_drugs")) %>%
   rowwise() %>% 
   mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
-         total_removed = miss_either + mape_over_50) %>% 
+         total_removed = missing_gp + miss_either + mape_over_50, 
+         n_rem = n - total_removed) %>% 
   knitr::kable(booktabs = TRUE, linesep = "", 
+               col.names = c("drug", "n", "gp", "covid", "10_non_covid",
+                             "either", "mape >50", "total", "remain"),
                caption = "Summary of GP practices removed for each drug.") %>% 
@@
 ```
+
+```{r, big-discrepacies, eval=FALSE}
+drugs <- unique(differences$drug)
+
+bigDiscreps <- function(x){
+  message(x)
+
+  big_discreps2 <- 
+    differences %>% 
+    filter(drug == x) %>% 
+    filter(prop <.3| prop > 2) %>% 
+    group_by(regional_unit) %>% 
+    count()
+
+  differences %>% 
+    filter(drug == x) %>% 
+    filter(regional_unit %in% big_discreps2$regional_unit) %>% 
+    mutate(uid = paste(x, regional_unit)) %>% 
+    ggplot(aes(x = datename, col = as.factor(regional_unit))) +
+    geom_line(aes(y = med), lty = 1) +
+    geom_line(aes(y = n), lty = 2) +
+    facet_wrap(~uid, scales = "free") +
+    theme(legend.position = "none")
+}
+
+map(.x = drugs, .f = ~bigDiscreps(.x))
+
+```
+
+## Forecasting
+
+### Forecasting models
+
+* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
+* We used the `fable` [@R-fable] and `fasster` [@R-fasster] packages to conduct the time series analyses.
+  * Time series linear model
+    * $y_t = \beta_0 + \beta_1x_t + \varepsilon_t$
+  * Simple methods
+      * Naïve (with and without drift)
+        * $\hat{y}_{T+h|T} = y_T$
+      * Seasonal naïve (with and without drift)
+        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where $m$ = seasonal period and $k$ is the complete years in $T+h$
+  * Seasonal and Trend decomposition using Loess (STL) model [@Cleveland1990]
+    * Fixed and variable seasonality
+  * Autoregressive integrated moving average [ARIMA; @Box2015]
+    * Using a version of the Hyndman-Khandakar algorithm [@Hyndman2008]
+  * Exponential smoothing [@Holt2004; @Winters1960]
+    * Simple exponential smoothing
+    * Holt-Winters Additive Model [@Chatfield1978]
+  * Forecasting with Additive Switching of Seasonality, Trends and Exogenous Regressors [fasster; @R-fasster]
+    * State space model
+  * Combination models [cf. @Clemen1989; @Thomson2019]
+    * Forecasts that are made by combining models are often more accurate than those of the individual forecasts and often a simple average can significantly improve forecast accuracy.
+
+* Prescribing quantities were log transformed and the forecasts use median estimates of prescribing to reduce bias that back transformation would introduce when using the mean
+* Using January 2015 to December 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
+  * Started with 36 months of data, used an 8-month horizon as this was the horizon we would be using for the forecasts, 1-month step
+    * Only interested in one forecast horizon: eight-months
+
+```{r, time-series-model-tab}
+
+readxl::read_xlsx("time_series_models.xlsx") %>% 
+    knitr::kable(booktabs = TRUE, linesep = "",
+               caption = "Description of time series models used.")
+
+```
+
+## Reproducability and code
+
+We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.
 
@@
   map_dfr(.id = "drug", .f = read_rds) %>% 
+  mutate(drug = str_remove_all(drug, "ddd_"),
+         drug = str_remove_all(drug, "quant_"),
+         drug = str_remove_all(drug, "_ddd"),
+         drug = relevel(as_factor(drug), ref = "all_drugs")) %>%
   rankModels() %>% 
@@
 
-```{r, individual-drug-accuracy-plot, fig.cap="Accuracy of best model for each regional unit by drug, as measured by mean absoloute percentage error (MAPE). Models with MAPE > 50 have been removed."}
+```{r, individual-drug-accuracy-plot, fig.cap="Accuracy of best model for each regional unit by drug, as measured by mean absoloute percentage error (MAPE).
+Models with MAPE > 50 have been removed.
+ACEi = ACE inhibitors, BAA = Beta~2~ adrenoceptor agonists, HCQ = Hydroxycholoroquine."}
+
+plan(cluster)
 cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
+  furrr::future_map_dfr(.id = "drug", .f = read_rds) %>% 
+  mutate(drug = str_remove_all(drug, "ddd_"),
+         drug = str_remove_all(drug, "quant_"),
+         drug = str_remove_all(drug, "_ddd"),
+         drug = case_when(drug == "all_drugs" ~ "All",
+                          drug == "ace" ~ "ACEi",
+                          drug == "adreno" ~ "BAA",
+                          drug == "cortico" ~ "Inhaled \ncortico",
+                          drug == "hcq" ~ "HCQ",
+                          drug == "nsaid" ~ "NSAIDs",
+                          drug == "oral_contra" ~ "Oral\ncontra",
+                          drug == "paracet" ~ "Paracet",
+                          drug == "ssri" ~ "SSRIs",
+                          drug == "vitd" ~ "Vit D",
+                          drug == "warfarin" ~ "Warfarin"),
+         drug = relevel(as_factor(drug), ref = "All")) %>%
   rankModels() %>% 
@@
   filter(MAPE < 50) %>% 
-  mutate(drug = as.factor(drug),
-         drug = relevel(as_factor(drug), ref = "all_drugs")) %>% 
   ggplot(aes(x = drug, y = MAPE, col = drug)) +
@@
   geom_jitter(alpha = .1) +
-  xlab("Medicine group")+
+  xlab("Medicine group") +
   theme(legend.position = "none")
+
 ```
@@
 ```{r best-cv-model-type, fig.cap="Performance by model type."}
+plan(cluster)
 cv_model_files %>% 
@@
   ggplot(aes(x = as.factor(.model))) +
-  geom_bar() +
+  geom_bar(aes(fill = as.factor(drug)), col = "black", size = .25) +
   theme(axis.text.x = element_text(angle = 90))
+plan(sequential)
+```
+
+---
+
+## GEE results
+
+```{r, gee-analysis, eval = FALSE}
+ace <- 
+  differences %>% 
+  filter(drug == "ddd_ace") %>% 
+  group_by(datename) %>% 
+  slice(1:100, .preserve = TRUE) %>% 
+  left_join(filter(gp, year == 2020), by = c("regional_unit" = "practice_id")) %>% 
+  mutate(time_order = as.numeric(as.factor(datename)))
+
+ace_gee <- geeglm(prop ~ wimd2019, data = ace, id = regional_unit, waves = time_order, corstr = "ar1")
+
+summary(ace_gee)
+```
+
+## GLS Results
+
+```{r, gls-functions}
+#### Prep GLS data ####
+glsData <- function(data){
+  df <- 
+    differences %>% 
+    filter(drug == data) %>% 
+    mutate(time_order = as.numeric(as.factor(datename)),
+           pct_change = 100*(prop - 1)) %>% 
+    select(c(regional_unit, time_order, pct_change))
+
+  baseline <- subset(df, time_order == 2, -time_order)
+  baseline <- upData(baseline, rename = c(pct_change = "prop0"), print = FALSE)
+  followup <- subset(df, time_order > 2)
+  both <- merge(baseline, followup, by = c("regional_unit"))
+
+  #### Join GP and GLS data ####
+  both <- 
+    both %>% 
+    left_join(gp_2020, by = "regional_unit") %>% 
+    mutate(gp_load = npat / ngp)
+
+  dd <- datadist(both)
+  options(datadist = "dd")
+
+  return(both)
+}
+
+#### GLS Analysis function ####
+bestGLS <- function(data){
+  cp <- list(corAR1, corExp, corCompSymm, corLin, corGaus, corSpher)
+  z <- vector("list", length(cp))
+
+  ### Fit models
+  for(k in 1:length(cp)){
+    z[[k]] <- gls(pct_change ~ dispensing + hboard + rcs(time_order, 4) + rcs(prop0, 4) + 
+                    rcs(wimd2019, 4) + rcs(p_male, 4) + rcs(pm_65, 4) + 
+                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + rcs(ngp, 4) + 
+                    rcs(gp_load, 4),
+                  data = data,
+                  correlation = cp[[k]](form = ~time_order | regional_unit))
+  }
+
+  ### Select best model
+  anova(z[[1]], z[[2]], z[[3]], z[[4]], z[[5]], z[[6]])
+  best_model_aic <- 
+    anova(z[[1]], z[[2]], z[[3]], z[[4]], z[[5]], z[[6]]) %>% 
+    select(-call) %>% 
+    tibble() %>% 
+    arrange(AIC) %>% 
+    head(1) %>% 
+    .$Model
+
+  ### Fit best model
+  a <-  Gls(pct_change ~ dispensing + hboard + rcs(time_order, 4) + 
+              rcs(prop0, 4) + rcs(wimd2019, 4) + rcs(p_male, 4) + rcs(pm_65, 4) +               rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4)+ rcs(ngp, 4) + 
+                    rcs(gp_load, 4),
+            data = data, B = 1000, 
+            correlation = cp[[best_model_aic]](form = ~time_order | regional_unit))
+
+  return(a)
+}
+
+#### GLS Assumption Checking ####
+glsAssump <- function(model, data){
+  data$resid <- r <- resid(model); data$fitted <- fitted(model)
+  y1 <- ylab("Residuals")
+  p1 <- ggplot(data, aes(x = fitted, y = resid)) + geom_point() + 
+    facet_grid(~hboard) + y1
+  p2 <- ggplot(data, aes(x = prop0, y = resid)) + geom_point() + y1
+  p3 <- ggplot(data, aes(x = time_order, y = resid)) + y1 + 
+    stat_summary(fun.data = "mean_sdl", geom = "smooth")
+  p4 <- ggplot(data, aes(sample = resid)) + stat_qq() + 
+    geom_abline(intercept = mean(r), slope = sd(r)) + y1
+
+  gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
+}
+
+#### GLS Estimated Effects ####
+glsEffects <- function(model, name){
+  p1 <- ggplot(Predict(model, time_order, dispensing, conf.int = FALSE),
+               adj.subitle = FALSE, legend.position = "top", )
+  p2 <- ggplot(Predict(model, prop0), adj.subtitle = FALSE)
+  p3 <- ggplot(Predict(model, pm_65), adj.subtitle = FALSE)
+  p4 <- ggplot(Predict(model, p_male), adj.subtitle = FALSE)
+  p5 <- ggplot(Predict(model, wimd2019), adj.subtitle = FALSE)
+  p6 <- ggplot(Predict(model, PC1), adj.subtitle = FALSE)
+  p7 <- ggplot(Predict(model, PC2), adj.subtitle = FALSE)
+  p8 <- ggplot(Predict(model, PC3), adj.subtitle = FALSE)
+  p9 <- ggplot(Predict(model, hboard), adj.subtitle = FALSE)
+  p10 <- ggplot(Predict(model, ngp), adj.subtitle = FALSE)
+  p11 <- ggplot(Predict(model, gp_load), adj.subtitle = FALSE)
+  gridExtra::grid.arrange(p1,p2,p3,p4, ncol = 2)
+  gridExtra::grid.arrange(p5,p6,p7,p8, ncol = 2)
+  gridExtra::grid.arrange(p9,p10,p11, ncol = 2)
+
+  capture.output(print(model))[16:53] %>% 
+    read_table(., col_names = c(" ", "Coef", "S.E.", "t", "Pr(>|t|)")) %>% 
+    kable(booktabs = TRUE, linesep = "", digits = 2,
+               caption = paste(name, "coefficents")) %>% 
+    kable_styling(bootstrap_options = "striped") %>% 
+    print()
+
+  plot(anova(model))
+
+  model %>% 
+    anova() %>% 
+    kable(booktabs = TRUE, linesep = "", digits = 2,
+          caption = paste(name, "anova")) %>% 
+    add_indent(positions = c(4,6,8,10,12,14,16,18,20,22)) %>% 
+    kable_styling(bootstrap_options = "striped") %>% 
+    print()
+
+  # time_order and prop0 dominate so not useful
+  # n <- nomogram(model, abbrev = TRUE)
+  # plot(n, )
+  cat("\n\n")
+}
+
+drugs <- unique(differences$drug)
+
+gls_analysis_fig_cap <- 
+  paste(paste(drugs, "assumptions"), paste(drugs, "effects1"), 
+        paste(drugs, "effects2"), paste(drugs, "effects3"), 
+        paste(drugs, "anova"), paste(drugs, "nomogram"))
+
+gls_analysis_fig_cap <- NULL
+for (i in 1:length(drugs)) {
+  gls_analysis_fig_cap <- 
+    c(gls_analysis_fig_cap, 
+      paste(drugs[i], c("assumptions", "effects1", "effects2", "effects3",
+                        "anova", "nomogram")))
+}
+
+```
+
+```{r, gls-analysis, results="asis", fig.cap=gls_analysis_fig_cap}
+drugs <- unique(differences$drug)
+
+best_models <- list()
+
+for(i in drugs){
+  cat("###", (i), "\n\n")
+  gls_data <- glsData(i)
+  dd <- datadist(gls_data)
+  options(datadist = "dd")
+  best_gls <- bestGLS(gls_data)
+  cat("####", "Assumptions\n\n")
+  glsAssump(best_gls, gls_data)
+  cat("\n\n")
+  cat("####", "Effects\n\n")
+  glsEffects(best_gls, i)
+  rm(dd)
+  cat("\n\n")
+  best_models[[i]] <- 
+    best_gls
+}
+
+best_model_coefs <- 
+  best_models %>% 
+  map(~capture.output(print(.))[16:53] %>% 
+        read_table(col_names = c("Coef", "Est", "S.E.", "t", "Pr(>|t|)"))) %>%
+  map_dfr(as_tibble, .id = "drug")
+
+best_model_corr <- 
+  best_models %>% 
+  map(~list(str = capture.output(print(.))[55],
+            measure = capture.output(print(.))[58],
+            value = capture.output(print(.))[59]))
+```
+
+```{r, gls-coef-tab-signif, results="asis"}
+
+best_model_coefs %>% 
+  mutate(`Pr(>|t|)` = as.numeric(str_remove_all(string = `Pr(>|t|)`, "<")),
+         Est = case_when(`Pr(>|t|)` < .05 ~ 
+                           paste0(printnum(Est, digits = 2), "*"),
+                         `Pr(>|t|)` >= .05 ~
+                           as.character(printnum(Est, digits = 2, format = "f")))) %>%
+  kable(booktabs = TRUE, linesep = "", digits = 2, align = "r",
+        caption = "Summary of GLS coefficents") %>% 
+  kable_styling(bootstrap_options = "striped") %>% 
+  landscape() %>% 
+  print()
+```
+
+```{r, gls-coef-tab-ci, results="asis"}
+
+best_model_coefs %>% 
+  mutate(`Pr(>|t|)` = as.numeric(str_remove_all(string = `Pr(>|t|)`, "<")),
+         Est = paste0(printnum(Est, digits = 2), "[", 
+                      printnum(Est - 1.96*S.E., digits = 2), ",", 
+                      printnum(Est + 1.96*S.E., digits = 2), "]")) %>% 
+  pivot_wider(id_cols = Coef, names_from = drug, values_from = Est) %>% 
+  kable(booktabs = TRUE, linesep = "", digits = 2, align = "r",
+        caption = "Summary of GLS coefficents [95% CI]") %>% 
+  kable_styling(bootstrap_options = "striped") %>% 
+  landscape() %>% 
+  print()
+```
+
+```{r, gls-coef-plot}
+coefs <- unique(best_model_coefs$Coef)
+
+coef_plot_order <- 
+  list(coefs[1:2],coefs[3:8], coefs[9:20], coefs[21:32],coefs[33:38])
+
+for (i in 1:length(coef_plot_order)) {
+  p <- best_model_coefs %>% 
+    filter(Coef %in% coef_plot_order[[i]]) %>% 
+    ggplot(aes(y = drug, group = as.factor(str_count(Coef, "'")), 
+                                           col = drug)) +
+    geom_point(aes(x = Est, shape = as.factor(str_count(Coef, "'"))), 
+               position = position_dodge(width=.75)) +
+    geom_errorbarh(aes(xmin = Est - 1.96* S.E., xmax = Est + 1.96* S.E.,
+                       height = 0),
+                   position = position_dodge(width=.75), ) +
+    geom_vline(aes(xintercept = 0), col = "grey") +
+    facet_wrap(~str_remove_all(Coef, "'"), scales = "free_x", ) + 
+    guides(shape = "legend", colour = "none")
+
+  print(p)
+
+}
+
 ```
@@
 ```{r, oac-gen-trend, fig.cap="Warfarin as a percentage of all oral anticoagulant prescribing in Wales. Pink shading covers duration of Wales' \"stay at home\" order."}
-oac <- read_rds(data_files[12])
-
-oac %>% 
-  mutate(warfarin = if_else(bnfchem == "0208020V0", TRUE, FALSE)) %>% 
-  group_by(warfarin, datename) %>% 
-  summarise(quantity = sum(quantity), .groups = "drop") %>% 
-  pivot_wider(id_cols = datename, values_from = quantity, names_from = warfarin) %>% 
-  mutate(prop = `TRUE` / (`TRUE` + `FALSE`),
-         datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
-  tsibble(index = datename) %>% 
+read_rds("../data/prescribing_data/warfarin_ddd.rds") %>% 
+  dplyr::group_by(datename) %>% 
+  dplyr::summarise(quantity = median(quantity, na.rm = TRUE)) %>% 
+  mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
   ggplot(aes(x = datename)) + 
-  geom_line(aes(y = prop))+
+  geom_line(aes(y = quantity)) +
   geom_vline(aes(xintercept = dmy("01-03-2020")), lty = 2, col = "red") +
@@
                 ymin = -Inf, ymax = Inf),
-            fill = 'pink', col = 0,alpha = 0.03) +
+            fill = 'pink', col = 0, alpha = 0.03) +
+  scale_x_yearmonth() +
   xlab("Date") +
-  ylab("Warfarin as a proportion of all oral anticoagulant prescribing")
+  ylab("Warfarin (percentage of all OACs)") +
+  ylim(0, 100) # Dyfrig's request
 

### 2021-09-09 writing/paper.Rmd

@@
 ---
-title             : "Variation in Primary Care Prescribing in Wales due to COVID-19"
-shorttitle        : "Welsh Primary Care COVID Prescribing"
-
+title: "Variation in Primary Care Prescribing in Wales due to COVID-19"
 author:
-  - name          : "Will Hardy"
-    affiliation   : "1,2"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-  - name          : "Susan Murphy"
-    affiliation   : "3"
-  - name          : "Dyfrig Hughes"
-    affiliation   : "1"
-  - name          : "Daniel Hill-McManus"
-    affiliation   : "1"
-
+- name: Will Hardy
+  affiliation: '1'
+  corresponding: yes
+  address: Postal address
+  email: my@email.com
+- name: Susan Murphy
+  affiliation: '3'
+- name: Dyfrig Hughes
+  affiliation: '1'
+- name: Daniel Hill-McManus
+  affiliation: '1'
+shorttitle: Welsh Primary Care COVID Prescribing
+output:
+  html_document: default
+  pdf_document: default
+keywords: keywords
+wordcount: X
+bibliography:
+- r-references.bib
+- ../references/library.bib
+header-includes: \usepackage{caption}
+csl: ../references/apa.csl
+always_allow_html: yes
 affiliation:
-  - id            : "1"
-    institution   : "Centre for Health Economics & Medicines Evaluation, Bangor University, LL55 2PZ"
-  - id            : "2"
-    institution   : "Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ"
-  - id            : "3"
-    institution   : "Betsi Cadwaladr University Health Board"
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["r-references.bib", "../references/library.bib"]
-
-header-includes:
-   - \usepackage{caption}
-csl               : "../references/apa.csl"
-always_allow_html : true
-output            : 
-  - html_document
-
+- id: '1'
+  institution: Centre for Health Economics & Medicines Evaluation, Bangor University,
+    LL55 2PZ
+- id: '2'
+  institution: Betsi Cadwaladr University Health Board
 ---
@@
 library(papaja)
+library(fuzzyjoin)
 
@@
 
+plan(cluster)
 ## Data
@@
 differences <- 
-  map_dfr(.x = differences_files,
+  furrr::future_map_dfr(.x = differences_files,
           .f = ~read_rds(paste0("../data/differences/", .x)),
           .id = "drug") %>% 
-  mutate(drug = case_when(drug == "contra" ~ "oral",
-                          !drug == "contra" ~ drug),
-         drug = relevel(as_factor(drug), ref = "all_drugs"),
-         sd = sd^.25) # Error in serCymruTools when calculated
+    mutate(.mean = mean(dist),
+           drug = relevel(as_factor(drug), ref = "quant_all_drugs"))
+plan(sequential)
 
@@
   str_remove_all(list.files("../data/prescribing_data"), ".rds")
-
-gp_extract <- 
-  map_dfr(.x = data_files,
-          .f = ~(read_rds(.x) %>% 
-            filter(practice_id %in% unique(differences$regional_unit))),
-          .id = "drug") 
+# 
+# gp_extract <- 
+#   map_dfr(.x = data_files[1:11],
+#           .f = ~(read_rds(.x)),
+#           .id = "drug")
 ```
@@
 set.seed(32)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = FALSE, echo = FALSE)
 kable_opts <- options(knitr.kable.NA = "-")
@@
 ```{r, table-2}
-read_rds("../data/gp_agesex_qof_combined.rds") %>% 
+tibble(regional_unit = unique(differences$regional_unit)) %>% 
+  left_join(read_rds("../data/gp_agesex_qof_combined.rds") %>% 
               mutate(npat = N,
                      N = NULL,
-         practice_id = as.character(practiceid)) %>% 
+                     regional_unit = as.character(practiceid)) %>% 
               ungroup() %>% 
               janitor::clean_names() %>%  
-  filter(year == 2020) %>% 
+              filter(year == 2020)) %>% 
   select(npat, ngp, dispensing, wimd2019:flu) %>% 
   mutate(across(p_male:flu, ~.x*100)) %>% 
-  psych::describe() %>% 
-  select(mean, sd, median, min, max) %>% 
+  tibble() %>% 
+  psych::describe(fast = TRUE) %>% 
+  kable(digits = 2, caption = "Summary of prescribing data and GP practice characteristics")
+```
+
+```{r}
+differences %>% 
+  dplyr::group_by(drug) %>% 
+  dplyr::count() %>% 
+  mutate(n = n/8)
+
+monthlyPrescribing <- 
+  function(data){
+    data %>% 
+      janitor::clean_names() %>% 
+      mutate(datename = dmy(paste0("28-", datename)),
+             practice_id = as.character(practice_id)) %>% 
+      countRegional(practice_id, datename, quantity) %>% 
+      mutate(year = year(datename)) %>%
+      as_tibble() %>% 
+      inner_join(gp %>% 
+                   select(practice_id, year, npat), 
+                 by = c("regional_unit" = "practice_id", "year")) %>% 
+      mutate(n = 1000*n/npat,
+             datename = yearmonth(datename),
+             regional_unit = as_factor(regional_unit)) %>% 
+      select(-c(npat, year)) %>% 
+      as_tsibble(index = datename, key = regional_unit) %>% 
+      fill_gaps()
+  }
+
+plan(cluster)
+pres_2019 <- 
+  data_files[c(1:10)] %>% 
+  furrr::future_map(read_rds) %>% 
+  furrr::future_map(monthlyPrescribing) %>% 
+  furrr::future_map_dfr(as_tibble, .id = "drug") %>% 
+  filter(year(datename) == 2019)
+plan(sequential)
+
+pres_2019 %>% 
+  right_join(differences %>% 
+               group_by(regional_unit, drug) %>% 
+               count() %>% 
+               select(-n)) %>% 
+  filter(drug != "warfarin_ddd") %>% 
+  bind_rows(read_rds(data_files[12]) %>% 
+              mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
+              rename(regional_unit = practice_id,
+                     n = quantity) %>% 
+              filter(year(datename) == 2019) %>% 
+              right_join(differences %>% 
+                           filter(drug == "warfarin_ddd") %>% 
+                           group_by(regional_unit, drug) %>% 
+                           count() %>% 
+                           select(-n))) %>% 
+  group_by(drug) %>% 
+  summarise(mean = mean(n, na.rm = TRUE),
+            sd = sd(n, na.rm = TRUE),
+            min = min(n, na.rm = TRUE),
+            max = max(n, na.rm = TRUE),
+            n = length(unique(regional_unit))) %>% 
+  select(drug, n, everything()) %>% 
   kable(digits = 2)
+
+warf_2019 <- 
+  read_rds(data_files[12]) %>% 
+  mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
+  rename(regional_unit = practice_id) %>% 
+  filter(year(datename) == 2019) %>% 
+  right_join(differences %>% 
+               filter(drug == "warfarin_ddd") %>% 
+               group_by(regional_unit, drug) %>% 
+               count() %>% 
+               select(-n)) %>%
+
 ```
@@
   na.omit() %>% 
-  group_by(datename, drug) %>% 
-  summarise(mean_prop = mean(prop, na.rm = T),
+  dplyr::group_by(datename, drug) %>% 
+  dplyr::summarise(mean_prop = mean(prop, na.rm = T),
             med_prop = median(prop, na.rm = T),
@@
             se_prop = sd(prop, na.rm = T)/sqrt(length(prop)),
-            enframe(quantile(prop, seq(.1,.9,.2)), 
+            enframe(stats::quantile(prop, seq(.1,.9,.2)), 
                     "Percentile", "prop"),
             .groups = "drop") %>% 
-  mutate(datename = month(datename),
+  dplyr::mutate(datename = month(datename),
          prop = 100*(prop - 1)) # Percentage change instead of proportion
@@
 differences_quantiles %>%
-  mutate(datename = factor(x = datename, levels = 1:8, 
+  dplyr::mutate(datename = factor(x = datename, levels = 1:8, 
                            labels = month.abb[1:8])) %>% 
-  mutate(drug = case_when(drug == "all_drugs" ~ "All",
-                          drug == "ace" ~ "ACE inhibitors",
-                          drug == "adreno" ~ "Adrenoceptor agonists",
-                          drug == "azithro" ~ "Azithromycin",
-                          drug == "contra" ~ "Oral contraceptives",
-                          drug == "cortico" ~ "Corticosteroids",
-                          drug == "hcq" ~ "Hydroxycholoroquine",
-                          drug == "nsaid" ~ "NSAIDs",
-                          drug == "paracet" ~ "Paracetamol",
-                          drug == "ssri" ~ "SSRIs",
-                          drug == "vitd" ~ "Vitamin D",
-                          drug == "warfarin" ~ "Warfarin"),
-         drug = relevel(as_factor(drug), ref = "All")) %>%
+  dplyr::mutate(drug = case_when(drug == "quant_all_drugs" ~ "All",
+                          drug == "ddd_ace" ~ "ACE inhibitors",
+                          drug == "ddd_adreno" ~ "Beta2 adrenoceptor agonists",
+                          drug == "ddd_cortico" ~ "Corticosteroids",
+                          drug == "ddd_hcq" ~ "Hydroxycholoroquine",
+                          drug == "ddd_nsaid" ~ "NSAIDs",
+                          drug == "ddd_oral_contra" ~ "Oral contraceptives",
+                          drug == "ddd_paracet" ~ "Paracetamol",
+                          drug == "ddd_ssri" ~ "SSRIs",
+                          drug == "ddd_vitd" ~ "Vitamin D",
+                          drug == "warfarin" ~ "Warfarin",
+                          drug == "warfarin_ddd" ~"Warfarin"),
+         drug = relevel(as_factor(drug), ref = "All")
+         ) %>%
   ggplot(aes(x = datename, col = drug, 
@@
   theme(legend.position = "bottom", text = element_text(size = 10)) +
-  scale_linetype_manual(breaks = c("10%", "30%", "50%"), # Remove 70% and 90% from legend
-                        values = c(3,2,1,2,3), # Replicate line type
-                        labels = c("10% lower; 90% upper", # Amalgamate line type labels
-                                   "30% lower; 70% uppper", "50%")) +
+  scale_linetype_manual(values = c(3,2,1,2,3),
+                        # labels = c("10% lower; 90% upper", # Amalgamate line type labels
+                        #            "30% lower; 70% upper", "50%"),
+                        # #breaks = NULL
+                        ) +
+  # scale_linetype_manual(breaks = c("10%", "30%", "50%"), # Remove 70% and 90% from legend
+  #                       values = c(3,2,1,2,3), # Replicate line type
+  #                       labels = c("10% lower; 90% upper", # Amalgamate line type labels
+  #                                   "30% lower; 70% upper", "50%")
+  #                       ) +
   xlab("Month") +
@@
 
-  ggsave(filename = "Draft 2/Figures/Figure 2.png", device = "png",
-         width = 10.5)
-
-```
-```{r}
-differences_quantiles %>%
-  mutate(datename = factor(x = datename, levels = 1:8, 
-                           labels = month.abb[1:8])) %>% 
-  mutate(drug = case_when(drug == "all_drugs" ~ "All",
-                          drug == "ace" ~ "ACE inhibitors",
-                          drug == "adreno" ~ "Adrenoceptor agonists",
-                          drug == "azithro" ~ "Azithromycin",
-                          drug == "contra" ~ "Oral contraceptives",
-                          drug == "cortico" ~ "Corticosteroids",
-                          drug == "hcq" ~ "Hydroxycholoroquine",
-                          drug == "nsaid" ~ "NSAIDs",
-                          drug == "paracet" ~ "Paracetamol",
-                          drug == "ssri" ~ "SSRIs",
-                          drug == "vitd" ~ "Vitamin D",
-                          drug == "warfarin" ~ "Warfarin"),
-         drug = relevel(as_factor(drug), ref = "All")) %>% 
-  filter(drug == "Adrenoceptor agonists" & 
-           datename == "Mar")
-
+ggsave(filename = "Draft 4/Figures/Figure 2.png", device = "png", width = 10.5)
 ```
@@
 
-```{python, composite-sd-function-py, eval=FALSE}
-
-from __future__ import print_function, division  # requires python 2.6 or later (2.7 or later preferred)
-import math
-
-__all__ = ['iterable', 'avg', 'sample_SD', 'composite_SD']
-
-def iterable(obj):
-    '''True iff obj is iterable: a list, tuple, or string.'''
-    return hasattr(obj, '__contains__')
-
-def avg(samples):
-    if len(samples) >= 1:
-        return sum(samples) / len(samples)
-    return float('nan')
-
-def sample_SD(samples):
-    '''input is an array of samples; result is the standard deviation'''
-    mean = avg(samples)
-    sum_of_squared_deviations = 0;
-    sd = 0
-    if len(samples) >= 2:
-        for datum in samples:
-            sum_of_squared_deviations += ((datum - mean) * (datum - mean));
-        sd = math.sqrt(sum_of_squared_deviations / (len(samples)-1) );
-    return sd
-
-def composite_SD(means, SDs, ncounts):
-    '''Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
-       See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
-       Inputs are:
-         means, the array of group means
-         SDs, the array of group standard deviations
-         ncounts, number of samples in each group (can be scalar
-                  if all groups have same number of samples)
-       Result is the overall standard deviation.
-    '''
-    G = len(means)  # number of groups
-    if G != len(SDs):
-        raise Exception('inconsistent list lengths')
-    if not iterable(ncounts):
-        ncounts = [ncounts] * G  # convert scalar ncounts to array
-    elif G != len(ncounts):
-        raise Exception('wrong ncounts list length')
-
-    # calculate total number of samples, N, and grand mean, GM
-    N = sum(ncounts)  # total number of samples
-    if N <= 1:
-        raise Exception("Warning: only " + str(N) + " samples, SD is incalculable")
-    GM = 0.0
-    for i in range(G):
-        GM += means[i] * ncounts[i]
-    GM /= N  # grand mean
-
-    # calculate Error Sum of Squares
-    ESS = 0.0
-    for i in range(G):
-        ESS += ((SDs[i])**2) * (ncounts[i] - 1)
-
-    # calculate Total Group Sum of Squares
-    TGSS = 0.0
-    for i in range(G):
-        TGSS += ((means[i]-GM)**2) * ncounts[i]
-
-    # calculate standard deviation as square root of grand variance
-    result = math.sqrt((ESS+TGSS)/(N-1))
-    return result
-
-samples = range(10)
-print(samples)
-print('avg=', avg(samples))
-sd = sample_SD(samples)
-print('sd=', sd)
-pt1 = [0,1,2]
-pt2 = [3,4]
-pt3 = [5,6,7,8,9]
-means = [avg(pt1), avg(pt2), avg(pt3)]
-SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
-ncounts = [len(pt1), len(pt2), len(pt3)]
-sd2 = composite_SD(means, SDs, ncounts)
-print('sd2=', sd2)
-
-samples = range(9)
-print('avg=', avg(samples))
-sd = sample_SD(samples)
-print('sd=', sd)
-pt1 = [0,1,2]
-pt2 = [3,4,5]
-pt3 = [6,7,8]
-means = [avg(pt1), avg(pt2), avg(pt3)]
-SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
-ncounts = 3
-sd2 = composite_SD(means, SDs, ncounts)
-print('sd2=', sd2)
-```
-
-```{r, composite-sd-function-r, echo=FALSE}
+```{r, composite-sd-function-r, eval=FALSE}
 avg <- function(samples){
@@
 
-```{r, table-3-single-fcts, eval=FALSE}
-nat_data <- 
+```{r, table-3-single-fcts, eval=TRUE}
+plan(cluster)
+nat_data <- # Data for all regional units combined
   data_files %>% 
-  map_dfr(read_rds, .id = "drug") %>% 
-  group_by(drug, datename) %>% 
-  summarise(n = sum(quantity), .groups = "drop")
+  furrr::future_map_dfr(read_rds, .id = "drug") %>% 
+  filter(drug != "warfarin_ddd") %>% 
+  dplyr::group_by(drug, datename) %>% 
+  dplyr::summarise(n = sum(quantity, na.rm = TRUE), .groups = "drop") %>% 
+  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
+         regional_unit = as.factor(drug)) %>% # Calling drug regional_unit to save rewriting all the code
+  as_tsibble(index = "datename", key = "regional_unit") %>% 
+  fill_gaps()
 
-plan(multisession)
 precribing_cv_models <- 
   nat_data %>% 
-  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
-         regional_unit = as.factor(drug)) %>% 
   filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
-  as_tsibble(index = "datename", key = "regional_unit") %>% 
-  serCymruTools::regionalCV(cv_dist = 8, init = 36, step = 3)
-plan(sequential)
-
-precribing_cv_models
+  serCymruTools::regionalCV(cv_dist = 8, init = 36, step = 1)
 
@@
 
-plan(cluster)
-system.time(prescribing_fcsts <-
+#### Monthly forecasts ####
+prescribing_fcsts <-
   nat_data %>% 
-  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
-         regional_unit = as.factor(drug)) %>% 
   filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
-  as_tsibble(index = "datename", key = "regional_unit") %>%
   filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
-              regionalJointFcsts())  
+  regionalJointFcsts()
+
+lockdown_fcsts <- 
+  nat_data %>% 
+  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
+  filter(!regional_unit %in% best_mape_over_50$regional_unit) %>% 
+  fableModels() %>%
+  generate(h = 8, times = 1000) %>%
+  as_tibble() %>% 
+  filter(!datename %in% 
+           yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug", "2020 Sept", "2020 Oct"))) %>% 
+  group_by(.model, regional_unit, .rep) %>% 
+  dplyr::summarise(.sim = sum(.sim)) %>%
+  # Store as a distribution
+  dplyr::summarise(total = distributional::dist_sample(list(.sim))) %>% 
+  mutate(mean = mean(total),
+         lb_95 = stats::quantile(total, .025),
+         lb_80 = stats::quantile(total, .1),
+         med = median(total),
+         ub_80 = stats::quantile(total, .9),
+         ub_95 = stats::quantile(total, .975),
+         sd = distributional::variance(total)^.5,
+         total = NULL)
+
 plan(sequential)
 
+#### Monthly discreps ####
 best_model_discrep <- 
@@
   select(.model, regional_unit) %>% 
-  inner_join(mutate(prescribing_fcsts,
+  inner_join(mutate(prescribing_fcsts, # Select best forecast
                     datename = yearmonth(datename)), 
              by = c(".model", "regional_unit")) %>%
-  left_join(mutate(select(                nat_data %>% 
-  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
-         regional_unit = as.factor(drug)) , 
+  left_join(dplyr::mutate(dplyr::select(nat_data, #Join observed dispensing data
                           c(regional_unit, datename, n)), 
@@
 
+#### Plot ####
 best_model_discrep %>% 
-  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
   group_by(regional_unit) %>% 
-  summarise(n = sum(n),
-            sd = compositeSD(.mean, sd, rep(1, length(sd))),
-            .mean = sum(.mean)) %>% 
-  mutate(lb = .mean - 1.96*sd,
-         ub = .mean + 1.96*sd,
-         lb_mean_pct_change = (100 * (n - ub)/ ub),
-         mean_pct_change = (100 * (n - .mean)/ .mean),
-         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
-  select(regional_unit, lb_mean_pct_change, mean_pct_change, ub_mean_pct_change) %>% 
-  mutate(pct_change = paste0(printnum(mean_pct_change), 
-                             "[", printnum(lb_mean_pct_change), ",", 
-                             printnum(ub_mean_pct_change), "]")) %>% 
-  select(regional_unit, pct_change)
+  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x)) %>% 
+  ggplot(aes(x = datename)) +
+  geom_line(aes(y = med)) +
+  geom_ribbon(aes(ymin = lb_95, ymax = ub_95), alpha = .3) +
+  geom_hline(aes(yintercept = 0), col = "red")+
+  facet_wrap(~regional_unit, scales = "free")
 
+#### Table ####
+monthly_diffs <- 
   best_model_discrep %>% 
-  mutate(prop = 100*(prop-1)) %>% 
-  pivot_wider(id_cols = regional_unit, names_from = datename, values_from = prop) %>% 
-  kable(digits = 2)
+  group_by(regional_unit) %>% 
+  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x)) %>% 
+  select(datename, regional_unit, lb_95, med, ub_95) %>% 
+  mutate(pct_change = paste0(printnum(med), 
+                             "[", printnum(ub_95), ",", 
+                             printnum(lb_95), "]")) %>% 
+  select(datename, regional_unit, pct_change) %>% 
+  pivot_wider(id_cols = regional_unit, names_from = datename, values_from = pct_change)
+
+#### Lockdown discreps ####
+lockdown_model_discrep <- 
+  best_model %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(lockdown_fcsts,  # Select best forecast
+             by = c(".model", "regional_unit")) %>%
+  left_join(nat_data %>% 
+              filter(datename > yearmonth("2020 Feb") &
+                       datename < yearmonth("2020 Aug")) %>% 
+              as_tibble() %>% 
+              select(-datename) %>% 
+              ungroup() %>% 
+              dplyr::group_by(regional_unit) %>% 
+              dplyr::summarise(n = sum(n)),
+            by = "regional_unit") %>% 
+  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x))
+
+#### Table ####
+lockdown_diffs <- 
+  lockdown_model_discrep %>% 
+  mutate(pct_change = paste0(printnum(med), 
+                             "[", printnum(ub_95), ",", 
+                             printnum(lb_95), "]")) %>% 
+  select(regional_unit, lckdwn = pct_change)
+
+#### Joint table ####
+lockdown_diffs %>% 
+  left_join(monthly_diffs, by = "regional_unit") %>% 
+  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
+        align = "lrrrrrrrrr",
+        booktabs = TRUE,
+        caption = "Monthly percentage change in prescribing") %>%
+  kable_styling(font_size = 8) %>% 
+  add_header_above(header = c(" " = 1,
+                              "Mean percentage change [95% CI]" = 9)) %>%
+  landscape()
 ```
 
-```{r, table-3}
+```{r, table-3, eval=FALSE}
 monthly_diffs <- 
@@
         caption = "Monthly percentage change in prescribing") %>%
+  kable_styling(font_size = 8) %>% 
   add_header_above(header = c(" " = 1,
@@
   landscape()
-```
-
-```{r, eval=FALSE}
-differences %>% 
-  filter(drug == "adreno" &
-           datename == yearmonth("2020 Mar")) %>% 
-  ggplot(aes(x = prop-1)) +
-  geom_histogram() +
-  geom_vline(aes(xintercept = mean(prop-1)))
-
-differences %>% 
-  select(drug, datename, .mean, sd, n) %>% 
-  na.omit() %>% 
-  group_by(drug, datename) %>% 
-  summarise(n = sum(n),
-            sd = compositeSD(.mean, sd, rep(nrow(.),length(.mean))),
-            .mean = sum(.mean),
-            .groups = "drop") %>% 
-  filter(drug == "adreno" &
-           datename == yearmonth("2020 Mar"))
-
-differences %>% 
-  filter(drug == "adreno" &
-           datename == yearmonth("2020 Mar")) %>% 
-  summarise(.mean = sum(.mean),
-            n = sum(n),
-            prop = mean(prop))
-
-differences %>% 
-  filter(drug == "adreno" &
-           datename == yearmonth("2020 Mar")) %>% 
-  mutate(prop_correct = if_else(prop == n/med, TRUE, FALSE))
 ```
@@
   group_by(drug) %>% 
-  summarise(n = sum(quantity)/1e6) %>% 
+  summarise(n = sum(quantity, na.rm = TRUE)/1e6) %>% 
   left_join(lockdown_diffs %>% 

### 2021-12-20 writing/appendix_a.Rmd
With RCS IVs for GLS models

@@
   pdf_document: default
-  html_document:
-    df_print: paged
-ouput: html_document
+
+papersize: a4
+header-includes:
+  \usepackage{float}
+  \let\origfigure\figure
+  \let\endorigfigure\endfigure
+  \renewenvironment{figure}[1][2] {
+      \expandafter\origfigure\expandafter[H]
+  } {
+      \endorigfigure
+  }
+
 ---
@@
 library(kableExtra)
-library(geepack)
 library(papaja)
@@
          practice_id = as.character(practiceid),
-         hboard = case_when(hboard == "W11000023" ~ 
-                              "Betsi Cadwaladr",
-                            hboard == "W11000024" ~ 
-                              "Powys",
-                            hboard == "W11000025" ~ 
-                              "Hywel Dda",
-                            hboard == "W11000028" ~ 
-                              "Aneurin Bevan",
-                            hboard == "W11000029" ~ 
-                              "Cardiff and Vale",
-                            hboard == "W11000030" ~ 
-                              "Cwm Taf Morgannwg",
-                            hboard == "W11000031" ~ 
-                              "Swansea Bay")) %>% 
+         hboard = case_when(hboard == "W11000023" ~ "BC",
+                            hboard == "W11000024" ~ "P",
+                            hboard == "W11000025" ~ "HD",
+                            hboard == "W11000028" ~ "AB",
+                            hboard == "W11000029" ~ "CaV",
+                            hboard == "W11000030" ~ "CTM",
+                            hboard == "W11000031" ~ "SB")) %>% 
   ungroup() %>% 
@@
   str_remove_all(list.files("../data/prescribing_data"), ".rds")
+pres_data <- 
+  map(data_files, read_rds)
 
@@
 set.seed(32)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = FALSE, 
-                      echo = FALSE, fig.pos = 'H')
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE, 
+                      echo = FALSE, fig.pos = 'h!')
 kable_opts <- options(knitr.kable.NA = "-")
@@
 #### Data ####
-gp_2020 <- filter(gp, year == 2020)
+gp_2020 <- 
+  filter(gp, year == 2020) %>% 
+  rename(regional_unit = practice_id)
 
@@
 gp_pca <- 
-  prcomp(select(gp_2020, chd:flu), center = TRUE, scale. = TRUE)
+  prcomp(select(gp_2020, c(chd:flu, p_fem, pm_65, pf_65)), center = TRUE, scale. = TRUE)
 
-plot(gp_pca, type = "lines", main = " ")
+plot(gp_pca, type = "lines", main = " ", pch = 3)
 addScree(gp_pca)
@@
 
+gp_2020 <- 
+  gp_2020 %>% 
+  left_join(bind_cols(regional_unit = gp_2020$regional_unit, gp_pca$x), 
+            by = "regional_unit") %>% 
+  select(regional_unit = regional_unit, everything(),
+         -c(practiceid, county, postcode, lsoacode, easting, northing,
+            chd:flu, PC6:PC20, year))
 ```
 
-```{r, gp-pca-direction, fig.cap="QoF disease register loadings on PC1 and PC2"}
-ggbiplot(gp_pca, ellipse = TRUE, groups = gp_2020$hboard, obs.scale = 1, 
-         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)
+```{r, gp-pca-direction, fig.cap=c("QoF disease register loadings on PC 1-2","QoF disease register loadings on PC 2-3","QoF disease register loadings on PC 3-4","QoF disease register loadings on PC 4-5")}
+p1 <- ggbiplot(gp_pca, ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
+         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
+      scale_colour_viridis_d(name = "Health board")
+p2 <- ggbiplot(gp_pca, choices = 2:3,
+         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
+         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
+      scale_colour_viridis_d(name = "Health board")
+p3 <- ggbiplot(gp_pca, choices = 3:4,
+         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
+         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
+      scale_colour_viridis_d(name = "Health board")
+p4 <- ggbiplot(gp_pca, choices = 4:5,
+         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
+         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
+      scale_colour_viridis_d(name = "Health board")
+p1
+cat("\n\n")
+p2
+cat("\n\n")
+p3
+cat("\n\n")
+p4
+cat("\n\n")
 
-gp_2020 <- 
-  gp_2020 %>% 
-  left_join(bind_cols(practice_id = gp_2020$practice_id, gp_pca$x), 
-            by = "practice_id") %>% 
-  select(regional_unit = practice_id, everything(),
-         -c(practiceid, county, cluster, postcode, lsoacode, easting, northing,
-            chd:flu, PC4:PC18, year))
 ```
@@
       summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
-                miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
+                miss_covid = sum(c_across(`2020 Jan`:`2020 Aug`))) %>% 
       filter(miss_covid > 0 | miss_non_covid > 0) %>% 
-      mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))
+      mutate(miss_10_non_covid = if_else(miss_non_covid >= 60/10, TRUE, FALSE))
   }
@@
       summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
-                miss_10_non_covid = sum(if_else(miss_non_covid > 60/10, TRUE,
+                miss_10_non_covid = sum(if_else(miss_non_covid >= 60/10, TRUE,
                                                 FALSE)),
@@
 full_data <- 
-  data_files[c(1:10,12)] %>% 
+  data_files[grep(pattern = "../data/prescribing_data/warfarin_ddd_nat.rds",
+                x = data_files, value = FALSE, invert = TRUE)] %>% 
   furrr::future_map(read_rds)
@@
   knitr::kable(booktabs = TRUE, linesep = "", 
-               col.names = c("drug", "n", "gp", "covid", "10_non_covid",
-                             "either", "mape >50", "total", "remain"),
+               col.names = c("Drug", "n", "GP", "COVID", "10% non-COVID",
+                             "Dispensing", "MAPE >50", "Total", "Remain"),
                caption = "Summary of GP practices removed for each drug.") %>% 
-  footnote(general = "The total is not always equal to the row sum, as a single practice may be missing both data in covid months and more than 10\\% of data in the non-covid months, but will only be excluded once.",
+  kableExtra::add_header_above(c(" "= 2, "Missing" = 4, "Removed" = 2, " " = 1)) %>% 
+  footnote(general = '"Dispensing" is not always equal to the sum of COVID and 10% non-COVID, as a single practice may be missing both data in covid months and more than 10% of data in the non-covid months, but will only be excluded once.',
            threeparttable = TRUE)
+
 ```
@@
 
----
+## Warfarin
 
-## GEE results
+```{r, oac-gen-trend, fig.cap="Warfarin as a percentage of all oral anticoagulant prescribing in Wales. Pink shading covers duration of Wales' \"stay at home\" order."}
+read_rds("../data/prescribing_data/warfarin_ddd.rds") %>% 
+  dplyr::group_by(datename) %>% 
+  dplyr::summarise(quantity = median(quantity, na.rm = TRUE)) %>% 
+  mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
+  ggplot(aes(x = datename)) + 
+  geom_rect(aes(xmin = dmy("01-03-2020"), xmax = dmy("31-07-2020"), 
+                ymin = -Inf, ymax = Inf),
+            fill = 'pink', col = 0, alpha = 0.03) +
+  geom_line(aes(y = quantity)) +
+  geom_vline(aes(xintercept = dmy("01-03-2020")), lty = 2, col = "red") +
+  scale_x_yearmonth() +
+  xlab("Date") +
+  ylab("Warfarin (percentage of all OACs)") +
+  ylim(0, 100) # Dyfrig's request
 
-```{r, gee-analysis, eval = FALSE}
-ace <- 
-  differences %>% 
-  filter(drug == "ddd_ace") %>% 
-  group_by(datename) %>% 
-  slice(1:100, .preserve = TRUE) %>% 
-  left_join(filter(gp, year == 2020), by = c("regional_unit" = "practice_id")) %>% 
-  mutate(time_order = as.numeric(as.factor(datename)))
-
-ace_gee <- geeglm(prop ~ wimd2019, data = ace, id = regional_unit, waves = time_order, corstr = "ar1")
-
-summary(ace_gee)
 ```
@@
 
+### Analysis
+
 ```{r, gls-functions}
+drugs <- unique(differences$drug)
+
 #### Prep GLS data ####
@@
     filter(drug == data) %>% 
-    mutate(time_order = as.numeric(as.factor(datename)),
+    mutate(Month = as.numeric(as.factor(datename)),
            pct_change = 100*(prop - 1)) %>% 
-    select(c(regional_unit, time_order, pct_change))
+    select(c(regional_unit, Month, pct_change))
 
-  baseline <- subset(df, time_order == 2, -time_order)
-  baseline <- upData(baseline, rename = c(pct_change = "prop0"), print = FALSE)
-  followup <- subset(df, time_order > 2)
+  baseline <- subset(df, Month == 2, -Month)
+  baseline <- upData(baseline, rename = c(pct_change = "feb_diff"), print = FALSE)
+  followup <- subset(df, Month > 2)
   both <- merge(baseline, followup, by = c("regional_unit"))
@@
 
+#### Redundancy analysis model ####
+redun <- list()
+for(i in drugs){
+  redun[[i]] <- redun(~hboard + dispensing + Month + feb_diff + wimd2019 + 
+                        PC1 + PC2 + PC3 + PC4 + PC5 + ngp + gp_load,
+                      data = glsData(i), r2 = .8, type = "adjusted") %>% 
+    .$Out
+}
+
+# No redundent variables
+
 #### GLS Analysis function ####
-bestGLS <- function(data){
-  cp <- list(corAR1, corExp, corCompSymm, corLin, corGaus, corSpher)
+bestGLS <- function(data, bootstrap = FALSE){
+  cp <- list(corExp, corCompSymm, corLin, corGaus, corSpher)
   z <- vector("list", length(cp))
@@
   for(k in 1:length(cp)){
-    z[[k]] <- gls(pct_change ~ dispensing + hboard + rcs(time_order, 4) + rcs(prop0, 4) + 
-                    rcs(wimd2019, 4) + rcs(p_male, 4) + rcs(pm_65, 4) + 
-                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + rcs(ngp, 4) + 
-                    rcs(gp_load, 4),
+    z[[k]] <- gls(pct_change ~ rcs(Month, 4:7) +
+                    hboard + dispensing +
+                    rcs(wimd2019, 4) + 
+                    rcs(ngp, 4) + rcs(gp_load, 4) + 
+                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                    rcs(PC4, 4) + rcs(PC5, 4) +
+                    hboard:rcs(Month, 4:7) +
+                    dispensing:rcs(Month, 4:7) +
+                    rcs(wimd2019, 4):rcs(Month, 4:7) +
+                    rcs(ngp, 4):rcs(Month, 4:7) +
+                    rcs(gp_load, 4):rcs(Month, 4:7),
                   data = data,
-                  correlation = cp[[k]](form = ~time_order | regional_unit))
+                  correlation = cp[[k]](form = ~ Month | regional_unit))
   }
 
+  arma_tab <- # Table for p and q values for corARMA()
+    tibble(p = 1:3, 
+           q = rep(0,3)) %>% 
+    mutate(model = row_number() + length(cp))
+
+  z <- c(z, map2(.x = arma_tab$p, .y = arma_tab$q, 
+                 .f = ~ if(.x > 0 | .y >0)
+                 { # p = 0 & q = 0 fails
+                   tryCatch(
+                     {gls(pct_change ~ rcs(Month, 4:7) +
+                            hboard + dispensing +
+                            rcs(wimd2019, 4) + 
+                            rcs(ngp, 4) + rcs(gp_load, 4) + 
+                            rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                            rcs(PC4, 4) + rcs(PC5, 4) +
+                            hboard:rcs(Month, 4:7) +
+                            dispensing:rcs(Month, 4:7) +
+                            rcs(wimd2019, 4):rcs(Month, 4:7) +
+                            rcs(ngp, 4):rcs(Month, 4:7) +
+                            rcs(gp_load, 4):rcs(Month, 4:7),
+                          data = data,
+                          correlation = corARMA(form = ~ Month|regional_unit, 
+                                                p=.x, q=.y))
+                     },
+                     error = function(cond){
+                       message(paste("Model causing error: p = ", 
+                                     .x, "q = ", .y))
+                       message("Original error message:")
+                       message(cond)
+                       return(NULL)
+                     },
+                     warning = function(cond){
+                       message(paste("Model causing warning: p = ", 
+                                     .x, "q = ", .y))
+                       message("Original warning message:")
+                       message(cond)
+                       return(NULL)
+                     }
+                   )
+                 }))
+
   ### Select best model
-  anova(z[[1]], z[[2]], z[[3]], z[[4]], z[[5]], z[[6]])
+  names(z) <- paste0("model", 1:length(z))
+  x <- z %>% 
+    map(summary)
+
+  # Get metrics for each model
+  aic <- map_dfr(x, pluck("AIC"), .id = "model") 
+  bic <- map_dfr(x, pluck("BIC"), .id = "model")
+  log_lik <- map_dfr(x, pluck("logLik"), .id = "model")
+
+  # Create table
+  mod_comparison <- 
+    bind_cols(metric = c("aic", "bic", "log_lik"), 
+              bind_rows(aic,bic,log_lik)) %>% 
+    pivot_longer(-metric) %>% 
+    pivot_wider(id_cols = name, values_from = value, names_from = metric) %>% 
+    rename(model = name) %>% 
+    mutate(model = as.numeric(str_remove_all(model, "model")))
+
+  # Select best model
   best_model_aic <- 
-    anova(z[[1]], z[[2]], z[[3]], z[[4]], z[[5]], z[[6]]) %>% 
-    select(-call) %>% 
-    tibble() %>% 
-    arrange(AIC) %>% 
+    mod_comparison %>% 
+    arrange(aic, bic, desc(log_lik)) %>% 
     head(1) %>% 
-    .$Model
+    .$model
 
   ### Fit best model
-  a <-  Gls(pct_change ~ dispensing + hboard + rcs(time_order, 4) + 
-              rcs(prop0, 4) + rcs(wimd2019, 4) + rcs(p_male, 4) + rcs(pm_65, 4) +               rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4)+ rcs(ngp, 4) + 
-                    rcs(gp_load, 4),
+  if(bootstrap == TRUE){  
+    if(best_model_aic <= 6){
+      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
+                  hboard + dispensing +  
+                  rcs(wimd2019, 4) + 
+                  rcs(ngp, 4) + rcs(gp_load, 4) + 
+                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                  rcs(PC4, 4) + rcs(PC5, 4) +
+                  hboard:rcs(Month, 4:7) +
+                  dispensing:rcs(Month, 4:7) +
+                  rcs(wimd2019, 4):rcs(Month, 4:7) +
+                  rcs(ngp, 4):rcs(Month, 4:7) +
+                  rcs(gp_load, 4):rcs(Month, 4:7),
                 data = data, B = 1000,
-            correlation = cp[[best_model_aic]](form = ~time_order | regional_unit))
-
+                correlation = 
+                  cp[[best_model_aic]](form = ~ Month | regional_unit))
+      }
+    else{
+      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
+                  hboard + dispensing +  
+                  rcs(wimd2019, 4) + 
+                  rcs(ngp, 4) + rcs(gp_load, 4) + 
+                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                  rcs(PC4, 4) + rcs(PC5, 4) +
+                  hboard:rcs(Month, 4:7) +
+                  dispensing:rcs(Month, 4:7) +
+                  rcs(wimd2019, 4):rcs(Month, 4:7) +
+                  rcs(ngp, 4):rcs(Month, 4:7) +
+                  rcs(gp_load, 4):rcs(Month, 4:7),
+                data = data, B = 1000,
+                correlation = 
+                  corARMA(form = ~ Month | regional_unit, 
+                          p = filter(arma_tab, model == best_model_aic)$p, 
+                          q = filter(arma_tab, model == best_model_aic)$q))
+      }
+  }
+  else{
+    if(best_model_aic <= 6){
+      a <- Gls(pct_change ~ rcs(Month, 4:7) +
+                 hboard + dispensing +  
+                 rcs(wimd2019, 4) + 
+                 rcs(ngp, 4) + rcs(gp_load, 4) + 
+                 rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                 rcs(PC4, 4) + rcs(PC5, 4) +
+                 hboard:rcs(Month, 4:7) +
+                 dispensing:rcs(Month, 4:7) +
+                 rcs(wimd2019, 4):rcs(Month, 4:7) +
+                 rcs(ngp, 4):rcs(Month, 4:7) +
+                 rcs(gp_load, 4):rcs(Month, 4:7),
+               data = data,
+               correlation = 
+                 cp[[best_model_aic]](form = ~ Month | regional_unit))
+    }
+    else{
+      a <- Gls(pct_change ~ rcs(Month, 4:7) +
+                  hboard + dispensing +  
+                  rcs(wimd2019, 4) + 
+                  rcs(ngp, 4) + rcs(gp_load, 4) + 
+                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                  rcs(PC4, 4) + rcs(PC5, 4) +
+                  hboard:rcs(Month, 4:7) +
+                  dispensing:rcs(Month, 4:7) +
+                  rcs(wimd2019, 4):rcs(Month, 4:7) +
+                  rcs(ngp, 4):rcs(Month, 4:7) +
+                  rcs(gp_load, 4):rcs(Month, 4:7),
+               data = data,
+               correlation = 
+                 corARMA(form = ~ Month | regional_unit, 
+                         p = filter(arma_tab, model == best_model_aic)$p, 
+                         q = filter(arma_tab, model == best_model_aic)$q))
+    }
+  }
   return(a)
@@
   y1 <- ylab("Residuals")
-  p1 <- ggplot(data, aes(x = fitted, y = resid)) + geom_point() + 
-    facet_grid(~hboard) + y1
-  p2 <- ggplot(data, aes(x = prop0, y = resid)) + geom_point() + y1
-  p3 <- ggplot(data, aes(x = time_order, y = resid)) + y1 + 
+  p1 <- ggplot(data, aes(x = fitted, y = resid)) + geom_point(alpha = .1) + y1
+  p2 <- ggplot(data, aes(x = feb_diff, y = resid)) + geom_point(alpha = .1) + y1
+  p3 <- ggplot(data, aes(x = Month, y = resid)) + y1 + 
     stat_summary(fun.data = "mean_sdl", geom = "smooth")
-  p4 <- ggplot(data, aes(sample = resid)) + stat_qq() + 
+  p4 <- ggplot(data, aes(sample = resid)) + stat_qq(alpha = .1) + 
     geom_abline(intercept = mean(r), slope = sd(r)) + y1
@@
 #### GLS Estimated Effects ####
-glsEffects <- function(model, name){
-  p1 <- ggplot(Predict(model, time_order, dispensing, conf.int = FALSE),
-               adj.subitle = FALSE, legend.position = "top", )
-  p2 <- ggplot(Predict(model, prop0), adj.subtitle = FALSE)
-  p3 <- ggplot(Predict(model, pm_65), adj.subtitle = FALSE)
-  p4 <- ggplot(Predict(model, p_male), adj.subtitle = FALSE)
-  p5 <- ggplot(Predict(model, wimd2019), adj.subtitle = FALSE)
-  p6 <- ggplot(Predict(model, PC1), adj.subtitle = FALSE)
-  p7 <- ggplot(Predict(model, PC2), adj.subtitle = FALSE)
-  p8 <- ggplot(Predict(model, PC3), adj.subtitle = FALSE)
-  p9 <- ggplot(Predict(model, hboard), adj.subtitle = FALSE)
-  p10 <- ggplot(Predict(model, ngp), adj.subtitle = FALSE)
-  p11 <- ggplot(Predict(model, gp_load), adj.subtitle = FALSE)
-  gridExtra::grid.arrange(p1,p2,p3,p4, ncol = 2)
-  gridExtra::grid.arrange(p5,p6,p7,p8, ncol = 2)
-  gridExtra::grid.arrange(p9,p10,p11, ncol = 2)
+percentiles <- function(data, var){
+  # return vector of 5th, 25th, 50th, 75th, and 95th percentile
+  var <- enquo(var)
+  data %>% 
+    summarise(enframe(stats::quantile(!!var, c(.05, .25, .5, .75, .95)), 
+                      "Percentile", "value"), .groups = "drop") %>% 
+    mutate(value = round(value)) %>% .$value
+}
 
-  capture.output(print(model))[16:53] %>% 
-    read_table(., col_names = c(" ", "Coef", "S.E.", "t", "Pr(>|t|)")) %>% 
-    kable(booktabs = TRUE, linesep = "", digits = 2,
-               caption = paste(name, "coefficents")) %>% 
-    kable_styling(bootstrap_options = "striped") %>% 
-    print()
+# dodge <- position_dodge(width = .25)
+predictPlot <- function(data = ., groups, names){
+  groups <- enquo(groups)
+  data %>% 
+    tibble() %>% 
+    group_by(Month, !!groups) %>% 
+    summarise(yhat = mean(yhat)) %>% 
+    mutate(groups = as.factor(!!groups)) %>% 
+    ggplot(aes(x = Month, y = yhat, group = groups)) +
+    geom_line(aes(col = groups)) +
+    scale_colour_viridis_d(name = names) +
+    scale_fill_viridis_d(name = names) +
+    theme(legend.position = "top") +
+    ylab(bquote(~X~hat(beta))) +
+    ggthemes::theme_hc()
+}
 
-  plot(anova(model))
+glsEffects <- function(model, name, data){
 
-  model %>% 
-    anova() %>% 
-    kable(booktabs = TRUE, linesep = "", digits = 2,
-          caption = paste(name, "anova")) %>% 
-    add_indent(positions = c(4,6,8,10,12,14,16,18,20,22)) %>% 
-    kable_styling(bootstrap_options = "striped") %>% 
-    print()
+  Name <- case_when(name == "all_drugs" ~ "All",
+                    name == "ace" ~ "ACEi",
+                    name == "adreno" ~ "BAA",
+                    name == "cortico" ~ "Inhaled \ncortico",
+                    name == "hcq" ~ "HCQ",
+                    name == "nsaid" ~ "NSAIDs",
+                    name == "oral_contra" ~ "Oral\ncontra",
+                    name == "paracet" ~ "Paracet",
+                    name == "ssri" ~ "SSRIs",
+                    name == "vitd" ~ "Vit D",
+                    name == "warfarin" ~ "Warfarin")
 
-  # time_order and prop0 dominate so not useful
-  # n <- nomogram(model, abbrev = TRUE)
-  # plot(n, )
+  cat("\n\n")
+
+  #### Plot interactions #### not including month*ngp as none significant
+  p1 <- Predict(model, Month, dispensing, hboard, conf.int = .95) %>% 
+    predictPlot(., groups = hboard, "Health board")
+  gridExtra::grid.arrange(p1,nrow = 1, newpage = TRUE) # Effects 1
+  cat("\n\n")
+
+  p2 <- Predict(model, Month,  dispensing, hboard, conf.int = .95) %>% 
+    predictPlot(., groups = dispensing, "Dispensing")
+  gridExtra::grid.arrange(p2,nrow = 1, newpage = TRUE) # Effects 2
+  cat("\n\n")
+
+  p1 <- Predict(model, Month, dispensing, hboard,
+                wimd2019 = percentiles(data, wimd2019),
+                conf.int = .95) %>% 
+        group_by(Month, wimd2019) %>% 
+    summarise(yhat = mean(yhat)) %>% 
+    predictPlot(., groups = wimd2019, "WIMD")
+    gridExtra::grid.arrange(p1, nrow = 1, newpage = TRUE) # Effects 3
+  cat("\n\n")
+
+  p1 <- Predict(model, Month, dispensing, hboard,
+                ngp = percentiles(data, ngp),
+                conf.int = .95) %>% 
+    predictPlot(., groups = ngp, "Number of GPs")
+  gridExtra::grid.arrange(p1, ncol = 1, newpage = TRUE) # Effects 5
+  cat("\n\n")
+
+  p2 <- Predict(model, Month, dispensing, hboard,
+                gp_load = percentiles(data, gp_load),
+                conf.int = .95) %>% 
+    predictPlot(., groups = gp_load, "GP load")
+  gridExtra::grid.arrange(p2, nrow = 1, newpage = TRUE) # Effects 4
+  cat("\n\n")
+
+  p1 <- Predict(model, Month, dispensing, hboard,
+                PC1 = percentiles(data, PC1),
+                conf.int = .95) %>% 
+    predictPlot(., groups = PC1, "PC1")
+  p2 <- Predict(model, Month, dispensing, hboard,
+                PC2 = percentiles(data, PC2),
+                conf.int = .95) %>% 
+    predictPlot(., groups = PC2, "PC2")
+  p3 <- Predict(model, Month, dispensing, hboard,
+                PC3 = percentiles(data, PC3),
+                conf.int = .95) %>% 
+    predictPlot(., groups = PC3, "PC3")
+  p4 <- Predict(model, Month, dispensing, hboard,
+                PC4 = percentiles(data, PC4),
+                conf.int = .95) %>% 
+    predictPlot(., groups = PC4, "PC4")
+  gridExtra::grid.arrange(p1,p2,p3,p4, ncol = 2, newpage = TRUE) # Effects 6
+  cat("\n\n")
+
+  # #### ANOVA plot ####
+  # p <- 
+  #   capture.output(anova(model))[4:41] %>%
+  #   read_fwf(fwf_empty(., col_names = c("Factor", "Chi-Square", "d.f.", "P"))) %>% 
+  #   mutate(Factor = 
+  #            str_remove_all(Factor, 
+  #                           c(OPEN_PAREN %R% "Factor" %R% PLUS %R% 
+  #                               "Higher Order Factors" %R% CLOSE_PAREN))) %>% 
+  #   filter(!str_detect(Factor, "Nonlinear") &
+  #            !str_detect(Factor, "TOTAL") &
+  #            Factor != "All Interactions",
+  #          !str_detect(Factor, c("f" %R% OPEN_PAREN %R% "A,B"))) %>% 
+  #   ggplot(aes(x = `Chi-Square`-`d.f.`, 
+  #              y = reorder(Factor, X = `Chi-Square`-`d.f.`))) +
+  #   geom_point(aes(col = 
+  #                    as.factor(if_else(as.numeric(str_remove_all(P, "<"))<.05, 
+  #                                      TRUE,FALSE)))) +
+  #   scale_color_discrete(name = "P < .05") + 
+  #   xlab(expression(chi^2-"d.f.")) +
+  #   ylab(NULL) +
+  #   ggthemes::theme_few() 
+  # 
+  # gridExtra::grid.arrange(p, newpage = TRUE)
+  # cat("\n\n")
+
+  p <- anova(model, rm.other = list("Month"), trans = sqrt,
+             tol = 1e-10, dec.chisq = 2, dec.p = 2) %>% 
+    plot()
+
+  p
+
+  #### ANOVA Table ####
+  # model %>% 
+  #   anova() %>% 
+  #   kable(booktabs = TRUE, linesep = "", digits = 2,
+  #         caption = paste(Name, "Wald z-test statistics")) %>% 
+  #   # add_indent(positions = c(3,5,6,8,10,11,13,15,17,19,21,23,25,27,28,30:34)) %>% 
+  #   kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 
+  #   print()
+
   cat("\n\n")
 }
-
-drugs <- unique(differences$drug)
-
-gls_analysis_fig_cap <- 
-  paste(paste(drugs, "assumptions"), paste(drugs, "effects1"), 
-        paste(drugs, "effects2"), paste(drugs, "effects3"), 
-        paste(drugs, "anova"), paste(drugs, "nomogram"))
 
@@
     c(gls_analysis_fig_cap, 
-      paste(drugs[i], c("assumptions", "effects1", "effects2", "effects3",
-                        "anova", "nomogram")))
+      paste(drugs[i], c("Assumptions", "Health board effects.", "Dispensing status effect.", "WIMD effects.
+Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Number of GPs effects.
+Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Patients per GP effects.
+Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Patient related variable principal components 1-4 effects.
+Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Relative importance of effects.")))
 }
@@
 
-```{r, gls-analysis, results="asis", fig.cap=gls_analysis_fig_cap}
+```{r, gls-analysis-save, results="asis", fig.cap=gls_analysis_fig_cap, warning=FALSE, message=FALSE, eval = FALSE}
+#### gls-analysis-save ####
 drugs <- unique(differences$drug)
@@
 best_models <- list()
+best_bs_models <- list()
 
+dd <- NULL
 for(i in drugs){
-  cat("###", (i), "\n\n")
   gls_data <- glsData(i)
@@
   best_gls <- bestGLS(gls_data)
-  cat("####", "Assumptions\n\n")
-  glsAssump(best_gls, gls_data)
+  best_bs_gls <- bestGLS(gls_data, TRUE)
+  rm(dd)
+  best_models[[i]] <-
+    best_gls
+  best_bs_models[[i]] <- 
+    best_bs_gls
+  options(datadist = NULL)
+}
+
+write_rds(best_models, "../data/gls/best_models.rds")
+write_rds(best_bs_models, "../data/gls/best_bs_models.rds")
+```
+
+```{r, gls-analysis-read}
+#### gls-analysis-read ####
+best_models <- read_rds("../data/gls/best_models.rds")
+best_bs_models <- read_rds("../data/gls/best_bs_models.rds")
+```
+
+```{r, gls-effects, results="asis", fig.cap=gls_analysis_fig_cap, dependson="gls-functions"}
+#### gls-effects ####
+drugs <- unique(differences$drug)
+
+dd <- NULL
+for(i in 1:length(best_bs_models)){
+  cat("####", (drugs[i]), "\n\n")
+  cat("#####", "Assumptions\n\n")
+  gls_data <- glsData(drugs[i])
+  dd <- datadist(gls_data)
+  options(datadist = "dd")
+  glsAssump(best_bs_models[[i]], gls_data)
   cat("\n\n")
-  cat("####", "Effects\n\n")
-  glsEffects(best_gls, i)
+  cat("#####", "Effects\n\n")
+  glsEffects(best_bs_models[[i]], drugs[i], gls_data)
   rm(dd)
   cat("\n\n")
-  best_models[[i]] <- 
-    best_gls
-}
-
-best_model_coefs <- 
-  best_models %>% 
-  map(~capture.output(print(.))[16:53] %>% 
-        read_table(col_names = c("Coef", "Est", "S.E.", "t", "Pr(>|t|)"))) %>%
-  map_dfr(as_tibble, .id = "drug")
-
-best_model_corr <- 
-  best_models %>% 
-  map(~list(str = capture.output(print(.))[55],
-            measure = capture.output(print(.))[58],
-            value = capture.output(print(.))[59]))
-```
-
-```{r, gls-coef-tab-signif, results="asis"}
-
-best_model_coefs %>% 
-  mutate(`Pr(>|t|)` = as.numeric(str_remove_all(string = `Pr(>|t|)`, "<")),
-         Est = case_when(`Pr(>|t|)` < .05 ~ 
-                           paste0(printnum(Est, digits = 2), "*"),
-                         `Pr(>|t|)` >= .05 ~
-                           as.character(printnum(Est, digits = 2, format = "f")))) %>%
-  kable(booktabs = TRUE, linesep = "", digits = 2, align = "r",
-        caption = "Summary of GLS coefficents") %>% 
-  kable_styling(bootstrap_options = "striped") %>% 
-  landscape() %>% 
-  print()
-```
-
-```{r, gls-coef-tab-ci, results="asis"}
-
-best_model_coefs %>% 
-  mutate(`Pr(>|t|)` = as.numeric(str_remove_all(string = `Pr(>|t|)`, "<")),
-         Est = paste0(printnum(Est, digits = 2), "[", 
-                      printnum(Est - 1.96*S.E., digits = 2), ",", 
-                      printnum(Est + 1.96*S.E., digits = 2), "]")) %>% 
-  pivot_wider(id_cols = Coef, names_from = drug, values_from = Est) %>% 
-  kable(booktabs = TRUE, linesep = "", digits = 2, align = "r",
-        caption = "Summary of GLS coefficents [95% CI]") %>% 
-  kable_styling(bootstrap_options = "striped") %>% 
-  landscape() %>% 
-  print()
-```
-
-```{r, gls-coef-plot}
-coefs <- unique(best_model_coefs$Coef)
-
-coef_plot_order <- 
-  list(coefs[1:2],coefs[3:8], coefs[9:20], coefs[21:32],coefs[33:38])
-
-for (i in 1:length(coef_plot_order)) {
-  p <- best_model_coefs %>% 
-    filter(Coef %in% coef_plot_order[[i]]) %>% 
-    ggplot(aes(y = drug, group = as.factor(str_count(Coef, "'")), 
-                                           col = drug)) +
-    geom_point(aes(x = Est, shape = as.factor(str_count(Coef, "'"))), 
-               position = position_dodge(width=.75)) +
-    geom_errorbarh(aes(xmin = Est - 1.96* S.E., xmax = Est + 1.96* S.E.,
-                       height = 0),
-                   position = position_dodge(width=.75), ) +
-    geom_vline(aes(xintercept = 0), col = "grey") +
-    facet_wrap(~str_remove_all(Coef, "'"), scales = "free_x", ) + 
-    guides(shape = "legend", colour = "none")
-
-  print(p)
-
+  options(datadist = NULL)
 }
@@
 
-## Warfarin
+### Summary of effects
 
-```{r, oac-gen-trend, fig.cap="Warfarin as a percentage of all oral anticoagulant prescribing in Wales. Pink shading covers duration of Wales' \"stay at home\" order."}
-read_rds("../data/prescribing_data/warfarin_ddd.rds") %>% 
-  dplyr::group_by(datename) %>% 
-  dplyr::summarise(quantity = median(quantity, na.rm = TRUE)) %>% 
-  mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
-  ggplot(aes(x = datename)) + 
-  geom_line(aes(y = quantity)) +
-  geom_vline(aes(xintercept = dmy("01-03-2020")), lty = 2, col = "red") +
-  geom_rect(aes(xmin = dmy("01-03-2020"), xmax = dmy("31-07-2020"), 
-                ymin = -Inf, ymax = Inf),
-            fill = 'pink', col = 0, alpha = 0.03) +
-  scale_x_yearmonth() +
-  xlab("Date") +
-  ylab("Warfarin (percentage of all OACs)") +
-  ylim(0, 100) # Dyfrig's request
+```{r, gls-anova-summary-tab}
+#### gls-anova-summary-tab ####
+best_bs_models %>% 
+  map(~anova(., tol = 1e-10)) %>% 
+  map(~as_tibble(x = ., rownames = "Coef")) %>% 
+  map(as.matrix) %>% 
+  map(as_tibble) %>% 
+  bind_rows(.id= "drug") %>% 
+  mutate(across(`Chi-Square`:P, as.numeric)) %>% 
+  select(-c(`Chi-Square`, d.f.)) %>% 
+  filter(!str_detect(Coef, "Nonlinear") &
+           !str_detect(Coef, "TOTAL") &
+           !str_detect(Coef,"All Interactions"),
+         !str_detect(Coef, c("f" %R% OPEN_PAREN %R% "A,B"))) %>%
+  pivot_wider(names_from = drug, values_from = P) %>% 
+  mutate(across(ace:warfarin, ~printnum(., zero = FALSE)),
+         Coef = str_remove_all(Coef, OPEN_PAREN %R% "Factor" %R% PLUS %R% 
+                                 "Higher Order Factors" %R% CLOSE_PAREN)) %>% 
+  select(Coef, all_drugs, everything()) %>% 
+  kable(booktabs = TRUE, linesep = "",
+        caption = paste("Wald test p-values"))%>% 
+  kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 
+  landscape()
+```
 
+### Full tables
+
+```{r, gls-full-model-table, results="asis"}
+options(prType="latex")
+
+best_bs_models %>% 
+  map(~print(., latex=TRUE))
+
+options(prType="plain")
 ```

### 2021-12-20 writing/paper.Rmd
With RCS IVs for GLS models

@@
 # devtools::install_github("https://github.com/w-hardy/serCymruTools")
+library(plyr); library(dplyr)
+library(rms)
+library(nlme)
 library(tidyverse)
@@
 library(kableExtra)
-library(geepack)
 library(papaja)
 library(fuzzyjoin)
+library(ggbiplot)
 
@@
   select(practice_id, year, npat)
+
+gp_2020 <- read_rds("../data/gp_2020.rds")
 
@@
 set.seed(32)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = FALSE, echo = FALSE)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE, echo = FALSE)
 kable_opts <- options(knitr.kable.NA = "-")
@@
 ```{r}
-differences %>% 
-  dplyr::group_by(drug) %>% 
-  dplyr::count() %>% 
-  mutate(n = n/8)
-
 monthlyPrescribing <- 
@@
                count() %>% 
-               select(-n)) %>% 
+               select(-n), by = c("drug", "regional_unit")) %>% 
   filter(drug != "warfarin_ddd") %>% 
   bind_rows(read_rds(data_files[12]) %>% 
-              mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
+              mutate(drug = "warfarin_ddd",
+                datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
               rename(regional_unit = practice_id,
                      n = quantity) %>% 
-              filter(year(datename) == 2019) %>% 
-              right_join(differences %>% 
-                           filter(drug == "warfarin_ddd") %>% 
-                           group_by(regional_unit, drug) %>% 
-                           count() %>% 
-                           select(-n))) %>% 
+              filter(year(datename) == 2019)) %>% 
   group_by(drug) %>% 
@@
             min = min(n, na.rm = TRUE),
-            max = max(n, na.rm = TRUE),
-            n = length(unique(regional_unit))) %>% 
+            max = max(n, na.rm = TRUE)) %>% 
+  left_join(differences %>% 
+              dplyr::group_by(drug) %>% 
+              dplyr::count() %>% 
+              mutate(n = n/8), by = "drug") %>% 
   select(drug, n, everything()) %>% 
   kable(digits = 2)
-
-warf_2019 <- 
-  read_rds(data_files[12]) %>% 
-  mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
-  rename(regional_unit = practice_id) %>% 
-  filter(year(datename) == 2019) %>% 
-  right_join(differences %>% 
-               filter(drug == "warfarin_ddd") %>% 
-               group_by(regional_unit, drug) %>% 
-               count() %>% 
-               select(-n)) %>%
-
 ```
@@
 
-```{r, figure-2, fig.cap="Distribution of the difference between observed and forecast prescribing, expressed as a percentage of forecast prescribing.
-Grey line marks forecast level of prescribing.
+```{r, fig-2, fig.cap="Distribution of the difference between observed and forecast dispensing, expressed as a percentage of forecast dispensing.
+Grey line marks forecast level of dispensing.
 Pink shading covers duration of Wales' \"stay at home\" order.
-Please note the difference y-axis scales across the plots.", dpi=450}
+Please note the difference y-axis scales across the plots.
+", dpi=450}
 differences_quantiles <- 
@@
             med_prop = median(prop, na.rm = T),
-            sd_prop = sd(prop, na.rm = T),
-            se_prop = sd(prop, na.rm = T)/sqrt(length(prop)),
-            enframe(stats::quantile(prop, seq(.1,.9,.2)), 
+            enframe(stats::quantile(prop, seq(.1,.9,.1)), 
                     "Percentile", "prop"),
@@
   dplyr::mutate(drug = case_when(drug == "quant_all_drugs" ~ "All",
-                          drug == "ddd_ace" ~ "ACE inhibitors",
-                          drug == "ddd_adreno" ~ "Beta2 adrenoceptor agonists",
-                          drug == "ddd_cortico" ~ "Corticosteroids",
-                          drug == "ddd_hcq" ~ "Hydroxycholoroquine",
+                          drug == "ddd_ace" ~ "ACEi",
+                          drug == "ddd_adreno" ~ "BAA",
+                          drug == "ddd_cortico" ~ "Inhaled cortico",
+                          drug == "ddd_hcq" ~ "HCQ",
                           drug == "ddd_nsaid" ~ "NSAIDs",
-                          drug == "ddd_oral_contra" ~ "Oral contraceptives",
-                          drug == "ddd_paracet" ~ "Paracetamol",
+                          drug == "ddd_oral_contra" ~ "Oral contra",
+                          drug == "ddd_paracet" ~ "Paracet",
                           drug == "ddd_ssri" ~ "SSRIs",
-                          drug == "ddd_vitd" ~ "Vitamin D",
+                          drug == "ddd_vitd" ~ "Vit D",
                           drug == "warfarin" ~ "Warfarin",
                           drug == "warfarin_ddd" ~"Warfarin"),
-         drug = relevel(as_factor(drug), ref = "All")
-         ) %>%
+         drug = relevel(as_factor(drug), ref = "All"),
+         line_type = if_else(Percentile == "50%", "Median", "Decile")) %>%
   ggplot(aes(x = datename, col = drug, 
@@
             fill = 'pink', col = 0,alpha = 0.03) +
-  geom_line(aes(y = prop, lty = Percentile)) +
+  geom_line(aes(y = prop, lty = line_type)) +
   geom_hline(aes(yintercept = 0), alpha = .5) +
@@
   guides(size = "legend", colour = "none") + 
-  theme(legend.position = "bottom", text = element_text(size = 10)) +
-  scale_linetype_manual(values = c(3,2,1,2,3),
-                        # labels = c("10% lower; 90% upper", # Amalgamate line type labels
-                        #            "30% lower; 70% upper", "50%"),
-                        # #breaks = NULL
-                        ) +
-  # scale_linetype_manual(breaks = c("10%", "30%", "50%"), # Remove 70% and 90% from legend
-  #                       values = c(3,2,1,2,3), # Replicate line type
-  #                       labels = c("10% lower; 90% upper", # Amalgamate line type labels
-  #                                   "30% lower; 70% upper", "50%")
-  #                       ) +
+  theme(text = element_text(size = 10),
+        legend.position = c(1, 0),
+        legend.justification = c(1, 0)) +
+  scale_linetype_manual(values = c(2,1), name = " ") +
   xlab("Month") +
-  ylab("Percentage difference from forecast prescribing")
+  ylab("Percentage difference from forecast dispensing")
 
-ggsave(filename = "Draft 4/Figures/Figure 2.png", device = "png", width = 10.5)
+ggsave(filename = "Draft 4/Figures/Figure 2.png", device = "png", height = 14, width = 25, units = "cm")
+
+differences_quantiles %>% 
+  filter(datename == 3 & prop > 0 & 
+           drug %in% c("quant_all_drugs", "ddd_ace", "ddd_adreno", 
+                       "ddd_cortico", "ddd_hcq", "ddd_paracet", "ddd_ssri")) %>% 
+  arrange(Percentile)
+
+differences_quantiles %>% 
+  select(-c(mean_prop, med_prop)) %>% 
+  filter(datename == 5 & prop < 0) %>% 
+  group_by(drug) %>% 
+  count()
+
+# Percentage of practices above or below forecast
+differences %>% 
+  na.omit() %>%
+  dplyr::mutate(datename = month(datename),
+         prop = 100*(prop - 1)) %>% 
+  dplyr::group_by(datename, drug) %>% 
+  summarise(high = round(100*sum(prop > 0)/n(),2),
+            low = 100 - high) %>% 
+  filter(datename == 6)
+
+# Practice level variability
+differences_quantiles %>% 
+  pivot_wider(id_cols = datename:drug, names_from = Percentile, 
+              values_from = prop) %>% 
+  mutate(variability = `90%` - `10%`) %>% 
+  select(-c(`10%`:`90%`)) %>% #filter(drug == "warfarin_ddd")
+  ggplot(aes(x = datename)) +
+  geom_line(aes(y = variability)) +
+  facet_wrap(~drug)
 ```
@@
 
-```{r, composite-sd-function-r, eval=FALSE}
-avg <- function(samples){
-  if (length(samples) >= 1){
-    return(sum(samples) / length(samples))
-  }
-  else{return(NaN)}
-}
-
-sample_SD <- function(samples){
-  # Input is an vector of samples; result is the standard deviation
-  mean = avg(samples)
-  sum_of_squared_deviations <-  0
-  sd <-  0
-  if(length(samples) >= 2){
-    for (datum in samples){
-      sum_of_squared_deviations <- 
-        sum_of_squared_deviations + ((datum - mean) * (datum - mean))
-      sd = sqrt(sum_of_squared_deviations / (length(samples)-1))
-    }
-      return(sd)
-  }
-}
-
-compositeSD <- function(means, SDs, ncounts){
-  #Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
-  # See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
-  #    Inputs are:
-  #      means, the array of group means
-  #      SDs, the array of group standard deviations
-  #      ncounts, number of samples in each group (can be scalar
-  #               if all groups have same number of samples)
-  #    Result is the overall standard deviation.
-  G <- length(means) # number of groups
-  if(G != length(SDs)) stop("Inconsistent lengths (means & sds")
-  if(!is.numeric(ncounts)) {(as.numeric(ncounts))}
-  if(G != length(ncounts)) stop("Inconsistent lengths (means & ncounts)")
-
-  # Calculate total number of samples, N, and grand mean, GM
-  N = sum(ncounts)  # total number of samples
-  if (N <= 1) stop(paste("Warning: only ", N, " samples, SD is incalculable"))
-  GM <-  0.0
-  for (i in 1:G){
-    GM <- GM + means[i] * ncounts[i]
-  }
-  GM <- GM / N  # grand mean
-
-  # calculate Error Sum of Squares
-  ESS <-  0.0
-  for (i in 1:G){
-    ESS <- ESS + ((SDs[i])**2) * (ncounts[i] - 1)
-  }
-
-  # calculate Total Group Sum of Squares
-  TGSS <-  0.0
-  for (i in 1:G){
-    TGSS <- TGSS + ((means[i]-GM)**2) * ncounts[i]
-  }
-
-  # calculate standard deviation as square root of grand variance
-  result <- sqrt((ESS+TGSS)/(N-1))
-  return(result)
-}
-
-samples = 0:9
-print(paste("avg =", avg(samples)))
-sd = sample_SD(samples)
-print(paste("sd =", sd))
-pt1 = c(0,1,2)
-pt2 = c(3,4)
-pt3 = c(5,6,7,8,9)
-means <- c(avg(pt1), avg(pt2), avg(pt3))
-SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
-ncounts <- c(length(pt1), length(pt2), length(pt3))
-sd2 <- compositeSD(means, SDs, ncounts)
-print(paste("sd2 =", sd2))
-
-samples = 0:8
-print(paste("avg =", avg(samples)))
-sd = sample_SD(samples)
-print(paste("sd =", sd))
-pt1 = c(0,1,2)
-pt2 = c(3,4,5)
-pt3 = c(6,7,8)
-means <- c(avg(pt1), avg(pt2), avg(pt3))
-SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
-ncounts <- c(length(pt1), length(pt2), length(pt3))
-sd2 <- compositeSD(means, SDs, ncounts)
-print(paste("sd2 =", sd2))
-
-```
-
-```{r, table-3-single-fcts, eval=TRUE}
+```{r, fig-2-single-fcts, eval=TRUE, fig.cap="Estimated percentage change [95% CI] from forecast dispensing.
+Grey line marks the level of forecast dispensing.
+Pink shading covers duration of Wales’ “stay at home” order.
+Please note the different y-axis scales across the plots.
+ACEi = ACE inhibitors, BAA = Beta~2~ adrenoceptor agonists, HCQ = Hydroxycholoroquine."}
 plan(cluster)
@@
 
+three_month_fcsts <- 
+  nat_data %>% 
+  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
+  filter(!regional_unit %in% best_mape_over_50$regional_unit) %>% 
+  fableModels() %>%
+  generate(h = 8, times = 1000) %>%
+  as_tibble() %>% 
+  filter(datename > yearmonth("2020 Feb") &
+                       datename < yearmonth("2020 Jun")) %>% 
+  group_by(.model, regional_unit, .rep) %>% 
+  dplyr::summarise(.sim = sum(.sim)) %>%
+  # Store as a distribution
+  dplyr::summarise(total = distributional::dist_sample(list(.sim))) %>% 
+  mutate(mean = mean(total),
+         lb_95 = stats::quantile(total, .025),
+         lb_80 = stats::quantile(total, .1),
+         med = median(total),
+         ub_80 = stats::quantile(total, .9),
+         ub_95 = stats::quantile(total, .975),
+         sd = distributional::variance(total)^.5,
+         total = NULL)
+
 plan(sequential)
@@
 best_model_discrep %>% 
-  group_by(regional_unit) %>% 
+  rename(drug = regional_unit) %>% 
+  dplyr::mutate(datename = month(datename),
+                datename = factor(x = datename, levels = 1:8, 
+                           labels = month.abb[1:8]),
+                drug = case_when(drug == "quant_all_drugs" ~ "All",
+                          drug == "ddd_ace" ~ "ACEi",
+                          drug == "ddd_adreno" ~ "BAA",
+                          drug == "ddd_cortico" ~ "Inhaled cortico",
+                          drug == "ddd_hcq" ~ "HCQ",
+                          drug == "ddd_nsaid" ~ "NSAIDs",
+                          drug == "ddd_oral_contra" ~ "Oral contraceptives",
+                          drug == "ddd_paracet" ~ "Paracetamol",
+                          drug == "ddd_ssri" ~ "SSRIs",
+                          drug == "ddd_vitd" ~ "Vitamin D",
+                          drug == "warfarin" ~ "Warfarin",
+                          drug == "warfarin_ddd_nat" ~"Warfarin"),
+         drug = relevel(as_factor(drug), ref = "All"))%>% 
+  group_by(drug) %>% 
   dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x)) %>% 
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = med)) +
-  geom_ribbon(aes(ymin = lb_95, ymax = ub_95), alpha = .3) +
-  geom_hline(aes(yintercept = 0), col = "red")+
-  facet_wrap(~regional_unit, scales = "free")
+  ggplot(aes(x = datename, group = drug)) +
+  geom_line(aes(y = med, col = drug)) +
+  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, fill = drug), alpha = .3) +
+  geom_hline(aes(yintercept = 0), col = "grey") +
+  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
+            fill = 'pink', col = 0,alpha = 0.03) +
+  xlab("Month") +
+  ylab("Percentage difference from forecast prescribing") +
+  facet_wrap(~drug, scales = "free")
 
@@
 
+#### Three month discreps ####
+three_month_model_discrep <- 
+  best_model %>% 
+  select(.model, regional_unit) %>% 
+  inner_join(three_month_fcsts,  # Select best forecast
+             by = c(".model", "regional_unit")) %>%
+  left_join(nat_data %>% 
+              filter(datename > yearmonth("2020 Feb") &
+                       datename < yearmonth("2020 Jun")) %>% 
+              as_tibble() %>% 
+              select(-datename) %>% 
+              ungroup() %>% 
+              dplyr::group_by(regional_unit) %>% 
+              dplyr::summarise(n = sum(n)),
+            by = "regional_unit") %>% 
+  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x))
+
 #### Table ####
@@
 
+three_month_diffs <- 
+  three_month_model_discrep %>% 
+  mutate(pct_change = paste0(printnum(med), 
+                             "[", printnum(ub_95), ",", 
+                             printnum(lb_95), "]")) %>% 
+  select(regional_unit, `Mar-May` = pct_change)
+
 #### Joint table ####
-lockdown_diffs %>% 
+three_month_diffs %>% 
+  left_join(lockdown_diffs, by = "regional_unit") %>% 
   left_join(monthly_diffs, by = "regional_unit") %>% 
-  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
+  kable(col.names = c("Drug", "Mar-May", "Lockdown", month.abb[1:8]),
         align = "lrrrrrrrrr",
@@
   add_header_above(header = c(" " = 1,
-                              "Mean percentage change [95% CI]" = 9)) %>%
+                              "Mean percentage change [95% CI]" = 10)) %>%
+  landscape()
+
+```
+
+## Table 4
+
+```{r, gls-functions}
+drugs <- unique(differences$drug)
+
+#### Prep GLS data ####
+glsData <- function(data){
+  df <- 
+    differences %>% 
+    filter(drug == data) %>% 
+    mutate(Month = as.numeric(as.factor(datename)),
+           pct_change = 100*(prop - 1)) %>% 
+    select(c(regional_unit, Month, pct_change)) %>% 
+    filter(Month > 2) %>% 
+    left_join(gp_2020, by = "regional_unit") %>% 
+    mutate(gp_load = npat / ngp)
+
+  dd <- datadist(df)
+  options(datadist = "dd")
+
+  return(df)
+}
+
+#### Redundancy analysis model ####
+redun <- list()
+for(i in drugs){
+  redun[[i]] <- redun(~hboard + dispensing + Month + wimd2019 + 
+                        PC1 + PC2 + PC3 + PC4 + PC5 + ngp + gp_load,
+                      data = glsData(i), r2 = .8, type = "adjusted") %>% 
+    .$Out
+}
+
+# redun # No redundant variables
+
+#### Collinearity diagnostics ####
+
+colin <- list()
+for(i in drugs){
+  dd <- datadist(glsData(i))
+  options(datadist = "dd")
+  colin[[i]] <- vif(ols(pct_change ~ hboard + dispensing + Month + wimd2019 + 
+                        PC1 + PC2 + PC3 + PC4 + ngp + gp_load,
+                      data = glsData(i)))
+  options(datadist = NULL)
+}
+
+# colin # PC5 causing collinearity issues
+
+#### GLS Analysis function ####
+bestGLS <- function(data, k = 4, bootstrap = FALSE){
+  cp <- list(corExp, corCompSymm, corLin, corGaus, corSpher)
+  z <- vector("list", length(cp))
+
+  ### Fit models
+  for(k in 1:length(cp)){
+    z[[k]] <- gls(pct_change ~ rcs(Month, 4:7) +
+                    hboard + dispensing +
+                    rcs(wimd2019, 4) + 
+                    rcs(ngp, 4) + rcs(gp_load, 4) + 
+                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                    rcs(PC4, 4) +
+                    hboard:rcs(Month, 4:7) +
+                    dispensing:rcs(Month, 4:7) +
+                    rcs(wimd2019, 4):rcs(Month, 4:7) +
+                    rcs(ngp, 4):rcs(Month, 4:7) +
+                    rcs(gp_load, 4):rcs(Month, 4:7),
+                  data = data,
+                  correlation = cp[[k]](form = ~ Month | regional_unit))
+  }
+
+  arma_tab <- # Table for p and q values for corARMA()
+    tibble(p = 1:3, 
+           q = rep(0,3)) %>% 
+    mutate(model = row_number() + length(cp))
+
+  z <- c(z, map2(.x = arma_tab$p, .y = arma_tab$q, 
+                 .f = ~ if(.x > 0 | .y >0)
+                 { # p = 0 & q = 0 fails
+                   tryCatch(
+                     {gls(pct_change ~ rcs(Month, 4:7) +
+                            hboard + dispensing +
+                            rcs(wimd2019, 4) + 
+                            rcs(ngp, 4) + rcs(gp_load, 4) + 
+                            rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                            rcs(PC4, 4) +
+                            hboard:rcs(Month, 4:7) +
+                            dispensing:rcs(Month, 4:7) +
+                            rcs(wimd2019, 4):rcs(Month, 4:7) +
+                            rcs(ngp, 4):rcs(Month, 4:7) +
+                            rcs(gp_load, 4):rcs(Month, 4:7),
+                          data = data,
+                          correlation = corARMA(form = ~ Month|regional_unit, 
+                                                p=.x, q=.y))
+                     },
+                     error = function(cond){
+                       message(paste("Model causing error: p = ", 
+                                     .x, "q = ", .y))
+                       message("Original error message:")
+                       message(cond)
+                       return(NULL)
+                     },
+                     warning = function(cond){
+                       message(paste("Model causing warning: p = ", 
+                                     .x, "q = ", .y))
+                       message("Original warning message:")
+                       message(cond)
+                       return(NULL)
+                     }
+                   )
+                 }))
+
+  ### Select best model
+  names(z) <- paste0("model", 1:length(z))
+  x <- z %>% 
+    map(summary)
+
+  # Get metrics for each model
+  aic <- map_dfr(x, pluck("AIC"), .id = "model") 
+  bic <- map_dfr(x, pluck("BIC"), .id = "model")
+  log_lik <- map_dfr(x, pluck("logLik"), .id = "model")
+
+  # Create table
+  mod_comparison <- 
+    bind_cols(metric = c("aic", "bic", "log_lik"), 
+              bind_rows(aic,bic,log_lik)) %>% 
+    pivot_longer(-metric) %>% 
+    pivot_wider(id_cols = name, values_from = value, names_from = metric) %>% 
+    rename(model = name) %>% 
+    mutate(model = as.numeric(str_remove_all(model, "model")))
+
+  # Select best model
+  best_model_aic <- 
+    mod_comparison %>% 
+    arrange(aic, bic, desc(log_lik)) %>% 
+    head(1) %>% 
+    .$model
+
+  ### Fit best model
+  if(bootstrap == TRUE){  
+    if(best_model_aic <= 6){
+      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
+                  hboard + dispensing +  
+                  rcs(wimd2019, 4) + 
+                  rcs(ngp, 4) + rcs(gp_load, 4) + 
+                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                  rcs(PC4, 4) + 
+                  hboard:rcs(Month, 4:7) +
+                  dispensing:rcs(Month, 4:7) +
+                  rcs(wimd2019, 4):rcs(Month, 4:7) +
+                  rcs(ngp, 4):rcs(Month, 4:7) +
+                  rcs(gp_load, 4):rcs(Month, 4:7),
+                data = data, B = 1000,
+                correlation = 
+                  cp[[best_model_aic]](form = ~ Month | regional_unit))
+      }
+    else{
+      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
+                  hboard + dispensing +  
+                  rcs(wimd2019, 4) + 
+                  rcs(ngp, 4) + rcs(gp_load, 4) + 
+                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                  rcs(PC4, 4) + 
+                  hboard:rcs(Month, 4:7) +
+                  dispensing:rcs(Month, 4:7) +
+                  rcs(wimd2019, 4):rcs(Month, 4:7) +
+                  rcs(ngp, 4):rcs(Month, 4:7) +
+                  rcs(gp_load, 4):rcs(Month, 4:7),
+                data = data, B = 1000,
+                correlation = 
+                  corARMA(form = ~ Month | regional_unit, 
+                          p = filter(arma_tab, model == best_model_aic)$p, 
+                          q = filter(arma_tab, model == best_model_aic)$q))
+      }
+  }
+  else{
+    if(best_model_aic <= 6){
+      a <- Gls(pct_change ~ rcs(Month, 4:7) +
+                 hboard + dispensing +  
+                 rcs(wimd2019, 4) + 
+                 rcs(ngp, 4) + rcs(gp_load, 4) + 
+                 rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                 rcs(PC4, 4) + 
+                 hboard:rcs(Month, 4:7) +
+                 dispensing:rcs(Month, 4:7) +
+                 rcs(wimd2019, 4):rcs(Month, 4:7) +
+                 rcs(ngp, 4):rcs(Month, 4:7) +
+                 rcs(gp_load, 4):rcs(Month, 4:7),
+               data = data,
+               correlation = 
+                 cp[[best_model_aic]](form = ~ Month | regional_unit))
+    }
+    else{
+      a <- Gls(pct_change ~ rcs(Month, 4:7) +
+                  hboard + dispensing +  
+                  rcs(wimd2019, 4) + 
+                  rcs(ngp, 4) + rcs(gp_load, 4) + 
+                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
+                  rcs(PC4, 4) + 
+                  hboard:rcs(Month, 4:7) +
+                  dispensing:rcs(Month, 4:7) +
+                  rcs(wimd2019, 4):rcs(Month, 4:7) +
+                  rcs(ngp, 4):rcs(Month, 4:7) +
+                  rcs(gp_load, 4):rcs(Month, 4:7),
+               data = data,
+               correlation = 
+                 corARMA(form = ~ Month | regional_unit, 
+                         p = filter(arma_tab, model == best_model_aic)$p, 
+                         q = filter(arma_tab, model == best_model_aic)$q))
+    }
+  }
+  return(a)
+}
+```
+
+```{r, gls-analysis-save, results="asis", warning=FALSE, message=FALSE, eval = FALSE}
+#### gls-analysis-save ####
+drugs <- unique(differences$drug)
+
+best_models <- list()
+best_bs_models <- list()
+
+dd <- NULL
+for(i in drugs){
+  gls_data <- glsData(i)
+  dd <- datadist(gls_data)
+  options(datadist = "dd")
+  best_gls <- bestGLS(gls_data)
+  best_bs_gls <- bestGLS(gls_data, TRUE)
+  rm(dd)
+  best_models[[i]] <-
+    best_gls
+  best_bs_models[[i]] <- 
+    best_bs_gls
+  options(datadist = NULL)
+}
+
+write_rds(best_models, "../data/gls/best_models.rds")
+write_rds(best_bs_models, "../data/gls/best_bs_models.rds")
+```
+
+```{r, gls-anova-summary-tab}
+best_bs_models <- read_rds("../data/gls/best_bs_models.rds")
+
+#### ANOVA Table ####
+best_bs_models %>% 
+  map(~anova(., tol = 1e-10)) %>% 
+  map(~as_tibble(x = ., rownames = "Coef")) %>% 
+  map(as.matrix) %>% 
+  map(as_tibble) %>% 
+  bind_rows(.id= "drug") %>% 
+  mutate(across(`Chi-Square`:P, as.numeric)) %>% 
+  select(-c(`Chi-Square`, d.f.)) %>% 
+  filter(!str_detect(Coef, "Nonlinear") &
+           !str_detect(Coef, "TOTAL") &
+           !str_detect(Coef,"All Interactions"),
+         !str_detect(Coef, c("f" %R% OPEN_PAREN %R% "A,B"))) %>%
+  pivot_wider(names_from = drug, values_from = P) %>% 
+  mutate(across(ddd_ace:warfarin_ddd, ~printnum(., zero = FALSE)),
+         Coef = str_remove_all(Coef, OPEN_PAREN %R% "Factor" %R% PLUS %R% 
+                                 "Higher Order Factors" %R% CLOSE_PAREN)) %>% 
+  select(Coef, quant_all_drugs, everything()) %>% 
+  kable(booktabs = TRUE, linesep = "",
+        caption = paste("Wald test p-values")) %>% 
+  kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 
   landscape()
 ```
-
-```{r, table-3, eval=FALSE}
-monthly_diffs <- 
-  differences %>%
-  select(drug, datename, .mean, sd, n) %>% 
-  na.omit() %>% 
-  group_by(drug, datename) %>% 
-  summarise(n = sum(n),
-            sd = compositeSD(.mean, sd, rep(nrow(.),length(.mean))),
-            .mean = sum(.mean),
-            .groups = "drop") %>% 
-  mutate(lb = .mean - 1.96*sd,
-         ub = .mean + 1.96*sd,
-         lb_mean_pct_change = (100 * (n - ub)/ ub),
-         mean_pct_change = (100 * (n - .mean)/ .mean),
-         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
-  mutate(datename = month(datename),
-         pct_change = paste0(printnum(mean_pct_change), 
-                             "[", printnum(lb_mean_pct_change), ",", 
-                             printnum(ub_mean_pct_change), "]")) %>% 
-  pivot_wider(id_cols = drug, names_from = datename, values_from = pct_change)
-
-lockdown_diffs <- 
-  differences %>% 
-  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
-  select(drug, datename, .mean, sd, n) %>% 
-  na.omit() %>% 
-  group_by(drug) %>% 
-  summarise(n = sum(n),
-            sd = compositeSD(.mean, sd, rep(1,length(.mean))),
-            .mean = sum(.mean),
-            .groups = "drop") %>% 
-  mutate(lb = .mean - 1.96*sd,
-         ub = .mean + 1.96*sd,
-         lb_mean_pct_change = (100 * (n - ub)/ ub),
-         mean_pct_change = (100 * (n - .mean)/ .mean),
-         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
-  mutate(pct_change = paste0(printnum(mean_pct_change), 
-                             "[", printnum(lb_mean_pct_change), ",", 
-                             printnum(ub_mean_pct_change), "]")) %>% 
-  select(drug, pct_change)
-
-left_join(lockdown_diffs, monthly_diffs) %>%
-  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
-        align = "lrrrrrrrrr",
-        booktabs = TRUE,
-        caption = "Monthly percentage change in prescribing") %>%
-  kable_styling(font_size = 8) %>% 
-  add_header_above(header = c(" " = 1,
-                              "Mean percentage change [95% CI]" = 9)) %>%
-  landscape()
-```
-
-```{r, eval=FALSE}
-differences %>% 
-  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
-  group_by(drug) %>% 
-  summarise(n = sum(n),
-            .mean = sum(.mean)) %>% 
-  mutate(pct_change = 100 * (n - .mean ) / .mean)
-```
-
-```{r, eval=FALSE}
-differences %>% 
-  select(drug, datename, .mean, sd, n) %>% 
-  na.omit() %>% 
-  group_by(drug) %>% 
-  summarise(across(where(is.numeric),.fns = max))
-```
-
-```{r, eval=FALSE}
-gp_extract %>% 
-  filter(str_detect(datename, "-19")) %>% 
-  group_by(drug) %>% 
-  summarise(n = sum(quantity, na.rm = TRUE)/1e6) %>% 
-  left_join(lockdown_diffs %>% 
-  select(drug, pct_change), by = "drug")
-```
-
-```{r, eval=FALSE}
-differences %>% 
-  group_by(drug) %>% 
-  summarise(discrepancy = sum(discrepancy, na.rm = TRUE),
-            n = sum(n, na.rm = TRUE),
-            pct = 100*discrepancy / n)
-
-differences %>% 
-  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
-  group_by(drug) %>% 
-  summarise(discrepancy = sum(discrepancy, na.rm = TRUE),
-            n = sum(n, na.rm = TRUE),
-            pct = 100*discrepancy / n) %>% 
-  ggplot(aes(x = reorder(drug, pct), y = pct)) +
-  geom_col()
-```

### 2022-02-14 writing/paper.Rmd
New figures

@@
 
-gp_2020 <- read_rds("../data/gp_2020.rds")
+gp_2020 <- 
+  read_rds("../data/gp_2020.rds") %>% 
+  mutate(gp_load = npat/ngp)
+
+quantile(gp_2020$wimd2019, 1/3)
+quantile(gp_2020$wimd2019, 2/3)
+
+gp_2020 <- 
+  gp_2020 %>% 
+  mutate(wimd2019 = case_when(wimd2019 <= 15.1 ~ 1,
+                              wimd2019 > 27 ~ 3,
+                              wimd2019 > 15.1 & wimd2019 <= 27 ~ 2),
+         wimd2019 = factor(x = wimd2019, levels = 1:3,
+                           labels = c("Low", "Med", "High")))
 
@@
                         .id = "drug") %>% 
-    mutate(.mean = mean(dist),
-           drug = relevel(as_factor(drug), ref = "quant_all_drugs"))
+  mutate(drug = relevel(as_factor(drug), ref = "quant_all_drugs"),
+         drug = str_remove_all(drug, "ddd_"),
+         drug = str_remove_all(drug, "quant_"),
+         drug = str_remove_all(drug, "_ddd")) %>% 
+  filter(regional_unit != "W95636") #https://abuhb.nhs.wales/news/news/important-information-regarding-lansbury-surgery-caerphilly/
 plan(sequential)
@@
 #           .id = "drug")
+
+# Functions
+
+#### Summarise and standardise prescribing ####
+monthlyPrescribing <- 
+  function(data){
+    data %>% 
+      janitor::clean_names() %>% 
+      mutate(datename = dmy(paste0("28-", datename)),
+             practice_id = as.character(practice_id)) %>% 
+      countRegional(practice_id, datename, quantity) %>% 
+      mutate(year = year(datename)) %>%
+      as_tibble() %>% 
+      inner_join(gp %>% 
+                   select(practice_id, year, npat), 
+                 by = c("regional_unit" = "practice_id", "year")) %>% 
+      mutate(n = 1000*n/npat,
+             datename = yearmonth(datename),
+             regional_unit = as_factor(regional_unit)) %>% 
+      select(-c(npat, year)) %>% 
+      as_tsibble(index = datename, key = regional_unit) %>% 
+      fill_gaps()
+  }
+
+#### Prep GLS data ####
+glsData <- function(data){
+  df <- 
+    differences %>% 
+    filter(drug == data) %>% 
+    mutate(Month = as.numeric(as.factor(datename)),
+           pct_change = 100*(prop - 1)) %>% 
+    select(c(regional_unit, Month, pct_change)) %>% 
+    filter(Month > 2) %>% 
+    left_join(gp_2020, by = "regional_unit") %>% 
+    mutate(gp_load = npat / ngp)
+
+  dd <- datadist(df)
+  options(datadist = "dd")
+
+  return(df)
+}
+
+#### GLS Analysis function ####
+bestGLS <- function(data, bootstrap = FALSE){
+  cp <- list(corExp, corCompSymm, corLin, corGaus, corSpher)
+  z <- vector("list", length(cp))
+
+  ### Fit models
+  for(k in 1:length(cp)){
+    z[[k]] <- gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
+                            wimd2019 + ngp + 
+                    gp_load + PC1 + PC2 + PC3 + PC4 +
+                            hboard:rcs(Month, 4:7) +
+                            dispensing:rcs(Month, 4:7) +
+                            wimd2019:rcs(Month, 4:7) +
+                            ngp:rcs(Month, 4:7) +
+                            gp_load:rcs(Month, 4:7),
+                  data = data,
+                  correlation = cp[[k]](form = ~ Month | regional_unit))
+  }
+
+  arma_tab <- # Table for p and q values for corARMA()
+    tibble(p = 1:2, 
+           q = rep(0,2)) %>% 
+    mutate(model = row_number() + length(cp))
+
+  z <- c(z, map2(.x = arma_tab$p, .y = arma_tab$q, 
+                 .f = ~ if(.x > 0 | .y >0)
+                 { # p = 0 & q = 0 fails
+                   tryCatch(
+                     {gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
+                            wimd2019 + ngp + 
+                            gp_load + PC1 + PC2 + PC3 + PC4 +
+                            hboard:rcs(Month, 4:7) +
+                            dispensing:rcs(Month, 4:7) +
+                            wimd2019:rcs(Month, 4:7) +
+                            ngp:rcs(Month, 4:7) +
+                            gp_load:rcs(Month, 4:7),
+                          data = data,
+                          correlation = corARMA(form = ~ Month|regional_unit, 
+                                                p=.x, q=.y))
+                     },
+                     error = function(cond){
+                       message(paste("Model causing error: p = ", 
+                                     .x, "q = ", .y))
+                       message("Original error message:")
+                       message(cond)
+                       return(NULL)
+                     },
+                     warning = function(cond){
+                       message(paste("Model causing warning: p = ", 
+                                     .x, "q = ", .y))
+                       message("Original warning message:")
+                       message(cond)
+                       return(NULL)
+                     }
+                   )
+                 }))
+
+  ### Select best model
+  names(z) <- paste0("model", 1:length(z))
+  x <- z %>% 
+    map(summary)
+
+  # Get metrics for each model
+  aic <- map_dfr(x, pluck("AIC"), .id = "model") 
+  bic <- map_dfr(x, pluck("BIC"), .id = "model")
+  log_lik <- map_dfr(x, pluck("logLik"), .id = "model")
+
+  # Create table
+  mod_comparison <- 
+    bind_cols(metric = c("aic", "bic", "log_lik"), 
+              bind_rows(aic, bic, log_lik)) %>% 
+    pivot_longer(-metric) %>% 
+    pivot_wider(id_cols = name, values_from = value, names_from = metric) %>% 
+    rename(model = name) %>% 
+    mutate(model = as.numeric(str_remove_all(model, "model")))
+
+  # Select best model
+  best_model_aic <- 
+    mod_comparison %>% 
+    arrange(aic, bic, desc(log_lik)) %>% 
+    head(1) %>% 
+    .$model
+
+  ### Fit best model
+  if(bootstrap == TRUE){  
+    if(best_model_aic <= 6){
+      a <-  Gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
+                            wimd2019 + ngp + 
+                  gp_load + PC1 + PC2 + PC3 + PC4 +
+                            hboard:rcs(Month, 4:7) +
+                            dispensing:rcs(Month, 4:7) +
+                            wimd2019:rcs(Month, 4:7) +
+                            ngp:rcs(Month, 4:7) +
+                            gp_load:rcs(Month, 4:7),
+                data = data, B = 1000,
+                correlation = 
+                  cp[[best_model_aic]](form = ~ Month | regional_unit))
+      }
+    else{
+      a <-  Gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
+                            wimd2019 + ngp + 
+                  gp_load + PC1 + PC2 + PC3 + PC4 +
+                            hboard:rcs(Month, 4:7) +
+                            dispensing:rcs(Month, 4:7) +
+                            wimd2019:rcs(Month, 4:7) +
+                            ngp:rcs(Month, 4:7) +
+                            gp_load:rcs(Month, 4:7),
+                data = data, B = 1000,
+                correlation = 
+                  corARMA(form = ~ Month | regional_unit, 
+                          p = filter(arma_tab, model == best_model_aic)$p, 
+                          q = filter(arma_tab, model == best_model_aic)$q))
+      }
+  }
+  else{
+    if(best_model_aic <= 6){
+      a <- Gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
+                            wimd2019 + ngp + 
+                 gp_load + PC1 + PC2 + PC3 + PC4 +
+                            hboard:rcs(Month, 4:7) +
+                            dispensing:rcs(Month, 4:7) +
+                            wimd2019:rcs(Month, 4:7) +
+                            ngp:rcs(Month, 4:7) +
+                            gp_load:rcs(Month, 4:7),
+               data = data,
+               correlation = 
+                 cp[[best_model_aic]](form = ~ Month | regional_unit))
+    }
+    else{
+      a <- Gls(pct_change ~ rcs(Month, 4:7) + hboard + dispensing + 
+                            wimd2019 + ngp + 
+                 gp_load + PC1 + PC2 + PC3 + PC4 +
+                            hboard:rcs(Month, 4:7) +
+                            dispensing:rcs(Month, 4:7) +
+                            wimd2019:rcs(Month, 4:7) +
+                            ngp:rcs(Month, 4:7) +
+                            gp_load:rcs(Month, 4:7),
+               data = data,
+               correlation = 
+                 corARMA(form = ~ Month | regional_unit, 
+                         p = filter(arma_tab, model == best_model_aic)$p, 
+                         q = filter(arma_tab, model == best_model_aic)$q))
+    }
+  }
+  return(a)
+}
+
+#### Percentiles for a given variable ####
+percentiles <- function(data, var){
+  # return vector of 5th, 25th, 50th, 75th, and 95th percentile
+  var <- enquo(var)
+  data %>% 
+    summarise(enframe(stats::quantile(!!var, c(.05, .25, .5, .75, .95)), 
+                      "Percentile", "value"), .groups = "drop") %>% 
+    mutate(value = round(value)) %>% .$value
+}
+
 ```
@@
 ```{r}
-monthlyPrescribing <- 
-  function(data){
-    data %>% 
-      janitor::clean_names() %>% 
-      mutate(datename = dmy(paste0("28-", datename)),
-             practice_id = as.character(practice_id)) %>% 
-      countRegional(practice_id, datename, quantity) %>% 
-      mutate(year = year(datename)) %>%
-      as_tibble() %>% 
-      inner_join(gp %>% 
-                   select(practice_id, year, npat), 
-                 by = c("regional_unit" = "practice_id", "year")) %>% 
-      mutate(n = 1000*n/npat,
-             datename = yearmonth(datename),
-             regional_unit = as_factor(regional_unit)) %>% 
-      select(-c(npat, year)) %>% 
-      as_tsibble(index = datename, key = regional_unit) %>% 
-      fill_gaps()
-  }
-
 plan(cluster)
@@
                            labels = month.abb[1:8])) %>% 
-  dplyr::mutate(drug = case_when(drug == "quant_all_drugs" ~ "All",
-                          drug == "ddd_ace" ~ "ACEi",
-                          drug == "ddd_adreno" ~ "BAA",
-                          drug == "ddd_cortico" ~ "Inhaled cortico",
-                          drug == "ddd_hcq" ~ "HCQ",
-                          drug == "ddd_nsaid" ~ "NSAIDs",
-                          drug == "ddd_oral_contra" ~ "Oral contra",
-                          drug == "ddd_paracet" ~ "Paracet",
-                          drug == "ddd_ssri" ~ "SSRIs",
-                          drug == "ddd_vitd" ~ "Vit D",
+  dplyr::mutate(drug = case_when(drug == "all_drugs" ~ "All",
+                          drug == "ace" ~ "ACEi",
+                          drug == "cortico" ~ "Inhaled cortico",
+                          drug == "hcq" ~ "HCQ",
+                          drug == "nsaid" ~ "NSAIDs",
+                          drug == "oral_contra" ~ "Oral contra",
+                          drug == "paracet" ~ "Paracet",
+                          drug == "sal" ~ "Salbutamol",
+                          drug == "ssri" ~ "SSRIs",
+                          drug == "vitd" ~ "Vit D",
                           drug == "warfarin" ~ "Warfarin",
@@
 
-ggsave(filename = "Draft 4/Figures/Figure 2.png", device = "png", height = 14, width = 25, units = "cm")
-
-differences_quantiles %>% 
-  filter(datename == 3 & prop > 0 & 
-           drug %in% c("quant_all_drugs", "ddd_ace", "ddd_adreno", 
-                       "ddd_cortico", "ddd_hcq", "ddd_paracet", "ddd_ssri")) %>% 
-  arrange(Percentile)
-
-differences_quantiles %>% 
-  select(-c(mean_prop, med_prop)) %>% 
-  filter(datename == 5 & prop < 0) %>% 
-  group_by(drug) %>% 
-  count()
-
-# Percentage of practices above or below forecast
-differences %>% 
-  na.omit() %>%
-  dplyr::mutate(datename = month(datename),
-         prop = 100*(prop - 1)) %>% 
-  dplyr::group_by(datename, drug) %>% 
-  summarise(high = round(100*sum(prop > 0)/n(),2),
-            low = 100 - high) %>% 
-  filter(datename == 6)
-
-# Practice level variability
-differences_quantiles %>% 
-  pivot_wider(id_cols = datename:drug, names_from = Percentile, 
-              values_from = prop) %>% 
-  mutate(variability = `90%` - `10%`) %>% 
-  select(-c(`10%`:`90%`)) %>% #filter(drug == "warfarin_ddd")
-  ggplot(aes(x = datename)) +
-  geom_line(aes(y = variability)) +
-  facet_wrap(~drug)
+ggsave(filename = "Draft 5/Figures/Figure 2.png", device = "png", height = 14, width = 25, units = "cm")
 ```
@@
 Please note the different y-axis scales across the plots.
-ACEi = ACE inhibitors, BAA = Beta~2~ adrenoceptor agonists, HCQ = Hydroxycholoroquine."}
+ACEi = ACE inhibitors, HCQ = Hydroxycholoroquine."}
 plan(cluster)
@@
 
-#### Plot ####
-best_model_discrep %>% 
-  rename(drug = regional_unit) %>% 
-  dplyr::mutate(datename = month(datename),
-                datename = factor(x = datename, levels = 1:8, 
-                           labels = month.abb[1:8]),
-                drug = case_when(drug == "quant_all_drugs" ~ "All",
-                          drug == "ddd_ace" ~ "ACEi",
-                          drug == "ddd_adreno" ~ "BAA",
-                          drug == "ddd_cortico" ~ "Inhaled cortico",
-                          drug == "ddd_hcq" ~ "HCQ",
-                          drug == "ddd_nsaid" ~ "NSAIDs",
-                          drug == "ddd_oral_contra" ~ "Oral contraceptives",
-                          drug == "ddd_paracet" ~ "Paracetamol",
-                          drug == "ddd_ssri" ~ "SSRIs",
-                          drug == "ddd_vitd" ~ "Vitamin D",
-                          drug == "warfarin" ~ "Warfarin",
-                          drug == "warfarin_ddd_nat" ~"Warfarin"),
-         drug = relevel(as_factor(drug), ref = "All"))%>% 
-  group_by(drug) %>% 
-  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x)) %>% 
-  ggplot(aes(x = datename, group = drug)) +
-  geom_line(aes(y = med, col = drug)) +
-  geom_ribbon(aes(ymin = lb_95, ymax = ub_95, fill = drug), alpha = .3) +
-  geom_hline(aes(yintercept = 0), col = "grey") +
-  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
-            fill = 'pink', col = 0,alpha = 0.03) +
-  xlab("Month") +
-  ylab("Percentage difference from forecast prescribing") +
-  facet_wrap(~drug, scales = "free")
-
 #### Table ####
@@
 
-#### Three month discreps ####
-three_month_model_discrep <- 
-  best_model %>% 
-  select(.model, regional_unit) %>% 
-  inner_join(three_month_fcsts,  # Select best forecast
-             by = c(".model", "regional_unit")) %>%
-  left_join(nat_data %>% 
-              filter(datename > yearmonth("2020 Feb") &
-                       datename < yearmonth("2020 Jun")) %>% 
-              as_tibble() %>% 
-              select(-datename) %>% 
-              ungroup() %>% 
-              dplyr::group_by(regional_unit) %>% 
-              dplyr::summarise(n = sum(n)),
-            by = "regional_unit") %>% 
-  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x))
-
 #### Table ####
@@
 
-three_month_diffs <- 
-  three_month_model_discrep %>% 
-  mutate(pct_change = paste0(printnum(med), 
-                             "[", printnum(ub_95), ",", 
-                             printnum(lb_95), "]")) %>% 
-  select(regional_unit, `Mar-May` = pct_change)
-
 #### Joint table ####
-three_month_diffs %>% 
-  left_join(lockdown_diffs, by = "regional_unit") %>% 
+lockdown_diffs %>% 
   left_join(monthly_diffs, by = "regional_unit") %>% 
-  kable(col.names = c("Drug", "Mar-May", "Lockdown", month.abb[1:8]),
-        align = "lrrrrrrrrr",
+  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
+        align = "lrrrrrrrr",
         booktabs = TRUE,
@@
   add_header_above(header = c(" " = 1,
-                              "Mean percentage change [95% CI]" = 10)) %>%
+                              "Mean percentage change [95% CI]" = 9)) %>%
   landscape()
@@
 
-```{r, gls-functions}
+```{r, gls-functions, echo=FALSE}
 drugs <- unique(differences$drug)
-
-#### Prep GLS data ####
-glsData <- function(data){
-  df <- 
-    differences %>% 
-    filter(drug == data) %>% 
-    mutate(Month = as.numeric(as.factor(datename)),
-           pct_change = 100*(prop - 1)) %>% 
-    select(c(regional_unit, Month, pct_change)) %>% 
-    filter(Month > 2) %>% 
-    left_join(gp_2020, by = "regional_unit") %>% 
-    mutate(gp_load = npat / ngp)
-
-  dd <- datadist(df)
-  options(datadist = "dd")
-
-  return(df)
-}
 
@@
   redun[[i]] <- redun(~hboard + dispensing + Month + wimd2019 + 
-                        PC1 + PC2 + PC3 + PC4 + PC5 + ngp + gp_load,
+                        PC1 + PC2 + PC3 + PC4 + PC5 + ngp + 
+                        gp_load,
                       data = glsData(i), r2 = .8, type = "adjusted") %>% 
@@
 #### Collinearity diagnostics ####
-
 colin <- list()
@@
   options(datadist = "dd")
-  colin[[i]] <- vif(ols(pct_change ~ hboard + dispensing + Month + wimd2019 + 
-                        PC1 + PC2 + PC3 + PC4 + ngp + gp_load,
-                      data = glsData(i)))
+  colin[[i]] <- sum(vif(ols(pct_change ~ hboard + dispensing + Month + wimd2019 + 
+                        PC1 + PC2 + PC3 + PC4 + ngp + 
+                          gp_load,
+                      data = glsData(i))) >= 5)
   options(datadist = NULL)
@@
 
-# colin # PC5 causing collinearity issues
-
-#### GLS Analysis function ####
-bestGLS <- function(data, k = 4, bootstrap = FALSE){
-  cp <- list(corExp, corCompSymm, corLin, corGaus, corSpher)
-  z <- vector("list", length(cp))
-
-  ### Fit models
-  for(k in 1:length(cp)){
-    z[[k]] <- gls(pct_change ~ rcs(Month, 4:7) +
-                    hboard + dispensing +
-                    rcs(wimd2019, 4) + 
-                    rcs(ngp, 4) + rcs(gp_load, 4) + 
-                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                    rcs(PC4, 4) +
-                    hboard:rcs(Month, 4:7) +
-                    dispensing:rcs(Month, 4:7) +
-                    rcs(wimd2019, 4):rcs(Month, 4:7) +
-                    rcs(ngp, 4):rcs(Month, 4:7) +
-                    rcs(gp_load, 4):rcs(Month, 4:7),
-                  data = data,
-                  correlation = cp[[k]](form = ~ Month | regional_unit))
-  }
-
-  arma_tab <- # Table for p and q values for corARMA()
-    tibble(p = 1:3, 
-           q = rep(0,3)) %>% 
-    mutate(model = row_number() + length(cp))
-
-  z <- c(z, map2(.x = arma_tab$p, .y = arma_tab$q, 
-                 .f = ~ if(.x > 0 | .y >0)
-                 { # p = 0 & q = 0 fails
-                   tryCatch(
-                     {gls(pct_change ~ rcs(Month, 4:7) +
-                            hboard + dispensing +
-                            rcs(wimd2019, 4) + 
-                            rcs(ngp, 4) + rcs(gp_load, 4) + 
-                            rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                            rcs(PC4, 4) +
-                            hboard:rcs(Month, 4:7) +
-                            dispensing:rcs(Month, 4:7) +
-                            rcs(wimd2019, 4):rcs(Month, 4:7) +
-                            rcs(ngp, 4):rcs(Month, 4:7) +
-                            rcs(gp_load, 4):rcs(Month, 4:7),
-                          data = data,
-                          correlation = corARMA(form = ~ Month|regional_unit, 
-                                                p=.x, q=.y))
-                     },
-                     error = function(cond){
-                       message(paste("Model causing error: p = ", 
-                                     .x, "q = ", .y))
-                       message("Original error message:")
-                       message(cond)
-                       return(NULL)
-                     },
-                     warning = function(cond){
-                       message(paste("Model causing warning: p = ", 
-                                     .x, "q = ", .y))
-                       message("Original warning message:")
-                       message(cond)
-                       return(NULL)
-                     }
-                   )
-                 }))
-
-  ### Select best model
-  names(z) <- paste0("model", 1:length(z))
-  x <- z %>% 
-    map(summary)
-
-  # Get metrics for each model
-  aic <- map_dfr(x, pluck("AIC"), .id = "model") 
-  bic <- map_dfr(x, pluck("BIC"), .id = "model")
-  log_lik <- map_dfr(x, pluck("logLik"), .id = "model")
-
-  # Create table
-  mod_comparison <- 
-    bind_cols(metric = c("aic", "bic", "log_lik"), 
-              bind_rows(aic,bic,log_lik)) %>% 
-    pivot_longer(-metric) %>% 
-    pivot_wider(id_cols = name, values_from = value, names_from = metric) %>% 
-    rename(model = name) %>% 
-    mutate(model = as.numeric(str_remove_all(model, "model")))
-
-  # Select best model
-  best_model_aic <- 
-    mod_comparison %>% 
-    arrange(aic, bic, desc(log_lik)) %>% 
-    head(1) %>% 
-    .$model
-
-  ### Fit best model
-  if(bootstrap == TRUE){  
-    if(best_model_aic <= 6){
-      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
-                  hboard + dispensing +  
-                  rcs(wimd2019, 4) + 
-                  rcs(ngp, 4) + rcs(gp_load, 4) + 
-                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                  rcs(PC4, 4) + 
-                  hboard:rcs(Month, 4:7) +
-                  dispensing:rcs(Month, 4:7) +
-                  rcs(wimd2019, 4):rcs(Month, 4:7) +
-                  rcs(ngp, 4):rcs(Month, 4:7) +
-                  rcs(gp_load, 4):rcs(Month, 4:7),
-                data = data, B = 1000,
-                correlation = 
-                  cp[[best_model_aic]](form = ~ Month | regional_unit))
-      }
-    else{
-      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
-                  hboard + dispensing +  
-                  rcs(wimd2019, 4) + 
-                  rcs(ngp, 4) + rcs(gp_load, 4) + 
-                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                  rcs(PC4, 4) + 
-                  hboard:rcs(Month, 4:7) +
-                  dispensing:rcs(Month, 4:7) +
-                  rcs(wimd2019, 4):rcs(Month, 4:7) +
-                  rcs(ngp, 4):rcs(Month, 4:7) +
-                  rcs(gp_load, 4):rcs(Month, 4:7),
-                data = data, B = 1000,
-                correlation = 
-                  corARMA(form = ~ Month | regional_unit, 
-                          p = filter(arma_tab, model == best_model_aic)$p, 
-                          q = filter(arma_tab, model == best_model_aic)$q))
-      }
-  }
-  else{
-    if(best_model_aic <= 6){
-      a <- Gls(pct_change ~ rcs(Month, 4:7) +
-                 hboard + dispensing +  
-                 rcs(wimd2019, 4) + 
-                 rcs(ngp, 4) + rcs(gp_load, 4) + 
-                 rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                 rcs(PC4, 4) + 
-                 hboard:rcs(Month, 4:7) +
-                 dispensing:rcs(Month, 4:7) +
-                 rcs(wimd2019, 4):rcs(Month, 4:7) +
-                 rcs(ngp, 4):rcs(Month, 4:7) +
-                 rcs(gp_load, 4):rcs(Month, 4:7),
-               data = data,
-               correlation = 
-                 cp[[best_model_aic]](form = ~ Month | regional_unit))
-    }
-    else{
-      a <- Gls(pct_change ~ rcs(Month, 4:7) +
-                  hboard + dispensing +  
-                  rcs(wimd2019, 4) + 
-                  rcs(ngp, 4) + rcs(gp_load, 4) + 
-                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                  rcs(PC4, 4) + 
-                  hboard:rcs(Month, 4:7) +
-                  dispensing:rcs(Month, 4:7) +
-                  rcs(wimd2019, 4):rcs(Month, 4:7) +
-                  rcs(ngp, 4):rcs(Month, 4:7) +
-                  rcs(gp_load, 4):rcs(Month, 4:7),
-               data = data,
-               correlation = 
-                 corARMA(form = ~ Month | regional_unit, 
-                         p = filter(arma_tab, model == best_model_aic)$p, 
-                         q = filter(arma_tab, model == best_model_aic)$q))
-    }
-  }
-  return(a)
-}
+# colin # no VIF >= 5
 ```
@@
   gls_data <- glsData(i)
+  gls_data %>% 
+    mutate(hboard = as.factor(hboard),
+           hboard = relevel(hboard, ref = "BC"))
   dd <- datadist(gls_data)
@@
   map(~anova(., tol = 1e-10)) %>% 
-  map(~as_tibble(x = ., rownames = "Coef")) %>% 
+  map(~as_tibble(x = ., rownames = "Variable")) %>% 
   map(as.matrix) %>% 
@@
   select(-c(`Chi-Square`, d.f.)) %>% 
-  filter(!str_detect(Coef, "Nonlinear") &
-           !str_detect(Coef, "TOTAL") &
-           !str_detect(Coef,"All Interactions"),
-         !str_detect(Coef, c("f" %R% OPEN_PAREN %R% "A,B"))) %>%
+  filter(!str_detect(Variable, "Nonlinear") &
+           !str_detect(Variable, "TOTAL") &
+           !str_detect(Variable,"All Interactions"),
+         !str_detect(Variable, c("f" %R% OPEN_PAREN %R% "A,B"))) %>%
   pivot_wider(names_from = drug, values_from = P) %>% 
-  mutate(across(ddd_ace:warfarin_ddd, ~printnum(., zero = FALSE)),
-         Coef = str_remove_all(Coef, OPEN_PAREN %R% "Factor" %R% PLUS %R% 
+  mutate(across(ace:warfarin, ~printnum(., zero = FALSE)),
+         Variable = str_remove_all(Variable, OPEN_PAREN %R% "Factor" %R% PLUS %R% 
                                  "Higher Order Factors" %R% CLOSE_PAREN)) %>% 
-  select(Coef, quant_all_drugs, everything()) %>% 
+  select(Variable, all_drugs, everything()) %>% 
   kable(booktabs = TRUE, linesep = "",
@@
 ```
+
+## Variation of impacts on dispensing
+
+```{r, gls-fig-setup}
+## Health board
+drugs_hb <- c("all_drugs", "cortico", "nsaid", "oral_contra", "sal", "ssri", 
+              "vitd", "warfarin")
+
+## Dispensing status
+drugs_disp <- c("all_drugs", "cortico", "paracet", "sal", "vitd")
+
+## WIMD
+drugs_wimd <- c("cortico", "sal", "ssri", "vitd")
+
+## NGPs
+drugs_ngp <- c("oral_contra", "sal")
+
+## GP load
+drugs_gpld <- c("oral_contra")
+
+```
+
+```{r, gp-2020-medians, include=FALSE}
+gp_2020 %>% 
+  dplyr::summarise(hboard = mode(hboard),
+                   dispensing = mode(dispensing),
+                   wimd2019 = mode(wimd2019),
+                   ngp = median(ngp),
+                   gp_load = median(gp_load),
+                   PC1 = median(PC1),
+                   PC2 = median(PC2),
+                   PC3 = median(PC3),
+                   PC4 = median(PC4))
+
+```
+
+```{r, gp-2020-percentiles, include=FALSE}
+gp_2020_percentiles <- 
+  data.frame(
+    percentile = c(5, 25, 50, 75, 95),
+    # wimd2019 = percentiles(gp_2020, wimd2019),
+    ngp = percentiles(gp_2020, ngp),
+    gp_load = percentiles(gp_2020, gp_load))
+```
+
+* Figures represent predicted changes to dispensing based on GLS models
+* When considering the effect of a specific predictor over time, all other predictors will be set to the median value for continuous predictors and the mode for categorical predictors.
+*
+
+### Month
+
+```{r gls-month-fig, fig.cap="Dispensing by health board", eval=FALSE}
+dd <- NULL
+gls_month_fig <- list()
+for(i in drugs){
+  dd <- datadist(glsData(i))
+  options(datadist = "dd")
+  gls_month_fig[[i]] <- 
+    Predict(best_bs_models[[i]], Month, 
+            hboard = "BC", dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
+            gp_load = 1329.486, 
+            PC1 = -0.1257104, PC2 = 0.1257104, PC3 = 0.1257104, PC4 = -0.09966945,
+            conf.int = .95)
+
+  options(datadist = NULL)
+}
+
+gls_month_fig %>% 
+  map_dfr(as_tibble, .id = "drug") %>% 
+  mutate(drug = as.factor(drug),
+           drug = relevel(drug, ref = "all_drugs")) %>%
+  ggplot(aes(x = Month, y = yhat)) +
+  geom_line() +
+  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) +
+  facet_wrap(~drug, scales = "free_y")
+
+```
+
+* This is broadly a repeat of what is seen in Figure 2 and what is described in the text referring to that section, therefore will not be repeated here.
+
+### Health board
+
+```{r gls-hb-fig-panel, fig.cap="Dispensing by health board"}
+dd <- NULL
+gls_hb_fig <- list()
+for(i in drugs_hb){
+  dd <- datadist(glsData(i))
+  options(datadist = "dd")
+  gls_hb_fig[[i]] <- 
+    Predict(best_bs_models[[i]], Month, hboard,
+            dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
+            gp_load = 1329.486, 
+            PC1 = -0.1257104, PC2 = 0.1257104, PC3 = 0.1257104, PC4 = -0.09966945,
+            conf.int = .95)
+
+  options(datadist = NULL)
+}
+
+gls_hb_fig %>% 
+  map_dfr(as_tibble, .id = "drug") %>% 
+  dplyr::mutate(Month = factor(x = Month, levels = 3:8, 
+                           labels = month.abb[3:8]),
+                drug = case_when(drug == "all_drugs" ~ "All",
+                          drug == "ace" ~ "ACEi",
+                          drug == "cortico" ~ "Inhaled \ncorticosteriods",
+                          drug == "hcq" ~ "HCQ",
+                          drug == "nsaid" ~ "NSAIDs",
+                          drug == "oral_contra" ~ "Oral \ncontraceptives",
+                          drug == "paracet" ~ "Paracetamol",
+                          drug == "sal" ~ "Salbutamol",
+                          drug == "ssri" ~ "SSRIs",
+                          drug == "vitd" ~ "Vitamin D",
+                          drug == "warfarin" ~ "Warfarin",
+                          drug == "warfarin_ddd" ~"Warfarin")) %>% 
+  ggplot(aes(x = Month, y = yhat, col = as.factor(hboard), group = hboard)) +
+  geom_line(alpha = 0, position = position_dodge(.7)) +
+  geom_point(position = position_dodge(.7), size = .5) +
+  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5, 
+                position = position_dodge(.7)) +
+  ggthemes::theme_few() +
+  guides(col = guide_legend(ncol = 2)) +
+  theme(legend.position = c(.8,.1),
+        legend.title = element_text(size = 10, face = "bold", hjust = .5),
+        legend.text = element_text(size = 10)) +
+  scale_colour_viridis_d("Health board") +
+  facet_wrap(~drug, scales = "free_y")
+
+ggsave(filename = "Draft 5/Figures/health-board.png", device = "png", height = 14, width = 25, units = "cm")
+
+```
+
+* Seven of the eleven groups of medicines were dispensed differently across health boards.
+*
+
+### Dispensing status
+
+```{r, disp-contrast-fig, fig.cap="Dispensing status contrasts and 95% confidence limits from GLS models."}
+disp_contrasts <- 
+  list(
+    all_drugs = contrast(best_bs_models$all_drugs, 
+                         list(Month = 3:8, dispensing = TRUE),
+                         list(Month = 3:8, dispensing = FALSE)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
+    cortico = contrast(best_bs_models$cortico, 
+                       list(Month = 3:8, dispensing = TRUE),
+                       list(Month = 3:8, dispensing = FALSE)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
+    paracet = contrast(best_bs_models$paracet, 
+                       list(Month = 3:8, dispensing = TRUE),
+                       list(Month = 3:8, dispensing = FALSE)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
+    sal = contrast(best_bs_models$sal, 
+                   list(Month = 3:8, dispensing = TRUE),
+                   list(Month = 3:8, dispensing = FALSE)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
+    vitd = contrast(best_bs_models$vitd, 
+                    list(Month = 3:8, dispensing = TRUE),
+                    list(Month = 3:8, dispensing = FALSE)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame()
+  ) %>% 
+  bind_rows(.id = "drug")
+
+(disp_plot <- disp_contrasts %>% 
+  mutate(Month = factor(x = Month, levels = 3:8, 
+                           labels = month.abb[3:8])) %>% 
+  ggplot(aes(x = Month, col = drug)) +
+  geom_point(aes(y = Contrast), size = .5, position = position_dodge(.25)) +
+  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(.25),
+                width = 0) +
+  geom_hline(aes(yintercept = 0), colour = "grey") +
+  ggthemes::theme_few() +
+  scale_colour_viridis_d("Drug", drop = FALSE) +
+  ylab("Dispensing - Non-dispensing"))
+
+ggsave(filename = "Draft 5/Figures/dispensing-status.png", device = "png", height = 14, width = 25, units = "cm")
+
+disp_contrasts %>% 
+  arrange(drug) %>% 
+  kable
+
+```
+
+* Predicted dispensing of all drugs, inhaled corticosteroids, paracetamol, and salbutamol was higher for dispensing practices during March 2020.
+* Predicted dispensing of vitamin d was lower for dispensing practices from March to August 2020.
+
+### WIMD
+
+```{r, wimd-contrast-fig, fig.cap="WIMD contrasts and 95% confidence limits from GLS models."}
+wimd_contrasts <- 
+  list(
+    cortico = contrast(best_bs_models$cortico, 
+                       list(Month = 3:8, wimd2019 = "Low"),
+                       list(Month = 3:8, wimd2019 = "High")) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
+    sal = contrast(best_bs_models$sal, 
+                   list(Month = 3:8, wimd2019 = "Low"),
+                   list(Month = 3:8, wimd2019 = "High")) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
+    ssri = contrast(best_bs_models$ssri, 
+                       list(Month = 3:8, wimd2019 = "Low"),
+                       list(Month = 3:8, wimd2019 = "High")) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
+    vitd = contrast(best_bs_models$vitd, 
+                    list(Month = 3:8, wimd2019 = "Low"),
+                    list(Month = 3:8, wimd2019 = "High")) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame()
+  ) %>% 
+  bind_rows(.id = "drug")
+
+(wimd_plot <- wimd_contrasts %>% 
+  mutate(Month = factor(x = Month, levels = 3:8, 
+                           labels = month.abb[3:8])) %>% 
+  ggplot(aes(x = Month, col = drug)) +
+  geom_point(aes(y = Contrast), size = .5, position = position_dodge(.25)) +
+  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(.25),
+                width = 0) +
+  geom_hline(aes(yintercept = 0), colour = "grey") +
+  ggthemes::theme_few() +
+  scale_colour_viridis_d("Drug", drop = FALSE) +
+  ylab("High - Low WIMD"))
+
+ggsave(filename = "Draft 5/Figures/wimd.png", device = "png", height = 14, width = 25, units = "cm")
+
+wimd_contrasts %>% 
+  arrange(drug) %>% 
+  kable
+
+```
+
+### Number of GPs
+
+```{r, ngp-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
+ngp_contrasts <- 
+  list(
+    oral_contra = contrast(best_bs_models$oral_contra, 
+                       list(Month = 3:8, ngp = 3),
+                       list(Month = 3:8, ngp = 8)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
+    sal = contrast(best_bs_models$sal, 
+                   list(Month = 3:8, ngp = 3),
+                   list(Month = 3:8, ngp = 8)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame()) %>% 
+  bind_rows(.id = "drug")
+
+(ngp_plot <- ngp_contrasts %>% 
+  mutate(Month = factor(x = Month, levels = 3:8, 
+                           labels = month.abb[3:8])) %>% 
+  ggplot(aes(x = Month, col = drug)) +
+  geom_point(aes(y = Contrast), size = .5, position = position_dodge(.25)) +
+  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(.25),
+                width = 0) +
+  geom_hline(aes(yintercept = 0), colour = "grey") +
+  ggthemes::theme_few() +
+  scale_colour_viridis_d("Drug", drop = FALSE) +
+  ylab("8 GPs - 3 GPs"))
+
+ggsave(filename = "Draft 5/Figures/number-gps.png", device = "png", height = 14, width = 25, units = "cm")
+
+ngp_contrasts %>% 
+  arrange(drug) %>% 
+  kable
+
+```
+
+### GP load
+
+```{r, gpld-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
+gpld_contrasts <- 
+  list(
+    oral_contra = contrast(best_bs_models$oral_contra, 
+                       list(Month = 3:8, gp_load = 1098),
+                       list(Month = 3:8, gp_load = 1710)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame()) %>% 
+  bind_rows(.id = "drug")
+
+(gp_load_plot <- gpld_contrasts %>% 
+  mutate(Month = factor(x = Month, levels = 3:8, 
+                           labels = month.abb[3:8])) %>% 
+  ggplot(aes(x = Month, col = drug)) +
+  geom_point(aes(y = Contrast), size = .5, position = position_dodge(.25)) +
+  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(.25),
+                width = 0) +
+  geom_hline(aes(yintercept = 0), colour = "grey") +
+  ggthemes::theme_few() +
+  scale_colour_viridis_d("Drug", drop = FALSE) +
+  ylab("1710 per GP - 1098 per GP"))
+
+ggsave(filename = "Draft 5/Figures/gp-workload.png", device = "png", height = 14, width = 25, units = "cm")
+
+gpld_contrasts %>% 
+  arrange(drug) %>% 
+  kable
+
+```
+
+### Summary figure
+
+```{r, summary-plot}
+# names(drugs) <- c("ACE inhibitors", "Inhaled corticosteriods", "
+#                   Hydroxychloroquine", "Non-steroidal anti-inflamatory drugs",
+#                   "Oral contraceptives", "Paracetamol", "Salbutamol", )
+
+contrasts <- 
+  bind_rows(disp_contrasts, wimd_contrasts, ngp_contrasts, gpld_contrasts,
+            .id = "effect") %>% 
+  mutate(Month = factor(x = Month, levels = 3:8, 
+                           labels = month.abb[3:8]),
+         effect = case_when(effect == 1 ~ "Dispensing - Non-dispensing",
+                            effect == 2 ~ "High - Low WIMD",
+                            effect == 3 ~ "8 GPs - 3 GPs",
+                            effect == 4 ~ "1710 per GP - 1098 per GP"),
+         drug = case_when(drug == "all_drugs" ~ "All",
+                          drug == "ace" ~ "ACEi",
+                          drug == "cortico" ~ "Inhaled \ncorticosteriods",
+                          drug == "hcq" ~ "HCQ",
+                          drug == "nsaid" ~ "NSAIDs",
+                          drug == "oral_contra" ~ "Oral \ncontraceptives",
+                          drug == "paracet" ~ "Paracetamol",
+                          drug == "sal" ~ "Salbutamol",
+                          drug == "ssri" ~ "SSRIs",
+                          drug == "vitd" ~ "Vitamin D",
+                          drug == "warfarin" ~ "Warfarin",
+                          drug == "warfarin_ddd" ~"Warfarin"),
+         drug = factor(drug),
+         effect = factor(effect,
+                         levels = c("Dispensing - Non-dispensing", 
+                                    "High - Low WIMD",
+                                    "8 GPs - 3 GPs", 
+                                    "1710 per GP - 1098 per GP")))
+
+contrasts %>% 
+  ggplot(aes(x = Month, col = drug)) +
+  geom_point(aes(y = Contrast), size = .5, position = position_dodge(.25)) +
+  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(.25),
+                width = 0) +
+  geom_hline(aes(yintercept = 0), colour = "grey") +
+  ggthemes::theme_few() +
+  theme(legend.spacing.y = unit(0.5, 'cm')) +
+  guides(col = guide_legend(byrow = TRUE)) +
+  labs(col = "Drug") +
+  facet_wrap(~effect)
+
+ggsave(filename = "Draft 5/Figures/gls-summary-figure.png", device = "png", height = 14, width = 25, units = "cm")
+```

### 2022-02-23 writing/paper.Rmd
Set predicitor variables to median/mode values for gls contrasts

@@
     ngp = percentiles(gp_2020, ngp),
-    gp_load = percentiles(gp_2020, gp_load))
+    gp_load = percentiles(gp_2020, gp_load),
+    PC1 = percentiles(gp_2020, PC1),
+    PC2 = percentiles(gp_2020, PC2),
+    PC3 = percentiles(gp_2020, PC3),
+    PC4 = percentiles(gp_2020, PC4))
+
+median(gp_2020$PC1)
 ```
@@
             gp_load = 1329.486, 
-            PC1 = -0.1257104, PC2 = 0.1257104, PC3 = 0.1257104, PC4 = -0.09966945,
+            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
             conf.int = .95)
@@
     all_drugs = contrast(best_bs_models$all_drugs, 
-                         list(Month = 3:8, dispensing = TRUE),
-                         list(Month = 3:8, dispensing = FALSE)) %>% 
+                         list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                              ngp = 5, gp_load = 1329,
+                              PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                              PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                              dispensing = TRUE),
+                         list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                              ngp = 5, gp_load = 1329,
+                              PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                              PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                              dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     cortico = contrast(best_bs_models$cortico, 
-                       list(Month = 3:8, dispensing = TRUE),
-                       list(Month = 3:8, dispensing = FALSE)) %>% 
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = TRUE),
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     paracet = contrast(best_bs_models$paracet, 
-                       list(Month = 3:8, dispensing = TRUE),
-                       list(Month = 3:8, dispensing = FALSE)) %>% 
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = TRUE),
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     sal = contrast(best_bs_models$sal, 
-                   list(Month = 3:8, dispensing = TRUE),
-                   list(Month = 3:8, dispensing = FALSE)) %>% 
+                   list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                        ngp = 5, gp_load = 1329,
+                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                        dispensing = TRUE),
+                   list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                        ngp = 5, gp_load = 1329,
+                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                        dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     vitd = contrast(best_bs_models$vitd, 
-                    list(Month = 3:8, dispensing = TRUE),
-                    list(Month = 3:8, dispensing = FALSE)) %>% 
+                    list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                         ngp = 5, gp_load = 1329,
+                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                         PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                         dispensing = TRUE),
+                    list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
+                         ngp = 5, gp_load = 1329,
+                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                         PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                         dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
 
-ggsave(filename = "Draft 5/Figures/dispensing-status.png", device = "png", height = 14, width = 25, units = "cm")
+ggsave(filename = "Draft 5/Figures/dispensing-status.png", device = "png", 
+       height = 14, width = 25, units = "cm")
 
@@
     cortico = contrast(best_bs_models$cortico, 
-                       list(Month = 3:8, wimd2019 = "Low"),
-                       list(Month = 3:8, wimd2019 = "High")) %>% 
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE),
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     sal = contrast(best_bs_models$sal, 
-                   list(Month = 3:8, wimd2019 = "Low"),
-                   list(Month = 3:8, wimd2019 = "High")) %>% 
+                   list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE),
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     ssri = contrast(best_bs_models$ssri, 
-                       list(Month = 3:8, wimd2019 = "Low"),
-                       list(Month = 3:8, wimd2019 = "High")) %>% 
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE),
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     vitd = contrast(best_bs_models$vitd, 
-                    list(Month = 3:8, wimd2019 = "Low"),
-                    list(Month = 3:8, wimd2019 = "High")) %>% 
+                    list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE),
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     oral_contra = contrast(best_bs_models$oral_contra, 
-                       list(Month = 3:8, ngp = 3),
-                       list(Month = 3:8, ngp = 8)) %>% 
+                           list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                                ngp = 3, gp_load = 1329,
+                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                                dispensing = FALSE),
+                           list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                                ngp = 8, gp_load = 1329,
+                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                                dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     sal = contrast(best_bs_models$sal, 
-                   list(Month = 3:8, ngp = 3),
-                   list(Month = 3:8, ngp = 8)) %>% 
+                   list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                        ngp = 3, gp_load = 1329,
+                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                        dispensing = FALSE),
+                   list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                        ngp = 8, gp_load = 1329,
+                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                        dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
     oral_contra = contrast(best_bs_models$oral_contra, 
-                       list(Month = 3:8, gp_load = 1098),
-                       list(Month = 3:8, gp_load = 1710)) %>% 
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                        ngp = 8, gp_load = 1098,
+                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                        dispensing = FALSE),
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                        ngp = 8, gp_load = 1710,
+                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                        dispensing = FALSE)) %>% 
       .[c("Month", "Contrast", "Lower", "Upper")] %>% 
@@
   ggthemes::theme_few() +
-  theme(legend.spacing.y = unit(0.5, 'cm')) +
+  theme(legend.spacing.y = unit(0.5, 'cm'),
+        plot.caption = element_text(size = 8, hjust = 1)) +
   guides(col = guide_legend(byrow = TRUE)) +
   labs(col = "Drug") +
-  facet_wrap(~effect)
+  facet_wrap(~effect) +
+  labs(caption = paste0("Adjusted to Health Board = BC, Dispensing status = FALSE, WIMD = Med, Number GPs = 5, \nGP workload = 1329, PC1 = ", printnum(median(gp_2020$PC1))," PC2 = ", printnum(median(gp_2020$PC1)), " PC3 = ", printnum(median(gp_2020$PC3)), " PC4 = ", printnum(median(gp_2020$PC4))))
 

### 2022-02-23 writing/appendix_a.Rmd
Tidying and removing sections that are duplicated in paper.Rmd

@@
 plan(sequential)
+
+drugs <- unique(differences$drug)
 
@@
 ```{r, big-discrepacies, eval=FALSE}
-drugs <- unique(differences$drug)
 
@@
 ```{r, gls-functions}
-drugs <- unique(differences$drug)
 
@@
            pct_change = 100*(prop - 1)) %>% 
-    select(c(regional_unit, Month, pct_change))
-
-  baseline <- subset(df, Month == 2, -Month)
-  baseline <- upData(baseline, rename = c(pct_change = "feb_diff"), print = FALSE)
-  followup <- subset(df, Month > 2)
-  both <- merge(baseline, followup, by = c("regional_unit"))
-
-  #### Join GP and GLS data ####
-  both <- 
-    both %>% 
+    select(c(regional_unit, Month, pct_change)) %>% 
+    filter(Month > 2) %>% 
     left_join(gp_2020, by = "regional_unit") %>% 
@@
 
-  dd <- datadist(both)
+  dd <- datadist(df)
   options(datadist = "dd")
 
-  return(both)
-}
-
-#### Redundancy analysis model ####
-redun <- list()
-for(i in drugs){
-  redun[[i]] <- redun(~hboard + dispensing + Month + feb_diff + wimd2019 + 
-                        PC1 + PC2 + PC3 + PC4 + PC5 + ngp + gp_load,
-                      data = glsData(i), r2 = .8, type = "adjusted") %>% 
-    .$Out
-}
-
-# No redundent variables
-
-#### GLS Analysis function ####
-bestGLS <- function(data, bootstrap = FALSE){
-  cp <- list(corExp, corCompSymm, corLin, corGaus, corSpher)
-  z <- vector("list", length(cp))
-
-  ### Fit models
-  for(k in 1:length(cp)){
-    z[[k]] <- gls(pct_change ~ rcs(Month, 4:7) +
-                    hboard + dispensing +
-                    rcs(wimd2019, 4) + 
-                    rcs(ngp, 4) + rcs(gp_load, 4) + 
-                    rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                    rcs(PC4, 4) + rcs(PC5, 4) +
-                    hboard:rcs(Month, 4:7) +
-                    dispensing:rcs(Month, 4:7) +
-                    rcs(wimd2019, 4):rcs(Month, 4:7) +
-                    rcs(ngp, 4):rcs(Month, 4:7) +
-                    rcs(gp_load, 4):rcs(Month, 4:7),
-                  data = data,
-                  correlation = cp[[k]](form = ~ Month | regional_unit))
-  }
-
-  arma_tab <- # Table for p and q values for corARMA()
-    tibble(p = 1:3, 
-           q = rep(0,3)) %>% 
-    mutate(model = row_number() + length(cp))
-
-  z <- c(z, map2(.x = arma_tab$p, .y = arma_tab$q, 
-                 .f = ~ if(.x > 0 | .y >0)
-                 { # p = 0 & q = 0 fails
-                   tryCatch(
-                     {gls(pct_change ~ rcs(Month, 4:7) +
-                            hboard + dispensing +
-                            rcs(wimd2019, 4) + 
-                            rcs(ngp, 4) + rcs(gp_load, 4) + 
-                            rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                            rcs(PC4, 4) + rcs(PC5, 4) +
-                            hboard:rcs(Month, 4:7) +
-                            dispensing:rcs(Month, 4:7) +
-                            rcs(wimd2019, 4):rcs(Month, 4:7) +
-                            rcs(ngp, 4):rcs(Month, 4:7) +
-                            rcs(gp_load, 4):rcs(Month, 4:7),
-                          data = data,
-                          correlation = corARMA(form = ~ Month|regional_unit, 
-                                                p=.x, q=.y))
-                     },
-                     error = function(cond){
-                       message(paste("Model causing error: p = ", 
-                                     .x, "q = ", .y))
-                       message("Original error message:")
-                       message(cond)
-                       return(NULL)
-                     },
-                     warning = function(cond){
-                       message(paste("Model causing warning: p = ", 
-                                     .x, "q = ", .y))
-                       message("Original warning message:")
-                       message(cond)
-                       return(NULL)
-                     }
-                   )
-                 }))
-
-  ### Select best model
-  names(z) <- paste0("model", 1:length(z))
-  x <- z %>% 
-    map(summary)
-
-  # Get metrics for each model
-  aic <- map_dfr(x, pluck("AIC"), .id = "model") 
-  bic <- map_dfr(x, pluck("BIC"), .id = "model")
-  log_lik <- map_dfr(x, pluck("logLik"), .id = "model")
-
-  # Create table
-  mod_comparison <- 
-    bind_cols(metric = c("aic", "bic", "log_lik"), 
-              bind_rows(aic,bic,log_lik)) %>% 
-    pivot_longer(-metric) %>% 
-    pivot_wider(id_cols = name, values_from = value, names_from = metric) %>% 
-    rename(model = name) %>% 
-    mutate(model = as.numeric(str_remove_all(model, "model")))
-
-  # Select best model
-  best_model_aic <- 
-    mod_comparison %>% 
-    arrange(aic, bic, desc(log_lik)) %>% 
-    head(1) %>% 
-    .$model
-
-  ### Fit best model
-  if(bootstrap == TRUE){  
-    if(best_model_aic <= 6){
-      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
-                  hboard + dispensing +  
-                  rcs(wimd2019, 4) + 
-                  rcs(ngp, 4) + rcs(gp_load, 4) + 
-                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                  rcs(PC4, 4) + rcs(PC5, 4) +
-                  hboard:rcs(Month, 4:7) +
-                  dispensing:rcs(Month, 4:7) +
-                  rcs(wimd2019, 4):rcs(Month, 4:7) +
-                  rcs(ngp, 4):rcs(Month, 4:7) +
-                  rcs(gp_load, 4):rcs(Month, 4:7),
-                data = data, B = 1000,
-                correlation = 
-                  cp[[best_model_aic]](form = ~ Month | regional_unit))
-      }
-    else{
-      a <-  Gls(pct_change ~ rcs(Month, 4:7) +
-                  hboard + dispensing +  
-                  rcs(wimd2019, 4) + 
-                  rcs(ngp, 4) + rcs(gp_load, 4) + 
-                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                  rcs(PC4, 4) + rcs(PC5, 4) +
-                  hboard:rcs(Month, 4:7) +
-                  dispensing:rcs(Month, 4:7) +
-                  rcs(wimd2019, 4):rcs(Month, 4:7) +
-                  rcs(ngp, 4):rcs(Month, 4:7) +
-                  rcs(gp_load, 4):rcs(Month, 4:7),
-                data = data, B = 1000,
-                correlation = 
-                  corARMA(form = ~ Month | regional_unit, 
-                          p = filter(arma_tab, model == best_model_aic)$p, 
-                          q = filter(arma_tab, model == best_model_aic)$q))
-      }
-  }
-  else{
-    if(best_model_aic <= 6){
-      a <- Gls(pct_change ~ rcs(Month, 4:7) +
-                 hboard + dispensing +  
-                 rcs(wimd2019, 4) + 
-                 rcs(ngp, 4) + rcs(gp_load, 4) + 
-                 rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                 rcs(PC4, 4) + rcs(PC5, 4) +
-                 hboard:rcs(Month, 4:7) +
-                 dispensing:rcs(Month, 4:7) +
-                 rcs(wimd2019, 4):rcs(Month, 4:7) +
-                 rcs(ngp, 4):rcs(Month, 4:7) +
-                 rcs(gp_load, 4):rcs(Month, 4:7),
-               data = data,
-               correlation = 
-                 cp[[best_model_aic]](form = ~ Month | regional_unit))
-    }
-    else{
-      a <- Gls(pct_change ~ rcs(Month, 4:7) +
-                  hboard + dispensing +  
-                  rcs(wimd2019, 4) + 
-                  rcs(ngp, 4) + rcs(gp_load, 4) + 
-                  rcs(PC1, 4) + rcs(PC2, 4) + rcs(PC3, 4) + 
-                  rcs(PC4, 4) + rcs(PC5, 4) +
-                  hboard:rcs(Month, 4:7) +
-                  dispensing:rcs(Month, 4:7) +
-                  rcs(wimd2019, 4):rcs(Month, 4:7) +
-                  rcs(ngp, 4):rcs(Month, 4:7) +
-                  rcs(gp_load, 4):rcs(Month, 4:7),
-               data = data,
-               correlation = 
-                 corARMA(form = ~ Month | regional_unit, 
-                         p = filter(arma_tab, model == best_model_aic)$p, 
-                         q = filter(arma_tab, model == best_model_aic)$q))
-    }
-  }
-  return(a)
+  return(df)
 }
@@
   p1 <- ggplot(data, aes(x = fitted, y = resid)) + geom_point(alpha = .1) + y1
-  p2 <- ggplot(data, aes(x = feb_diff, y = resid)) + geom_point(alpha = .1) + y1
+  # p2 <- ggplot(data, aes(x = feb_diff, y = resid)) + geom_point(alpha = .1) + y1
   p3 <- ggplot(data, aes(x = Month, y = resid)) + y1 + 
@@
 
-  gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
+  gridExtra::grid.arrange(p1, #p2, 
+                          p3, p4, ncol = 2)
 }
@@
 
-  p1 <- Predict(model, Month, dispensing, hboard,
-                PC1 = percentiles(data, PC1),
-                conf.int = .95) %>% 
-    predictPlot(., groups = PC1, "PC1")
-  p2 <- Predict(model, Month, dispensing, hboard,
-                PC2 = percentiles(data, PC2),
-                conf.int = .95) %>% 
-    predictPlot(., groups = PC2, "PC2")
-  p3 <- Predict(model, Month, dispensing, hboard,
-                PC3 = percentiles(data, PC3),
-                conf.int = .95) %>% 
-    predictPlot(., groups = PC3, "PC3")
-  p4 <- Predict(model, Month, dispensing, hboard,
-                PC4 = percentiles(data, PC4),
-                conf.int = .95) %>% 
-    predictPlot(., groups = PC4, "PC4")
-  gridExtra::grid.arrange(p1,p2,p3,p4, ncol = 2, newpage = TRUE) # Effects 6
-  cat("\n\n")
+  # p1 <- Predict(model, Month, dispensing, hboard,
+  #               PC1 = percentiles(data, PC1),
+  #               conf.int = .95) %>% 
+  #   predictPlot(., groups = PC1, "PC1")
+  # p2 <- Predict(model, Month, dispensing, hboard,
+  #               PC2 = percentiles(data, PC2),
+  #               conf.int = .95) %>% 
+  #   predictPlot(., groups = PC2, "PC2")
+  # p3 <- Predict(model, Month, dispensing, hboard,
+  #               PC3 = percentiles(data, PC3),
+  #               conf.int = .95) %>% 
+  #   predictPlot(., groups = PC3, "PC3")
+  # p4 <- Predict(model, Month, dispensing, hboard,
+  #               PC4 = percentiles(data, PC4),
+  #               conf.int = .95) %>% 
+  #   predictPlot(., groups = PC4, "PC4")
+  # gridExtra::grid.arrange(p1,p2,p3,p4, ncol = 2, newpage = TRUE) # Effects 6
+  # cat("\n\n")
 
@@
 
-```{r, gls-analysis-save, results="asis", fig.cap=gls_analysis_fig_cap, warning=FALSE, message=FALSE, eval = FALSE}
-#### gls-analysis-save ####
-drugs <- unique(differences$drug)
-
-best_models <- list()
-best_bs_models <- list()
-
-dd <- NULL
-for(i in drugs){
-  gls_data <- glsData(i)
-  dd <- datadist(gls_data)
-  options(datadist = "dd")
-  best_gls <- bestGLS(gls_data)
-  best_bs_gls <- bestGLS(gls_data, TRUE)
-  rm(dd)
-  best_models[[i]] <-
-    best_gls
-  best_bs_models[[i]] <- 
-    best_bs_gls
-  options(datadist = NULL)
-}
-
-write_rds(best_models, "../data/gls/best_models.rds")
-write_rds(best_bs_models, "../data/gls/best_bs_models.rds")
-```
-
 ```{r, gls-analysis-read}
@@
 #### gls-effects ####
-drugs <- unique(differences$drug)
 
@@
   kable(booktabs = TRUE, linesep = "",
-        caption = paste("Wald test p-values"))%>% 
+        caption = paste("Wald test p-values")) %>% 
   kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 

### 2022-02-23 writing/appendix_a.Rmd
Removed sections duplicated between paper, supplementay info, and appendix

@@
 
-## GP PCA
-
-```{r, gp-pca, fig.cap="Variance of QoF variables explained by individual principal components (lines) with cumulative proportion of variance explained (text)."}
-#### Data ####
-gp_2020 <- 
-  filter(gp, year == 2020) %>% 
-  rename(regional_unit = practice_id)
-
-#### Functions ####
-# Add cumulative fraction of variance explained
-addScree <- function(x, npcs=min(10, length(x$sdev)),
-                     plotv = FALSE,
-                     col = 1, offset = .8, adj = 0, pr = FALSE){
-  vars <- x$sdev^2
-  cumv <- cumsum(vars)/sum(vars)
-  if(pr) print(cumv)
-  text(1:npcs, vars[1:npcs] + offset*par("cxy")[2],
-       as.character(round(cumv[1:npcs], 2)),
-       srt = 45, adj = adj, cex = .65, xpd = NA, col = col)
-}
-
-#### Analysis ####
-gp_pca <- 
-  prcomp(select(gp_2020, c(chd:flu, p_fem, pm_65, pf_65)), center = TRUE, scale. = TRUE)
-
-plot(gp_pca, type = "lines", main = " ", pch = 3)
-addScree(gp_pca)
-abline(h = 1, col = "blue")
-
-gp_2020 <- 
-  gp_2020 %>% 
-  left_join(bind_cols(regional_unit = gp_2020$regional_unit, gp_pca$x), 
-            by = "regional_unit") %>% 
-  select(regional_unit = regional_unit, everything(),
-         -c(practiceid, county, postcode, lsoacode, easting, northing,
-            chd:flu, PC6:PC20, year))
-```
-
-```{r, gp-pca-direction, fig.cap=c("QoF disease register loadings on PC 1-2","QoF disease register loadings on PC 2-3","QoF disease register loadings on PC 3-4","QoF disease register loadings on PC 4-5")}
-p1 <- ggbiplot(gp_pca, ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
-         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
-      scale_colour_viridis_d(name = "Health board")
-p2 <- ggbiplot(gp_pca, choices = 2:3,
-         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
-         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
-      scale_colour_viridis_d(name = "Health board")
-p3 <- ggbiplot(gp_pca, choices = 3:4,
-         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
-         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
-      scale_colour_viridis_d(name = "Health board")
-p4 <- ggbiplot(gp_pca, choices = 4:5,
-         ellipse = FALSE, groups = gp_2020$hboard, obs.scale = 1, 
-         var.scale = 1, alpha = .3, varname.size = 5, varname.adjust = 5)  +
-      scale_colour_viridis_d(name = "Health board")
-p1
-cat("\n\n")
-p2
-cat("\n\n")
-p3
-cat("\n\n")
-p4
-cat("\n\n")
-
-```
-
-## Excluded practices
-
-Table with a row for each drug and a column for each reason a practice could be excluded, with a total column at the end
-
-(a) missing any data in the COVID months, (b) more than 10% of the pre-COVID data (i.e., 6 months) missing, or (c) MAPE >50.
-
-```{r, excluded-practices-tab, eval=TRUE}
-months <- c("2015 Jan","2015 Feb","2015 Mar","2015 Apr","2015 May","2015 Jun",
-            "2015 Jul","2015 Aug","2015 Sep","2015 Oct","2015 Nov","2015 Dec",
-            "2016 Jan","2016 Feb","2016 Mar","2016 Apr","2016 May","2016 Jun",
-            "2016 Jul","2016 Aug","2016 Sep","2016 Oct","2016 Nov","2016 Dec",
-            "2017 Jan","2017 Feb","2017 Mar","2017 Apr","2017 May","2017 Jun",
-            "2017 Jul","2017 Aug","2017 Sep","2017 Oct","2017 Nov","2017 Dec",
-            "2018 Jan","2018 Feb","2018 Mar","2018 Apr","2018 May","2018 Jun",
-            "2018 Jul","2018 Aug","2018 Sep","2018 Oct","2018 Nov","2018 Dec",
-            "2019 Jan","2019 Feb","2019 Mar","2019 Apr","2019 May","2019 Jun",
-            "2019 Jul","2019 Aug","2019 Sep","2019 Oct","2019 Nov","2019 Dec",
-            "2020 Jan","2020 Feb","2020 Mar","2020 Apr","2020 May","2020 Jun",
-            "2020 Jul","2020 Aug")
-
-monthlyPrescribing <- 
-  function(data){
-    data %>% 
-      janitor::clean_names() %>% 
-      mutate(datename = dmy(paste0("28-", datename)),
-             practice_id = as.character(practice_id)) %>% 
-      countRegional(practice_id, datename, quantity) %>% 
-      mutate(year = year(datename)) %>%
-      as_tibble() %>% 
-      inner_join(gp %>% 
-                   select(practice_id, year, npat), 
-                 by = c("regional_unit" = "practice_id", "year")) %>% 
-      mutate(n = 1000*n/npat,
-             datename = yearmonth(datename),
-             regional_unit = as_factor(regional_unit)) %>% 
-      select(-c(npat, year)) %>% 
-      as_tsibble(index = datename, key = regional_unit) %>% 
-      fill_gaps()
-  }
-
-gpMissing <- 
-  function(data){
-    data %>% 
-      as_tibble() %>% 
-      pivot_wider(id_cols = regional_unit, names_from = datename,
-                  values_from = n, values_fill = NA) %>% 
-      select(all_of(months), everything()) %>% 
-      rowwise() %>% 
-      mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
-      group_by(regional_unit) %>% 
-      summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2019 Dec`)),
-                miss_covid = sum(c_across(`2020 Jan`:`2020 Aug`))) %>% 
-      filter(miss_covid > 0 | miss_non_covid > 0) %>% 
-      mutate(miss_10_non_covid = if_else(miss_non_covid >= 60/10, TRUE, FALSE))
-  }
-
-missRemove <- 
-  function(data){
-    data %>% 
-      mutate(remove = if_else((miss_covid > 0 | miss_10_non_covid == TRUE), 
-                              TRUE, FALSE)) %>% 
-      summarise(miss_covid = sum(if_else(miss_covid > 0, TRUE, FALSE)),
-                miss_10_non_covid = sum(if_else(miss_non_covid >= 60/10, TRUE,
-                                                FALSE)),
-                miss_either = sum(if_else(remove == TRUE, TRUE, FALSE)))
-  }
-
-plan(cluster)
-
-full_data <- 
-  data_files[grep(pattern = "../data/prescribing_data/warfarin_ddd_nat.rds",
-                x = data_files, value = FALSE, invert = TRUE)] %>% 
-  furrr::future_map(read_rds)
-
-n_practices <- 
-  full_data %>% 
-  map(pluck("practice_id")) %>% 
-  map(unique) %>% 
-  map_dfr(length) %>% 
-  pivot_longer(cols = everything(), names_to = "drug", values_to = "n")
-
-missing_gp  <-
-  full_data %>% 
-  map(pluck("practice_id")) %>% 
-  map(unique) %>% 
-  map_dfr(~length(.)-sum(. %in% gp$practice_id), .id = "drug") %>% 
-  pivot_longer(cols = everything(), names_to = "drug", 
-               values_to = "missing_gp")
-
-missing_raw_data <- 
-  full_data %>% 
-  furrr::future_map(monthlyPrescribing) %>% 
-  furrr::future_map(gpMissing) %>% 
-  furrr::future_map_dfr(missRemove, .id = "drug")
-
-poor_forcasts <- 
-  cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE >= 50) %>% 
-  group_by(drug) %>% 
-  summarise(mape_over_50 = n())
-plan(sequential)
-
-n_practices %>% 
-  left_join(missing_gp, by = "drug") %>% 
-  left_join(missing_raw_data, by = "drug") %>% 
-  left_join(poor_forcasts, by = "drug") %>% 
-  mutate(drug = str_remove_all(drug, "ddd_"),
-         drug = str_remove_all(drug, "quant_"),
-         drug = str_remove_all(drug, "_ddd"),
-         drug = relevel(as_factor(drug), ref = "all_drugs")) %>%
-  rowwise() %>% 
-  mutate(mape_over_50 = if_else(is.na(mape_over_50), as.integer(0), mape_over_50),
-         total_removed = missing_gp + miss_either + mape_over_50, 
-         n_rem = n - total_removed) %>% 
-  knitr::kable(booktabs = TRUE, linesep = "", 
-               col.names = c("Drug", "n", "GP", "COVID", "10% non-COVID",
-                             "Dispensing", "MAPE >50", "Total", "Remain"),
-               caption = "Summary of GP practices removed for each drug.") %>% 
-  kableExtra::add_header_above(c(" "= 2, "Missing" = 4, "Removed" = 2, " " = 1)) %>% 
-  footnote(general = '"Dispensing" is not always equal to the sum of COVID and 10% non-COVID, as a single practice may be missing both data in covid months and more than 10% of data in the non-covid months, but will only be excluded once.',
-           threeparttable = TRUE)
-
-```
-
-```{r, big-discrepacies, eval=FALSE}
-
-bigDiscreps <- function(x){
-  message(x)
-
-  big_discreps2 <- 
-    differences %>% 
-    filter(drug == x) %>% 
-    filter(prop <.3| prop > 2) %>% 
-    group_by(regional_unit) %>% 
-    count()
-
-  differences %>% 
-    filter(drug == x) %>% 
-    filter(regional_unit %in% big_discreps2$regional_unit) %>% 
-    mutate(uid = paste(x, regional_unit)) %>% 
-    ggplot(aes(x = datename, col = as.factor(regional_unit))) +
-    geom_line(aes(y = med), lty = 1) +
-    geom_line(aes(y = n), lty = 2) +
-    facet_wrap(~uid, scales = "free") +
-    theme(legend.position = "none")
-}
-
-map(.x = drugs, .f = ~bigDiscreps(.x))
-
-```
-
-## Forecasting
-
-### Forecasting models
-
-* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
-* We used the `fable` [@R-fable] and `fasster` [@R-fasster] packages to conduct the time series analyses.
-  * Time series linear model
-    * $y_t = \beta_0 + \beta_1x_t + \varepsilon_t$
-  * Simple methods
-      * Naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_T$
-      * Seasonal naïve (with and without drift)
-        * $\hat{y}_{T+h|T} = y_{T-m(k+1)}$ where $m$ = seasonal period and $k$ is the complete years in $T+h$
-  * Seasonal and Trend decomposition using Loess (STL) model [@Cleveland1990]
-    * Fixed and variable seasonality
-  * Autoregressive integrated moving average [ARIMA; @Box2015]
-    * Using a version of the Hyndman-Khandakar algorithm [@Hyndman2008]
-  * Exponential smoothing [@Holt2004; @Winters1960]
-    * Simple exponential smoothing
-    * Holt-Winters Additive Model [@Chatfield1978]
-  * Forecasting with Additive Switching of Seasonality, Trends and Exogenous Regressors [fasster; @R-fasster]
-    * State space model
-  * Combination models [cf. @Clemen1989; @Thomson2019]
-    * Forecasts that are made by combining models are often more accurate than those of the individual forecasts and often a simple average can significantly improve forecast accuracy.
-
-* Prescribing quantities were log transformed and the forecasts use median estimates of prescribing to reduce bias that back transformation would introduce when using the mean
-* Using January 2015 to December 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
-  * Started with 36 months of data, used an 8-month horizon as this was the horizon we would be using for the forecasts, 1-month step
-    * Only interested in one forecast horizon: eight-months
-
-```{r, time-series-model-tab}
-
-readxl::read_xlsx("time_series_models.xlsx") %>% 
-    knitr::kable(booktabs = TRUE, linesep = "",
-               caption = "Description of time series models used.")
-
-```
-
-## Reproducability and code
-
-We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.
-
-## Cross-validated model accuracy
-
-```{r, cv-model-accuracy-by-drug-tab, eval=FALSE}
-cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
-  mutate(drug = str_remove_all(drug, "ddd_"),
-         drug = str_remove_all(drug, "quant_"),
-         drug = str_remove_all(drug, "_ddd"),
-         drug = relevel(as_factor(drug), ref = "all_drugs")) %>%
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE < 50) %>% 
-  group_by(drug) %>% 
-  summarise(n_practice_retained = n(),
-            mape_mean = mean(MAPE),
-            mape_sd = sd(MAPE)) %>% 
-  kable(caption = "Accuaracy of cross-validated models retained for forecasting.",
-               digits = 2)
-```
-
-```{r, individual-drug-accuracy-plot, fig.cap="Accuracy of best model for each regional unit by drug, as measured by mean absoloute percentage error (MAPE).
-Models with MAPE > 50 have been removed.
-ACEi = ACE inhibitors, BAA = Beta~2~ adrenoceptor agonists, HCQ = Hydroxycholoroquine."}
-
-plan(cluster)
-cv_model_files %>% 
-  furrr::future_map_dfr(.id = "drug", .f = read_rds) %>% 
-  mutate(drug = str_remove_all(drug, "ddd_"),
-         drug = str_remove_all(drug, "quant_"),
-         drug = str_remove_all(drug, "_ddd"),
-         drug = case_when(drug == "all_drugs" ~ "All",
-                          drug == "ace" ~ "ACEi",
-                          drug == "adreno" ~ "BAA",
-                          drug == "cortico" ~ "Inhaled \ncortico",
-                          drug == "hcq" ~ "HCQ",
-                          drug == "nsaid" ~ "NSAIDs",
-                          drug == "oral_contra" ~ "Oral\ncontra",
-                          drug == "paracet" ~ "Paracet",
-                          drug == "ssri" ~ "SSRIs",
-                          drug == "vitd" ~ "Vit D",
-                          drug == "warfarin" ~ "Warfarin"),
-         drug = relevel(as_factor(drug), ref = "All")) %>%
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE < 50) %>% 
-  ggplot(aes(x = drug, y = MAPE, col = drug)) +
-  geom_violin() +
-  geom_jitter(alpha = .1) +
-  xlab("Medicine group") +
-  theme(legend.position = "none")
-
-```
-
-```{r best-cv-model-type, fig.cap="Performance by model type."}
-plan(cluster)
-cv_model_files %>% 
-  map_dfr(.id = "drug", .f = read_rds) %>% 
-  rankModels() %>% 
-  group_by(drug, regional_unit) %>% 
-  slice(1, .preserve = TRUE) %>% 
-  filter(MAPE < 50) %>% 
-  ggplot(aes(x = as.factor(.model))) +
-  geom_bar(aes(fill = as.factor(drug)), col = "black", size = .25) +
-  theme(axis.text.x = element_text(angle = 90))
-plan(sequential)
-```
-
-## Warfarin
-
-```{r, oac-gen-trend, fig.cap="Warfarin as a percentage of all oral anticoagulant prescribing in Wales. Pink shading covers duration of Wales' \"stay at home\" order."}
-read_rds("../data/prescribing_data/warfarin_ddd.rds") %>% 
-  dplyr::group_by(datename) %>% 
-  dplyr::summarise(quantity = median(quantity, na.rm = TRUE)) %>% 
-  mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
-  ggplot(aes(x = datename)) + 
-  geom_rect(aes(xmin = dmy("01-03-2020"), xmax = dmy("31-07-2020"), 
-                ymin = -Inf, ymax = Inf),
-            fill = 'pink', col = 0, alpha = 0.03) +
-  geom_line(aes(y = quantity)) +
-  geom_vline(aes(xintercept = dmy("01-03-2020")), lty = 2, col = "red") +
-  scale_x_yearmonth() +
-  xlab("Date") +
-  ylab("Warfarin (percentage of all OACs)") +
-  ylim(0, 100) # Dyfrig's request
-
-```
-
 ## GLS Results
@@
 ```{r, gls-functions}
-
-#### Prep GLS data ####
-glsData <- function(data){
-  df <- 
-    differences %>% 
-    filter(drug == data) %>% 
-    mutate(Month = as.numeric(as.factor(datename)),
-           pct_change = 100*(prop - 1)) %>% 
-    select(c(regional_unit, Month, pct_change)) %>% 
-    filter(Month > 2) %>% 
-    left_join(gp_2020, by = "regional_unit") %>% 
-    mutate(gp_load = npat / ngp)
-
-  dd <- datadist(df)
-  options(datadist = "dd")
-
-  return(df)
-}
 
@@
 #### GLS Estimated Effects ####
-percentiles <- function(data, var){
-  # return vector of 5th, 25th, 50th, 75th, and 95th percentile
-  var <- enquo(var)
-  data %>% 
-    summarise(enframe(stats::quantile(!!var, c(.05, .25, .5, .75, .95)), 
-                      "Percentile", "value"), .groups = "drop") %>% 
-    mutate(value = round(value)) %>% .$value
-}
-
-# dodge <- position_dodge(width = .25)
-predictPlot <- function(data = ., groups, names){
-  groups <- enquo(groups)
-  data %>% 
-    tibble() %>% 
-    group_by(Month, !!groups) %>% 
-    summarise(yhat = mean(yhat)) %>% 
-    mutate(groups = as.factor(!!groups)) %>% 
-    ggplot(aes(x = Month, y = yhat, group = groups)) +
-    geom_line(aes(col = groups)) +
-    scale_colour_viridis_d(name = names) +
-    scale_fill_viridis_d(name = names) +
-    theme(legend.position = "top") +
-    ylab(bquote(~X~hat(beta))) +
-    ggthemes::theme_hc()
-}
 
@@
 
-gls_analysis_fig_cap <- NULL
-for (i in 1:length(drugs)) {
-  gls_analysis_fig_cap <- 
-    c(gls_analysis_fig_cap, 
-      paste(drugs[i], c("Assumptions", "Health board effects.", "Dispensing status effect.", "WIMD effects.
-Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Number of GPs effects.
-Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Patients per GP effects.
-Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Patient related variable principal components 1-4 effects.
-Lines represent the 5th, 25th, 50th, 75th, and 95th quantiles.", "Relative importance of effects.")))
-}
-
 ```

### 2022-02-23 writing/paper.Rmd
Removed sections duplicated between paper, supplementay info, and appendix

@@
                       "Percentile", "value"), .groups = "drop") %>% 
-    mutate(value = round(value)) %>% .$value
+    mutate(value = round(value, 2)) %>% .$value
 }
@@
 ```{r, gls-functions, echo=FALSE}
-drugs <- unique(differences$drug)
+drugs <- unique(differences$drug) # Remove? Should be in setup
+
+## Assumption checking? ##
 
@@
 ## WIMD
-drugs_wimd <- c("cortico", "sal", "ssri", "vitd")
+drugs_wimd <- c("ace", "cortico", "sal", "ssri", "vitd")
 
@@
 
-median(gp_2020$PC1)
 ```
@@
   list(
+    ace = contrast(best_bs_models$ace, 
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE),
+                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
+                            ngp = 5, gp_load = 1329,
+                            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
+                            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
+                            dispensing = FALSE)) %>% 
+      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
+      as.data.frame(),
     cortico = contrast(best_bs_models$cortico, 

### 2022-04-27 writing/paper.Rmd
Tidying

@@
   str_remove_all(list.files("../data/prescribing_data"), ".rds")
-# 
-# gp_extract <- 
-#   map_dfr(.x = data_files[1:11],
-#           .f = ~(read_rds(.x)),
-#           .id = "drug")
-
-# Functions
+
+#### Functions ####
 
@@
   return(df)
+}
+
+#### Assumption checking ####
+glsAssump <- function(model, data){
+  data$resid <- r <- resid(model); data$fitted <- fitted(model)
+  y1 <- ylab("Residuals")
+  p1 <- ggplot(data, aes(x = fitted, y = resid)) + geom_point(alpha = .1) + y1
+  p2 <- ggplot(data, aes(x = Month, y = resid)) + y1 + 
+    stat_summary(fun.data = "mean_sdl", geom = "smooth")
+  p3 <- ggplot(data, aes(sample = resid)) + stat_qq(alpha = .1) + 
+    geom_abline(intercept = mean(r), slope = sd(r)) + y1
+  p4 <- textGrob(drugs[i])
+
+  gridExtra::grid.arrange(p1, p2, 
+                          p3, p4, ncol = 2)
 }
@@
 
+drugs <- unique(differences$drug)
+drugs <- factor(drugs)
+drugs <- relevel(drugs, ref = "all_drugs")
 ```
@@
 
-```{r, table-2}
+### 2019 dispensing summary
+
+```{r, table-2a}
 tibble(regional_unit = unique(differences$regional_unit)) %>% 
@@
               janitor::clean_names() %>%  
-              filter(year == 2020)) %>% 
+              filter(year == 2020),
+            by = "regional_unit") %>% 
   select(npat, ngp, dispensing, wimd2019:flu) %>% 
-  mutate(across(p_male:flu, ~.x*100)) %>% 
+  mutate(across(p_male:flu, ~.x*100),
+         dispensing = if_else(dispensing == "Yes", 1, 0)) %>% 
   tibble() %>% 
@@
 
-```{r}
+### 2020 GP practice summary
+
+```{r, table-2b}
 plan(cluster)
@@
   furrr::future_map_dfr(as_tibble, .id = "drug") %>% 
-  filter(year(datename) == 2019)
+  filter(year(datename) == 2019) %>% 
+  mutate(drug = relevel(as_factor(drug), ref = "quant_all_drugs"),
+         drug = str_remove_all(drug, "ddd_"),
+         drug = str_remove_all(drug, "quant_"),
+         drug = str_remove_all(drug, "_ddd"))
 plan(sequential)
@@
 pres_2019 %>% 
-  right_join(differences %>% 
+  left_join(differences %>% 
                group_by(regional_unit, drug) %>% 
@@
   filter(drug != "warfarin_ddd") %>% 
-  bind_rows(read_rds(data_files[12]) %>% 
+  bind_rows(read_rds(data_files["warfarin_ddd"]) %>% 
               mutate(drug = "warfarin_ddd",
@@
             max = max(n, na.rm = TRUE)) %>% 
-  left_join(differences %>% 
-              dplyr::group_by(drug) %>% 
-              dplyr::count() %>% 
-              mutate(n = n/8), by = "drug") %>% 
-  select(drug, n, everything()) %>% 
+  mutate(drug = relevel(as_factor(drug), ref = "all_drugs")) %>% 
+  select(drug, everything()) %>% 
+  arrange(drug) %>% 
   kable(digits = 2)
@@
                            labels = month.abb[1:8])) %>% 
-  dplyr::mutate(drug = case_when(drug == "all_drugs" ~ "All",
+  dplyr::mutate(drug = case_when(drug == "all_drugs" ~ "All dispensing",
                           drug == "ace" ~ "ACEi",
@@
                           drug == "warfarin_ddd" ~"Warfarin"),
-         drug = relevel(as_factor(drug), ref = "All"),
+         drug = relevel(as_factor(drug), ref = "All dispensing"),
          line_type = if_else(Percentile == "50%", "Median", "Decile")) %>%
@@
 Please note the different y-axis scales across the plots.
-ACEi = ACE inhibitors, HCQ = Hydroxycholoroquine."}
+ACEi = ACE inhibitors, HCQ = Hydroxycholoroquine.", cache=TRUE}
 plan(cluster)
@@
   group_by(.model, regional_unit, .rep) %>% 
-  dplyr::summarise(.sim = sum(.sim)) %>%
+  dplyr::summarise(.sim = sum(.sim), 
+                   .groups = "drop_last") %>%
   # Store as a distribution
-  dplyr::summarise(total = distributional::dist_sample(list(.sim))) %>% 
+  dplyr::summarise(total = distributional::dist_sample(list(.sim)), 
+                   .groups = "drop_last") %>% 
   mutate(mean = mean(total),
@@
   group_by(.model, regional_unit, .rep) %>% 
-  dplyr::summarise(.sim = sum(.sim)) %>%
+  dplyr::summarise(.sim = sum(.sim),
+                   .groups = "drop_last") %>%
   # Store as a distribution
-  dplyr::summarise(total = distributional::dist_sample(list(.sim))) %>% 
+  dplyr::summarise(total = distributional::dist_sample(list(.sim)),
+                   .groups = "drop_last") %>% 
   mutate(mean = mean(total),
@@
         caption = "Monthly percentage change in prescribing") %>%
-  kable_styling(font_size = 8) %>% 
+  kable_styling(font_size = 10) %>% 
   add_header_above(header = c(" " = 1,
@@
 
-```{r, gls-functions, echo=FALSE}
-drugs <- unique(differences$drug) # Remove? Should be in setup
-
-## Assumption checking? ##
-
-#### Redundancy analysis model ####
-redun <- list()
-for(i in drugs){
-  redun[[i]] <- redun(~hboard + dispensing + Month + wimd2019 + 
-                        PC1 + PC2 + PC3 + PC4 + PC5 + ngp + 
-                        gp_load,
-                      data = glsData(i), r2 = .8, type = "adjusted") %>% 
-    .$Out
-}
-
-# redun # No redundant variables
-
-#### Collinearity diagnostics ####
-colin <- list()
-for(i in drugs){
-  dd <- datadist(glsData(i))
-  options(datadist = "dd")
-  colin[[i]] <- sum(vif(ols(pct_change ~ hboard + dispensing + Month + wimd2019 + 
-                        PC1 + PC2 + PC3 + PC4 + ngp + 
-                          gp_load,
-                      data = glsData(i))) >= 5)
-  options(datadist = NULL)
-}
-
-# colin # no VIF >= 5
-```
-
 ```{r, gls-analysis-save, results="asis", warning=FALSE, message=FALSE, eval = FALSE}
 #### gls-analysis-save ####
-drugs <- unique(differences$drug)
-
 best_models <- list()
@@
 
+```{r, gls-analysis-read}
+#### gls-analysis-read ####
+best_models <- read_rds("../data/gls/best_models.rds")
+best_bs_models <- read_rds("../data/gls/best_bs_models.rds")
+```
+
+```{r, gls-functions, echo=FALSE}
+#### Assumption checking ####
+dd <- NULL
+for(i in 1:length(best_bs_models)){
+  gls_data <- glsData(drugs[i])
+  dd <- datadist(gls_data)
+  options(datadist = "dd")
+  glsAssump(best_bs_models[[i]], gls_data)
+  rm(dd)
+  options(datadist = NULL)
+}
+
+#### Redundancy analysis model ####
+redun <- list()
+for(i in drugs){
+  redun[[i]] <- redun(~hboard + dispensing + Month + wimd2019 + 
+                        PC1 + PC2 + PC3 + PC4 + PC5 + ngp + 
+                        gp_load,
+                      data = glsData(i), r2 = .8, type = "adjusted") %>% 
+    .$Out
+}
+
+# redun # No redundant variables
+
+#### Collinearity diagnostics ####
+colin <- list()
+for(i in drugs){
+  dd <- datadist(glsData(i))
+  options(datadist = "dd")
+  colin[[i]] <- sum(vif(ols(pct_change ~ hboard + dispensing + Month + wimd2019 + 
+                        PC1 + PC2 + PC3 + PC4 + ngp + 
+                          gp_load,
+                      data = glsData(i))) >= 5)
+  options(datadist = NULL)
+}
+
+# colin # no VIF >= 5
+```
+
 ```{r, gls-anova-summary-tab}
-best_bs_models <- read_rds("../data/gls/best_bs_models.rds")
-
 #### ANOVA Table ####
@@
 ```{r, gp-2020-percentiles, include=FALSE}
-gp_2020_percentiles <- 
+(gp_2020_percentiles <- 
    data.frame(
      percentile = c(5, 25, 50, 75, 95),
-    # wimd2019 = percentiles(gp_2020, wimd2019),
      ngp = percentiles(gp_2020, ngp),
@@
      PC3 = percentiles(gp_2020, PC3),
-    PC4 = percentiles(gp_2020, PC4))
-
-```
-
-* Figures represent predicted changes to dispensing based on GLS models
-* When considering the effect of a specific predictor over time, all other predictors will be set to the median value for continuous predictors and the mode for categorical predictors.
-*
-
-### Month
-
-```{r gls-month-fig, fig.cap="Dispensing by health board", eval=FALSE}
-dd <- NULL
-gls_month_fig <- list()
-for(i in drugs){
-  dd <- datadist(glsData(i))
-  options(datadist = "dd")
-  gls_month_fig[[i]] <- 
-    Predict(best_bs_models[[i]], Month, 
-            hboard = "BC", dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
-            gp_load = 1329.486, 
-            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
-            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
-            conf.int = .95)
-
-  options(datadist = NULL)
-}
-
-gls_month_fig %>% 
-  map_dfr(as_tibble, .id = "drug") %>% 
-  mutate(drug = as.factor(drug),
-           drug = relevel(drug, ref = "all_drugs")) %>%
-  ggplot(aes(x = Month, y = yhat)) +
-  geom_line() +
-  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) +
-  facet_wrap(~drug, scales = "free_y")
-
-```
-
-* This is broadly a repeat of what is seen in Figure 2 and what is described in the text referring to that section, therefore will not be repeated here.
-
-### Health board
-
-```{r gls-hb-fig-panel, fig.cap="Dispensing by health board"}
-dd <- NULL
-gls_hb_fig <- list()
-for(i in drugs_hb){
-  dd <- datadist(glsData(i))
-  options(datadist = "dd")
-  gls_hb_fig[[i]] <- 
-    Predict(best_bs_models[[i]], Month, hboard,
-            dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
-            gp_load = 1329.486, 
-            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
-            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
-            conf.int = .95)
-
-  options(datadist = NULL)
-}
-
-gls_hb_fig %>% 
-  map_dfr(as_tibble, .id = "drug") %>% 
-  dplyr::mutate(Month = factor(x = Month, levels = 3:8, 
-                           labels = month.abb[3:8]),
-                drug = case_when(drug == "all_drugs" ~ "All",
-                          drug == "ace" ~ "ACEi",
-                          drug == "cortico" ~ "Inhaled \ncorticosteriods",
-                          drug == "hcq" ~ "HCQ",
-                          drug == "nsaid" ~ "NSAIDs",
-                          drug == "oral_contra" ~ "Oral \ncontraceptives",
-                          drug == "paracet" ~ "Paracetamol",
-                          drug == "sal" ~ "Salbutamol",
-                          drug == "ssri" ~ "SSRIs",
-                          drug == "vitd" ~ "Vitamin D",
-                          drug == "warfarin" ~ "Warfarin",
-                          drug == "warfarin_ddd" ~"Warfarin")) %>% 
-  ggplot(aes(x = Month, y = yhat, col = as.factor(hboard), group = hboard)) +
-  geom_line(alpha = 0, position = position_dodge(.7)) +
-  geom_point(position = position_dodge(.7), size = .5) +
-  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5, 
-                position = position_dodge(.7)) +
-  ggthemes::theme_few() +
-  guides(col = guide_legend(ncol = 2)) +
-  theme(legend.position = c(.8,.1),
-        legend.title = element_text(size = 10, face = "bold", hjust = .5),
-        legend.text = element_text(size = 10)) +
-  scale_colour_viridis_d("Health board") +
-  facet_wrap(~drug, scales = "free_y")
-
-ggsave(filename = "Draft 5/Figures/health-board.png", device = "png", height = 14, width = 25, units = "cm")
-
-```
-
-* Seven of the eleven groups of medicines were dispensed differently across health boards.
-*
+     PC4 = percentiles(gp_2020, PC4)))
+
+```
 
@@
     all_drugs = contrast(best_bs_models$all_drugs, 
-                         list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                              ngp = 5, gp_load = 1329,
+                         list(Month = 3:8, wimd2019 = "Med", 
+                              ngp = median(gp_2020$ngp), 
+                              gp_load = median(gp_2020$gp_load),
                               PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                               dispensing = TRUE),
-                         list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                              ngp = 5, gp_load = 1329,
+                         list(Month = 3:8, wimd2019 = "Med", 
+                              ngp = median(gp_2020$ngp),
+                              gp_load = median(gp_2020$gp_load),
                               PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     cortico = contrast(best_bs_models$cortico, 
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                            ngp = 5, gp_load = 1329,
+                       list(Month = 3:8, wimd2019 = "Med", 
+                            ngp = median(gp_2020$ngp),
+                            gp_load = median(gp_2020$gp_load),
                             PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                             dispensing = TRUE),
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                            ngp = 5, gp_load = 1329,
+                       list(Month = 3:8, wimd2019 = "Med", 
+                            ngp = median(gp_2020$ngp),
+                            gp_load = median(gp_2020$gp_load),
                             PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     paracet = contrast(best_bs_models$paracet, 
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                            ngp = 5, gp_load = 1329,
+                       list(Month = 3:8, wimd2019 = "Med", 
+                            ngp = median(gp_2020$ngp),
+                            gp_load = median(gp_2020$gp_load),
                             PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     sal = contrast(best_bs_models$sal, 
-                   list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                        ngp = 5, gp_load = 1329,
+                   list(Month = 3:8, wimd2019 = "Med", 
+                        ngp = median(gp_2020$ngp),
+                        gp_load = median(gp_2020$gp_load),
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                         dispensing = TRUE),
-                   list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                        ngp = 5, gp_load = 1329,
+                   list(Month = 3:8, wimd2019 = "Med", 
+                        ngp = median(gp_2020$ngp),
+                        gp_load = median(gp_2020$gp_load),
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     vitd = contrast(best_bs_models$vitd, 
-                    list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                         ngp = 5, gp_load = 1329,
+                    list(Month = 3:8, wimd2019 = "Med", 
+                         ngp = median(gp_2020$ngp),
+                         gp_load = median(gp_2020$gp_load),
                          PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                          dispensing = TRUE),
-                    list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
-                         ngp = 5, gp_load = 1329,
+                    list(Month = 3:8, wimd2019 = "Med", 
+                         ngp = median(gp_2020$ngp),
+                         gp_load = median(gp_2020$gp_load),
                          PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
   arrange(drug) %>% 
-  kable
-
+  mutate(across(where(is.numeric), printnum),
+         contrast = paste0(Contrast, "[", Lower, ",", Upper, "]"),
+         Month = factor(x = Month, levels = 3:8,
+                           labels = month.abb[3:8])) %>%
+  pivot_wider(id_cols = drug, values_from = contrast, names_from = Month) %>%
+  kable(align = "r") %>%
+  kable_styling() %>%
+  landscape()
 ```
@@
     ace = contrast(best_bs_models$ace, 
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
-                            ngp = 5, gp_load = 1329,
+                   list(Month = 3:8, wimd2019 = "Low", 
+                        ngp = median(gp_2020$ngp), 
+                        gp_load = median(gp_2020$gp_load),
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                         dispensing = FALSE),
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                            ngp = 5, gp_load = 1329,
+                   list(Month = 3:8, wimd2019 = "High", 
+                        ngp = median(gp_2020$ngp), 
+                        gp_load = median(gp_2020$gp_load),
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     cortico = contrast(best_bs_models$cortico, 
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
-                            ngp = 5, gp_load = 1329,
+                       list(Month = 3:8, wimd2019 = "Low", 
+                            ngp = median(gp_2020$ngp), 
+                            gp_load = median(gp_2020$gp_load),
                             PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                             dispensing = FALSE),
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                            ngp = 5, gp_load = 1329,
+                       list(Month = 3:8, wimd2019 = "High", 
+                            ngp = median(gp_2020$ngp), 
+                            gp_load = median(gp_2020$gp_load),
                             PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     sal = contrast(best_bs_models$sal, 
-                   list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
-                            ngp = 5, gp_load = 1329,
+                   list(Month = 3:8, wimd2019 = "Low", 
+                        ngp = median(gp_2020$ngp), 
+                        gp_load = median(gp_2020$gp_load),
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     ssri = contrast(best_bs_models$ssri, 
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
-                            ngp = 5, gp_load = 1329,
+                    list(Month = 3:8, wimd2019 = "Low", 
+                         ngp = median(gp_2020$ngp), 
+                         gp_load = median(gp_2020$gp_load),
                          PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                          dispensing = FALSE),
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                            ngp = 5, gp_load = 1329,
+                    list(Month = 3:8, wimd2019 = "High", 
+                         ngp = median(gp_2020$ngp), 
+                         gp_load = median(gp_2020$gp_load),
                          PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     vitd = contrast(best_bs_models$vitd, 
-                    list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
-                            ngp = 5, gp_load = 1329,
+                    list(Month = 3:8, wimd2019 = "Low", 
+                         ngp = median(gp_2020$ngp), 
+                         gp_load = median(gp_2020$gp_load),
                          PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
   arrange(drug) %>% 
-  kable
+  mutate(across(where(is.numeric), printnum),
+         contrast = paste0(Contrast, "[", Lower, ",", Upper, "]"),
+         Month = factor(x = Month, levels = 3:8,
+                           labels = month.abb[3:8])) %>%
+  pivot_wider(id_cols = drug, values_from = contrast, names_from = Month) %>%
+  kable(align = "r") %>%
+  kable_styling() %>%
+  landscape()
 
@@
     oral_contra = contrast(best_bs_models$oral_contra, 
-                           list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                                ngp = 3, gp_load = 1329,
+                           list(Month = 3:8, wimd2019 = "Med", 
+                                ngp = 3, 
+                                gp_load = median(gp_2020$gp_load),
                                 PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                                 dispensing = FALSE),
-                           list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                                ngp = 8, gp_load = 1329,
+                           list(Month = 3:8, wimd2019 = "Med", 
+                                ngp = 8, 
+                                gp_load = median(gp_2020$gp_load),
                                 PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     sal = contrast(best_bs_models$sal, 
-                   list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                        ngp = 3, gp_load = 1329,
+                   list(Month = 3:8, wimd2019 = "Med", 
+                        ngp = 3, 
+                        gp_load = median(gp_2020$gp_load),
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                         dispensing = FALSE),
-                   list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                        ngp = 8, gp_load = 1329,
+                   list(Month = 3:8, wimd2019 = "Med", 
+                        ngp = 8, 
+                        gp_load = median(gp_2020$gp_load),
                         PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
     oral_contra = contrast(best_bs_models$oral_contra, 
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                        ngp = 8, gp_load = 1098,
+                           list(Month = 3:8, wimd2019 = "Med",
+                                ngp = median(gp_2020$ngp), 
+                                gp_load = 1098,
                                 PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
                                 dispensing = FALSE),
-                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
-                        ngp = 8, gp_load = 1710,
+                           list(Month = 3:8, wimd2019 = "Med", 
+                                ngp = median(gp_2020$ngp), 
+                                gp_load = 1710,
                                 PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
@@
 ```{r, summary-plot}
-# names(drugs) <- c("ACE inhibitors", "Inhaled corticosteriods", "
-#                   Hydroxychloroquine", "Non-steroidal anti-inflamatory drugs",
-#                   "Oral contraceptives", "Paracetamol", "Salbutamol", )
-
 contrasts <- 
@@
                             effect == 4 ~ "1710 per GP - 1098 per GP"),
-         drug = case_when(drug == "all_drugs" ~ "All",
+         drug = case_when(drug == "all_drugs" ~ "All dispensing",
                           drug == "ace" ~ "ACEi",
@@
   facet_wrap(~effect) +
-  labs(caption = paste0("Adjusted to Health Board = BC, Dispensing status = FALSE, WIMD = Med, Number GPs = 5, \nGP workload = 1329, PC1 = ", printnum(median(gp_2020$PC1))," PC2 = ", printnum(median(gp_2020$PC1)), " PC3 = ", printnum(median(gp_2020$PC3)), " PC4 = ", printnum(median(gp_2020$PC4))))
+  labs(caption = paste0("Unless specified, predictors adjusted to Dispensing status = FALSE, WIMD = Med, Number GPs = ", printnum(median(gp_2020$ngp)),", \nGP workload = ", printnum(median(gp_2020$gp_load)),", PC1 = ", printnum(median(gp_2020$PC1)),", PC2 = ", printnum(median(gp_2020$PC1)), ", PC3 = ", printnum(median(gp_2020$PC3)), ", PC4 = ", printnum(median(gp_2020$PC4))))
 
